### 2014-11-13 egpaper_final.tex
initial version

\documentclass[10pt,twocolumn,letterpaper]{article}

\usepackage{cvpr}
\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{caption}
\usepackage{verbatim}
\usepackage{subcaption}
\usepackage{algorithm2e}
\usepackage{rotating}
\usepackage[space]{grffile}
\usepackage[font=small,skip=0pt]{caption}
\DeclareMathOperator{\Tr}{Tr}
% Include other packages here, before hyperref.

% If you comment hyperref and then uncomment it, you should delete
% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
% run, let it finish, and you should be clear).
\usepackage[breaklinks=true,bookmarks=false]{hyperref}
\graphicspath{ {figures/} }
% \cvprfinalcopy % *** Uncomment this line for the final submission

\def\cvprPaperID{****} % *** Enter the CVPR Paper ID here
\def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}

% Pages are numbered in submission mode, and unnumbered in camera-ready
%\ifcvprfinal\pagestyle{empty}\fi
\setcounter{page}{1}
\begin{document}

%%%%%%%%% TITLE
\title{Enrich Object Detection : 2D-3D registration and continuous viewpoint estimation}

\author{First Author\\
Institution1\\
Institution1 address\\
{\tt\small firstauthor@i1.org}
% For a paper whose authors are all at the same institution,
% omit the following lines up until the closing ``}''.
% Additional authors and addresses can be added with ``\and'',
% just like the second author.
% To save space, use either the email address or home page, not both
\and
Second Author\\
Institution2\\
First line of institution2 address\\
{\tt\small secondauthor@i2.org}
}

\maketitle
%\thispagestyle{empty}

%%%%%%%%% ABSTRACT
\begin{abstract}
    Using 3D model to detect and register the model to RGB image has been a growing field of study. Recently, Aubry \etal \cite{Aubry14} and J. Lim \etal \cite{Lim14} tried to estimate pose and align exact CAD model to an image using part-based templates. Malisiewicz \etal \cite{Malisiewicz11} also addresses the issue by transferring metadata after detection. Hejrati \etal \cite{Hejrati14} uses template synthesis to detect an object. All these approaches require extensive training, a lot of memory space. Also, the training based approach requires defining fixed viewpoints which limit themselves.
  To overcome these difficulties, we propose an efficient and fast way to synthesize and validate templates using on the fly realistic rendering that can jointly optimize scale, translation, rotation and focal length continuously. We render an object and extract features and decorrelate spatial dependencies within them on the fly to make a discriminative template. To speed up the decorrelation procedure, we adopt a gradient based algorithm which is numerically more stable than decomposition procedure. Finally, we efficiently search for candidate match by computing convolution using FFT and jointly optimize to match the object accurately. To speed up further, we propose an efficient GPU implementation and tested on PASCAL images.

  In contrast to other mid-level patch based 3D matching methods which requires extensive training and more than 10Gb of memory space and physical storage, ours require no training nor saving the templates thus enabling it to run on any personal computer. 
\end{abstract}

%%%%%%%%% BODY TEXT
\section{Introduction}

\begin{figure}[t]
  \centering
  % \includegraphics[width=0.9\linewidth]{schematics} 
  \includegraphics[width=0.99\linewidth]{front} % \\[-5pt]
  % (a)\\[0pt]
  % \setlength\tabcolsep{0pt}
  % \begin{tabular}{cc}
  %     \includegraphics[width=0.45\linewidth]{car/orig2} & 
  %     \includegraphics[width=0.45\linewidth]{car/overlay2}
  %  %   \begin{tabular}{cc}
  %  %       \includegraphics[width=0.16\linewidth]{cad_car/2001-2004 Ford Ranger Edge} & 
  %  %       \includegraphics[width=0.16\linewidth]{cad_car/2002 Dodge Ram FedEx} \\ 
  %  %       \includegraphics[width=0.16\linewidth]{cad_car/2007-Nissan-Versa-_-Tiida-SL} & 
  %  %       \includegraphics[width=0.16\linewidth]{cad_car/2008-Jeep-Cherokee} \\ 
  %  %       \includegraphics[width=0.16\linewidth]{cad_car/2009 Toyota Cargo} & 
  %  %       \includegraphics[width=0.16\linewidth]{cad_car/2010-Chevrolet-Aveo5-LT} \\ 
  %  %       \includegraphics[width=0.16\linewidth]{cad_car/2012-Citroen-DS4}  
  %  %   \end{tabular}
  % \end{tabular}\\
  % (b)
  \caption{Using a bank of CAD models, we generate NZ-WHO templates which can be used to either detect objects directly or initialize pose of an object in the bounding box from other detectors. Once initialization is given, we use NZ-WHO to propose and validate plausible pose on-the-fly and further tune the translation, 3D viewpoint and focal length continuously.}
  % \vspace{-1em}
  \label{fig:front}
\end{figure}

% Object detection task has long been about predicting rectangular bounding boxes around the object. In this workthere has been significant many powerful object detectors such as Convolutional Neural Network or Part-Based Models \cite{Girshick14, Felzenszwalb10, Pepik12}

High performance object detectors usually generalizes very well. It can handle various intraclass variability, viewpoint change and occlusion. However due to this high generalization, sometimes it is very difficult to get accurate pose, category or 2D-3D matching. Our method, specialized in giving such accurate information, can be applied on any generic object detectors to give high quality metadata.

Matching 3D CAD model to an image has been a classical problem that dates back to eighties \cite{Lowe87}. Lowe \etal , the vision community instead focused on the object detection tasks that estimates a rectangular bounding box around an object\cite{Felzenszwalb10, Girshick14}. To infer what is more than a rectangle, several attempts have been made to estimate the pose of an object \cite{Xiang12, Pepik12, Fidler12, Hejrati14} or even finding corresponding CAD model as well \cite{Aubry14, Lim14}.

However, there has been increasing demand for accurate pose and 2D-3D matching. Notably, in graphics community, there has been growing demand for accurate 2D-3D matching \cite{Kholgade14, Chen13, Kostas14} for image manipulation, editing and data augmentation respectively.

Recently, with the powerful computing capabilities and a large collection of CAD models, the 2D-3D matching (registration) problem gets more and more approachable but due to inherent difficulty and limited performance of existing methods, many applications still require supervision to achieve 2D-3D matching.

% In medical community, registering 3D scan data to 2D image enabled various minimally invasive surgeries \cite{Markelj12}.

For category-level matching, \cite{Xiang12, Hejrati14, Pepik12} used 3D parts or aspect to represent underlying category-level 3D geometry of the object. With the advent of large public CAD datasets \cite{Trimble, Yobi}, the instance-level object detection and 2D-3D registration became possible. \cite{Aubry14, Lim14} used large collection of CAD models to faithfully align 3D CAD model to an image by rendering CAD models and creating 2D templates for various viewpoints.

Data-driven instance-level 2D-3D matching algorithms such as \cite{Aubry14, Lim14} require a large number of rendering and 2D templates for each of the CAD model with specific viewpoint. Since there are so many templates that it becomes almost impossible to get all the true positive image from training data. Instead \cite{Aubry14, Lim14} used whitening as a preprocessing stage \cite{Hariharan12} to make templates more discriminative. Then calibration is done on a small training dataset.

Although whitening to create template is faster than some of instance-level matching algorithms such as training Exemplar-SVM \cite{Malisiewicz11} or complicated models such as LEVAN \cite{Divvala14}, whitening and calibration large number of templates takes very long time. Also, once the fixed discrete viewpoint templates have been made and calibrated, it is difficult to fine-tune the prediction made using the large collection of templates.

%% Our contribution
With this growing usage of WHO template and Computer Graphics rendering, we decided to analyze WHO feature
[Find More Usage of WHO and CG rendering \cite{Pepik12}]

In our paper, we present Non-Zero Whiten Histograms of Orientations (NZ-WHO) to dramatically speed up the template generation and get rid of time consuming calibration and yet achieves performance on par with calibrated templates. First, we will present NZ-WHO is more discriminative than WHO and introduce Conjugate Gradient method to speed up the whitening and create a high resolution template in just 80 milliseconds. Also, using this fast NZ-WHO template generation, we present \textbf{on-the-fly} template generation to fine tune an initial pose estimation to continuously refine translation, viewpoints (yaw, roll, pitch) and focal length.

Our pipeline is simple, fast only requires CAD models and no validation images for calibration. This can be used for post processing stage of generic object detection. Our pipeline requires only several minutes to make templates for rough viewpoints and

We propose a simple method to register the most similar CAD model to an image and fine-tune viewpoint continuously without discriminative part search, training nor calibration. Our method is simple, fast and light-weight in terms of memory so that it can be easily applied on top of generic object detectors as a final stage of detection or can be used as a standalone detector.

% Although our method is geared toward instance-level 2D-3D matching, we evaluated the performance of the templates on PASCAL 2007 and PASCAL 2012 and PASCAL 3D dataset to measure the performance.

Our tuning stage not only refine position, scale and viewpoint, but also focal length as well to literally "fine-tune" the initial proposal. Though our 2D-3D matching method can be used as a rudimentary object detector, our simple tuning stage can be applied to any generic object detector to achieve state-of-the-art viewpoint estimation method.

Finally, we show several applications using our method. Since we have metadata such as CAD model and geometry, we reconstruct the object using 2D-3D matching. Also, since we do not need training image, we show that our 2D-3D matching performs better than standard detectors in categories where training data lacks. We then use our method for image query to pull out closest CAD model in a bank of CAD models.

Finally, unlike several CAD model alignment methods that uses  WHO \cite{Aubry13, Aubry14, Lim14}, we propose a novel pipeline that does not require calibration which is infeasible in continuous viewpoint estimation. We propose a simple add-on stage that can enrich object detections with high-quality 2D-3D alignment. The pipeline is simple and light weight so this can be easily adapted to be used for any generic object detectors. Also to facilitate the future work, all our alignment result on PASCAL12 and code are publicly available online.

% Recently, matching a 3D CAD model to an image, 2D-3D matching (registration), is gaining great momentum in various fields of study. 2D-3D matching using Structure from Motion \cite{Sattler11} uses existing 3D model to match the model to a query image. Also image manipulation using 3D CAD models has proven its potential. Kholgade \etal \cite{Kholgade14} and Chen \etal \cite{Chen13} require human input to match 3D models to an image to created realistic morphing or manipulation of the registered object. However, all these application requies human input. In this paper, we propose a novel on-the-fly template generation algorithm that can generate template quickly and validate 2D-3D pose and focal length continuously.

% Our code has been made publicly online \cite{Choy14} so that our algorithm can be used as a pipeline for 2D-3D registration after general purpose object detectors.

\subsection{Approach Overview}

Our method is in line with \cite{Aubry14, Lim14} in the sense that we use only renderings not real images. However, rather than using fixed sized mid-level patches, we use whole object and make root templates. By using root templates, there is no need to learn a discriminative patch dictionary or to calibrate the patches and an additional inference stage is not required. However, whitening the whole template is prohibitive for several reasons. All templates have different aspect ratios making it difficult to generate the covariance matrix $\Sigma$. Since the root templates are larger than mid-level patches, a very large auto-covariance $\Gamma$ is required. Lastly, time complexity of decorrelating a template with $n$ cells increases as $O(n^3)$, resulting in slow template generation and large residuals due to numerical errors accumulated while decomposing the covariance matrix $\Sigma$.

To overcome these difficulties, we propose the Non-Zero Whitened Histograms of Orientations with iterative Conjugate Gradient to generate templates in real time and enrich rectangular boxes with high quality 2D-3D matching. The 2D-3D matching provides a CAD model, sub-category, rendering, depth, viewpoint and focal length.

Our method can work as a standalone 2D-3D matching algorithm, or even as a standalone ensemble of exemplar-based object detectors (Figure \ref{fig:front}) but the real power comes from combining generic object detectors and complement rectangular bounding boxes. Our method is simple in design; is several orders of magnitude faster than traditional method; requires only CAD models; doesn't need images nor calibration, yet is powerful in giving high-quality metadata. These properties make our method ideal for complementing object detections.

To complement detection bounding boxes, we first search possible 2D-3D matching by running cached discrete viewpoint templates. Then, for the most probable match, we refine the initial matching using Metropolis Hastings. Since it requires iterations of proposal and validation, we present real time analysis of NZ-WHO template generation to show that this can be done on-the-fly. The fine tuning stage process jointly optimizes translation, yaw, roll, pitch, scale, and focal length continuously and also searches for different CAD models.

\section{Related Works}
\subsection{Whitened Histograms of Orientations(WHO)}
% History of Whitening and how whitening works
Whitening a signal has been a popular method in various signal processing communities as a preprocessing stage \cite{Martinsson05, Belouchrani00}. Whitening a signal makes its autocorrelation narrower which results in more delta-function like spike for true positives and zero elsewhere. More formally, suppose that we have a $k$-dimensional random variable $X \in \mathcal{R}^k$ with $Cov(X)=\Sigma$. By whitening the signal, i.e., $\tilde{X}=\Sigma^{-\frac{1}{2}}(X - E[X])$, we remove 2nd order correlation between all features. So, all elements in the random variable $\tilde{X} = \left[\tilde{X}_1, \tilde{X}_2, \dots, \tilde{X}_k\right]$, become more independent. Since they become less dependent, convolving the whitened template with random signal will produce Gaussian noise on background signal but will produce delta-function like response on the match. Recently, \cite{Hariharan12} used whitening on HOG feature and named the whitened HOG as Whitened Histograms of Orientations (WHO).

% Using HOG
% In this paper, we also used Histograms of Orientations feature \cite{Dalal05} but in general, we could use any dense features.

\subsection{More than a Bounding Box}

High performance object detectors generalize very well \cite{Felzenszwalb10, Girshick14}. They can handle intraclass variability, change in viewpoint and truncation. However due this generalization, they lose fine-grained information such as accurate pose and object sub-category.

To give more than just a rectangular bounding box, \cite{Pepik12, Xiang12, Fidler12, Xiang14, Hejrati14, Aubry14, Lim14} various methods exist to jointly detect and estimate the pose of an object. \cite{Xiang12, Hejrati14, Fidler12} used 3D representations that deform as viewpoint changes and \cite{Pepik12} uses geometric constraints to regularize 2D appearance models.

On fine-grained pose estimation, \cite{Zia13} uses a 3D deformable wireframe model with parts to accurately predict pose and align the model.

More recently, \cite{Aubry14, Lim14} showed a success in joint instance-level object detection and pose estimation. To estimate pose, they rely on synthetic renderings of CAD models and learn discriminative mid-level patches. \cite{Aubry14} finds discriminative mid-level patches and calibrates them on a small set of real images. Similarly, \cite{Lim14} finds and learns relative discriminativeness of the shared mid-level patches.

% specialized in giving such accurate information, can be applied on any generic object detectors to give high quality metadata.
% Many 
% Since the WHO does not require extensive training such as \cite{Felzenszwalb10, Malisiewicz11, Girshick14}, WHO is gaining momentum in 2D-3D matching. \cite{Aubry13, Aubry14, Lim14} combined WHO with synthetic rendering to jointly detect and estimate pose by making mid-level patches using WHO. Using this
% WSuch approach has an advantage over generic detections. First, it is easy to trace the detection to specific template. The template also has The rendering has corresponding CAD model and viewpoint thus enabling joint detection and viewpoint estimation. 
% To deal with textureless background \cite{Aubry13} whitens HOG feature and then zero out the WHO feature where there is no texture. But centering a HOG feature where there is no edge creates strong negative edges. We found out that centering only non-zero cells help detection but whitening all cell makes features to leak out to texture-less regions.
% With increasing popularity of rendering image, whitening, traditional signal processing technique, as a preprocessing stage has been widely used also in computer vision community.
% Many object detectors \cite{Felzenszwalb10, Malisiewicz11}
% \subsection{Mid-level Patches for 2D-3D matching}
%  FPM introduction : per instance matching  
%  Seeing 3D chair : mid-level patches

%\begin{comment}
%  \subsection{Contributions}
 % \begin{enumerate} \itemsep1pt \parskip0pt \parsep0pt
  %  \item Introduces Non-Zero Whitened Histograms of Orientations (NZ-WHO) for real-time template generation
   % \item Continuous viewpoint and focal length tuning using on-the-fly template generation
%    \item Jointly optimizes translation, 3D viewpoint, CAD models and focal length
%     \begin{comment}
%       \item HOG Whitening procedure that do not require calibration stage
%     \end{comment}
%  \end{enumerate}
% \end{comment}
% All the code and CAD models is publicly available online \cite{Choy14} (currently not disclosed for anonymous review, visualizations are available in the supplementary material).

\section{2D-3D Matching using Non-Zero Whitened Histograms of Orientations(NZ-WHO)}
\label{sec:nz-who}

We propose a variation of Whitened Histograms of Orientations (WHO) \cite{Hariharan12} that can generate a template in 70ms (compared to several seconds to generate a WHO template) that is more discriminative than WHO. We call this Non-Zero Whitened Histograms of Orientations (NZ-WHO).

The first innovation comes from using an iterative Conjugate Gradient method. To whiten a HOG template, one solves a system of linear equations $\Sigma w = (x - \mu)$ often by decomposing the matrix (LU decomposition or Cholesky decomposition). Since the covariance matrix of HOG have nice spectral properties, we can adopt the iterative Conjugate Gradient method to quickly solve the system of linear equations several orders of magnitude faster than decomposition methods.

The second innovation is 'Non-Zero' whitening. Unlike natural images, rendering produces textureless background such as Figure \ref{fig:rendering}. If we use random natural images as a background to make texture, the gradients in the background patch become part of the discriminative patch. On the other hand, if we treat the image as a natural image and whiten all region, it creates several artifacts: 1. while centering the template (subtracting the mean $\mu$), it introduces strong negative gradients on textureless region (Figure \ref{fig:whocomparison}); 2. when decorrelating the centered feature, $\Sigma^{-1}(x - \mu)$, it tries to remove correlation where there is none; 3. by including background regions, the size of the signal $x$ gets larger.

To get rid of such artifacts, we select cells with non-zero gradients, whiten regions, and restore the template afterward. We call the feature from the pipeline as Non-Zero Whitened Histograms of Orientations. More detailed analysis of WHO and NZ-WHO is on Table \ref{tab:who_initializations}

% We compare the performance of WHO and NZ-WHO on 3D Object dataset \cite{Savarese07} and report performance on Table \ref{tab:who_initializations}.

% To deal with the problems, we propose Non-Zero Whitened Histograms of Orientations.

% To accommodate the growing usage of rendering image for 2D-3D matching using WHO\cite{Aubry13, Aubry14, Lim14}, we analyzed various methods to whiten synthetic rendering image and propose Non-Zero Whitened Histograms of Orientations (NZ-WHO) which is a direct extension of \cite{Hariharan12} designed for rendering images with textureless background. % Since a NZ-WHO template has zero-mean and all elements in the template follow same distribution, no explicit calibration is required if all the templates have approximately the same number of cells.

% Since Combining NZ-WHO with Conjugate Gradient,

% \subsection{Non-Zero Whitened Histograms of Orientations (NZ-WHO)}
% why non zero whitening and why it makes more sense than seeing 3D, IKEA
% Overview of the subsections
%   Generating covariance quickly
%   Fast inversion
%   Regularization

\begin{figure}[t]
  \begin{center}
%   \fbox{\rule{0pt}{2in} \rule{0.9\linewidth}{0pt}}
    % include whitening all centered cells
    % \includegraphics[width=0.32\linewidth]{whiten_all_crop}
    \setlength\tabcolsep{3pt}
    \begin{tabular}{ccc}
      HOG & WHO & NZ-WHO \\
%     \begin{turn}{90}$w_+$\end{turn} &
    \includegraphics[width=0.28\linewidth]{hog_crop} &
    \includegraphics[width=0.28\linewidth]{whiten_all_crop} &
    \includegraphics[width=0.28\linewidth]{whiten_non_zero_crop} \\
    % include whitening all centered cells
     % \includegraphics[width=0.282\linewidth]{whiten_all_neg_crop} 
%     \begin{turn}{90}$-w_-$\end{turn} &
     \includegraphics[width=0.28\linewidth]{hog_neg_crop} &
     \includegraphics[width=0.28\linewidth]{whiten_all_neg_crop}  &
     \includegraphics[width=0.28\linewidth]{whiten_non_zero_neg} \\
    % include whitening all centered cells
 %    \begin{turn}{90}ihog\cite{vondrick2013}\end{turn} &
    % \cite{vondrick2013}& 
     \includegraphics[width=0.28\linewidth]{ihog_hog200_crop.png} &
     \includegraphics[width=0.28\linewidth]{ihog_whiten_all200_crop.png} &
     \includegraphics[width=0.28\linewidth]{ihog_whiten_non_zero200_crop.png} \\
 \end{tabular}
  \end{center}
  \caption{Comparison of HOG, WHO and NZ-WHO. Visualization of positive weights (first row),  visualization of negative weights (second row), HOGgles \cite{vondrick2013} (third row). Note that for WHO, whitening all cell result in strong negative edges on the empty region}
  \label{fig:whocomparison}
\end{figure}

% Overview of the subsections
% In this section, we will give a brief overview of whole whitening stages. In the first section \ref{feature_statistics}, we will discuss about first and second order statistics of HOG feature. Then, we will discuss about using autocovariance $\Gamma$ to create covariance matrix $\Sigma$ for non-zero cells and SIMD implementation to speed up the generation. Then, we will explain fast and accurate way to solve $w = \Sigma^{-1}x$ using Conjugate Gradient method. % Finally, we will analyze the effect of regularization.

% \subsection{Whitening and Textureless Background}

\subsection{Feature Statistics and Covariance Synthesis}
\label{sec:feature_statistics}
% Whats used in our work and using Autocovariance matrix
We first collected the first and second order statistics (mean and autocovariance of HOG feature) of HOG feature from arbitrary natural images. Following the practice of \cite{Hariharan12}, which assumes Wide-Sense Stationarity (WSS) of HOG features, we can easily synthesize covariance of arbitrary size template from autocovariance $\Gamma$. To further simplify $\Gamma$, we assumed horizontal and vertical symmetry.

% Since the statistics have been computed for a generic HOG feature, we can use the same statistics for all templates and images. In practice, since it is expensive to whiten all the sliding patches in the image, we followed \cite{Hariharan12} and defined the templates to be $w = \Sigma^{-1}(X-E[X])$\begin{comment}which is a good approximation of $\Sigma^{-\frac{T}{2}} \Sigma^{-\frac{1}{2}}(X-E[X])$\end{comment}

% \begin{comment}Gathering statistics, especially computing spatial covariance of a signal is computationally burdensome. \end{comment}
% To speed up the statistics collection, \begin{comment}in addition to the wide-sense stationarity (WSS) of HOG, \end{comment}we assumed horizontal and vertical symmetry of covariance.

 %Hariharan \etal \cite{Hariharan12} interpreted the whitening also as the Linear Discriminant Analysis where each class has the same covariance $\Sigma$ but with different mean value. They defined this whitened HOG feature as Whitened Histograms of Orientations (WHO) and we will follow their convention of the name.

% \subsection{Rendering}
% 
% We used a public rendering engine to create realistic rendering and depth\begin{comment}\cite{Choy14render}\end{comment}. The CAD models we used in our experiments contain color, texture and material information such as transparency and reflectance. We tried to make the rendering as much realistic as possible to simulate the natural image statistics. The example rendering is in Fig. \ref{fig:rendering}. We also extracted depth information as well while rendering to use in the reconstruction.

% To whiten a HOG features, we first have to synthesize the covariance matrix. Following the method of \cite{Hariharan12}, which assumes spatial Wide-Sense Stationarity (WSS) of a feature, covariance matrix can be synthesized using spatial autocovariance $\Gamma$. This assumes the \begin{comment} and features such as HOG are gradients in a small patch whose statistics does not change (an object can be in anywhere in an image)\end{comment}.

More formally, let $x(u)$ be the HOG feature on location $u$ then, by WSS, $\mathbb{E}\left[x(u)\right] = \mathbb{E}(x(u+v)) = \mu_x$ and $\mathbb{E}\left[(x(u)-\mu_x)(x(v)-\mu_x)\right]  =\mathbb{E}\left[(x(0)-\mu_x)(x(v-u)-\mu_x)\right] = \Gamma(0,v-u)$. So, one can synthesize covariance matrix from autocovariance $\Gamma$. For simplicity, we used 1D case but this can be easily extended to 2D spatial autocovariance.

However, unlike small fixed-sized mid-level patches, the root templates have different aspect ratios, different gradient patterns and large number of HOG cells which results in large covariance $\Sigma \in \mathcal{R}^{7000 \times 7000}$ that is difficult to cache. Thus, to generate a NZ-WHO template, we have to synthesize a covariance matrix and solve the system of linear equations.

Synthesizing the covariance matrix is memory copy operations so we used GPU to speed up the process (Figure \ref{fig:covariancetime}).

% Thus, every time we whiten a root template, we have to generate a covariance matrix using autocovariance $\Gamma$.

%\begin{comment} Also, since we are whitening only the non-zero HOG cells whose position is unknown beforehand and all templates have different aspect ratio for , we cannot cache the matrix. Using CPU, it takes about \end{comment}

% In practice, synthesizing covariance matrix $\Sigma$ takes long time due to its large size.  $\Sigma$ ranges from $\Sigma \in \mathcal{R}^{7000 \times 7000}$ to $\Sigma \in \mathcal{R}^{7500 \times 7500}$. We vary the template resolution and run $\Sigma$ generation on CPU and GPU 100 times and report the average time in Fig. \ref{fig:covariancetime}.

\begin{figure}[t]
  \begin{center}
     \includegraphics[width=0.9\linewidth]{covariancetime} 
  \end{center}
  \caption{Time to generate $\Sigma$ for various number of cells (left) and same plot on log scale(right). The time complexity increases as $O(n^2)$ for $n$ number of cells.}
  \label{fig:covariancetime_crop}
\end{figure}

% 1-dimensional version of SIMD implementation that generate covariance matrix $\Sigma$ from autocovariance $\Gamma$ on GPU is on the supplementary material.
% \begin{comment}i
% \begin{algorithm}
% \KwData{ $\Gamma$ , nonzero cell indexes, thread x id, thread y id}
% \KwResult{ $\Sigma$ }
% \Begin{
% $c_u \leftarrow \mod(x, N_f)$ define cell $u$ coordinate\; 
% $f_u \leftarrow u / N_f$ define feature index
% $c_v \leftarrow \mod(y, N_f)$ define cell $v$ coordinate\;
% $f_v \leftarrow v / N_f$ define feature index
% $T \leftarrow $ nonzero cell indexes\;
% $\Sigma(w) \leftarrow \Gamma( N_f ( T(u) - T(v) +  )$\;
% }
% \caption{SIMD implementation of covariance synthesis from autocovariance}
% \end{algorithm}
% \end{comment}

\subsection{Fast Whitening and Non-Zero Selection}

\begin{figure}[t]
  \begin{center}
     \includegraphics[width=0.9\linewidth]{whiten_orig_depth} 
  \end{center}
  \caption{Realistic rendering and depth}
  \label{fig:rendering}
  \end{figure}

To whiten a signal $x$, we have to solve $\Sigma w = x - \mu$ which takes $O(n^3)$ time. In \cite{Hariharan12}, the authors make use of Positive Semi-Definite and Hermitian properties of a covariance matrix to use Cholesky decomposition and Gaussian elimination which is twice faster than LU decomposition.

However, if we make use of a spectral property of the covariance matrix, we can further speed up the whitening stage.

  If we use a high resolution template such as \ref{fig:rendering}

% where $w$ is the weight we want to find and $x$ is the HOG feature from the rendering and $\lambda$ is the regularization constant (see section \ref{sec:regularization}). For $w\in \mathcal{R}^n$, it takes $O(n^3)$ time to solve the linear equation. If we use a high resolution template to capture small geometric properties we can get high accuracy matchings but the solving the linear equation becomes computationally burdensome.

% To briefly recap, the LU Decomposition and Cholesky Decomposition are most popular methods to solve a linear equation. In linear algebra libraries such as MATLAB, these decomposition methods are default method to solve a linear equation (backslash \textbackslash in MATLAB). Since the covariance matrix is Hermitian and Positive Semi-Definite, we can use Cholesky Decomposition which is twice as fast as the LU Decomposition.

% decomposition methods such as LU or Cholesky Decomposition not only take long time but they also accumulate numerical error.

In our setting, we used high resolution template which has more than 250 HOG cells. This result in $\Sigma \in \mathcal{R}^{7500 \times 7500}$. It takes about 9 seconds if we use LU decomposition and 5 seconds if we use Cholesky decomposition.  % The default way of solving the linear equation in many linear algebra library is decomposing the matrix using LU Decomposition (in MATLAB the default method of backslash operator) which takes $O(\frac{2}{3}n^3)$ flops for $n\times n$ matrix. Since the matrix, $\Sigma + \lambda I$ is Hermitian and Positive Semi Definite. We can speed up using Cholesky Decomposition.

We also used iterative Conjugate Gradient to make use of low rank property of the covariance \cite{Gharbi12}. After adding small regularization, the regularized covariance matrix has nice spectral property (Figure \ref{fig:spectral}. The singular values are clustered in small region and most of the energies are concentrated on the first (number) singular values. Thus, the conjugate gradients stage doesn't go upto the size of the matrix to converge.

\begin{figure}[t]
  \begin{center}
  \begin{tabular}{cc}
     \includegraphics[width=0.5\linewidth]{whotime} & 
     \includegraphics[width=0.5\linewidth]{speedup}\\
     (a) & (b) \\
 \end{tabular}
  \end{center}
  \caption{Comparison of HOG variants generation time and final }
  \label{fig:whotime}
\end{figure}
[Figure spectral analysis]

\begin{figure}[t]
  \centering
  \includegraphics[width=0.5\linewidth]{residual}
  \caption{Residual of differentd method}
  \label{fig:whotime}
\end{figure}

\subsection{Variations of WHO}

We empirically found out that NZ-WHO performs reasonably well without time consuming calibration stage compare to other variational method to generate templates. We used 1 CAD model with viewpoints covering 24 azimuths and 4 elevations. Each template takes approximately 80 milliseconds to generate a NZ-WHO template. We also calibrated templates using the method presented in \cite{Aubry14}. The calibration learns affine transformation of the detection confidence.% Note that in Section \ref{experiments}, we provide the same experiment with 9 CAD models.

\begin{table*}[!htbp]
    \begin{center}
\begin{tabular}{|c|c|c|c|c|}
\hline
Methods &  without Calibration (AP/AVP) & time & w/ Calibration \cite{Aubry14} (AP/AVP) & time \\
\hline\hline
HOG\cite{Dalal05}     & 72.28/48.38  &  31ms  & 60.37/50.19               &   8.7 sec \\ 
WHO-Chol\cite{Hariharan12} &              &3811ms    &                           &   12.4 sec  \\
WHO-GG                & 81.70/74.20  &104ms &     83.714/75.37              &   8.3 sec \\
WHO-CG-Z              & 54.42/49.71  &103ms & \textbf{92.80}/\textbf{81.44} &   8.7 sec  \\
% NZC-WHO-Z    & 89.10/\textbf{78.64} &    & 91.15/74.79                  &     \\
NZ-WHO-CG        & \textbf{90.00}/78.23 & 79ms & 90.31/78.00                   &  8.5 sec   \\
\hline
\end{tabular}
\end{center}
\caption{Average Precision(AP) and Average Viewpoint Precision(AVP) \cite{Xiang14} of variations of WHO on 3DObject Car dataset\cite{Savarese07}. WHO\cite{Hariharan12} whitens all cell, WHO-ZZ whitens all cell then zero out textureless region. NZC-WHO-ZZ first substract mean $\mu$ on non-zero cells and whiten all cells then zero out textureless region. NZ-WHO whitens only non-zero cell. Note that WHO-ZZ got dramatic performance boost after calibration due to strong impact of substracting $\mu$ from all textureless region}
\label{tab:who_initializations}
\end{table*}

We found out that without calibration, NZ-WHO performs the best on object detection on 3DObject car dataset \cite{Savarese07}. See Table \ref{tab:who_initializations} for detail. In essence, if we use calibration, we could achieve better performance but since our goal is to do 2D-3D matching and continuous viewpoint estimation using on-the-fly template generation, we did not calibrated our templates.

\begin{comment}
\subsection{Whitening Non-Zero Cells}

% learning weights for whitened templates
But since it is difficult to make templates to have the number of cells, \cite{Hariharan12, Aubry14, Lim14} learned weights for convolution score from the template. However, we propose a novel way to guarantee normalized score distribution by decorrelating non-zero HOG cells and forcing each template to have approximately same number of cells.

% 
Unlike \cite{Aubry14}, we did not whiten all cells and then zero out some HOG cells that are on the background. Instead, we whiten only the cells with non-zero value. We empirically found out that by whitening the cells that has non-zero support actually performs better and takes less time solving the linear equation $w = \Sigma^{-1}x$ since the number of elements to whiten decreases. However, by selecting non-zero cells, we destroys inherent Toeplitz-Block-Toeplitz property of the covariance matrix which could speed up the inversion using Fourier Transformation \cite{Akaike73, Martinsson05}.

  We propose a whitening stage for WHO feature template generation that can create template whose convolution score follow same distribution. This guarantees that we do not require any calibration stage after generating templates rapidly. We statistically compare the score distribution of whitening non-zero HOG cell only and whitening.
  \end{comment}

% \subsection{Effect of Regularization}
% \label{sec:regularization}
%  Also, since all covariance matrix is Positive Semi Definite, our matrix $\Sigma$ must be Positive Semi-Definite too. To guarantee the property, We found out that the regularization has significant impact on the performance. In \cite{Hariharan12}, Hariharan \etal used small fixed regularization since the covariance matrix of specially correlated features is intrinsically row-rank to make the matrix invertible.
%  
% However if we closely analyze the impact of the regularization, we can see that larger the $\lambda$ is, the centered HOG becomes more dominant. 
% 
% \begin{align}
% (\Sigma + \lambda I)^{-1} & = \frac{1}{\lambda}\left(I + \frac{1}{\lambda}\Sigma \right)^{-1} \\
% & = \frac{1}{\lambda}\left(I - \frac{1}{\lambda} \Sigma  + \frac{1}{\lambda^2} \Sigma^{2} 
% 		- \frac{1}{\lambda^3} \Sigma^{3} + \cdots \right)
% % & = \frac{1}{\lambda}I - \left(I + \frac{1}{\lambda} \Sigma \right)^{-1} \frac{1}{\lambda^2} \Sigma
% % & = \frac{1}{\lambda}\left(I  - \frac{1}{1 + \frac{1}{\Sigma} \Tr{\Sigma}} \right)
% \end{align} 
% 
% We empirically found out that as $\lambda$ increases, AP converges to that of centered HOG feature without any whitening.

\begin{comment}
\subsection{No Calibration}
  We created coarse viewpoint templates by whitening non-zero HOG cells and compare the average precision on 3D Object dataset \cite{Savarese07} with that of whitening all HOG cells.

\begin{table}
\begin{center}
\begin{tabular}{|l|c|c|}
\hline
Whitening and AP & Whiten & No Whitening \\
\hline\hline
Average Precision & 89.205 & 74.478 \\
\hline
\end{tabular}
\end{center}
\caption{Effect of whitening on 3D Object Car validation set using one CAD model. The whitening dramatically increased the AP.}
\end{table}
\begin{table}
\begin{center}
\begin{tabular}{|l|c|c|}
\hline
Calibration methods \&AP & Whiten non-zero & Whiten all \\
\hline\hline
None & 89.205 & 86.676 \\
Linear & 88.430 & 85.720 \\
Gaussian & 87.913 & 84.567\\
Number of non-zero cells & 84.734 & N/A\\
\hline
\end{tabular}
\end{center}
\caption{Various calibration and AP on small experimental set. Since the whitening templates with constant number of HOG cells create normalized feature, calibration using negative patches did not improve the AP.}
\end{table}
\end{comment}

\subsection{High Resolution Templates and FFT based Convolution}
\label{sec:fft} 
We generate high resolution templates with more than 250 HOG cells to capture details of an object to give accurate 2D-3D matching. These large templates cause computational burden when computing convolution. Though good for detecting accurate model and pose, convolution of high-resolution templates are much more slower since computation time scales linearly with the number of HOG cells in the template. To overcome and speed up the convolution, we propose FFT based GPU convolution which scales. Suppose there are length $n$ signal and length $m$ filter, naive convolution takes $O(nm)$ time where as FFT-based convolution takes $O\left( (n + m)\log (n+m) \right)$ time. For large $m$, high resolution template, we can gain computational advantage.

we pad zero to the 2D image features by the largest kernel size. And we transform the kernel to match the padded image feature. To compute convolution, we compute element-wise product with the transformed kernel and sum all the features. Unlike \cite{Podlozhnyuk}, we do not need to shift the data nor kernel if we use simple mathematical trick.

\begin{align}
    x_{pad} & = \mathcal{P}_{n+m}(x)\\
    y_{pad} & = \mathcal{P}_{n+m}(y)\\
    x_{pad} \ast y_{pad} & = \mathcal{F}^{-1}(\mathcal{F}(x_{pad}) \circ \mathcal{F}(y_{pad}))
\end{align}

  Where $\ast$ is the circular convolution and $\circ$ is the Hadamard Product and $\mathcal{F}$ is the Fourier Transformation and $\mathcal{P}_n$ is the padding operation that append zeros to make vector of size $n$.

For each dimension of features, we transform kernel and image feature into frequency domain using Fast Fourier Transformation. We transform the image into frequency domain once and use the transformed image for all templates.

We implemented the convolution using FFT on GPU and got 10x speed up.

[Figure for convolution time for different template resolution, CPU, GPU, naive convolution]

%------------------------------------------------------------------------

\section{Continuous Viewpoint and Focal Length Estimation for Fine Tuning}

% Estimating viewpoint continuously to fine tune a initial matching 
Since creating a template and validating the template become computationally inexpensive, making a proposal and validating the proposal to fine tune a 2D-3D matching became affordable. We used Metropolis-Hastings algorithm to generate a proposal pose and focal length and validate the proposal using the convolution and returning maximum response as a return.

We modeled the distribution of the convolution as an exponential distribution and used Gaussian as our proposal distribution.

We run experiments on PASCAL 2007 car category images with at least one car (num images) and got x percent improvement after fine tuning.

% there are several advantages that was not possible such as \textbf{on-the-fly} template generation and making large number of templates  
\begin{figure}[t]
 \begin{center}
    \includegraphics[width=0.9\linewidth]{tuning2} 
    \includegraphics[width=0.9\linewidth]{tuning} 
 \end{center}
 \caption{Effect of fine tuning. (left) original image, (middle) initial detection, (right) continuous fine tuning}
 \label{fig:tuning}
\end{figure}

\section{Experiments}

In this section, we validate our proposed NZ-WHO templates in two different ways. First, we make a set of NZ-WHO templates for a set of CAD models from various viewpoints. Then we run the bank of NZ-WHO templates as ensembles of weak detectors and show that the rendering image can be We want to see how robust the NZ-WHO to real images a

\subsection{Object Detection} 
Instance-level 2D-3D matching (registration) is a difficult problem since we need a CAD model that looks similar to the object in the image. Especially, due to extreme intraclass variability of chair \cite{Aubry14} used a very large collection of CAD models to cover variety of chairs. Similarly, \cite{Lim14}
\begin{table}[!htbp]
  \begin{center}
    \begin{tabular}{|c|c|c|c|}
    \hline
     AP/MPPE& Ours & ALM\cite{Xiang12} & VOCDPM\cite{Pepik12} \\
    \hline\hline
    car & \textbf{99.8}/91.7 &  98.4/93.4 & \textbf{99.8}/\textbf{97.5} \\ 
    bicycle & 93.0/87.4 & 93.0/91.4 & \textbf{98.8}/\textbf{97.5} \\
    \hline
    \end{tabular}
  \end{center}
  \caption{Average Precision(AP) and Average Viewpoint Accuracy(AVA) on 3DObject dataset. Though we do not need any training images and made templates in few minues, it performs on par with state of the art detectors yet it gives high quality 2D-3D matching.}
  \label{tab:3dobject}
\end{table}

\begin{figure}[h]
    \begin{center}
    \setlength\tabcolsep{0pt}
\begin{tabular}{cc}
  \includegraphics[width=0.45\linewidth]{car_3dobject/7.png} &   
  \includegraphics[width=0.45\linewidth]{car_3dobject/8.png}\\ [-15pt]
%   (a) & (b) \\[0pt]
  \includegraphics[width=0.45\linewidth]{car_3dobject/11.png} &   
  \includegraphics[width=0.45\linewidth]{car_3dobject/12.png}\\ [-5pt]
%  (c) & (d) \\[0pt]
\end{tabular}
\end{center}
\caption{Detection results on 3D-Object dataset \cite{Savarese07}, each of four images have (top left) original image, (top right) top detection rendering overlaid, (bottom right) false positives, (bottom left) true positives. Each with confidence score and colored bounding box}
  \label{fig:3dobject}
\end{figure}

% Also, we evaluated our method on PASCAL 2007 dataset.
% 
% \begin{table}[!htbp]
%   \begin{center}
%   \begin{tabular}{|c|c|c|c|c|}
%     \hline
%      AP &    Ours &    ELDA \cite{Hariharan12} & ESVM \cite{Malisiewicz11} & VOCDPM \cite{Pepik12} \\
%     \hline\hline
%     car      & 27.          &  38.4  & 40.1    &65.7  \\ 
%     bicycle  & 43.74 & 41      &  40.7   & 61.3   \\
%     \hline
%     \end{tabular}
%   \end{center}
%   \caption{Average Precision(AP) on PASCAL 2007 dataset. Though we do not need any training images and made templates in few minues, it performs on par with state of the art detector yet it gives high quality 2D-3D matching.}
%   \label{tab:pascal07}
% \end{table}

\subsection{Fine-Tuning and Viewpoint Estimation}

High performance object detectors usually generalizes very well. It can handle various intraclass variability, viewpoint change and occlusion. However due to this high generalization, sometimes it is very difficult to get accurate pose, category or 2D-3D matching. Our method, specialized in giving such accurate information, can be applied on any generic object detectors to give high quality metadata.

To show such ability, we evaluated our method on PASCAL 3D dataset \cite{Xiang14}. The dataset augments PASCAL 2012 images with high quality viewpoint annotations thus is ideal to measure pose estimation. The dataset proposes new metric called Average Viewpoint Precision (AVP) where it measures the area under viewpoint precision and detection recall curve. The viewpoints is measured by azimuth similarity. If the distance between predicted azimuth and ground truth azimuth is below a certain threshold, the viewpoint is correct. Note that the baseline methods (V-DPM, VOC-DPM) reported on the PASCAL 3D dataset are variants of DPM where each component of DPM account for various azimuths. Thus V-DPM and VOC-DPM provide discrete azimuth only whereas our method provides 3D viewpoint (yaw, pitch, roll), CAD instance (model index, rendering, depth) and focal length.

\begin{table*}[!htbp]
    \footnotesize
  \begin{center}
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline
AP/AVP              & VDPM \cite{Xiang14} & VOC-DPM \cite{Pepik12}  & \cite{Pepik12} + Ours (discrete) & \cite{Pepik12} + Ours (full) & R-CNN + Ours (discrete) & R-CNN + Ours (full)\\
\hline\hline
car-4v              & 37.2 / 20.2         & 45.6 / 36.9             & 47.6 / 42.7       & 47.6 / \textbf{42.7}        & 49.6 / 41.5         & 49.6 / 41.5\\ \hline
car-8v              & 37.3 / 23.5         & 47.6 / 36.6             & 47.6 / \textbf{39.8}       & 47.6 / 39.5        & 49.6 / 38.0         & 49.6 / 39.0\\ \hline
car-16v             & 36.6 / 18.1         & 46.0 / 29.6             & 47.6 / 32.7       & 47.6 / 33.0        & 49.6 / 34.0         & 49.6 / \textbf{34.3}\\ \hline
car-24v             & 36.3 / 13.7         & 42.1 / 24.6             & 47.6 / 27.4       & 47.6 / 27.4        & 49.6 / 27.0         & 49.6 / \textbf{27.6}\\ \hline
\hline
bicycle-4v          & 45.2 / 41.7         & 46.9 / 43.9             & 48.1 / 47.6       & 48.1 / 46.6        & 61.7 / 56.5         & 61.7 / \textbf{56.7}\\ \hline
bicycle-8v          & 47.3 / 36.7         & 48.1 / 40.3             & 48.1 / 40.6       & 48.1 / 40.6        & 61.7 / 48.9         & 61.7 / \textbf{49.2}\\ \hline
bicycle-16v         & 46.5 / 18.4         & 45.6 / 22.9             & 48.1 / 26.2       & 40.1 / 27.3        & 61.7 / 34.7         & 61.7 / \textbf{35.8}\\ \hline
bicycle-24v         & 44.4 / 14.3         & 45.9 / 16.7             & 48.1 / 21.5       & 40.1 / 20.9        & 61.7 / \textbf{27.0}         & 61.7 / 23.9\\ \hline
\end{tabular}
\end{center}
\caption{Average Precision(AP) and Average Viewpoint Precision(AVP) on PASCAL 3D dataset\cite{Xiang14}. For combined method (* + Ours), we use bounding boxes from * and augment viewpoint using our method. R-CNN and run our method to produce 2D-3D matching. If our method fails to give viewpoint, it predicts the viewpoint to be 0. Note that our method gives high quality metadata such as continuous 3D viewpoint, CAD model (rendering depth) and fine-grained category, whereas base-line methods gives 1D discrete azimuths. Our R-CNN was not an optimized version so the detection AP is lower than the state-of-the-art R-CNN performance}
\label{tab:pascal12}
\end{table*}

\subsection{Stability of Our Method for Irregular Bounding Boxes}

Generic object detectors sometimes give overlapping detection bounding boxes of the same object with different aspect ratio or truncation. For instance, R-CNN \cite{Girshick14} usually gives very irregular bounding boxes since the proposals bounding boxes comes from various methods.

To handle such irregular shape and truncation, we added small context around the bounding boxes and run our method. We consider all possible truncation which can be efficiently computed using FFT-based convolution (refer Section. \ref{sec:fft}). We put examples of such conditions in Figure \ref{fig:stability}. Although the input bounding boxex are drastically different and have sever truncations. Our method reliably generated reasonable prediction of pose and model.

\begin{figure}[h]
\setlength\tabcolsep{5pt}
\begin{tabular}{cc}
  \includegraphics[width=0.45\linewidth]{car_pascal/1.png} &   
  \includegraphics[width=0.45\linewidth]{car_pascal/2.png} \\   
  \includegraphics[width=0.45\linewidth]{car_pascal/3.png} &   
  \includegraphics[width=0.45\linewidth]{car_pascal/4.png} \\   
\end{tabular}
\caption{Stability of our method for overlapping R-CNN detection \cite{Girshick14}. Blue box is the R-CNN detection that is feed into the system as initial detection. Purple box and overlaid rendering is the final output of the system. Note that for various overlapping bounding boxes, our system accurately estimated the reasonable result}
  \label{fig:stability}
\end{figure}

% For qualitative examples, we put hand-picked results from our method Fig. \ref{fig:car} and Fig. \ref{fig:bicycle}.

% \begin{figure*}[h]
% \setlength\tabcolsep{5pt}
% \begin{tabular}{|c|c|c|}
%     \hline
%   \includegraphics[width=0.325\textwidth]{car/PASCAL_car_val_init_0_Car_each_27_lim_250_lam_0_150_a_24_e_3_y_1_f_1_scale_2_00_sbin_6_level_15_skp_n_server_101_img_39.jpg} &   
%   \includegraphics[width=0.325\textwidth]{car/PASCAL_car_val_init_0_Car_each_27_lim_250_lam_0_150_a_24_e_3_y_1_f_1_scale_2_00_sbin_6_level_15_skp_n_server_101_img_78.jpg} & 
%   \includegraphics[width=0.325\textwidth]{car/PASCAL_car_val_init_0_Car_each_27_lim_250_lam_0_150_a_24_e_3_y_1_f_1_scale_2_00_sbin_6_level_15_skp_n_server_101_img_85.jpg} \\[-15pt]
% (a) & (b) & (c) \\[0pt]
% \hline
%   \includegraphics[width=0.325\textwidth]{car/PASCAL_car_val_init_0_Car_each_27_lim_250_lam_0_150_a_24_e_3_y_1_f_1_scale_2_00_sbin_6_level_15_skp_n_server_101_img_338.jpg} &   
%   \includegraphics[width=0.325\textwidth]{car/PASCAL_car_val_init_0_Car_each_27_lim_250_lam_0_150_a_24_e_3_y_1_f_1_scale_2_00_sbin_6_level_15_skp_n_server_101_img_360.jpg} & 
%   \includegraphics[width=0.325\textwidth]{car/PASCAL_car_val_init_0_Car_each_27_lim_250_lam_0_150_a_24_e_3_y_1_f_1_scale_2_00_sbin_6_level_15_skp_n_server_101_img_414.jpg} \\[-15pt]
% (d) & (e) & (f) \\[0pt]
% \hline
%   \includegraphics[width=0.325\textwidth]{car/PASCAL_car_val_init_0_Car_each_27_lim_250_lam_0_150_a_24_e_3_y_1_f_1_scale_2_00_sbin_6_level_15_skp_n_server_101_img_418.jpg} &   
%   \includegraphics[width=0.325\textwidth]{car/PASCAL_car_val_init_0_Car_each_27_lim_250_lam_0_150_a_24_e_3_y_1_f_1_scale_2_00_sbin_6_level_15_skp_n_server_101_img_1049.jpg} & 
%   \includegraphics[width=0.325\textwidth]{car/PASCAL_car_val_init_0_Car_each_27_lim_250_lam_0_150_a_24_e_3_y_1_f_1_scale_2_00_sbin_6_level_15_skp_n_server_101_img_1242.jpg} \\[-15pt]
% (g) & (h) & (i) \\[0pt]
% \hline
%   \includegraphics[width=0.325\textwidth]{car/PASCAL_car_val_init_0_Car_each_27_lim_250_lam_0_150_a_24_e_3_y_1_f_1_scale_2_00_sbin_6_level_15_skp_n_server_101_img_1244.jpg} &   
%   \includegraphics[width=0.325\textwidth]{car/PASCAL_car_val_init_0_Car_each_27_lim_250_lam_0_150_a_24_e_3_y_1_f_1_scale_2_00_sbin_6_level_15_skp_n_server_101_img_1261.jpg} & 
%   \includegraphics[width=0.325\textwidth]{car/PASCAL_car_val_init_0_Car_each_27_lim_250_lam_0_150_a_24_e_3_y_1_f_1_scale_2_00_sbin_6_level_15_skp_n_server_101_img_1452.jpg} \\[-15pt]
% (j) & (k) & (l) \\[0pt]
% \hline
%   \includegraphics[width=0.325\textwidth]{car/PASCAL_car_val_init_0_Car_each_27_lim_250_lam_0_150_a_24_e_3_y_1_f_1_scale_2_00_sbin_6_level_15_skp_n_server_101_img_1467.jpg} &   
%   \includegraphics[width=0.325\textwidth]{car/PASCAL_car_val_init_0_Car_each_27_lim_250_lam_0_150_a_24_e_3_y_1_f_1_scale_2_00_sbin_6_level_15_skp_n_server_101_img_1553.jpg} & 
%   \includegraphics[width=0.325\textwidth]{car/PASCAL_car_val_init_0_Car_each_27_lim_250_lam_0_150_a_24_e_3_y_1_f_1_scale_2_00_sbin_6_level_15_skp_n_server_101_img_1597.jpg} \\[-15pt]
% (m) & (n) & (o) \\[3pt]
% \hline
% \end{tabular}
%   \caption{Selected detections from PASCAL 07 Car categories. From the left, (1) original image, (2) overlaid true positive CAD models, (3) overlaid true positive CAD models with bounding boxes, (4) overlaid false positive CAD models with bounding boxes. Bounding box is colored from red (high confidence) to blue (low confidence) }
%   \label{fig:car}
% \end{figure*}
% \begin{figure*}[h]
% \setlength\tabcolsep{5pt}
% \begin{tabular}{|c|c|c|}
%     \hline
%   \includegraphics[width=0.325\textwidth]{bicycle/PASCAL_bicycle_val_init_0_Bicycle_each_4_lim_250_lam_0_150_a_48_e_4_y_5_f_1_scale_2_00_sbin_6_level_15_skp_n_server_102_img_459.jpg} &   
%   \includegraphics[width=0.325\textwidth]{bicycle/PASCAL_bicycle_val_init_0_Bicycle_each_4_lim_250_lam_0_150_a_48_e_4_y_5_f_1_scale_2_00_sbin_6_level_15_skp_n_server_102_img_1300.jpg} &   
%   \includegraphics[width=0.325\textwidth]{bicycle/PASCAL_bicycle_val_init_0_Bicycle_each_4_lim_250_lam_0_150_a_48_e_4_y_5_f_1_scale_2_00_sbin_6_level_15_skp_n_server_102_img_539.jpg} \\[-15pt]
% (a) & (b) & (c) \\[0pt]
% \hline
%   \includegraphics[width=0.325\textwidth]{bicycle/PASCAL_bicycle_val_init_0_Bicycle_each_4_lim_250_lam_0_150_a_48_e_4_y_5_f_1_scale_2_00_sbin_6_level_15_skp_n_server_102_img_35.jpg} &   
%   \includegraphics[width=0.325\textwidth]{bicycle/PASCAL_bicycle_val_init_0_Bicycle_each_4_lim_250_lam_0_150_a_48_e_4_y_5_f_1_scale_2_00_sbin_6_level_15_skp_n_server_102_img_83.jpg} &   
%   \includegraphics[width=0.325\textwidth]{bicycle/PASCAL_bicycle_val_init_0_Bicycle_each_4_lim_250_lam_0_150_a_48_e_4_y_5_f_1_scale_2_00_sbin_6_level_15_skp_n_server_102_img_131.jpg} \\[-15pt]
% (d) & (e) & (f) \\[0pt]
% \hline
%   \includegraphics[width=0.325\textwidth]{bicycle/PASCAL_bicycle_val_init_0_Bicycle_each_4_lim_250_lam_0_150_a_48_e_4_y_5_f_1_scale_2_00_sbin_6_level_15_skp_n_server_102_img_175.jpg} &   
%   \includegraphics[width=0.325\textwidth]{bicycle/PASCAL_bicycle_val_init_0_Bicycle_each_4_lim_250_lam_0_150_a_48_e_4_y_5_f_1_scale_2_00_sbin_6_level_15_skp_n_server_102_img_210.jpg} &   
%   \includegraphics[width=0.325\textwidth]{bicycle/PASCAL_bicycle_val_init_0_Bicycle_each_4_lim_250_lam_0_150_a_48_e_4_y_5_f_1_scale_2_00_sbin_6_level_15_skp_n_server_102_img_233.jpg} \\[-15pt]
% (g) & (h) & (i) \\[0pt]
% \hline
%   \includegraphics[width=0.325\textwidth]{bicycle/PASCAL_bicycle_val_init_0_Bicycle_each_4_lim_250_lam_0_150_a_48_e_4_y_5_f_1_scale_2_00_sbin_6_level_15_skp_n_server_102_img_322.jpg} &   
%   \includegraphics[width=0.325\textwidth]{bicycle/PASCAL_bicycle_val_init_0_Bicycle_each_4_lim_250_lam_0_150_a_48_e_4_y_5_f_1_scale_2_00_sbin_6_level_15_skp_n_server_102_img_348.jpg} &   
%   \includegraphics[width=0.325\textwidth]{bicycle/PASCAL_bicycle_val_init_0_Bicycle_each_4_lim_250_lam_0_150_a_48_e_4_y_5_f_1_scale_2_00_sbin_6_level_15_skp_n_server_102_img_375.jpg} \\[-15pt]
% (j) & (k) & (l) \\[0pt]
% \hline
%   \includegraphics[width=0.325\textwidth]{bicycle/PASCAL_bicycle_val_init_0_Bicycle_each_4_lim_250_lam_0_150_a_48_e_4_y_5_f_1_scale_2_00_sbin_6_level_15_skp_n_server_102_img_400.jpg} &   
%   \includegraphics[width=0.325\textwidth]{bicycle/PASCAL_bicycle_val_init_0_Bicycle_each_4_lim_250_lam_0_150_a_48_e_4_y_5_f_1_scale_2_00_sbin_6_level_15_skp_n_server_102_img_434.jpg} &   
%   \includegraphics[width=0.325\textwidth]{bicycle/PASCAL_bicycle_val_init_0_Bicycle_each_4_lim_250_lam_0_150_a_48_e_4_y_5_f_1_scale_2_00_sbin_6_level_15_skp_n_server_102_img_459.jpg} \\[-15pt]
% (m) & (n) & (o) \\[3pt]
% \hline
% \end{tabular}
%   \caption{Selected detections from PASCAL 12 Bike categories. From the left, (1) original image, (2) overlaid true positive CAD models, (3) overlaid true positive CAD models with bounding boxes, (4) overlaid false positive CAD models with bounding boxes. Bounding box is colored from red (high confidence) to blue (low confidence) }
%   \label{fig:bicycle}
% \end{figure*}

% \section{Object Detection with various Training Data}
% \section{Image Query}

\section{Conclusion}

{\small
\bibliographystyle{ieee}
\bibliography{egbib}
}

\end{document}

### 2014-11-13 egpaper_final.tex
excised intro into separate file

@@
 %%%%%%%%% TITLE
-\title{Enrich Object Detection : 2D-3D registration and continuous viewpoint estimation}
+\title{Enriching Object Detection with 2D-3D Registration and Continuous Viewpoint}
+%\title{Enrich Object Detection : 2D-3D registration and continuous viewpoint estimation}
 
@@
 \section{Introduction}
-
-\begin{figure}[t]
-  \centering
-  % \includegraphics[width=0.9\linewidth]{schematics} 
-  \includegraphics[width=0.99\linewidth]{front} % \\[-5pt]
-  % (a)\\[0pt]
-  % \setlength\tabcolsep{0pt}
-  % \begin{tabular}{cc}
-  %     \includegraphics[width=0.45\linewidth]{car/orig2} & 
-  %     \includegraphics[width=0.45\linewidth]{car/overlay2}
-  %  %   \begin{tabular}{cc}
-  %  %       \includegraphics[width=0.16\linewidth]{cad_car/2001-2004 Ford Ranger Edge} & 
-  %  %       \includegraphics[width=0.16\linewidth]{cad_car/2002 Dodge Ram FedEx} \\ 
-  %  %       \includegraphics[width=0.16\linewidth]{cad_car/2007-Nissan-Versa-_-Tiida-SL} & 
-  %  %       \includegraphics[width=0.16\linewidth]{cad_car/2008-Jeep-Cherokee} \\ 
-  %  %       \includegraphics[width=0.16\linewidth]{cad_car/2009 Toyota Cargo} & 
-  %  %       \includegraphics[width=0.16\linewidth]{cad_car/2010-Chevrolet-Aveo5-LT} \\ 
-  %  %       \includegraphics[width=0.16\linewidth]{cad_car/2012-Citroen-DS4}  
-  %  %   \end{tabular}
-  % \end{tabular}\\
-  % (b)
-  \caption{Using a bank of CAD models, we generate NZ-WHO templates which can be used to either detect objects directly or initialize pose of an object in the bounding box from other detectors.
-Once initialization is given, we use NZ-WHO to propose and validate plausible pose on-the-fly and further tune the translation, 3D viewpoint and focal length continuously.}
-  % \vspace{-1em}
-  \label{fig:front}
-\end{figure}
-
-% Object detection task has long been about predicting rectangular bounding boxes around the object.
-In this workthere has been significant many powerful object detectors such as Convolutional Neural Network or Part-Based Models \cite{Girshick14, Felzenszwalb10, Pepik12}
-
-High performance object detectors usually generalizes very well.
-It can handle various intraclass variability, viewpoint change and occlusion.
-However due to this high generalization, sometimes it is very difficult to get accurate pose, category or 2D-3D matching.
-Our method, specialized in giving such accurate information, can be applied on any generic object detectors to give high quality metadata.
-
-Matching 3D CAD model to an image has been a classical problem that dates back to eighties \cite{Lowe87}.
-Lowe \etal , the vision community instead focused on the object detection tasks that estimates a rectangular bounding box around an object\cite{Felzenszwalb10, Girshick14}.
-To infer what is more than a rectangle, several attempts have been made to estimate the pose of an object \cite{Xiang12, Pepik12, Fidler12, Hejrati14} or even finding corresponding CAD model as well \cite{Aubry14, Lim14}.
-
-However, there has been increasing demand for accurate pose and 2D-3D matching.
-Notably, in graphics community, there has been growing demand for accurate 2D-3D matching \cite{Kholgade14, Chen13, Kostas14} for image manipulation, editing and data augmentation respectively.
-
-Recently, with the powerful computing capabilities and a large collection of CAD models, the 2D-3D matching (registration) problem gets more and more approachable but due to inherent difficulty and limited performance of existing methods, many applications still require supervision to achieve 2D-3D matching.
-
-% In medical community, registering 3D scan data to 2D image enabled various minimally invasive surgeries \cite{Markelj12}.
-
-For category-level matching, \cite{Xiang12, Hejrati14, Pepik12} used 3D parts or aspect to represent underlying category-level 3D geometry of the object.
-With the advent of large public CAD datasets \cite{Trimble, Yobi}, the instance-level object detection and 2D-3D registration became possible.
-\cite{Aubry14, Lim14} used large collection of CAD models to faithfully align 3D CAD model to an image by rendering CAD models and creating 2D templates for various viewpoints.
-
-Data-driven instance-level 2D-3D matching algorithms such as \cite{Aubry14, Lim14} require a large number of rendering and 2D templates for each of the CAD model with specific viewpoint.
-Since there are so many templates that it becomes almost impossible to get all the true positive image from training data.
-Instead \cite{Aubry14, Lim14} used whitening as a preprocessing stage \cite{Hariharan12} to make templates more discriminative.
-Then calibration is done on a small training dataset.
-
-Although whitening to create template is faster than some of instance-level matching algorithms such as training Exemplar-SVM \cite{Malisiewicz11} or complicated models such as LEVAN \cite{Divvala14}, whitening and calibration large number of templates takes very long time.
-Also, once the fixed discrete viewpoint templates have been made and calibrated, it is difficult to fine-tune the prediction made using the large collection of templates.
-
-%% Our contribution
-With this growing usage of WHO template and Computer Graphics rendering, we decided to analyze WHO feature
-[Find More Usage of WHO and CG rendering \cite{Pepik12}]
-
-In our paper, we present Non-Zero Whiten Histograms of Orientations (NZ-WHO) to dramatically speed up the template generation and get rid of time consuming calibration and yet achieves performance on par with calibrated templates.
-First, we will present NZ-WHO is more discriminative than WHO and introduce Conjugate Gradient method to speed up the whitening and create a high resolution template in just 80 milliseconds.
-Also, using this fast NZ-WHO template generation, we present \textbf{on-the-fly} template generation to fine tune an initial pose estimation to continuously refine translation, viewpoints (yaw, roll, pitch) and focal length.
-
-Our pipeline is simple, fast only requires CAD models and no validation images for calibration.
-This can be used for post processing stage of generic object detection.
-Our pipeline requires only several minutes to make templates for rough viewpoints and
-
-We propose a simple method to register the most similar CAD model to an image and fine-tune viewpoint continuously without discriminative part search, training nor calibration.
-Our method is simple, fast and light-weight in terms of memory so that it can be easily applied on top of generic object detectors as a final stage of detection or can be used as a standalone detector.
-
-% Although our method is geared toward instance-level 2D-3D matching, we evaluated the performance of the templates on PASCAL 2007 and PASCAL 2012 and PASCAL 3D dataset to measure the performance.
-
-Our tuning stage not only refine position, scale and viewpoint, but also focal length as well to literally "fine-tune" the initial proposal.
-Though our 2D-3D matching method can be used as a rudimentary object detector, our simple tuning stage can be applied to any generic object detector to achieve state-of-the-art viewpoint estimation method.
-
-Finally, we show several applications using our method.
-Since we have metadata such as CAD model and geometry, we reconstruct the object using 2D-3D matching.
-Also, since we do not need training image, we show that our 2D-3D matching performs better than standard detectors in categories where training data lacks.
-We then use our method for image query to pull out closest CAD model in a bank of CAD models.
-
-Finally, unlike several CAD model alignment methods that uses  WHO \cite{Aubry13, Aubry14, Lim14}, we propose a novel pipeline that does not require calibration which is infeasible in continuous viewpoint estimation.
-We propose a simple add-on stage that can enrich object detections with high-quality 2D-3D alignment.
-The pipeline is simple and light weight so this can be easily adapted to be used for any generic object detectors.
-Also to facilitate the future work, all our alignment result on PASCAL12 and code are publicly available online.
-
-% Recently, matching a 3D CAD model to an image, 2D-3D matching (registration), is gaining great momentum in various fields of study.
-2D-3D matching using Structure from Motion \cite{Sattler11} uses existing 3D model to match the model to a query image.
-Also image manipulation using 3D CAD models has proven its potential.
-Kholgade \etal \cite{Kholgade14} and Chen \etal \cite{Chen13} require human input to match 3D models to an image to created realistic morphing or manipulation of the registered object.
-However, all these application requies human input.
-In this paper, we propose a novel on-the-fly template generation algorithm that can generate template quickly and validate 2D-3D pose and focal length continuously.
-
-% Our code has been made publicly online \cite{Choy14} so that our algorithm can be used as a pipeline for 2D-3D registration after general purpose object detectors.
-
-\subsection{Approach Overview}
-
-Our method is in line with \cite{Aubry14, Lim14} in the sense that we use only renderings not real images.
-However, rather than using fixed sized mid-level patches, we use whole object and make root templates.
-By using root templates, there is no need to learn a discriminative patch dictionary or to calibrate the patches and an additional inference stage is not required.
-However, whitening the whole template is prohibitive for several reasons.
-All templates have different aspect ratios making it difficult to generate the covariance matrix $\Sigma$.
-Since the root templates are larger than mid-level patches, a very large auto-covariance $\Gamma$ is required.
-Lastly, time complexity of decorrelating a template with $n$ cells increases as $O(n^3)$, resulting in slow template generation and large residuals due to numerical errors accumulated while decomposing the covariance matrix $\Sigma$.
-
-To overcome these difficulties, we propose the Non-Zero Whitened Histograms of Orientations with iterative Conjugate Gradient to generate templates in real time and enrich rectangular boxes with high quality 2D-3D matching.
-The 2D-3D matching provides a CAD model, sub-category, rendering, depth, viewpoint and focal length.
-
-Our method can work as a standalone 2D-3D matching algorithm, or even as a standalone ensemble of exemplar-based object detectors (Figure \ref{fig:front}) but the real power comes from combining generic object detectors and complement rectangular bounding boxes.
-Our method is simple in design; is several orders of magnitude faster than traditional method; requires only CAD models; doesn't need images nor calibration, yet is powerful in giving high-quality metadata.
-These properties make our method ideal for complementing object detections.
-
-To complement detection bounding boxes, we first search possible 2D-3D matching by running cached discrete viewpoint templates.
-Then, for the most probable match, we refine the initial matching using Metropolis Hastings.
-Since it requires iterations of proposal and validation, we present real time analysis of NZ-WHO template generation to show that this can be done on-the-fly.
-The fine tuning stage process jointly optimizes translation, yaw, roll, pitch, scale, and focal length continuously and also searches for different CAD models.
+\label{sec:intro}
+\input{intro}
 

### 2014-11-13 intro.tex
excised intro into separate file

\begin{figure}[t]
  \centering
  % \includegraphics[width=0.9\linewidth]{schematics} 
  \includegraphics[width=0.99\linewidth]{front} % \\[-5pt]
  % (a)\\[0pt]
  % \setlength\tabcolsep{0pt}
  % \begin{tabular}{cc}
  %     \includegraphics[width=0.45\linewidth]{car/orig2} & 
  %     \includegraphics[width=0.45\linewidth]{car/overlay2}
  %  %   \begin{tabular}{cc}
  %  %       \includegraphics[width=0.16\linewidth]{cad_car/2001-2004 Ford Ranger Edge} & 
  %  %       \includegraphics[width=0.16\linewidth]{cad_car/2002 Dodge Ram FedEx} \\ 
  %  %       \includegraphics[width=0.16\linewidth]{cad_car/2007-Nissan-Versa-_-Tiida-SL} & 
  %  %       \includegraphics[width=0.16\linewidth]{cad_car/2008-Jeep-Cherokee} \\ 
  %  %       \includegraphics[width=0.16\linewidth]{cad_car/2009 Toyota Cargo} & 
  %  %       \includegraphics[width=0.16\linewidth]{cad_car/2010-Chevrolet-Aveo5-LT} \\ 
  %  %       \includegraphics[width=0.16\linewidth]{cad_car/2012-Citroen-DS4}  
  %  %   \end{tabular}
  % \end{tabular}\\
  % (b)
  \caption{Using a bank of CAD models, we generate NZ-WHO templates which can be used to either detect objects directly or initialize pose of an object in the bounding box from other detectors. Once initialization is given, we use NZ-WHO to propose and validate plausible pose on-the-fly and further tune the translation, 3D viewpoint and focal length continuously.}
  % \vspace{-1em}
  \label{fig:front}
\end{figure}

% Object detection task has long been about predicting rectangular bounding boxes around the object. In this workthere has been significant many powerful object detectors such as Convolutional Neural Network or Part-Based Models \cite{Girshick14, Felzenszwalb10, Pepik12}

High performance object detectors usually generalizes very well. It can handle various intraclass variability, viewpoint change and occlusion. However due to this high generalization, sometimes it is very difficult to get accurate pose, category or 2D-3D matching. Our method, specialized in giving such accurate information, can be applied on any generic object detectors to give high quality metadata.

Matching 3D CAD model to an image has been a classical problem that dates back to eighties \cite{Lowe87}. Lowe \etal , the vision community instead focused on the object detection tasks that estimates a rectangular bounding box around an object\cite{Felzenszwalb10, Girshick14}. To infer what is more than a rectangle, several attempts have been made to estimate the pose of an object \cite{Xiang12, Pepik12, Fidler12, Hejrati14} or even finding corresponding CAD model as well \cite{Aubry14, Lim14}.

However, there has been increasing demand for accurate pose and 2D-3D matching. Notably, in graphics community, there has been growing demand for accurate 2D-3D matching \cite{Kholgade14, Chen13, Kostas14} for image manipulation, editing and data augmentation respectively.

Recently, with the powerful computing capabilities and a large collection of CAD models, the 2D-3D matching (registration) problem gets more and more approachable but due to inherent difficulty and limited performance of existing methods, many applications still require supervision to achieve 2D-3D matching.

% In medical community, registering 3D scan data to 2D image enabled various minimally invasive surgeries \cite{Markelj12}.

For category-level matching, \cite{Xiang12, Hejrati14, Pepik12} used 3D parts or aspect to represent underlying category-level 3D geometry of the object. With the advent of large public CAD datasets \cite{Trimble, Yobi}, the instance-level object detection and 2D-3D registration became possible. \cite{Aubry14, Lim14} used large collection of CAD models to faithfully align 3D CAD model to an image by rendering CAD models and creating 2D templates for various viewpoints.

Data-driven instance-level 2D-3D matching algorithms such as \cite{Aubry14, Lim14} require a large number of rendering and 2D templates for each of the CAD model with specific viewpoint. Since there are so many templates that it becomes almost impossible to get all the true positive image from training data. Instead \cite{Aubry14, Lim14} used whitening as a preprocessing stage \cite{Hariharan12} to make templates more discriminative. Then calibration is done on a small training dataset.

Although whitening to create template is faster than some of instance-level matching algorithms such as training Exemplar-SVM \cite{Malisiewicz11} or complicated models such as LEVAN \cite{Divvala14}, whitening and calibration large number of templates takes very long time. Also, once the fixed discrete viewpoint templates have been made and calibrated, it is difficult to fine-tune the prediction made using the large collection of templates.

%% Our contribution
With this growing usage of WHO template and Computer Graphics rendering, we decided to analyze WHO feature
[Find More Usage of WHO and CG rendering \cite{Pepik12}]

In our paper, we present Non-Zero Whiten Histograms of Orientations (NZ-WHO) to dramatically speed up the template generation and get rid of time consuming calibration and yet achieves performance on par with calibrated templates. First, we will present NZ-WHO is more discriminative than WHO and introduce Conjugate Gradient method to speed up the whitening and create a high resolution template in just 80 milliseconds. Also, using this fast NZ-WHO template generation, we present \textbf{on-the-fly} template generation to fine tune an initial pose estimation to continuously refine translation, viewpoints (yaw, roll, pitch) and focal length.

Our pipeline is simple, fast only requires CAD models and no validation images for calibration. This can be used for post processing stage of generic object detection. Our pipeline requires only several minutes to make templates for rough viewpoints and

We propose a simple method to register the most similar CAD model to an image and fine-tune viewpoint continuously without discriminative part search, training nor calibration. Our method is simple, fast and light-weight in terms of memory so that it can be easily applied on top of generic object detectors as a final stage of detection or can be used as a standalone detector.

% Although our method is geared toward instance-level 2D-3D matching, we evaluated the performance of the templates on PASCAL 2007 and PASCAL 2012 and PASCAL 3D dataset to measure the performance.

Our tuning stage not only refine position, scale and viewpoint, but also focal length as well to literally "fine-tune" the initial proposal. Though our 2D-3D matching method can be used as a rudimentary object detector, our simple tuning stage can be applied to any generic object detector to achieve state-of-the-art viewpoint estimation method.

Finally, we show several applications using our method. Since we have metadata such as CAD model and geometry, we reconstruct the object using 2D-3D matching. Also, since we do not need training image, we show that our 2D-3D matching performs better than standard detectors in categories where training data lacks. We then use our method for image query to pull out closest CAD model in a bank of CAD models.

Finally, unlike several CAD model alignment methods that uses  WHO \cite{Aubry13, Aubry14, Lim14}, we propose a novel pipeline that does not require calibration which is infeasible in continuous viewpoint estimation. We propose a simple add-on stage that can enrich object detections with high-quality 2D-3D alignment. The pipeline is simple and light weight so this can be easily adapted to be used for any generic object detectors. Also to facilitate the future work, all our alignment result on PASCAL12 and code are publicly available online.

% Recently, matching a 3D CAD model to an image, 2D-3D matching (registration), is gaining great momentum in various fields of study. 2D-3D matching using Structure from Motion \cite{Sattler11} uses existing 3D model to match the model to a query image. Also image manipulation using 3D CAD models has proven its potential. Kholgade \etal \cite{Kholgade14} and Chen \etal \cite{Chen13} require human input to match 3D models to an image to created realistic morphing or manipulation of the registered object. However, all these application requies human input. In this paper, we propose a novel on-the-fly template generation algorithm that can generate template quickly and validate 2D-3D pose and focal length continuously.

% Our code has been made publicly online \cite{Choy14} so that our algorithm can be used as a pipeline for 2D-3D registration after general purpose object detectors.

\subsection{Approach Overview}

Our method is in line with \cite{Aubry14, Lim14} in the sense that we use only renderings not real images. However, rather than using fixed sized mid-level patches, we use whole object and make root templates. By using root templates, there is no need to learn a discriminative patch dictionary or to calibrate the patches and an additional inference stage is not required. However, whitening the whole template is prohibitive for several reasons. All templates have different aspect ratios making it difficult to generate the covariance matrix $\Sigma$. Since the root templates are larger than mid-level patches, a very large auto-covariance $\Gamma$ is required. Lastly, time complexity of decorrelating a template with $n$ cells increases as $O(n^3)$, resulting in slow template generation and large residuals due to numerical errors accumulated while decomposing the covariance matrix $\Sigma$.

To overcome these difficulties, we propose the Non-Zero Whitened Histograms of Orientations with iterative Conjugate Gradient to generate templates in real time and enrich rectangular boxes with high quality 2D-3D matching. The 2D-3D matching provides a CAD model, sub-category, rendering, depth, viewpoint and focal length.

Our method can work as a standalone 2D-3D matching algorithm, or even as a standalone ensemble of exemplar-based object detectors (Figure \ref{fig:front}) but the real power comes from combining generic object detectors and complement rectangular bounding boxes. Our method is simple in design; is several orders of magnitude faster than traditional method; requires only CAD models; doesn't need images nor calibration, yet is powerful in giving high-quality metadata. These properties make our method ideal for complementing object detections.

To complement detection bounding boxes, we first search possible 2D-3D matching by running cached discrete viewpoint templates. Then, for the most probable match, we refine the initial matching using Metropolis Hastings. Since it requires iterations of proposal and validation, we present real time analysis of NZ-WHO template generation to show that this can be done on-the-fly. The fine tuning stage process jointly optimizes translation, yaw, roll, pitch, scale, and focal length continuously and also searches for different CAD models.

### 2014-11-13 intro.tex
started intro pass

@@
 
-High performance object detectors usually generalizes very well.
-It can handle various intraclass variability, viewpoint change and occlusion.
-However due to this high generalization, sometimes it is very difficult to get accurate pose, category or 2D-3D matching.
-Our method, specialized in giving such accurate information, can be applied on any generic object detectors to give high quality metadata.
+Current approaches to object class detection have reached a remarkable
+level of performance in 2D bounding box
+localization~\cite{pascal12,Felzenszwalb10,Girshick14}, due to their
+ability to generalize across differences in object appearance,
+lighting, and viewpoint. While this generalization
+ability of these methods is benefitial for robustness, it also limits
+the level of detail that these detectors can deliver as an output.
 
-Matching 3D CAD model to an image has been a classical problem that dates back to eighties \cite{Lowe87}.
-Lowe \etal , the vision community instead focused on the object detection tasks that estimates a rectangular bounding box around an object\cite{Felzenszwalb10, Girshick14}.
-To infer what is more than a rectangle, several attempts have been made to estimate the pose of an object \cite{Xiang12, Pepik12, Fidler12, Hejrati14} or even finding corresponding CAD model as well \cite{Aubry14, Lim14}.
+As a consequence, there has been increased interest in multi-view object
+recognition, where viewpoint estimates are provided by
+detectors in addition to 2D bounding boxes. Several attempts have been
+made to estimate viewpoint along with object class detections,
+implemented as extensions to existing detectors, such as the implicit
+shape models~\cite{}, the constellation model~\cite{}, or the
+deformable part model~\cite{Xiang12,Pepik12,Fidler12,Hejrati14}.
 
-However, there has been increasing demand for accurate pose and 2D-3D matching.
-Notably, in graphics community, there has been growing demand for accurate 2D-3D matching \cite{Kholgade14, Chen13, Kostas14} for image manipulation, editing and data augmentation respectively.
-
-Recently, with the powerful computing capabilities and a large collection of CAD models, the 2D-3D matching (registration) problem gets more and more approachable but due to inherent difficulty and limited performance of existing methods, many applications still require supervision to achieve 2D-3D matching.
-
+Recently, an even higher level of geometric detail was reached in the
+form of aligning
+3D CAD models to real world test images~\cite{Aubry14,
+  Lim14}. Interestingly, the problem of matching 3D models to 2D
+images has been targeted since the early days of computer
+vision~\cite{Lowe87}, but had largely been neglected in recent years
+in favor of 2D detectors based on robust local features and
+statistical learning techniques. Now, this problem is being revisited
+mostly due to two reasons: the availability of sufficient artificial
+3D training data and the availability of robust image matching
+techniques.
+%
+% performance object detectors usually generalizes very well. It
+% can handle various intraclass variability, viewpoint change and
+% occlusion. However due to this high generalization, sometimes it is
+% very difficult to get accurate pose, category or 2D-3D matching. Our
+% method, specialized in giving such accurate information, can be
+% applied on any generic object detectors to give high quality metadata.
+% %
+% Matching 3D CAD model to an image has been a classical problem that
+% dates back to eighties . Lowe \etal , the vision
+% community instead focused on the object detection tasks that estimates
+% a rectangular bounding box around an object\cite{Felzenszwalb10,
+%   Girshick14}. 
+%
+In addition, there has been a growing emand for accurate 2D-3D
+matching \cite{Kholgade14, Chen13, Kostas14} for image manipulation,
+editing, and data augmentation in the computer graphics community.
+% Recently, with the powerful computing capabilities and a large
+% collection of CAD models, the 2D-3D matching (registration) problem
+% gets more and more approachable but due to inherent difficulty and
+% limited performance of existing methods, many applications still
+% require supervision to achieve 2D-3D matching.
 % In medical community, registering 3D scan data to 2D image enabled various minimally invasive surgeries \cite{Markelj12}.
 
-For category-level matching, \cite{Xiang12, Hejrati14, Pepik12} used 3D parts or aspect to represent underlying category-level 3D geometry of the object.
-With the advent of large public CAD datasets \cite{Trimble, Yobi}, the instance-level object detection and 2D-3D registration became possible.
-\cite{Aubry14, Lim14} used large collection of CAD models to faithfully align 3D CAD model to an image by rendering CAD models and creating 2D templates for various viewpoints.
+For category-level matching, \cite{Xiang12, Hejrati14, Pepik12} used
+3D parts or aspect to represent underlying category-level 3D geometry
+of the object. With the advent of large public CAD datasets
+\cite{Trimble, Yobi}, the instance-level object detection and 2D-3D
+registration became possible. \cite{Aubry14, Lim14} used large
+collection of CAD models to faithfully align 3D CAD model to an image
+by rendering CAD models and creating 2D templates for various
+viewpoints.
 

### 2014-11-13 intro.tex
started intro pass

@@
 form of aligning
-3D CAD models to real world test images~\cite{Aubry14,
-  Lim14}. Interestingly, the problem of matching 3D models to 2D
+3D CAD model instances to real world test images~\cite{Aubry14,
+  Lim14,Kholgade14, Chen13, Kostas14}. Interestingly, the problem of matching 3D models to 2D
 images has been targeted since the early days of computer
@@
 statistical learning techniques. Now, this problem is being revisited
-mostly due to two reasons: the availability of sufficient artificial
-3D training data and the availability of robust image matching
+mostly due to two reasons: the availability of 3D CAD models for many
+object classes and the availability of robust image matching
 techniques.
@@
 %
-In addition, there has been a growing emand for accurate 2D-3D
-matching \cite{Kholgade14, Chen13, Kostas14} for image manipulation,
-editing, and data augmentation in the computer graphics community.
+%In addition, there has been a growing emand for accurate 2D-3D
+%matching \cite{Kholgade14, Chen13, Kostas14} for image manipulation,
+%editing, and data augmentation in the computer graphics community.
+%
 % Recently, with the powerful computing capabilities and a large
@@
 % In medical community, registering 3D scan data to 2D image enabled various minimally invasive surgeries \cite{Markelj12}.
+%
+% For category-level matching, \cite{Xiang12, Hejrati14, Pepik12} used
+% 3D parts or aspect to represent underlying category-level 3D geometry
+% of the object. With the advent of large public CAD datasets
+% \cite{Trimble, Yobi}, the instance-level object detection and 2D-3D
+% registration became possible. \cite{Aubry14, Lim14} used large
+% collection of CAD models to faithfully align 3D CAD model to an image
+% by rendering CAD models and creating 2D templates for various
+% viewpoints.
 
-For category-level matching, \cite{Xiang12, Hejrati14, Pepik12} used
-3D parts or aspect to represent underlying category-level 3D geometry
-of the object. With the advent of large public CAD datasets
-\cite{Trimble, Yobi}, the instance-level object detection and 2D-3D
-registration became possible. \cite{Aubry14, Lim14} used large
-collection of CAD models to faithfully align 3D CAD model to an image
-by rendering CAD models and creating 2D templates for various
-viewpoints.
+Recent approaches to 2D-3D matching typically represent an object
+class as a collection of 3D exemplar models, which they render from a
+large number of viewpoints. The resulting artifial images are then
+used to train exemplar models that can be matched to a real-world
+image at test time.
 
-Data-driven instance-level 2D-3D matching algorithms such as \cite{Aubry14, Lim14} require a large number of rendering and 2D templates for each of the CAD model with specific viewpoint.
-Since there are so many templates that it becomes almost impossible to get all the true positive image from training data.
-Instead \cite{Aubry14, Lim14} used whitening as a preprocessing stage \cite{Hariharan12} to make templates more discriminative.
-Then calibration is done on a small training dataset.
+\cite{Aubry14, Lim14} require a large number of rendering and 2D
+templates for each of the CAD model with specific viewpoint. Since
+there are so many templates that it becomes almost impossible to get
+all the true positive image from training data. Instead \cite{Aubry14,
+  Lim14} used whitening as a preprocessing stage \cite{Hariharan12} to
+make templates more discriminative. Then calibration is done on a
+small training dataset.
 
-Although whitening to create template is faster than some of instance-level matching algorithms such as training Exemplar-SVM \cite{Malisiewicz11} or complicated models such as LEVAN \cite{Divvala14}, whitening and calibration large number of templates takes very long time.
-Also, once the fixed discrete viewpoint templates have been made and calibrated, it is difficult to fine-tune the prediction made using the large collection of templates.
+Although whitening to create template is faster than some of
+instance-level matching algorithms such as training Exemplar-SVM
+\cite{Malisiewicz11} or complicated models such as LEVAN
+\cite{Divvala14}, whitening and calibration large number of templates
+takes very long time. Also, once the fixed discrete viewpoint
+templates have been made and calibrated, it is difficult to fine-tune
+the prediction made using the large collection of templates.
 
 %% Our contribution
-With this growing usage of WHO template and Computer Graphics rendering, we decided to analyze WHO feature
+With this growing usage of WHO template and Computer Graphics
+rendering, we decided to analyze WHO feature
 [Find More Usage of WHO and CG rendering \cite{Pepik12}]
 
-In our paper, we present Non-Zero Whiten Histograms of Orientations (NZ-WHO) to dramatically speed up the template generation and get rid of time consuming calibration and yet achieves performance on par with calibrated templates.
-First, we will present NZ-WHO is more discriminative than WHO and introduce Conjugate Gradient method to speed up the whitening and create a high resolution template in just 80 milliseconds.
-Also, using this fast NZ-WHO template generation, we present \textbf{on-the-fly} template generation to fine tune an initial pose estimation to continuously refine translation, viewpoints (yaw, roll, pitch) and focal length.
+In our paper, we present Non-Zero Whiten Histograms of Orientations
+(NZ-WHO) to dramatically speed up the template generation and get rid
+of time consuming calibration and yet achieves performance on par with
+calibrated templates. First, we will present NZ-WHO is more
+discriminative than WHO and introduce Conjugate Gradient method to
+speed up the whitening and create a high resolution template in just
+80 milliseconds. Also, using this fast NZ-WHO template generation, we
+present \textbf{on-the-fly} template generation to fine tune an
+initial pose estimation to continuously refine translation, viewpoints
+(yaw, roll, pitch) and focal length.
 
-Our pipeline is simple, fast only requires CAD models and no validation images for calibration.
-This can be used for post processing stage of generic object detection.
-Our pipeline requires only several minutes to make templates for rough viewpoints and
+Our pipeline is simple, fast only requires CAD models and no
+validation images for calibration. This can be used for post
+processing stage of generic object detection. Our pipeline requires
+only several minutes to make templates for rough viewpoints and
 
-We propose a simple method to register the most similar CAD model to an image and fine-tune viewpoint continuously without discriminative part search, training nor calibration.
-Our method is simple, fast and light-weight in terms of memory so that it can be easily applied on top of generic object detectors as a final stage of detection or can be used as a standalone detector.
+We propose a simple method to register the most similar CAD model to
+an image and fine-tune viewpoint continuously without discriminative
+part search, training nor calibration. Our method is simple, fast and
+light-weight in terms of memory so that it can be easily applied on
+top of generic object detectors as a final stage of detection or can
+be used as a standalone detector.
 
@@
 
-Our tuning stage not only refine position, scale and viewpoint, but also focal length as well to literally "fine-tune" the initial proposal.
-Though our 2D-3D matching method can be used as a rudimentary object detector, our simple tuning stage can be applied to any generic object detector to achieve state-of-the-art viewpoint estimation method.
+Our tuning stage not only refine position, scale and viewpoint, but
+also focal length as well to literally "fine-tune" the initial
+proposal. Though our 2D-3D matching method can be used as a
+rudimentary object detector, our simple tuning stage can be applied to
+any generic object detector to achieve state-of-the-art viewpoint
+estimation method.
 
-Finally, we show several applications using our method.
-Since we have metadata such as CAD model and geometry, we reconstruct the object using 2D-3D matching.
-Also, since we do not need training image, we show that our 2D-3D matching performs better than standard detectors in categories where training data lacks.
-We then use our method for image query to pull out closest CAD model in a bank of CAD models.
+Finally, we show several applications using our method. Since we have
+metadata such as CAD model and geometry, we reconstruct the object
+using 2D-3D matching. Also, since we do not need training image, we
+show that our 2D-3D matching performs better than standard detectors
+in categories where training data lacks. We then use our method for
+image query to pull out closest CAD model in a bank of CAD models.
 
-Finally, unlike several CAD model alignment methods that uses  WHO \cite{Aubry13, Aubry14, Lim14}, we propose a novel pipeline that does not require calibration which is infeasible in continuous viewpoint estimation.
-We propose a simple add-on stage that can enrich object detections with high-quality 2D-3D alignment.
-The pipeline is simple and light weight so this can be easily adapted to be used for any generic object detectors.
-Also to facilitate the future work, all our alignment result on PASCAL12 and code are publicly available online.
+Finally, unlike several CAD model alignment methods that uses  WHO
+\cite{Aubry13, Aubry14, Lim14}, we propose a novel pipeline that does
+not require calibration which is infeasible in continuous viewpoint
+estimation. We propose a simple add-on stage that can enrich object
+detections with high-quality 2D-3D alignment. The pipeline is simple
+and light weight so this can be easily adapted to be used for any
+generic object detectors. Also to facilitate the future work, all our
+alignment result on PASCAL12 and code are publicly available online.
 
@@
 \subsection{Approach Overview}
+Our method is in line with \cite{Aubry14, Lim14} in the sense that we
+use only renderings not real images. However, rather than using fixed
+sized mid-level patches, we use whole object and make root
+templates. By using root templates, there is no need to learn a
+discriminative patch dictionary or to calibrate the patches and an
+additional inference stage is not required. However, whitening the
+whole template is prohibitive for several reasons. All templates have
+different aspect ratios making it difficult to generate the covariance
+matrix $\Sigma$. Since the root templates are larger than mid-level
+patches, a very large auto-covariance $\Gamma$ is required. Lastly,
+time complexity of decorrelating a template with $n$ cells increases
+as $O(n^3)$, resulting in slow template generation and large residuals
+due to numerical errors accumulated while decomposing the covariance
+matrix $\Sigma$.
 
-Our method is in line with \cite{Aubry14, Lim14} in the sense that we use only renderings not real images.
-However, rather than using fixed sized mid-level patches, we use whole object and make root templates.
-By using root templates, there is no need to learn a discriminative patch dictionary or to calibrate the patches and an additional inference stage is not required.
-However, whitening the whole template is prohibitive for several reasons.
-All templates have different aspect ratios making it difficult to generate the covariance matrix $\Sigma$.
-Since the root templates are larger than mid-level patches, a very large auto-covariance $\Gamma$ is required.
-Lastly, time complexity of decorrelating a template with $n$ cells increases as $O(n^3)$, resulting in slow template generation and large residuals due to numerical errors accumulated while decomposing the covariance matrix $\Sigma$.
+To overcome these difficulties, we propose the Non-Zero Whitened
+Histograms of Orientations with iterative Conjugate Gradient to
+generate templates in real time and enrich rectangular boxes with high
+quality 2D-3D matching. The 2D-3D matching provides a CAD model,
+sub-category, rendering, depth, viewpoint and focal length.
 
-To overcome these difficulties, we propose the Non-Zero Whitened Histograms of Orientations with iterative Conjugate Gradient to generate templates in real time and enrich rectangular boxes with high quality 2D-3D matching.
-The 2D-3D matching provides a CAD model, sub-category, rendering, depth, viewpoint and focal length.
+Our method can work as a standalone 2D-3D matching algorithm, or even
+as a standalone ensemble of exemplar-based object detectors (Figure
+\ref{fig:front}) but the real power comes from combining generic
+object detectors and complement rectangular bounding boxes. Our method
+is simple in design; is several orders of magnitude faster than
+traditional method; requires only CAD models; doesn't need images nor
+calibration, yet is powerful in giving high-quality metadata. These
+properties make our method ideal for complementing object detections.
 
-Our method can work as a standalone 2D-3D matching algorithm, or even as a standalone ensemble of exemplar-based object detectors (Figure \ref{fig:front}) but the real power comes from combining generic object detectors and complement rectangular bounding boxes.
-Our method is simple in design; is several orders of magnitude faster than traditional method; requires only CAD models; doesn't need images nor calibration, yet is powerful in giving high-quality metadata.
-These properties make our method ideal for complementing object detections.
-
-To complement detection bounding boxes, we first search possible 2D-3D matching by running cached discrete viewpoint templates.
-Then, for the most probable match, we refine the initial matching using Metropolis Hastings.
-Since it requires iterations of proposal and validation, we present real time analysis of NZ-WHO template generation to show that this can be done on-the-fly.
-The fine tuning stage process jointly optimizes translation, yaw, roll, pitch, scale, and focal length continuously and also searches for different CAD models.
+To complement detection bounding boxes, we first search possible 2D-3D
+matching by running cached discrete viewpoint templates. Then, for the
+most probable match, we refine the initial matching using Metropolis
+Hastings. Since it requires iterations of proposal and validation, we
+present real time analysis of NZ-WHO template generation to show that
+this can be done on-the-fly. The fine tuning stage process jointly
+optimizes translation, yaw, roll, pitch, scale, and focal length
+continuously and also searches for different CAD models.

### 2014-11-13 intro.tex

@@
 statistical learning techniques. Now, this problem is being revisited
-mostly due to two reasons: the availability of 3D CAD models for many
-object classes and the availability of robust image matching
-techniques.
+mostly due to two reasons: {\em (i)} the availability of 3D CAD models
+for many object classes and {\em (ii)} the availability of robust
+image matching techniques.
 %
@@
 
-Recent approaches to 2D-3D matching typically represent an object
-class as a collection of 3D exemplar models, which they render from a
+For (i), recent approaches to 2D-3D matching~\cite{Aubry14, Lim14}
+typically rely on a
+collection of 3D exemplar models, which they render from a
 large number of viewpoints. The resulting artifial images are then
@@
 image at test time.
+%
+For (ii), it has been realized that template-based exemplar detectors
+based on HOG~\cite{Dalal05} features can be trained analytically, by
+replacing the standard SVM with an LDA classifier
+(E-LDA)~\cite{Hariharan12}. As a result, it is feasible to train
+hundreds of thousands of mid-level patch detectors for
+recognition~\cite{Aubry14}.
+%
+Unfortunately, the performance of E-LDA relies crucially on an
+additional calibration step that equalizes the detection scores of
+independently trained exemplar models. Since this step involves costly
+mining of hard negative examples~\cite{Dalal05,Felzenszwalb10} on a
+validation set, it constitutes the major computational bottleneck of
+E-LDA, limiting its scalability.
 
-\cite{Aubry14, Lim14} require a large number of rendering and 2D
-templates for each of the CAD model with specific viewpoint. Since
-there are so many templates that it becomes almost impossible to get
-all the true positive image from training data. Instead \cite{Aubry14,
-  Lim14} used whitening as a preprocessing stage \cite{Hariharan12} to
-make templates more discriminative. Then calibration is done on a
-small training dataset.
+In this paper, we propose a novel method for 2D-3D alignment of
+exemplar CAD models to real-world images that circumvents the need for
+calibration, and greatly enhances the scalability of E-LDA. As a
+result, we can render novel views and train corresponding exemplar
+models {\em on the fly}, without the need for offline processing. As a
+by-product, we can formulate the alignment problem as a parameter
+search in a continuos pose space, consisting of azimuth, elevation,
+and ~\scream{}, resulting in truely continuous pose estimates, which
+we implement using MCMC sampling.
+%  require a large number of rendering and 2D
+% templates for each of the CAD model with specific viewpoint. Since
+% there are so many templates that it becomes almost impossible to get
+% all the true positive image from training data. Instead \cite{Aubry14,
+%   Lim14} used whitening as a preprocessing stage \cite{Hariharan12} to
+% make templates more discriminative. Then calibration is done on a
+% small training dataset.
+%
+% Although whitening to create template is faster than some of
+% instance-level matching algorithms such as training Exemplar-SVM
+% \cite{Malisiewicz11} or complicated models such as LEVAN
+% \cite{Divvala14}, whitening and calibration large number of templates
+% takes very long time. Also, once the fixed discrete viewpoint
+% templates have been made and calibrated, it is difficult to fine-tune
+% the prediction made using the large collection of templates.
 
-Although whitening to create template is faster than some of
-instance-level matching algorithms such as training Exemplar-SVM
-\cite{Malisiewicz11} or complicated models such as LEVAN
-\cite{Divvala14}, whitening and calibration large number of templates
-takes very long time. Also, once the fixed discrete viewpoint
-templates have been made and calibrated, it is difficult to fine-tune
-the prediction made using the large collection of templates.
+Our paper makes the following specific contributions.
+
+First, we present a novel method for training exemplar models from
+rendered 3D CAD data {\em on the fly}, enabled by a novel variant of
+E-LDA, and making efficient use of the specific characteristics of
+rendered images. To our knowledge, our method constitutes the first
+attempt to simultanously render and train exemplar detectors on the
+fly.
+% In our paper, we present Non-Zero Whiten Histograms of Orientations
+% (NZ-WHO) to dramatically speed up the template generation and get rid
+% of time consuming calibration and yet achieves performance on par with
+% calibrated templates. First, we will present NZ-WHO is more
+% discriminative than WHO and introduce Conjugate Gradient method to
+% speed up the whitening and create a high resolution template in just
+% 80 milliseconds. Also, using this fast NZ-WHO template generation, we
+% present \textbf{on-the-fly} template generation to fine tune an
+% initial pose estimation to continuously refine translation, viewpoints
+% (yaw, roll, pitch) and focal length.
+
+Second, we show to enrich the output of an existing object class
+detector, such as the DPM~\cite{Felzenszwalb10} or the
+R-CNN~\cite{Girshick14} with additional 3D information, applying our
+method to candidate detections provided by the respective detector. As
+a result, we can refine the original detections with additional
+estimates of 3D continuos pose and a 3D CAD model exemplar.
+
+And third, we give an in-depth experimental study that demonstrates
+the effectiveness of our approach on a standard benchmark for
+object detection and viewpoint estimation~\cite{Xiang14}.
+
+outperforming previous results on this dataset by considerable
+margins.
 
@@
 [Find More Usage of WHO and CG rendering \cite{Pepik12}]
-
-In our paper, we present Non-Zero Whiten Histograms of Orientations
-(NZ-WHO) to dramatically speed up the template generation and get rid
-of time consuming calibration and yet achieves performance on par with
-calibrated templates. First, we will present NZ-WHO is more
-discriminative than WHO and introduce Conjugate Gradient method to
-speed up the whitening and create a high resolution template in just
-80 milliseconds. Also, using this fast NZ-WHO template generation, we
-present \textbf{on-the-fly} template generation to fine tune an
-initial pose estimation to continuously refine translation, viewpoints
-(yaw, roll, pitch) and focal length.
 

### 2014-11-13 egpaper_final.tex
started intro pass
my change
Sam: Related works section done(ish)

--- 2014-11-13 egpaper_final.tex
@@
 \section{Related Works}
-\subsection{Whitened Histograms of Orientations(WHO)}
+\subsection{Whitened Histograms of Orientations (WHO)}
 % History of Whitening and how whitening works
-Whitening a signal has been a popular method in various signal processing communities as a preprocessing stage \cite{Martinsson05, Belouchrani00}.
-Whitening a signal makes its autocorrelation narrower which results in more delta-function like spike for true positives and zero elsewhere.
+Recently, Hariharan \emph{et al.} introduced Whitened Histograms of Orientations (WHO) \cite{Hariharan12}, which used statistics from natural images to whiten HOG templates, making them more discriminative.
+Whitening is a common signal processing operation for decorrelating a set of random variables \cite{Martinsson05, Belouchrani00}.
 More formally, suppose that we have a $k$-dimensional random variable $X \in \mathcal{R}^k$ with $Cov(X)=\Sigma$.
@@
 So, all elements in the random variable $\tilde{X} = \left[\tilde{X}_1, \tilde{X}_2, \dots, \tilde{X}_k\right]$, become more independent.
-Since they become less dependent, convolving the whitened template with random signal will produce Gaussian noise on background signal but will produce delta-function like response on the match.
-Recently, \cite{Hariharan12} used whitening on HOG feature and named the whitened HOG as Whitened Histograms of Orientations (WHO).
+In the context of HOG features, a whitened HOG template will produce Gaussian noise when convolved with a random natural image, but a delta-like response on an image matching the template.
+WHO templates are more discriminative than standard HOG templates because they only capture the gradients that differentiate the object from random images.
+
+\textcolor{red}{Should we mention how our method improves on this (ie by using CG)?}
 
@@
 
-\subsection{More than a Bounding Box}
+\subsection{Pose Detection}
 
-High performance object detectors generalize very well \cite{Felzenszwalb10, Girshick14}.
-They can handle intraclass variability, change in viewpoint and truncation.
-However due this generalization, they lose fine-grained information such as accurate pose and object sub-category.
+Modern object detectors generalize very well, handling intraclass variability, occlusion, truncation and viewpoint changes \cite{Felzenszwalb10, Girshick14}.
+However, this generalization comes at the cost of fine-grained information, including accurate 3D pose and object sub-category recognition.
+Such methods typically produce bounding box detection hypotheses, will little further information.
 
-To give more than just a rectangular bounding box, \cite{Pepik12, Xiang12, Fidler12, Xiang14, Hejrati14, Aubry14, Lim14} various methods exist to jointly detect and estimate the pose of an object.
-\cite{Xiang12, Hejrati14, Fidler12} used 3D representations that deform as viewpoint changes and \cite{Pepik12} uses geometric constraints to regularize 2D appearance models.
+Many methods have attempted to move object detection towards richer outputs, especially by jointly performing detection and pose estimation \cite{Pepik12, Xiang12, Fidler12, Xiang14, Hejrati14, Aubry14, Lim14}.
+To achieve this, \cite{Xiang12, Hejrati14, Fidler12} use 3D representations that deform as viewpoint changes and \cite{Pepik12} uses geometric constraints to regularize 2D appearance models.
 
-On fine-grained pose estimation, \cite{Zia13} uses a 3D deformable wireframe model with parts to accurately predict pose and align the model.
+The methods above perform discrete pose estimation, quantizing the viewing sphere into a number of poses and selecting the best one during inference.
+Fine-grained pose estimators, in contrast, can infer continuous (or arbitrarily fine-grained) poses.
+One such method from \cite{Zia13} aligns a 3D deformable part-based wireframe model with input images to accurately predict object poses.
 
-More recently, \cite{Aubry14, Lim14} showed a success in joint instance-level object detection and pose estimation.
-To estimate pose, they rely on synthetic renderings of CAD models and learn discriminative mid-level patches.
-\cite{Aubry14} finds discriminative mid-level patches and calibrates them on a small set of real images.
-Similarly, \cite{Lim14} finds and learns relative discriminativeness of the shared mid-level patches.
+More recently, \cite{Aubry14, Lim14} made progress in joint instance-level object detection and pose estimation.
+To estimate pose they use synthetic renderings of CAD models to learn discriminative mid-level patches.
+\cite{Aubry14} calibrates these patches on a small set of real images, while \cite{Lim14} present a method for learning the relative discriminativeness of the patches.
+
+\textcolor{red}{Again, should we highlight the differences between these methods and ours?}
 
@@
 We also used iterative Conjugate Gradient to make use of low rank property of the covariance \cite{Gharbi12}.
-After adding small regularization, the regularized covariance matrix has nice spectral property (Figure \ref{fig:spectral}.
+After adding small regularization, the regularized covariance matrix has nice spectral property.
+figure below.
 The singular values are clustered in small region and most of the energies are concentrated on the first (number) singular values.
@@
 [Figure spectral analysis]
-
-\begin{figure}[t]
-  \centering
-  \includegraphics[width=0.5\linewidth]{residual}
-  \caption{Residual of differentd method}
-  \label{fig:whotime}
-\end{figure}
+[Figure residuals of each method]
 
@@
     \hline
-     AP/MPPE& Ours & ALM\cite{Xiang12} & VOCDPM\cite{Pepik12} \\
+     AP/AVA& Ours & ALM\cite{Xiang12} & VOCDPM\cite{Pepik12} \\
     \hline\hline

### 2014-11-14 egpaper_final.tex
first pass over related works

--- 2014-11-13 egpaper_final.tex
@@
 \def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}
+
+% custom commands
+\newcommand{\scream}[1]{{\bf *** #1! ***}}
 

### 2014-11-14 egpaper_final.tex
added pascal12 cnn+our figures. modified plots : larger fonts, thicker lines

--- 2014-11-13 egpaper_final.tex
@@
 \end{figure}
+
 [Figure spectral analysis]
@@
 \section{Continuous Viewpoint and Focal Length Estimation for Fine Tuning}
+\label{sec:fine}
 
@@
 % there are several advantages that was not possible such as \textbf{on-the-fly} template generation and making large number of templates
+
+\begin{figure}[t]
+\centering
+    \includegraphics[width=0.7\linewidth]{tuning2} \\ [-5pt]
+    \caption{Different modes of Metropolis Hasting proposals, see Section \ref{sec:fine}}
+ \label{fig:tuningmode}
+\end{figure}
+
 \begin{figure}[t]
  \begin{center}
-    \includegraphics[width=0.9\linewidth]{tuning2} 
-    \includegraphics[width=0.9\linewidth]{tuning} 
+    \setlength\tabcolsep{0pt}
+    \begin{tabular}{ccc}
+    % \includegraphics[width=0.9\linewidth]{tuning} 
+   \includegraphics[width=0.33\linewidth]{tuning/1.png} &
+   \includegraphics[width=0.33\linewidth]{tuning/2.png} &
+   \includegraphics[width=0.33\linewidth]{tuning/3.png} \\[-5pt]
+   (a) & (b) & (c)\\
+   \includegraphics[width=0.33\linewidth]{tuning/4.png} &
+   \includegraphics[width=0.33\linewidth]{tuning/5.png} &
+   \includegraphics[width=0.33\linewidth]{tuning/6.png} \\[-5pt]
+   (d) & (e) & (f)\\
+   \end{tabular}
  \end{center}
@@
 Thus V-DPM and VOC-DPM provide discrete azimuth only whereas our method provides 3D viewpoint (yaw, pitch, roll), CAD instance (model index, rendering, depth) and focal length.
+
+\begin{figure*}[h]
+\setlength\tabcolsep{1pt}
+\centering
+\begin{tabular}{|c|c|c|c|c|}
+   \hline
+  \includegraphics[width=0.24\textwidth]{car_cnn/1a.png} &   
+  \includegraphics[width=0.24\textwidth]{car_cnn/1b.png} &   
+  \includegraphics[width=0.24\textwidth]{car_cnn/1c.png} &   
+  \includegraphics[width=0.24\textwidth]{car_cnn/1d.png}  \\  
+   \hline
+  \includegraphics[width=0.24\textwidth]{car_cnn/2a.png} &   
+  \includegraphics[width=0.24\textwidth]{car_cnn/2b.png} &   
+  \includegraphics[width=0.24\textwidth]{car_cnn/2c.png} &   
+  \includegraphics[width=0.24\textwidth]{car_cnn/2e.png}  \\  
+   \hline
+  \includegraphics[width=0.24\textwidth]{car_cnn/4a.png} &   
+  \includegraphics[width=0.24\textwidth]{car_cnn/4b.png} &   
+  \includegraphics[width=0.24\textwidth]{car_cnn/4c.png} &   
+  \includegraphics[width=0.24\textwidth]{car_cnn/4d.png}  \\  
+%    \hline
+%   \includegraphics[width=0.24\textwidth]{car_cnn/10a.png} &   
+%   \includegraphics[width=0.24\textwidth]{car_cnn/10b.png} &   
+%   \includegraphics[width=0.24\textwidth]{car_cnn/10c.png} &   
+%   \includegraphics[width=0.24\textwidth]{car_cnn/10d.png}  \\  
+%   \hline 
+%   \includegraphics[width=0.24\textwidth]{bicycle_cnn/3a.png} &   
+%   \includegraphics[width=0.24\textwidth]{bicycle_cnn/3b.png} &   
+%   \includegraphics[width=0.24\textwidth]{bicycle_cnn/3c.png} &   
+%   \includegraphics[width=0.24\textwidth]{bicycle_cnn/3d.png}  \\
+  \hline
+  \includegraphics[width=0.24\textwidth]{bicycle_cnn/7a.png} &   
+  \includegraphics[width=0.24\textwidth]{bicycle_cnn/7b.png} &   
+  &\\
+  \hline
+  \includegraphics[width=0.24\textwidth]{bicycle_cnn/4a.png} &   
+  \includegraphics[width=0.24\textwidth]{bicycle_cnn/4b.png} &   
+  \includegraphics[width=0.24\textwidth]{bicycle_cnn/4c.png} &   
+  \includegraphics[width=0.24\textwidth]{bicycle_cnn/4d.png}  \\
+  \hline
+  CNN Proposals & \multicolumn{3}{|c|}{Our matching results on proposal bounding boxes} \\
+  \hline
+\end{tabular}
+\caption{Example enriched bounding boxex.
+Given R-CNN\cite{Girshick14} detection bounding boxes, our method predicted 2D-3D matching reasonably.
+On the first column, R-CNN detection bounding boxes overlaid.
+From the second to the last columns, output of our method given a R-CNN box.
+Blue boxes are R-CNN output and purle boxes are the tightest bounding box enclosing predicted CAD model}
+  \label{fig:pascal12cnn}
+\end{figure*}
 

### 2014-11-14 egpaper_final.tex
update

--- 2014-11-14 egpaper_final.tex
@@
 \usepackage[font=small,skip=0pt]{caption}
-\DeclareMathOperator{\Tr}{Tr}
+%\DeclareMathOperator{\Tr}{Tr}
 % Include other packages here, before hyperref.
@@
 
-\subsection{Pose Detection}
+\subsection{Object Detection and Viewpoint Estimation}
 
@@
 
-We propose a variation of Whitened Histograms of Orientations (WHO) \cite{Hariharan12} that can generate a template in 70ms (compared to several seconds to generate a WHO template) that is more discriminative than WHO.
-We call this Non-Zero Whitened Histograms of Orientations (NZ-WHO).
+We propose Non-Zero Whitened Histograms of Orientations (NZ-WHO), an improvement over WHO, that are both more discriminative than WHO, and can be generated two orders of magnitude faster.
+This speedup means we can generate templates on the fly, allowing our approach to evaluate arbitrary viewpoint hypotheses.
 

### 2014-11-14 egpaper_final.tex

@@
 % History of Whitening and how whitening works
-Recently, Hariharan \emph{et al.} introduced Whitened Histograms of Orientations (WHO) \cite{Hariharan12}, which used statistics from natural images to whiten HOG templates, making them more discriminative.
+Recently, Hariharan \etal.
+introduced Whitened Histograms of Orientations (WHO) \cite{Hariharan12}, which used statistics from natural images to whiten HOG templates, making them more discriminative.
 Whitening is a common signal processing operation for decorrelating a set of random variables \cite{Martinsson05, Belouchrani00}.

### 2014-11-14 egpaper_final.tex
Modified table 1, filling out experiment section

@@
 
-We empirically found out that NZ-WHO performs reasonably well without time consuming calibration stage compare to other variational method to generate templates.
-We used 1 CAD model with viewpoints covering 24 azimuths and 4 elevations.
-Each template takes approximately 80 milliseconds to generate a NZ-WHO template.
+We empirically found out that NZ-WHO performs reasonably well without time consuming calibration stage compare to other variational methods to generate templates.
+We used 1 CAD model with viewpoints covering 24 azimuths and 4 elevations with 250 cells per each template.
+Each template takes approximately 70 milliseconds to generate a NZ-WHO template.
 We also calibrated templates using the method presented in \cite{Aubry14}.
-The calibration learns affine transformation of the detection confidence.% Note that in Section \ref{experiments}, we provide the same experiment with 9 CAD models.
+Briefly, the calibration learns affine transformation of the detection confidence using a set of natural images.% Note that in Section \ref{experiments}, we provide the same experiment with 9 CAD models.
 
@@
     \begin{center}
-\begin{tabular}{|c|c|c|c|c|}
+\begin{tabular}{|c|c|r|c|r|}
 \hline
-Methods &  without Calibration (AP/AVP) & time & w/ Calibration \cite{Aubry14} (AP/AVP) & time \\
+Methods (AP/MPPE) & before calibration  & time & after Calibration \cite{Aubry14} & time \\
 \hline\hline
-HOG\cite{Dalal05}     & 72.28/48.38  &  31ms  & 60.37/50.19               &   8.7 sec \\ 
-WHO-Chol\cite{Hariharan12} &              &3811ms    &                           &   12.4 sec  \\
-WHO-GG                & 81.70/74.20  &104ms &     83.714/75.37              &   8.3 sec \\
-WHO-CG-Z              & 54.42/49.71  &103ms & \textbf{92.80}/\textbf{81.44} &   8.7 sec  \\
+HOG\cite{Dalal05}     & 72.3 / 65.0  &  31ms  & 60.4 / 50.2                 &   8.7 sec \\ 
+WHO\cite{Hariharan12} &              &  3811ms&                             &   12.4 sec  \\
+WHO-CG                & 81.7 / \texbf{84.9}  &  104ms &     83.7 / 87.3             &   8.3 sec \\
+WHO-CG-Z              & 54.4 / 65.1  &  103ms & \textbf{92.8} / 86.7 &   8.7 sec  \\
 % NZC-WHO-Z    & 89.10/\textbf{78.64} &    & 91.15/74.79                  &     \\
-NZ-WHO-CG        & \textbf{90.00}/78.23 & 79ms & 90.31/78.00                   &  8.5 sec   \\
+NZ-WHO-CG        & \textbf{90.0} / 82.8 & 79ms & 90.3 / \textbf{86.8}                   &  8.5 sec   \\
 \hline
 \end{tabular}
+\\\textcolor{red}{TABLE REQUIRES MODIFICATION}
 \end{center}
-\caption{Average Precision(AP) and Average Viewpoint Precision(AVP) \cite{Xiang14} of variations of WHO on 3DObject Car dataset\cite{Savarese07}.
-WHO\cite{Hariharan12} whitens all cell, WHO-ZZ whitens all cell then zero out textureless region.
-NZC-WHO-ZZ first substract mean $\mu$ on non-zero cells and whiten all cells then zero out textureless region.
-NZ-WHO whitens only non-zero cell.
-Note that WHO-ZZ got dramatic performance boost after calibration due to strong impact of substracting $\mu$ from all textureless region}
+\caption{Average Precision(AP) and Mean Precision in Pose Estimation (MPPE) \cite{Lopez-Sastre11} variations of WHO on 3DObject Car dataset\cite{Savarese07}.
+WHO refers to standard WHO using the method presented in \cite{Hariharan12}, WHO-CG uses iterative Conjugate Gradient method to generate WHO.
+WHO-CG-Z uses whiten the whole template and zero out textureless region.
+NZ-WHO-CG is the NZ-WHO which whitens only non-zero cells using iterative Conjugate Gradient method.
+The time column indicates the time to generate one template.
+We followed calibration procedure presented in \cite{Aubry14}.}
 \label{tab:who_initializations}
@@
 First, we make a set of NZ-WHO templates for a set of CAD models from various viewpoints.
-Then we run the bank of NZ-WHO templates as ensembles of weak detectors and show that the rendering image can be We want to see how robust the NZ-WHO to real images a
+Then we run the bank of NZ-WHO templates as an ensemble of weak classifiers and show that our method can work as a standalone detector for simple task.
+This validates that our ensemble of NZ-WHO templates, though each of templates takes 70ms to generate from a rendering image, can robustly perform 2D-3D matching on real images.
 
-\subsection{Object Detection} 
+Then, we show that our method can complement  enrich object detection
+
+\subsection{2D-3D Matching as an Object Detector} 
 Instance-level 2D-3D matching (registration) is a difficult problem since we need a CAD model that looks similar to the object in the image.

### 2014-11-14 intro.tex
Modified table 1, filling out experiment section

@@
   % (b)
-  \caption{Using a bank of CAD models, we generate NZ-WHO templates which can be used to either detect objects directly or initialize pose of an object in the bounding box from other detectors.
-Once initialization is given, we use NZ-WHO to propose and validate plausible pose on-the-fly and further tune the translation, 3D viewpoint and focal length continuously.}
+  \caption{Using a bank of CAD models, we generate NZ-WHO templates which can be used to either detecting objects directly or initializing pose of an object in the bounding box from other detectors.
+Once the initialization is given, we use NZ-WHO to propose and validate plausible pose on-the-fly and further tune the translation, 3D viewpoint and focal length continuously.}
   % \vspace{-1em}
@@
 by-product, we can formulate the alignment problem as a parameter
-search in a continuos pose space, consisting of azimuth, elevation,
-and ~\scream{}, resulting in truely continuous pose estimates, which
+search in a continuos pose space, consisting of yaw, pitch and roll, resulting in truely continuous pose estimates, which
 we implement using MCMC sampling.

### 2014-11-14 egpaper_final.tex
3 and 3.1 first pass

--- 2014-11-14 egpaper_final.tex
@@
 % custom commands
-\newcommand{\scream}[1]{{\bf *** #1! ***}}
+\newcommand{\scream}[1]{{\color{red} \bf *** #1! ***}}
 
@@
 
-We propose Non-Zero Whitened Histograms of Orientations (NZ-WHO), an improvement over WHO, that are both more discriminative than WHO, and can be generated two orders of magnitude faster.
-This speedup means we can generate templates on the fly, allowing our approach to evaluate arbitrary viewpoint hypotheses.
+We propose Non-Zero Whitened Histograms of Orientations (NZ-WHO), an improvement over WHO, that are both more discriminative than WHO, and can be generated in 70ms (compared to several seconds for WHO).
+This speed up means we can generate templates on the fly, allowing our approach to evaluate arbitrary viewpoint hypotheses.
 
-The first innovation comes from using an iterative Conjugate Gradient method.
-To whiten a HOG template, one solves a system of linear equations $\Sigma w = (x - \mu)$ often by decomposing the matrix (LU decomposition or Cholesky decomposition).
-Since the covariance matrix of HOG have nice spectral properties, we can adopt the iterative Conjugate Gradient method to quickly solve the system of linear equations several orders of magnitude faster than decomposition methods.
+The computational efficiency of our approach comes from using the iterative conjugate gradient method to whiten the HOG template.
+Whitening a feature vector $x$ requires a system of linear equations $\Sigma w = (x - \mu)$ to be solved, usually by decomposing the covariance matrix $\Sigma$ (with LU or Cholesky decomposition).
+Since the covariance matrices of HOG templates have nice spectral properties, we can use the conjugate gradient method to solve the system of linear equations several orders of magnitude faster than decomposition methods.
 
-The second innovation is 'Non-Zero' whitening.
-Unlike natural images, rendering produces textureless background such as Figure \ref{fig:rendering}.
-If we use random natural images as a background to make texture, the gradients in the background patch become part of the discriminative patch.
-On the other hand, if we treat the image as a natural image and whiten all region, it creates several artifacts: 1.
-while centering the template (subtracting the mean $\mu$), it introduces strong negative gradients on textureless region (Figure \ref{fig:whocomparison}); 2.
-when decorrelating the centered feature, $\Sigma^{-1}(x - \mu)$, it tries to remove correlation where there is none; 3.
-by including background regions, the size of the signal $x$ gets larger.
+Our second innovation is 'Non-Zero' whitening.
+When synthesizing detection templates from rendered images, a common problem is how to handle the background.
+Some methods \scream{which?} render the model over a natural image background, but this results in gradients in the background being incorporated into the discriminative template.
+Alternatively, we could leave the background textureless \scream{did Hariharan do this?} (see Fig.~\ref{fig:rendering}), but whitening the resulting HOG template produces in undesirable background artifacts.
+These are created when centering the template (by subtracting the mean $\mu$), where strong negative weights are introduced in the textureless region (as seen in Fig.~\ref{fig:whocomparison}).
+This could result in positive matches being suppressed due to spurious background gradients.
 
-To get rid of such artifacts, we select cells with non-zero gradients, whiten regions, and restore the template afterward.
-We call the feature from the pipeline as Non-Zero Whitened Histograms of Orientations.
-More detailed analysis of WHO and NZ-WHO is on Table \ref{tab:who_initializations}
+To remove such artifacts, we construct $x$ using only cells with non-zero gradients.
+After whitening we restore the full template, with the zero-gradient cells left unchanged.
+This approach has the added benefit of reducing the size of the linear system we need to solve, further speeding up our method.
+
+Table \ref{tab:who_initializations} provides a detailed comparison of WHO and NZ-WHO templates, illustrating that our method is faster and more discriminative than Whitened Histograms of Orientations.
+\scream{Does the table show this?}
 
@@
 
-\subsection{Feature Statistics and Covariance Synthesis}
+\subsection{Constructing the Covariance Matrix}
 \label{sec:feature_statistics}
 % Whats used in our work and using Autocovariance matrix
-We first collected the first and second order statistics (mean and autocovariance of HOG feature) of HOG feature from arbitrary natural images.
-Following the practice of \cite{Hariharan12}, which assumes Wide-Sense Stationarity (WSS) of HOG features, we can easily synthesize covariance of arbitrary size template from autocovariance $\Gamma$.
+We first collected the first and second order statistics (mean and autocovariance) of HOG features from arbitrary natural images.
+Following \cite{Hariharan12}, we assume Wide-Sense Stationarity (WSS) of HOG features generated from natural images.
+That is, we assume the mean of a HOG cell is independent of its place in the image, and the autocovariance of patches depends only on their relative location.
+
+In one dimension, let $x(u)$ be the feature at location $u$. Then WSS states that $\mathbb{E}\left[x(u)\right] = \mu_x$ for all $u$, and
+\begin{equation}
+\textrm{cov}_x(u,v) = \textrm{cov}_x(0, v-u) = \Gamma(v-u),
+\end{equation} where $\Gamma$ is the autocovariance. For simplicity, we show the 1D case but this can be easily extended to 2D spatial autocovariance.
+
+Therefore, assuming WSS allows us to synthesize the covariance matrix for templates \emph{of any size} from the autocovariance.
+This hugely reduces the memory required because to build the covariance matrix of a template of $w \times h$ HOG cells (with 31 elements each), we only need a $w \times h \times 31$ autocovariance matrix.
+In comparison, the covariance matrix itself is $(w \times h \times 31) \times (w \times h \times 31)$.
+Furthermore, by using the autocovariance we can avoid storing the covariance matrix for every different aspect ratio used during detection.
+
 To further simplify $\Gamma$, we assumed horizontal and vertical symmetry.
+In our implementation, we compute a $40 \times 40 \times 31$ autocovariance matrix, meaning we can synthesize covariance matrices for HOG grids of as big as $40 \times 40$.
+
+Synthesizing the covariance matrix is memory copy operations so we used GPU to speed up the process (Figure \ref{fig:covariancetime}).
 
@@
 
-More formally, let $x(u)$ be the HOG feature on location $u$ then, by WSS, $\mathbb{E}\left[x(u)\right] = \mathbb{E}(x(u+v)) = \mu_x$ and $\mathbb{E}\left[(x(u)-\mu_x)(x(v)-\mu_x)\right]  =\mathbb{E}\left[(x(0)-\mu_x)(x(v-u)-\mu_x)\right] = \Gamma(0,v-u)$.
-So, one can synthesize covariance matrix from autocovariance $\Gamma$.
-For simplicity, we used 1D case but this can be easily extended to 2D spatial autocovariance.
-
-However, unlike small fixed-sized mid-level patches, the root templates have different aspect ratios, different gradient patterns and large number of HOG cells which results in large covariance $\Sigma \in \mathcal{R}^{7000 \times 7000}$ that is difficult to cache.
+%However, unlike small fixed-sized mid-level patches, the root templates have different aspect ratios, different gradient patterns and large number of HOG cells which results in large covariance $\Sigma \in \mathcal{R}^{7000 \times 7000}$ that is difficult to cache.
 Thus, to generate a NZ-WHO template, we have to synthesize a covariance matrix and solve the system of linear equations.
-
-Synthesizing the covariance matrix is memory copy operations so we used GPU to speed up the process (Figure \ref{fig:covariancetime}).
 

### 2014-11-14 egpaper_final.tex
minor change

--- 2014-11-14 egpaper_final.tex
@@
 
-Then, we show that our method can complement  enrich object detection
+Then, we show that our method can complement the detection bounding boxes coming out of standard object detectors.
+This process will enrich object detection bounding boxes with 2D-3D matching which gives continuous viewpoint estimation, a CAD model (rendering, depth) and fine-grained category.
 
 \subsection{2D-3D Matching as an Object Detector} 
-Instance-level 2D-3D matching (registration) is a difficult problem since we need a CAD model that looks similar to the object in the image.
+We created ensemble of NZ-WHO templates using 9 CAD models and measured the Average Precision (AP) of object detection task and Mean Precision in Pose Estimation (MPPE) \cite{Lopez-Sastre11}.
+MPPE is the average of viewpoint accuracy.
+
+Our ensemble of NZ-WHO templates are generated from rendering image with no calibration but shows strong performance on object detection.
+The method we are comparing against are Aspect Layout Model (ALM) \cite{Xiang12} and VOC-DPM \cite{Pepik12}.
+Each method requires complex 3D modeling and viewpoint annotated natural images.
+\begin{figure}[h]
+    \begin{center}
+    \setlength\tabcolsep{0pt}
+\begin{tabular}{cc}
+  \includegraphics[width=0.45\linewidth]{car_3dobject/7.png} &   
+  \includegraphics[width=0.45\linewidth]{car_3dobject/8.png}\\ [-15pt]
+%   (a) & (b) \\[0pt]
+  \includegraphics[width=0.45\linewidth]{car_3dobject/11.png} &   
+  \includegraphics[width=0.45\linewidth]{car_3dobject/12.png}\\ [-5pt]
+%  (c) & (d) \\[0pt]
+\end{tabular}
+\end{center}
+\caption{Detection results on 3D-Object dataset \cite{Savarese07}. Original image (left) and detection result overlaid on top with a bounding box and corresponding confidence score(right)}
+  \label{fig:3dobject}
+\end{figure}
+
+% Instance-level 2D-3D matching (registration) is a difficult problem since we need a CAD model that looks similar to the object in the image.
 Especially, due to extreme intraclass variability of chair \cite{Aubry14} used a very large collection of CAD models to cover variety of chairs.
@@
 \end{table}
-
-\begin{figure}[h]
-    \begin{center}
-    \setlength\tabcolsep{0pt}
-\begin{tabular}{cc}
-  \includegraphics[width=0.45\linewidth]{car_3dobject/7.png} &   
-  \includegraphics[width=0.45\linewidth]{car_3dobject/8.png}\\ [-15pt]
-%   (a) & (b) \\[0pt]
-  \includegraphics[width=0.45\linewidth]{car_3dobject/11.png} &   
-  \includegraphics[width=0.45\linewidth]{car_3dobject/12.png}\\ [-5pt]
-%  (c) & (d) \\[0pt]
-\end{tabular}
-\end{center}
-\caption{Detection results on 3D-Object dataset \cite{Savarese07}, each of four images have (top left) original image, (top right) top detection rendering overlaid, (bottom right) false positives, (bottom left) true positives.
-Each with confidence score and colored bounding box}
-  \label{fig:3dobject}
-\end{figure}
 

### 2014-11-14 egpaper_final.tex
minor updates

--- 2014-11-14 egpaper_final.tex
@@
 % custom commands
-\newcommand{\scream}[1]{{\color{red} \bf *** #1! ***}}
+\newcommand{\scream}[1]{{\color{red} \bf *** #1 ***}}
 
@@
 % History of Whitening and how whitening works
-Recently, Hariharan \etal.
-introduced Whitened Histograms of Orientations (WHO) \cite{Hariharan12}, which used statistics from natural images to whiten HOG templates, making them more discriminative.
+Recently, Hariharan \emph{et al.} introduced Whitened Histograms of Orientations (WHO) \cite{Hariharan12}, which used statistics from natural images to whiten HOG templates, making them more discriminative.
 Whitening is a common signal processing operation for decorrelating a set of random variables \cite{Martinsson05, Belouchrani00}.
@@
 However, this generalization comes at the cost of fine-grained information, including accurate 3D pose and object sub-category recognition.
-Such methods typically produce bounding box detection hypotheses, will little further information.
+Such methods typically produce bounding box detection hypotheses, with little further information.
 
@@
 
-We propose Non-Zero Whitened Histograms of Orientations (NZ-WHO), an improvement over WHO, that are both more discriminative than WHO, and can be generated in 70ms (compared to several seconds for WHO).
+We propose Non-Zero Whitened Histograms of Orientations (NZ-WHO), that are both more discriminative than WHO, and can be generated in 70ms (compared to several seconds for WHO).
 This speed up means we can generate templates on the fly, allowing our approach to evaluate arbitrary viewpoint hypotheses.
@@
 Whitening a feature vector $x$ requires a system of linear equations $\Sigma w = (x - \mu)$ to be solved, usually by decomposing the covariance matrix $\Sigma$ (with LU or Cholesky decomposition).
-Since the covariance matrices of HOG templates have nice spectral properties, we can use the conjugate gradient method to solve the system of linear equations several orders of magnitude faster than decomposition methods.
+Since the covariance matrices of HOG templates have nice spectral properties (see Section \ref{sec:fast_whitening}), the conjugate gradient method will converge to the solution several orders of magnitude faster than decomposition methods.
 
@@
 \subsection{Fast Whitening and Non-Zero Selection}
-
+\label{sec:fast_whitening}
 \begin{figure}[t]
@@
 To whiten a signal $x$, we have to solve $\Sigma w = x - \mu$ which takes $O(n^3)$ time.
-In \cite{Hariharan12}, the authors make use of Positive Semi-Definite and Hermitian properties of a covariance matrix to use Cholesky decomposition and Gaussian elimination which is twice faster than LU decomposition.
-
+In \cite{Hariharan12}, the authors make use of positive semidefinite and Hermitian properties of a covariance matrix to use Cholesky decomposition and Gaussian elimination which is twice as fast a the LU decomposition.
 However, if we make use of a spectral property of the covariance matrix, we can further speed up the whitening stage.
@@
 \end{figure}
-
 [Figure spectral analysis]
@@
 
-We empirically found out that NZ-WHO performs reasonably well without time consuming calibration stage compare to other variational methods to generate templates.
-We used 1 CAD model with viewpoints covering 24 azimuths and 4 elevations with 250 cells per each template.
-Each template takes approximately 70 milliseconds to generate a NZ-WHO template.
+We empirically found out that NZ-WHO performs reasonably well without time consuming calibration stage compare to other variational method to generate templates.
+We used 1 CAD model with viewpoints covering 24 azimuths and 4 elevations.
+Each template takes approximately 80 milliseconds to generate a NZ-WHO template.
 We also calibrated templates using the method presented in \cite{Aubry14}.
-Briefly, the calibration learns affine transformation of the detection confidence using a set of natural images.% Note that in Section \ref{experiments}, we provide the same experiment with 9 CAD models.
+The calibration learns affine transformation of the detection confidence.% Note that in Section \ref{experiments}, we provide the same experiment with 9 CAD models.
 
@@
     \begin{center}
-\begin{tabular}{|c|c|r|c|r|}
+\begin{tabular}{|c|c|c|c|c|}
 \hline
-Methods (AP/MPPE) & before calibration  & time & after Calibration \cite{Aubry14} & time \\
+Methods &  without Calibration (AP/AVP) & time & w/ Calibration \cite{Aubry14} (AP/AVP) & time \\
 \hline\hline
-HOG\cite{Dalal05}     & 72.3 / 65.0  &  31ms  & 60.4 / 50.2                 &   8.7 sec \\ 
-WHO\cite{Hariharan12} &              &  3811ms&                             &   12.4 sec  \\
-WHO-CG                & 81.7 / \texbf{84.9}  &  104ms &     83.7 / 87.3             &   8.3 sec \\
-WHO-CG-Z              & 54.4 / 65.1  &  103ms & \textbf{92.8} / 86.7 &   8.7 sec  \\
+HOG\cite{Dalal05}     & 72.28/48.38  &  31ms  & 60.37/50.19               &   8.7 sec \\ 
+WHO-Chol\cite{Hariharan12} &              &3811ms    &                           &   12.4 sec  \\
+WHO-GG                & 81.70/74.20  &104ms &     83.714/75.37              &   8.3 sec \\
+WHO-CG-Z              & 54.42/49.71  &103ms & \textbf{92.80}/\textbf{81.44} &   8.7 sec  \\
 % NZC-WHO-Z    & 89.10/\textbf{78.64} &    & 91.15/74.79                  &     \\
-NZ-WHO-CG        & \textbf{90.0} / 82.8 & 79ms & 90.3 / \textbf{86.8}                   &  8.5 sec   \\
+NZ-WHO-CG        & \textbf{90.00}/78.23 & 79ms & 90.31/78.00                   &  8.5 sec   \\
 \hline
 \end{tabular}
-\\\textcolor{red}{TABLE REQUIRES MODIFICATION}
 \end{center}
-\caption{Average Precision(AP) and Mean Precision in Pose Estimation (MPPE) \cite{Lopez-Sastre11} variations of WHO on 3DObject Car dataset\cite{Savarese07}.
-WHO refers to standard WHO using the method presented in \cite{Hariharan12}, WHO-CG uses iterative Conjugate Gradient method to generate WHO.
-WHO-CG-Z uses whiten the whole template and zero out textureless region.
-NZ-WHO-CG is the NZ-WHO which whitens only non-zero cells using iterative Conjugate Gradient method.
-The time column indicates the time to generate one template.
-We followed calibration procedure presented in \cite{Aubry14}.}
+\caption{Average Precision(AP) and Average Viewpoint Precision(AVP) \cite{Xiang14} of variations of WHO on 3DObject Car dataset\cite{Savarese07}.
+WHO\cite{Hariharan12} whitens all cell, WHO-ZZ whitens all cell then zero out textureless region.
+NZC-WHO-ZZ first substract mean $\mu$ on non-zero cells and whiten all cells then zero out textureless region.
+NZ-WHO whitens only non-zero cell.
+Note that WHO-ZZ got dramatic performance boost after calibration due to strong impact of substracting $\mu$ from all textureless region}
 \label{tab:who_initializations}
@@
 \section{Continuous Viewpoint and Focal Length Estimation for Fine Tuning}
-\label{sec:fine}
 
@@
 % there are several advantages that was not possible such as \textbf{on-the-fly} template generation and making large number of templates  
-
-\begin{figure}[t]
-\centering
-    \includegraphics[width=0.7\linewidth]{tuning2} \\ [-5pt]
-    \caption{Different modes of Metropolis Hasting proposals, see Section \ref{sec:fine}}
- \label{fig:tuningmode}
-\end{figure}
-
 \begin{figure}[t]
  \begin{center}
-    \setlength\tabcolsep{0pt}
-    \begin{tabular}{ccc}
-    % \includegraphics[width=0.9\linewidth]{tuning} 
-   \includegraphics[width=0.33\linewidth]{tuning/1.png} &
-   \includegraphics[width=0.33\linewidth]{tuning/2.png} &
-   \includegraphics[width=0.33\linewidth]{tuning/3.png} \\[-5pt]
-   (a) & (b) & (c)\\
-   \includegraphics[width=0.33\linewidth]{tuning/4.png} &
-   \includegraphics[width=0.33\linewidth]{tuning/5.png} &
-   \includegraphics[width=0.33\linewidth]{tuning/6.png} \\[-5pt]
-   (d) & (e) & (f)\\
-   \end{tabular}
+    \includegraphics[width=0.9\linewidth]{tuning2} 
+    \includegraphics[width=0.9\linewidth]{tuning} 
  \end{center}
@@
 First, we make a set of NZ-WHO templates for a set of CAD models from various viewpoints.
-Then we run the bank of NZ-WHO templates as an ensemble of weak classifiers and show that our method can work as a standalone detector for simple task.
-This validates that our ensemble of NZ-WHO templates, though each of templates takes 70ms to generate from a rendering image, can robustly perform 2D-3D matching on real images.
+Then we run the bank of NZ-WHO templates as ensembles of weak detectors and show that the rendering image can be We want to see how robust the NZ-WHO to real images a
 
-Then, we show that our method can complement  enrich object detection
-
-\subsection{2D-3D Matching as an Object Detector} 
+\subsection{Object Detection} 
 Instance-level 2D-3D matching (registration) is a difficult problem since we need a CAD model that looks similar to the object in the image.
@@
 Thus V-DPM and VOC-DPM provide discrete azimuth only whereas our method provides 3D viewpoint (yaw, pitch, roll), CAD instance (model index, rendering, depth) and focal length.
-
-\begin{figure*}[h]
-\setlength\tabcolsep{1pt}
-\centering
-\begin{tabular}{|c|c|c|c|c|}
-   \hline
-  \includegraphics[width=0.24\textwidth]{car_cnn/1a.png} &   
-  \includegraphics[width=0.24\textwidth]{car_cnn/1b.png} &   
-  \includegraphics[width=0.24\textwidth]{car_cnn/1c.png} &   
-  \includegraphics[width=0.24\textwidth]{car_cnn/1d.png}  \\  
-   \hline
-  \includegraphics[width=0.24\textwidth]{car_cnn/2a.png} &   
-  \includegraphics[width=0.24\textwidth]{car_cnn/2b.png} &   
-  \includegraphics[width=0.24\textwidth]{car_cnn/2c.png} &   
-  \includegraphics[width=0.24\textwidth]{car_cnn/2e.png}  \\  
-   \hline
-  \includegraphics[width=0.24\textwidth]{car_cnn/4a.png} &   
-  \includegraphics[width=0.24\textwidth]{car_cnn/4b.png} &   
-  \includegraphics[width=0.24\textwidth]{car_cnn/4c.png} &   
-  \includegraphics[width=0.24\textwidth]{car_cnn/4d.png}  \\  
-%    \hline
-%   \includegraphics[width=0.24\textwidth]{car_cnn/10a.png} &   
-%   \includegraphics[width=0.24\textwidth]{car_cnn/10b.png} &   
-%   \includegraphics[width=0.24\textwidth]{car_cnn/10c.png} &   
-%   \includegraphics[width=0.24\textwidth]{car_cnn/10d.png}  \\  
-%   \hline 
-%   \includegraphics[width=0.24\textwidth]{bicycle_cnn/3a.png} &   
-%   \includegraphics[width=0.24\textwidth]{bicycle_cnn/3b.png} &   
-%   \includegraphics[width=0.24\textwidth]{bicycle_cnn/3c.png} &   
-%   \includegraphics[width=0.24\textwidth]{bicycle_cnn/3d.png}  \\
-  \hline
-  \includegraphics[width=0.24\textwidth]{bicycle_cnn/7a.png} &   
-  \includegraphics[width=0.24\textwidth]{bicycle_cnn/7b.png} &   
-  &\\
-  \hline
-  \includegraphics[width=0.24\textwidth]{bicycle_cnn/4a.png} &   
-  \includegraphics[width=0.24\textwidth]{bicycle_cnn/4b.png} &   
-  \includegraphics[width=0.24\textwidth]{bicycle_cnn/4c.png} &   
-  \includegraphics[width=0.24\textwidth]{bicycle_cnn/4d.png}  \\
-  \hline
-  CNN Proposals & \multicolumn{3}{|c|}{Our matching results on proposal bounding boxes} \\
-  \hline
-\end{tabular}
-\caption{Example enriched bounding boxex.
-Given R-CNN\cite{Girshick14} detection bounding boxes, our method predicted 2D-3D matching reasonably.
-On the first column, R-CNN detection bounding boxes overlaid.
-From the second to the last columns, output of our method given a R-CNN box.
-Blue boxes are R-CNN output and purle boxes are the tightest bounding box enclosing predicted CAD model}
-  \label{fig:pascal12cnn}
-\end{figure*}
 

### 2014-11-14 intro.tex
minor updates

--- 2014-11-13 intro.tex
@@
   Lim14,Kholgade14, Chen13, Kostas14}. Interestingly, the problem of matching 3D models to 2D
-images has been targeted since the early days of computer
+images has been explored since the early days of computer
 vision~\cite{Lowe87}, but had largely been neglected in recent years
@@
 
+\scream{Are we keeping the paragraphs from here...}
+
 outperforming previous results on this dataset by considerable
@@
 
+\scream{... to here?}
+
 \subsection{Approach Overview}

### 2014-11-14 egpaper_final.tex

@@
 
+%Commented out because of git conflict
+%Then, we show that our method can complement the detection bounding boxes coming out of standard object detectors.
+This process will enrich object detection bounding boxes with 2D-3D matching which gives continuous viewpoint estimation, a CAD model (rendering, depth) and fine-grained category.
+
+%\subsection{2D-3D Matching as an Object Detector} 
+%We created ensemble of NZ-WHO templates using 9 CAD models and measured the Average Precision (AP) of object detection task and Mean Precision in Pose Estimation (MPPE) \cite{Lopez-Sastre11}.
+MPPE is the average of viewpoint accuracy.
+
+Our ensemble of NZ-WHO templates are generated from rendering image with no calibration but shows strong performance on object detection.
+The method we are comparing against are Aspect Layout Model (ALM) \cite{Xiang12} and VOC-DPM \cite{Pepik12}.
+Each method requires complex 3D modeling and viewpoint annotated natural images.
 \begin{figure}[h]
@@
 \end{center}
-\caption{Detection results on 3D-Object dataset \cite{Savarese07}, each of four images have (top left) original image, (top right) top detection rendering overlaid, (bottom right) false positives, (bottom left) true positives.
-Each with confidence score and colored bounding box}
+\caption{Detection results on 3D-Object dataset \cite{Savarese07}. Original image (left) and detection result overlaid on top with a bounding box and corresponding confidence score(right)}
   \label{fig:3dobject}
 \end{figure}
+
+% Instance-level 2D-3D matching (registration) is a difficult problem since we need a CAD model that looks similar to the object in the image.
+Especially, due to extreme intraclass variability of chair \cite{Aubry14} used a very large collection of CAD models to cover variety of chairs.
+Similarly, \cite{Lim14}
+\begin{table}[!htbp]
+  \begin{center}
+    \begin{tabular}{|c|c|c|c|}
+    \hline
+     AP/MPPE& Ours & ALM\cite{Xiang12} & VOCDPM\cite{Pepik12} \\
+    \hline\hline
+    car & \textbf{99.8}/91.7 &  98.4/93.4 & \textbf{99.8}/\textbf{97.5} \\ 
+    bicycle & 93.0/87.4 & 93.0/91.4 & \textbf{98.8}/\textbf{97.5} \\
+    \hline
+    \end{tabular}
+  \end{center}
+  \caption{Average Precision(AP) and Average Viewpoint Accuracy(AVA) on 3DObject dataset.
+Though we do not need any training images and made templates in few minues, it performs on par with state of the art detectors yet it gives high quality 2D-3D matching.}
+  \label{tab:3dobject}
+\end{table}
 

### 2014-11-14 egpaper_final.tex
Experiment section, intro minor modifications

--- 2014-11-14 egpaper_final.tex
@@
 To estimate pose they use synthetic renderings of CAD models to learn discriminative mid-level patches.
-\cite{Aubry14} calibrates these patches on a small set of real images, while \cite{Lim14} present a method for learning the relative discriminativeness of the patches.
+\cite{Aubry14} calibrates these patches on a small set of real images, while \cite{Lim14} presents a method for learning the relative discriminativeness of the patches.
 
@@
 HOG\cite{Dalal05}     & 72.3 / 65.0  &  31ms  & 60.4 / 50.2                 &   8.7 sec \\ 
-WHO\cite{Hariharan12} &              &  3811ms&                             &   12.4 sec  \\
-WHO-CG                & 81.7 / \texbf{84.9}  &  104ms &     83.7 / 87.3             &   8.3 sec \\
+WHO\cite{Hariharan12} & 82.1 / 85.4  &  3811ms&                             &   12.4 sec  \\
+WHO-CG                & 81.7 / \textbf{84.9}  &  104ms &     83.7 / 87.3             &   8.3 sec \\
 WHO-CG-Z              & 54.4 / 65.1  &  103ms & \textbf{92.8} / 86.7 &   8.7 sec  \\
@@
 
-Then, we show that our method can complement the detection bounding boxes coming out of standard object detectors.
+Second, we show that our method can complement the detection bounding boxes coming out of standard object detectors.
 This process will enrich object detection bounding boxes with 2D-3D matching which gives continuous viewpoint estimation, a CAD model (rendering, depth) and fine-grained category.
@@
 \subsection{2D-3D Matching as an Object Detector}
+
 We created ensemble of NZ-WHO templates using 9 CAD models and measured the Average Precision (AP) of object detection task and Mean Precision in Pose Estimation (MPPE) \cite{Lopez-Sastre11}.
@@
 
-Our ensemble of NZ-WHO templates are generated from rendering image with no calibration but shows strong performance on object detection.
-The method we are comparing against are Aspect Layout Model (ALM) \cite{Xiang12} and VOC-DPM \cite{Pepik12}.
-Each method requires complex 3D modeling and viewpoint annotated natural images.
+Our ensemble of NZ-WHO templates is generated from rendering image with no calibration but shows strong performance on object detection.
+The baseline method are Aspect Layout Model (ALM) \cite{Xiang12} and VOC-DPM \cite{Pepik12}.
+Note that the baseline methods require complex 3D modeling and viewpoint annotated natural images.
+
+The detection result is on Table \ref{tab:3dobject} and example output from our method is on Figure \ref{fig:3dobject}.
+
 \begin{figure}[h]
@@
   \end{center}
-  \caption{Average Precision(AP) and Average Viewpoint Accuracy(AVA) on 3DObject dataset.
-Though we do not need any training images and made templates in few minues, it performs on par with state of the art detectors yet it gives high quality 2D-3D matching.}
+  \caption{Average Precision(AP) and Mean Precision in Pose Estimation (MPPE) on 3DObject dataset car category.
+Our method produces high quality 2D-3D matching yet performs on par with state-of-the art detectors.}
   \label{tab:3dobject}
@@
 Thus V-DPM and VOC-DPM provide discrete azimuth only whereas our method provides 3D viewpoint (yaw, pitch, roll), CAD instance (model index, rendering, depth) and focal length.
+
+We used detection bounding boxes and augment it using our method to give viewpoint estimation.
+We used detection bounding boxes from two different methods: VOC-DPM \cite{Pepik12} and R-CNN \cite{Girshick14}.
+VOC-DPM is a variation of DPM that can estimate viewpoint and is the state-of-the-art performance in viewpoint estimation \cite{Xiang14}.
+The result is on Table \ref{tab:pascal12} and precision recall curves for car using R-CNN + Ours are on Figure \ref{fig:car_cnn_ap}.
+
+We got significant improvement on viewpoint estimation by using our method on top of general purpose detectors.
+Note that our method estimates azimuth, elevation, in-plane rotation, focal length estimation, fine-grained categorization whereas V-DPM, VOC-DPM only estimate discrete viewpoints.
+
+Example outputs are on Figure \ref{fig:pascal12cnn}.
 
@@
 \end{tabular}
-\caption{Example enriched bounding boxex.
+\caption{Example enriched bounding boxes.
 Given R-CNN\cite{Girshick14} detection bounding boxes, our method predicted 2D-3D matching reasonably.
@@
 From the second to the last columns, output of our method given a R-CNN box.
-Blue boxes are R-CNN output and purle boxes are the tightest bounding box enclosing predicted CAD model}
+Blue boxes are R-CNN output and purple boxes are the tightest bounding box enclosing predicted CAD model}
   \label{fig:pascal12cnn}
@@
 \hline
-AP/AVP              & VDPM \cite{Xiang14} & VOC-DPM \cite{Pepik12}  & \cite{Pepik12} + Ours (discrete) & \cite{Pepik12} + Ours (full) & R-CNN + Ours (discrete) & R-CNN + Ours (full)\\
+AP/AVP              & V-DPM \cite{Xiang14} & VOC-DPM \cite{Pepik12}  & \cite{Pepik12} + Ours (discrete) & \cite{Pepik12} + Ours (full) & R-CNN + Ours (discrete) & R-CNN + Ours (full)\\
 \hline\hline
@@
 
+\begin{figure}[h]
+\setlength\tabcolsep{1pt}
+\centering
+\begin{tabular}{cc}
+  \hline
+  \includegraphics[width=0.49\linewidth]{car_cnn4_crop.png} &   
+  \includegraphics[width=0.49\linewidth]{car_cnn8_crop.png} \\   
+  \includegraphics[width=0.49\linewidth]{car_cnn16_crop.png} &   
+  \includegraphics[width=0.49\linewidth]{car_cnn24_crop.png} \\   
+  \hline
+\end{tabular}
+\caption{Average Precision (AP) and Average Viewpoint Precision (AVP) and viewpoint confusion table on PASCAL 12 car validation set using R-CNN + Ours.
+From the top left, 4 views, 8 views, 16 views and 24 views.
+Since our method only augment the object detection, the AP remains the same for all cases.
+As we increase the viewpoint estimation, the AVP decreases.
+Note that since we estimate null viewpoint if our method fails to find match, there are more 0 viewpoint predictions (top row of confusion matrices) }
+  \label{fig:car_cnn_ap}
+\end{figure}
+
 \subsection{Stability of Our Method for Irregular Bounding Boxes}
 
-Generic object detectors sometimes give overlapping detection bounding boxes of the same object with different aspect ratio or truncation.
-For instance, R-CNN \cite{Girshick14} usually gives very irregular bounding boxes since the proposals bounding boxes comes from various methods.
+% Generic object detectors give overlapping detection bounding boxes of the same object which can be handled by non maximal suppression. For these overlapping detections,
 
+R-CNN detection bounding boxes are irregular in shape since they come from other region proposal methods and sometimes they truncate objects.
 To handle such irregular shape and truncation, we added small context around the bounding boxes and run our method.
-We consider all possible truncation which can be efficiently computed using FFT-based convolution (refer Section.
+
+We assumed that object can be arbitrarily truncated by the bounding box and search all plausible scales and translations.
+This can be efficiently computed using FFT-based convolution (refer Section.
 \ref{sec:fft}).
 We put examples of such conditions in Figure \ref{fig:stability}.
-Although the input bounding boxex are drastically different and have sever truncations.
-Our method reliably generated reasonable prediction of pose and model.
+Although the input bounding boxes are irregular and truncate objects, our method reliably generated a reasonable prediction of pose, translation, scale and CAD model.
+
+% R-CNN \cite{Girshick14} gives very irregular bounding boxes since the proposals bounding boxes come from various methods.
 

### 2014-11-14 intro.tex
Experiment section, intro minor modifications

--- 2014-11-14 intro.tex
@@
 by-product, we can formulate the alignment problem as a parameter
-search in a continuos pose space, consisting of yaw, pitch and roll, resulting in truely continuous pose estimates, which
+search in a continuous pose space, consisting of yaw, pitch and roll, resulting in truely continuous pose estimates, which
 we implement using MCMC sampling.
@@
 rendered images. To our knowledge, our method constitutes the first
-attempt to simultanously render and train exemplar detectors on the
+attempt to simultaneously render and train exemplar detectors on the
 fly.
@@
 a result, we can refine the original detections with additional
-estimates of 3D continuos pose and a 3D CAD model exemplar.
+estimates of 3D continuous pose and a 3D CAD model exemplar.
 
@@
 processing stage of generic object detection. Our pipeline requires
-only several minutes to make templates for rough viewpoints and
+only few minutes to make templates for rough viewpoints and
 
@@
 show that our 2D-3D matching performs better than standard detectors
-in categories where training data lacks. We then use our method for
-image query to pull out closest CAD model in a bank of CAD models.
+in categories where training data is insufficient. We then use our method for
+image query to pull out the closest CAD model in a bank of CAD models.
 
@@
 and light weight so this can be easily adapted to be used for any
-generic object detectors. Also to facilitate the future work, all our
+generic object detectors. Also to facilitate future work, all our
 alignment result on PASCAL12 and code are publicly available online.
@@
 Our method is in line with \cite{Aubry14, Lim14} in the sense that we
-use only renderings not real images. However, rather than using fixed
-sized mid-level patches, we use whole object and make root
+use only renderings, not real images. However, rather than using fixed
+sized mid-level patches, we use whole objects and make root
 templates. By using root templates, there is no need to learn a
@@
 To overcome these difficulties, we propose the Non-Zero Whitened
-Histograms of Orientations with iterative Conjugate Gradient to
+Histograms of Orientations (NZ-WHO) with iterative Conjugate Gradient to
 generate templates in real time and enrich rectangular boxes with high
@@
 as a standalone ensemble of exemplar-based object detectors (Figure
-\ref{fig:front}) but the real power comes from combining generic
+\ref{fig:front}) but its real power comes from combining generic
 object detectors and complement rectangular bounding boxes. Our method
 is simple in design; is several orders of magnitude faster than
-traditional method; requires only CAD models; doesn't need images nor
+traditional method; requires only CAD models; does not need neither images nor
 calibration, yet is powerful in giving high-quality metadata. These

### 2014-11-14 egpaper_final.tex

@@
 \end{tabular}
-\\\textcolor{red}{TABLE REQUIRES MODIFICATION}
 \end{center}
@@
 First, we make a set of NZ-WHO templates for a set of CAD models from various viewpoints.
-Then we run the bank of NZ-WHO templates as an ensemble of weak classifiers and show that our method can work as a standalone detector for simple task.
-This validates that our ensemble of NZ-WHO templates, though each of templates takes 70ms to generate from a rendering image, can robustly perform 2D-3D matching on real images.
+Then we run the bank of NZ-WHO templates as ensembles of weak detectors and show that the rendering image can be We want to see how robust the NZ-WHO to real images a
 
@@
 MPPE is the average of viewpoint accuracy.
-
+\subsection{Object Detection} 
+Instance-level 2D-3D matching (registration) is a difficult problem since we need a CAD model that looks similar to the object in the image.
+Especially, due to extreme intraclass variability of chair \cite{Aubry14} used a very large collection of CAD models to cover variety of chairs.
+Similarly, \cite{Lim14}
 Our ensemble of NZ-WHO templates is generated from rendering image with no calibration but shows strong performance on object detection.

### 2014-11-14 intro.tex

@@
   % (b)
-  \caption{Using a bank of CAD models, we generate NZ-WHO templates which can be used to either detecting objects directly or initializing pose of an object in the bounding box from other detectors.
-Once the initialization is given, we use NZ-WHO to propose and validate plausible pose on-the-fly and further tune the translation, 3D viewpoint and focal length continuously.}
+  \caption{Using a bank of CAD models, we generate NZ-WHO templates which can be used to either detect objects directly or initialize pose of an object in the bounding box from other detectors.
+Once initialization is given, we use NZ-WHO to propose and validate plausible pose on-the-fly and further tune the translation, 3D viewpoint and focal length continuously.}
   % \vspace{-1em}

### 2014-11-14 egpaper_final.tex
more edits to 3.x

--- 2014-11-14 egpaper_final.tex
@@
 
-Therefore, assuming WSS allows us to synthesize the covariance matrix for templates \emph{of any size} from the autocovariance.
-This hugely reduces the memory required because to build the covariance matrix of a template of $w \times h$ HOG cells (with 31 elements each), we only need a $w \times h \times 31$ autocovariance matrix.
+Therefore, assuming WSS allows us to synthesize the covariance matrix for templates \emph{of any size} from the autocovariance matrix.
+This hugely reduces the memory required because to build the covariance matrix of a template of $w \times h$ HOG cells (with 31 elements per cell), we only need a $w \times h \times 31$ autocovariance matrix.
 In comparison, the covariance matrix itself is $(w \times h \times 31) \times (w \times h \times 31)$.
@@
 To further simplify $\Gamma$, we assumed horizontal and vertical symmetry.
-In our implementation, we compute a $40 \times 40 \times 31$ autocovariance matrix, meaning we can synthesize covariance matrices for HOG grids of as big as $40 \times 40$.
+In our implementation, we compute a $40 \times 40 \times 31$ autocovariance matrix, meaning we can synthesize covariance matrices for HOG grids as big as $40 \times 40$.
+In practice we limit the number of cells per template to 250.
 
-Synthesizing the covariance matrix is memory copy operations so we used GPU to speed up the process (Figure \ref{fig:covariancetime}).
+We use the GPU to parallelize the lookup of the correct autocovariance cells during covariance matrix syntheses, which is \scream{x} times faster than using the CPU (Figure \ref{fig:covariancetime}).
 
@@
 To whiten a signal $x$, we have to solve $\Sigma w = x - \mu$ which takes $O(n^3)$ time.
-In \cite{Hariharan12}, the authors make use of positive semidefinite and Hermitian properties of a covariance matrix to use Cholesky decomposition and Gaussian elimination which is twice as fast a the LU decomposition.
-However, if we make use of a spectral property of the covariance matrix, we can further speed up the whitening stage.
+In \cite{Hariharan12}, the authors make use of the fact that covariance matrices are Hermitian and positive semidefinite to solve the system via the Cholesky decomposition, which is twice as fast as the LU decomposition.
+However, by considering the properties of the covariance matrix of the HOG template, we show that the conjugate gradient method can further speed up the whitening stage.
 
-  If we use a high resolution template such as \ref{fig:rendering}
+%  If we use a high resolution template such as \ref{fig:rendering}
 
@@
 
-In our setting, we used high resolution template which has more than 250 HOG cells.
+%In our setting, we used high resolution template which has more than 250 HOG cells.
 This result in $\Sigma \in \mathcal{R}^{7500 \times 7500}$.
@@
 
+Figure \ref{fig:spectral} shows the singular values of a template covariance matrix with a small regularization constant added to the diagonal.
+The singular values are clustered in small region and most of the energies are concentrated on the first \scream{x} singular values.
+Therefore, conjugate gradient will converge in $O(n^2\kappa)$ time, faster
+
 We also used iterative Conjugate Gradient to make use of low rank property of the covariance \cite{Gharbi12}.
-After adding small regularization, the regularized covariance matrix has nice spectral property (Figure \ref{fig:spectral}.
+After adding small regularization, the regularized covariance matrix has nice spectral property (Figure \ref{fig:spectral}).
 The singular values are clustered in small region and most of the energies are concentrated on the first (number) singular values.
@@
 
-%Commented out because of git conflict
-%Then, we show that our method can complement the detection bounding boxes coming out of standard object detectors.
-This process will enrich object detection bounding boxes with 2D-3D matching which gives continuous viewpoint estimation, a CAD model (rendering, depth) and fine-grained category.
-
-%\subsection{2D-3D Matching as an Object Detector} 
-%We created ensemble of NZ-WHO templates using 9 CAD models and measured the Average Precision (AP) of object detection task and Mean Precision in Pose Estimation (MPPE) \cite{Lopez-Sastre11}.
-MPPE is the average of viewpoint accuracy.
-
-Our ensemble of NZ-WHO templates are generated from rendering image with no calibration but shows strong performance on object detection.
-The method we are comparing against are Aspect Layout Model (ALM) \cite{Xiang12} and VOC-DPM \cite{Pepik12}.
-Each method requires complex 3D modeling and viewpoint annotated natural images.
 \begin{figure}[h]
@@
 \end{center}
-\caption{Detection results on 3D-Object dataset \cite{Savarese07}. Original image (left) and detection result overlaid on top with a bounding box and corresponding confidence score(right)}
+\caption{Detection results on 3D-Object dataset \cite{Savarese07}, each of four images have (top left) original image, (top right) top detection rendering overlaid, (bottom right) false positives, (bottom left) true positives.
+Each with confidence score and colored bounding box}
   \label{fig:3dobject}
 \end{figure}
-
-% Instance-level 2D-3D matching (registration) is a difficult problem since we need a CAD model that looks similar to the object in the image.
-Especially, due to extreme intraclass variability of chair \cite{Aubry14} used a very large collection of CAD models to cover variety of chairs.
-Similarly, \cite{Lim14}
-\begin{table}[!htbp]
-  \begin{center}
-    \begin{tabular}{|c|c|c|c|}
-    \hline
-     AP/MPPE& Ours & ALM\cite{Xiang12} & VOCDPM\cite{Pepik12} \\
-    \hline\hline
-    car & \textbf{99.8}/91.7 &  98.4/93.4 & \textbf{99.8}/\textbf{97.5} \\ 
-    bicycle & 93.0/87.4 & 93.0/91.4 & \textbf{98.8}/\textbf{97.5} \\
-    \hline
-    \end{tabular}
-  \end{center}
-  \caption{Average Precision(AP) and Average Viewpoint Accuracy(AVA) on 3DObject dataset.
-Though we do not need any training images and made templates in few minues, it performs on par with state of the art detectors yet it gives high quality 2D-3D matching.}
-  \label{tab:3dobject}
-\end{table}
 

### 2014-11-14 egpaper_final.tex

--- 2014-11-14 egpaper_final.tex
@@
 \end{center}
-\caption{Detection results on 3D-Object dataset \cite{Savarese07}. Original image (left) and detection result overlaid on top with a bounding box and corresponding confidence score(right)}
+\caption{Detection results on 3D-Object dataset \cite{Savarese07}, each of four images have (top left) original image, (top right) top detection rendering overlaid, (bottom right) false positives, (bottom left) true positives.
+Each with confidence score and colored bounding box}
   \label{fig:3dobject}

### 2014-11-14 egpaper_final.tex
3.2 first pass, numbers still needed

--- 2014-11-14 egpaper_final.tex
@@
 
-To whiten a signal $x$, we have to solve $\Sigma w = x - \mu$ which takes $O(n^3)$ time.
+To whiten a signal $x$, we have to solve $\Sigma w = x - \mu$.
 In \cite{Hariharan12}, the authors make use of the fact that covariance matrices are Hermitian and positive semidefinite to solve the system via the Cholesky decomposition, which is twice as fast as the LU decomposition.
-However, by considering the properties of the covariance matrix of the HOG template, we show that the conjugate gradient method can further speed up the whitening stage.
+These decompositions require $O(n^3)$ time, whereas the conjugate gradient method takes $O(n^2\kappa)$ time, where $\kappa$ is the condition number of the matrix.
+This makes conjugate gradient a faster option for matrices with small condition numbers relative to their size.
+
+Figure \ref{fig:spectral} shows the singular values of a covariance matrix for one HOG template after a small regularization constant is added to the diagonal.
+The condition number of of the matrix is \scream{x}, much smaller than the size of the matrix (7500).
+As a result, conjugate gradient converges in \scream{x ms}, two orders of magnitude faster than the system can be solved using the Cholesky factorization (\scream{5 s}).
 
@@
 
-Figure \ref{fig:spectral} shows the singular values of a template covariance matrix with a small regularization constant added to the diagonal.
-The singular values are clustered in small region and most of the energies are concentrated on the first \scream{x} singular values.
-Therefore, conjugate gradient will converge in $O(n^2\kappa)$ time, faster
-
-We also used iterative Conjugate Gradient to make use of low rank property of the covariance \cite{Gharbi12}.
+%We also used iterative Conjugate Gradient to make use of low rank property of the covariance \cite{Gharbi12}.
 After adding small regularization, the regularized covariance matrix has nice spectral property (Figure \ref{fig:spectral}).
@@
 WHO-Chol\cite{Hariharan12} &              &3811ms    &                           &   12.4 sec  \\
-WHO-GG                & 81.70/74.20  &104ms &     83.714/75.37              &   8.3 sec \\
+WHO-CG                & 81.70/74.20  &104ms &     83.714/75.37              &   8.3 sec \\
 WHO-CG-Z              & 54.42/49.71  &103ms & \textbf{92.80}/\textbf{81.44} &   8.7 sec  \\

### 2014-11-14 egpaper_final.tex
abstract

--- 2014-11-14 egpaper_final.tex
@@
 \begin{abstract}
-    Using 3D model to detect and register the model to RGB image has been a growing field of study.
+A large body of recent work on object detection has focused on exploiting 3D CAD model databases to improve detection performance.
+Many of these approaches work by aligning exact 3D models to images using templates generated from renderings of the 3D models at a finite set of discrete viewpoints.
+The training procedures for these approaches, however, are very expensive and require gigabytes of memory and storage, and the viewpoint discretization hampers pose estimation performance.
+
+We propose an efficient method for synthesizing templates from 3D models that runs on the fly -- that is, it quickly produces detectors for an arbitrary viewpoint of a 3D model without expensive dataset-dependent training or template storage.
+Given a 3D model and an arbitrary continuous detection viewpoint, our method synthesizes a discriminative template by extracting features from a rendered view of the object and decorrelating spatial dependences among the features.
+Our decorrelation procedure relies on a gradient-based algorithm that is more numerically stable than standard decomposition-based procedures, and we efficiently search for candidate detections by computing FFT-based template convolutions.
+Due to the speed of our template synthesis procedure, we are able to perform joint optimization on continuous scale, translation, rotation, and focal length.
+We provide an efficient GPU implementation of our algorithm, and we validate its performance on 3DObject dataset and PASCAL 2012 dataset.
+
+%     Using 3D model to detect and register the model to RGB image has been a growing field of study.
 Recently, Aubry \etal \cite{Aubry14} and J.
@@
 Also, the training based approach requires defining fixed viewpoints which limit themselves.
-  To overcome these difficulties, we propose an efficient and fast way to synthesize and validate templates using on the fly realistic rendering that can jointly optimize scale, translation, rotation and focal length continuously.
+%  To overcome these difficulties, we propose an efficient and fast way to synthesize and validate templates using on the fly realistic rendering that can jointly optimize scale, translation, rotation and focal length continuously.
 We render an object and extract features and decorrelate spatial dependencies within them on the fly to make a discriminative template.
@@
 
-  In contrast to other mid-level patch based 3D matching methods which requires extensive training and more than 10Gb of memory space and physical storage, ours require no training nor saving the templates thus enabling it to run on any personal computer.
+%   In contrast to other mid-level patch based 3D matching methods which requires extensive training and more than 10Gb of memory space and physical storage, ours require no training nor saving the templates thus enabling it to run on any personal computer.
 \end{abstract}
@@
 WHO templates are more discriminative than standard HOG templates because they only capture the gradients that differentiate the object from random images.
+\scream{chris added the following} Hariharan \etal.
+also interpreted the whitening as Linear Discriminant Analysis (LDA) where all classes have different means but have the same covariance.
+The whitening and LDA have the same formulation when we make a decision boundary $w = \Sigma^{-1}(\mu_+ - \mu_0)$ where $\mu_+$ is the features from a class (LDA) or a signal to whiten (whitening), $\mu_0$ is the negative class center (LDA) or a signal statistics (whitening) and $\Sigma$ is the covariance matrix of classes (LDA) or correlation within signal (whitening).
 
 \textcolor{red}{Should we mention how our method improves on this (ie by using CG)?}
-
 % Using HOG
@@
 When synthesizing detection templates from rendered images, a common problem is how to handle the background.
-Some methods \scream{which?} render the model over a natural image background, but this results in gradients in the background being incorporated into the discriminative template.
+If we render the model over a natural image background, gradients in the background will be incorporated into the discriminative template.
 Alternatively, we could leave the background textureless \scream{did Hariharan do this?} (see Fig.~\ref{fig:rendering}), but whitening the resulting HOG template produces in undesirable background artifacts.
@@
 
-Therefore, assuming WSS allows us to synthesize the covariance matrix for templates \emph{of any size} from the autocovariance matrix.
-This hugely reduces the memory required because to build the covariance matrix of a template of $w \times h$ HOG cells (with 31 elements per cell), we only need a $w \times h \times 31$ autocovariance matrix.
+Therefore, assuming WSS allows us to synthesize the covariance matrix for templates \emph{of any size} from the autocovariance.
+This hugely reduces the memory required because to build the covariance matrix of a template of $w \times h$ HOG cells (with 31 elements each), we only need a $w \times h \times 31$ autocovariance matrix.
 In comparison, the covariance matrix itself is $(w \times h \times 31) \times (w \times h \times 31)$.
@@
 To further simplify $\Gamma$, we assumed horizontal and vertical symmetry.
-In our implementation, we compute a $40 \times 40 \times 31$ autocovariance matrix, meaning we can synthesize covariance matrices for HOG grids as big as $40 \times 40$.
-In practice we limit the number of cells per template to 250.
+In our implementation, we compute a $40 \times 40 \times 31$ autocovariance matrix, meaning we can synthesize covariance matrices for HOG grids of as big as $40 \times 40$.
 
-We use the GPU to parallelize the lookup of the correct autocovariance cells during covariance matrix syntheses, which is \scream{x} times faster than using the CPU (Figure \ref{fig:covariancetime}).
+Synthesizing the covariance matrix is memory copy operations so we used GPU to speed up the process (Figure \ref{fig:covariancetime}).
 
@@
 To whiten a signal $x$, we have to solve $\Sigma w = x - \mu$ which takes $O(n^3)$ time.
-In \cite{Hariharan12}, the authors make use of the fact that covariance matrices are Hermitian and positive semidefinite to solve the system via the Cholesky decomposition, which is twice as fast as the LU decomposition.
-However, by considering the properties of the covariance matrix of the HOG template, we show that the conjugate gradient method can further speed up the whitening stage.
+In \cite{Hariharan12}, the authors make use of positive semidefinite and Hermitian properties of a covariance matrix to use Cholesky decomposition and Gaussian elimination which is twice as fast a the LU decomposition.
+However, if we make use of a spectral property of the covariance matrix, we can further speed up the whitening stage.
 
-%  If we use a high resolution template such as \ref{fig:rendering}
+  If we use a high resolution template such as \ref{fig:rendering}
 
@@
 
-%In our setting, we used high resolution template which has more than 250 HOG cells.
+In our setting, we used high resolution template which has more than 250 HOG cells.
 This result in $\Sigma \in \mathcal{R}^{7500 \times 7500}$.
@@
 
-Figure \ref{fig:spectral} shows the singular values of a template covariance matrix with a small regularization constant added to the diagonal.
-The singular values are clustered in small region and most of the energies are concentrated on the first \scream{x} singular values.
-Therefore, conjugate gradient will converge in $O(n^2\kappa)$ time, faster
-
 We also used iterative Conjugate Gradient to make use of low rank property of the covariance \cite{Gharbi12}.
-After adding small regularization, the regularized covariance matrix has nice spectral property (Figure \ref{fig:spectral}).
+After adding small regularization, the regularized covariance matrix has nice spectral property (Figure \ref{fig:spectral}.
 The singular values are clustered in small region and most of the energies are concentrated on the first (number) singular values.
@@
 \end{center}
-\caption{Detection results on 3D-Object dataset \cite{Savarese07}, each of four images have (top left) original image, (top right) top detection rendering overlaid, (bottom right) false positives, (bottom left) true positives.
-Each with confidence score and colored bounding box}
+\caption{Detection results on 3D-Object dataset \cite{Savarese07}. Original image (left) and detection result overlaid on top with a bounding box and corresponding confidence score(right)}
   \label{fig:3dobject}

### 2014-11-14 egpaper_final.tex

@@
 To estimate pose they use synthetic renderings of CAD models to learn discriminative mid-level patches.
-\cite{Aubry14} calibrates these patches on a small set of real images, while \cite{Lim14} presents a method for learning the relative discriminativeness of the patches.
+\cite{Aubry14} calibrates these patches on a small set of real images, while \cite{Lim14} present a method for learning the relative discriminativeness of the patches.
 
@@
 
-To whiten a signal $x$, we have to solve $\Sigma w = x - \mu$ which takes $O(n^3)$ time.
-In \cite{Hariharan12}, the authors make use of positive semidefinite and Hermitian properties of a covariance matrix to use Cholesky decomposition and Gaussian elimination which is twice as fast a the LU decomposition.
-However, if we make use of a spectral property of the covariance matrix, we can further speed up the whitening stage.
+To whiten a signal $x$, we have to solve $\Sigma w = x - \mu$.
+In \cite{Hariharan12}, the authors make use of the fact that covariance matrices are Hermitian and positive semidefinite to solve the system via the Cholesky decomposition, which is twice as fast as the LU decomposition.
+These decompositions require $O(n^3)$ time, whereas the conjugate gradient method takes $O(n^2\kappa)$ time, where $\kappa$ is the condition number of the matrix.
+This makes conjugate gradient a faster option for matrices with small condition numbers relative to their size.
 
-  If we use a high resolution template such as \ref{fig:rendering}
+Figure \ref{fig:spectral} shows the singular values of a covariance matrix for one HOG template after a small regularization constant is added to the diagonal.
+The condition number of of the matrix is \scream{x}, much smaller than the size of the matrix (7500).
+As a result, conjugate gradient converges in \scream{x ms}, two orders of magnitude faster than the system can be solved using the Cholesky factorization (\scream{5 s}).
+
+%  If we use a high resolution template such as \ref{fig:rendering}
 
@@
 
-We also used iterative Conjugate Gradient to make use of low rank property of the covariance \cite{Gharbi12}.
-After adding small regularization, the regularized covariance matrix has nice spectral property (Figure \ref{fig:spectral}.
+%We also used iterative Conjugate Gradient to make use of low rank property of the covariance \cite{Gharbi12}.
+After adding small regularization, the regularized covariance matrix has nice spectral property (Figure \ref{fig:spectral}).
 The singular values are clustered in small region and most of the energies are concentrated on the first (number) singular values.
@@
 % there are several advantages that was not possible such as \textbf{on-the-fly} template generation and making large number of templates  
-
 \begin{figure}[t]
@@
 
-Second, we show that our method can complement the detection bounding boxes coming out of standard object detectors.
-This process will enrich object detection bounding boxes with 2D-3D matching which gives continuous viewpoint estimation, a CAD model (rendering, depth) and fine-grained category.
-
-\subsection{2D-3D Matching as an Object Detector}
-
-We created ensemble of NZ-WHO templates using 9 CAD models and measured the Average Precision (AP) of object detection task and Mean Precision in Pose Estimation (MPPE) \cite{Lopez-Sastre11}.
-MPPE is the average of viewpoint accuracy.
 \subsection{Object Detection} 
@@
 \end{figure}
-
-% Instance-level 2D-3D matching (registration) is a difficult problem since we need a CAD model that looks similar to the object in the image.
-Especially, due to extreme intraclass variability of chair \cite{Aubry14} used a very large collection of CAD models to cover variety of chairs.
-Similarly, \cite{Lim14}
-\begin{table}[!htbp]
-  \begin{center}
-    \begin{tabular}{|c|c|c|c|}
-    \hline
-     AP/MPPE& Ours & ALM\cite{Xiang12} & VOCDPM\cite{Pepik12} \\
-    \hline\hline
-    car & \textbf{99.8}/91.7 &  98.4/93.4 & \textbf{99.8}/\textbf{97.5} \\ 
-    bicycle & 93.0/87.4 & 93.0/91.4 & \textbf{98.8}/\textbf{97.5} \\
-    \hline
-    \end{tabular}
-  \end{center}
-  \caption{Average Precision(AP) and Mean Precision in Pose Estimation (MPPE) on 3DObject dataset car category.
-Our method produces high quality 2D-3D matching yet performs on par with state-of-the art detectors.}
-  \label{tab:3dobject}
-\end{table}
 
@@
 
-We used detection bounding boxes and augment it using our method to give viewpoint estimation.
-We used detection bounding boxes from two different methods: VOC-DPM \cite{Pepik12} and R-CNN \cite{Girshick14}.
-VOC-DPM is a variation of DPM that can estimate viewpoint and is the state-of-the-art performance in viewpoint estimation \cite{Xiang14}.
-The result is on Table \ref{tab:pascal12} and precision recall curves for car using R-CNN + Ours are on Figure \ref{fig:car_cnn_ap}.
-
-We got significant improvement on viewpoint estimation by using our method on top of general purpose detectors.
-Note that our method estimates azimuth, elevation, in-plane rotation, focal length estimation, fine-grained categorization whereas V-DPM, VOC-DPM only estimate discrete viewpoints.
-
-Example outputs are on Figure \ref{fig:pascal12cnn}.
-
-\begin{figure*}[h]
-\setlength\tabcolsep{1pt}
-\centering
-\begin{tabular}{|c|c|c|c|c|}
-   \hline
-  \includegraphics[width=0.24\textwidth]{car_cnn/1a.png} &   
-  \includegraphics[width=0.24\textwidth]{car_cnn/1b.png} &   
-  \includegraphics[width=0.24\textwidth]{car_cnn/1c.png} &   
-  \includegraphics[width=0.24\textwidth]{car_cnn/1d.png}  \\  
-   \hline
-  \includegraphics[width=0.24\textwidth]{car_cnn/2a.png} &   
-  \includegraphics[width=0.24\textwidth]{car_cnn/2b.png} &   
-  \includegraphics[width=0.24\textwidth]{car_cnn/2c.png} &   
-  \includegraphics[width=0.24\textwidth]{car_cnn/2e.png}  \\  
-   \hline
-  \includegraphics[width=0.24\textwidth]{car_cnn/4a.png} &   
-  \includegraphics[width=0.24\textwidth]{car_cnn/4b.png} &   
-  \includegraphics[width=0.24\textwidth]{car_cnn/4c.png} &   
-  \includegraphics[width=0.24\textwidth]{car_cnn/4d.png}  \\  
-%    \hline
-%   \includegraphics[width=0.24\textwidth]{car_cnn/10a.png} &   
-%   \includegraphics[width=0.24\textwidth]{car_cnn/10b.png} &   
-%   \includegraphics[width=0.24\textwidth]{car_cnn/10c.png} &   
-%   \includegraphics[width=0.24\textwidth]{car_cnn/10d.png}  \\  
-%   \hline 
-%   \includegraphics[width=0.24\textwidth]{bicycle_cnn/3a.png} &   
-%   \includegraphics[width=0.24\textwidth]{bicycle_cnn/3b.png} &   
-%   \includegraphics[width=0.24\textwidth]{bicycle_cnn/3c.png} &   
-%   \includegraphics[width=0.24\textwidth]{bicycle_cnn/3d.png}  \\
-  \hline
-  \includegraphics[width=0.24\textwidth]{bicycle_cnn/7a.png} &   
-  \includegraphics[width=0.24\textwidth]{bicycle_cnn/7b.png} &   
-  &\\
-  \hline
-  \includegraphics[width=0.24\textwidth]{bicycle_cnn/4a.png} &   
-  \includegraphics[width=0.24\textwidth]{bicycle_cnn/4b.png} &   
-  \includegraphics[width=0.24\textwidth]{bicycle_cnn/4c.png} &   
-  \includegraphics[width=0.24\textwidth]{bicycle_cnn/4d.png}  \\
-  \hline
-  CNN Proposals & \multicolumn{3}{|c|}{Our matching results on proposal bounding boxes} \\
-  \hline
-\end{tabular}
-\caption{Example enriched bounding boxes.
-Given R-CNN\cite{Girshick14} detection bounding boxes, our method predicted 2D-3D matching reasonably.
-On the first column, R-CNN detection bounding boxes overlaid.
-From the second to the last columns, output of our method given a R-CNN box.
-Blue boxes are R-CNN output and purple boxes are the tightest bounding box enclosing predicted CAD model}
-  \label{fig:pascal12cnn}
-\end{figure*}
-
 \begin{table*}[!htbp]
@@
 
-\begin{figure}[h]
-\setlength\tabcolsep{1pt}
-\centering
-\begin{tabular}{cc}
-  \hline
-  \includegraphics[width=0.49\linewidth]{car_cnn4_crop.png} &   
-  \includegraphics[width=0.49\linewidth]{car_cnn8_crop.png} \\   
-  \includegraphics[width=0.49\linewidth]{car_cnn16_crop.png} &   
-  \includegraphics[width=0.49\linewidth]{car_cnn24_crop.png} \\   
-  \hline
-\end{tabular}
-\caption{Average Precision (AP) and Average Viewpoint Precision (AVP) and viewpoint confusion table on PASCAL 12 car validation set using R-CNN + Ours.
-From the top left, 4 views, 8 views, 16 views and 24 views.
-Since our method only augment the object detection, the AP remains the same for all cases.
-As we increase the viewpoint estimation, the AVP decreases.
-Note that since we estimate null viewpoint if our method fails to find match, there are more 0 viewpoint predictions (top row of confusion matrices) }
-  \label{fig:car_cnn_ap}
-\end{figure}
-
 \subsection{Stability of Our Method for Irregular Bounding Boxes}
@@
 Although the input bounding boxes are irregular and truncate objects, our method reliably generated a reasonable prediction of pose, translation, scale and CAD model.
-
-% R-CNN \cite{Girshick14} gives very irregular bounding boxes since the proposals bounding boxes come from various methods.
 

### 2014-11-14 egpaper_final.tex
3.4 (FFT part) collapsed into 3.2

--- 2014-11-14 egpaper_final.tex
@@
 
-\subsection{Fast Whitening and Non-Zero Selection}
+\subsection{Fast Whitening and Convolution}
 \label{sec:fast_whitening}
@@
 As a result, conjugate gradient converges in \scream{x ms}, two orders of magnitude faster than the system can be solved using the Cholesky factorization (\scream{5 s}).
+
+The final challenge in on-the-fly template evaluation is performing the convolution between the template and the target image.
+Standard convolution would be prohibitively slow for the high resolution templates we're using, so we implemented the convolution via Fast Fourier Transform on the GPU.
+This allows template evaluation to run in \scream{x ms}, compared to \scream{x ms} for the naive CPU implementation.
 
@@
 
+\begin{comment}
 \subsection{High Resolution Templates and FFT based Convolution}
@@
 [Figure for convolution time for different template resolution, CPU, GPU, naive convolution]
-
+\end{comment}
 %------------------------------------------------------------------------

### 2014-11-14 egpaper_final.tex
3.4 (FFT part) collapsed into 3.2
minor change

--- 2014-11-14 egpaper_final.tex
@@
 This speed up means we can generate templates on the fly, allowing our approach to evaluate arbitrary viewpoint hypotheses.
+\scream{chris:We propose Non-Zero Whitened Histograms of Orientations (NZ-WHO), an improvement over WHO which is both more discriminative than WHO and can be computed many orders of magnitude faster than WHO (70ms as opposed to to several seconds for WHO).
+This speedup allows us to generate NZ-WHO templates on the fly, allowing us to quickly evaluate arbitrary viewpoint hypotheses.}
 
@@
 HOG\cite{Dalal05}     & 72.3 / 65.0           &  31ms  & 60.4 / 50.2                 & 8.7 sec \\ 
-WHO\cite{Hariharan12} & 82.1 / 85.4  &  3811ms&                             &   12.4 sec  \\
+WHO\cite{Hariharan12} & 82.1 / 85.4           &  3811ms& 84.4 / 83.0                 & 12.4 sec  \\
 WHO-CG                & 81.7 / \textbf{84.9}  &  104ms & 83.7 / 87.3                 & 8.3 sec \\

### 2014-11-14 egpaper_final.tex

@@
 %   In contrast to other mid-level patch based 3D matching methods which requires extensive training and more than 10Gb of memory space and physical storage, ours require no training nor saving the templates thus enabling it to run on any personal computer.
+%   To overcome these difficulties, we propose an efficient and fast way to synthesize and validate templates using on the fly realistic rendering that can jointly optimize scale, translation, rotation and focal length continuously.
+We render an object and extract features and decorrelate spatial dependencies within them on the fly to make a discriminative template.
+To speed up the decorrelation procedure, we adopt a gradient based algorithm which is numerically more stable than decomposition procedure.
+Finally, we efficiently search for candidate match by computing convolution using FFT and jointly optimize to match the object accurately.
+To speed up further, we propose an efficient GPU implementation and tested on PASCAL images.
+
 \end{abstract}
@@
 \textcolor{red}{Should we mention how our method improves on this (ie by using CG)?}
+
 % Using HOG
@@
 \begin{table*}[!htbp]
+    \footnotesize
     \begin{center}
@@
 \hline
-Methods (AP/MPPE) & before calibration  & time & after Calibration \cite{Aubry14} & time \\
+Methods (AP/MPPE) & before calibration  & time & after calibration \cite{Aubry14} & time \\
 \hline\hline
@@
 % Estimating viewpoint continuously to fine tune a initial matching
+The NZ-WHO template matching method we have presented makes template generation and evaluation computationally inexpensive. 
 Since creating a template and validating the template become computationally inexpensive, making a proposal and validating the proposal to fine tune a 2D-3D matching became affordable.
@@
 
-\subsection{Object Detection} 
-Instance-level 2D-3D matching (registration) is a difficult problem since we need a CAD model that looks similar to the object in the image.
+Second, we show that our method can complement the detection bounding boxes coming out of standard object detectors.
+This process will enrich object detection bounding boxes with 2D-3D matching which gives continuous viewpoint estimation, a CAD model (rendering, depth) and fine-grained category.
+
+\subsection{2D-3D Matching as an Object Detector}
+
+We created ensemble of NZ-WHO templates using 9 CAD models and measured the Average Precision (AP) of object detection task and Mean Precision in Pose Estimation (MPPE) \cite{Lopez-Sastre11}.
+MPPE is the average of viewpoint accuracy.
+
+% Instance-level 2D-3D matching (registration) is a difficult problem since we need a CAD model that looks similar to the object in the image.
 Especially, due to extreme intraclass variability of chair \cite{Aubry14} used a very large collection of CAD models to cover variety of chairs.
 Similarly, \cite{Lim14}
-Our ensemble of NZ-WHO templates is generated from rendering image with no calibration but shows strong performance on object detection.
+
+Our ensemble of NZ-WHO templates is generated from rendering images within few minutes but shows reasonable performance on object detection task.
 The baseline method are Aspect Layout Model (ALM) \cite{Xiang12} and VOC-DPM \cite{Pepik12}.
@@
 The detection result is on Table \ref{tab:3dobject} and example output from our method is on Figure \ref{fig:3dobject}.
+
+\begin{table}[!htbp]
+    \footnotesize
+  \begin{center}
+    \begin{tabular}{|c|c|c|c|}
+    \hline
+     AP/MPPE& Ours & ALM\cite{Xiang12} & VOC-DPM\cite{Pepik12} \\
+    \hline\hline
+    car & \textbf{99.8}/91.7 &  98.4/93.4 & \textbf{99.8}/\textbf{97.5} \\ 
+    bicycle & 93.0/87.4 & 93.0/91.4 & \textbf{98.8}/\textbf{97.5} \\
+    \hline
+    \end{tabular}
+  \end{center}
+  \caption{Average Precision(AP) and Mean Precision in Pose Estimation (MPPE) on 3DObject dataset car category.
+Our method produces high quality 2D-3D matching yet performs on par with state-of-the art detectors.}
+  \label{tab:3dobject}
+\end{table}
 
@@
 
+We used detection bounding boxes and augment it using our method to give viewpoint estimation.
+We used detection bounding boxes from two different methods: VOC-DPM \cite{Pepik12} and R-CNN \cite{Girshick14}.
+VOC-DPM is a variation of DPM that can estimate viewpoint and is the state-of-the-art performance in viewpoint estimation \cite{Xiang14}.
+The result is on Table \ref{tab:pascal12} and precision recall curves for car using R-CNN + Ours are on Figure \ref{fig:car_cnn_ap}.
+
+We got significant improvement on viewpoint estimation by using our method on top of general purpose detectors.
+Note that our method estimates azimuth, elevation, in-plane rotation, focal length estimation, fine-grained categorization whereas V-DPM, VOC-DPM only estimate discrete viewpoints.
+
+Example outputs are on Figure \ref{fig:pascal12cnn}.
+
+\begin{figure*}[h]
+\setlength\tabcolsep{1pt}
+\centering
+\begin{tabular}{|c|c|c|c|c|}
+   \hline
+  \includegraphics[width=0.24\textwidth]{car_cnn/1a.png} &   
+  \includegraphics[width=0.24\textwidth]{car_cnn/1b.png} &   
+  \includegraphics[width=0.24\textwidth]{car_cnn/1c.png} &   
+  \includegraphics[width=0.24\textwidth]{car_cnn/1d.png}  \\  
+   \hline
+  \includegraphics[width=0.24\textwidth]{car_cnn/2a.png} &   
+  \includegraphics[width=0.24\textwidth]{car_cnn/2b.png} &   
+  \includegraphics[width=0.24\textwidth]{car_cnn/2c.png} &   
+  \includegraphics[width=0.24\textwidth]{car_cnn/2e.png}  \\  
+   \hline
+  \includegraphics[width=0.24\textwidth]{car_cnn/4a.png} &   
+  \includegraphics[width=0.24\textwidth]{car_cnn/4b.png} &   
+  \includegraphics[width=0.24\textwidth]{car_cnn/4c.png} &   
+  \includegraphics[width=0.24\textwidth]{car_cnn/4d.png}  \\  
+%    \hline
+%   \includegraphics[width=0.24\textwidth]{car_cnn/10a.png} &   
+%   \includegraphics[width=0.24\textwidth]{car_cnn/10b.png} &   
+%   \includegraphics[width=0.24\textwidth]{car_cnn/10c.png} &   
+%   \includegraphics[width=0.24\textwidth]{car_cnn/10d.png}  \\  
+%   \hline 
+%   \includegraphics[width=0.24\textwidth]{bicycle_cnn/3a.png} &   
+%   \includegraphics[width=0.24\textwidth]{bicycle_cnn/3b.png} &   
+%   \includegraphics[width=0.24\textwidth]{bicycle_cnn/3c.png} &   
+%   \includegraphics[width=0.24\textwidth]{bicycle_cnn/3d.png}  \\
+  \hline
+  \includegraphics[width=0.24\textwidth]{bicycle_cnn/7a.png} &   
+  \includegraphics[width=0.24\textwidth]{bicycle_cnn/7b.png} &   
+  &\\
+  \hline
+  \includegraphics[width=0.24\textwidth]{bicycle_cnn/4a.png} &   
+  \includegraphics[width=0.24\textwidth]{bicycle_cnn/4b.png} &   
+  \includegraphics[width=0.24\textwidth]{bicycle_cnn/4c.png} &   
+  \includegraphics[width=0.24\textwidth]{bicycle_cnn/4d.png}  \\
+  \hline
+  CNN Proposals & \multicolumn{3}{|c|}{Our matching results on proposal bounding boxes} \\
+  \hline
+\end{tabular}
+\caption{Example enriched bounding boxes.
+Given R-CNN\cite{Girshick14} detection bounding boxes, our method predicted 2D-3D matching reasonably.
+On the first column, R-CNN detection bounding boxes overlaid.
+From the second to the last columns, output of our method given a R-CNN box.
+Blue boxes are R-CNN output and purple boxes are the tightest bounding box enclosing predicted CAD model}
+  \label{fig:pascal12cnn}
+\end{figure*}
 \begin{table*}[!htbp]
@@
 \end{table*}
+
+\begin{figure}[h]
+\setlength\tabcolsep{1pt}
+\centering
+\begin{tabular}{cc}
+  \hline
+  \includegraphics[width=0.49\linewidth]{car_cnn4_crop.png} &   
+  \includegraphics[width=0.49\linewidth]{car_cnn8_crop.png} \\   
+  \includegraphics[width=0.49\linewidth]{car_cnn16_crop.png} &   
+  \includegraphics[width=0.49\linewidth]{car_cnn24_crop.png} \\   
+  \hline
+\end{tabular}
+\caption{Average Precision (AP) and Average Viewpoint Precision (AVP) and viewpoint confusion table on PASCAL 12 car validation set using R-CNN + Ours.
+From the top left, 4 views, 8 views, 16 views and 24 views.
+Since our method only augment the object detection, the AP remains the same for all cases.
+As we increase the viewpoint estimation, the AVP decreases.
+Note that since we estimate null viewpoint if our method fails to find match, there are more 0 viewpoint predictions (top row of confusion matrices) }
+  \label{fig:car_cnn_ap}
+\end{figure}
 

### 2014-11-14 egpaper_final.tex
excised exps into tex file

--- 2014-11-14 egpaper_final.tex
@@
 \section{Experiments}
-
-In this section, we validate our proposed NZ-WHO templates in two different ways.
-First, we make a set of NZ-WHO templates for a set of CAD models from various viewpoints.
-Then we run the bank of NZ-WHO templates as ensembles of weak detectors and show that the rendering image can be We want to see how robust the NZ-WHO to real images a
-
-\subsection{Object Detection} 
-Instance-level 2D-3D matching (registration) is a difficult problem since we need a CAD model that looks similar to the object in the image.
-Especially, due to extreme intraclass variability of chair \cite{Aubry14} used a very large collection of CAD models to cover variety of chairs.
-Similarly, \cite{Lim14}
-Our ensemble of NZ-WHO templates is generated from rendering image with no calibration but shows strong performance on object detection.
-The baseline method are Aspect Layout Model (ALM) \cite{Xiang12} and VOC-DPM \cite{Pepik12}.
-Note that the baseline methods require complex 3D modeling and viewpoint annotated natural images.
-
-The detection result is on Table \ref{tab:3dobject} and example output from our method is on Figure \ref{fig:3dobject}.
-
-\begin{figure}[h]
-    \begin{center}
-    \setlength\tabcolsep{0pt}
-\begin{tabular}{cc}
-  \includegraphics[width=0.45\linewidth]{car_3dobject/7.png} &   
-  \includegraphics[width=0.45\linewidth]{car_3dobject/8.png}\\ [-15pt]
-%   (a) & (b) \\[0pt]
-  \includegraphics[width=0.45\linewidth]{car_3dobject/11.png} &   
-  \includegraphics[width=0.45\linewidth]{car_3dobject/12.png}\\ [-5pt]
-%  (c) & (d) \\[0pt]
-\end{tabular}
-\end{center}
-\caption{Detection results on 3D-Object dataset \cite{Savarese07}. Original image (left) and detection result overlaid on top with a bounding box and corresponding confidence score(right)}
-  \label{fig:3dobject}
-\end{figure}
-
-% Also, we evaluated our method on PASCAL 2007 dataset.
-% 
-% \begin{table}[!htbp]
-%   \begin{center}
-%   \begin{tabular}{|c|c|c|c|c|}
-%     \hline
-%      AP &    Ours &    ELDA \cite{Hariharan12} & ESVM \cite{Malisiewicz11} & VOCDPM \cite{Pepik12} \\
-%     \hline\hline
-%     car      & 27.          &  38.4  & 40.1    &65.7  \\ 
-%     bicycle  & 43.74 & 41      &  40.7   & 61.3   \\
-%     \hline
-%     \end{tabular}
-%   \end{center}
-%   \caption{Average Precision(AP) on PASCAL 2007 dataset.
-Though we do not need any training images and made templates in few minues, it performs on par with state of the art detector yet it gives high quality 2D-3D matching.}
-%   \label{tab:pascal07}
-% \end{table}
-
-\subsection{Fine-Tuning and Viewpoint Estimation}
-
-High performance object detectors usually generalizes very well.
-It can handle various intraclass variability, viewpoint change and occlusion.
-However due to this high generalization, sometimes it is very difficult to get accurate pose, category or 2D-3D matching.
-Our method, specialized in giving such accurate information, can be applied on any generic object detectors to give high quality metadata.
-
-To show such ability, we evaluated our method on PASCAL 3D dataset \cite{Xiang14}.
-The dataset augments PASCAL 2012 images with high quality viewpoint annotations thus is ideal to measure pose estimation.
-The dataset proposes new metric called Average Viewpoint Precision (AVP) where it measures the area under viewpoint precision and detection recall curve.
-The viewpoints is measured by azimuth similarity.
-If the distance between predicted azimuth and ground truth azimuth is below a certain threshold, the viewpoint is correct.
-Note that the baseline methods (V-DPM, VOC-DPM) reported on the PASCAL 3D dataset are variants of DPM where each component of DPM account for various azimuths.
-Thus V-DPM and VOC-DPM provide discrete azimuth only whereas our method provides 3D viewpoint (yaw, pitch, roll), CAD instance (model index, rendering, depth) and focal length.
-
-\begin{table*}[!htbp]
-    \footnotesize
-  \begin{center}
-\begin{tabular}{|c|c|c|c|c|c|c|}
-\hline
-AP/AVP              & V-DPM \cite{Xiang14} & VOC-DPM \cite{Pepik12}  & \cite{Pepik12} + Ours (discrete) & \cite{Pepik12} + Ours (full) & R-CNN + Ours (discrete) & R-CNN + Ours (full)\\
-\hline\hline
-car-4v              & 37.2 / 20.2         & 45.6 / 36.9             & 47.6 / 42.7       & 47.6 / \textbf{42.7}        & 49.6 / 41.5         & 49.6 / 41.5\\ \hline
-car-8v              & 37.3 / 23.5         & 47.6 / 36.6             & 47.6 / \textbf{39.8}       & 47.6 / 39.5        & 49.6 / 38.0         & 49.6 / 39.0\\ \hline
-car-16v             & 36.6 / 18.1         & 46.0 / 29.6             & 47.6 / 32.7       & 47.6 / 33.0        & 49.6 / 34.0         & 49.6 / \textbf{34.3}\\ \hline
-car-24v             & 36.3 / 13.7         & 42.1 / 24.6             & 47.6 / 27.4       & 47.6 / 27.4        & 49.6 / 27.0         & 49.6 / \textbf{27.6}\\ \hline
-\hline
-bicycle-4v          & 45.2 / 41.7         & 46.9 / 43.9             & 48.1 / 47.6       & 48.1 / 46.6        & 61.7 / 56.5         & 61.7 / \textbf{56.7}\\ \hline
-bicycle-8v          & 47.3 / 36.7         & 48.1 / 40.3             & 48.1 / 40.6       & 48.1 / 40.6        & 61.7 / 48.9         & 61.7 / \textbf{49.2}\\ \hline
-bicycle-16v         & 46.5 / 18.4         & 45.6 / 22.9             & 48.1 / 26.2       & 40.1 / 27.3        & 61.7 / 34.7         & 61.7 / \textbf{35.8}\\ \hline
-bicycle-24v         & 44.4 / 14.3         & 45.9 / 16.7             & 48.1 / 21.5       & 40.1 / 20.9        & 61.7 / \textbf{27.0}         & 61.7 / 23.9\\ \hline
-\end{tabular}
-\end{center}
-\caption{Average Precision(AP) and Average Viewpoint Precision(AVP) on PASCAL 3D dataset\cite{Xiang14}.
-For combined method (* + Ours), we use bounding boxes from * and augment viewpoint using our method.
-R-CNN and run our method to produce 2D-3D matching.
-If our method fails to give viewpoint, it predicts the viewpoint to be 0.
-Note that our method gives high quality metadata such as continuous 3D viewpoint, CAD model (rendering depth) and fine-grained category, whereas base-line methods gives 1D discrete azimuths.
-Our R-CNN was not an optimized version so the detection AP is lower than the state-of-the-art R-CNN performance}
-\label{tab:pascal12}
-\end{table*}
-
-\subsection{Stability of Our Method for Irregular Bounding Boxes}
-
-% Generic object detectors give overlapping detection bounding boxes of the same object which can be handled by non maximal suppression. For these overlapping detections,
-
-R-CNN detection bounding boxes are irregular in shape since they come from other region proposal methods and sometimes they truncate objects.
-To handle such irregular shape and truncation, we added small context around the bounding boxes and run our method.
-
-We assumed that object can be arbitrarily truncated by the bounding box and search all plausible scales and translations.
-This can be efficiently computed using FFT-based convolution (refer Section.
-\ref{sec:fft}).
-We put examples of such conditions in Figure \ref{fig:stability}.
-Although the input bounding boxes are irregular and truncate objects, our method reliably generated a reasonable prediction of pose, translation, scale and CAD model.
-
-\begin{figure}[h]
-\setlength\tabcolsep{5pt}
-\begin{tabular}{cc}
-  \includegraphics[width=0.45\linewidth]{car_pascal/1.png} &   
-  \includegraphics[width=0.45\linewidth]{car_pascal/2.png} \\   
-  \includegraphics[width=0.45\linewidth]{car_pascal/3.png} &   
-  \includegraphics[width=0.45\linewidth]{car_pascal/4.png} \\   
-\end{tabular}
-\caption{Stability of our method for overlapping R-CNN detection \cite{Girshick14}.
-Blue box is the R-CNN detection that is feed into the system as initial detection.
-Purple box and overlaid rendering is the final output of the system.
-Note that for various overlapping bounding boxes, our system accurately estimated the reasonable result}
-  \label{fig:stability}
-\end{figure}
-
-% For qualitative examples, we put hand-picked results from our method Fig. \ref{fig:car} and Fig. \ref{fig:bicycle}.
-
-% \begin{figure*}[h]
-% \setlength\tabcolsep{5pt}
-% \begin{tabular}{|c|c|c|}
-%     \hline
-%   \includegraphics[width=0.325\textwidth]{car/PASCAL_car_val_init_0_Car_each_27_lim_250_lam_0_150_a_24_e_3_y_1_f_1_scale_2_00_sbin_6_level_15_skp_n_server_101_img_39.jpg} &   
-%   \includegraphics[width=0.325\textwidth]{car/PASCAL_car_val_init_0_Car_each_27_lim_250_lam_0_150_a_24_e_3_y_1_f_1_scale_2_00_sbin_6_level_15_skp_n_server_101_img_78.jpg} & 
-%   \includegraphics[width=0.325\textwidth]{car/PASCAL_car_val_init_0_Car_each_27_lim_250_lam_0_150_a_24_e_3_y_1_f_1_scale_2_00_sbin_6_level_15_skp_n_server_101_img_85.jpg} \\[-15pt]
-% (a) & (b) & (c) \\[0pt]
-% \hline
-%   \includegraphics[width=0.325\textwidth]{car/PASCAL_car_val_init_0_Car_each_27_lim_250_lam_0_150_a_24_e_3_y_1_f_1_scale_2_00_sbin_6_level_15_skp_n_server_101_img_338.jpg} &   
-%   \includegraphics[width=0.325\textwidth]{car/PASCAL_car_val_init_0_Car_each_27_lim_250_lam_0_150_a_24_e_3_y_1_f_1_scale_2_00_sbin_6_level_15_skp_n_server_101_img_360.jpg} & 
-%   \includegraphics[width=0.325\textwidth]{car/PASCAL_car_val_init_0_Car_each_27_lim_250_lam_0_150_a_24_e_3_y_1_f_1_scale_2_00_sbin_6_level_15_skp_n_server_101_img_414.jpg} \\[-15pt]
-% (d) & (e) & (f) \\[0pt]
-% \hline
-%   \includegraphics[width=0.325\textwidth]{car/PASCAL_car_val_init_0_Car_each_27_lim_250_lam_0_150_a_24_e_3_y_1_f_1_scale_2_00_sbin_6_level_15_skp_n_server_101_img_418.jpg} &   
-%   \includegraphics[width=0.325\textwidth]{car/PASCAL_car_val_init_0_Car_each_27_lim_250_lam_0_150_a_24_e_3_y_1_f_1_scale_2_00_sbin_6_level_15_skp_n_server_101_img_1049.jpg} & 
-%   \includegraphics[width=0.325\textwidth]{car/PASCAL_car_val_init_0_Car_each_27_lim_250_lam_0_150_a_24_e_3_y_1_f_1_scale_2_00_sbin_6_level_15_skp_n_server_101_img_1242.jpg} \\[-15pt]
-% (g) & (h) & (i) \\[0pt]
-% \hline
-%   \includegraphics[width=0.325\textwidth]{car/PASCAL_car_val_init_0_Car_each_27_lim_250_lam_0_150_a_24_e_3_y_1_f_1_scale_2_00_sbin_6_level_15_skp_n_server_101_img_1244.jpg} &   
-%   \includegraphics[width=0.325\textwidth]{car/PASCAL_car_val_init_0_Car_each_27_lim_250_lam_0_150_a_24_e_3_y_1_f_1_scale_2_00_sbin_6_level_15_skp_n_server_101_img_1261.jpg} & 
-%   \includegraphics[width=0.325\textwidth]{car/PASCAL_car_val_init_0_Car_each_27_lim_250_lam_0_150_a_24_e_3_y_1_f_1_scale_2_00_sbin_6_level_15_skp_n_server_101_img_1452.jpg} \\[-15pt]
-% (j) & (k) & (l) \\[0pt]
-% \hline
-%   \includegraphics[width=0.325\textwidth]{car/PASCAL_car_val_init_0_Car_each_27_lim_250_lam_0_150_a_24_e_3_y_1_f_1_scale_2_00_sbin_6_level_15_skp_n_server_101_img_1467.jpg} &   
-%   \includegraphics[width=0.325\textwidth]{car/PASCAL_car_val_init_0_Car_each_27_lim_250_lam_0_150_a_24_e_3_y_1_f_1_scale_2_00_sbin_6_level_15_skp_n_server_101_img_1553.jpg} & 
-%   \includegraphics[width=0.325\textwidth]{car/PASCAL_car_val_init_0_Car_each_27_lim_250_lam_0_150_a_24_e_3_y_1_f_1_scale_2_00_sbin_6_level_15_skp_n_server_101_img_1597.jpg} \\[-15pt]
-% (m) & (n) & (o) \\[3pt]
-% \hline
-% \end{tabular}
-%   \caption{Selected detections from PASCAL 07 Car categories.
-From the left, (1) original image, (2) overlaid true positive CAD models, (3) overlaid true positive CAD models with bounding boxes, (4) overlaid false positive CAD models with bounding boxes.
-Bounding box is colored from red (high confidence) to blue (low confidence) }
-%   \label{fig:car}
-% \end{figure*}
-% \begin{figure*}[h]
-% \setlength\tabcolsep{5pt}
-% \begin{tabular}{|c|c|c|}
-%     \hline
-%   \includegraphics[width=0.325\textwidth]{bicycle/PASCAL_bicycle_val_init_0_Bicycle_each_4_lim_250_lam_0_150_a_48_e_4_y_5_f_1_scale_2_00_sbin_6_level_15_skp_n_server_102_img_459.jpg} &   
-%   \includegraphics[width=0.325\textwidth]{bicycle/PASCAL_bicycle_val_init_0_Bicycle_each_4_lim_250_lam_0_150_a_48_e_4_y_5_f_1_scale_2_00_sbin_6_level_15_skp_n_server_102_img_1300.jpg} &   
-%   \includegraphics[width=0.325\textwidth]{bicycle/PASCAL_bicycle_val_init_0_Bicycle_each_4_lim_250_lam_0_150_a_48_e_4_y_5_f_1_scale_2_00_sbin_6_level_15_skp_n_server_102_img_539.jpg} \\[-15pt]
-% (a) & (b) & (c) \\[0pt]
-% \hline
-%   \includegraphics[width=0.325\textwidth]{bicycle/PASCAL_bicycle_val_init_0_Bicycle_each_4_lim_250_lam_0_150_a_48_e_4_y_5_f_1_scale_2_00_sbin_6_level_15_skp_n_server_102_img_35.jpg} &   
-%   \includegraphics[width=0.325\textwidth]{bicycle/PASCAL_bicycle_val_init_0_Bicycle_each_4_lim_250_lam_0_150_a_48_e_4_y_5_f_1_scale_2_00_sbin_6_level_15_skp_n_server_102_img_83.jpg} &   
-%   \includegraphics[width=0.325\textwidth]{bicycle/PASCAL_bicycle_val_init_0_Bicycle_each_4_lim_250_lam_0_150_a_48_e_4_y_5_f_1_scale_2_00_sbin_6_level_15_skp_n_server_102_img_131.jpg} \\[-15pt]
-% (d) & (e) & (f) \\[0pt]
-% \hline
-%   \includegraphics[width=0.325\textwidth]{bicycle/PASCAL_bicycle_val_init_0_Bicycle_each_4_lim_250_lam_0_150_a_48_e_4_y_5_f_1_scale_2_00_sbin_6_level_15_skp_n_server_102_img_175.jpg} &   
-%   \includegraphics[width=0.325\textwidth]{bicycle/PASCAL_bicycle_val_init_0_Bicycle_each_4_lim_250_lam_0_150_a_48_e_4_y_5_f_1_scale_2_00_sbin_6_level_15_skp_n_server_102_img_210.jpg} &   
-%   \includegraphics[width=0.325\textwidth]{bicycle/PASCAL_bicycle_val_init_0_Bicycle_each_4_lim_250_lam_0_150_a_48_e_4_y_5_f_1_scale_2_00_sbin_6_level_15_skp_n_server_102_img_233.jpg} \\[-15pt]
-% (g) & (h) & (i) \\[0pt]
-% \hline
-%   \includegraphics[width=0.325\textwidth]{bicycle/PASCAL_bicycle_val_init_0_Bicycle_each_4_lim_250_lam_0_150_a_48_e_4_y_5_f_1_scale_2_00_sbin_6_level_15_skp_n_server_102_img_322.jpg} &   
-%   \includegraphics[width=0.325\textwidth]{bicycle/PASCAL_bicycle_val_init_0_Bicycle_each_4_lim_250_lam_0_150_a_48_e_4_y_5_f_1_scale_2_00_sbin_6_level_15_skp_n_server_102_img_348.jpg} &   
-%   \includegraphics[width=0.325\textwidth]{bicycle/PASCAL_bicycle_val_init_0_Bicycle_each_4_lim_250_lam_0_150_a_48_e_4_y_5_f_1_scale_2_00_sbin_6_level_15_skp_n_server_102_img_375.jpg} \\[-15pt]
-% (j) & (k) & (l) \\[0pt]
-% \hline
-%   \includegraphics[width=0.325\textwidth]{bicycle/PASCAL_bicycle_val_init_0_Bicycle_each_4_lim_250_lam_0_150_a_48_e_4_y_5_f_1_scale_2_00_sbin_6_level_15_skp_n_server_102_img_400.jpg} &   
-%   \includegraphics[width=0.325\textwidth]{bicycle/PASCAL_bicycle_val_init_0_Bicycle_each_4_lim_250_lam_0_150_a_48_e_4_y_5_f_1_scale_2_00_sbin_6_level_15_skp_n_server_102_img_434.jpg} &   
-%   \includegraphics[width=0.325\textwidth]{bicycle/PASCAL_bicycle_val_init_0_Bicycle_each_4_lim_250_lam_0_150_a_48_e_4_y_5_f_1_scale_2_00_sbin_6_level_15_skp_n_server_102_img_459.jpg} \\[-15pt]
-% (m) & (n) & (o) \\[3pt]
-% \hline
-% \end{tabular}
-%   \caption{Selected detections from PASCAL 12 Bike categories.
-From the left, (1) original image, (2) overlaid true positive CAD models, (3) overlaid true positive CAD models with bounding boxes, (4) overlaid false positive CAD models with bounding boxes.
-Bounding box is colored from red (high confidence) to blue (low confidence) }
-%   \label{fig:bicycle}
-% \end{figure*}
-
-% \section{Object Detection with various Training Data}
-% \section{Image Query}
+\label{sec:experiments}
+\input{experiments}
 

### 2014-11-14 egpaper_final.tex
minor changes
breaking lines

--- 2014-11-14 egpaper_final.tex
@@
 \begin{abstract}
-A large body of recent work on object detection has focused on exploiting 3D CAD model databases to improve detection performance.
-Many of these approaches work by aligning exact 3D models to images using templates generated from renderings of the 3D models at a finite set of discrete viewpoints.
-The training procedures for these approaches, however, are very expensive and require gigabytes of memory and storage, and the viewpoint discretization hampers pose estimation performance.
+A large body of recent work on object detection has focused on exploiting 3D CAD
+model databases to improve detection performance. Many of these approaches work
+by aligning exact 3D models to images using templates generated from renderings
+of the 3D models at a finite set of discrete viewpoints. The training procedures
+for these approaches, however, are very expensive and require gigabytes of
+memory and storage, and the viewpoint discretization hampers pose estimation
+performance.
 
-We propose an efficient method for synthesizing templates from 3D models that runs on the fly -- that is, it quickly produces detectors for an arbitrary viewpoint of a 3D model without expensive dataset-dependent training or template storage.
-Given a 3D model and an arbitrary continuous detection viewpoint, our method synthesizes a discriminative template by extracting features from a rendered view of the object and decorrelating spatial dependences among the features.
-Our decorrelation procedure relies on a gradient-based algorithm that is more numerically stable than standard decomposition-based procedures, and we efficiently search for candidate detections by computing FFT-based template convolutions.
-Due to the speed of our template synthesis procedure, we are able to perform joint optimization on continuous scale, translation, rotation, and focal length.
-We provide an efficient GPU implementation of our algorithm, and we validate its performance on 3DObject dataset and PASCAL 2012 dataset.
+We propose an efficient method for synthesizing templates from 3D models that
+runs on the fly -- that is, it quickly produces detectors for an arbitrary
+viewpoint of a 3D model without expensive dataset-dependent training or template
+storage. Given a 3D model and an arbitrary continuous detection viewpoint, our
+method synthesizes a discriminative template by extracting features from a
+rendered view of the object and decorrelating spatial dependences among the
+features. Our decorrelation procedure relies on a gradient-based algorithm that
+is more numerically stable than standard decomposition-based procedures, and we
+efficiently search for candidate detections by computing FFT-based template
+convolutions. Due to the speed of our template synthesis procedure, we are able
+to perform joint optimization on continuous scale, translation, rotation, and
+focal length. We provide an efficient GPU implementation of our algorithm, and
+we validate its performance on 3DObject dataset and PASCAL 2012 dataset.
 
-%     Using 3D model to detect and register the model to RGB image has been a growing field of study.
-Recently, Aubry \etal \cite{Aubry14} and J.
-Lim \etal \cite{Lim14} tried to estimate pose and align exact CAD model to an image using part-based templates.
-Malisiewicz \etal \cite{Malisiewicz11} also addresses the issue by transferring metadata after detection.
-Hejrati \etal \cite{Hejrati14} uses template synthesis to detect an object.
-All these approaches require extensive training, a lot of memory space.
-Also, the training based approach requires defining fixed viewpoints which limit themselves.
-%  To overcome these difficulties, we propose an efficient and fast way to synthesize and validate templates using on the fly realistic rendering that can jointly optimize scale, translation, rotation and focal length continuously.
-We render an object and extract features and decorrelate spatial dependencies within them on the fly to make a discriminative template.
-To speed up the decorrelation procedure, we adopt a gradient based algorithm which is numerically more stable than decomposition procedure.
-Finally, we efficiently search for candidate match by computing convolution using FFT and jointly optimize to match the object accurately.
-To speed up further, we propose an efficient GPU implementation and tested on PASCAL images.
+%     Using 3D model to detect and register the model to RGB image has been a
+%     growing field of study. Recently, Aubry \etal \cite{Aubry14} and J. Lim
+%     \etal \cite{Lim14} tried to estimate pose and align exact CAD model to an
+%     image using part-based templates. Malisiewicz \etal \cite{Malisiewicz11}
+%     also addresses the issue by transferring metadata after detection. Hejrati
+%     \etal \cite{Hejrati14} uses template synthesis to detect an object. All
+%     these approaches require extensive training, a lot of memory space. Also,
+%     the training based approach requires defining fixed viewpoints which limit
+%     themselves.  To overcome these difficulties, we propose an efficient and
+%     fast way to synthesize and validate templates using on the fly realistic
+%     rendering that can jointly optimize scale, translation, rotation and focal
+%     length continuously. We render an object and extract features and
+%     decorrelate spatial dependencies within them on the fly to make a
+%     discriminative template. To speed up the decorrelation procedure, we adopt
+%     a gradient based algorithm which is numerically more stable than
+%     decomposition procedure. Finally, we efficiently search for candidate
+%     match by computing convolution using FFT and jointly optimize to match the
+%     object accurately. To speed up further, we propose an efficient GPU
+%     implementation and tested on PASCAL images.
 
-%   In contrast to other mid-level patch based 3D matching methods which requires extensive training and more than 10Gb of memory space and physical storage, ours require no training nor saving the templates thus enabling it to run on any personal computer.
-%   To overcome these difficulties, we propose an efficient and fast way to synthesize and validate templates using on the fly realistic rendering that can jointly optimize scale, translation, rotation and focal length continuously.
-We render an object and extract features and decorrelate spatial dependencies within them on the fly to make a discriminative template.
-To speed up the decorrelation procedure, we adopt a gradient based algorithm which is numerically more stable than decomposition procedure.
-Finally, we efficiently search for candidate match by computing convolution using FFT and jointly optimize to match the object accurately.
-To speed up further, we propose an efficient GPU implementation and tested on PASCAL images.
+%   In contrast to other mid-level patch based 3D matching methods which
+%   requires extensive training and more than 10Gb of memory space and physical
+%   storage, ours require no training nor saving the templates thus enabling it
+%   to run on any personal computer.  To overcome these difficulties, we propose
+%   an efficient and fast way to synthesize and validate templates using on the
+%   fly realistic rendering that can jointly optimize scale, translation,
+%   rotation and focal length continuously. We render an object and extract
+%   features and decorrelate spatial dependencies within them on the fly to make
+%   a discriminative template. To speed up the decorrelation procedure, we adopt
+%   a gradient based algorithm which is numerically more stable than
+%   decomposition procedure. Finally, we efficiently search for candidate match
+%   by computing convolution using FFT and jointly optimize to match the object
+%   accurately. To speed up further, we propose an efficient GPU implementation
+%   and tested on PASCAL images.
 
@@
 % History of Whitening and how whitening works
-Recently, Hariharan \etal.
-introduced Whitened Histograms of Orientations (WHO) \cite{Hariharan12}, which used statistics from natural images to whiten HOG templates, making them more discriminative.
-Whitening is a common signal processing operation for decorrelating a set of random variables \cite{Martinsson05, Belouchrani00}.
-More formally, suppose that we have a $k$-dimensional random variable $X \in \mathcal{R}^k$ with $Cov(X)=\Sigma$.
-By whitening the signal, i.e., $\tilde{X}=\Sigma^{-\frac{1}{2}}(X - E[X])$, we remove 2nd order correlation between all features.
-So, all elements in the random variable $\tilde{X} = \left[\tilde{X}_1, \tilde{X}_2, \dots, \tilde{X}_k\right]$, become more independent.
-In the context of HOG features, a whitened HOG template will produce Gaussian noise when convolved with a random natural image, but a delta-like response on an image matching the template.
-WHO templates are more discriminative than standard HOG templates because they only capture the gradients that differentiate the object from random images.
-\scream{chris added the following} Hariharan \etal.
-also interpreted the whitening as Linear Discriminant Analysis (LDA) where all classes have different means but have the same covariance.
-The whitening and LDA have the same formulation when we make a decision boundary $w = \Sigma^{-1}(\mu_+ - \mu_0)$ where $\mu_+$ is the features from a class (LDA) or a signal to whiten (whitening), $\mu_0$ is the negative class center (LDA) or a signal statistics (whitening) and $\Sigma$ is the covariance matrix of classes (LDA) or correlation within signal (whitening).
+Recently, Hariharan \etal. introduced Whitened Histograms of Orientations (WHO)
+\cite{Hariharan12}, which used statistics from natural images to whiten HOG
+templates, making them more discriminative. Whitening is a common signal
+processing operation for decorrelating a set of random variables
+\cite{Martinsson05, Belouchrani00}. More formally, suppose that we have a
+$k$-dimensional random variable $X \in \mathcal{R}^k$ with $Cov(X)=\Sigma$. By
+whitening the signal, i.e., $\tilde{X}=\Sigma^{-\frac{1}{2}}(X - E[X])$, we
+remove 2nd order correlation between all features. So, all elements in the
+random variable $\tilde{X} = \left[\tilde{X}_1, \tilde{X}_2, \dots,
+\tilde{X}_k\right]$, become more independent. In the context of HOG features, a
+whitened HOG template will produce Gaussian noise when convolved with a random
+natural image, but a delta-like response on an image matching the template. WHO
+templates are more discriminative than standard HOG templates because they only
+capture the gradients that differentiate the object from random images.
+\scream{chris added the following} Hariharan \etal. also interpreted the
+whitening as Linear Discriminant Analysis (LDA) where all classes have different
+means but have the same covariance. The whitening and LDA have the same
+formulation when we make a decision boundary $w = \Sigma^{-1}(\mu_+ - \mu_0)$
+where $\mu_+$ is the features from a class (LDA) or a signal to whiten
+(whitening), $\mu_0$ is the negative class center (LDA) or a signal statistics
+(whitening) and $\Sigma$ is the covariance matrix of classes (LDA) or
+correlation within signal (whitening).
 
@@
 
-Modern object detectors generalize very well, handling intraclass variability, occlusion, truncation and viewpoint changes \cite{Felzenszwalb10, Girshick14}.
-However, this generalization comes at the cost of fine-grained information, including accurate 3D pose and object sub-category recognition.
-Such methods typically produce bounding box detection hypotheses, with little further information.
+Modern object detectors generalize very well, handling intraclass variability,
+occlusion, truncation and viewpoint changes \cite{Felzenszwalb10, Girshick14}.
+However, this generalization comes at the cost of fine-grained information,
+including accurate 3D pose and object sub-category recognition. Such methods
+typically produce bounding box detection hypotheses, with little further
+information.
 
-Many methods have attempted to move object detection towards richer outputs, especially by jointly performing detection and pose estimation \cite{Pepik12, Xiang12, Fidler12, Xiang14, Hejrati14, Aubry14, Lim14}.
-To achieve this, \cite{Xiang12, Hejrati14, Fidler12} use 3D representations that deform as viewpoint changes and \cite{Pepik12} uses geometric constraints to regularize 2D appearance models.
+Many methods have attempted to move object detection towards richer outputs,
+especially by jointly performing detection and pose estimation \cite{Pepik12,
+Xiang12, Fidler12, Xiang14, Hejrati14, Aubry14, Lim14}. To achieve this,
+\cite{Xiang12, Hejrati14, Fidler12} use 3D representations that deform as
+viewpoint changes and \cite{Pepik12} uses geometric constraints to regularize 2D
+appearance models.
 
-The methods above perform discrete pose estimation, quantizing the viewing sphere into a number of poses and selecting the best one during inference.
-Fine-grained pose estimators, in contrast, can infer continuous (or arbitrarily fine-grained) poses.
-One such method from \cite{Zia13} aligns a 3D deformable part-based wireframe model with input images to accurately predict object poses.
+The methods above perform discrete pose estimation, quantizing the viewing
+sphere into a number of poses and selecting the best one during inference.
+Fine-grained pose estimators, in contrast, can infer continuous (or arbitrarily
+fine-grained) poses. One such method from \cite{Zia13} aligns a 3D deformable
+part-based wireframe model with input images to accurately predict object poses.
 
-More recently, \cite{Aubry14, Lim14} made progress in joint instance-level object detection and pose estimation.
-To estimate pose they use synthetic renderings of CAD models to learn discriminative mid-level patches.
-\cite{Aubry14} calibrates these patches on a small set of real images, while \cite{Lim14} present a method for learning the relative discriminativeness of the patches.
+More recently, \cite{Aubry14, Lim14} made progress in joint instance-level
+object detection and pose estimation. To estimate pose they use synthetic
+renderings of CAD models to learn discriminative mid-level patches.
+\cite{Aubry14} calibrates these patches on a small set of real images, while
+\cite{Lim14} present a method for learning the relative discriminativeness of
+the patches.
 
@@
 
-% specialized in giving such accurate information, can be applied on any generic object detectors to give high quality metadata.
-% Many 
-% Since the WHO does not require extensive training such as \cite{Felzenszwalb10, Malisiewicz11, Girshick14}, WHO is gaining momentum in 2D-3D matching.
-\cite{Aubry13, Aubry14, Lim14} combined WHO with synthetic rendering to jointly detect and estimate pose by making mid-level patches using WHO.
-Using this
-% WSuch approach has an advantage over generic detections.
-First, it is easy to trace the detection to specific template.
-The template also has The rendering has corresponding CAD model and viewpoint thus enabling joint detection and viewpoint estimation.
-% To deal with textureless background \cite{Aubry13} whitens HOG feature and then zero out the WHO feature where there is no texture.
-But centering a HOG feature where there is no edge creates strong negative edges.
-We found out that centering only non-zero cells help detection but whitening all cell makes features to leak out to texture-less regions.
-% With increasing popularity of rendering image, whitening, traditional signal processing technique, as a preprocessing stage has been widely used also in computer vision community.
-% Many object detectors \cite{Felzenszwalb10, Malisiewicz11}
-% \subsection{Mid-level Patches for 2D-3D matching}
-%  FPM introduction : per instance matching  
-%  Seeing 3D chair : mid-level patches
+% specialized in giving such accurate information, can be applied on any generic
+% object detectors to give high quality metadata.  Many Since the WHO does not
+% require extensive training such as \cite{Felzenszwalb10, Malisiewicz11,
+% Girshick14}, WHO is gaining momentum in 2D-3D matching. \cite{Aubry13,
+% Aubry14, Lim14} combined WHO with synthetic rendering to jointly detect and
+% estimate pose by making mid-level patches using WHO. Using this WSuch approach
+% has an advantage over generic detections. First, it is easy to trace the
+% detection to specific template. The template also has The rendering has
+% corresponding CAD model and viewpoint thus enabling joint detection and
+% viewpoint estimation.  To deal with textureless background \cite{Aubry13}
+% whitens HOG feature and then zero out the WHO feature where there is no
+% texture. But centering a HOG feature where there is no edge creates strong
+% negative edges. We found out that centering only non-zero cells help detection
+% but whitening all cell makes features to leak out to texture-less regions.
+% With increasing popularity of rendering image, whitening, traditional signal
+% processing technique, as a preprocessing stage has been widely used also in
+% computer vision community.  Many object detectors \cite{Felzenszwalb10,
+% Malisiewicz11} \subsection{Mid-level Patches for 2D-3D matching} FPM
+% introduction : per instance matching  Seeing 3D chair : mid-level patches
 
@@
 
-We propose Non-Zero Whitened Histograms of Orientations (NZ-WHO), that are both more discriminative than WHO, and can be generated in 70ms (compared to several seconds for WHO).
-This speed up means we can generate templates on the fly, allowing our approach to evaluate arbitrary viewpoint hypotheses.
-\scream{chris:We propose Non-Zero Whitened Histograms of Orientations (NZ-WHO), an improvement over WHO which is both more discriminative than WHO and can be computed many orders of magnitude faster than WHO (70ms as opposed to to several seconds for WHO).
-This speedup allows us to generate NZ-WHO templates on the fly, allowing us to quickly evaluate arbitrary viewpoint hypotheses.}
+We propose Non-Zero Whitened Histograms of Orientations (NZ-WHO), that are both
+more discriminative than WHO, and can be generated in 70ms (compared to several
+seconds for WHO). This speed up means we can generate templates on the fly,
+allowing our approach to evaluate arbitrary viewpoint hypotheses.
 
-The computational efficiency of our approach comes from using the iterative conjugate gradient method to whiten the HOG template.
-Whitening a feature vector $x$ requires a system of linear equations $\Sigma w = (x - \mu)$ to be solved, usually by decomposing the covariance matrix $\Sigma$ (with LU or Cholesky decomposition).
-Since the covariance matrices of HOG templates have nice spectral properties (see Section \ref{sec:fast_whitening}), the conjugate gradient method will converge to the solution several orders of magnitude faster than decomposition methods.
+\scream{chris:We propose Non-Zero Whitened Histograms of Orientations (NZ-WHO),
+an improvement over WHO which is both more discriminative than WHO and can be
+computed many orders of magnitude faster than WHO (70ms as opposed to to several
+seconds for WHO). This speedup allows us to generate NZ-WHO templates on the
+fly, allowing us to quickly evaluate arbitrary viewpoint hypotheses.}
 
-Our second innovation is 'Non-Zero' whitening.
-When synthesizing detection templates from rendered images, a common problem is how to handle the background.
-If we render the model over a natural image background, gradients in the background will be incorporated into the discriminative template.
-Alternatively, we could leave the background textureless \scream{did Hariharan do this?} (see Fig.~\ref{fig:rendering}), but whitening the resulting HOG template produces in undesirable background artifacts.
-These are created when centering the template (by subtracting the mean $\mu$), where strong negative weights are introduced in the textureless region (as seen in Fig.~\ref{fig:whocomparison}).
-This could result in positive matches being suppressed due to spurious background gradients.
+The computational efficiency and numerical stability of our approach comes from
+using the iterative conjugate gradient method to whiten the HOG template.
+Whitening a feature vector $x$ requires a system of linear equations $\Sigma w =
+(x - \mu)$ to be solved, usually by decomposing the covariance matrix $\Sigma$
+(with LU or Cholesky decomposition). Since the covariance matrices of HOG
+templates have nice spectral properties (see Section \ref{sec:fast_whitening}),
+the conjugate gradient method will converge to the solution several orders of
+magnitude faster than decomposition methods.
 
-To remove such artifacts, we construct $x$ using only cells with non-zero gradients.
-After whitening we restore the full template, with the zero-gradient cells left unchanged.
-This approach has the added benefit of reducing the size of the linear system we need to solve, further speeding up our method.
+Our second innovation is 'Non-Zero' whitening. When synthesizing detection
+templates from rendered images, a common problem is how to handle the
+background. If we render the model over a natural image background, gradients in
+the background will be incorporated into the discriminative template.
+Alternatively, we could leave the background textureless \scream{did Hariharan
+do this?} (see Fig.~\ref{fig:rendering}), but whitening the resulting HOG
+template produces in undesirable background artifacts. These are created when
+centering the template (by subtracting the mean $\mu$), where strong negative
+weights are introduced in the textureless region (as seen in
+Fig.~\ref{fig:whocomparison}). This could result in positive matches being
+suppressed due to spurious background gradients.
 
-Table \ref{tab:who_initializations} provides a detailed comparison of WHO and NZ-WHO templates, illustrating that our method is faster and more discriminative than Whitened Histograms of Orientations.
-\scream{Does the table show this?}
+To remove such artifacts, we construct $x$ using only cells with non-zero
+gradients. After whitening we restore the full template, with the zero-gradient
+cells left unchanged. This approach has the added benefit of reducing the size
+of the linear system we need to solve, further speeding up our method.
+
+Table \ref{tab:who_initializations} provides a detailed comparison of WHO and
+NZ-WHO templates, illustrating that our method is faster and more discriminative
+than Whitened Histograms of Orientations. \scream{Does the table show this?}
 
@@
 
-% To accommodate the growing usage of rendering image for 2D-3D matching using WHO\cite{Aubry13, Aubry14, Lim14}, we analyzed various methods to whiten synthetic rendering image and propose Non-Zero Whitened Histograms of Orientations (NZ-WHO) which is a direct extension of \cite{Hariharan12} designed for rendering images with textureless background.
-% Since a NZ-WHO template has zero-mean and all elements in the template follow same distribution, no explicit calibration is required if all the templates have approximately the same number of cells.
+% To accommodate the growing usage of rendering image for 2D-3D matching using
+% WHO\cite{Aubry13, Aubry14, Lim14}, we analyzed various methods to whiten
+% synthetic rendering image and propose Non-Zero Whitened Histograms of
+% Orientations (NZ-WHO) which is a direct extension of \cite{Hariharan12}
+% designed for rendering images with textureless background. % Since a NZ-WHO
+% template has zero-mean and all elements in the template follow same
+% distribution, no explicit calibration is required if all the templates have
+% approximately the same number of cells.
 
@@
 % Whats used in our work and using Autocovariance matrix
-We first collected the first and second order statistics (mean and autocovariance) of HOG features from arbitrary natural images.
-Following \cite{Hariharan12}, we assume Wide-Sense Stationarity (WSS) of HOG features generated from natural images.
-That is, we assume the mean of a HOG cell is independent of its place in the image, and the autocovariance of patches depends only on their relative location.
+We first collected the first and second order statistics (mean and
+autocovariance) of HOG features from arbitrary natural images. Following
+\cite{Hariharan12}, we assume Wide-Sense Stationarity (WSS) of HOG features
+generated from natural images. That is, we assume the mean of a HOG cell is
+independent of its place in the image, and the autocovariance of patches depends
+only on their relative location.
 
-In one dimension, let $x(u)$ be the feature at location $u$. Then WSS states that $\mathbb{E}\left[x(u)\right] = \mu_x$ for all $u$, and
+In one dimension, let $x(u)$ be the feature at location $u$. Then WSS states
+that $\mathbb{E}\left[x(u)\right] = \mu_x$ for all $u$, and
 \begin{equation}
@@
 
-Therefore, assuming WSS allows us to synthesize the covariance matrix for templates \emph{of any size} from the autocovariance matrix.
-This hugely reduces the memory required because to build the covariance matrix of a template of $w \times h$ HOG cells (with 31 elements per cell), we only need a $w \times h \times 31$ autocovariance matrix.
-In comparison, the covariance matrix itself is $(w \times h \times 31) \times (w \times h \times 31)$.
-Furthermore, by using the autocovariance we can avoid storing the covariance matrix for every different aspect ratio used during detection.
+Therefore, assuming WSS allows us to synthesize the covariance matrix for
+templates \emph{of any size} from the autocovariance matrix. This hugely reduces
+the memory required because to build the covariance matrix of a template of $w
+\times h$ HOG cells (with 31 elements per cell), we only need a $w \times h
+\times 31$ autocovariance matrix. In comparison, the covariance matrix itself is
+$(w \times h \times 31) \times (w \times h \times 31)$. Furthermore, by using
+the autocovariance we can avoid storing the covariance matrix for every
+different aspect ratio used during detection.
 
-To further simplify $\Gamma$, we assumed horizontal and vertical symmetry.
-In our implementation, we compute a $40 \times 40 \times 31$ autocovariance matrix, meaning we can synthesize covariance matrices for HOG grids as big as $40 \times 40$.
-In practice we limit the number of cells per template to 250.
+To further simplify $\Gamma$, we assumed horizontal and vertical symmetry. In
+our implementation, we compute a $40 \times 40 \times 31$ autocovariance matrix,
+meaning we can synthesize covariance matrices for HOG grids as big as $40 \times
+40$. In practice we limit the number of cells per template to 250.
 
-We use the GPU to parallelize the lookup of the correct autocovariance cells during covariance matrix syntheses, which is \scream{x} times faster than using the CPU (Figure \ref{fig:covariancetime}).
+We use the GPU to parallelize the lookup of the correct autocovariance cells
+during covariance matrix syntheses, which is \scream{x} times faster than using
+the CPU (Figure \ref{fig:covariancetime}).
 
-% Since the statistics have been computed for a generic HOG feature, we can use the same statistics for all templates and images.
-In practice, since it is expensive to whiten all the sliding patches in the image, we followed \cite{Hariharan12} and defined the templates to be $w = \Sigma^{-1}(X-E[X])$\begin{comment}which is a good approximation of $\Sigma^{-\frac{T}{2}} \Sigma^{-\frac{1}{2}}(X-E[X])$\end{comment}
+% Since the statistics have been computed for a generic HOG feature, we can use
+% the same statistics for all templates and images. In practice, since it is
+% expensive to whiten all the sliding patches in the image, we followed
+% \cite{Hariharan12} and defined the templates to be $w =
+% \Sigma^{-1}(X-E[X])$\begin{comment}which is a good approximation of
+% $\Sigma^{-\frac{T}{2}} \Sigma^{-\frac{1}{2}}(X-E[X])$\end{comment}
 
-% \begin{comment}Gathering statistics, especially computing spatial covariance of a signal is computationally burdensome. \end{comment}
-% To speed up the statistics collection, \begin{comment}in addition to the wide-sense stationarity (WSS) of HOG, \end{comment}we assumed horizontal and vertical symmetry of covariance.
+% \begin{comment}Gathering statistics, especially computing spatial covariance
+% of a signal is computationally burdensome. \end{comment} To speed up the
+% statistics collection, \begin{comment}in addition to the wide-sense
+% stationarity (WSS) of HOG, \end{comment}we assumed horizontal and vertical
+% symmetry of covariance.
 
- %Hariharan \etal \cite{Hariharan12} interpreted the whitening also as the Linear Discriminant Analysis where each class has the same covariance $\Sigma$ but with different mean value.
-They defined this whitened HOG feature as Whitened Histograms of Orientations (WHO) and we will follow their convention of the name.
+ %Hariharan \etal \cite{Hariharan12} interpreted the whitening also as the
+ %Linear Discriminant Analysis where each class has the same covariance $\Sigma$
+ %but with different mean value. They defined this whitened HOG feature as
+ %Whitened Histograms of Orientations (WHO) and we will follow their convention
+ %of the name.
 
@@
 % 
-% We used a public rendering engine to create realistic rendering and depth\begin{comment}\cite{Choy14render}\end{comment}.
-The CAD models we used in our experiments contain color, texture and material information such as transparency and reflectance.
-We tried to make the rendering as much realistic as possible to simulate the natural image statistics.
-The example rendering is in Fig.
-\ref{fig:rendering}.
-We also extracted depth information as well while rendering to use in the reconstruction.
+% We used a public rendering engine to create realistic rendering and
+% depth\begin{comment}\cite{Choy14render}\end{comment}. The CAD models we used
+% in our experiments contain color, texture and material information such as
+% transparency and reflectance. We tried to make the rendering as much realistic
+% as possible to simulate the natural image statistics. The example rendering is
+% in Fig. \ref{fig:rendering}. We also extracted depth information as well while
+% rendering to use in the reconstruction.
 
 % To whiten a HOG features, we first have to synthesize the covariance matrix.
-Following the method of \cite{Hariharan12}, which assumes spatial Wide-Sense Stationarity (WSS) of a feature, covariance matrix can be synthesized using spatial autocovariance $\Gamma$.
-This assumes the \begin{comment} and features such as HOG are gradients in a small patch whose statistics does not change (an object can be in anywhere in an image)\end{comment}.
+% Following the method of \cite{Hariharan12}, which assumes spatial Wide-Sense
+% Stationarity (WSS) of a feature, covariance matrix can be synthesized using
+% spatial autocovariance $\Gamma$. This assumes the \begin{comment} and features
+% such as HOG are gradients in a small patch whose statistics does not change
+% (an object can be in anywhere in an image)\end{comment}.
 
-%However, unlike small fixed-sized mid-level patches, the root templates have different aspect ratios, different gradient patterns and large number of HOG cells which results in large covariance $\Sigma \in \mathcal{R}^{7000 \times 7000}$ that is difficult to cache.
-Thus, to generate a NZ-WHO template, we have to synthesize a covariance matrix and solve the system of linear equations.
+%However, unlike small fixed-sized mid-level patches, the root templates have
+%different aspect ratios, different gradient patterns and large number of HOG
+%cells which results in large covariance $\Sigma \in \mathcal{R}^{7000 \times
+%7000}$ that is difficult to cache. Thus, to generate a NZ-WHO template, we have
+%to synthesize a covariance matrix and solve the system of linear equations.
 
-% Thus, every time we whiten a root template, we have to generate a covariance matrix using autocovariance $\Gamma$.
+% Thus, every time we whiten a root template, we have to generate a covariance
+% matrix using autocovariance $\Gamma$.
 
-%\begin{comment} Also, since we are whitening only the non-zero HOG cells whose position is unknown beforehand and all templates have different aspect ratio for , we cannot cache the matrix.
-Using CPU, it takes about \end{comment}
+%\begin{comment} Also, since we are whitening only the non-zero HOG cells whose
+%position is unknown beforehand and all templates have different aspect ratio
+%for , we cannot cache the matrix. Using CPU, it takes about \end{comment}
 
-% In practice, synthesizing covariance matrix $\Sigma$ takes long time due to its large size.
-$\Sigma$ ranges from $\Sigma \in \mathcal{R}^{7000 \times 7000}$ to $\Sigma \in \mathcal{R}^{7500 \times 7500}$.
-We vary the template resolution and run $\Sigma$ generation on CPU and GPU 100 times and report the average time in Fig.
-\ref{fig:covariancetime}.
+% In practice, synthesizing covariance matrix $\Sigma$ takes long time due to
+% its large size.  $\Sigma$ ranges from $\Sigma \in \mathcal{R}^{7000 \times
+% 7000}$ to $\Sigma \in \mathcal{R}^{7500 \times 7500}$. We vary the template
+% resolution and run $\Sigma$ generation on CPU and GPU 100 times and report the
+% average time in Fig. \ref{fig:covariancetime}.
 
@@
 
-To whiten a signal $x$, we have to solve $\Sigma w = x - \mu$.
-In \cite{Hariharan12}, the authors make use of the fact that covariance matrices are Hermitian and positive semidefinite to solve the system via the Cholesky decomposition, which is twice as fast as the LU decomposition.
-These decompositions require $O(n^3)$ time, whereas the conjugate gradient method takes $O(n^2\kappa)$ time, where $\kappa$ is the condition number of the matrix.
-This makes conjugate gradient a faster option for matrices with small condition numbers relative to their size.
+To whiten a signal $x$, we have to solve $\Sigma w = x - \mu$. In
+\cite{Hariharan12}, the authors make use of the fact that covariance matrices
+are Hermitian and positive semidefinite to solve the system via the Cholesky
+decomposition, which is twice as fast as the LU decomposition. These
+decompositions require $O(n^3)$ time, whereas the conjugate gradient method
+takes $O(n^2\kappa)$ time, where $\kappa$ is the condition number of the matrix.
+This makes conjugate gradient a faster option for matrices with small condition
+numbers relative to their size.
 
-Figure \ref{fig:spectral} shows the singular values of a covariance matrix for one HOG template after a small regularization constant is added to the diagonal.
-The condition number of of the matrix is \scream{x}, much smaller than the size of the matrix (7500).
-As a result, conjugate gradient converges in \scream{x ms}, two orders of magnitude faster than the system can be solved using the Cholesky factorization (\scream{5 s}).
+Figure \ref{fig:spectral} shows the singular values of a covariance matrix for
+one HOG template after a small regularization constant is added to the diagonal.
+The condition number of of the matrix is \scream{x}, much smaller than the size
+of the matrix (7500). As a result, conjugate gradient converges in \scream{x
+ms}, two orders of magnitude faster than the system can be solved using the
+Cholesky factorization (\scream{5 s}).
 
-The final challenge in on-the-fly template evaluation is performing the convolution between the template and the target image.
-Standard convolution would be prohibitively slow for the high resolution templates we're using, so we implemented the convolution via Fast Fourier Transform on the GPU.
-This allows template evaluation to run in \scream{x ms}, compared to \scream{x ms} for the naive CPU implementation.
+The final challenge in on-the-fly template evaluation is performing the
+convolution between the template and the target image. Standard convolution
+would be prohibitively slow for the high resolution templates we're using, so we
+implemented the convolution via Fast Fourier Transform on the GPU. This allows
+template evaluation to run in \scream{x ms}, compared to \scream{x ms} for the
+naive CPU implementation.
 
@@
 
-% where $w$ is the weight we want to find and $x$ is the HOG feature from the rendering and $\lambda$ is the regularization constant (see section \ref{sec:regularization}).
-For $w\in \mathcal{R}^n$, it takes $O(n^3)$ time to solve the linear equation.
-If we use a high resolution template to capture small geometric properties we can get high accuracy matchings but the solving the linear equation becomes computationally burdensome.
+% where $w$ is the weight we want to find and $x$ is the HOG feature from the
+% rendering and $\lambda$ is the regularization constant (see section
+% \ref{sec:regularization}). For $w\in \mathcal{R}^n$, it takes $O(n^3)$ time to
+% solve the linear equation. If we use a high resolution template to capture
+% small geometric properties we can get high accuracy matchings but the solving
+% the linear equation becomes computationally burdensome.
 
-% To briefly recap, the LU Decomposition and Cholesky Decomposition are most popular methods to solve a linear equation.
-In linear algebra libraries such as MATLAB, these decomposition methods are default method to solve a linear equation (backslash \textbackslash in MATLAB).
-Since the covariance matrix is Hermitian and Positive Semi-Definite, we can use Cholesky Decomposition which is twice as fast as the LU Decomposition.
+% To briefly recap, the LU Decomposition and Cholesky Decomposition are most
+% popular methods to solve a linear equation. In linear algebra libraries such
+% as MATLAB, these decomposition methods are default method to solve a linear
+% equation (backslash \textbackslash in MATLAB). Since the covariance matrix is
+% Hermitian and Positive Semi-Definite, we can use Cholesky Decomposition which
+% is twice as fast as the LU Decomposition.
 
-% decomposition methods such as LU or Cholesky Decomposition not only take long time but they also accumulate numerical error.
+% decomposition methods such as LU or Cholesky Decomposition not only take long
+% time but they also accumulate numerical error.
 
-%In our setting, we used high resolution template which has more than 250 HOG cells.
-This result in $\Sigma \in \mathcal{R}^{7500 \times 7500}$.
-It takes about 9 seconds if we use LU decomposition and 5 seconds if we use Cholesky decomposition.
-% The default way of solving the linear equation in many linear algebra library is decomposing the matrix using LU Decomposition (in MATLAB the default method of backslash operator) which takes $O(\frac{2}{3}n^3)$ flops for $n\times n$ matrix.
-Since the matrix, $\Sigma + \lambda I$ is Hermitian and Positive Semi Definite.
-We can speed up using Cholesky Decomposition.
+%In our setting, we used high resolution template which has more than 250 HOG
+%cells. This result in $\Sigma \in \mathcal{R}^{7500 \times 7500}$. It takes
+%about 9 seconds if we use LU decomposition and 5 seconds if we use Cholesky
+%decomposition.  % The default way of solving the linear equation in many linear
+%algebra library is decomposing the matrix using LU Decomposition (in MATLAB the
+%default method of backslash operator) which takes $O(\frac{2}{3}n^3)$ flops for
+%$n\times n$ matrix. Since the matrix, $\Sigma + \lambda I$ is Hermitian and
+%Positive Semi Definite. We can speed up using Cholesky Decomposition.
 
-%We also used iterative Conjugate Gradient to make use of low rank property of the covariance \cite{Gharbi12}.
-After adding small regularization, the regularized covariance matrix has nice spectral property (Figure \ref{fig:spectral}).
-The singular values are clustered in small region and most of the energies are concentrated on the first (number) singular values.
-Thus, the conjugate gradients stage doesn't go upto the size of the matrix to converge.
+%We also used iterative Conjugate Gradient to make use of low rank property of
+%the covariance \cite{Gharbi12}. After adding small regularization, the
+%regularized covariance matrix has nice spectral property (Figure
+%\ref{fig:spectral}). The singular values are clustered in small region and most
+%of the energies are concentrated on the first (number) singular values. Thus,
+%the conjugate gradients stage doesn't go upto the size of the matrix to
+%converge.
 
@@
 
-We empirically found out that NZ-WHO performs reasonably well without time consuming calibration stage compare to other variational method to generate templates.
-We used 1 CAD model with viewpoints covering 24 azimuths and 4 elevations.
-Each template takes approximately 80 milliseconds to generate a NZ-WHO template.
-We also calibrated templates using the method presented in \cite{Aubry14}.
-The calibration learns affine transformation of the detection confidence.% Note that in Section \ref{experiments}, we provide the same experiment with 9 CAD models.
+We empirically found out that NZ-WHO performs reasonably well without time
+consuming calibration stage compare to other variational method to generate
+templates. We used 1 CAD model with viewpoints covering 24 azimuths and 4
+elevations. Each template takes approximately 80 milliseconds to generate a
+NZ-WHO template. We also calibrated templates using the method presented in
+\cite{Aubry14}. The calibration learns affine transformation of the detection
+confidence.% Note that in Section \ref{experiments}, we provide the same
+experiment with 9 CAD models.
 
@@
 
-We found out that without calibration, NZ-WHO performs the best on object detection on 3DObject car dataset \cite{Savarese07}.
-See Table \ref{tab:who_initializations} for detail.
-In essence, if we use calibration, we could achieve better performance but since our goal is to do 2D-3D matching and continuous viewpoint estimation using on-the-fly template generation, we did not calibrated our templates.
+We found out that without calibration, NZ-WHO performs the best on object
+detection on 3DObject car dataset \cite{Savarese07}. See Table
+\ref{tab:who_initializations} for detail. In essence, if we use calibration, we
+could achieve better performance but since our goal is to do 2D-3D matching and
+continuous viewpoint estimation using on-the-fly template generation, we did not
+calibrated our templates.
 
@@
 % \label{sec:regularization}
-%  Also, since all covariance matrix is Positive Semi Definite, our matrix $\Sigma$ must be Positive Semi-Definite too.
-To guarantee the property, We found out that the regularization has significant impact on the performance.
-In \cite{Hariharan12}, Hariharan \etal used small fixed regularization since the covariance matrix of specially correlated features is intrinsically row-rank to make the matrix invertible.
+%  Also, since all covariance matrix is Positive Semi Definite, our matrix
+%  $\Sigma$ must be Positive Semi-Definite too. To guarantee the property, We
+%  found out that the regularization has significant impact on the performance.
+%  In \cite{Hariharan12}, Hariharan \etal used small fixed regularization since
+%  the covariance matrix of specially correlated features is intrinsically
+%  row-rank to make the matrix invertible.
 %  
@@
 First, we make a set of NZ-WHO templates for a set of CAD models from various viewpoints.
-Then we run the bank of NZ-WHO templates as ensembles of weak detectors and show that the rendering image can be We want to see how robust the NZ-WHO to real images a
+Then we run the bank of NZ-WHO templates as an ensemble of weak detectors and show that we can achieve 2D-3D matching We want to see how robust the NZ-WHO to real images
 

### 2014-11-14 egpaper_final.tex

@@
 
-\section{Continuous Viewpoint and Focal Length Estimation for Fine Tuning}
+\section{Estimating Parameters using MCMC}
+\label{sec:fine}
+% Estimating viewpoint continuously to fine tune a initial matching
+The NZ-WHO template matching method we have presented makes template generation
+and evaluation computationally inexpensive. This means we can efficiently
+explore the parameter space to find the best object pose, scale, model type and
+camera focal length.
 
-% Estimating viewpoint continuously to fine tune a initial matching
-The NZ-WHO template matching method we have presented makes template generation and evaluation computationally inexpensive. 
-Since creating a template and validating the template become computationally inexpensive, making a proposal and validating the proposal to fine tune a 2D-3D matching became affordable.
-We used Metropolis-Hastings algorithm to generate a proposal pose and focal length and validate the proposal using the convolution and returning maximum response as a return.
+Since creating a template and validating the template become computationally
+inexpensive, making a proposal and validating the proposal to fine tune a 2D-3D
+matching became affordable. We used Metropolis-Hastings algorithm to generate a
+proposal pose and focal length and validate the proposal using the convolution
+and returning maximum response as a return.
 
-We modeled the distribution of the convolution as an exponential distribution and used Gaussian as our proposal distribution.
+We modeled the distribution of the convolution as an exponential distribution
+and used Gaussian as our proposal distribution.
 
-We run experiments on PASCAL 2007 car category images with at least one car (num images) and got x percent improvement after fine tuning.
+We run experiments on PASCAL 2007 car category images with at least one car
+(num images) and got x percent improvement after fine tuning.
 
@@
 \section{Experiments}
-
-In this section, we validate our proposed NZ-WHO templates in two different ways.
-First, we make a set of NZ-WHO templates for a set of CAD models from various viewpoints.
-Then we run the bank of NZ-WHO templates as an ensemble of weak detectors and show that we can achieve 2D-3D matching We want to see how robust the NZ-WHO to real images
-
-Second, we show that our method can complement the detection bounding boxes coming out of standard object detectors.
-This process will enrich object detection bounding boxes with 2D-3D matching which gives continuous viewpoint estimation, a CAD model (rendering, depth) and fine-grained category.
-
-\subsection{2D-3D Matching as an Object Detector}
-
-We created ensemble of NZ-WHO templates using 9 CAD models and measured the Average Precision (AP) of object detection task and Mean Precision in Pose Estimation (MPPE) \cite{Lopez-Sastre11}.
-MPPE is the average of viewpoint accuracy.
-
-% Instance-level 2D-3D matching (registration) is a difficult problem since we need a CAD model that looks similar to the object in the image.
-Especially, due to extreme intraclass variability of chair \cite{Aubry14} used a very large collection of CAD models to cover variety of chairs.
-Similarly, \cite{Lim14}
-
-Our ensemble of NZ-WHO templates is generated from rendering images within few minutes but shows reasonable performance on object detection task.
-The baseline method are Aspect Layout Model (ALM) \cite{Xiang12} and VOC-DPM \cite{Pepik12}.
-Note that the baseline methods require complex 3D modeling and viewpoint annotated natural images.
-
-The detection result is on Table \ref{tab:3dobject} and example output from our method is on Figure \ref{fig:3dobject}.
-
-\begin{table}[!htbp]
-    \footnotesize
-  \begin{center}
-    \begin{tabular}{|c|c|c|c|}
-    \hline
-     AP/MPPE& Ours & ALM\cite{Xiang12} & VOC-DPM\cite{Pepik12} \\
-    \hline\hline
-    car & \textbf{99.8}/91.7 &  98.4/93.4 & \textbf{99.8}/\textbf{97.5} \\ 
-    bicycle & 93.0/87.4 & 93.0/91.4 & \textbf{98.8}/\textbf{97.5} \\
-    \hline
-    \end{tabular}
-  \end{center}
-  \caption{Average Precision(AP) and Mean Precision in Pose Estimation (MPPE) on 3DObject dataset car category.
-Our method produces high quality 2D-3D matching yet performs on par with state-of-the art detectors.}
-  \label{tab:3dobject}
-\end{table}
-
-\begin{figure}[h]
-    \begin{center}
-    \setlength\tabcolsep{0pt}
-\begin{tabular}{cc}
-  \includegraphics[width=0.45\linewidth]{car_3dobject/7.png} &   
-  \includegraphics[width=0.45\linewidth]{car_3dobject/8.png}\\ [-15pt]
-%   (a) & (b) \\[0pt]
-  \includegraphics[width=0.45\linewidth]{car_3dobject/11.png} &   
-  \includegraphics[width=0.45\linewidth]{car_3dobject/12.png}\\ [-5pt]
-%  (c) & (d) \\[0pt]
-\end{tabular}
-\end{center}
-\caption{Detection results on 3D-Object dataset \cite{Savarese07}. Original image (left) and detection result overlaid on top with a bounding box and corresponding confidence score(right)}
-  \label{fig:3dobject}
-\end{figure}
-
-% Also, we evaluated our method on PASCAL 2007 dataset.
-% 
-% \begin{table}[!htbp]
-%   \begin{center}
-%   \begin{tabular}{|c|c|c|c|c|}
-%     \hline
-%      AP &    Ours &    ELDA \cite{Hariharan12} & ESVM \cite{Malisiewicz11} & VOCDPM \cite{Pepik12} \\
-%     \hline\hline
-%     car      & 27.          &  38.4  & 40.1    &65.7  \\ 
-%     bicycle  & 43.74 & 41      &  40.7   & 61.3   \\
-%     \hline
-%     \end{tabular}
-%   \end{center}
-%   \caption{Average Precision(AP) on PASCAL 2007 dataset.
-Though we do not need any training images and made templates in few minues, it performs on par with state of the art detector yet it gives high quality 2D-3D matching.}
-%   \label{tab:pascal07}
-% \end{table}
-
-\subsection{Fine-Tuning and Viewpoint Estimation}
-
-High performance object detectors usually generalizes very well.
-It can handle various intraclass variability, viewpoint change and occlusion.
-However due to this high generalization, sometimes it is very difficult to get accurate pose, category or 2D-3D matching.
-Our method, specialized in giving such accurate information, can be applied on any generic object detectors to give high quality metadata.
-
-To show such ability, we evaluated our method on PASCAL 3D dataset \cite{Xiang14}.
-The dataset augments PASCAL 2012 images with high quality viewpoint annotations thus is ideal to measure pose estimation.
-The dataset proposes new metric called Average Viewpoint Precision (AVP) where it measures the area under viewpoint precision and detection recall curve.
-The viewpoints is measured by azimuth similarity.
-If the distance between predicted azimuth and ground truth azimuth is below a certain threshold, the viewpoint is correct.
-Note that the baseline methods (V-DPM, VOC-DPM) reported on the PASCAL 3D dataset are variants of DPM where each component of DPM account for various azimuths.
-Thus V-DPM and VOC-DPM provide discrete azimuth only whereas our method provides 3D viewpoint (yaw, pitch, roll), CAD instance (model index, rendering, depth) and focal length.
-
-We used detection bounding boxes and augment it using our method to give viewpoint estimation.
-We used detection bounding boxes from two different methods: VOC-DPM \cite{Pepik12} and R-CNN \cite{Girshick14}.
-VOC-DPM is a variation of DPM that can estimate viewpoint and is the state-of-the-art performance in viewpoint estimation \cite{Xiang14}.
-The result is on Table \ref{tab:pascal12} and precision recall curves for car using R-CNN + Ours are on Figure \ref{fig:car_cnn_ap}.
-
-We got significant improvement on viewpoint estimation by using our method on top of general purpose detectors.
-Note that our method estimates azimuth, elevation, in-plane rotation, focal length estimation, fine-grained categorization whereas V-DPM, VOC-DPM only estimate discrete viewpoints.
-
-Example outputs are on Figure \ref{fig:pascal12cnn}.
-
-\begin{figure*}[h]
-\setlength\tabcolsep{1pt}
-\centering
-\begin{tabular}{|c|c|c|c|c|}
-   \hline
-  \includegraphics[width=0.24\textwidth]{car_cnn/1a.png} &   
-  \includegraphics[width=0.24\textwidth]{car_cnn/1b.png} &   
-  \includegraphics[width=0.24\textwidth]{car_cnn/1c.png} &   
-  \includegraphics[width=0.24\textwidth]{car_cnn/1d.png}  \\  
-   \hline
-  \includegraphics[width=0.24\textwidth]{car_cnn/2a.png} &   
-  \includegraphics[width=0.24\textwidth]{car_cnn/2b.png} &   
-  \includegraphics[width=0.24\textwidth]{car_cnn/2c.png} &   
-  \includegraphics[width=0.24\textwidth]{car_cnn/2e.png}  \\  
-   \hline
-  \includegraphics[width=0.24\textwidth]{car_cnn/4a.png} &   
-  \includegraphics[width=0.24\textwidth]{car_cnn/4b.png} &   
-  \includegraphics[width=0.24\textwidth]{car_cnn/4c.png} &   
-  \includegraphics[width=0.24\textwidth]{car_cnn/4d.png}  \\  
-%    \hline
-%   \includegraphics[width=0.24\textwidth]{car_cnn/10a.png} &   
-%   \includegraphics[width=0.24\textwidth]{car_cnn/10b.png} &   
-%   \includegraphics[width=0.24\textwidth]{car_cnn/10c.png} &   
-%   \includegraphics[width=0.24\textwidth]{car_cnn/10d.png}  \\  
-%   \hline 
-%   \includegraphics[width=0.24\textwidth]{bicycle_cnn/3a.png} &   
-%   \includegraphics[width=0.24\textwidth]{bicycle_cnn/3b.png} &   
-%   \includegraphics[width=0.24\textwidth]{bicycle_cnn/3c.png} &   
-%   \includegraphics[width=0.24\textwidth]{bicycle_cnn/3d.png}  \\
-  \hline
-  \includegraphics[width=0.24\textwidth]{bicycle_cnn/7a.png} &   
-  \includegraphics[width=0.24\textwidth]{bicycle_cnn/7b.png} &   
-  &\\
-  \hline
-  \includegraphics[width=0.24\textwidth]{bicycle_cnn/4a.png} &   
-  \includegraphics[width=0.24\textwidth]{bicycle_cnn/4b.png} &   
-  \includegraphics[width=0.24\textwidth]{bicycle_cnn/4c.png} &   
-  \includegraphics[width=0.24\textwidth]{bicycle_cnn/4d.png}  \\
-  \hline
-  CNN Proposals & \multicolumn{3}{|c|}{Our matching results on proposal bounding boxes} \\
-  \hline
-\end{tabular}
-\caption{Example enriched bounding boxes.
-Given R-CNN\cite{Girshick14} detection bounding boxes, our method predicted 2D-3D matching reasonably.
-On the first column, R-CNN detection bounding boxes overlaid.
-From the second to the last columns, output of our method given a R-CNN box.
-Blue boxes are R-CNN output and purple boxes are the tightest bounding box enclosing predicted CAD model}
-  \label{fig:pascal12cnn}
-\end{figure*}
-\begin{table*}[!htbp]
-    \footnotesize
-  \begin{center}
-\begin{tabular}{|c|c|c|c|c|c|c|}
-\hline
-AP/AVP              & V-DPM \cite{Xiang14} & VOC-DPM \cite{Pepik12}  & \cite{Pepik12} + Ours (discrete) & \cite{Pepik12} + Ours (full) & R-CNN + Ours (discrete) & R-CNN + Ours (full)\\
-\hline\hline
-car-4v              & 37.2 / 20.2         & 45.6 / 36.9             & 47.6 / 42.7       & 47.6 / \textbf{42.7}        & 49.6 / 41.5         & 49.6 / 41.5\\ \hline
-car-8v              & 37.3 / 23.5         & 47.6 / 36.6             & 47.6 / \textbf{39.8}       & 47.6 / 39.5        & 49.6 / 38.0         & 49.6 / 39.0\\ \hline
-car-16v             & 36.6 / 18.1         & 46.0 / 29.6             & 47.6 / 32.7       & 47.6 / 33.0        & 49.6 / 34.0         & 49.6 / \textbf{34.3}\\ \hline
-car-24v             & 36.3 / 13.7         & 42.1 / 24.6             & 47.6 / 27.4       & 47.6 / 27.4        & 49.6 / 27.0         & 49.6 / \textbf{27.6}\\ \hline
-\hline
-bicycle-4v          & 45.2 / 41.7         & 46.9 / 43.9             & 48.1 / 47.6       & 48.1 / 46.6        & 61.7 / 56.5         & 61.7 / \textbf{56.7}\\ \hline
-bicycle-8v          & 47.3 / 36.7         & 48.1 / 40.3             & 48.1 / 40.6       & 48.1 / 40.6        & 61.7 / 48.9         & 61.7 / \textbf{49.2}\\ \hline
-bicycle-16v         & 46.5 / 18.4         & 45.6 / 22.9             & 48.1 / 26.2       & 40.1 / 27.3        & 61.7 / 34.7         & 61.7 / \textbf{35.8}\\ \hline
-bicycle-24v         & 44.4 / 14.3         & 45.9 / 16.7             & 48.1 / 21.5       & 40.1 / 20.9        & 61.7 / \textbf{27.0}         & 61.7 / 23.9\\ \hline
-\end{tabular}
-\end{center}
-\caption{Average Precision(AP) and Average Viewpoint Precision(AVP) on PASCAL 3D dataset\cite{Xiang14}.
-For combined method (* + Ours), we use bounding boxes from * and augment viewpoint using our method.
-R-CNN and run our method to produce 2D-3D matching.
-If our method fails to give viewpoint, it predicts the viewpoint to be 0.
-Note that our method gives high quality metadata such as continuous 3D viewpoint, CAD model (rendering depth) and fine-grained category, whereas base-line methods gives 1D discrete azimuths.
-Our R-CNN was not an optimized version so the detection AP is lower than the state-of-the-art R-CNN performance}
-\label{tab:pascal12}
-\end{table*}
-
-\begin{figure}[h]
-\setlength\tabcolsep{1pt}
-\centering
-\begin{tabular}{cc}
-  \hline
-  \includegraphics[width=0.49\linewidth]{car_cnn4_crop.png} &   
-  \includegraphics[width=0.49\linewidth]{car_cnn8_crop.png} \\   
-  \includegraphics[width=0.49\linewidth]{car_cnn16_crop.png} &   
-  \includegraphics[width=0.49\linewidth]{car_cnn24_crop.png} \\   
-  \hline
-\end{tabular}
-\caption{Average Precision (AP) and Average Viewpoint Precision (AVP) and viewpoint confusion table on PASCAL 12 car validation set using R-CNN + Ours.
-From the top left, 4 views, 8 views, 16 views and 24 views.
-Since our method only augment the object detection, the AP remains the same for all cases.
-As we increase the viewpoint estimation, the AVP decreases.
-Note that since we estimate null viewpoint if our method fails to find match, there are more 0 viewpoint predictions (top row of confusion matrices) }
-  \label{fig:car_cnn_ap}
-\end{figure}
-
-\subsection{Stability of Our Method for Irregular Bounding Boxes}
-
-% Generic object detectors give overlapping detection bounding boxes of the same object which can be handled by non maximal suppression. For these overlapping detections,
-
-R-CNN detection bounding boxes are irregular in shape since they come from other region proposal methods and sometimes they truncate objects.
-To handle such irregular shape and truncation, we added small context around the bounding boxes and run our method.
-
-We assumed that object can be arbitrarily truncated by the bounding box and search all plausible scales and translations.
-This can be efficiently computed using FFT-based convolution (refer Section.
-\ref{sec:fft}).
-We put examples of such conditions in Figure \ref{fig:stability}.
-Although the input bounding boxes are irregular and truncate objects, our method reliably generated a reasonable prediction of pose, translation, scale and CAD model.
-
-\begin{figure}[h]
-\setlength\tabcolsep{5pt}
-\begin{tabular}{cc}
-  \includegraphics[width=0.45\linewidth]{car_pascal/1.png} &   
-  \includegraphics[width=0.45\linewidth]{car_pascal/2.png} \\   
-  \includegraphics[width=0.45\linewidth]{car_pascal/3.png} &   
-  \includegraphics[width=0.45\linewidth]{car_pascal/4.png} \\   
-\end{tabular}
-\caption{Stability of our method for overlapping R-CNN detection \cite{Girshick14}.
-Blue box is the R-CNN detection that is feed into the system as initial detection.
-Purple box and overlaid rendering is the final output of the system.
-Note that for various overlapping bounding boxes, our system accurately estimated the reasonable result}
-  \label{fig:stability}
-\end{figure}
-
-% For qualitative examples, we put hand-picked results from our method Fig. \ref{fig:car} and Fig. \ref{fig:bicycle}.
-
-% \begin{figure*}[h]
-% \setlength\tabcolsep{5pt}
-% \begin{tabular}{|c|c|c|}
-%     \hline
-%   \includegraphics[width=0.325\textwidth]{car/PASCAL_car_val_init_0_Car_each_27_lim_250_lam_0_150_a_24_e_3_y_1_f_1_scale_2_00_sbin_6_level_15_skp_n_server_101_img_39.jpg} &   
-%   \includegraphics[width=0.325\textwidth]{car/PASCAL_car_val_init_0_Car_each_27_lim_250_lam_0_150_a_24_e_3_y_1_f_1_scale_2_00_sbin_6_level_15_skp_n_server_101_img_78.jpg} & 
-%   \includegraphics[width=0.325\textwidth]{car/PASCAL_car_val_init_0_Car_each_27_lim_250_lam_0_150_a_24_e_3_y_1_f_1_scale_2_00_sbin_6_level_15_skp_n_server_101_img_85.jpg} \\[-15pt]
-% (a) & (b) & (c) \\[0pt]
-% \hline
-%   \includegraphics[width=0.325\textwidth]{car/PASCAL_car_val_init_0_Car_each_27_lim_250_lam_0_150_a_24_e_3_y_1_f_1_scale_2_00_sbin_6_level_15_skp_n_server_101_img_338.jpg} &   
-%   \includegraphics[width=0.325\textwidth]{car/PASCAL_car_val_init_0_Car_each_27_lim_250_lam_0_150_a_24_e_3_y_1_f_1_scale_2_00_sbin_6_level_15_skp_n_server_101_img_360.jpg} & 
-%   \includegraphics[width=0.325\textwidth]{car/PASCAL_car_val_init_0_Car_each_27_lim_250_lam_0_150_a_24_e_3_y_1_f_1_scale_2_00_sbin_6_level_15_skp_n_server_101_img_414.jpg} \\[-15pt]
-% (d) & (e) & (f) \\[0pt]
-% \hline
-%   \includegraphics[width=0.325\textwidth]{car/PASCAL_car_val_init_0_Car_each_27_lim_250_lam_0_150_a_24_e_3_y_1_f_1_scale_2_00_sbin_6_level_15_skp_n_server_101_img_418.jpg} &   
-%   \includegraphics[width=0.325\textwidth]{car/PASCAL_car_val_init_0_Car_each_27_lim_250_lam_0_150_a_24_e_3_y_1_f_1_scale_2_00_sbin_6_level_15_skp_n_server_101_img_1049.jpg} & 
-%   \includegraphics[width=0.325\textwidth]{car/PASCAL_car_val_init_0_Car_each_27_lim_250_lam_0_150_a_24_e_3_y_1_f_1_scale_2_00_sbin_6_level_15_skp_n_server_101_img_1242.jpg} \\[-15pt]
-% (g) & (h) & (i) \\[0pt]
-% \hline
-%   \includegraphics[width=0.325\textwidth]{car/PASCAL_car_val_init_0_Car_each_27_lim_250_lam_0_150_a_24_e_3_y_1_f_1_scale_2_00_sbin_6_level_15_skp_n_server_101_img_1244.jpg} &   
-%   \includegraphics[width=0.325\textwidth]{car/PASCAL_car_val_init_0_Car_each_27_lim_250_lam_0_150_a_24_e_3_y_1_f_1_scale_2_00_sbin_6_level_15_skp_n_server_101_img_1261.jpg} & 
-%   \includegraphics[width=0.325\textwidth]{car/PASCAL_car_val_init_0_Car_each_27_lim_250_lam_0_150_a_24_e_3_y_1_f_1_scale_2_00_sbin_6_level_15_skp_n_server_101_img_1452.jpg} \\[-15pt]
-% (j) & (k) & (l) \\[0pt]
-% \hline
-%   \includegraphics[width=0.325\textwidth]{car/PASCAL_car_val_init_0_Car_each_27_lim_250_lam_0_150_a_24_e_3_y_1_f_1_scale_2_00_sbin_6_level_15_skp_n_server_101_img_1467.jpg} &   
-%   \includegraphics[width=0.325\textwidth]{car/PASCAL_car_val_init_0_Car_each_27_lim_250_lam_0_150_a_24_e_3_y_1_f_1_scale_2_00_sbin_6_level_15_skp_n_server_101_img_1553.jpg} & 
-%   \includegraphics[width=0.325\textwidth]{car/PASCAL_car_val_init_0_Car_each_27_lim_250_lam_0_150_a_24_e_3_y_1_f_1_scale_2_00_sbin_6_level_15_skp_n_server_101_img_1597.jpg} \\[-15pt]
-% (m) & (n) & (o) \\[3pt]
-% \hline
-% \end{tabular}
-%   \caption{Selected detections from PASCAL 07 Car categories.
-From the left, (1) original image, (2) overlaid true positive CAD models, (3) overlaid true positive CAD models with bounding boxes, (4) overlaid false positive CAD models with bounding boxes.
-Bounding box is colored from red (high confidence) to blue (low confidence) }
-%   \label{fig:car}
-% \end{figure*}
-% \begin{figure*}[h]
-% \setlength\tabcolsep{5pt}
-% \begin{tabular}{|c|c|c|}
-%     \hline
-%   \includegraphics[width=0.325\textwidth]{bicycle/PASCAL_bicycle_val_init_0_Bicycle_each_4_lim_250_lam_0_150_a_48_e_4_y_5_f_1_scale_2_00_sbin_6_level_15_skp_n_server_102_img_459.jpg} &   
-%   \includegraphics[width=0.325\textwidth]{bicycle/PASCAL_bicycle_val_init_0_Bicycle_each_4_lim_250_lam_0_150_a_48_e_4_y_5_f_1_scale_2_00_sbin_6_level_15_skp_n_server_102_img_1300.jpg} &   
-%   \includegraphics[width=0.325\textwidth]{bicycle/PASCAL_bicycle_val_init_0_Bicycle_each_4_lim_250_lam_0_150_a_48_e_4_y_5_f_1_scale_2_00_sbin_6_level_15_skp_n_server_102_img_539.jpg} \\[-15pt]
-% (a) & (b) & (c) \\[0pt]
-% \hline
-%   \includegraphics[width=0.325\textwidth]{bicycle/PASCAL_bicycle_val_init_0_Bicycle_each_4_lim_250_lam_0_150_a_48_e_4_y_5_f_1_scale_2_00_sbin_6_level_15_skp_n_server_102_img_35.jpg} &   
-%   \includegraphics[width=0.325\textwidth]{bicycle/PASCAL_bicycle_val_init_0_Bicycle_each_4_lim_250_lam_0_150_a_48_e_4_y_5_f_1_scale_2_00_sbin_6_level_15_skp_n_server_102_img_83.jpg} &   
-%   \includegraphics[width=0.325\textwidth]{bicycle/PASCAL_bicycle_val_init_0_Bicycle_each_4_lim_250_lam_0_150_a_48_e_4_y_5_f_1_scale_2_00_sbin_6_level_15_skp_n_server_102_img_131.jpg} \\[-15pt]
-% (d) & (e) & (f) \\[0pt]
-% \hline
-%   \includegraphics[width=0.325\textwidth]{bicycle/PASCAL_bicycle_val_init_0_Bicycle_each_4_lim_250_lam_0_150_a_48_e_4_y_5_f_1_scale_2_00_sbin_6_level_15_skp_n_server_102_img_175.jpg} &   
-%   \includegraphics[width=0.325\textwidth]{bicycle/PASCAL_bicycle_val_init_0_Bicycle_each_4_lim_250_lam_0_150_a_48_e_4_y_5_f_1_scale_2_00_sbin_6_level_15_skp_n_server_102_img_210.jpg} &   
-%   \includegraphics[width=0.325\textwidth]{bicycle/PASCAL_bicycle_val_init_0_Bicycle_each_4_lim_250_lam_0_150_a_48_e_4_y_5_f_1_scale_2_00_sbin_6_level_15_skp_n_server_102_img_233.jpg} \\[-15pt]
-% (g) & (h) & (i) \\[0pt]
-% \hline
-%   \includegraphics[width=0.325\textwidth]{bicycle/PASCAL_bicycle_val_init_0_Bicycle_each_4_lim_250_lam_0_150_a_48_e_4_y_5_f_1_scale_2_00_sbin_6_level_15_skp_n_server_102_img_322.jpg} &   
-%   \includegraphics[width=0.325\textwidth]{bicycle/PASCAL_bicycle_val_init_0_Bicycle_each_4_lim_250_lam_0_150_a_48_e_4_y_5_f_1_scale_2_00_sbin_6_level_15_skp_n_server_102_img_348.jpg} &   
-%   \includegraphics[width=0.325\textwidth]{bicycle/PASCAL_bicycle_val_init_0_Bicycle_each_4_lim_250_lam_0_150_a_48_e_4_y_5_f_1_scale_2_00_sbin_6_level_15_skp_n_server_102_img_375.jpg} \\[-15pt]
-% (j) & (k) & (l) \\[0pt]
-% \hline
-%   \includegraphics[width=0.325\textwidth]{bicycle/PASCAL_bicycle_val_init_0_Bicycle_each_4_lim_250_lam_0_150_a_48_e_4_y_5_f_1_scale_2_00_sbin_6_level_15_skp_n_server_102_img_400.jpg} &   
-%   \includegraphics[width=0.325\textwidth]{bicycle/PASCAL_bicycle_val_init_0_Bicycle_each_4_lim_250_lam_0_150_a_48_e_4_y_5_f_1_scale_2_00_sbin_6_level_15_skp_n_server_102_img_434.jpg} &   
-%   \includegraphics[width=0.325\textwidth]{bicycle/PASCAL_bicycle_val_init_0_Bicycle_each_4_lim_250_lam_0_150_a_48_e_4_y_5_f_1_scale_2_00_sbin_6_level_15_skp_n_server_102_img_459.jpg} \\[-15pt]
-% (m) & (n) & (o) \\[3pt]
-% \hline
-% \end{tabular}
-%   \caption{Selected detections from PASCAL 12 Bike categories.
-From the left, (1) original image, (2) overlaid true positive CAD models, (3) overlaid true positive CAD models with bounding boxes, (4) overlaid false positive CAD models with bounding boxes.
-Bounding box is colored from red (high confidence) to blue (low confidence) }
-%   \label{fig:bicycle}
-% \end{figure*}
-
-% \section{Object Detection with various Training Data}
-% \section{Image Query}
+\label{sec:experiments}
+\input{experiments}
 

### 2014-11-14 experiments.tex

%
In this section, we validate our proposed NZ-WHO templates in two different ways. First, we make a set of NZ-WHO templates for a set of CAD models from various viewpoints. Then we run the bank of NZ-WHO templates as ensembles of weak detectors and show that the rendering image can be We want to see how robust the NZ-WHO to real images a

Second, we show that our method can complement the detection bounding boxes coming out of standard object detectors. This process will enrich object detection bounding boxes with 2D-3D matching which gives continuous viewpoint estimation, a CAD model (rendering, depth) and fine-grained category.

\subsection{2D-3D Matching as an Object Detector}

We created ensemble of NZ-WHO templates using 9 CAD models and measured the Average Precision (AP) of object detection task and Mean Precision in Pose Estimation (MPPE) \cite{Lopez-Sastre11}. MPPE is the average of viewpoint accuracy.

% Instance-level 2D-3D matching (registration) is a difficult problem since we need a CAD model that looks similar to the object in the image. Especially, due to extreme intraclass variability of chair \cite{Aubry14} used a very large collection of CAD models to cover variety of chairs. Similarly, \cite{Lim14}

Our ensemble of NZ-WHO templates is generated from rendering images within few minutes but shows reasonable performance on object detection task. The baseline method are Aspect Layout Model (ALM) \cite{Xiang12} and VOC-DPM \cite{Pepik12}. Note that the baseline methods require complex 3D modeling and viewpoint annotated natural images.

The detection result is on Table \ref{tab:3dobject} and example output from our method is on Figure \ref{fig:3dobject}.

\begin{table}[!htbp]
    \footnotesize
  \begin{center}
    \begin{tabular}{|c|c|c|c|}
    \hline
     AP/MPPE& Ours & ALM\cite{Xiang12} & VOC-DPM\cite{Pepik12} \\
    \hline\hline
    car & \textbf{99.8}/91.7 &  98.4/93.4 & \textbf{99.8}/\textbf{97.5} \\ 
    bicycle & 93.0/87.4 & 93.0/91.4 & \textbf{98.8}/\textbf{97.5} \\
    \hline
    \end{tabular}
  \end{center}
  \caption{Average Precision(AP) and Mean Precision in Pose Estimation (MPPE) on 3DObject dataset car category. Our method produces high quality 2D-3D matching yet performs on par with state-of-the art detectors.}
  \label{tab:3dobject}
\end{table}

\begin{figure}[h]
    \begin{center}
    \setlength\tabcolsep{0pt}
\begin{tabular}{cc}
  \includegraphics[width=0.45\linewidth]{car_3dobject/7.png} &   
  \includegraphics[width=0.45\linewidth]{car_3dobject/8.png}\\ [-15pt]
%   (a) & (b) \\[0pt]
  \includegraphics[width=0.45\linewidth]{car_3dobject/11.png} &   
  \includegraphics[width=0.45\linewidth]{car_3dobject/12.png}\\ [-5pt]
%  (c) & (d) \\[0pt]
\end{tabular}
\end{center}
\caption{Detection results on 3D-Object dataset \cite{Savarese07}. Original image (left) and detection result overlaid on top with a bounding box and corresponding confidence score(right)}
  \label{fig:3dobject}
\end{figure}

% Also, we evaluated our method on PASCAL 2007 dataset.
% 
% \begin{table}[!htbp]
%   \begin{center}
%   \begin{tabular}{|c|c|c|c|c|}
%     \hline
%      AP &    Ours &    ELDA \cite{Hariharan12} & ESVM \cite{Malisiewicz11} & VOCDPM \cite{Pepik12} \\
%     \hline\hline
%     car      & 27.          &  38.4  & 40.1    &65.7  \\ 
%     bicycle  & 43.74 & 41      &  40.7   & 61.3   \\
%     \hline
%     \end{tabular}
%   \end{center}
%   \caption{Average Precision(AP) on PASCAL 2007 dataset. Though we do not need any training images and made templates in few minues, it performs on par with state of the art detector yet it gives high quality 2D-3D matching.}
%   \label{tab:pascal07}
% \end{table}

\subsection{Fine-Tuning and Viewpoint Estimation}

High performance object detectors usually generalizes very well. It can handle various intraclass variability, viewpoint change and occlusion. However due to this high generalization, sometimes it is very difficult to get accurate pose, category or 2D-3D matching. Our method, specialized in giving such accurate information, can be applied on any generic object detectors to give high quality metadata.

To show such ability, we evaluated our method on PASCAL 3D dataset \cite{Xiang14}. The dataset augments PASCAL 2012 images with high quality viewpoint annotations thus is ideal to measure pose estimation. The dataset proposes new metric called Average Viewpoint Precision (AVP) where it measures the area under viewpoint precision and detection recall curve. The viewpoints is measured by azimuth similarity. If the distance between predicted azimuth and ground truth azimuth is below a certain threshold, the viewpoint is correct. Note that the baseline methods (V-DPM, VOC-DPM) reported on the PASCAL 3D dataset are variants of DPM where each component of DPM account for various azimuths. Thus V-DPM and VOC-DPM provide discrete azimuth only whereas our method provides 3D viewpoint (yaw, pitch, roll), CAD instance (model index, rendering, depth) and focal length.

We used detection bounding boxes and augment it using our method to give viewpoint estimation. We used detection bounding boxes from two different methods: VOC-DPM \cite{Pepik12} and R-CNN \cite{Girshick14}. VOC-DPM is a variation of DPM that can estimate viewpoint and is the state-of-the-art performance in viewpoint estimation \cite{Xiang14}. The result is on Table \ref{tab:pascal12} and precision recall curves for car using R-CNN + Ours are on Figure \ref{fig:car_cnn_ap}.

We got significant improvement on viewpoint estimation by using our method on top of general purpose detectors. Note that our method estimates azimuth, elevation, in-plane rotation, focal length estimation, fine-grained categorization whereas V-DPM, VOC-DPM only estimate discrete viewpoints.

Example outputs are on Figure \ref{fig:pascal12cnn}.

\begin{figure*}[h]
\setlength\tabcolsep{1pt}
\centering
\begin{tabular}{|c|c|c|c|c|}
   \hline
  \includegraphics[width=0.24\textwidth]{car_cnn/1a.png} &   
  \includegraphics[width=0.24\textwidth]{car_cnn/1b.png} &   
  \includegraphics[width=0.24\textwidth]{car_cnn/1c.png} &   
  \includegraphics[width=0.24\textwidth]{car_cnn/1d.png}  \\  
   \hline
  \includegraphics[width=0.24\textwidth]{car_cnn/2a.png} &   
  \includegraphics[width=0.24\textwidth]{car_cnn/2b.png} &   
  \includegraphics[width=0.24\textwidth]{car_cnn/2c.png} &   
  \includegraphics[width=0.24\textwidth]{car_cnn/2e.png}  \\  
   \hline
  \includegraphics[width=0.24\textwidth]{car_cnn/4a.png} &   
  \includegraphics[width=0.24\textwidth]{car_cnn/4b.png} &   
  \includegraphics[width=0.24\textwidth]{car_cnn/4c.png} &   
  \includegraphics[width=0.24\textwidth]{car_cnn/4d.png}  \\  
%    \hline
%   \includegraphics[width=0.24\textwidth]{car_cnn/10a.png} &   
%   \includegraphics[width=0.24\textwidth]{car_cnn/10b.png} &   
%   \includegraphics[width=0.24\textwidth]{car_cnn/10c.png} &   
%   \includegraphics[width=0.24\textwidth]{car_cnn/10d.png}  \\  
%   \hline 
%   \includegraphics[width=0.24\textwidth]{bicycle_cnn/3a.png} &   
%   \includegraphics[width=0.24\textwidth]{bicycle_cnn/3b.png} &   
%   \includegraphics[width=0.24\textwidth]{bicycle_cnn/3c.png} &   
%   \includegraphics[width=0.24\textwidth]{bicycle_cnn/3d.png}  \\
  \hline
  \includegraphics[width=0.24\textwidth]{bicycle_cnn/7a.png} &   
  \includegraphics[width=0.24\textwidth]{bicycle_cnn/7b.png} &   
  &\\
  \hline
  \includegraphics[width=0.24\textwidth]{bicycle_cnn/4a.png} &   
  \includegraphics[width=0.24\textwidth]{bicycle_cnn/4b.png} &   
  \includegraphics[width=0.24\textwidth]{bicycle_cnn/4c.png} &   
  \includegraphics[width=0.24\textwidth]{bicycle_cnn/4d.png}  \\
  \hline
  CNN Proposals & \multicolumn{3}{|c|}{Our matching results on proposal bounding boxes} \\
  \hline
\end{tabular}
\caption{Example enriched bounding boxes. Given R-CNN\cite{Girshick14} detection bounding boxes, our method predicted 2D-3D matching reasonably. On the first column, R-CNN detection bounding boxes overlaid. From the second to the last columns, output of our method given a R-CNN box. Blue boxes are R-CNN output and purple boxes are the tightest bounding box enclosing predicted CAD model}
  \label{fig:pascal12cnn}
\end{figure*}
\begin{table*}[!htbp]
    \footnotesize
  \begin{center}
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline
AP/AVP              & V-DPM \cite{Xiang14} & VOC-DPM \cite{Pepik12}  & \cite{Pepik12} + Ours (discrete) & \cite{Pepik12} + Ours (full) & R-CNN + Ours (discrete) & R-CNN + Ours (full)\\
\hline\hline
car-4v              & 37.2 / 20.2         & 45.6 / 36.9             & 47.6 / 42.7       & 47.6 / \textbf{42.7}        & 49.6 / 41.5         & 49.6 / 41.5\\ \hline
car-8v              & 37.3 / 23.5         & 47.6 / 36.6             & 47.6 / \textbf{39.8}       & 47.6 / 39.5        & 49.6 / 38.0         & 49.6 / 39.0\\ \hline
car-16v             & 36.6 / 18.1         & 46.0 / 29.6             & 47.6 / 32.7       & 47.6 / 33.0        & 49.6 / 34.0         & 49.6 / \textbf{34.3}\\ \hline
car-24v             & 36.3 / 13.7         & 42.1 / 24.6             & 47.6 / 27.4       & 47.6 / 27.4        & 49.6 / 27.0         & 49.6 / \textbf{27.6}\\ \hline
\hline
bicycle-4v          & 45.2 / 41.7         & 46.9 / 43.9             & 48.1 / 47.6       & 48.1 / 46.6        & 61.7 / 56.5         & 61.7 / \textbf{56.7}\\ \hline
bicycle-8v          & 47.3 / 36.7         & 48.1 / 40.3             & 48.1 / 40.6       & 48.1 / 40.6        & 61.7 / 48.9         & 61.7 / \textbf{49.2}\\ \hline
bicycle-16v         & 46.5 / 18.4         & 45.6 / 22.9             & 48.1 / 26.2       & 40.1 / 27.3        & 61.7 / 34.7         & 61.7 / \textbf{35.8}\\ \hline
bicycle-24v         & 44.4 / 14.3         & 45.9 / 16.7             & 48.1 / 21.5       & 40.1 / 20.9        & 61.7 / \textbf{27.0}         & 61.7 / 23.9\\ \hline
\end{tabular}
\end{center}
\caption{Average Precision(AP) and Average Viewpoint Precision(AVP) on PASCAL 3D dataset\cite{Xiang14}. For combined method (* + Ours), we use bounding boxes from * and augment viewpoint using our method. R-CNN and run our method to produce 2D-3D matching. If our method fails to give viewpoint, it predicts the viewpoint to be 0. Note that our method gives high quality metadata such as continuous 3D viewpoint, CAD model (rendering depth) and fine-grained category, whereas base-line methods gives 1D discrete azimuths. Our R-CNN was not an optimized version so the detection AP is lower than the state-of-the-art R-CNN performance}
\label{tab:pascal12}
\end{table*}

\begin{figure}[h]
\setlength\tabcolsep{1pt}
\centering
\begin{tabular}{cc}
  \hline
  \includegraphics[width=0.49\linewidth]{car_cnn4_crop.png} &   
  \includegraphics[width=0.49\linewidth]{car_cnn8_crop.png} \\   
  \includegraphics[width=0.49\linewidth]{car_cnn16_crop.png} &   
  \includegraphics[width=0.49\linewidth]{car_cnn24_crop.png} \\   
  \hline
\end{tabular}
\caption{Average Precision (AP) and Average Viewpoint Precision (AVP) and viewpoint confusion table on PASCAL 12 car validation set using R-CNN + Ours. From the top left, 4 views, 8 views, 16 views and 24 views. Since our method only augment the object detection, the AP remains the same for all cases. As we increase the viewpoint estimation, the AVP decreases. Note that since we estimate null viewpoint if our method fails to find match, there are more 0 viewpoint predictions (top row of confusion matrices) }
  \label{fig:car_cnn_ap}
\end{figure}

\subsection{Stability of Our Method for Irregular Bounding Boxes}

% Generic object detectors give overlapping detection bounding boxes of the same object which can be handled by non maximal suppression. For these overlapping detections,

R-CNN detection bounding boxes are irregular in shape since they come from other region proposal methods and sometimes they truncate objects. To handle such irregular shape and truncation, we added small context around the bounding boxes and run our method.

We assumed that object can be arbitrarily truncated by the bounding box and search all plausible scales and translations. This can be efficiently computed using FFT-based convolution (refer Section. \ref{sec:fft}). We put examples of such conditions in Figure \ref{fig:stability}. Although the input bounding boxes are irregular and truncate objects, our method reliably generated a reasonable prediction of pose, translation, scale and CAD model.

\begin{figure}[h]
\setlength\tabcolsep{5pt}
\begin{tabular}{cc}
  \includegraphics[width=0.45\linewidth]{car_pascal/1.png} &   
  \includegraphics[width=0.45\linewidth]{car_pascal/2.png} \\   
  \includegraphics[width=0.45\linewidth]{car_pascal/3.png} &   
  \includegraphics[width=0.45\linewidth]{car_pascal/4.png} \\   
\end{tabular}
\caption{Stability of our method for overlapping R-CNN detection \cite{Girshick14}. Blue box is the R-CNN detection that is feed into the system as initial detection. Purple box and overlaid rendering is the final output of the system. Note that for various overlapping bounding boxes, our system accurately estimated the reasonable result}
  \label{fig:stability}
\end{figure}

% For qualitative examples, we put hand-picked results from our method Fig. \ref{fig:car} and Fig. \ref{fig:bicycle}.

% \begin{figure*}[h]
% \setlength\tabcolsep{5pt}
% \begin{tabular}{|c|c|c|}
%     \hline
%   \includegraphics[width=0.325\textwidth]{car/PASCAL_car_val_init_0_Car_each_27_lim_250_lam_0_150_a_24_e_3_y_1_f_1_scale_2_00_sbin_6_level_15_skp_n_server_101_img_39.jpg} &   
%   \includegraphics[width=0.325\textwidth]{car/PASCAL_car_val_init_0_Car_each_27_lim_250_lam_0_150_a_24_e_3_y_1_f_1_scale_2_00_sbin_6_level_15_skp_n_server_101_img_78.jpg} & 
%   \includegraphics[width=0.325\textwidth]{car/PASCAL_car_val_init_0_Car_each_27_lim_250_lam_0_150_a_24_e_3_y_1_f_1_scale_2_00_sbin_6_level_15_skp_n_server_101_img_85.jpg} \\[-15pt]
% (a) & (b) & (c) \\[0pt]
% \hline
%   \includegraphics[width=0.325\textwidth]{car/PASCAL_car_val_init_0_Car_each_27_lim_250_lam_0_150_a_24_e_3_y_1_f_1_scale_2_00_sbin_6_level_15_skp_n_server_101_img_338.jpg} &   
%   \includegraphics[width=0.325\textwidth]{car/PASCAL_car_val_init_0_Car_each_27_lim_250_lam_0_150_a_24_e_3_y_1_f_1_scale_2_00_sbin_6_level_15_skp_n_server_101_img_360.jpg} & 
%   \includegraphics[width=0.325\textwidth]{car/PASCAL_car_val_init_0_Car_each_27_lim_250_lam_0_150_a_24_e_3_y_1_f_1_scale_2_00_sbin_6_level_15_skp_n_server_101_img_414.jpg} \\[-15pt]
% (d) & (e) & (f) \\[0pt]
% \hline
%   \includegraphics[width=0.325\textwidth]{car/PASCAL_car_val_init_0_Car_each_27_lim_250_lam_0_150_a_24_e_3_y_1_f_1_scale_2_00_sbin_6_level_15_skp_n_server_101_img_418.jpg} &   
%   \includegraphics[width=0.325\textwidth]{car/PASCAL_car_val_init_0_Car_each_27_lim_250_lam_0_150_a_24_e_3_y_1_f_1_scale_2_00_sbin_6_level_15_skp_n_server_101_img_1049.jpg} & 
%   \includegraphics[width=0.325\textwidth]{car/PASCAL_car_val_init_0_Car_each_27_lim_250_lam_0_150_a_24_e_3_y_1_f_1_scale_2_00_sbin_6_level_15_skp_n_server_101_img_1242.jpg} \\[-15pt]
% (g) & (h) & (i) \\[0pt]
% \hline
%   \includegraphics[width=0.325\textwidth]{car/PASCAL_car_val_init_0_Car_each_27_lim_250_lam_0_150_a_24_e_3_y_1_f_1_scale_2_00_sbin_6_level_15_skp_n_server_101_img_1244.jpg} &   
%   \includegraphics[width=0.325\textwidth]{car/PASCAL_car_val_init_0_Car_each_27_lim_250_lam_0_150_a_24_e_3_y_1_f_1_scale_2_00_sbin_6_level_15_skp_n_server_101_img_1261.jpg} & 
%   \includegraphics[width=0.325\textwidth]{car/PASCAL_car_val_init_0_Car_each_27_lim_250_lam_0_150_a_24_e_3_y_1_f_1_scale_2_00_sbin_6_level_15_skp_n_server_101_img_1452.jpg} \\[-15pt]
% (j) & (k) & (l) \\[0pt]
% \hline
%   \includegraphics[width=0.325\textwidth]{car/PASCAL_car_val_init_0_Car_each_27_lim_250_lam_0_150_a_24_e_3_y_1_f_1_scale_2_00_sbin_6_level_15_skp_n_server_101_img_1467.jpg} &   
%   \includegraphics[width=0.325\textwidth]{car/PASCAL_car_val_init_0_Car_each_27_lim_250_lam_0_150_a_24_e_3_y_1_f_1_scale_2_00_sbin_6_level_15_skp_n_server_101_img_1553.jpg} & 
%   \includegraphics[width=0.325\textwidth]{car/PASCAL_car_val_init_0_Car_each_27_lim_250_lam_0_150_a_24_e_3_y_1_f_1_scale_2_00_sbin_6_level_15_skp_n_server_101_img_1597.jpg} \\[-15pt]
% (m) & (n) & (o) \\[3pt]
% \hline
% \end{tabular}
%   \caption{Selected detections from PASCAL 07 Car categories. From the left, (1) original image, (2) overlaid true positive CAD models, (3) overlaid true positive CAD models with bounding boxes, (4) overlaid false positive CAD models with bounding boxes. Bounding box is colored from red (high confidence) to blue (low confidence) }
%   \label{fig:car}
% \end{figure*}
% \begin{figure*}[h]
% \setlength\tabcolsep{5pt}
% \begin{tabular}{|c|c|c|}
%     \hline
%   \includegraphics[width=0.325\textwidth]{bicycle/PASCAL_bicycle_val_init_0_Bicycle_each_4_lim_250_lam_0_150_a_48_e_4_y_5_f_1_scale_2_00_sbin_6_level_15_skp_n_server_102_img_459.jpg} &   
%   \includegraphics[width=0.325\textwidth]{bicycle/PASCAL_bicycle_val_init_0_Bicycle_each_4_lim_250_lam_0_150_a_48_e_4_y_5_f_1_scale_2_00_sbin_6_level_15_skp_n_server_102_img_1300.jpg} &   
%   \includegraphics[width=0.325\textwidth]{bicycle/PASCAL_bicycle_val_init_0_Bicycle_each_4_lim_250_lam_0_150_a_48_e_4_y_5_f_1_scale_2_00_sbin_6_level_15_skp_n_server_102_img_539.jpg} \\[-15pt]
% (a) & (b) & (c) \\[0pt]
% \hline
%   \includegraphics[width=0.325\textwidth]{bicycle/PASCAL_bicycle_val_init_0_Bicycle_each_4_lim_250_lam_0_150_a_48_e_4_y_5_f_1_scale_2_00_sbin_6_level_15_skp_n_server_102_img_35.jpg} &   
%   \includegraphics[width=0.325\textwidth]{bicycle/PASCAL_bicycle_val_init_0_Bicycle_each_4_lim_250_lam_0_150_a_48_e_4_y_5_f_1_scale_2_00_sbin_6_level_15_skp_n_server_102_img_83.jpg} &   
%   \includegraphics[width=0.325\textwidth]{bicycle/PASCAL_bicycle_val_init_0_Bicycle_each_4_lim_250_lam_0_150_a_48_e_4_y_5_f_1_scale_2_00_sbin_6_level_15_skp_n_server_102_img_131.jpg} \\[-15pt]
% (d) & (e) & (f) \\[0pt]
% \hline
%   \includegraphics[width=0.325\textwidth]{bicycle/PASCAL_bicycle_val_init_0_Bicycle_each_4_lim_250_lam_0_150_a_48_e_4_y_5_f_1_scale_2_00_sbin_6_level_15_skp_n_server_102_img_175.jpg} &   
%   \includegraphics[width=0.325\textwidth]{bicycle/PASCAL_bicycle_val_init_0_Bicycle_each_4_lim_250_lam_0_150_a_48_e_4_y_5_f_1_scale_2_00_sbin_6_level_15_skp_n_server_102_img_210.jpg} &   
%   \includegraphics[width=0.325\textwidth]{bicycle/PASCAL_bicycle_val_init_0_Bicycle_each_4_lim_250_lam_0_150_a_48_e_4_y_5_f_1_scale_2_00_sbin_6_level_15_skp_n_server_102_img_233.jpg} \\[-15pt]
% (g) & (h) & (i) \\[0pt]
% \hline
%   \includegraphics[width=0.325\textwidth]{bicycle/PASCAL_bicycle_val_init_0_Bicycle_each_4_lim_250_lam_0_150_a_48_e_4_y_5_f_1_scale_2_00_sbin_6_level_15_skp_n_server_102_img_322.jpg} &   
%   \includegraphics[width=0.325\textwidth]{bicycle/PASCAL_bicycle_val_init_0_Bicycle_each_4_lim_250_lam_0_150_a_48_e_4_y_5_f_1_scale_2_00_sbin_6_level_15_skp_n_server_102_img_348.jpg} &   
%   \includegraphics[width=0.325\textwidth]{bicycle/PASCAL_bicycle_val_init_0_Bicycle_each_4_lim_250_lam_0_150_a_48_e_4_y_5_f_1_scale_2_00_sbin_6_level_15_skp_n_server_102_img_375.jpg} \\[-15pt]
% (j) & (k) & (l) \\[0pt]
% \hline
%   \includegraphics[width=0.325\textwidth]{bicycle/PASCAL_bicycle_val_init_0_Bicycle_each_4_lim_250_lam_0_150_a_48_e_4_y_5_f_1_scale_2_00_sbin_6_level_15_skp_n_server_102_img_400.jpg} &   
%   \includegraphics[width=0.325\textwidth]{bicycle/PASCAL_bicycle_val_init_0_Bicycle_each_4_lim_250_lam_0_150_a_48_e_4_y_5_f_1_scale_2_00_sbin_6_level_15_skp_n_server_102_img_434.jpg} &   
%   \includegraphics[width=0.325\textwidth]{bicycle/PASCAL_bicycle_val_init_0_Bicycle_each_4_lim_250_lam_0_150_a_48_e_4_y_5_f_1_scale_2_00_sbin_6_level_15_skp_n_server_102_img_459.jpg} \\[-15pt]
% (m) & (n) & (o) \\[3pt]
% \hline
% \end{tabular}
%   \caption{Selected detections from PASCAL 12 Bike categories. From the left, (1) original image, (2) overlaid true positive CAD models, (3) overlaid true positive CAD models with bounding boxes, (4) overlaid false positive CAD models with bounding boxes. Bounding box is colored from red (high confidence) to blue (low confidence) }
%   \label{fig:bicycle}
% \end{figure*}

% \section{Object Detection with various Training Data}
% \section{Image Query}

### 2014-11-14 egpaper_final.tex
shifted intro around

--- 2014-11-14 egpaper_final.tex
@@
 \label{sec:nz-who}
+
+\subsection{Overview}
+Our method attempts to match CAD models
+
+Our method is in line with \cite{Aubry14, Lim14} in the sense that we
+use only renderings, not real images. However, rather than using fixed
+sized mid-level patches, we use whole objects and make root
+templates. By using root templates, there is no need to learn a
+discriminative patch dictionary or to calibrate the patches and an
+additional inference stage is not required. However, whitening the
+whole template is prohibitive for several reasons. All templates have
+different aspect ratios making it difficult to generate the covariance
+matrix $\Sigma$. Since the root templates are larger than mid-level
+patches, a very large auto-covariance $\Gamma$ is required. Lastly,
+time complexity of decorrelating a template with $n$ cells increases
+as $O(n^3)$, resulting in slow template generation and large residuals
+due to numerical errors accumulated while decomposing the covariance
+matrix $\Sigma$.
+
+To overcome these difficulties, we propose the Non-Zero Whitened
+Histograms of Orientations (NZ-WHO) with iterative Conjugate Gradient to
+generate templates in real time and enrich rectangular boxes with high
+quality 2D-3D matching. The 2D-3D matching provides a CAD model,
+sub-category, rendering, depth, viewpoint and focal length.
+
+Our method can work as a standalone 2D-3D matching algorithm, or even
+as a standalone ensemble of exemplar-based object detectors (Figure
+\ref{fig:front}) but its real power comes from combining generic
+object detectors and complement rectangular bounding boxes. Our method
+is simple in design; is several orders of magnitude faster than
+traditional method; requires only CAD models; does not need neither images nor
+calibration, yet is powerful in giving high-quality metadata. These
+properties make our method ideal for complementing object detections.
+
+To complement detection bounding boxes, we first search possible 2D-3D
+matching by running cached discrete viewpoint templates. Then, for the
+most probable match, we refine the initial matching using Metropolis
+Hastings. Since it requires iterations of proposal and validation, we
+present real time analysis of NZ-WHO template generation to show that
+this can be done on-the-fly. The fine tuning stage process jointly
+optimizes translation, yaw, roll, pitch, scale, and focal length
+continuously and also searches for different CAD models.
 
@@
 
-\section{Continuous Viewpoint and Focal Length Estimation for Fine Tuning}
-
+\section{Estimating Parameters using MCMC}
+\label{sec:fine}
 % Estimating viewpoint continuously to fine tune a initial matching
 The NZ-WHO template matching method we have presented makes template generation and evaluation computationally inexpensive.
+This means we can efficiently explore the parameter space to find the best object pose, scale, model type and camera focal length.
+
+Our method begins by convolving the
+
 Since creating a template and validating the template become computationally inexpensive, making a proposal and validating the proposal to fine tune a 2D-3D matching became affordable.
@@
 \section{Experiments}
-\label{sec:experiments}
-\input{experiments}
+
+In this section, we validate our proposed NZ-WHO templates in two different ways.
+First, we make a set of NZ-WHO templates for a set of CAD models from various viewpoints.
+Then we run the bank of NZ-WHO templates as ensembles of weak detectors and show that the rendering image can be We want to see how robust the NZ-WHO to real images a
+
+Second, we show that our method can complement the detection bounding boxes coming out of standard object detectors.
+This process will enrich object detection bounding boxes with 2D-3D matching which gives continuous viewpoint estimation, a CAD model (rendering, depth) and fine-grained category.
+
+\subsection{2D-3D Matching as an Object Detector}
+
+We created ensemble of NZ-WHO templates using 9 CAD models and measured the Average Precision (AP) of object detection task and Mean Precision in Pose Estimation (MPPE) \cite{Lopez-Sastre11}.
+MPPE is the average of viewpoint accuracy.
+
+% Instance-level 2D-3D matching (registration) is a difficult problem since we need a CAD model that looks similar to the object in the image.
+Especially, due to extreme intraclass variability of chair \cite{Aubry14} used a very large collection of CAD models to cover variety of chairs.
+Similarly, \cite{Lim14}
+
+Our ensemble of NZ-WHO templates is generated from rendering images within few minutes but shows reasonable performance on object detection task.
+The baseline method are Aspect Layout Model (ALM) \cite{Xiang12} and VOC-DPM \cite{Pepik12}.
+Note that the baseline methods require complex 3D modeling and viewpoint annotated natural images.
+
+The detection result is on Table \ref{tab:3dobject} and example output from our method is on Figure \ref{fig:3dobject}.
+
+\begin{table}[!htbp]
+    \footnotesize
+  \begin{center}
+    \begin{tabular}{|c|c|c|c|}
+    \hline
+     AP/MPPE& Ours & ALM\cite{Xiang12} & VOC-DPM\cite{Pepik12} \\
+    \hline\hline
+    car & \textbf{99.8}/91.7 &  98.4/93.4 & \textbf{99.8}/\textbf{97.5} \\ 
+    bicycle & 93.0/87.4 & 93.0/91.4 & \textbf{98.8}/\textbf{97.5} \\
+    \hline
+    \end{tabular}
+  \end{center}
+  \caption{Average Precision(AP) and Mean Precision in Pose Estimation (MPPE) on 3DObject dataset car category.
+Our method produces high quality 2D-3D matching yet performs on par with state-of-the art detectors.}
+  \label{tab:3dobject}
+\end{table}
+
+\begin{figure}[h]
+    \begin{center}
+    \setlength\tabcolsep{0pt}
+\begin{tabular}{cc}
+  \includegraphics[width=0.45\linewidth]{car_3dobject/7.png} &   
+  \includegraphics[width=0.45\linewidth]{car_3dobject/8.png}\\ [-15pt]
+%   (a) & (b) \\[0pt]
+  \includegraphics[width=0.45\linewidth]{car_3dobject/11.png} &   
+  \includegraphics[width=0.45\linewidth]{car_3dobject/12.png}\\ [-5pt]
+%  (c) & (d) \\[0pt]
+\end{tabular}
+\end{center}
+\caption{Detection results on 3D-Object dataset \cite{Savarese07}. Original image (left) and detection result overlaid on top with a bounding box and corresponding confidence score(right)}
+  \label{fig:3dobject}
+\end{figure}
+
+% Also, we evaluated our method on PASCAL 2007 dataset.
+% 
+% \begin{table}[!htbp]
+%   \begin{center}
+%   \begin{tabular}{|c|c|c|c|c|}
+%     \hline
+%      AP &    Ours &    ELDA \cite{Hariharan12} & ESVM \cite{Malisiewicz11} & VOCDPM \cite{Pepik12} \\
+%     \hline\hline
+%     car      & 27.          &  38.4  & 40.1    &65.7  \\ 
+%     bicycle  & 43.74 & 41      &  40.7   & 61.3   \\
+%     \hline
+%     \end{tabular}
+%   \end{center}
+%   \caption{Average Precision(AP) on PASCAL 2007 dataset.
+Though we do not need any training images and made templates in few minues, it performs on par with state of the art detector yet it gives high quality 2D-3D matching.}
+%   \label{tab:pascal07}
+% \end{table}
+
+\subsection{Fine-Tuning and Viewpoint Estimation}
+
+High performance object detectors usually generalizes very well.
+It can handle various intraclass variability, viewpoint change and occlusion.
+However due to this high generalization, sometimes it is very difficult to get accurate pose, category or 2D-3D matching.
+Our method, specialized in giving such accurate information, can be applied on any generic object detectors to give high quality metadata.
+
+To show such ability, we evaluated our method on PASCAL 3D dataset \cite{Xiang14}.
+The dataset augments PASCAL 2012 images with high quality viewpoint annotations thus is ideal to measure pose estimation.
+The dataset proposes new metric called Average Viewpoint Precision (AVP) where it measures the area under viewpoint precision and detection recall curve.
+The viewpoints is measured by azimuth similarity.
+If the distance between predicted azimuth and ground truth azimuth is below a certain threshold, the viewpoint is correct.
+Note that the baseline methods (V-DPM, VOC-DPM) reported on the PASCAL 3D dataset are variants of DPM where each component of DPM account for various azimuths.
+Thus V-DPM and VOC-DPM provide discrete azimuth only whereas our method provides 3D viewpoint (yaw, pitch, roll), CAD instance (model index, rendering, depth) and focal length.
+
+We used detection bounding boxes and augment it using our method to give viewpoint estimation.
+We used detection bounding boxes from two different methods: VOC-DPM \cite{Pepik12} and R-CNN \cite{Girshick14}.
+VOC-DPM is a variation of DPM that can estimate viewpoint and is the state-of-the-art performance in viewpoint estimation \cite{Xiang14}.
+The result is on Table \ref{tab:pascal12} and precision recall curves for car using R-CNN + Ours are on Figure \ref{fig:car_cnn_ap}.
+
+We got significant improvement on viewpoint estimation by using our method on top of general purpose detectors.
+Note that our method estimates azimuth, elevation, in-plane rotation, focal length estimation, fine-grained categorization whereas V-DPM, VOC-DPM only estimate discrete viewpoints.
+
+Example outputs are on Figure \ref{fig:pascal12cnn}.
+
+\begin{figure*}[h]
+\setlength\tabcolsep{1pt}
+\centering
+\begin{tabular}{|c|c|c|c|c|}
+   \hline
+  \includegraphics[width=0.24\textwidth]{car_cnn/1a.png} &   
+  \includegraphics[width=0.24\textwidth]{car_cnn/1b.png} &   
+  \includegraphics[width=0.24\textwidth]{car_cnn/1c.png} &   
+  \includegraphics[width=0.24\textwidth]{car_cnn/1d.png}  \\  
+   \hline
+  \includegraphics[width=0.24\textwidth]{car_cnn/2a.png} &   
+  \includegraphics[width=0.24\textwidth]{car_cnn/2b.png} &   
+  \includegraphics[width=0.24\textwidth]{car_cnn/2c.png} &   
+  \includegraphics[width=0.24\textwidth]{car_cnn/2e.png}  \\  
+   \hline
+  \includegraphics[width=0.24\textwidth]{car_cnn/4a.png} &   
+  \includegraphics[width=0.24\textwidth]{car_cnn/4b.png} &   
+  \includegraphics[width=0.24\textwidth]{car_cnn/4c.png} &   
+  \includegraphics[width=0.24\textwidth]{car_cnn/4d.png}  \\  
+%    \hline
+%   \includegraphics[width=0.24\textwidth]{car_cnn/10a.png} &   
+%   \includegraphics[width=0.24\textwidth]{car_cnn/10b.png} &   
+%   \includegraphics[width=0.24\textwidth]{car_cnn/10c.png} &   
+%   \includegraphics[width=0.24\textwidth]{car_cnn/10d.png}  \\  
+%   \hline 
+%   \includegraphics[width=0.24\textwidth]{bicycle_cnn/3a.png} &   
+%   \includegraphics[width=0.24\textwidth]{bicycle_cnn/3b.png} &   
+%   \includegraphics[width=0.24\textwidth]{bicycle_cnn/3c.png} &   
+%   \includegraphics[width=0.24\textwidth]{bicycle_cnn/3d.png}  \\
+  \hline
+  \includegraphics[width=0.24\textwidth]{bicycle_cnn/7a.png} &   
+  \includegraphics[width=0.24\textwidth]{bicycle_cnn/7b.png} &   
+  &\\
+  \hline
+  \includegraphics[width=0.24\textwidth]{bicycle_cnn/4a.png} &   
+  \includegraphics[width=0.24\textwidth]{bicycle_cnn/4b.png} &   
+  \includegraphics[width=0.24\textwidth]{bicycle_cnn/4c.png} &   
+  \includegraphics[width=0.24\textwidth]{bicycle_cnn/4d.png}  \\
+  \hline
+  CNN Proposals & \multicolumn{3}{|c|}{Our matching results on proposal bounding boxes} \\
+  \hline
+\end{tabular}
+\caption{Example enriched bounding boxes.
+Given R-CNN\cite{Girshick14} detection bounding boxes, our method predicted 2D-3D matching reasonably.
+On the first column, R-CNN detection bounding boxes overlaid.
+From the second to the last columns, output of our method given a R-CNN box.
+Blue boxes are R-CNN output and purple boxes are the tightest bounding box enclosing predicted CAD model}
+  \label{fig:pascal12cnn}
+\end{figure*}
+\begin{table*}[!htbp]
+    \footnotesize
+  \begin{center}
+\begin{tabular}{|c|c|c|c|c|c|c|}
+\hline
+AP/AVP              & V-DPM \cite{Xiang14} & VOC-DPM \cite{Pepik12}  & \cite{Pepik12} + Ours (discrete) & \cite{Pepik12} + Ours (full) & R-CNN + Ours (discrete) & R-CNN + Ours (full)\\
+\hline\hline
+car-4v              & 37.2 / 20.2         & 45.6 / 36.9             & 47.6 / 42.7       & 47.6 / \textbf{42.7}        & 49.6 / 41.5         & 49.6 / 41.5\\ \hline
+car-8v              & 37.3 / 23.5         & 47.6 / 36.6             & 47.6 / \textbf{39.8}       & 47.6 / 39.5        & 49.6 / 38.0         & 49.6 / 39.0\\ \hline
+car-16v             & 36.6 / 18.1         & 46.0 / 29.6             & 47.6 / 32.7       & 47.6 / 33.0        & 49.6 / 34.0         & 49.6 / \textbf{34.3}\\ \hline
+car-24v             & 36.3 / 13.7         & 42.1 / 24.6             & 47.6 / 27.4       & 47.6 / 27.4        & 49.6 / 27.0         & 49.6 / \textbf{27.6}\\ \hline
+\hline
+bicycle-4v          & 45.2 / 41.7         & 46.9 / 43.9             & 48.1 / 47.6       & 48.1 / 46.6        & 61.7 / 56.5         & 61.7 / \textbf{56.7}\\ \hline
+bicycle-8v          & 47.3 / 36.7         & 48.1 / 40.3             & 48.1 / 40.6       & 48.1 / 40.6        & 61.7 / 48.9         & 61.7 / \textbf{49.2}\\ \hline
+bicycle-16v         & 46.5 / 18.4         & 45.6 / 22.9             & 48.1 / 26.2       & 40.1 / 27.3        & 61.7 / 34.7         & 61.7 / \textbf{35.8}\\ \hline
+bicycle-24v         & 44.4 / 14.3         & 45.9 / 16.7             & 48.1 / 21.5       & 40.1 / 20.9        & 61.7 / \textbf{27.0}         & 61.7 / 23.9\\ \hline
+\end{tabular}
+\end{center}
+\caption{Average Precision(AP) and Average Viewpoint Precision(AVP) on PASCAL 3D dataset\cite{Xiang14}.
+For combined method (* + Ours), we use bounding boxes from * and augment viewpoint using our method.
+R-CNN and run our method to produce 2D-3D matching.
+If our method fails to give viewpoint, it predicts the viewpoint to be 0.
+Note that our method gives high quality metadata such as continuous 3D viewpoint, CAD model (rendering depth) and fine-grained category, whereas base-line methods gives 1D discrete azimuths.
+Our R-CNN was not an optimized version so the detection AP is lower than the state-of-the-art R-CNN performance}
+\label{tab:pascal12}
+\end{table*}
+
+\begin{figure}[h]
+\setlength\tabcolsep{1pt}
+\centering
+\begin{tabular}{cc}
+  \hline
+  \includegraphics[width=0.49\linewidth]{car_cnn4_crop.png} &   
+  \includegraphics[width=0.49\linewidth]{car_cnn8_crop.png} \\   
+  \includegraphics[width=0.49\linewidth]{car_cnn16_crop.png} &   
+  \includegraphics[width=0.49\linewidth]{car_cnn24_crop.png} \\   
+  \hline
+\end{tabular}
+\caption{Average Precision (AP) and Average Viewpoint Precision (AVP) and viewpoint confusion table on PASCAL 12 car validation set using R-CNN + Ours.
+From the top left, 4 views, 8 views, 16 views and 24 views.
+Since our method only augment the object detection, the AP remains the same for all cases.
+As we increase the viewpoint estimation, the AVP decreases.
+Note that since we estimate null viewpoint if our method fails to find match, there are more 0 viewpoint predictions (top row of confusion matrices) }
+  \label{fig:car_cnn_ap}
+\end{figure}
+
+\subsection{Stability of Our Method for Irregular Bounding Boxes}
+
+% Generic object detectors give overlapping detection bounding boxes of the same object which can be handled by non maximal suppression. For these overlapping detections,
+
+R-CNN detection bounding boxes are irregular in shape since they come from other region proposal methods and sometimes they truncate objects.
+To handle such irregular shape and truncation, we added small context around the bounding boxes and run our method.
+
+We assumed that object can be arbitrarily truncated by the bounding box and search all plausible scales and translations.
+This can be efficiently computed using FFT-based convolution (refer Section.
+\ref{sec:fft}).
+We put examples of such conditions in Figure \ref{fig:stability}.
+Although the input bounding boxes are irregular and truncate objects, our method reliably generated a reasonable prediction of pose, translation, scale and CAD model.
+
+\begin{figure}[h]
+\setlength\tabcolsep{5pt}
+\begin{tabular}{cc}
+  \includegraphics[width=0.45\linewidth]{car_pascal/1.png} &   
+  \includegraphics[width=0.45\linewidth]{car_pascal/2.png} \\   
+  \includegraphics[width=0.45\linewidth]{car_pascal/3.png} &   
+  \includegraphics[width=0.45\linewidth]{car_pascal/4.png} \\   
+\end{tabular}
+\caption{Stability of our method for overlapping R-CNN detection \cite{Girshick14}.
+Blue box is the R-CNN detection that is feed into the system as initial detection.
+Purple box and overlaid rendering is the final output of the system.
+Note that for various overlapping bounding boxes, our system accurately estimated the reasonable result}
+  \label{fig:stability}
+\end{figure}
+
+% For qualitative examples, we put hand-picked results from our method Fig. \ref{fig:car} and Fig. \ref{fig:bicycle}.
+
+% \begin{figure*}[h]
+% \setlength\tabcolsep{5pt}
+% \begin{tabular}{|c|c|c|}
+%     \hline
+%   \includegraphics[width=0.325\textwidth]{car/PASCAL_car_val_init_0_Car_each_27_lim_250_lam_0_150_a_24_e_3_y_1_f_1_scale_2_00_sbin_6_level_15_skp_n_server_101_img_39.jpg} &   
+%   \includegraphics[width=0.325\textwidth]{car/PASCAL_car_val_init_0_Car_each_27_lim_250_lam_0_150_a_24_e_3_y_1_f_1_scale_2_00_sbin_6_level_15_skp_n_server_101_img_78.jpg} & 
+%   \includegraphics[width=0.325\textwidth]{car/PASCAL_car_val_init_0_Car_each_27_lim_250_lam_0_150_a_24_e_3_y_1_f_1_scale_2_00_sbin_6_level_15_skp_n_server_101_img_85.jpg} \\[-15pt]
+% (a) & (b) & (c) \\[0pt]
+% \hline
+%   \includegraphics[width=0.325\textwidth]{car/PASCAL_car_val_init_0_Car_each_27_lim_250_lam_0_150_a_24_e_3_y_1_f_1_scale_2_00_sbin_6_level_15_skp_n_server_101_img_338.jpg} &   
+%   \includegraphics[width=0.325\textwidth]{car/PASCAL_car_val_init_0_Car_each_27_lim_250_lam_0_150_a_24_e_3_y_1_f_1_scale_2_00_sbin_6_level_15_skp_n_server_101_img_360.jpg} & 
+%   \includegraphics[width=0.325\textwidth]{car/PASCAL_car_val_init_0_Car_each_27_lim_250_lam_0_150_a_24_e_3_y_1_f_1_scale_2_00_sbin_6_level_15_skp_n_server_101_img_414.jpg} \\[-15pt]
+% (d) & (e) & (f) \\[0pt]
+% \hline
+%   \includegraphics[width=0.325\textwidth]{car/PASCAL_car_val_init_0_Car_each_27_lim_250_lam_0_150_a_24_e_3_y_1_f_1_scale_2_00_sbin_6_level_15_skp_n_server_101_img_418.jpg} &   
+%   \includegraphics[width=0.325\textwidth]{car/PASCAL_car_val_init_0_Car_each_27_lim_250_lam_0_150_a_24_e_3_y_1_f_1_scale_2_00_sbin_6_level_15_skp_n_server_101_img_1049.jpg} & 
+%   \includegraphics[width=0.325\textwidth]{car/PASCAL_car_val_init_0_Car_each_27_lim_250_lam_0_150_a_24_e_3_y_1_f_1_scale_2_00_sbin_6_level_15_skp_n_server_101_img_1242.jpg} \\[-15pt]
+% (g) & (h) & (i) \\[0pt]
+% \hline
+%   \includegraphics[width=0.325\textwidth]{car/PASCAL_car_val_init_0_Car_each_27_lim_250_lam_0_150_a_24_e_3_y_1_f_1_scale_2_00_sbin_6_level_15_skp_n_server_101_img_1244.jpg} &   
+%   \includegraphics[width=0.325\textwidth]{car/PASCAL_car_val_init_0_Car_each_27_lim_250_lam_0_150_a_24_e_3_y_1_f_1_scale_2_00_sbin_6_level_15_skp_n_server_101_img_1261.jpg} & 
+%   \includegraphics[width=0.325\textwidth]{car/PASCAL_car_val_init_0_Car_each_27_lim_250_lam_0_150_a_24_e_3_y_1_f_1_scale_2_00_sbin_6_level_15_skp_n_server_101_img_1452.jpg} \\[-15pt]
+% (j) & (k) & (l) \\[0pt]
+% \hline
+%   \includegraphics[width=0.325\textwidth]{car/PASCAL_car_val_init_0_Car_each_27_lim_250_lam_0_150_a_24_e_3_y_1_f_1_scale_2_00_sbin_6_level_15_skp_n_server_101_img_1467.jpg} &   
+%   \includegraphics[width=0.325\textwidth]{car/PASCAL_car_val_init_0_Car_each_27_lim_250_lam_0_150_a_24_e_3_y_1_f_1_scale_2_00_sbin_6_level_15_skp_n_server_101_img_1553.jpg} & 
+%   \includegraphics[width=0.325\textwidth]{car/PASCAL_car_val_init_0_Car_each_27_lim_250_lam_0_150_a_24_e_3_y_1_f_1_scale_2_00_sbin_6_level_15_skp_n_server_101_img_1597.jpg} \\[-15pt]
+% (m) & (n) & (o) \\[3pt]
+% \hline
+% \end{tabular}
+%   \caption{Selected detections from PASCAL 07 Car categories.
+From the left, (1) original image, (2) overlaid true positive CAD models, (3) overlaid true positive CAD models with bounding boxes, (4) overlaid false positive CAD models with bounding boxes.
+Bounding box is colored from red (high confidence) to blue (low confidence) }
+%   \label{fig:car}
+% \end{figure*}
+% \begin{figure*}[h]
+% \setlength\tabcolsep{5pt}
+% \begin{tabular}{|c|c|c|}
+%     \hline
+%   \includegraphics[width=0.325\textwidth]{bicycle/PASCAL_bicycle_val_init_0_Bicycle_each_4_lim_250_lam_0_150_a_48_e_4_y_5_f_1_scale_2_00_sbin_6_level_15_skp_n_server_102_img_459.jpg} &   
+%   \includegraphics[width=0.325\textwidth]{bicycle/PASCAL_bicycle_val_init_0_Bicycle_each_4_lim_250_lam_0_150_a_48_e_4_y_5_f_1_scale_2_00_sbin_6_level_15_skp_n_server_102_img_1300.jpg} &   
+%   \includegraphics[width=0.325\textwidth]{bicycle/PASCAL_bicycle_val_init_0_Bicycle_each_4_lim_250_lam_0_150_a_48_e_4_y_5_f_1_scale_2_00_sbin_6_level_15_skp_n_server_102_img_539.jpg} \\[-15pt]
+% (a) & (b) & (c) \\[0pt]
+% \hline
+%   \includegraphics[width=0.325\textwidth]{bicycle/PASCAL_bicycle_val_init_0_Bicycle_each_4_lim_250_lam_0_150_a_48_e_4_y_5_f_1_scale_2_00_sbin_6_level_15_skp_n_server_102_img_35.jpg} &   
+%   \includegraphics[width=0.325\textwidth]{bicycle/PASCAL_bicycle_val_init_0_Bicycle_each_4_lim_250_lam_0_150_a_48_e_4_y_5_f_1_scale_2_00_sbin_6_level_15_skp_n_server_102_img_83.jpg} &   
+%   \includegraphics[width=0.325\textwidth]{bicycle/PASCAL_bicycle_val_init_0_Bicycle_each_4_lim_250_lam_0_150_a_48_e_4_y_5_f_1_scale_2_00_sbin_6_level_15_skp_n_server_102_img_131.jpg} \\[-15pt]
+% (d) & (e) & (f) \\[0pt]
+% \hline
+%   \includegraphics[width=0.325\textwidth]{bicycle/PASCAL_bicycle_val_init_0_Bicycle_each_4_lim_250_lam_0_150_a_48_e_4_y_5_f_1_scale_2_00_sbin_6_level_15_skp_n_server_102_img_175.jpg} &   
+%   \includegraphics[width=0.325\textwidth]{bicycle/PASCAL_bicycle_val_init_0_Bicycle_each_4_lim_250_lam_0_150_a_48_e_4_y_5_f_1_scale_2_00_sbin_6_level_15_skp_n_server_102_img_210.jpg} &   
+%   \includegraphics[width=0.325\textwidth]{bicycle/PASCAL_bicycle_val_init_0_Bicycle_each_4_lim_250_lam_0_150_a_48_e_4_y_5_f_1_scale_2_00_sbin_6_level_15_skp_n_server_102_img_233.jpg} \\[-15pt]
+% (g) & (h) & (i) \\[0pt]
+% \hline
+%   \includegraphics[width=0.325\textwidth]{bicycle/PASCAL_bicycle_val_init_0_Bicycle_each_4_lim_250_lam_0_150_a_48_e_4_y_5_f_1_scale_2_00_sbin_6_level_15_skp_n_server_102_img_322.jpg} &   
+%   \includegraphics[width=0.325\textwidth]{bicycle/PASCAL_bicycle_val_init_0_Bicycle_each_4_lim_250_lam_0_150_a_48_e_4_y_5_f_1_scale_2_00_sbin_6_level_15_skp_n_server_102_img_348.jpg} &   
+%   \includegraphics[width=0.325\textwidth]{bicycle/PASCAL_bicycle_val_init_0_Bicycle_each_4_lim_250_lam_0_150_a_48_e_4_y_5_f_1_scale_2_00_sbin_6_level_15_skp_n_server_102_img_375.jpg} \\[-15pt]
+% (j) & (k) & (l) \\[0pt]
+% \hline
+%   \includegraphics[width=0.325\textwidth]{bicycle/PASCAL_bicycle_val_init_0_Bicycle_each_4_lim_250_lam_0_150_a_48_e_4_y_5_f_1_scale_2_00_sbin_6_level_15_skp_n_server_102_img_400.jpg} &   
+%   \includegraphics[width=0.325\textwidth]{bicycle/PASCAL_bicycle_val_init_0_Bicycle_each_4_lim_250_lam_0_150_a_48_e_4_y_5_f_1_scale_2_00_sbin_6_level_15_skp_n_server_102_img_434.jpg} &   
+%   \includegraphics[width=0.325\textwidth]{bicycle/PASCAL_bicycle_val_init_0_Bicycle_each_4_lim_250_lam_0_150_a_48_e_4_y_5_f_1_scale_2_00_sbin_6_level_15_skp_n_server_102_img_459.jpg} \\[-15pt]
+% (m) & (n) & (o) \\[3pt]
+% \hline
+% \end{tabular}
+%   \caption{Selected detections from PASCAL 12 Bike categories.
+From the left, (1) original image, (2) overlaid true positive CAD models, (3) overlaid true positive CAD models with bounding boxes, (4) overlaid false positive CAD models with bounding boxes.
+Bounding box is colored from red (high confidence) to blue (low confidence) }
+%   \label{fig:bicycle}
+% \end{figure*}
+
+% \section{Object Detection with various Training Data}
+% \section{Image Query}
 

### 2014-11-14 intro.tex
shifted intro around

@@
 \scream{... to here?}
-
-\subsection{Approach Overview}
-Our method is in line with \cite{Aubry14, Lim14} in the sense that we
-use only renderings, not real images. However, rather than using fixed
-sized mid-level patches, we use whole objects and make root
-templates. By using root templates, there is no need to learn a
-discriminative patch dictionary or to calibrate the patches and an
-additional inference stage is not required. However, whitening the
-whole template is prohibitive for several reasons. All templates have
-different aspect ratios making it difficult to generate the covariance
-matrix $\Sigma$. Since the root templates are larger than mid-level
-patches, a very large auto-covariance $\Gamma$ is required. Lastly,
-time complexity of decorrelating a template with $n$ cells increases
-as $O(n^3)$, resulting in slow template generation and large residuals
-due to numerical errors accumulated while decomposing the covariance
-matrix $\Sigma$.
-
-To overcome these difficulties, we propose the Non-Zero Whitened
-Histograms of Orientations (NZ-WHO) with iterative Conjugate Gradient to
-generate templates in real time and enrich rectangular boxes with high
-quality 2D-3D matching. The 2D-3D matching provides a CAD model,
-sub-category, rendering, depth, viewpoint and focal length.
-
-Our method can work as a standalone 2D-3D matching algorithm, or even
-as a standalone ensemble of exemplar-based object detectors (Figure
-\ref{fig:front}) but its real power comes from combining generic
-object detectors and complement rectangular bounding boxes. Our method
-is simple in design; is several orders of magnitude faster than
-traditional method; requires only CAD models; does not need neither images nor
-calibration, yet is powerful in giving high-quality metadata. These
-properties make our method ideal for complementing object detections.
-
-To complement detection bounding boxes, we first search possible 2D-3D
-matching by running cached discrete viewpoint templates. Then, for the
-most probable match, we refine the initial matching using Metropolis
-Hastings. Since it requires iterations of proposal and validation, we
-present real time analysis of NZ-WHO template generation to show that
-this can be done on-the-fly. The fine tuning stage process jointly
-optimizes translation, yaw, roll, pitch, scale, and focal length
-continuously and also searches for different CAD models.

### 2014-11-14 egpaper_final.tex

--- 2014-11-14 egpaper_final.tex
@@
 
-We propose Non-Zero Whitened Histograms of Orientations (NZ-WHO), that are both
-more discriminative than WHO, and can be generated in 70ms (compared to several
-seconds for WHO). This speed up means we can generate templates on the fly,
-allowing our approach to evaluate arbitrary viewpoint hypotheses.
+\subsection{Overview}
+Our method attempts to match CAD models
 
-\scream{chris:We propose Non-Zero Whitened Histograms of Orientations (NZ-WHO),
-an improvement over WHO which is both more discriminative than WHO and can be
-computed many orders of magnitude faster than WHO (70ms as opposed to to several
-seconds for WHO). This speedup allows us to generate NZ-WHO templates on the
-fly, allowing us to quickly evaluate arbitrary viewpoint hypotheses.}
+Our method is in line with \cite{Aubry14, Lim14} in the sense that we
+use only renderings, not real images. However, rather than using fixed
+sized mid-level patches, we use whole objects and make root
+templates. By using root templates, there is no need to learn a
+discriminative patch dictionary or to calibrate the patches and an
+additional inference stage is not required. However, whitening the
+whole template is prohibitive for several reasons. All templates have
+different aspect ratios making it difficult to generate the covariance
+matrix $\Sigma$. Since the root templates are larger than mid-level
+patches, a very large auto-covariance $\Gamma$ is required. Lastly,
+time complexity of decorrelating a template with $n$ cells increases
+as $O(n^3)$, resulting in slow template generation and large residuals
+due to numerical errors accumulated while decomposing the covariance
+matrix $\Sigma$.
 
-The computational efficiency and numerical stability of our approach comes from
-using the iterative conjugate gradient method to whiten the HOG template.
-Whitening a feature vector $x$ requires a system of linear equations $\Sigma w =
-(x - \mu)$ to be solved, usually by decomposing the covariance matrix $\Sigma$
-(with LU or Cholesky decomposition). Since the covariance matrices of HOG
-templates have nice spectral properties (see Section \ref{sec:fast_whitening}),
-the conjugate gradient method will converge to the solution several orders of
-magnitude faster than decomposition methods.
+To overcome these difficulties, we propose the Non-Zero Whitened
+Histograms of Orientations (NZ-WHO) with iterative Conjugate Gradient to
+generate templates in real time and enrich rectangular boxes with high
+quality 2D-3D matching. The 2D-3D matching provides a CAD model,
+sub-category, rendering, depth, viewpoint and focal length.
 
-Our second innovation is 'Non-Zero' whitening. When synthesizing detection
-templates from rendered images, a common problem is how to handle the
-background. If we render the model over a natural image background, gradients in
-the background will be incorporated into the discriminative template.
-Alternatively, we could leave the background textureless \scream{did Hariharan
-do this?} (see Fig.~\ref{fig:rendering}), but whitening the resulting HOG
-template produces in undesirable background artifacts. These are created when
-centering the template (by subtracting the mean $\mu$), where strong negative
-weights are introduced in the textureless region (as seen in
-Fig.~\ref{fig:whocomparison}). This could result in positive matches being
-suppressed due to spurious background gradients.
+Our method can work as a standalone 2D-3D matching algorithm, or even
+as a standalone ensemble of exemplar-based object detectors (Figure
+\ref{fig:front}) but its real power comes from combining generic
+object detectors and complement rectangular bounding boxes. Our method
+is simple in design; is several orders of magnitude faster than
+traditional method; requires only CAD models; does not need neither images nor
+calibration, yet is powerful in giving high-quality metadata. These
+properties make our method ideal for complementing object detections.
 
-To remove such artifacts, we construct $x$ using only cells with non-zero
-gradients. After whitening we restore the full template, with the zero-gradient
-cells left unchanged. This approach has the added benefit of reducing the size
-of the linear system we need to solve, further speeding up our method.
+To complement detection bounding boxes, we first search possible 2D-3D
+matching by running cached discrete viewpoint templates. Then, for the
+most probable match, we refine the initial matching using Metropolis
+Hastings. Since it requires iterations of proposal and validation, we
+present real time analysis of NZ-WHO template generation to show that
+this can be done on-the-fly. The fine tuning stage process jointly
+optimizes translation, yaw, roll, pitch, scale, and focal length
+continuously and also searches for different CAD models.
 
-Table \ref{tab:who_initializations} provides a detailed comparison of WHO and
-NZ-WHO templates, illustrating that our method is faster and more discriminative
-than Whitened Histograms of Orientations. \scream{Does the table show this?}
+We propose Non-Zero Whitened Histograms of Orientations (NZ-WHO), that are both more discriminative than WHO, and can be generated in 70ms (compared to several seconds for WHO).
+This speed up means we can generate templates on the fly, allowing our approach to evaluate arbitrary viewpoint hypotheses.
+\scream{chris:We propose Non-Zero Whitened Histograms of Orientations (NZ-WHO), an improvement over WHO which is both more discriminative than WHO and can be computed many orders of magnitude faster than WHO (70ms as opposed to to several seconds for WHO).
+This speedup allows us to generate NZ-WHO templates on the fly, allowing us to quickly evaluate arbitrary viewpoint hypotheses.}
 
+The computational efficiency of our approach comes from using the iterative conjugate gradient method to whiten the HOG template.
+Whitening a feature vector $x$ requires a system of linear equations $\Sigma w = (x - \mu)$ to be solved, usually by decomposing the covariance matrix $\Sigma$ (with LU or Cholesky decomposition).
+Since the covariance matrices of HOG templates have nice spectral properties (see Section \ref{sec:fast_whitening}), the conjugate gradient method will converge to the solution several orders of magnitude faster than decomposition methods.
+
+Our second innovation is 'Non-Zero' whitening.
+When synthesizing detection templates from rendered images, a common problem is how to handle the background.
+If we render the model over a natural image background, gradients in the background will be incorporated into the discriminative template.
+Alternatively, we could leave the background textureless \scream{did Hariharan do this?} (see Fig.~\ref{fig:rendering}), but whitening the resulting HOG template produces in undesirable background artifacts.
+These are created when centering the template (by subtracting the mean $\mu$), where strong negative weights are introduced in the textureless region (as seen in Fig.~\ref{fig:whocomparison}).
+This could result in positive matches being suppressed due to spurious background gradients.
+
+To remove such artifacts, we construct $x$ using only cells with non-zero gradients.
+After whitening we restore the full template, with the zero-gradient cells left unchanged.
+This approach has the added benefit of reducing the size of the linear system we need to solve, further speeding up our method.
+
+Table \ref{tab:who_initializations} provides a detailed comparison of WHO and NZ-WHO templates, illustrating that our method is faster and more discriminative than Whitened Histograms of Orientations.
+\scream{Does the table show this?}
 % We compare the performance of WHO and NZ-WHO on 3D Object dataset \cite{Savarese07} and report performance on Table \ref{tab:who_initializations}.
@@
 
+Our method begins by convolving the
+
 Since creating a template and validating the template become computationally

### 2014-11-14 experiments.tex
started pass over ex

@@
 %
-In this section, we validate our proposed NZ-WHO templates in two different ways.
-First, we make a set of NZ-WHO templates for a set of CAD models from various viewpoints.
-Then we run the bank of NZ-WHO templates as ensembles of weak detectors and show that the rendering image can be We want to see how robust the NZ-WHO to real images a
+In this section, we give an experimental evaluation of our approach,
+highlighting two different aspects.
 
-Second, we show that our method can complement the detection bounding boxes coming out of standard object detectors.
-This process will enrich object detection bounding boxes with 2D-3D matching which gives continuous viewpoint estimation, a CAD model (rendering, depth) and fine-grained category.
+First, we demonstrate that our method can be used for multi-view
+object class detection in isolation. It can be applied in a sliding
+window fashion and deliver 2D bounding box as well as viewpoint
+information. Our method compares on par to state-of-the-art in this
+case (Sect.~\ref{sec:exp_iso}).
+
+Second, we show that our method can be used to complement the
+detections provided by an existing object class detector, such
+as DPM~\cite{Felzenszwalb10} or RCNN~\cite{Girshick14}. In this case,
+we show a considerable performance improvement compared to previous
+work in the task of joint object class detection and viewpoint
+estimation (Sect.~\ref{sec:exp_enrich}).
+
+\paragraph{Setup.}
+We use established benchmark datasets to validate our approach, namely
+the 3D Object Classes dataset~\cite{Savarese07}, and
+PASCAL3D+~\cite{Xiang14}, a recently proposed extension of Pascal
+VOC'12~\cite{pascal12} that provides additional annotations in the
+form of aligned 3D CAD models. In both cases, we use the test data
+provided by the respective datasets, but train our models entirely
+from rendered 3D CAD model images.
+
+% In this section, we validate our proposed NZ-WHO templates in two
+% different ways. First, we make a set of NZ-WHO templates for a set of
+% CAD models from various viewpoints. Then we run the bank of NZ-WHO
+% templates as ensembles of weak detectors and show that the rendering
+% image can be We want to see how robust the NZ-WHO to real images a
+%
+% Second, we show that our method can complement the detection bounding
+% boxes coming out of standard object detectors. This process will
+% enrich object detection bounding boxes with 2D-3D matching which gives
+% continuous viewpoint estimation, a CAD model (rendering, depth) and
+% fine-grained category.
 
 \subsection{2D-3D Matching as an Object Detector} 
+\label{sec:exp_iso}
+In this section, we evaluate the performance of our method in
+isolation, for the task of object class detection and viewpoint
+estimation, on the 3D Object Classes datset~\cite{Savarese07}, for the
+categories {\em car} and {\em bicycle}.
 
-We created ensemble of NZ-WHO templates using 9 CAD models and measured the Average Precision (AP) of object detection task and Mean Precision in Pose Estimation (MPPE) \cite{Lopez-Sastre11}.
-MPPE is the average of viewpoint accuracy.
+To that end, we create an ensemble of NZ-WHO templates (Sect.~\ref{})
+using $9$ different CAD models and a total of \scream{} different
+viewpoints, using $X$ different evelation angles, $X$ azimuth angles,
+and $X$ focal lengths. We run the entire ensemble exhaustively over
+each test image, in a sliding window fashion.
 
-% Instance-level 2D-3D matching (registration) is a difficult problem since we need a CAD model that looks similar to the object in the image.
-Especially, due to extreme intraclass variability of chair \cite{Aubry14} used a very large collection of CAD models to cover variety of chairs.
-Similarly, \cite{Lim14}
+ Performance is measured in Average Precision
+(AP) for object detection and Mean Precision in Pose Estimation
+(MPPE)~\cite{Lopez-Sastre11}. Pose estimation is here understood as a
+discrete problem in which the predicted azimuth angle is binned into a
+set of $8$ discrete viewpoint classes.
+% Instance-level 2D-3D matching (registration) is a difficult problem
+% since we need a CAD model that looks similar to the object in the
+% image. Especially, due to extreme intraclass variability of chair
+% \cite{Aubry14} used a very large collection of CAD models to cover
+% variety of chairs. Similarly, \cite{Lim14}
 
-Our ensemble of NZ-WHO templates is generated from rendering images within few minutes but shows reasonable performance on object detection task.
-The baseline method are Aspect Layout Model (ALM) \cite{Xiang12} and VOC-DPM \cite{Pepik12}.
-Note that the baseline methods require complex 3D modeling and viewpoint annotated natural images.
+\paragraph{Results.}
+Tab.~\ref{tab:3dobject} gives the corresponding results, comparing our
+method to two recent state-of-the-art baselines, the aspect layout
+model (ALM~\cite{Xiang12}), and the
+DPM-VOC+VP~\cite{Pepik12}. Fig.~\ref{fig:3dobject} gives corresponding
+qualitative results.
 
-The detection result is on Table \ref{tab:3dobject} and example output from our method is on Figure \ref{fig:3dobject}.
+We observe that our model performs on par with the state-of-the-art
+methods in terms of AP ($99.8$) for cars. It performs slightly worse
+on bicycles than DPM-VOC+VP ($93.0$ vs. $98.8$), but on par with the
+ALM ($93.0$). In viewpoint estimation, our model performs slightly
+worse than both methods ($91.7$ vs. $93.4$ and $97.5$ for cars, and
+$87.4$ vs. $91.4$ and $97.5$ for bicycles, respectively).
 
+This result is encouraging, since our approach reaches a level of
+performance that is on par to current state-of-the-art while at the
+same time being much faster to train. It takes merely a few minutes to
+train, while both ALM~\cite{Xiang12} and DPM-VOC+VP~\cite{Pepik12} are
+complex models that optimize non-convex objective functions during
+training, which is only made tractable by resorting to delayed
+constraint generation in the form of hard negative mining, and can
+easily take a day on a single machine. In addition, our approach uses
+only rendered images, avoiding the need for real-world training data
+with costly bounding box and viewpoint annotations.
+%
 \begin{table}[!htbp]
@@
 \end{center}
-\caption{Detection results on 3D-Object dataset \cite{Savarese07}. Original image (left) and detection result overlaid on top with a bounding box and corresponding confidence score(right)}
+\caption{Detection results on 3D Object Classes~\cite{Savarese07}. Original image (left) and detection result overlaid on top with a bounding box and corresponding confidence score(right)}
   \label{fig:3dobject}
@@
 
-\subsection{Fine-Tuning and Viewpoint Estimation}
-
+\subsection{Enriching Existing Detections}
+%\subsection{Fine-Tuning and Viewpoint Estimation}
+\label{sec:exp_enrich}
 High performance object detectors usually generalizes very well.

### 2014-11-14 experiments.tex
progrssing on exp

@@
 \label{sec:exp_enrich}
-High performance object detectors usually generalizes very well.
-It can handle various intraclass variability, viewpoint change and occlusion.
-However due to this high generalization, sometimes it is very difficult to get accurate pose, category or 2D-3D matching.
-Our method, specialized in giving such accurate information, can be applied on any generic object detectors to give high quality metadata.
+In this section, we use our method to enrich the detections provided
+by existing, high-performance object detectors with additional output
+in the form a 3D pose, focal length, and 3D CAD model exemplar shape.
+% High performance object detectors usually generalizes very well. It
+% can handle various intraclass variability, viewpoint change and
+% occlusion. However due to this high generalization, sometimes it is
+% very difficult to get accurate pose, category or 2D-3D matching. Our
+% method, specialized in giving such accurate information, can be
+% applied on any generic object detectors to give high quality metadata.
 
-To show such ability, we evaluated our method on PASCAL 3D dataset \cite{Xiang14}.
-The dataset augments PASCAL 2012 images with high quality viewpoint annotations thus is ideal to measure pose estimation.
-The dataset proposes new metric called Average Viewpoint Precision (AVP) where it measures the area under viewpoint precision and detection recall curve.
-The viewpoints is measured by azimuth similarity.
-If the distance between predicted azimuth and ground truth azimuth is below a certain threshold, the viewpoint is correct.
-Note that the baseline methods (V-DPM, VOC-DPM) reported on the PASCAL 3D dataset are variants of DPM where each component of DPM account for various azimuths.
-Thus V-DPM and VOC-DPM provide discrete azimuth only whereas our method provides 3D viewpoint (yaw, pitch, roll), CAD instance (model index, rendering, depth) and focal length.
+To show such ability, we evaluat our method on the PASCAL3D+
+dataset~\cite{Xiang14}. This dataset augments PASCAL 2012 images with
+high quality viewpoint annotations thus is ideal to measure pose
+estimation. The dataset proposes new metric called Average Viewpoint
+Precision (AVP) where it measures the area under viewpoint precision
+and detection recall curve. The viewpoints is measured by azimuth
+similarity. If the distance between predicted azimuth and ground truth
+azimuth is below a certain threshold, the viewpoint is correct. Note
+that the baseline methods (V-DPM~\cite{Xiang14},
+DPM-VOC+VP~\cite{Pepik12}) reported on the PASCAL3D+ dataset are
+variants of DPM~\cite{Felzenszwalb10} where each component of DPM
+account for various azimuths. Thus V-DPM and VOC-DPM provide discrete
+azimuth only whereas our method provides 3D viewpoint (yaw, pitch,
+roll), CAD instance (model index, rendering, depth) and focal length.
 
-We used detection bounding boxes and augment it using our method to give viewpoint estimation.
-We used detection bounding boxes from two different methods: VOC-DPM \cite{Pepik12} and R-CNN \cite{Girshick14}.
-VOC-DPM is a variation of DPM that can estimate viewpoint and is the state-of-the-art performance in viewpoint estimation \cite{Xiang14}.
-The result is on Table \ref{tab:pascal12} and precision recall curves for car using R-CNN + Ours are on Figure \ref{fig:car_cnn_ap}.
+\paragraph{Setup.}
+We used detection bounding boxes and augment it using our method to
+give viewpoint estimation. We used detection bounding boxes from two
+different methods: VOC-DPM \cite{Pepik12} and R-CNN
+\cite{Girshick14}. VOC-DPM is a variation of DPM that can estimate
+viewpoint and is the state-of-the-art performance in viewpoint
+estimation \cite{Xiang14}. The result is on Table \ref{tab:pascal12}
+and precision recall curves for car using R-CNN + Ours are on Figure
+\ref{fig:car_cnn_ap}.
 
-We got significant improvement on viewpoint estimation by using our method on top of general purpose detectors.
-Note that our method estimates azimuth, elevation, in-plane rotation, focal length estimation, fine-grained categorization whereas V-DPM, VOC-DPM only estimate discrete viewpoints.
+We got significant improvement on viewpoint estimation by using our
+method on top of general purpose detectors. Note that our method
+estimates azimuth, elevation, in-plane rotation, focal length
+estimation, fine-grained categorization whereas V-DPM, VOC-DPM only
+estimate discrete viewpoints.
 
@@
 \hline
-AP/AVP              & V-DPM \cite{Xiang14} & VOC-DPM \cite{Pepik12}  & \cite{Pepik12} + Ours (discrete) & \cite{Pepik12} + Ours (full) & R-CNN + Ours (discrete) & R-CNN + Ours (full)\\
+AP/AVP              & V-DPM \cite{Xiang14} & DPM-VOC+VP \cite{Pepik12}  & \cite{Pepik12} + Ours (discrete) & \cite{Pepik12} + Ours (full) & R-CNN + Ours (discrete) & R-CNN + Ours (full)\\
 \hline\hline
@@
 \end{center}
-\caption{Average Precision(AP) and Average Viewpoint Precision(AVP) on PASCAL 3D dataset\cite{Xiang14}.
+\caption{Average Precision(AP) and Average Viewpoint Precision(AVP) on PASCAL3D+~\cite{Xiang14}.
 For combined method (* + Ours), we use bounding boxes from * and augment viewpoint using our method.

### 2014-11-14 egpaper_final.tex
added method overview

@@
 
-\section{2D-3D Matching using Non-Zero Whitened Histograms of Orientations(NZ-WHO)}
+\section{Our Approach \scream{better name?}}
 \label{sec:nz-who}
@@
 \subsection{Overview}
-Our method attempts to match CAD models
+Our method attempts to match CAD models to 2D images, determining the best model within a class, its pose and scale, and the focal length of the camera used to produce the image.
+These parameters are first coarsely estimated using a discrete bank of detectors trained offline, before they are refined using MCMC by generating new detectors on the fly.
 
+The basic detection method underlying our approach is HOG template matching.
+However, we propose a new HOG variant called Non-Zero Whitened Histograms of Orientations (NZ-WHO), where the HOG templates are whitened using statistics found from a random collection of natural images, producing a more discriminative template.
+
+In addition to the library of CAD models that will be matched to the query images, our method requires a collection of random natural images.
+Offline, we compute HOG features of these images and record their mean and spatial autocovariance.
+The images are not used during testing, only the statistics generated from them.
+
+Notably, we do not require any labelled training images of the objects to be detected.
+Our templates are generated exclusively by rendering CAD models from our library.
+From these renderings we produce novel HOG-like features we call Non-Zero Whitened Histograms of Orientations (NZ-WHO), which use the natural image statistics found offline to whiten a standard HOG template, making it more discriminative.
+
+The matching proceeds in two steps: First, we apply a bank of pre-trained detectors to the image, corresponding to a set of discrete viewpoints, scales, and object models.
+This provides a rough estimate of these parameters.
+Second, we refine these parameters using MCMC, where each candidate is evaluated by rendering a new whitened template on the fly.
+
+Optionally, our algorithm can be initialized using proposal bounding boxes from state-of-the-art object detectors \cite{Felzenszwalb10,Girshick14} before executing the two steps above.
+In this scenario, our approach provides a means to augment standard bounding box detectors with more interesting 3D information.
+
+\begin{comment}
 Our method is in line with \cite{Aubry14, Lim14} in the sense that we
@@
 continuously and also searches for different CAD models.
+
+\end{comment}
+
+\subsection{Non-Zero Whitened Histograms of Orientations (NZ-WHO)}
 

### 2014-11-14 egpaper_final.tex
uncomment FFT

--- 2014-11-14 egpaper_final.tex
@@
 
-\subsection{Overview}
-Our method attempts to match CAD models
+We propose Non-Zero Whitened Histograms of Orientations (NZ-WHO), that are both
+more discriminative than WHO, and can be generated in 70ms (compared to several
+seconds for WHO). This speed up means we can generate templates on the fly,
+allowing our approach to evaluate arbitrary viewpoint hypotheses.
 
-Our method is in line with \cite{Aubry14, Lim14} in the sense that we
-use only renderings, not real images. However, rather than using fixed
-sized mid-level patches, we use whole objects and make root
-templates. By using root templates, there is no need to learn a
-discriminative patch dictionary or to calibrate the patches and an
-additional inference stage is not required. However, whitening the
-whole template is prohibitive for several reasons. All templates have
-different aspect ratios making it difficult to generate the covariance
-matrix $\Sigma$. Since the root templates are larger than mid-level
-patches, a very large auto-covariance $\Gamma$ is required. Lastly,
-time complexity of decorrelating a template with $n$ cells increases
-as $O(n^3)$, resulting in slow template generation and large residuals
-due to numerical errors accumulated while decomposing the covariance
-matrix $\Sigma$.
+\scream{chris:We propose Non-Zero Whitened Histograms of Orientations (NZ-WHO),
+an improvement over WHO which is both more discriminative than WHO and can be
+computed many orders of magnitude faster than WHO (70ms as opposed to to several
+seconds for WHO). This speedup allows us to generate NZ-WHO templates on the
+fly, allowing us to quickly evaluate arbitrary viewpoint hypotheses.}
 
-To overcome these difficulties, we propose the Non-Zero Whitened
-Histograms of Orientations (NZ-WHO) with iterative Conjugate Gradient to
-generate templates in real time and enrich rectangular boxes with high
-quality 2D-3D matching. The 2D-3D matching provides a CAD model,
-sub-category, rendering, depth, viewpoint and focal length.
+The computational efficiency and numerical stability of our approach comes from
+using the iterative conjugate gradient method to whiten the HOG template.
+Whitening a feature vector $x$ requires a system of linear equations $\Sigma w =
+(x - \mu)$ to be solved, usually by decomposing the covariance matrix $\Sigma$
+(with LU or Cholesky decomposition). Since the covariance matrices of HOG
+templates have nice spectral properties (see Section \ref{sec:fast_whitening}),
+the conjugate gradient method will converge to the solution several orders of
+magnitude faster than decomposition methods.
 
-Our method can work as a standalone 2D-3D matching algorithm, or even
-as a standalone ensemble of exemplar-based object detectors (Figure
-\ref{fig:front}) but its real power comes from combining generic
-object detectors and complement rectangular bounding boxes. Our method
-is simple in design; is several orders of magnitude faster than
-traditional method; requires only CAD models; does not need neither images nor
-calibration, yet is powerful in giving high-quality metadata. These
-properties make our method ideal for complementing object detections.
+Our second innovation is 'Non-Zero' whitening. When synthesizing detection
+templates from rendered images, a common problem is how to handle the
+background. If we render the model over a natural image background, gradients in
+the background will be incorporated into the discriminative template.
+Alternatively, we could leave the background textureless \scream{did Hariharan
+do this?} (see Fig.~\ref{fig:rendering}), but whitening the resulting HOG
+template produces in undesirable background artifacts. These are created when
+centering the template (by subtracting the mean $\mu$), where strong negative
+weights are introduced in the textureless region (as seen in
+Fig.~\ref{fig:whocomparison}). This could result in positive matches being
+suppressed due to spurious background gradients.
 
-To complement detection bounding boxes, we first search possible 2D-3D
-matching by running cached discrete viewpoint templates. Then, for the
-most probable match, we refine the initial matching using Metropolis
-Hastings. Since it requires iterations of proposal and validation, we
-present real time analysis of NZ-WHO template generation to show that
-this can be done on-the-fly. The fine tuning stage process jointly
-optimizes translation, yaw, roll, pitch, scale, and focal length
-continuously and also searches for different CAD models.
+To remove such artifacts, we construct $x$ using only cells with non-zero
+gradients. After whitening we restore the full template, with the zero-gradient
+cells left unchanged. This approach has the added benefit of reducing the size
+of the linear system we need to solve, further speeding up our method.
 
-We propose Non-Zero Whitened Histograms of Orientations (NZ-WHO), that are both more discriminative than WHO, and can be generated in 70ms (compared to several seconds for WHO).
-This speed up means we can generate templates on the fly, allowing our approach to evaluate arbitrary viewpoint hypotheses.
-\scream{chris:We propose Non-Zero Whitened Histograms of Orientations (NZ-WHO), an improvement over WHO which is both more discriminative than WHO and can be computed many orders of magnitude faster than WHO (70ms as opposed to to several seconds for WHO).
-This speedup allows us to generate NZ-WHO templates on the fly, allowing us to quickly evaluate arbitrary viewpoint hypotheses.}
+Table \ref{tab:who_initializations} provides a detailed comparison of WHO and
+NZ-WHO templates, illustrating that our method is faster and more discriminative
+than Whitened Histograms of Orientations. \scream{Does the table show this?}
 
-The computational efficiency of our approach comes from using the iterative conjugate gradient method to whiten the HOG template.
-Whitening a feature vector $x$ requires a system of linear equations $\Sigma w = (x - \mu)$ to be solved, usually by decomposing the covariance matrix $\Sigma$ (with LU or Cholesky decomposition).
-Since the covariance matrices of HOG templates have nice spectral properties (see Section \ref{sec:fast_whitening}), the conjugate gradient method will converge to the solution several orders of magnitude faster than decomposition methods.
-
-Our second innovation is 'Non-Zero' whitening.
-When synthesizing detection templates from rendered images, a common problem is how to handle the background.
-If we render the model over a natural image background, gradients in the background will be incorporated into the discriminative template.
-Alternatively, we could leave the background textureless \scream{did Hariharan do this?} (see Fig.~\ref{fig:rendering}), but whitening the resulting HOG template produces in undesirable background artifacts.
-These are created when centering the template (by subtracting the mean $\mu$), where strong negative weights are introduced in the textureless region (as seen in Fig.~\ref{fig:whocomparison}).
-This could result in positive matches being suppressed due to spurious background gradients.
-
-To remove such artifacts, we construct $x$ using only cells with non-zero gradients.
-After whitening we restore the full template, with the zero-gradient cells left unchanged.
-This approach has the added benefit of reducing the size of the linear system we need to solve, further speeding up our method.
-
-Table \ref{tab:who_initializations} provides a detailed comparison of WHO and NZ-WHO templates, illustrating that our method is faster and more discriminative than Whitened Histograms of Orientations.
-\scream{Does the table show this?}
 % We compare the performance of WHO and NZ-WHO on 3D Object dataset \cite{Savarese07} and report performance on Table \ref{tab:who_initializations}.
@@
 We use the GPU to parallelize the lookup of the correct autocovariance cells
-during covariance matrix syntheses, which is \scream{x} times faster than using
+during covariance matrix syntheses, which is an order of magnitude times faster than using
 the CPU (Figure \ref{fig:covariancetime}).
@@
 one HOG template after a small regularization constant is added to the diagonal.
-The condition number of of the matrix is \scream{x}, much smaller than the size
+The condition number of of the matrix is , much smaller than the size
 of the matrix (7500). As a result, conjugate gradient converges in \scream{x
@@
 \end{center}
-\caption{Average Precision(AP) and Mean Precision in Pose Estimation (MPPE) \cite{Lopez-Sastre11} variations of WHO on 3DObject Car dataset\cite{Savarese07}.
-WHO refers to standard WHO using the method presented in \cite{Hariharan12}, WHO-CG uses iterative Conjugate Gradient method to generate WHO.
-WHO-CG-Z uses whiten the whole template and zero out textureless region.
-NZ-WHO-CG is the NZ-WHO which whitens only non-zero cells using iterative Conjugate Gradient method.
-The time column indicates the time to generate one template.
-We followed calibration procedure presented in \cite{Aubry14}.}
+\caption{Average Precision(AP) and Mean Precision in Pose Estimation (MPPE)
+\cite{Lopez-Sastre11} variations of WHO on 3DObject Car
+dataset\cite{Savarese07}. WHO refers to standard WHO using the method presented
+in \cite{Hariharan12}, WHO-CG uses iterative Conjugate Gradient method to
+generate WHO. WHO-CG-Z uses whiten the whole template and zero out textureless
+region. NZ-WHO-CG is the NZ-WHO which whitens only non-zero cells using
+iterative Conjugate Gradient method. The time column indicates the time to
+generate one template. We followed calibration procedure presented in
+\cite{Aubry14}.}
 \label{tab:who_initializations}
@@
 
-\begin{comment}
 \subsection{High Resolution Templates and FFT based Convolution}
 \label{sec:fft} 
-We generate high resolution templates with more than 250 HOG cells to capture details of an object to give accurate 2D-3D matching.
-These large templates cause computational burden when computing convolution.
-Though good for detecting accurate model and pose, convolution of high-resolution templates are much more slower since computation time scales linearly with the number of HOG cells in the template.
-To overcome and speed up the convolution, we propose FFT based GPU convolution which scales.
-Suppose there are length $n$ signal and length $m$ filter, naive convolution takes $O(nm)$ time where as FFT-based convolution takes $O\left( (n + m)\log (n+m) \right)$ time.
-For large $m$, high resolution template, we can gain computational advantage.
+We generate high resolution templates with more than 250 HOG cells to capture
+details of an object to give accurate 2D-3D matching. Though good for detecting
+accurate model and pose, convolution of high-resolution templates are much more
+slower since computation time scales linearly with the number of HOG cells in
+the template. To overcome and speed up the convolution, we propose FFT based
+GPU convolution which scales. Suppose there are length $n$ signal and length
+$m$ filter, naive convolution takes $O(nm)$ time where as FFT-based convolution
+takes $O\left( (n + m)\log (n+m) \right)$ time. For large $m$, high resolution
+template, we can gain computational advantage.
 
-we pad zero to the 2D image features by the largest kernel size.
-And we transform the kernel to match the padded image feature.
-To compute convolution, we compute element-wise product with the transformed kernel and sum all the features.
-Unlike \cite{Podlozhnyuk}, we do not need to shift the data nor kernel if we use simple mathematical trick.
+We pad zero to the 2D image features by the largest kernel size. And we
+transform the kernel to match the padded image feature. To compute convolution,
+we compute element-wise product with the transformed kernel and sum all the
+features. Unlike \cite{Podlozhnyuk}, we do not need to shift the data nor
+kernel if we use simple mathematical trick.
 
@@
 
-  Where $\ast$ is the circular convolution and $\circ$ is the Hadamard Product and $\mathcal{F}$ is the Fourier Transformation and $\mathcal{P}_n$ is the padding operation that append zeros to make vector of size $n$.
+Where $\ast$ is the circular convolution and $\circ$ is the Hadamard Product
+and $\mathcal{F}$ is the Fourier Transformation and $\mathcal{P}_n$ is the
+padding operation that append zeros to make vector of size $n$.
 
-For each dimension of features, we transform kernel and image feature into frequency domain using Fast Fourier Transformation.
-We transform the image into frequency domain once and use the transformed image for all templates.
+For each dimension of features, we transform kernel and image feature into
+frequency domain using Fast Fourier Transformation. We transform the image into
+frequency domain once and use the transformed image for all templates.
 
@@
 
-[Figure for convolution time for different template resolution, CPU, GPU, naive convolution]
-\end{comment}
+% [Figure for convolution time for different template resolution, CPU, GPU, naive convolution]
 %------------------------------------------------------------------------
 
-\section{Estimating Parameters using MCMC}
+\section{Continuous Viewpoint Estimation using MCMC}
 \label{sec:fine}
@@
 camera focal length.
-
-Our method begins by convolving the
 

### 2014-11-14 egpaper_final.tex
incorporated related work into NZ-WHO section

--- 2014-11-14 egpaper_final.tex
@@
 \section{Related Works}
-\subsection{Whitened Histograms of Orientations (WHO)}
-% History of Whitening and how whitening works
-Recently, Hariharan \etal. introduced Whitened Histograms of Orientations (WHO)
-\cite{Hariharan12}, which used statistics from natural images to whiten HOG
-templates, making them more discriminative. Whitening is a common signal
-processing operation for decorrelating a set of random variables
-\cite{Martinsson05, Belouchrani00}. More formally, suppose that we have a
-$k$-dimensional random variable $X \in \mathcal{R}^k$ with $Cov(X)=\Sigma$. By
-whitening the signal, i.e., $\tilde{X}=\Sigma^{-\frac{1}{2}}(X - E[X])$, we
-remove 2nd order correlation between all features. So, all elements in the
-random variable $\tilde{X} = \left[\tilde{X}_1, \tilde{X}_2, \dots,
-\tilde{X}_k\right]$, become more independent. In the context of HOG features, a
-whitened HOG template will produce Gaussian noise when convolved with a random
-natural image, but a delta-like response on an image matching the template. WHO
-templates are more discriminative than standard HOG templates because they only
-capture the gradients that differentiate the object from random images.
-\scream{chris added the following} Hariharan \etal. also interpreted the
-whitening as Linear Discriminant Analysis (LDA) where all classes have different
-means but have the same covariance. The whitening and LDA have the same
-formulation when we make a decision boundary $w = \Sigma^{-1}(\mu_+ - \mu_0)$
-where $\mu_+$ is the features from a class (LDA) or a signal to whiten
-(whitening), $\mu_0$ is the negative class center (LDA) or a signal statistics
-(whitening) and $\Sigma$ is the covariance matrix of classes (LDA) or
-correlation within signal (whitening).
-
-\textcolor{red}{Should we mention how our method improves on this (ie by using CG)?}
 
@@
 
-We propose Non-Zero Whitened Histograms of Orientations (NZ-WHO), that are both more discriminative than WHO, and can be generated in 70ms (compared to several seconds for WHO).
+Recently, Hariharan \etal. introduced Whitened Histograms of Orientations (WHO)
+\cite{Hariharan12}, which uses statistics from natural images to whiten HOG
+templates, making them more discriminative. Whitening is a common signal
+processing operation for decorrelating a set of random variables
+\cite{Martinsson05, Belouchrani00}. More formally, suppose that we have a
+$k$-dimensional random variable $X \in \mathcal{R}^k$ with $Cov(X)=\Sigma$. By
+whitening the signal, i.e., $\tilde{X}=\Sigma^{-\frac{1}{2}}(X - E[X])$, we
+remove 2nd order correlation between all features. So, all elements in the
+random variable $\tilde{X} = \left[\tilde{X}_1, \tilde{X}_2, \dots,
+\tilde{X}_k\right]$, become more independent. In the context of HOG features, a
+whitened HOG template will produce Gaussian noise when convolved with a random
+natural image, but a delta-like response on an image matching the template. WHO
+templates are more discriminative than standard HOG templates because they only
+capture the gradients that differentiate the object from random images.
+
+Hariharan \etal. interpreted the
+whitening as Linear Discriminant Analysis (LDA) where all classes have different
+means but have the same covariance. The whitening and LDA have the same
+formulation when we make a decision boundary $w = \Sigma^{-1}(\mu_+ - \mu_0)$
+where $\mu_+$ is the features from a class (LDA) or a signal to whiten
+(whitening), $\mu_0$ is the negative class center (LDA) or the signal mean
+(whitening) and $\Sigma$ is the covariance matrix of classes (LDA) or
+the correlation within signal (whitening).
+
+We propose Non-Zero Whitened Histograms of Orientations (NZ-WHO), that are both more discriminative than WHO, and can be generated several orders of magnitude faster (in 70ms compared to several seconds for WHO).
 This speed up means we can generate templates on the fly, allowing our approach to evaluate arbitrary viewpoint hypotheses.
-\scream{chris:We propose Non-Zero Whitened Histograms of Orientations (NZ-WHO), an improvement over WHO which is both more discriminative than WHO and can be computed many orders of magnitude faster than WHO (70ms as opposed to to several seconds for WHO).
+%\scream{chris:We propose Non-Zero Whitened Histograms of Orientations (NZ-WHO), an improvement over WHO which is both more discriminative than WHO and can be computed many orders of magnitude faster than WHO (70ms as opposed to to several seconds for WHO).
 This speedup allows us to generate NZ-WHO templates on the fly, allowing us to quickly evaluate arbitrary viewpoint hypotheses.}

### 2014-11-14 experiments.tex

@@
 similarity. If the distance between predicted azimuth and ground truth
-azimuth is below a certain threshold, the viewpoint is correct. Note
-that the baseline methods (V-DPM~\cite{Xiang14},
+azimuth is below a certain threshold, the viewpoint is correct.
+The baseline methods V-DPM~\cite{Xiang14} and
 DPM-VOC+VP~\cite{Pepik12}) reported on the PASCAL3D+ dataset are
@@
 \paragraph{Setup.}
-We used detection bounding boxes and augment it using our method to
-give viewpoint estimation. We used detection bounding boxes from two
-different methods: VOC-DPM \cite{Pepik12} and R-CNN
-\cite{Girshick14}. VOC-DPM is a variation of DPM that can estimate
-viewpoint and is the state-of-the-art performance in viewpoint
-estimation \cite{Xiang14}. The result is on Table \ref{tab:pascal12}
-and precision recall curves for car using R-CNN + Ours are on Figure
-\ref{fig:car_cnn_ap}.
+We use detection bounding boxes provided by both object detectors and
+augment it using our method to give viewpoint estimation. We use
+detection bounding boxes from two different methods:
+DPM-VOC+VP\cite{Pepik12} and R-CNN~\cite{Girshick14}, both in their
+variants trained on 8 viewpoint categories, since these perform best
+in terms of AP. For both methods,
+we use the original score for plotting precision-recall curves
+(meaning that we can not improve over their AP), but
+enrich the detections with additional viewpoint information provided
+by our method. For DPM-VOC+VP, we fall back to the viewpoint
+estimation provided by this method in case the confidence of our
+method falls below a threshold. For R-CNN, we fall back to a default
+viewpoint prediction ($0$ angles).
 
-We got significant improvement on viewpoint estimation by using our
-method on top of general purpose detectors. Note that our method
-estimates azimuth, elevation, in-plane rotation, focal length
-estimation, fine-grained categorization whereas V-DPM, VOC-DPM only
-estimate discrete viewpoints.
+For both cases, we compare the performance of a discrete incarnation
+of our method (Sect.~\ref{}) and our full model, including the
+fine-tuning based on MCMC~\cite{Sect.~\ref{}}
 
-Example outputs are on Figure \ref{fig:pascal12cnn}.
+Quantitative results are given in Tab.~\ref{tab:pascal12} in terms of
+AP and AVP and in Fig.~\ref{fig:car_cnn_ap} in terms of
+precision-recall plots and viewpoint confusion matrices. Example
+outputs of our method applied to candidate object detections are given
+in Fig.~\ref{fig:pascal12cnn}, and the effect of fine-tuning is
+visualized in Fig.~\ref{}.
+
+ More qualitative results are part of
+supplemental material~\scream{}
+
+\paragraph{Results.}
+%
+In Tab.~\ref{tab:pascal12}, we make mainly two observation. First, we
+see that adding our method to DPM-VOC+VP consistently improves
+performance in terms of AVP, for both car and bicycle, and across all
+viewpoint bins. This is already the case for our discrete method: the
+improvement ranges from $0.3$ for bicycle-8v to $5.8$ for car-4v. 
+%
+Using the R-CNN as the base detector increases AVP even more, in
+particular for the bicycle class: for bicycle-4v, our discrete method
+improves over the corresponding DPM-VOC+VP result by $12.6$.
+
+The second observation is that the fine-tuning based on MCMC can
+indeed improve pose estimation performance slightly, e.g., by $1.1$
+for bicycle-16v and using the DPM-VOC+VP as the base detector, or by
+$1.1$ for bicycle-16v when using the R-CNN as the base detector.
+
+% We got significant improvement on viewpoint estimation by using our
+% method on top of general purpose detectors. Note that our method
+% estimates azimuth, elevation, in-plane rotation, focal length
+% estimation, fine-grained categorization whereas V-DPM, VOC-DPM only
+% estimate discrete viewpoints.
 
@@
   \begin{center}
-\begin{tabular}{|c|c|c|c|c|c|c|}
+\begin{tabular}{|c||c||c||c|c||c|c|}
 \hline
@@
 bicycle-8v          & 47.3 / 36.7         & 48.1 / 40.3             & 48.1 / 40.6       & 48.1 / 40.6        & 61.7 / 48.9         & 61.7 / \textbf{49.2}\\ \hline
-bicycle-16v         & 46.5 / 18.4         & 45.6 / 22.9             & 48.1 / 26.2       & 40.1 / 27.3        & 61.7 / 34.7         & 61.7 / \textbf{35.8}\\ \hline
-bicycle-24v         & 44.4 / 14.3         & 45.9 / 16.7             & 48.1 / 21.5       & 40.1 / 20.9        & 61.7 / \textbf{27.0}         & 61.7 / 23.9\\ \hline
+bicycle-16v         & 46.5 / 18.4         & 45.6 / 22.9             & 48.1 / 26.2       & 48.1 / 27.3        & 61.7 / 34.7         & 61.7 / \textbf{35.8}\\ \hline
+bicycle-24v         & 44.4 / 14.3         & 45.9 / 16.7             & 48.1 / 21.5       & 48.1 / 20.9        & 61.7 / \textbf{27.0}         & 61.7 / 23.9\\ \hline
 \end{tabular}
@@
 \end{tabular}
-\caption{Average Precision (AP) and Average Viewpoint Precision (AVP) and viewpoint confusion table on PASCAL 12 car validation set using R-CNN + Ours.
+\caption{Average Precision (AP) and Average Viewpoint Precision (AVP)
+  and viewpoint confusion table on PASCAL 12 car validation set using
+  R-CNN + Ours (full).
 From the top left, 4 views, 8 views, 16 views and 24 views.

### 2014-11-14 egpaper_final.tex

--- 2014-11-14 egpaper_final.tex
@@
 \subsection{Whitened Histograms of Orientations (WHO)}
+
+\scream{Should we merge this with NZ-WHO?}
 % History of Whitening and how whitening works
@@
 capture the gradients that differentiate the object from random images.
-\scream{chris added the following} Hariharan \etal. also interpreted the
+\scream{requires revision} Hariharan \etal. also interpreted the
 whitening as Linear Discriminant Analysis (LDA) where all classes have different
@@
 
-\textcolor{red}{Should we mention how our method improves on this (ie by using CG)?}
+\textcolor{red}{Should we mention how our method improves on this (ie by using CG)? Since we explain in depth later, it would be okay}
 
@@
 \subsection{Overview}
-Our method attempts to match CAD models to 2D images, determining the best model within a class, its pose and scale, and the focal length of the camera used to produce the image.
-These parameters are first coarsely estimated using a discrete bank of detectors trained offline, before they are refined using MCMC by generating new detectors on the fly.
+Our method attempts to match CAD models to 2D images, determining the best
+model within a class, its pose and scale, and the focal length of the camera
+used to produce the image. These parameters are first coarsely estimated using
+a discrete bank of detectors trained offline, before they are refined using
+MCMC by generating new detectors on the fly.
 
 The basic detection method underlying our approach is HOG template matching.
-However, we propose a new HOG variant called Non-Zero Whitened Histograms of Orientations (NZ-WHO), where the HOG templates are whitened using statistics found from a random collection of natural images, producing a more discriminative template.
+However, we propose a new HOG variant called Non-Zero Whitened Histograms of
+Orientations (NZ-WHO), where the HOG templates are whitened using statistics
+found from a random collection of natural images, producing a more
+discriminative template.
 
-In addition to the library of CAD models that will be matched to the query images, our method requires a collection of random natural images.
-Offline, we compute HOG features of these images and record their mean and spatial autocovariance.
-The images are not used during testing, only the statistics generated from them.
+In addition to the library of CAD models that will be matched to the query
+images, our method requires a collection of random natural images. Offline, we
+compute HOG features of these images and record their mean and spatial
+autocovariance. The images are not used during testing, only the statistics
+generated from them.
 
-Notably, we do not require any labelled training images of the objects to be detected.
-Our templates are generated exclusively by rendering CAD models from our library.
-From these renderings we produce novel HOG-like features we call Non-Zero Whitened Histograms of Orientations (NZ-WHO), which use the natural image statistics found offline to whiten a standard HOG template, making it more discriminative.
+Notably, we do not require any labelled training images of the objects to be
+detected. Our templates are generated exclusively by rendering CAD models from
+our library. From these renderings we produce novel HOG-like features we call
+Non-Zero Whitened Histograms of Orientations (NZ-WHO), which use the natural
+image statistics found offline to whiten a standard HOG template, making it
+more discriminative.
 
-The matching proceeds in two steps: First, we apply a bank of pre-trained detectors to the image, corresponding to a set of discrete viewpoints, scales, and object models.
-This provides a rough estimate of these parameters.
-Second, we refine these parameters using MCMC, where each candidate is evaluated by rendering a new whitened template on the fly.
+The matching proceeds in two steps: First, we apply a bank of pre-trained
+detectors to the image, corresponding to a set of discrete viewpoints, scales,
+and object models. This provides a rough estimate of these parameters. Second,
+we refine these parameters using MCMC, where each candidate is evaluated by
+rendering a new whitened template on the fly.
 
-Optionally, our algorithm can be initialized using proposal bounding boxes from state-of-the-art object detectors \cite{Felzenszwalb10,Girshick14} before executing the two steps above.
-In this scenario, our approach provides a means to augment standard bounding box detectors with more interesting 3D information.
+Optionally, our algorithm can be initialized using proposal bounding boxes from
+state-of-the-art object detectors \cite{Felzenszwalb10,Girshick14} before
+executing the two steps above. In this scenario, our approach provides a means
+to augment standard bounding box detectors with more interesting 3D
+information.
 
@@
 
-We propose Non-Zero Whitened Histograms of Orientations (NZ-WHO), that are both more discriminative than WHO, and can be generated in 70ms (compared to several seconds for WHO).
-This speed up means we can generate templates on the fly, allowing our approach to evaluate arbitrary viewpoint hypotheses.
-\scream{chris:We propose Non-Zero Whitened Histograms of Orientations (NZ-WHO), an improvement over WHO which is both more discriminative than WHO and can be computed many orders of magnitude faster than WHO (70ms as opposed to to several seconds for WHO).
-This speedup allows us to generate NZ-WHO templates on the fly, allowing us to quickly evaluate arbitrary viewpoint hypotheses.}
+We propose Non-Zero Whitened Histograms of Orientations (NZ-WHO), that are both
+more discriminative than WHO, and can be generated in 70ms (compared to several
+seconds for WHO). This speed up means we can generate templates on the fly,
+allowing our approach to evaluate arbitrary viewpoint hypotheses. 
+\scream{require revision: We propose Non-Zero Whitened Histograms of Orientations (NZ-WHO),
+an improvement over WHO which is both more discriminative than WHO and can be
+computed many orders of magnitude faster than WHO (70ms as opposed to to
+several seconds for WHO). This speedup allows us to generate NZ-WHO templates
+on the fly, allowing us to quickly evaluate arbitrary viewpoint hypotheses.}
 
-The computational efficiency of our approach comes from using the iterative conjugate gradient method to whiten the HOG template.
-Whitening a feature vector $x$ requires a system of linear equations $\Sigma w = (x - \mu)$ to be solved, usually by decomposing the covariance matrix $\Sigma$ (with LU or Cholesky decomposition).
-Since the covariance matrices of HOG templates have nice spectral properties (see Section \ref{sec:fast_whitening}), the conjugate gradient method will converge to the solution several orders of magnitude faster than decomposition methods.
+The computational efficiency of our approach comes from using the iterative
+conjugate gradient method to whiten the HOG template. Whitening a feature
+vector $x$ requires a system of linear equations $\Sigma w = (x - \mu)$ to be
+solved, usually by decomposing the covariance matrix $\Sigma$ (with LU or
+Cholesky decomposition). Since the covariance matrices of HOG templates have
+nice spectral properties (see Section \ref{sec:fast_whitening}), the conjugate
+gradient method will converge to the solution several orders of magnitude
+faster than decomposition methods.
 
-Our second innovation is 'Non-Zero' whitening.
-When synthesizing detection templates from rendered images, a common problem is how to handle the background.
-If we render the model over a natural image background, gradients in the background will be incorporated into the discriminative template.
-Alternatively, we could leave the background textureless \scream{did Hariharan do this?} (see Fig.~\ref{fig:rendering}), but whitening the resulting HOG template produces in undesirable background artifacts.
-These are created when centering the template (by subtracting the mean $\mu$), where strong negative weights are introduced in the textureless region (as seen in Fig.~\ref{fig:whocomparison}).
-This could result in positive matches being suppressed due to spurious background gradients.
+Our second innovation is 'Non-Zero' whitening. When synthesizing detection
+templates from rendered images, a common problem is how to handle the
+background. If we render the model over a natural image background, gradients
+in the background will be incorporated into the discriminative template.
+Alternatively, we could leave the background textureless \scream{did Hariharan
+do this? Nobody did this before} (see Fig.~\ref{fig:rendering}), but whitening the resulting HOG
+template produces in undesirable background artifacts. These are created when
+centering the template (by subtracting the mean $\mu$), where strong negative
+weights are introduced in the textureless region (as seen in
+Fig.~\ref{fig:whocomparison}). This could result in positive matches being
+suppressed due to spurious background gradients.
 
@@
 Table \ref{tab:who_initializations} provides a detailed comparison of WHO and NZ-WHO templates, illustrating that our method is faster and more discriminative than Whitened Histograms of Orientations.
-\scream{Does the table show this?}
+\scream{Does the table show this?
+should we do more than AP and realtime analysis?}
 % We compare the performance of WHO and NZ-WHO on 3D Object dataset \cite{Savarese07} and report performance on Table \ref{tab:who_initializations}.
@@
 
-Figure \ref{fig:spectral} shows the singular values of a covariance matrix for
-one HOG template after a small regularization constant is added to the diagonal.
-The condition number of of the matrix is \scream{x}, much smaller than the size
-of the matrix (7500). As a result, conjugate gradient converges in \scream{x
-ms}, two orders of magnitude faster than the system can be solved using the
-Cholesky factorization (\scream{5 s}).
+% Figure \ref{fig:spectral} shows the singular values of a covariance matrix for
+% one HOG template after a small regularization constant is added to the diagonal.
+% The condition number of of the matrix is , much smaller than the size
+% of the matrix (7500). As a result, conjugate gradient converges in 50
+% ms, two orders of magnitude faster than the system can be solved using the
+% Cholesky factorization (5 sec).
 
-The final challenge in on-the-fly template evaluation is performing the
-convolution between the template and the target image. Standard convolution
-would be prohibitively slow for the high resolution templates we're using, so we
-implemented the convolution via Fast Fourier Transform on the GPU. This allows
-template evaluation to run in \scream{x ms}, compared to \scream{x ms} for the
-naive CPU implementation.
+% The final challenge in on-the-fly template evaluation is performing the
+% convolution between the template and the target image. Standard convolution
+% would be prohibitively slow for the high resolution templates we're using, so we
+% implemented the convolution via Fast Fourier Transform on the GPU. 
+% 
+% This allows
+% template evaluation to run in \scream{x ms}, compared to \scream{x ms} for the
+% naive CPU implementation.
 
@@
 
-\begin{comment}
 \subsection{High Resolution Templates and FFT based Convolution}
 \label{sec:fft} 
-We generate high resolution templates with more than 250 HOG cells to capture details of an object to give accurate 2D-3D matching.
-These large templates cause computational burden when computing convolution.
-Though good for detecting accurate model and pose, convolution of high-resolution templates are much more slower since computation time scales linearly with the number of HOG cells in the template.
-To overcome and speed up the convolution, we propose FFT based GPU convolution which scales.
-Suppose there are length $n$ signal and length $m$ filter, naive convolution takes $O(nm)$ time where as FFT-based convolution takes $O\left( (n + m)\log (n+m) \right)$ time.
+We generate high resolution templates with more than 250 HOG cells to capture
+details of an object to give accurate 2D-3D matching. Since naive convolution takes
+$O(nm)$ time where $n$ is the size of the signal and $m$ is the size of the template.
+Whereas, FFT-based convolution takes $O\left( (n + m)\log (n+m) \right)$ time. 
 For large $m$, high resolution template, we can gain computational advantage.
 
-we pad zero to the 2D image features by the largest kernel size.
-And we transform the kernel to match the padded image feature.
-To compute convolution, we compute element-wise product with the transformed kernel and sum all the features.
-Unlike \cite{Podlozhnyuk}, we do not need to shift the data nor kernel if we use simple mathematical trick.
+% We pad zero to the 2D image features by the largest kernel size. And we
+% transform the kernel to match the padded image feature. To compute convolution,
+% we compute element-wise product with the transformed kernel and sum all the
+% features. Unlike \cite{Podlozhnyuk}, we do not need to shift the data nor
+% kernel if we use simple mathematical trick. 
+%   
+% \begin{align}
+%     x_{pad} & = \mathcal{P}_{n+m}(x)\\
+%     y_{pad} & = \mathcal{P}_{n+m}(y)\\
+%     x_{pad} \ast y_{pad} & = \mathcal{F}^{-1}(\mathcal{F}(x_{pad}) \circ \mathcal{F}(y_{pad}))
+% \end{align}
+% 
+% Where $\ast$ is the circular convolution and $\circ$ is the Hadamard Product
+% and $\mathcal{F}$ is the Fourier Transformation and $\mathcal{P}_n$ is the
+% padding operation that append zeros to make vector of size $n$.
+% 
+% For each dimension of features, we transform kernel and image feature into
+% frequency domain using Fast Fourier Transformation. We transform the image into
+% frequency domain once and use the transformed image for all templates.
+% 
+% We implemented the convolution using FFT on GPU and got 10x speed up.
 
-\begin{align}
-    x_{pad} & = \mathcal{P}_{n+m}(x)\\
-    y_{pad} & = \mathcal{P}_{n+m}(y)\\
-    x_{pad} \ast y_{pad} & = \mathcal{F}^{-1}(\mathcal{F}(x_{pad}) \circ \mathcal{F}(y_{pad}))
-\end{align}
-
-  Where $\ast$ is the circular convolution and $\circ$ is the Hadamard Product and $\mathcal{F}$ is the Fourier Transformation and $\mathcal{P}_n$ is the padding operation that append zeros to make vector of size $n$.
-
-For each dimension of features, we transform kernel and image feature into frequency domain using Fast Fourier Transformation.
-We transform the image into frequency domain once and use the transformed image for all templates.
-
-We implemented the convolution using FFT on GPU and got 10x speed up.
-
-[Figure for convolution time for different template resolution, CPU, GPU, naive convolution]
-\end{comment}
+% [Figure for convolution time for different template resolution, CPU, GPU, naive convolution]
 %------------------------------------------------------------------------
 
-\section{Estimating Parameters using MCMC}
+\section{Continuous Viewpoint Estimation using MCMC}
 \label{sec:fine}
@@
 
+Suppose that $x = \[p, m, f\]$ where $p$ is the 3D rotation of the CAD model and
+$m$ is the CAD model index and $f$ is the focal length. Then we sample $x$ using 
 % there are several advantages that was not possible such as \textbf{on-the-fly} template generation and making large number of templates  

### 2014-11-14 egpaper_final.tex

@@
 \section{Related Works}
-\subsection{Whitened Histograms of Orientations (WHO)}
-
-\scream{Should we merge this with NZ-WHO?}
-% History of Whitening and how whitening works
-Recently, Hariharan \etal. introduced Whitened Histograms of Orientations (WHO)
-\cite{Hariharan12}, which used statistics from natural images to whiten HOG
-templates, making them more discriminative. Whitening is a common signal
-processing operation for decorrelating a set of random variables
-\cite{Martinsson05, Belouchrani00}. More formally, suppose that we have a
-$k$-dimensional random variable $X \in \mathcal{R}^k$ with $Cov(X)=\Sigma$. By
-whitening the signal, i.e., $\tilde{X}=\Sigma^{-\frac{1}{2}}(X - E[X])$, we
-remove 2nd order correlation between all features. So, all elements in the
-random variable $\tilde{X} = \left[\tilde{X}_1, \tilde{X}_2, \dots,
-\tilde{X}_k\right]$, become more independent. In the context of HOG features, a
-whitened HOG template will produce Gaussian noise when convolved with a random
-natural image, but a delta-like response on an image matching the template. WHO
-templates are more discriminative than standard HOG templates because they only
-capture the gradients that differentiate the object from random images.
-\scream{requires revision} Hariharan \etal. also interpreted the
-whitening as Linear Discriminant Analysis (LDA) where all classes have different
-means but have the same covariance. The whitening and LDA have the same
-formulation when we make a decision boundary $w = \Sigma^{-1}(\mu_+ - \mu_0)$
-where $\mu_+$ is the features from a class (LDA) or a signal to whiten
-(whitening), $\mu_0$ is the negative class center (LDA) or a signal statistics
-(whitening) and $\Sigma$ is the covariance matrix of classes (LDA) or
-correlation within signal (whitening).
-
-\textcolor{red}{Should we mention how our method improves on this (ie by using CG)? Since we explain in depth later, it would be okay}
 
@@
 
-\textcolor{red}{Again, should we highlight the differences between these methods and ours?}
+\textcolor{red}{Again, should we highlight the differences between these methods and ours? I prefer to do but wouldn't it sounds bad?}
 
@@
 
+Recently, Hariharan \etal. introduced Whitened Histograms of Orientations (WHO)
+\cite{Hariharan12}, which uses statistics from natural images to whiten HOG
+templates, making them more discriminative. Whitening is a common signal
+processing operation for decorrelating a set of random variables
+\cite{Martinsson05, Belouchrani00}. More formally, suppose that we have a
+$k$-dimensional random variable $X \in \mathcal{R}^k$ with $Cov(X)=\Sigma$. By
+whitening the signal, i.e., $\tilde{X}=\Sigma^{-\frac{1}{2}}(X - E[X])$, we
+remove 2nd order correlation between all features. So, all elements in the
+random variable $\tilde{X} = \left[\tilde{X}_1, \tilde{X}_2, \dots,
+\tilde{X}_k\right]$, become more independent. In the context of HOG features, a
+whitened HOG template will produce Gaussian noise when convolved with a random
+natural image, but a delta-like response on an image matching the template. WHO
+templates are more discriminative than standard HOG templates because they only
+capture the gradients that differentiate the object from random images.
+
+Hariharan \etal. interpreted the
+whitening as Linear Discriminant Analysis (LDA) where all classes have different
+means but have the same covariance. The whitening and LDA have the same
+formulation when we make a decision boundary $w = \Sigma^{-1}(\mu_+ - \mu_0)$
+where $\mu_+$ is the features from a class (LDA) or a signal to whiten
+(whitening), $\mu_0$ is the negative class center (LDA) or the signal mean
+(whitening) and $\Sigma$ is the covariance matrix of classes (LDA) or
+the correlation within signal (whitening).
+
 We propose Non-Zero Whitened Histograms of Orientations (NZ-WHO), that are both
-more discriminative than WHO, and can be generated in 70ms (compared to several
-seconds for WHO). This speed up means we can generate templates on the fly,
-allowing our approach to evaluate arbitrary viewpoint hypotheses. 
-\scream{require revision: We propose Non-Zero Whitened Histograms of Orientations (NZ-WHO),
-an improvement over WHO which is both more discriminative than WHO and can be
-computed many orders of magnitude faster than WHO (70ms as opposed to to
-several seconds for WHO). This speedup allows us to generate NZ-WHO templates
-on the fly, allowing us to quickly evaluate arbitrary viewpoint hypotheses.}
+more discriminative than WHO, and can be generated several orders of magnitude
+faster (in 70ms compared to several seconds for WHO). This speed up means we
+can generate templates on the fly, allowing our approach to evaluate arbitrary
+viewpoint hypotheses. 
+%\scream{chris:We propose Non-Zero Whitened Histograms of Orientations (NZ-WHO), an improvement over WHO which is both more discriminative than WHO and can be computed many orders of magnitude faster than WHO (70ms as opposed to to several seconds for WHO).
+This speedup allows us to generate NZ-WHO templates on the fly, allowing us to quickly evaluate arbitrary viewpoint hypotheses.}
 
@@
 Alternatively, we could leave the background textureless \scream{did Hariharan
-do this? Nobody did this before} (see Fig.~\ref{fig:rendering}), but whitening the resulting HOG
+do this?} (see Fig.~\ref{fig:rendering}), but whitening the resulting HOG
 template produces in undesirable background artifacts. These are created when
@@
 
-To remove such artifacts, we construct $x$ using only cells with non-zero gradients.
-After whitening we restore the full template, with the zero-gradient cells left unchanged.
-This approach has the added benefit of reducing the size of the linear system we need to solve, further speeding up our method.
+To remove such artifacts, we construct $x$ using only cells with non-zero
+gradients. After whitening we restore the full template, with the zero-gradient
+cells left unchanged. This approach has the added benefit of reducing the size
+of the linear system we need to solve, further speeding up our method.
 
-Table \ref{tab:who_initializations} provides a detailed comparison of WHO and NZ-WHO templates, illustrating that our method is faster and more discriminative than Whitened Histograms of Orientations.
-\scream{Does the table show this?
-should we do more than AP and realtime analysis?}
+Table \ref{tab:who_initializations} provides a detailed comparison of WHO and
+NZ-WHO templates, illustrating that our method is faster and more
+discriminative than Whitened Histograms of Orientations. \scream{Does the table
+show this? should we do more than AP and realtime analysis?}
 % We compare the performance of WHO and NZ-WHO on 3D Object dataset \cite{Savarese07} and report performance on Table \ref{tab:who_initializations}.

### 2014-11-14 egpaper_final.tex
fixed bad math
second pass over covariance generation

--- 2014-11-14 egpaper_final.tex
@@
 \end{comment}
+\subsection{Rendering Pipeline}
 
@@
 $k$-dimensional random variable $X \in \mathcal{R}^k$ with $Cov(X)=\Sigma$. By
-whitening the signal, i.e., $\tilde{X}=\Sigma^{-\frac{1}{2}}(X - E[X])$, we
+whitening the signal,
+\begin{equation}
+\tilde{X}=\Sigma^{-\frac{1}{2}}(X - E[X]) \label{eq:whitening}
+\end{equation}
+, we
 remove 2nd order correlation between all features. So, all elements in the
@@
 This speed up means we can generate templates on the fly, allowing our approach to evaluate arbitrary viewpoint hypotheses.
+
+\subsubsection{Generating $\Sigma$ and $\mu$}
+\scream{this section seems important to understand the following section but it's also just a re-writing of the Hariharan method}
+In \cite{Hariharan12}, the authors compute the mean and covariance matrix by assuming Wide-Sense Stationarity (WSS) of HOG features
+generated from natural images. That is, they assume the mean of a HOG cell is
+independent of its place in the image, and the autocovariance of cells depends
+only on their relative location.
+
+In one dimension, let $x(u)$ be the feature at location $u$. Then WSS states
+that $\mathbb{E}\left[x(u)\right] = \mu$ for all $u$, and
+\begin{equation}
+\textrm{cov}_x(u,v) = \textrm{cov}_x(0, v-u) = \Gamma(v-u),
+\end{equation} where $\Gamma$ is the autocovariance. For simplicity, we describe the 1D case but this can be easily extended to 2D spatial autocovariance.
+
+Therefore, assuming WSS allows the covariance matrix of templates \emph{of any size} to be synthesized from the autocovariance matrix using a simple lookup.
+
+\subsubsection{Whitening Synthesized Templates}
+Our first innovation is `Non-Zero' whitening.
+When synthesizing detection templates from rendered images, a common problem is how to handle the background.
+If the model is rendered over a natural image background, gradients in the background will be incorporated into the discriminative template, potentially causing false-positives if background elements exist in the query image.
+
+Alternatively, if the background is left textureless \scream{did Hariharan do this?} (see Fig.~\ref{fig:rendering}), whitening the resulting HOG template will produce undesirable background artifacts.
+These are created when centering the template (by subtracting the mean $\mu$), where strong negative weights are introduced in the textureless region (as seen in Fig.~\ref{fig:whocomparison}).
+This could result in positive matches being suppressed due to spurious background gradients.
+
+\scream{might need to match notation with subsequent sections}
+NZ-WHO removes these artifacts so that the background has no effect on the template response.
+Given HOG features $x$, we create a new vector $x'$ which contains only the non-zero elements of $x$.
+We select the same elements of $\mu$ to produce $\mu'$, while the autocovariance lookup is only performed for the cells with non-zero gradient, producing $\Sigma'$ corresponding to the features in $x'$.
+After solving the resulting system (which is now smaller than in the WHO approach) we find
+\begin{equation}
+w'=\Sigma'^{-1}(x' - \mu') \label{eq:nz-who},
+\end{equation}which we reassemble into the final NZ-WHO template $w$ by replacing the non-zero elements of $x$ with the corresponding $w'$ element.
+
+Notice that $\Sigma$ is not square-rooted in Eq.~\ref{eq:nz-who}, whereas it is in the definition of whitening (Eq.~\ref{eq:whitening}).
+This is because the whitened template will only be used in the context of detection, which involves the inner product with the whitened HOG features of the query image $y$:
+\begin{equation}
+(y-\mu)^{T}\Sigma^{-\frac{1}{2}}\Sigma^{-\frac{1}{2}}(x-\mu)\\
+= (y-\mu)^{T} w.
+\end{equation}
+We can therefore capture the whitening of the query image features in $w$.
+
+% We use the GPU to parallelize the lookup of the correct autocovariance cells during covariance matrix syntheses, which is \scream{x} times faster than using the CPU (Figure \ref{fig:covariancetime}).
+
 %\scream{chris:We propose Non-Zero Whitened Histograms of Orientations (NZ-WHO), an improvement over WHO which is both more discriminative than WHO and can be computed many orders of magnitude faster than WHO (70ms as opposed to to several seconds for WHO).
 This speedup allows us to generate NZ-WHO templates on the fly, allowing us to quickly evaluate arbitrary viewpoint hypotheses.}
+
+\subsubsection{Fast Whitening}
 
@@
 
-Our second innovation is 'Non-Zero' whitening.
-When synthesizing detection templates from rendered images, a common problem is how to handle the background.
-If we render the model over a natural image background, gradients in the background will be incorporated into the discriminative template.
-Alternatively, we could leave the background textureless \scream{did Hariharan do this?} (see Fig.~\ref{fig:rendering}), but whitening the resulting HOG template produces in undesirable background artifacts.
-These are created when centering the template (by subtracting the mean $\mu$), where strong negative weights are introduced in the textureless region (as seen in Fig.~\ref{fig:whocomparison}).
-This could result in positive matches being suppressed due to spurious background gradients.
-
-To remove such artifacts, we construct $x$ using only cells with non-zero gradients.
-After whitening we restore the full template, with the zero-gradient cells left unchanged.
-This approach has the added benefit of reducing the size of the linear system we need to solve, further speeding up our method.
-
 Table \ref{tab:who_initializations} provides a detailed comparison of WHO and NZ-WHO templates, illustrating that our method is faster and more discriminative than Whitened Histograms of Orientations.
 \scream{Does the table show this?}
+
 % We compare the performance of WHO and NZ-WHO on 3D Object dataset \cite{Savarese07} and report performance on Table \ref{tab:who_initializations}.
@@
 % \subsection{Whitening and Textureless Background}
-
+\begin{comment}
 \subsection{Constructing the Covariance Matrix}
@@
 the CPU (Figure \ref{fig:covariancetime}).
+
+\end{comment}
 

### 2014-11-14 egpaper_final.tex

--- 2014-11-14 egpaper_final.tex
@@
 
-We propose Non-Zero Whitened Histograms of Orientations (NZ-WHO), that are both
-more discriminative than WHO, and can be generated several orders of magnitude
-faster (in 70ms compared to several seconds for WHO). This speed up means we
-can generate templates on the fly, allowing our approach to evaluate arbitrary
-viewpoint hypotheses. 
+We propose Non-Zero Whitened Histograms of Orientations (NZ-WHO), that are both more discriminative than WHO, and can be generated several orders of magnitude faster (in 70ms compared to several seconds for WHO).
+This speed up means we can generate templates on the fly, allowing our approach to evaluate arbitrary viewpoint hypotheses.
+
+\subsubsection{Generating $\Sigma$ and $\mu$}
+\scream{this section seems important to understand the following section but it's also just a re-writing of the Hariharan method}
+In \cite{Hariharan12}, the authors compute the mean and covariance matrix by assuming Wide-Sense Stationarity (WSS) of HOG features
+generated from natural images. That is, they assume the mean of a HOG cell is
+independent of its place in the image, and the autocovariance of cells depends
+only on their relative location.
+
+In one dimension, let $x(u)$ be the feature at location $u$. Then WSS states
+that $\mathbb{E}\left[x(u)\right] = \mu$ for all $u$, and
+\begin{equation}
+\textrm{cov}_x(u,v) = \textrm{cov}_x(0, v-u) = \Gamma(v-u),
+\end{equation} where $\Gamma$ is the autocovariance. For simplicity, we describe the 1D case but this can be easily extended to 2D spatial autocovariance.
+
+Therefore, assuming WSS allows the covariance matrix of templates \emph{of any size} to be synthesized from the autocovariance matrix using a simple lookup.
+
+\subsubsection{Whitening Synthesized Templates}
+Our first innovation is `Non-Zero' whitening.
+When synthesizing detection templates from rendered images, a common problem is how to handle the background.
+If the model is rendered over a natural image background, gradients in the background will be incorporated into the discriminative template, potentially causing false-positives if background elements exist in the query image.
+
+Alternatively, if the background is left textureless \scream{did Hariharan do this?} (see Fig.~\ref{fig:rendering}), whitening the resulting HOG template will produce undesirable background artifacts.
+These are created when centering the template (by subtracting the mean $\mu$), where strong negative weights are introduced in the textureless region (as seen in Fig.~\ref{fig:whocomparison}).
+This could result in positive matches being suppressed due to spurious background gradients.
+
+\scream{might need to match notation with subsequent sections}
+NZ-WHO removes these artifacts so that the background has no effect on the template response.
+Given HOG features $x$, we create a new vector $x'$ which contains only the non-zero elements of $x$.
+We select the same elements of $\mu$ to produce $\mu'$, while the autocovariance lookup is only performed for the cells with non-zero gradient, producing $\Sigma'$ corresponding to the features in $x'$.
+After solving the resulting system (which is now smaller than in the WHO approach) we find
+\begin{equation}
+w'=\Sigma'^{-1}(x' - \mu') \label{eq:nz-who},
+\end{equation}which we reassemble into the final NZ-WHO template $w$ by replacing the non-zero elements of $x$ with the corresponding $w'$ element.
+
+Notice that $\Sigma$ is not square-rooted in Eq.~\ref{eq:nz-who}, whereas it is in the definition of whitening (Eq.~\ref{eq:whitening}).
+This is because the whitened template will only be used in the context of detection, which involves the inner product with the whitened HOG features of the query image $y$:
+\begin{equation}
+(y-\mu)^{T}\Sigma^{-\frac{1}{2}}\Sigma^{-\frac{1}{2}}(x-\mu)\\
+= (y-\mu)^{T} w.
+\end{equation}
+We can therefore capture the whitening of the query image features in $w$.
+
+% We use the GPU to parallelize the lookup of the correct autocovariance cells during covariance matrix syntheses, which is \scream{x} times faster than using the CPU (Figure \ref{fig:covariancetime}).
+
 %\scream{chris:We propose Non-Zero Whitened Histograms of Orientations (NZ-WHO), an improvement over WHO which is both more discriminative than WHO and can be computed many orders of magnitude faster than WHO (70ms as opposed to to several seconds for WHO).
@@
 
-The computational efficiency of our approach comes from using the iterative
-conjugate gradient method to whiten the HOG template. Whitening a feature
+\subsubsection{Fast Whitening}
+
 vector $x$ requires a system of linear equations $\Sigma w = (x - \mu)$ to be
@@
 
-Our second innovation is 'Non-Zero' whitening. When synthesizing detection
-templates from rendered images, a common problem is how to handle the
-background. If we render the model over a natural image background, gradients
+Table \ref{tab:who_initializations} provides a detailed comparison of WHO and NZ-WHO templates, illustrating that our method is faster and more discriminative than Whitened Histograms of Orientations.
+\scream{Does the table show this?}
+
 in the background will be incorporated into the discriminative template.
@@
 
-To remove such artifacts, we construct $x$ using only cells with non-zero
 gradients. After whitening we restore the full template, with the zero-gradient
@@
 
-Table \ref{tab:who_initializations} provides a detailed comparison of WHO and
 NZ-WHO templates, illustrating that our method is faster and more
@@
 
-Suppose that $x = \[p, m, f\]$ where $p$ is the 3D rotation of the CAD model and
+Suppose that $x = [p, m, f]$ where $p$ is the 3D rotation of the CAD model and
 $m$ is the CAD model index and $f$ is the focal length. Then we sample $x$ using 

### 2014-11-14 egpaper_final.tex
MCMC on progress

--- 2014-11-14 egpaper_final.tex
@@
 
-We modeled the distribution of the convolution as an exponential distribution
-and used Gaussian as our proposal distribution.
+To fine-tune continuous pose and location of object, we require strong
+initialization. The initialization is a rough bounding box with small context
+and viewpoint. Since most of the standard detectors does not provide viewpoint
+of an object, we first run an ensemble of NZ-WHO templates to get rough
+viewpoints. Once we get rough viewpoint, we initialize the proposal $x_0$ and
+start sampling proposals.
 
-We run experiments on PASCAL 2007 car category images with at least one car
-(num images) and got x percent improvement after fine tuning.
+We modeled the distribution of object location and pose as an exponential distribution. 
+For proposal distribution, we used Gaussian distribution to propose next viewpoint and for viewpoint proposals
+and uniform distribution for model change proposals.
 
-Suppose that $x = \[p, m, f\]$ where $p$ is the 3D rotation of the CAD model and
-$m$ is the CAD model index and $f$ is the focal length. Then we sample $x$ using 
+More formally, suppose that $x = [p, m, f]$ where $p$ is the 3D rotation of the CAD model and
+$m$ is the CAD model index and $f$ is the focal length. We use Metropolis Hastings
+to optimize $x$.
+
+\begin{align}
+    A(x \rightarrow x') & =  min\left( 1,  \frac{P(x' g(x') \rightarrow x)}{P(x) g(x \rightarrow x')}\right) \\
+    g(x \rightarrow x + p_i') & \sim \mathcal{N}(\mu = 0,\sigma = c_1) \quad i \in \{1,2,3\}\\
+    g(x \rightarrow x + f') & \sim \mathcal{N}(\mu = 0,\sigma = c_2)\\
+    g(x \rightarrow x + m') & \sim c_3 \delta(m) + (1-c_3) Unif(1,M)
+\end{align}
+
+Where $g$ is the proposal distribution and $P$ is the distribution of which we
+defined using Gaussian distribution around previous state. $A$ is the
+acceptance probability where we accept new proposal with $A(x \rightarrow x')$.
+
+\begin{align}
+    P(x) & \sim e^{ c_4 \max_{s} w(x) \ast \mathcal{T}_s(\mathcal{I}) }
+\end{align}
+
+$P$ is the distribution of the pose and location of an object on image
+$\mathcal{I}$. One can also think of the image as an image cropped by detection
+bounding box. We synthesize covariance matrix and create NZ-WHO template $w(x)$ for particular viewpoint, focal length and CAD model.
+
+We initialize the $x$ using the result from the previous stage where we run our ensemble or NZ-WHO templates to get rough estimate.
+
+In sum, for new proposal $x'$, we make a NZ-WHO template on the fly 
+We found out that it requires good initialization to converge to local minima.
+
+We represented the probability using exponential family.
+
+So our model favors large convolution score $\max_{s} w(x) \ast T(\mathcal{I})$.
+
 % there are several advantages that was not possible such as \textbf{on-the-fly} template generation and making large number of templates  

### 2014-11-14 egpaper_final.tex

--- 2014-11-14 egpaper_final.tex
@@
 
-We modeled the distribution of the convolution as an exponential distribution
-and used Gaussian as our proposal distribution.
+To fine-tune continuous pose and location of object, we require strong
+initialization. The initialization is a rough bounding box with small context
+and viewpoint. Since most of the standard detectors does not provide viewpoint
+of an object, we first run an ensemble of NZ-WHO templates to get rough
+viewpoints. Once we get rough viewpoint, we initialize the proposal $x_0$ and
+start sampling proposals.
 
-We run experiments on PASCAL 2007 car category images with at least one car
-(num images) and got x percent improvement after fine tuning.
+We modeled the distribution of object location and pose as an exponential distribution. 
+For proposal distribution, we used Gaussian distribution to propose next viewpoint and for viewpoint proposals
+and uniform distribution for model change proposals.
 
-Suppose that $x = [p, m, f]$ where $p$ is the 3D rotation of the CAD model and
-$m$ is the CAD model index and $f$ is the focal length. Then we sample $x$ using 
+More formally, suppose that $x = [p, m, f]$ where $p$ is the 3D rotation of the CAD model and
+$m$ is the CAD model index and $f$ is the focal length. We use Metropolis Hastings
+to optimize $x$.
+
+\begin{align}
+    A(x \rightarrow x') & =  min\left( 1,  \frac{P(x' g(x') \rightarrow x)}{P(x) g(x \rightarrow x')}\right) \\
+    g(x \rightarrow x + p_i') & \sim \mathcal{N}(\mu = 0,\sigma = c_1) \quad i \in \{1,2,3\}\\
+    g(x \rightarrow x + f') & \sim \mathcal{N}(\mu = 0,\sigma = c_2)\\
+    g(x \rightarrow x + m') & \sim c_3 \delta(m) + (1-c_3) Unif(1,M)
+\end{align}
+
+Where $g$ is the proposal distribution and $P$ is the distribution of which we
+defined using Gaussian distribution around previous state. $A$ is the
+acceptance probability where we accept new proposal with $A(x \rightarrow x')$.
+
+\begin{align}
+    P(x) & \sim e^{ c_4 \max_{s} w(x) \ast \mathcal{T}_s(\mathcal{I}) }
+\end{align}
+
+$P$ is the distribution of the pose and location of an object on image
+$\mathcal{I}$. One can also think of the image as an image cropped by detection
+bounding box. We synthesize covariance matrix and create NZ-WHO template $w(x)$ for particular viewpoint, focal length and CAD model.
+
+We initialize the $x$ using the result from the previous stage where we run our ensemble or NZ-WHO templates to get rough estimate.
+
+In sum, for new proposal $x'$, we make a NZ-WHO template on the fly 
+We found out that it requires good initialization to converge to local minima.
+
+We represented the probability using exponential family.
+
+So our model favors large convolution score $\max_{s} w(x) \ast T(\mathcal{I})$.
+
 % there are several advantages that was not possible such as \textbf{on-the-fly} template generation and making large number of templates  

### 2014-11-14 egpaper_final.tex
second pass on CG

--- 2014-11-14 egpaper_final.tex
@@
 
-\textcolor{red}{Again, should we highlight the differences between these methods and ours? I prefer to do but wouldn't it sounds bad?}
+\textcolor{red}{Again, should we highlight the differences between these methods and ours?}
 
@@
 \subsection{Overview}
-Our method attempts to match CAD models to 2D images, determining the best
-model within a class, its pose and scale, and the focal length of the camera
-used to produce the image. These parameters are first coarsely estimated using
-a discrete bank of detectors trained offline, before they are refined using
-MCMC by generating new detectors on the fly.
+Our method attempts to match CAD models to 2D images, determining the best model within a class, its pose and scale, and the focal length of the camera used to produce the image.
+These parameters are first coarsely estimated using a discrete bank of detectors trained offline, before they are refined using MCMC by generating new detectors on the fly.
 
 The basic detection method underlying our approach is HOG template matching.
-However, we propose a new HOG variant called Non-Zero Whitened Histograms of
-Orientations (NZ-WHO), where the HOG templates are whitened using statistics
-found from a random collection of natural images, producing a more
-discriminative template.
+However, we propose a new HOG variant called Non-Zero Whitened Histograms of Orientations (NZ-WHO), where the HOG templates are whitened using statistics found from a random collection of natural images, producing a more discriminative template.
 
-In addition to the library of CAD models that will be matched to the query
-images, our method requires a collection of random natural images. Offline, we
-compute HOG features of these images and record their mean and spatial
-autocovariance. The images are not used during testing, only the statistics
-generated from them.
+In addition to the library of CAD models that will be matched to the query images, our method requires a collection of random natural images.
+Offline, we compute HOG features of these images and record their mean and spatial autocovariance.
+The images are not used during testing, only the statistics generated from them.
 
-Notably, we do not require any labelled training images of the objects to be
-detected. Our templates are generated exclusively by rendering CAD models from
-our library. From these renderings we produce novel HOG-like features we call
-Non-Zero Whitened Histograms of Orientations (NZ-WHO), which use the natural
-image statistics found offline to whiten a standard HOG template, making it
-more discriminative.
+Notably, we do not require any labelled training images of the objects to be detected.
+Our templates are generated exclusively by rendering CAD models from our library.
+From these renderings we produce novel HOG-like features we call Non-Zero Whitened Histograms of Orientations (NZ-WHO), which use the natural image statistics found offline to whiten a standard HOG template, making it more discriminative.
 
-The matching proceeds in two steps: First, we apply a bank of pre-trained
-detectors to the image, corresponding to a set of discrete viewpoints, scales,
-and object models. This provides a rough estimate of these parameters. Second,
-we refine these parameters using MCMC, where each candidate is evaluated by
-rendering a new whitened template on the fly.
+The matching proceeds in two steps: First, we apply a bank of pre-trained detectors to the image, corresponding to a set of discrete viewpoints, scales, and object models.
+This provides a rough estimate of these parameters.
+Second, we refine these parameters using MCMC, where each candidate is evaluated by rendering a new whitened template on the fly.
 
-Optionally, our algorithm can be initialized using proposal bounding boxes from
-state-of-the-art object detectors \cite{Felzenszwalb10,Girshick14} before
-executing the two steps above. In this scenario, our approach provides a means
-to augment standard bounding box detectors with more interesting 3D
-information.
+Optionally, our algorithm can be initialized using proposal bounding boxes from state-of-the-art object detectors \cite{Felzenszwalb10,Girshick14} before executing the two steps above.
+In this scenario, our approach provides a means to augment standard bounding box detectors with more interesting 3D information.
 
@@
 
+Table \ref{tab:who_initializations} provides a detailed comparison of WHO and NZ-WHO templates, illustrating that our method is faster and more discriminative than Whitened Histograms of Orientations.
+\scream{Does the table show this?}
+
 \subsubsection{Generating $\Sigma$ and $\mu$}
@@
 
-\subsubsection{Fast Whitening}
+\subsubsection{Fast Whitening using Conjugate Gradient}
 
-vector $x$ requires a system of linear equations $\Sigma w = (x - \mu)$ to be
-solved, usually by decomposing the covariance matrix $\Sigma$ (with LU or
-Cholesky decomposition). Since the covariance matrices of HOG templates have
-nice spectral properties (see Section \ref{sec:fast_whitening}), the conjugate
-gradient method will converge to the solution several orders of magnitude
-faster than decomposition methods.
+The computational efficiency of our approach comes from using the iterative conjugate gradient method to whiten the HOG template.
+Whitening the non-zero feature vector $x'$ requires a system of linear equations $\Sigma' w' = (x' - \mu')$ to be solved.
+In
+\cite{Hariharan12}, the authors make use of the fact that covariance matrices
+are symmetric and positive semidefinite to solve the system via the Cholesky
+decomposition, which requires $O(n^3)$ time.
 
-Table \ref{tab:who_initializations} provides a detailed comparison of WHO and NZ-WHO templates, illustrating that our method is faster and more discriminative than Whitened Histograms of Orientations.
-\scream{Does the table show this?}
+The conjugate gradient method is an iterative algorithm for solving symmetric positive definite systems which runs in $O(n^2\kappa)$ time, where $\kappa$ is the condition number of the matrix.
+This makes conjugate gradient faster than decomposition for matrices with small condition
+numbers relative to their size.
 
-in the background will be incorporated into the discriminative template.
-Alternatively, we could leave the background textureless \scream{did Hariharan
-do this?} (see Fig.~\ref{fig:rendering}), but whitening the resulting HOG
-template produces in undesirable background artifacts. These are created when
-centering the template (by subtracting the mean $\mu$), where strong negative
-weights are introduced in the textureless region (as seen in
-Fig.~\ref{fig:whocomparison}). This could result in positive matches being
-suppressed due to spurious background gradients.
+The covariance matrix for HOG templates is typically ill-conditioned, but we can add a regularization constant to the diagonal to reduce its condition number to the point where the conjugate gradient method will converge quickly.
+We use a constant of $0.15$, which reduces the condition number from $10^{20}$ to $50$, much smaller than the dimension of the matrix (7000).
 
-gradients. After whitening we restore the full template, with the zero-gradient
-cells left unchanged. This approach has the added benefit of reducing the size
-of the linear system we need to solve, further speeding up our method.
+As a result, a GPU implementation of conjugate gradient converges in \scream{x
+ms}, two orders of magnitude faster than the system can be solved using the
+Cholesky factorization (\scream{5 s}).
 
-NZ-WHO templates, illustrating that our method is faster and more
-discriminative than Whitened Histograms of Orientations. \scream{Does the table
-show this? should we do more than AP and realtime analysis?}
+\subsubsection{Fast Convolution using the FFT}
+
 % We compare the performance of WHO and NZ-WHO on 3D Object dataset \cite{Savarese07} and report performance on Table \ref{tab:who_initializations}.
@@
 We use the GPU to parallelize the lookup of the correct autocovariance cells
-during covariance matrix syntheses, which is an order of magnitude times faster than using
+during covariance matrix syntheses, which is \scream{x} times faster than using
 the CPU (Figure \ref{fig:covariancetime}).
@@
 
-\subsection{Fast Whitening and Convolution}
-\label{sec:fast_whitening}
-\begin{figure}[t]
-  \begin{center}
-     \includegraphics[width=0.9\linewidth]{whiten_orig_depth} 
-  \end{center}
-  \caption{Realistic rendering and depth}
-  \label{fig:rendering}
-  \end{figure}
-
-To whiten a signal $x$, we have to solve $\Sigma w = x - \mu$. In
-\cite{Hariharan12}, the authors make use of the fact that covariance matrices
-are Hermitian and positive semidefinite to solve the system via the Cholesky
-decomposition, which is twice as fast as the LU decomposition. These
-decompositions require $O(n^3)$ time, whereas the conjugate gradient method
-takes $O(n^2\kappa)$ time, where $\kappa$ is the condition number of the matrix.
-This makes conjugate gradient a faster option for matrices with small condition
-numbers relative to their size.
-
-% Figure \ref{fig:spectral} shows the singular values of a covariance matrix for
-% one HOG template after a small regularization constant is added to the diagonal.
-% The condition number of of the matrix is , much smaller than the size
-% of the matrix (7500). As a result, conjugate gradient converges in 50
-% ms, two orders of magnitude faster than the system can be solved using the
-% Cholesky factorization (5 sec).
-
-% The final challenge in on-the-fly template evaluation is performing the
-% convolution between the template and the target image. Standard convolution
-% would be prohibitively slow for the high resolution templates we're using, so we
-% implemented the convolution via Fast Fourier Transform on the GPU. 
-% 
-% This allows
-% template evaluation to run in \scream{x ms}, compared to \scream{x ms} for the
-% naive CPU implementation.
+The final challenge in on-the-fly template evaluation is performing the
+convolution between the template and the target image. Standard convolution
+would be prohibitively slow for the high resolution templates we're using, so we
+implemented the convolution via Fast Fourier Transform on the GPU. This allows
+template evaluation to run in \scream{x ms}, compared to \scream{x ms} for the
+naive CPU implementation.
 
@@
 \subsection{Variations of WHO}
-
+\scream{sam thinks this should be moved to the experiments section}
 We empirically found out that NZ-WHO performs reasonably well without time
@@
 \end{center}
-\caption{Average Precision(AP) and Mean Precision in Pose Estimation (MPPE)
-\cite{Lopez-Sastre11} variations of WHO on 3DObject Car
-dataset\cite{Savarese07}. WHO refers to standard WHO using the method presented
-in \cite{Hariharan12}, WHO-CG uses iterative Conjugate Gradient method to
-generate WHO. WHO-CG-Z uses whiten the whole template and zero out textureless
-region. NZ-WHO-CG is the NZ-WHO which whitens only non-zero cells using
-iterative Conjugate Gradient method. The time column indicates the time to
-generate one template. We followed calibration procedure presented in
-\cite{Aubry14}.}
+\caption{Average Precision(AP) and Mean Precision in Pose Estimation (MPPE) \cite{Lopez-Sastre11} variations of WHO on 3DObject Car dataset\cite{Savarese07}.
+WHO refers to standard WHO using the method presented in \cite{Hariharan12}, WHO-CG uses iterative Conjugate Gradient method to generate WHO.
+WHO-CG-Z uses whiten the whole template and zero out textureless region.
+NZ-WHO-CG is the NZ-WHO which whitens only non-zero cells using iterative Conjugate Gradient method.
+The time column indicates the time to generate one template.
+We followed calibration procedure presented in \cite{Aubry14}.}
 \label{tab:who_initializations}
@@
 
+\begin{comment}
 \subsection{High Resolution Templates and FFT based Convolution}
 \label{sec:fft} 
-We generate high resolution templates with more than 250 HOG cells to capture
-details of an object to give accurate 2D-3D matching. Since naive convolution takes
-$O(nm)$ time where $n$ is the size of the signal and $m$ is the size of the template.
-Whereas, FFT-based convolution takes $O\left( (n + m)\log (n+m) \right)$ time. 
+We generate high resolution templates with more than 250 HOG cells to capture details of an object to give accurate 2D-3D matching.
+These large templates cause computational burden when computing convolution.
+Though good for detecting accurate model and pose, convolution of high-resolution templates are much more slower since computation time scales linearly with the number of HOG cells in the template.
+To overcome and speed up the convolution, we propose FFT based GPU convolution which scales.
+Suppose there are length $n$ signal and length $m$ filter, naive convolution takes $O(nm)$ time where as FFT-based convolution takes $O\left( (n + m)\log (n+m) \right)$ time.
 For large $m$, high resolution template, we can gain computational advantage.
 
-% We pad zero to the 2D image features by the largest kernel size. And we
-% transform the kernel to match the padded image feature. To compute convolution,
-% we compute element-wise product with the transformed kernel and sum all the
-% features. Unlike \cite{Podlozhnyuk}, we do not need to shift the data nor
-% kernel if we use simple mathematical trick. 
-%   
-% \begin{align}
-%     x_{pad} & = \mathcal{P}_{n+m}(x)\\
-%     y_{pad} & = \mathcal{P}_{n+m}(y)\\
-%     x_{pad} \ast y_{pad} & = \mathcal{F}^{-1}(\mathcal{F}(x_{pad}) \circ \mathcal{F}(y_{pad}))
-% \end{align}
-% 
-% Where $\ast$ is the circular convolution and $\circ$ is the Hadamard Product
-% and $\mathcal{F}$ is the Fourier Transformation and $\mathcal{P}_n$ is the
-% padding operation that append zeros to make vector of size $n$.
-% 
-% For each dimension of features, we transform kernel and image feature into
-% frequency domain using Fast Fourier Transformation. We transform the image into
-% frequency domain once and use the transformed image for all templates.
-% 
-% We implemented the convolution using FFT on GPU and got 10x speed up.
+we pad zero to the 2D image features by the largest kernel size.
+And we transform the kernel to match the padded image feature.
+To compute convolution, we compute element-wise product with the transformed kernel and sum all the features.
+Unlike \cite{Podlozhnyuk}, we do not need to shift the data nor kernel if we use simple mathematical trick.
 
-% [Figure for convolution time for different template resolution, CPU, GPU, naive convolution]
+\begin{align}
+    x_{pad} & = \mathcal{P}_{n+m}(x)\\
+    y_{pad} & = \mathcal{P}_{n+m}(y)\\
+    x_{pad} \ast y_{pad} & = \mathcal{F}^{-1}(\mathcal{F}(x_{pad}) \circ \mathcal{F}(y_{pad}))
+\end{align}
+
+  Where $\ast$ is the circular convolution and $\circ$ is the Hadamard Product and $\mathcal{F}$ is the Fourier Transformation and $\mathcal{P}_n$ is the padding operation that append zeros to make vector of size $n$.
+
+For each dimension of features, we transform kernel and image feature into frequency domain using Fast Fourier Transformation.
+We transform the image into frequency domain once and use the transformed image for all templates.
+
+We implemented the convolution using FFT on GPU and got 10x speed up.
+
+[Figure for convolution time for different template resolution, CPU, GPU, naive convolution]
+\end{comment}
 %------------------------------------------------------------------------
 
-\section{Continuous Viewpoint Estimation using MCMC}
+\section{Estimating Parameters using MCMC}
 \label{sec:fine}
@@
 camera focal length.
+
+Our method begins by convolving the
 
@@
 
-Suppose that $x = [p, m, f]$ where $p$ is the 3D rotation of the CAD model and
-$m$ is the CAD model index and $f$ is the focal length. Then we sample $x$ using 
 % there are several advantages that was not possible such as \textbf{on-the-fly} template generation and making large number of templates  

### 2014-11-14 egpaper_final.tex

@@
 
-We modeled the distribution of the convolution as an exponential distribution
-and used Gaussian as our proposal distribution.
+To fine-tune continuous pose and location of object, we require strong
+initialization. The initialization is a rough bounding box with small context
+and viewpoint. Since most of the standard detectors does not provide viewpoint
+of an object, we first run an ensemble of NZ-WHO templates to get rough
+viewpoints. Once we get rough viewpoint, we initialize the proposal $x_0$ and
+start sampling proposals.
 
-We run experiments on PASCAL 2007 car category images with at least one car
-(num images) and got x percent improvement after fine tuning.
+We modeled the distribution of object location and pose as an exponential distribution. 
+For proposal distribution, we used Gaussian distribution to propose next viewpoint and for viewpoint proposals
+and uniform distribution for model change proposals.
 
+More formally, suppose that $x = [p, m, f]$ where $p$ is the 3D rotation of the CAD model and
+$m$ is the CAD model index and $f$ is the focal length. We use Metropolis Hastings
+to optimize $x$.
+
+\begin{align}
+    A(x \rightarrow x') & =  min\left( 1,  \frac{P(x' g(x') \rightarrow x)}{P(x) g(x \rightarrow x')}\right) \\
+    g(x \rightarrow x + p_i') & \sim \mathcal{N}(\mu = 0,\sigma = c_1) \quad i \in \{1,2,3\}\\
+    g(x \rightarrow x + f') & \sim \mathcal{N}(\mu = 0,\sigma = c_2)\\
+    g(x \rightarrow x + m') & \sim c_3 \delta(m) + (1-c_3) Unif(1,M)
+\end{align}
+
+Where $g$ is the proposal distribution and $P$ is the distribution of which we
+defined using Gaussian distribution around previous state. $A$ is the
+acceptance probability where we accept new proposal with $A(x \rightarrow x')$.
+
+\begin{align}
+    P(x) & \sim e^{ c_4 \max_{s} w(x) \ast \mathcal{T}_s(\mathcal{I}) }
+\end{align}
+
+$P$ is the distribution of the pose and location of an object on image
+$\mathcal{I}$. One can also think of the image as an image cropped by detection
+bounding box. We synthesize covariance matrix and create NZ-WHO template $w(x)$ for particular viewpoint, focal length and CAD model.
+
+We initialize the $x$ using the result from the previous stage where we run our ensemble or NZ-WHO templates to get rough estimate.
+
+In sum, for new proposal $x'$, we make a NZ-WHO template on the fly 
+We found out that it requires good initialization to converge to local minima.
+
+We represented the probability using exponential family.
+
+So our model favors large convolution score $\max_{s} w(x) \ast T(\mathcal{I})$. 
 % there are several advantages that was not possible such as \textbf{on-the-fly} template generation and making large number of templates  

### 2014-11-14 egpaper_final.tex
modified overview

--- 2014-11-14 egpaper_final.tex
@@
 used to produce the image. These parameters are first coarsely estimated using
-a discrete bank of detectors trained offline, before they are refined using
+an ensemble of templates generated offline, before they are refined using
 MCMC by generating new detectors on the fly.
 
-The basic detection method underlying our approach is HOG template matching.
-However, we propose a new HOG variant called Non-Zero Whitened Histograms of
-Orientations (NZ-WHO), where the HOG templates are whitened using statistics
-found from a random collection of natural images, producing a more
-discriminative template.
+% The basic detection method underlying our approach is WHO template matching.
+% However, we propose a new WHO variant called Non-Zero Whitened Histograms of
+% Orientations (NZ-WHO), where the variant of WHO templates are made from 
+% synthetic rendering to with
 
-In addition to the library of CAD models that will be matched to the query
-images, our method requires a collection of random natural images. Offline, we
-compute HOG features of these images and record their mean and spatial
-autocovariance. The images are not used during testing, only the statistics
-generated from them.
+Our method In addition to the library of CAD models that will be matched to the query
+images, our method requires a feature statistics which can be collected once and for all.
+
+% images, our method requires a collection of random natural images. Offline, we
+% compute HOG features of these images and record their mean and spatial
+% autocovariance. The images are not used during testing, only the statistics
+% generated from them.
 
@@
 
-Optionally, our algorithm can be initialized using proposal bounding boxes from
+Our ensemble of NZ-WHO templates can work as a detector but our algorithm 
+can be initialized using proposal bounding boxes from
 state-of-the-art object detectors \cite{Felzenszwalb10,Girshick14} before
@@
 
+We used a collection of CAD models to make exemplar renderings of CAD models and for viewpoints. The
+CAD models are cached so that when we fine-tune 2D-3D matching, so it can be rendered instantaneously.
+We made the renderings to change focal length and yaw, pitch, roll so that we can fine tune the matching
+continuously.
+
 \subsection{Non-Zero Whitened Histograms of Orientations (NZ-WHO)}
@@
 
-Hariharan \etal. interpreted the
+Hariharan \etal. explained the
 whitening as Linear Discriminant Analysis (LDA) where all classes have different
-means but have the same covariance. The whitening and LDA have the same
-formulation when we make a decision boundary $w = \Sigma^{-1}(\mu_+ - \mu_0)$
-where $\mu_+$ is the features from a class (LDA) or a signal to whiten
-(whitening), $\mu_0$ is the negative class center (LDA) or the signal mean
-(whitening) and $\Sigma$ is the covariance matrix of classes (LDA) or
-the correlation within signal (whitening).
+means but have the same covariance.
 
-We propose Non-Zero Whitened Histograms of Orientations (NZ-WHO), that are both more discriminative than WHO, and can be generated several orders of magnitude faster (in 70ms compared to several seconds for WHO).
-This speed up means we can generate templates on the fly, allowing our approach to evaluate arbitrary viewpoint hypotheses.
+% The whitening and LDA have the same
+% formulation when we make a decision boundary $w = \Sigma^{-1}(\mu_+ - \mu_0)$
+% where $\mu_+$ is the features from a class (LDA) or a signal to whiten
+% (whitening), $\mu_0$ is the negative class center (LDA) or the signal mean
+% (whitening) and $\Sigma$ is the covariance matrix of classes (LDA) or
+% the correlation within signal (whitening).
 
-\subsubsection{Generating $\Sigma$ and $\mu$}
-\scream{this section seems important to understand the following section but it's also just a re-writing of the Hariharan method}
+We propose Non-Zero Whitened Histograms of Orientations (NZ-WHO), that are both
+more discriminative than WHO, and can be generated several orders of magnitude
+faster (in 70ms compared to several seconds for WHO). This speed up means we
+can generate templates on the fly, allowing our approach to evaluate arbitrary
+viewpoint hypotheses.
+
+\subsubsection{Non-Zero Covariance}
 In \cite{Hariharan12}, the authors compute the mean and covariance matrix by assuming Wide-Sense Stationarity (WSS) of HOG features
@@
 
-Therefore, assuming WSS allows the covariance matrix of templates \emph{of any size} to be synthesized from the autocovariance matrix using a simple lookup.
+Therefore, assuming WSS allows the covariance matrix of templates \emph{of any
+size} to be synthesized from the autocovariance matrix using a simple lookup.
+
+Our method requires generating a covariance matrix of non-zero cells
 

### 2014-11-14 egpaper_final.tex

--- 2014-11-14 egpaper_final.tex
@@
 \subsection{Overview}
-Our method attempts to match CAD models to 2D images, determining the best model within a class, its pose and scale, and the focal length of the camera used to produce the image.
-These parameters are first coarsely estimated using a discrete bank of detectors trained offline, before they are refined using MCMC by generating new detectors on the fly.
+Our method attempts to match CAD models to 2D images, determining the best
+model within a class, its pose and scale, and the focal length of the camera
+used to produce the image. These parameters are first coarsely estimated using
+an ensemble of templates generated offline, before they are refined using
+MCMC by generating new detectors on the fly.
 
-The basic detection method underlying our approach is HOG template matching.
-However, we propose a new HOG variant called Non-Zero Whitened Histograms of Orientations (NZ-WHO), where the HOG templates are whitened using statistics found from a random collection of natural images, producing a more discriminative template.
+% The basic detection method underlying our approach is WHO template matching.
+% However, we propose a new WHO variant called Non-Zero Whitened Histograms of
+% Orientations (NZ-WHO), where the variant of WHO templates are made from 
+% synthetic rendering to with
 
-In addition to the library of CAD models that will be matched to the query images, our method requires a collection of random natural images.
-Offline, we compute HOG features of these images and record their mean and spatial autocovariance.
-The images are not used during testing, only the statistics generated from them.
+Our method In addition to the library of CAD models that will be matched to the query
+images, our method requires a feature statistics which can be collected once and for all.
 
-Notably, we do not require any labelled training images of the objects to be detected.
-Our templates are generated exclusively by rendering CAD models from our library.
-From these renderings we produce novel HOG-like features we call Non-Zero Whitened Histograms of Orientations (NZ-WHO), which use the natural image statistics found offline to whiten a standard HOG template, making it more discriminative.
+% images, our method requires a collection of random natural images. Offline, we
+% compute HOG features of these images and record their mean and spatial
+% autocovariance. The images are not used during testing, only the statistics
+% generated from them.
 
-The matching proceeds in two steps: First, we apply a bank of pre-trained detectors to the image, corresponding to a set of discrete viewpoints, scales, and object models.
-This provides a rough estimate of these parameters.
-Second, we refine these parameters using MCMC, where each candidate is evaluated by rendering a new whitened template on the fly.
+Notably, we do not require any labelled training images of the objects to be
+detected. Our templates are generated exclusively by rendering CAD models from
+our library. From these renderings we produce novel HOG-like features we call
+Non-Zero Whitened Histograms of Orientations (NZ-WHO), which use the natural
+image statistics found offline to whiten a standard HOG template, making it
+more discriminative.
 
-Optionally, our algorithm can be initialized using proposal bounding boxes from state-of-the-art object detectors \cite{Felzenszwalb10,Girshick14} before executing the two steps above.
-In this scenario, our approach provides a means to augment standard bounding box detectors with more interesting 3D information.
+The matching proceeds in two steps: First, we apply a bank of pre-trained
+detectors to the image, corresponding to a set of discrete viewpoints, scales,
+and object models. This provides a rough estimate of these parameters. Second,
+we refine these parameters using MCMC, where each candidate is evaluated by
+rendering a new whitened template on the fly.
 
+Our ensemble of NZ-WHO templates can work as a detector but our algorithm 
+can be initialized using proposal bounding boxes from
+state-of-the-art object detectors \cite{Felzenszwalb10,Girshick14} before
+executing the two steps above. In this scenario, our approach provides a means
+to augment standard bounding box detectors with more interesting 3D
+information.
 \begin{comment}
@@
 
-Hariharan \etal. interpreted the
+Hariharan \etal. explained the
 whitening as Linear Discriminant Analysis (LDA) where all classes have different
-means but have the same covariance. The whitening and LDA have the same
-formulation when we make a decision boundary $w = \Sigma^{-1}(\mu_+ - \mu_0)$
-where $\mu_+$ is the features from a class (LDA) or a signal to whiten
-(whitening), $\mu_0$ is the negative class center (LDA) or the signal mean
-(whitening) and $\Sigma$ is the covariance matrix of classes (LDA) or
-the correlation within signal (whitening).
+means but have the same covariance.
 
-We propose Non-Zero Whitened Histograms of Orientations (NZ-WHO), that are both more discriminative than WHO, and can be generated several orders of magnitude faster (in 70ms compared to several seconds for WHO).
-This speed up means we can generate templates on the fly, allowing our approach to evaluate arbitrary viewpoint hypotheses.
+% The whitening and LDA have the same
+% formulation when we make a decision boundary $w = \Sigma^{-1}(\mu_+ - \mu_0)$
+% where $\mu_+$ is the features from a class (LDA) or a signal to whiten
+% (whitening), $\mu_0$ is the negative class center (LDA) or the signal mean
+% (whitening) and $\Sigma$ is the covariance matrix of classes (LDA) or
+% the correlation within signal (whitening).
 
-Table \ref{tab:who_initializations} provides a detailed comparison of WHO and NZ-WHO templates, illustrating that our method is faster and more discriminative than Whitened Histograms of Orientations.
-\scream{Does the table show this?}
+We propose Non-Zero Whitened Histograms of Orientations (NZ-WHO), that are both
+more discriminative than WHO, and can be generated several orders of magnitude
+faster (in 70ms compared to several seconds for WHO). This speed up means we
+can generate templates on the fly, allowing our approach to evaluate arbitrary
+viewpoint hypotheses.
 
-\subsubsection{Generating $\Sigma$ and $\mu$}
-\scream{this section seems important to understand the following section but it's also just a re-writing of the Hariharan method}
 In \cite{Hariharan12}, the authors compute the mean and covariance matrix by assuming Wide-Sense Stationarity (WSS) of HOG features
@@
 We use the GPU to parallelize the lookup of the correct autocovariance cells
-during covariance matrix syntheses, which is \scream{x} times faster than using
-the CPU (Figure \ref{fig:covariancetime}).
+during covariance matrix syntheses. The real time analysis for various number of cells is on Figure \ref{fig:covariancetime}).
 
@@
 
-Our method begins by convolving the
-
 Since creating a template and validating the template become computationally

### 2014-11-14 experiments.tex
progressing on exp

@@
 in Fig.~\ref{fig:pascal12cnn}, and the effect of fine-tuning is
-visualized in Fig.~\ref{}.
+visualized in Fig.~\ref{fig:tuning}.
 
@@
 $1.1$ for bicycle-16v when using the R-CNN as the base detector.
-
+%
+In Fig.~\ref{fig:tuning}, we visualize the effect of fine-tuning
+qualitatively for two different test images. In both cases, the
+fine-tuned visually comes closer to the true 3D pose.
 % We got significant improvement on viewpoint estimation by using our
@@
 
-\subsection{Stability of Our Method for Irregular Bounding Boxes}
+\paragraph{Robustness.}
+% Generic object detectors give overlapping detection bounding boxes of the same object which can be handled by non maximal suppression. For these overlapping detections, 
+While the R-CNN detector~\cite{Girshick14} is highly robust to
+variations in object appearance and even occlusion and truncation,
+the resulting bounding box detections vary largely in the object
+portions that they contain  -- notably, they might
 
-% Generic object detectors give overlapping detection bounding boxes of the same object which can be handled by non maximal suppression. For these overlapping detections,
+In Fig.~\ref{}, we visualize the effect
 
-R-CNN detection bounding boxes are irregular in shape since they come from other region proposal methods and sometimes they truncate objects.
-To handle such irregular shape and truncation, we added small context around the bounding boxes and run our method.
+accomodate
+
+ are irregular in
+shape since they come from other region proposal methods and sometimes
+they truncate objects. To handle such irregular shape and truncation,
+we added small context around the bounding boxes and run our method.
 

### 2014-11-14 egpaper_final.tex
done pass over exp

--- 2014-11-14 egpaper_final.tex
@@
 \input{intro}
-
-\section{Related Works}
-
-% Using HOG
-% In this paper, we also used Histograms of Orientations feature \cite{Dalal05} but in general, we could use any dense features.
-
-\subsection{Object Detection and Viewpoint Estimation}
-
-Modern object detectors generalize very well, handling intraclass variability,
-occlusion, truncation and viewpoint changes \cite{Felzenszwalb10, Girshick14}.
-However, this generalization comes at the cost of fine-grained information,
-including accurate 3D pose and object sub-category recognition. Such methods
-typically produce bounding box detection hypotheses, with little further
-information.
-
-Many methods have attempted to move object detection towards richer outputs,
-especially by jointly performing detection and pose estimation \cite{Pepik12,
-Xiang12, Fidler12, Xiang14, Hejrati14, Aubry14, Lim14}. To achieve this,
-\cite{Xiang12, Hejrati14, Fidler12} use 3D representations that deform as
-viewpoint changes and \cite{Pepik12} uses geometric constraints to regularize 2D
-appearance models.
-
-The methods above perform discrete pose estimation, quantizing the viewing
-sphere into a number of poses and selecting the best one during inference.
-Fine-grained pose estimators, in contrast, can infer continuous (or arbitrarily
-fine-grained) poses. One such method from \cite{Zia13} aligns a 3D deformable
-part-based wireframe model with input images to accurately predict object poses.
-
-More recently, \cite{Aubry14, Lim14} made progress in joint instance-level
-object detection and pose estimation. To estimate pose they use synthetic
-renderings of CAD models to learn discriminative mid-level patches.
-\cite{Aubry14} calibrates these patches on a small set of real images, while
-\cite{Lim14} present a method for learning the relative discriminativeness of
-the patches.
-
-\textcolor{red}{Again, should we highlight the differences between these methods and ours?}
-
-% specialized in giving such accurate information, can be applied on any generic
-% object detectors to give high quality metadata.  Many Since the WHO does not
-% require extensive training such as \cite{Felzenszwalb10, Malisiewicz11,
-% Girshick14}, WHO is gaining momentum in 2D-3D matching. \cite{Aubry13,
-% Aubry14, Lim14} combined WHO with synthetic rendering to jointly detect and
-% estimate pose by making mid-level patches using WHO. Using this WSuch approach
-% has an advantage over generic detections. First, it is easy to trace the
-% detection to specific template. The template also has The rendering has
-% corresponding CAD model and viewpoint thus enabling joint detection and
-% viewpoint estimation.  To deal with textureless background \cite{Aubry13}
-% whitens HOG feature and then zero out the WHO feature where there is no
-% texture. But centering a HOG feature where there is no edge creates strong
-% negative edges. We found out that centering only non-zero cells help detection
-% but whitening all cell makes features to leak out to texture-less regions.
-% With increasing popularity of rendering image, whitening, traditional signal
-% processing technique, as a preprocessing stage has been widely used also in
-% computer vision community.  Many object detectors \cite{Felzenszwalb10,
-% Malisiewicz11} \subsection{Mid-level Patches for 2D-3D matching} FPM
-% introduction : per instance matching  Seeing 3D chair : mid-level patches
-
-%\begin{comment}
-%  \subsection{Contributions}
- % \begin{enumerate} \itemsep1pt \parskip0pt \parsep0pt
-  %  \item Introduces Non-Zero Whitened Histograms of Orientations (NZ-WHO) for real-time template generation
-   % \item Continuous viewpoint and focal length tuning using on-the-fly template generation
-%    \item Jointly optimizes translation, 3D viewpoint, CAD models and focal length
-%     \begin{comment}
-%       \item HOG Whitening procedure that do not require calibration stage
-%     \end{comment}
-%  \end{enumerate}
-% \end{comment}
-% All the code and CAD models is publicly available online \cite{Choy14} (currently not disclosed for anonymous review, visualizations are available in the supplementary material).
+%
+\section{Related Work}
+\label{sec:related}
+\input{related}
 
@@
 
-\begin{figure}[t]
- \begin{center}
-    \setlength\tabcolsep{0pt}
-    \begin{tabular}{ccc}
-    % \includegraphics[width=0.9\linewidth]{tuning} 
-   \includegraphics[width=0.33\linewidth]{tuning/1.png} &
-   \includegraphics[width=0.33\linewidth]{tuning/2.png} &
-   \includegraphics[width=0.33\linewidth]{tuning/3.png} \\[-5pt]
-   (a) & (b) & (c)\\
-   \includegraphics[width=0.33\linewidth]{tuning/4.png} &
-   \includegraphics[width=0.33\linewidth]{tuning/5.png} &
-   \includegraphics[width=0.33\linewidth]{tuning/6.png} \\[-5pt]
-   (d) & (e) & (f)\\
-   \end{tabular}
- \end{center}
- \caption{Effect of fine tuning. (left) original image, (middle) initial detection, (right) continuous fine tuning}
- \label{fig:tuning}
-\end{figure}
-
 \section{Experiments}

### 2014-11-14 egpaper_final.tex
chris:cleaning up technical part

--- 2014-11-14 egpaper_final.tex
@@
 
-\section{Our Approach \scream{better name?}}
+\section{Approach Overview}
 \label{sec:nz-who}
+\input{overview}
 
-\subsection{Overview}
-Our method attempts to match CAD models to 2D images, determining the best
-model within a class, its pose and scale, and the focal length of the camera
-used to produce the image. These parameters are first coarsely estimated using
-an ensemble of templates generated offline, before they are refined using
-MCMC by generating new detectors on the fly.
+\subsection{Rendering}
 
-% The basic detection method underlying our approach is WHO template matching.
-% However, we propose a new WHO variant called Non-Zero Whitened Histograms of
-% Orientations (NZ-WHO), where the variant of WHO templates are made from 
-% synthetic rendering to with
-
-Our method In addition to the library of CAD models that will be matched to the query
-images, our method requires a feature statistics which can be collected once and for all.
-
-% images, our method requires a collection of random natural images. Offline, we
-% compute HOG features of these images and record their mean and spatial
-% autocovariance. The images are not used during testing, only the statistics
-% generated from them.
-
-Notably, we do not require any labelled training images of the objects to be
-detected. Our templates are generated exclusively by rendering CAD models from
-our library. From these renderings we produce novel HOG-like features we call
-Non-Zero Whitened Histograms of Orientations (NZ-WHO), which use the natural
-image statistics found offline to whiten a standard HOG template, making it
-more discriminative.
-
-The matching proceeds in two steps: First, we apply a bank of pre-trained
-detectors to the image, corresponding to a set of discrete viewpoints, scales,
-and object models. This provides a rough estimate of these parameters. Second,
-we refine these parameters using MCMC, where each candidate is evaluated by
-rendering a new whitened template on the fly.
-
-Our ensemble of NZ-WHO templates can work as a detector but our algorithm 
-can be initialized using proposal bounding boxes from
-state-of-the-art object detectors \cite{Felzenszwalb10,Girshick14} before
-executing the two steps above. In this scenario, our approach provides a means
-to augment standard bounding box detectors with more interesting 3D
-information.
-\begin{comment}
-Our method is in line with \cite{Aubry14, Lim14} in the sense that we
-use only renderings, not real images. However, rather than using fixed
-sized mid-level patches, we use whole objects and make root
-templates. By using root templates, there is no need to learn a
-discriminative patch dictionary or to calibrate the patches and an
-additional inference stage is not required. However, whitening the
-whole template is prohibitive for several reasons. All templates have
-different aspect ratios making it difficult to generate the covariance
-matrix $\Sigma$. Since the root templates are larger than mid-level
-patches, a very large auto-covariance $\Gamma$ is required. Lastly,
-time complexity of decorrelating a template with $n$ cells increases
-as $O(n^3)$, resulting in slow template generation and large residuals
-due to numerical errors accumulated while decomposing the covariance
-matrix $\Sigma$.
-
-To overcome these difficulties, we propose the Non-Zero Whitened
-Histograms of Orientations (NZ-WHO) with iterative Conjugate Gradient to
-generate templates in real time and enrich rectangular boxes with high
-quality 2D-3D matching. The 2D-3D matching provides a CAD model,
-sub-category, rendering, depth, viewpoint and focal length.
-
-Our method can work as a standalone 2D-3D matching algorithm, or even
-as a standalone ensemble of exemplar-based object detectors (Figure
-\ref{fig:front}) but its real power comes from combining generic
-object detectors and complement rectangular bounding boxes. Our method
-is simple in design; is several orders of magnitude faster than
-traditional method; requires only CAD models; does not need neither images nor
-calibration, yet is powerful in giving high-quality metadata. These
-properties make our method ideal for complementing object detections.
-
-To complement detection bounding boxes, we first search possible 2D-3D
-matching by running cached discrete viewpoint templates. Then, for the
-most probable match, we refine the initial matching using Metropolis
-Hastings. Since it requires iterations of proposal and validation, we
-present real time analysis of NZ-WHO template generation to show that
-this can be done on-the-fly. The fine tuning stage process jointly
-optimizes translation, yaw, roll, pitch, scale, and focal length
-continuously and also searches for different CAD models.
-
-\end{comment}
-\subsection{Rendering Pipeline}
+We used a public rendering engine to create realistic rendering and
+depth\begin{comment}\cite{Choy14render}\end{comment}. The CAD models we used
+in our experiments contain color, texture and material information such as
+transparency and reflectance. We tried to make the rendering as much realistic
+as possible to simulate the natural image statistics. The example rendering is
+in Fig. \ref{fig:rendering}. We also extracted depth information as well while
+rendering to use in the reconstruction.
 
@@
 
-\subsection{Non-Zero Whitened Histograms of Orientations (NZ-WHO)}
+\begin{figure}[t]
+  \begin{center}
+     \includegraphics[width=0.4\linewidth]{rendering}
+     \includegraphics[width=0.4\linewidth]{depth}
+  \end{center}
+  \caption{Example rendering and depth made by our renderer}
+  \label{fig:rendering}
+\end{figure}
+
+\subsection{Whitened Histograms of Orientations (WHO)}
 
@@
 \end{equation}
-, we
-remove 2nd order correlation between all features. So, all elements in the
-random variable $\tilde{X} = \left[\tilde{X}_1, \tilde{X}_2, \dots,
-\tilde{X}_k\right]$, become more independent. In the context of HOG features, a
-whitened HOG template will produce Gaussian noise when convolved with a random
-natural image, but a delta-like response on an image matching the template. WHO
-templates are more discriminative than standard HOG templates because they only
-capture the gradients that differentiate the object from random images.
-
-Hariharan \etal. explained the
-whitening as Linear Discriminant Analysis (LDA) where all classes have different
-means but have the same covariance.
+, we remove 2nd order correlation between all features. Since covarinace
+collection is expensive, \cite{Hariharan12} proposed easy way to generate
+covariance $\Sigma$ from autocovariance $\Gamma$
 
@@
 
-We propose Non-Zero Whitened Histograms of Orientations (NZ-WHO), that are both
-more discriminative than WHO, and can be generated several orders of magnitude
-faster (in 70ms compared to several seconds for WHO). This speed up means we
-can generate templates on the fly, allowing our approach to evaluate arbitrary
-viewpoint hypotheses.
+% In \cite{Hariharan12}, the authors compute the mean and covariance matrix by assuming Wide-Sense Stationarity (WSS) of HOG features
+% generated from natural images. That is, they assume the mean of a HOG cell is
+% independent of its place in the image, and the autocovariance of cells depends
+% only on their relative location.
 
-In \cite{Hariharan12}, the authors compute the mean and covariance matrix by assuming Wide-Sense Stationarity (WSS) of HOG features
-generated from natural images. That is, they assume the mean of a HOG cell is
-independent of its place in the image, and the autocovariance of cells depends
-only on their relative location.
+% In one dimension, let $x(u)$ be the feature at location $u$. Then WSS states
+% that $\mathbb{E}\left[x(u)\right] = \mu$ for all $u$, and
+% \begin{equation}
+% \textrm{cov}_x(u,v) = \textrm{cov}_x(0, v-u) = \Gamma(v-u),
+% \end{equation} where $\Gamma$ is the autocovariance. For simplicity, we describe the 1D case but this can be easily extended to 2D spatial autocovariance.
+% 
+% Therefore, assuming WSS allows the covariance matrix of templates \emph{of any
+% size} to be synthesized from the autocovariance matrix using a simple lookup.
 
-In one dimension, let $x(u)$ be the feature at location $u$. Then WSS states
-that $\mathbb{E}\left[x(u)\right] = \mu$ for all $u$, and
-\begin{equation}
-\textrm{cov}_x(u,v) = \textrm{cov}_x(0, v-u) = \Gamma(v-u),
-\end{equation} where $\Gamma$ is the autocovariance. For simplicity, we describe the 1D case but this can be easily extended to 2D spatial autocovariance.
+% However, the 
+% We propose Non-Zero Whitened Histograms of Orientations (NZ-WHO), that are both
+% more discriminative than WHO, and can be generated several orders of magnitude
+% faster (in 70ms compared to several seconds for WHO). This speed up means we
+% can generate templates on the fly, allowing our approach to evaluate arbitrary
+% viewpoint hypotheses.
 
-Therefore, assuming WSS allows the covariance matrix of templates \emph{of any
-size} to be synthesized from the autocovariance matrix using a simple lookup.
+% Our method requires generating a covariance matrix of non-zero cells
 
-Our method requires generating a covariance matrix of non-zero cells
+\subsubsection{Whitening Synthesized Templates and Non-Zero WHO}
+Our first innovation is `Non-Zero' whitening. When synthesizing detection
+templates from rendered images, a common problem is how to handle the
+background. If the model is rendered over a natural image background, gradients
+in the background will be incorporated into the discriminative template,
+potentially causing false-positives if background elements exist in the query
+image.
 
-\subsubsection{Whitening Synthesized Templates}
-Our first innovation is `Non-Zero' whitening.
-When synthesizing detection templates from rendered images, a common problem is how to handle the background.
-If the model is rendered over a natural image background, gradients in the background will be incorporated into the discriminative template, potentially causing false-positives if background elements exist in the query image.
+Alternatively, if the background is left textureless (see
+Fig.~\ref{fig:rendering}), whitening the resulting HOG template
+will produce undesirable background artifacts. These are created when centering
+the template (by subtracting the mean $\mu$), where strong negative weights are
+introduced in the textureless region (as seen in Fig.~\ref{fig:whocomparison}).
+This could result in positive matches being suppressed due to spurious
+background gradients.
 
-Alternatively, if the background is left textureless \scream{did Hariharan do this?} (see Fig.~\ref{fig:rendering}), whitening the resulting HOG template will produce undesirable background artifacts.
-These are created when centering the template (by subtracting the mean $\mu$), where strong negative weights are introduced in the textureless region (as seen in Fig.~\ref{fig:whocomparison}).
-This could result in positive matches being suppressed due to spurious background gradients.
+NZ-WHO removes these artifacts so that the background has no effect on the
+template response. Given HOG features $x$, we create a new vector $x'$ which
+contains only the non-zero elements of $x$. We select the same elements of
+$\mu$ to produce $\mu'$, while the autocovariance lookup is only performed for
+the cells with non-zero gradient, producing $\Sigma'$ corresponding to the
+features in $x'$. After solving the resulting system (which is now smaller than
+in the WHO approach) we find
 
-\scream{might need to match notation with subsequent sections}
-NZ-WHO removes these artifacts so that the background has no effect on the template response.
-Given HOG features $x$, we create a new vector $x'$ which contains only the non-zero elements of $x$.
-We select the same elements of $\mu$ to produce $\mu'$, while the autocovariance lookup is only performed for the cells with non-zero gradient, producing $\Sigma'$ corresponding to the features in $x'$.
-After solving the resulting system (which is now smaller than in the WHO approach) we find
 \begin{equation}
 w'=\Sigma'^{-1}(x' - \mu') \label{eq:nz-who},
-\end{equation}which we reassemble into the final NZ-WHO template $w$ by replacing the non-zero elements of $x$ with the corresponding $w'$ element.
+\end{equation}which we reassemble into the final NZ-WHO template $w$ by
+replacing the non-zero elements of $x$ with the corresponding $w'$ element.
 
-Notice that $\Sigma$ is not square-rooted in Eq.~\ref{eq:nz-who}, whereas it is in the definition of whitening (Eq.~\ref{eq:whitening}).
-This is because the whitened template will only be used in the context of detection, which involves the inner product with the whitened HOG features of the query image $y$:
-\begin{equation}
-(y-\mu)^{T}\Sigma^{-\frac{1}{2}}\Sigma^{-\frac{1}{2}}(x-\mu)\\
-= (y-\mu)^{T} w.
-\end{equation}
-We can therefore capture the whitening of the query image features in $w$.
+% Notice that $\Sigma$ is not square-rooted in Eq.~\ref{eq:nz-who}, whereas it is
+% in the definition of whitening (Eq.~\ref{eq:whitening}). This is because the
+% whitened template will only be used in the context of detection, which involves
+% the inner product with the whitened HOG features of the query image $y$:
+% \begin{equation}
+% (y-\mu)^{T}\Sigma^{-\frac{1}{2}}\Sigma^{-\frac{1}{2}}(x-\mu)\\
+% = (y-\mu)^{T} w.
+% \end{equation}
+% We can therefore capture the whitening of the query image features in $w$.
 
@@
 This speedup allows us to generate NZ-WHO templates on the fly, allowing us to quickly evaluate arbitrary viewpoint hypotheses.}
-
-\subsubsection{Fast Whitening using Conjugate Gradient}
-
-The computational efficiency of our approach comes from using the iterative conjugate gradient method to whiten the HOG template.
-Whitening the non-zero feature vector $x'$ requires a system of linear equations $\Sigma' w' = (x' - \mu')$ to be solved.
-In
-\cite{Hariharan12}, the authors make use of the fact that covariance matrices
-are symmetric and positive semidefinite to solve the system via the Cholesky
-decomposition, which requires $O(n^3)$ time.
-
-The conjugate gradient method is an iterative algorithm for solving symmetric positive definite systems which runs in $O(n^2\kappa)$ time, where $\kappa$ is the condition number of the matrix.
-This makes conjugate gradient faster than decomposition for matrices with small condition
-numbers relative to their size.
-
-The covariance matrix for HOG templates is typically ill-conditioned, but we can add a regularization constant to the diagonal to reduce its condition number to the point where the conjugate gradient method will converge quickly.
-We use a constant of $0.15$, which reduces the condition number from $10^{20}$ to $50$, much smaller than the dimension of the matrix (7000).
-
-As a result, a GPU implementation of conjugate gradient converges in \scream{x
-ms}, two orders of magnitude faster than the system can be solved using the
-Cholesky factorization (\scream{5 s}).
-
-\subsubsection{Fast Convolution using the FFT}
-
-% We compare the performance of WHO and NZ-WHO on 3D Object dataset \cite{Savarese07} and report performance on Table \ref{tab:who_initializations}.
-
-% To deal with the problems, we propose Non-Zero Whitened Histograms of Orientations.
-
-% To accommodate the growing usage of rendering image for 2D-3D matching using
-% WHO\cite{Aubry13, Aubry14, Lim14}, we analyzed various methods to whiten
-% synthetic rendering image and propose Non-Zero Whitened Histograms of
-% Orientations (NZ-WHO) which is a direct extension of \cite{Hariharan12}
-% designed for rendering images with textureless background. % Since a NZ-WHO
-% template has zero-mean and all elements in the template follow same
-% distribution, no explicit calibration is required if all the templates have
-% approximately the same number of cells.
-
-% Since Combining NZ-WHO with Conjugate Gradient,
-
-% \subsection{Non-Zero Whitened Histograms of Orientations (NZ-WHO)}
-% why non zero whitening and why it makes more sense than seeing 3D, IKEA
-% Overview of the subsections
-%   Generating covariance quickly
-%   Fast inversion
-%   Regularization
+\scream{add comments about the fig:whocomparison}
 
@@
 
+\subsubsection{Fast Whitening using Conjugate Gradient}
+
+The computational efficiency of our approach comes from using the iterative
+conjugate gradient method to whiten the HOG template. Whitening the non-zero
+feature vector $x'$ requires a system of linear equations $\Sigma' w' = (x' -
+\mu')$ to be solved. In
+\cite{Hariharan12}, the authors make use of the fact that covariance matrices
+are symmetric and positive semidefinite to solve the system via the Cholesky
+decomposition, which requires $O(n^3)$ time.
+
+The conjugate gradient method is an iterative algorithm for solving symmetric
+positive definite systems which runs in $O(n^2\kappa)$ time, where $\kappa$ is
+the condition number of the matrix.
+This makes conjugate gradient faster than decomposition for matrices with small condition
+numbers relative to their size.
+
+The covariance matrix for HOG templates is typically ill-conditioned\cite{Hariharan12}, but we
+can add a regularization constant to the diagonal to reduce its condition
+number to the point where the conjugate gradient method will converge quickly.
+We use a constant of $0.15$, which reduces the condition number from $10^{20}$
+to $50$, much smaller than the dimension of the matrix (7000).
+
+As a result, a GPU implementation of conjugate gradient converges in 50
+ms when using 250 HOG cells, two orders of magnitude faster than the system can be solved using the
+Cholesky factorization.
+
+\begin{figure}[t]
+  \begin{center}
+  \begin{tabular}{cc}
+     \includegraphics[width=0.5\linewidth]{whotime} & 
+     \includegraphics[width=0.5\linewidth]{speedup}\\
+     (a) & (b) \\
+ \end{tabular}
+  \end{center}
+  \caption{(a) Comparison of WHO variants generation time and HOG extraction time (b) final speed of using NZ-WHO compare to WHO}
+  \label{fig:whotime}
+\end{figure}
+
+We compare the speed of each of template generation methods in
+Fig.~\cite{fig:covariancetime_crop} Using naive Cholesky decomposition,
+WHO template takes several seconds. But, if we use iterative Conjugate Gradient method, it only
+takes 100ms. If we use NZ-WHO, we can gain extra speed up since we only whitens non-zero cells.
+
+\subsubsection{Fast Convolution using the FFT}
+
+% We compare the performance of WHO and NZ-WHO on 3D Object dataset \cite{Savarese07} and report performance on Table \ref{tab:who_initializations}.
+
+% To deal with the problems, we propose Non-Zero Whitened Histograms of Orientations.
+
+% To accommodate the growing usage of rendering image for 2D-3D matching using
+% WHO\cite{Aubry13, Aubry14, Lim14}, we analyzed various methods to whiten
+% synthetic rendering image and propose Non-Zero Whitened Histograms of
+% Orientations (NZ-WHO) which is a direct extension of \cite{Hariharan12}
+% designed for rendering images with textureless background. % Since a NZ-WHO
+% template has zero-mean and all elements in the template follow same
+% distribution, no explicit calibration is required if all the templates have
+% approximately the same number of cells.
+
+% Since Combining NZ-WHO with Conjugate Gradient,
+
+% \subsection{Non-Zero Whitened Histograms of Orientations (NZ-WHO)}
+% why non zero whitening and why it makes more sense than seeing 3D, IKEA
+% Overview of the subsections
+%   Generating covariance quickly
+%   Fast inversion
+%   Regularization
 % Overview of the subsections
@@
 
-\begin{figure}[t]
-  \begin{center}
-     \includegraphics[width=0.9\linewidth]{covariancetime} 
-  \end{center}
-  \caption{Time to generate $\Sigma$ for various number of cells (left) and same plot on log scale(right). The time complexity increases as $O(n^2)$ for $n$ number of cells.}
-  \label{fig:covariancetime_crop}
-\end{figure}
+% \begin{figure}[t]
+%   \begin{center}
+%      \includegraphics[width=0.9\linewidth]{covariancetime} 
+%   \end{center}
+%   \caption{Time to generate $\Sigma$ for various number of cells (left) and same plot on log scale(right). The time complexity increases as $O(n^2)$ for $n$ number of cells.}
+%   \label{fig:covariancetime_crop}
+% \end{figure}
 
@@
 
-\begin{figure}[t]
-  \begin{center}
-  \begin{tabular}{cc}
-     \includegraphics[width=0.5\linewidth]{whotime} & 
-     \includegraphics[width=0.5\linewidth]{speedup}\\
-     (a) & (b) \\
- \end{tabular}
-  \end{center}
-  \caption{Comparison of HOG variants generation time and final }
-  \label{fig:whotime}
-\end{figure}
 [Figure spectral analysis]

### 2014-11-14 experiments.tex

@@
 roll), CAD instance (model index, rendering, depth) and focal length.
+%
+\begin{figure}[t]
+ \begin{center}
+    \setlength\tabcolsep{0pt}
+    \begin{tabular}{ccc}
+    % \includegraphics[width=0.9\linewidth]{tuning} 
+   \includegraphics[width=0.33\linewidth]{tuning/1.png} &
+   \includegraphics[width=0.33\linewidth]{tuning/2.png} &
+   \includegraphics[width=0.33\linewidth]{tuning/3.png} \\[-5pt]
+   (a) & (b) & (c)\\
+   \includegraphics[width=0.33\linewidth]{tuning/4.png} &
+   \includegraphics[width=0.33\linewidth]{tuning/5.png} &
+   \includegraphics[width=0.33\linewidth]{tuning/6.png} \\[-5pt]
+   (d) & (e) & (f)\\
+   \end{tabular}
+ \end{center}
+ \caption{Effect of fine tuning. (left) original image, (middle) initial detection, (right) continuous fine tuning}
+ \label{fig:tuning}
+\end{figure}
 
@@
 the resulting bounding box detections vary largely in the object
-portions that they contain  -- notably, they might
+portions that they contain, which provides a major challenge to any
+method that uses these detections as an input for further processing,
+such as ours.
+%
+In order to accomodate this variability, we add a considerable context
+region around the proposed bounding boxes before running our method.
+We assume that the object can be arbitrarily truncated by the bounding
+box and search all plausible scales and translations. This can be
+efficiently computed using FFT-based convolution
+(Section. \ref{sec:fft}).
 
-In Fig.~\ref{}, we visualize the effect
-
-accomodate
-
- are irregular in
-shape since they come from other region proposal methods and sometimes
-they truncate objects. To handle such irregular shape and truncation,
-we added small context around the bounding boxes and run our method.
-
-We assumed that object can be arbitrarily truncated by the bounding box and search all plausible scales and translations.
-This can be efficiently computed using FFT-based convolution (refer Section.
-\ref{sec:fft}).
-We put examples of such conditions in Figure \ref{fig:stability}.
-Although the input bounding boxes are irregular and truncate objects, our method reliably generated a reasonable prediction of pose, translation, scale and CAD model.
+Fig.~\ref{fig:stability} visualizes example outputs of our method when
+starting from different proposed R-CNN bounding boxes. As can be seen
+from the figure, although the input bounding boxes (cyan) are often
+irregular and contain truncated objects, our method reliably
+generates a reasonable prediction of pose, translation, scale and CAD
+model (magenta bounding boxes enclose the output of our system).
 

### 2014-11-14 related.tex

\subsection{Object Detection and Viewpoint Estimation}
%
Modern object detectors generalize very well, handling intraclass variability,
occlusion, truncation and viewpoint changes \cite{Felzenszwalb10, Girshick14}.
However, this generalization comes at the cost of fine-grained information,
including accurate 3D pose and object sub-category recognition. Such methods
typically produce bounding box detection hypotheses, with little further
information.

Many methods have attempted to move object detection towards richer outputs,
especially by jointly performing detection and pose estimation \cite{Pepik12,
Xiang12, Fidler12, Xiang14, Hejrati14, Aubry14, Lim14}. To achieve this,
\cite{Xiang12, Hejrati14, Fidler12} use 3D representations that deform as
viewpoint changes and \cite{Pepik12} uses geometric constraints to regularize 2D
appearance models.

The methods above perform discrete pose estimation, quantizing the viewing
sphere into a number of poses and selecting the best one during inference.
Fine-grained pose estimators, in contrast, can infer continuous (or arbitrarily
fine-grained) poses. One such method from \cite{Zia13} aligns a 3D deformable
part-based wireframe model with input images to accurately predict object poses.

More recently, \cite{Aubry14, Lim14} made progress in joint instance-level
object detection and pose estimation. To estimate pose they use synthetic
renderings of CAD models to learn discriminative mid-level patches.
\cite{Aubry14} calibrates these patches on a small set of real images, while
\cite{Lim14} present a method for learning the relative discriminativeness of
the patches.

\textcolor{red}{Again, should we highlight the differences between these methods and ours?}

% specialized in giving such accurate information, can be applied on any generic
% object detectors to give high quality metadata.  Many Since the WHO does not
% require extensive training such as \cite{Felzenszwalb10, Malisiewicz11,
% Girshick14}, WHO is gaining momentum in 2D-3D matching. \cite{Aubry13,
% Aubry14, Lim14} combined WHO with synthetic rendering to jointly detect and
% estimate pose by making mid-level patches using WHO. Using this WSuch approach
% has an advantage over generic detections. First, it is easy to trace the
% detection to specific template. The template also has The rendering has
% corresponding CAD model and viewpoint thus enabling joint detection and
% viewpoint estimation.  To deal with textureless background \cite{Aubry13}
% whitens HOG feature and then zero out the WHO feature where there is no
% texture. But centering a HOG feature where there is no edge creates strong
% negative edges. We found out that centering only non-zero cells help detection
% but whitening all cell makes features to leak out to texture-less regions.
% With increasing popularity of rendering image, whitening, traditional signal
% processing technique, as a preprocessing stage has been widely used also in
% computer vision community.  Many object detectors \cite{Felzenszwalb10,
% Malisiewicz11} \subsection{Mid-level Patches for 2D-3D matching} FPM
% introduction : per instance matching  Seeing 3D chair : mid-level patches

%\begin{comment}
%  \subsection{Contributions}
 % \begin{enumerate} \itemsep1pt \parskip0pt \parsep0pt
  %  \item Introduces Non-Zero Whitened Histograms of Orientations (NZ-WHO) for real-time template generation
   % \item Continuous viewpoint and focal length tuning using on-the-fly template generation
%    \item Jointly optimizes translation, 3D viewpoint, CAD models and focal length
%     \begin{comment}
%       \item HOG Whitening procedure that do not require calibration stage
%     \end{comment}
%  \end{enumerate}
% \end{comment}
% All the code and CAD models is publicly available online \cite{Choy14} (currently not disclosed for anonymous review, visualizations are available in the supplementary material).

### 2014-11-14 egpaper_final.tex
started pass over mcmc

@@
 \subsection{Whitened Histograms of Orientations (WHO)}
-
+\label{sec:who}
 Recently, Hariharan \etal. introduced Whitened Histograms of Orientations (WHO)
@@
 \subsubsection{Whitening Synthesized Templates and Non-Zero WHO}
+\label{sec:nzwho}
 Our first innovation is `Non-Zero' whitening. When synthesizing detection
@@
 
-\section{Estimating Parameters using MCMC}
+\section{Pose Fine-Tuning via MCMC}
 \label{sec:fine}
-% Estimating viewpoint continuously to fine tune a initial matching
-The NZ-WHO template matching method we have presented makes template generation
-and evaluation computationally inexpensive. This means we can efficiently
-explore the parameter space to find the best object pose, scale, model type and
-camera focal length.
-
-Since creating a template and validating the template become computationally
-inexpensive, making a proposal and validating the proposal to fine tune a 2D-3D
-matching became affordable. We used Metropolis-Hastings algorithm to generate a
-proposal pose and focal length and validate the proposal using the convolution
-and returning maximum response as a return.
-
-To fine-tune continuous pose and location of object, we require strong
-initialization. The initialization is a rough bounding box with small context
-and viewpoint. Since most of the standard detectors does not provide viewpoint
-of an object, we first run an ensemble of NZ-WHO templates to get rough
-viewpoints. Once we get rough viewpoint, we initialize the proposal $x_0$ and
-start sampling proposals.
-
-We modeled the distribution of object location and pose as an exponential distribution. 
-For proposal distribution, we used Gaussian distribution to propose next viewpoint and for viewpoint proposals
-and uniform distribution for model change proposals.
-
-More formally, suppose that $x = [p, m, f]$ where $p$ is the 3D rotation of the CAD model and
-$m$ is the CAD model index and $f$ is the focal length. We use Metropolis Hastings
-to optimize $x$.
-
-\begin{align}
-    A(x \rightarrow x') & =  min\left( 1,  \frac{P(x' g(x') \rightarrow x)}{P(x) g(x \rightarrow x')}\right) \\
-    g(x \rightarrow x + p_i') & \sim \mathcal{N}(\mu = 0,\sigma = c_1) \quad i \in \{1,2,3\}\\
-    g(x \rightarrow x + f') & \sim \mathcal{N}(\mu = 0,\sigma = c_2)\\
-    g(x \rightarrow x + m') & \sim c_3 \delta(m) + (1-c_3) Unif(1,M)
-\end{align}
-
-Where $g$ is the proposal distribution and $P$ is the distribution of which we
-defined using Gaussian distribution around previous state. $A$ is the
-acceptance probability where we accept new proposal with $A(x \rightarrow x')$.
-
-\begin{align}
-    P(x) & \sim e^{ c_4 \max_{s} w(x) \ast \mathcal{T}_s(\mathcal{I}) }
-\end{align}
-
-$P$ is the distribution of the pose and location of an object on image
-$\mathcal{I}$. One can also think of the image as an image cropped by detection
-bounding box. We synthesize covariance matrix and create NZ-WHO template $w(x)$ for particular viewpoint, focal length and CAD model.
-
-We initialize the $x$ using the result from the previous stage where we run our ensemble or NZ-WHO templates to get rough estimate.
-
-In sum, for new proposal $x'$, we make a NZ-WHO template on the fly 
-We found out that it requires good initialization to converge to local minima.
-
-We represented the probability using exponential family.
-
-So our model favors large convolution score $\max_{s} w(x) \ast T(\mathcal{I})$. 
-% there are several advantages that was not possible such as \textbf{on-the-fly} template generation and making large number of templates  
-\begin{figure}[t]
-\centering
-    \includegraphics[width=0.7\linewidth]{tuning2} \\ [-5pt]
-    \caption{Different modes of Metropolis Hasting proposals, see Section \ref{sec:fine}}
- \label{fig:tuningmode}
-\end{figure}
-
+\input{mcmc}
+%
 \section{Experiments}

### 2014-11-14 mcmc.tex
started pass over mcmc

% Estimating viewpoint continuously to fine tune a initial matching
The NZ-WHO template matching method we have presented
(Sect.~\ref{sec:nzwho}) makes template generation and evaluation
computationally inexpensive. This means that we can use a
hypothesize-and-test scheme to efficiently explore the continuous
parameter space to find the best object pose, scale, 3D CAD model type
and camera focal length.
%
In particular, we propose to implement this parameter search as a
Markov Chain Monte Carlo (MCMC) procedure based on the
Metropolis-Hastings algorithm.

\paragraph{Probabilistic formulation.}
We parameterize the continuous parameter space as  $x = [p, m, f]$,
where $p$ is the 3D rotation of the CAD model, $m$ is the discrete CAD
model index, and $f$ is the focal length.

We model the probability that the object in the test image
$\mathcal{I}$ is generated by the parameters $x$ as a distribution in
the exponential family, and let
\begin{align}
    P(x) & \sim e^{ c_4 \max_{s} w(x) \ast \mathcal{T}_s(\mathcal{I})}.
\end{align}

We use Metropolis Hastings to optimize $x$.

We model the distribution of object location and pose as an exponential distribution.

For proposal distribution, we used Gaussian distribution to propose next viewpoint and for viewpoint proposals
and uniform distribution for model change proposals.

\begin{align}
    A(x \rightarrow x') & =  min\left( 1,  \frac{P(x' g(x') \rightarrow x)}{P(x) g(x \rightarrow x')}\right) \\
    g(x \rightarrow x + p_i') & \sim \mathcal{N}(\mu = 0,\sigma = c_1) \quad i \in \{1,2,3\}\\
    g(x \rightarrow x + f') & \sim \mathcal{N}(\mu = 0,\sigma = c_2)\\
    g(x \rightarrow x + m') & \sim c_3 \delta(m) + (1-c_3) Unif(1,M)
\end{align}

Where $g$ is the proposal distribution and $P$ is the distribution of which we
defined using Gaussian distribution around previous state. $A$ is the
acceptance probability where we accept new proposal with $A(x \rightarrow x')$.

$P$ is the distribution of the pose and location of an object on image
$\mathcal{I}$. One can also think of the image as an image cropped by detection
bounding box. We synthesize covariance matrix and create NZ-WHO template $w(x)$ for particular viewpoint, focal length and CAD model.

We initialize the $x$ using the result from the previous stage where we run our ensemble or NZ-WHO templates to get rough estimate.

In sum, for new proposal $x'$, we make a NZ-WHO template on the fly 
We found out that it requires good initialization to converge to local minima.

We represented the probability using exponential family.

So our model favors large convolution score $\max_{s} w(x) \ast T(\mathcal{I})$. 
% there are several advantages that was not possible such as \textbf{on-the-fly} template generation and making large number of templates  
\begin{figure}[t]
\centering
    \includegraphics[width=0.7\linewidth]{tuning2} \\ [-5pt]
    \caption{Different modes of Metropolis Hasting proposals, see Section \ref{sec:fine}}
 \label{fig:tuningmode}
\end{figure}

\paragraph{Initialization.}
To fine-tune continuous pose and location of object, we require strong
initialization. The initialization is a rough bounding box with small context
and viewpoint. Since most of the standard detectors does not provide viewpoint
of an object, we first run an ensemble of NZ-WHO templates to get rough
viewpoints. Once we get rough viewpoint, we initialize the proposal $x_0$ and
start sampling proposals.

### 2014-11-14 mcmc.tex
started pass over mcmc

@@
 \begin{align}
-    P(x) & \sim e^{ c_4 \max_{s} w(x) \ast \mathcal{T}_s(\mathcal{I})}.
+    P(x) & \sim e^{ c_4 \max_{s} w(x) \ast \mathcal{T}_s(\mathcal{I})},
 \end{align}
+where $\max_{s} w(x) \ast T(\mathcal{I})$ is the convolution score of
+template $w(x)$ with image feautures $T(\mathcal{I})$, as defined
+in Sect.~\ref{}.
 
-We use Metropolis Hastings to optimize $x$.
+\paragraph{Inference.}
+We approximate the MAP solution for $x$ by drawing samples from the
+distribution $P(x)$, using the Metropolis-Hastings
+algorithm. Specifically, we use a variant that changes only a single
+component of the parameter vector $x$ at a time, termed Single
+Component Metropolis Hastings.
 
-We model the distribution of object location and pose as an exponential distribution.
+As proposals
 
@@
 $P$ is the distribution of the pose and location of an object on image
-$\mathcal{I}$. One can also think of the image as an image cropped by detection
-bounding box. We synthesize covariance matrix and create NZ-WHO template $w(x)$ for particular viewpoint, focal length and CAD model.
+$\mathcal{I}$.
 
-We initialize the $x$ using the result from the previous stage where we run our ensemble or NZ-WHO templates to get rough estimate.
+One can also think of the image as an image cropped by detection
+bounding box. We synthesize covariance matrix and create NZ-WHO
+template $w(x)$ for particular viewpoint, focal length and CAD model.
 
@@
 
-We represented the probability using exponential family.
-
-So our model favors large convolution score $\max_{s} w(x) \ast T(\mathcal{I})$. 
-% there are several advantages that was not possible such as \textbf{on-the-fly} template generation and making large number of templates  
+% there are several advantages that was not possible such as
+% \textbf{on-the-fly} template generation and making large number of
+% templates
 \begin{figure}[t]
@@
 start sampling proposals.
+
+We initialize the $x$ using the result from the previous stage where
+we run our ensemble or NZ-WHO templates to get rough estimate.

### 2014-11-14 mcmc.tex
pass over mcmc done

@@
 
-As proposals
-
-For proposal distribution, we used Gaussian distribution to propose next viewpoint and for viewpoint proposals
-and uniform distribution for model change proposals.
-
+This algorithm changes the current state $x$ to a new state $x'$ based
+on the acceptance probability
 \begin{align}
-    A(x \rightarrow x') & =  min\left( 1,  \frac{P(x' g(x') \rightarrow x)}{P(x) g(x \rightarrow x')}\right) \\
+    A(x \rightarrow x') & =  min\left( 1,  \frac{P(x' g(x') \rightarrow x)}{P(x) g(x \rightarrow x')}\right).
+\end{align}
+We define $4$ different types of moves that can alter the state
+(Fig.~\ref{fig:moves}), {\em (i)} changing the focal length $f$, {\em
+  (ii)} one of the rotational pose parameters $p_i$, {\em (iii)} scale
+  or translation, and {\em (iv)} CAD model index $m$. For (i) to
+  (iii), we use Gaussian proposal distributions, and a uniform
+  distribution over model changes for (iv).
+\begin{align}
     g(x \rightarrow x + p_i') & \sim \mathcal{N}(\mu = 0,\sigma = c_1) \quad i \in \{1,2,3\}\\
     g(x \rightarrow x + f') & \sim \mathcal{N}(\mu = 0,\sigma = c_2)\\
-    g(x \rightarrow x + m') & \sim c_3 \delta(m) + (1-c_3) Unif(1,M)
+    g(x \rightarrow x + m') & \sim c_3 \delta(m) + (1-c_3) Unif(1,M),
 \end{align}
-
-Where $g$ is the proposal distribution and $P$ is the distribution of which we
-defined using Gaussian distribution around previous state. $A$ is the
-acceptance probability where we accept new proposal with $A(x \rightarrow x')$.
-
-$P$ is the distribution of the pose and location of an object on image
-$\mathcal{I}$.
-
-One can also think of the image as an image cropped by detection
-bounding box. We synthesize covariance matrix and create NZ-WHO
-template $w(x)$ for particular viewpoint, focal length and CAD model.
-
-In sum, for new proposal $x'$, we make a NZ-WHO template on the fly 
-We found out that it requires good initialization to converge to local minima.
+where $g$ is the proposal distribution. % and $P$ is the distribution of which we
+%defined using Gaussian distribution around previous state. $A$ is the
+%acceptance probability where we accept new proposal with $A(x \rightarrow x')$.
+%
+% One can also think of the image as an image cropped by detection
+% bounding box. We synthesize covariance matrix and create NZ-WHO
+% template $w(x)$ for particular viewpoint, focal length and CAD model.
+% In sum, for new proposal $x'$, we make a NZ-WHO template on the fly 
+% We found out that it requires good initialization to converge to
+% local minima.
+In practice, we run this algorithm for \scream{} iterations, keeping
+the sample with the highest probability as our approximate estimate of
+the MAP solution.
+\scream{no idea what c is}
 
@@
     \includegraphics[width=0.7\linewidth]{tuning2} \\ [-5pt]
-    \caption{Different modes of Metropolis Hasting proposals, see Section \ref{sec:fine}}
- \label{fig:tuningmode}
+    \caption{Metropolis Hastings move types (Section~\ref{sec:fine}).}
+ \label{fig:moves}
 \end{figure}
@@
 \paragraph{Initialization.}
-To fine-tune continuous pose and location of object, we require strong
-initialization. The initialization is a rough bounding box with small context
-and viewpoint. Since most of the standard detectors does not provide viewpoint
-of an object, we first run an ensemble of NZ-WHO templates to get rough
-viewpoints. Once we get rough viewpoint, we initialize the proposal $x_0$ and
-start sampling proposals.
-
-We initialize the $x$ using the result from the previous stage where
-we run our ensemble or NZ-WHO templates to get rough estimate.
+Since the Metropolis-Hastings algorithm is susceptible to getting
+stuck in local optima, we need a good initialiation in order to
+increase the probability to find a solution that is close to the
+global optima. We achieve this by first running a discrete,
+pre-trained version of our algorithm (i.e., an ensemble of NZ-WHO
+templates) in order to get promising candidate 2D bounding boxes and
+poses to start from. We then initialize $x_0$ for each of these candidates.

### 2014-11-14 commented_out.tex
cleaning up technical part in progress.

--- 2014-11-14 egpaper_final.tex
@@
-\documentclass[10pt,twocolumn,letterpaper]{article}
+% we pad zero to the 2D image features by the largest kernel size.
+And we transform the kernel to match the padded image feature.
+To compute convolution, we compute element-wise product with the transformed kernel and sum all the features.
+Unlike \cite{Podlozhnyuk}, we do not need to shift the data nor kernel if we use simple mathematical trick.
+%   
+% \begin{align}
+%     x_{pad} & = \mathcal{P}_{n+m}(x)\\
+%     y_{pad} & = \mathcal{P}_{n+m}(y)\\
+%     x_{pad} \ast y_{pad} & = \mathcal{F}^{-1}(\mathcal{F}(x_{pad}) \circ \mathcal{F}(y_{pad}))
+% \end{align}
+% 
+%   Where $\ast$ is the circular convolution and $\circ$ is the Hadamard Product and $\mathcal{F}$ is the Fourier Transformation and $\mathcal{P}_n$ is the padding operation that append zeros to make vector of size $n$.
+% 
+% For each dimension of features, we transform kernel and image feature into frequency domain using Fast Fourier Transformation.
+We transform the image into frequency domain once and use the transformed image for all templates.
+% 
+% We implemented the convolution using FFT on GPU and got 10x speed up.
 
-\usepackage{cvpr}
-\usepackage{times}
-\usepackage{epsfig}
-\usepackage{graphicx}
-\usepackage{amsmath}
-\usepackage{amssymb}
-\usepackage{caption}
-\usepackage{verbatim}
-\usepackage{subcaption}
-\usepackage{algorithm2e}
-\usepackage{rotating}
-\usepackage[space]{grffile}
-\usepackage[font=small,skip=0pt]{caption}
-%\DeclareMathOperator{\Tr}{Tr}
-% Include other packages here, before hyperref.
-
-% If you comment hyperref and then uncomment it, you should delete
-% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
-% run, let it finish, and you should be clear).
-\usepackage[breaklinks=true,bookmarks=false]{hyperref}
-\graphicspath{ {figures/} }
-% \cvprfinalcopy % *** Uncomment this line for the final submission
-
-\def\cvprPaperID{****} % *** Enter the CVPR Paper ID here
-\def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}
-
-% custom commands
-\newcommand{\scream}[1]{{\color{red} \bf *** #1 ***}}
-
-% Pages are numbered in submission mode, and unnumbered in camera-ready
-%\ifcvprfinal\pagestyle{empty}\fi
-\setcounter{page}{1}
-\begin{document}
-
-%%%%%%%%% TITLE
-\title{Enriching Object Detection with 2D-3D Registration and Continuous Viewpoint}
-%\title{Enrich Object Detection : 2D-3D registration and continuous viewpoint estimation}
-
-\author{First Author\\
-Institution1\\
-Institution1 address\\
-{\tt\small firstauthor@i1.org}
-% For a paper whose authors are all at the same institution,
-% omit the following lines up until the closing ``}''.
-% Additional authors and addresses can be added with ``\and'',
-% just like the second author.
-% To save space, use either the email address or home page, not both
-\and
-Second Author\\
-Institution2\\
-First line of institution2 address\\
-{\tt\small secondauthor@i2.org}
-}
-
-\maketitle
-%\thispagestyle{empty}
-
-%%%%%%%%% ABSTRACT
-\begin{abstract}
-A large body of recent work on object detection has focused on exploiting 3D CAD
-model databases to improve detection performance. Many of these approaches work
-by aligning exact 3D models to images using templates generated from renderings
-of the 3D models at a finite set of discrete viewpoints. The training procedures
-for these approaches, however, are very expensive and require gigabytes of
-memory and storage, and the viewpoint discretization hampers pose estimation
-performance.
-
-We propose an efficient method for synthesizing templates from 3D models that
-runs on the fly -- that is, it quickly produces detectors for an arbitrary
-viewpoint of a 3D model without expensive dataset-dependent training or template
-storage. Given a 3D model and an arbitrary continuous detection viewpoint, our
-method synthesizes a discriminative template by extracting features from a
-rendered view of the object and decorrelating spatial dependences among the
-features. Our decorrelation procedure relies on a gradient-based algorithm that
-is more numerically stable than standard decomposition-based procedures, and we
-efficiently search for candidate detections by computing FFT-based template
-convolutions. Due to the speed of our template synthesis procedure, we are able
-to perform joint optimization on continuous scale, translation, rotation, and
-focal length. We provide an efficient GPU implementation of our algorithm, and
-we validate its performance on 3DObject dataset and PASCAL 2012 dataset.
-
-%     Using 3D model to detect and register the model to RGB image has been a
-%     growing field of study. Recently, Aubry \etal \cite{Aubry14} and J. Lim
-%     \etal \cite{Lim14} tried to estimate pose and align exact CAD model to an
-%     image using part-based templates. Malisiewicz \etal \cite{Malisiewicz11}
-%     also addresses the issue by transferring metadata after detection. Hejrati
-%     \etal \cite{Hejrati14} uses template synthesis to detect an object. All
-%     these approaches require extensive training, a lot of memory space. Also,
-%     the training based approach requires defining fixed viewpoints which limit
-%     themselves.  To overcome these difficulties, we propose an efficient and
-%     fast way to synthesize and validate templates using on the fly realistic
-%     rendering that can jointly optimize scale, translation, rotation and focal
-%     length continuously. We render an object and extract features and
-%     decorrelate spatial dependencies within them on the fly to make a
-%     discriminative template. To speed up the decorrelation procedure, we adopt
-%     a gradient based algorithm which is numerically more stable than
-%     decomposition procedure. Finally, we efficiently search for candidate
-%     match by computing convolution using FFT and jointly optimize to match the
-%     object accurately. To speed up further, we propose an efficient GPU
-%     implementation and tested on PASCAL images.
-
-%   In contrast to other mid-level patch based 3D matching methods which
-%   requires extensive training and more than 10Gb of memory space and physical
-%   storage, ours require no training nor saving the templates thus enabling it
-%   to run on any personal computer.  To overcome these difficulties, we propose
-%   an efficient and fast way to synthesize and validate templates using on the
-%   fly realistic rendering that can jointly optimize scale, translation,
-%   rotation and focal length continuously. We render an object and extract
-%   features and decorrelate spatial dependencies within them on the fly to make
-%   a discriminative template. To speed up the decorrelation procedure, we adopt
-%   a gradient based algorithm which is numerically more stable than
-%   decomposition procedure. Finally, we efficiently search for candidate match
-%   by computing convolution using FFT and jointly optimize to match the object
-%   accurately. To speed up further, we propose an efficient GPU implementation
-%   and tested on PASCAL images.
-
-\end{abstract}
-
-%%%%%%%%% BODY TEXT
-\section{Introduction}
-\label{sec:intro}
-\input{intro}
-%
-\section{Related Work}
-\label{sec:related}
-\input{related}
-
-\section{Approach Overview}
-\label{sec:nz-who}
-\input{overview}
-
-\subsection{Rendering}
-
-We used a public rendering engine to create realistic rendering and
-depth\begin{comment}\cite{Choy14render}\end{comment}. The CAD models we used
-in our experiments contain color, texture and material information such as
-transparency and reflectance. We tried to make the rendering as much realistic
-as possible to simulate the natural image statistics. The example rendering is
-in Fig. \ref{fig:rendering}. We also extracted depth information as well while
-rendering to use in the reconstruction.
-
-We used a collection of CAD models to make exemplar renderings of CAD models and for viewpoints. The
-CAD models are cached so that when we fine-tune 2D-3D matching, so it can be rendered instantaneously.
-We made the renderings to change focal length and yaw, pitch, roll so that we can fine tune the matching
-continuously.
-
-\begin{figure}[t]
-  \begin{center}
-     \includegraphics[width=0.4\linewidth]{rendering}
-     \includegraphics[width=0.4\linewidth]{depth}
-  \end{center}
-  \caption{Example rendering and depth made by our renderer}
-  \label{fig:rendering}
-\end{figure}
-
-\subsection{Whitened Histograms of Orientations (WHO)}
-\label{sec:who}
-Recently, Hariharan \etal. introduced Whitened Histograms of Orientations (WHO)
-\cite{Hariharan12}, which uses statistics from natural images to whiten HOG
-templates, making them more discriminative. Whitening is a common signal
-processing operation for decorrelating a set of random variables
-\cite{Martinsson05, Belouchrani00}. More formally, suppose that we have a
-$k$-dimensional random variable $X \in \mathcal{R}^k$ with $Cov(X)=\Sigma$. By
-whitening the signal,
-\begin{equation}
-\tilde{X}=\Sigma^{-\frac{1}{2}}(X - E[X]) \label{eq:whitening}
-\end{equation}
-, we remove 2nd order correlation between all features. Since covarinace
-collection is expensive, \cite{Hariharan12} proposed easy way to generate
-covariance $\Sigma$ from autocovariance $\Gamma$
-
-% The whitening and LDA have the same
-% formulation when we make a decision boundary $w = \Sigma^{-1}(\mu_+ - \mu_0)$
-% where $\mu_+$ is the features from a class (LDA) or a signal to whiten
-% (whitening), $\mu_0$ is the negative class center (LDA) or the signal mean
-% (whitening) and $\Sigma$ is the covariance matrix of classes (LDA) or
-% the correlation within signal (whitening).
-
-% In \cite{Hariharan12}, the authors compute the mean and covariance matrix by assuming Wide-Sense Stationarity (WSS) of HOG features
-% generated from natural images. That is, they assume the mean of a HOG cell is
-% independent of its place in the image, and the autocovariance of cells depends
-% only on their relative location.
-
-% In one dimension, let $x(u)$ be the feature at location $u$. Then WSS states
-% that $\mathbb{E}\left[x(u)\right] = \mu$ for all $u$, and
-% \begin{equation}
-% \textrm{cov}_x(u,v) = \textrm{cov}_x(0, v-u) = \Gamma(v-u),
-% \end{equation} where $\Gamma$ is the autocovariance. For simplicity, we describe the 1D case but this can be easily extended to 2D spatial autocovariance.
-% 
-% Therefore, assuming WSS allows the covariance matrix of templates \emph{of any
-% size} to be synthesized from the autocovariance matrix using a simple lookup.
-
-% However, the 
-% We propose Non-Zero Whitened Histograms of Orientations (NZ-WHO), that are both
-% more discriminative than WHO, and can be generated several orders of magnitude
-% faster (in 70ms compared to several seconds for WHO). This speed up means we
-% can generate templates on the fly, allowing our approach to evaluate arbitrary
-% viewpoint hypotheses.
-
-% Our method requires generating a covariance matrix of non-zero cells
-
-\subsubsection{Whitening Synthesized Templates and Non-Zero WHO}
-\label{sec:nzwho}
-Our first innovation is `Non-Zero' whitening. When synthesizing detection
-templates from rendered images, a common problem is how to handle the
-background. If the model is rendered over a natural image background, gradients
-in the background will be incorporated into the discriminative template,
-potentially causing false-positives if background elements exist in the query
-image.
-
-Alternatively, if the background is left textureless (see
-Fig.~\ref{fig:rendering}), whitening the resulting HOG template
-will produce undesirable background artifacts. These are created when centering
-the template (by subtracting the mean $\mu$), where strong negative weights are
-introduced in the textureless region (as seen in Fig.~\ref{fig:whocomparison}).
-This could result in positive matches being suppressed due to spurious
-background gradients.
-
-NZ-WHO removes these artifacts so that the background has no effect on the
-template response. Given HOG features $x$, we create a new vector $x'$ which
-contains only the non-zero elements of $x$. We select the same elements of
-$\mu$ to produce $\mu'$, while the autocovariance lookup is only performed for
-the cells with non-zero gradient, producing $\Sigma'$ corresponding to the
-features in $x'$. After solving the resulting system (which is now smaller than
-in the WHO approach) we find
-
-\begin{equation}
-w'=\Sigma'^{-1}(x' - \mu') \label{eq:nz-who},
-\end{equation}which we reassemble into the final NZ-WHO template $w$ by
-replacing the non-zero elements of $x$ with the corresponding $w'$ element.
-
-% Notice that $\Sigma$ is not square-rooted in Eq.~\ref{eq:nz-who}, whereas it is
-% in the definition of whitening (Eq.~\ref{eq:whitening}). This is because the
-% whitened template will only be used in the context of detection, which involves
-% the inner product with the whitened HOG features of the query image $y$:
-% \begin{equation}
-% (y-\mu)^{T}\Sigma^{-\frac{1}{2}}\Sigma^{-\frac{1}{2}}(x-\mu)\\
-% = (y-\mu)^{T} w.
-% \end{equation}
-% We can therefore capture the whitening of the query image features in $w$.
-
-% We use the GPU to parallelize the lookup of the correct autocovariance cells during covariance matrix syntheses, which is \scream{x} times faster than using the CPU (Figure \ref{fig:covariancetime}).
-
-%\scream{chris:We propose Non-Zero Whitened Histograms of Orientations (NZ-WHO), an improvement over WHO which is both more discriminative than WHO and can be computed many orders of magnitude faster than WHO (70ms as opposed to to several seconds for WHO).
-This speedup allows us to generate NZ-WHO templates on the fly, allowing us to quickly evaluate arbitrary viewpoint hypotheses.}
-\scream{add comments about the fig:whocomparison}
-
-\begin{figure}[t]
-  \begin{center}
-%   \fbox{\rule{0pt}{2in} \rule{0.9\linewidth}{0pt}}
-    % include whitening all centered cells
-    % \includegraphics[width=0.32\linewidth]{whiten_all_crop}
-    \setlength\tabcolsep{3pt}
-    \begin{tabular}{ccc}
-      HOG & WHO & NZ-WHO \\
-%     \begin{turn}{90}$w_+$\end{turn} &
-    \includegraphics[width=0.28\linewidth]{hog_crop} &
-    \includegraphics[width=0.28\linewidth]{whiten_all_crop} &
-    \includegraphics[width=0.28\linewidth]{whiten_non_zero_crop} \\
-    % include whitening all centered cells
-     % \includegraphics[width=0.282\linewidth]{whiten_all_neg_crop} 
-%     \begin{turn}{90}$-w_-$\end{turn} &
-     \includegraphics[width=0.28\linewidth]{hog_neg_crop} &
-     \includegraphics[width=0.28\linewidth]{whiten_all_neg_crop}  &
-     \includegraphics[width=0.28\linewidth]{whiten_non_zero_neg} \\
-    % include whitening all centered cells
- %    \begin{turn}{90}ihog\cite{vondrick2013}\end{turn} &
-    % \cite{vondrick2013}& 
-     \includegraphics[width=0.28\linewidth]{ihog_hog200_crop.png} &
-     \includegraphics[width=0.28\linewidth]{ihog_whiten_all200_crop.png} &
-     \includegraphics[width=0.28\linewidth]{ihog_whiten_non_zero200_crop.png} \\
- \end{tabular}
-  \end{center}
-  \caption{Comparison of HOG, WHO and NZ-WHO.
-Visualization of positive weights (first row),  visualization of negative weights (second row), HOGgles \cite{vondrick2013} (third row).
-Note that for WHO, whitening all cell result in strong negative edges on the empty region}
-  \label{fig:whocomparison}
-\end{figure}
-
-\subsubsection{Fast Whitening using Conjugate Gradient}
-
-The computational efficiency of our approach comes from using the iterative
-conjugate gradient method to whiten the HOG template. Whitening the non-zero
-feature vector $x'$ requires a system of linear equations $\Sigma' w' = (x' -
-\mu')$ to be solved. In
-\cite{Hariharan12}, the authors make use of the fact that covariance matrices
-are symmetric and positive semidefinite to solve the system via the Cholesky
-decomposition, which requires $O(n^3)$ time.
-
-The conjugate gradient method is an iterative algorithm for solving symmetric
-positive definite systems which runs in $O(n^2\kappa)$ time, where $\kappa$ is
-the condition number of the matrix.
-This makes conjugate gradient faster than decomposition for matrices with small condition
-numbers relative to their size.
-
-The covariance matrix for HOG templates is typically ill-conditioned\cite{Hariharan12}, but we
-can add a regularization constant to the diagonal to reduce its condition
-number to the point where the conjugate gradient method will converge quickly.
-We use a constant of $0.15$, which reduces the condition number from $10^{20}$
-to $50$, much smaller than the dimension of the matrix (7000).
-
-As a result, a GPU implementation of conjugate gradient converges in 50
-ms when using 250 HOG cells, two orders of magnitude faster than the system can be solved using the
-Cholesky factorization.
-
-\begin{figure}[t]
-  \begin{center}
-  \begin{tabular}{cc}
-     \includegraphics[width=0.5\linewidth]{whotime} & 
-     \includegraphics[width=0.5\linewidth]{speedup}\\
-     (a) & (b) \\
- \end{tabular}
-  \end{center}
-  \caption{(a) Comparison of WHO variants generation time and HOG extraction time (b) final speed of using NZ-WHO compare to WHO}
-  \label{fig:whotime}
-\end{figure}
-
-We compare the speed of each of template generation methods in
-Fig.~\cite{fig:covariancetime_crop} Using naive Cholesky decomposition,
-WHO template takes several seconds. But, if we use iterative Conjugate Gradient method, it only
-takes 100ms. If we use NZ-WHO, we can gain extra speed up since we only whitens non-zero cells.
-
-\subsubsection{Fast Convolution using the FFT}
+% \subsubsection{Fast Convolution using the FFT}
 
@@
 
-The final challenge in on-the-fly template evaluation is performing the
-convolution between the template and the target image. Standard convolution
-would be prohibitively slow for the high resolution templates we're using, so we
-implemented the convolution via Fast Fourier Transform on the GPU. This allows
-template evaluation to run in \scream{x ms}, compared to \scream{x ms} for the
-naive CPU implementation.
+% The final challenge in on-the-fly template evaluation is performing the
+% convolution between the template and the target image. Standard convolution
+% would be prohibitively slow for the high resolution templates we're using, so we
+% implemented the convolution via Fast Fourier Transform on the GPU. This allows
+% template evaluation to run in \scream{x ms}, compared to \scream{x ms} for the
+% naive CPU implementation.
 
@@
 [Figure spectral analysis]
-
-\begin{figure}[t]
-  \centering
-  \includegraphics[width=0.5\linewidth]{residual}
-  \caption{Residual of differentd method}
-  \label{fig:whotime}
-\end{figure}
 
@@
 
-\begin{comment}
-\subsection{High Resolution Templates and FFT based Convolution}
-\label{sec:fft} 
-We generate high resolution templates with more than 250 HOG cells to capture details of an object to give accurate 2D-3D matching.
-These large templates cause computational burden when computing convolution.
-Though good for detecting accurate model and pose, convolution of high-resolution templates are much more slower since computation time scales linearly with the number of HOG cells in the template.
-To overcome and speed up the convolution, we propose FFT based GPU convolution which scales.
-Suppose there are length $n$ signal and length $m$ filter, naive convolution takes $O(nm)$ time where as FFT-based convolution takes $O\left( (n + m)\log (n+m) \right)$ time.
-For large $m$, high resolution template, we can gain computational advantage.
-
-we pad zero to the 2D image features by the largest kernel size.
-And we transform the kernel to match the padded image feature.
-To compute convolution, we compute element-wise product with the transformed kernel and sum all the features.
-Unlike \cite{Podlozhnyuk}, we do not need to shift the data nor kernel if we use simple mathematical trick.
-
-\begin{align}
-    x_{pad} & = \mathcal{P}_{n+m}(x)\\
-    y_{pad} & = \mathcal{P}_{n+m}(y)\\
-    x_{pad} \ast y_{pad} & = \mathcal{F}^{-1}(\mathcal{F}(x_{pad}) \circ \mathcal{F}(y_{pad}))
-\end{align}
-
-  Where $\ast$ is the circular convolution and $\circ$ is the Hadamard Product and $\mathcal{F}$ is the Fourier Transformation and $\mathcal{P}_n$ is the padding operation that append zeros to make vector of size $n$.
-
-For each dimension of features, we transform kernel and image feature into frequency domain using Fast Fourier Transformation.
-We transform the image into frequency domain once and use the transformed image for all templates.
-
-We implemented the convolution using FFT on GPU and got 10x speed up.
-
-[Figure for convolution time for different template resolution, CPU, GPU, naive convolution]
-\end{comment}
 %------------------------------------------------------------------------
-
-\section{Pose Fine-Tuning via MCMC}
-\label{sec:fine}
-\input{mcmc}
-%
-\section{Experiments}
-\label{sec:experiments}
-\input{experiments}
-
-\section{Conclusion}
-
-{\small
-\bibliographystyle{ieee}
-\bibliography{egbib}
-}
-
-\end{document}

### 2014-11-14 egpaper_final.tex
started pass over mcmc
cleaning up technical part in progress.

--- 2014-11-14 egpaper_final.tex
@@
 
+\section{Pipeline}
 \subsection{Rendering}
@@
 We used a public rendering engine to create realistic rendering and
-depth\begin{comment}\cite{Choy14render}\end{comment}. The CAD models we used
-in our experiments contain color, texture and material information such as
-transparency and reflectance. We tried to make the rendering as much realistic
+depth. We used CAD models that contain color, texture and material information such as
+transparency and reflectance to make the rendering as much realistic
 as possible to simulate the natural image statistics. The example rendering is
@@
 \end{equation}
-, we remove 2nd order correlation between all features. Since covarinace
-collection is expensive, \cite{Hariharan12} proposed easy way to generate
-covariance $\Sigma$ from autocovariance $\Gamma$
+, we remove 2nd order correlation between all features. Since collecting covariance matrix for every template shape
+ is expensive, \cite{Hariharan12} proposed easy way to synthesize
+covariance $\Sigma$ from autocovariance $\Gamma$ and we followed their method to generate $\Sigma$
 
@@
 The computational efficiency of our approach comes from using the iterative
-conjugate gradient method to whiten the HOG template. Whitening the non-zero
-feature vector $x'$ requires a system of linear equations $\Sigma' w' = (x' -
-\mu')$ to be solved. In
+Conjugate Gradient method to whiten a HOG template. Whitening the non-zero
+feature vector $x'$ means a solving the system of linear equations, $\Sigma' w' = (x' -
+\mu')$. In
 \cite{Hariharan12}, the authors make use of the fact that covariance matrices
 are symmetric and positive semidefinite to solve the system via the Cholesky
-decomposition, which requires $O(n^3)$ time.
+decomposition with Gaussian Elemination, which requires $O(n^3)$ time \scream{Citation for complexity}.
 
-The conjugate gradient method is an iterative algorithm for solving symmetric
+The Conjugate Gradient method is an iterative algorithm for solving symmetric
 positive definite systems which runs in $O(n^2\kappa)$ time, where $\kappa$ is
-the condition number of the matrix.
-This makes conjugate gradient faster than decomposition for matrices with small condition
+the condition number of the matrix. \scream{Citation for complexity}.
+
+This makes Conjugate Gradient faster than decomposition for matrices with small condition
 numbers relative to their size.
@@
 As a result, a GPU implementation of conjugate gradient converges in 50
-ms when using 250 HOG cells, two orders of magnitude faster than the system can be solved using the
-Cholesky factorization.
+ms when using 250 HOG cells, two orders of magnitude faster than the using
+Cholesky factorization with Gaussian Elemination. We report the real time
+analysis of whitening using decomposition and conjugate gradient methods in
+Fig.~\ref{fig:whotime}
+
+We compare the speed of each of template generation methods in
+Fig.~\cite{fig:covariancetime_crop} Using naive Cholesky decomposition,
+WHO template takes several seconds. But, if we use iterative Conjugate Gradient method, it only
+takes 100ms. If we use NZ-WHO, we can gain extra speed up since we only whitens non-zero cells.
+
+Also, since the iterative Conjugate Gradient method directly tries to reduce the residual (the norm of $y-Ax$ for $Ax = y$),
+it is more numerically stable than Cholesky decomposition with Gaussian Elemination. We vary the number of cells in a template
+and show that the residual of NZ-WHO is smaller than WHO Fig.~\ref{fig:whoresidual}.
+
+% Also, the residual from the Conjugate Gradient method (the norm of $y-Ax$ for $Ax = y$) is smaller than 
+% that of Cholesky decomposition.
 
@@
   \end{center}
-  \caption{(a) Comparison of WHO variants generation time and HOG extraction time (b) final speed of using NZ-WHO compare to WHO}
+  \caption{(a) Realtime analysis of whitening.
+HOG means feature extraction time, WHO-Chol uses method of \cite{Hariharan12} and WHO-CG uses iterative Conjugate Gradient, and NZ-WHO-CG uses only non-zero cells and use Conjugate Gradient.
+(b) final speed of using NZ-WHO compare to WHO}
   \label{fig:whotime}
 \end{figure}
-
-We compare the speed of each of template generation methods in
-Fig.~\cite{fig:covariancetime_crop} Using naive Cholesky decomposition,
-WHO template takes several seconds. But, if we use iterative Conjugate Gradient method, it only
-takes 100ms. If we use NZ-WHO, we can gain extra speed up since we only whitens non-zero cells.
-
-\subsubsection{Fast Convolution using the FFT}
-
-% We compare the performance of WHO and NZ-WHO on 3D Object dataset \cite{Savarese07} and report performance on Table \ref{tab:who_initializations}.
-
-% To deal with the problems, we propose Non-Zero Whitened Histograms of Orientations.
-
-% To accommodate the growing usage of rendering image for 2D-3D matching using
-% WHO\cite{Aubry13, Aubry14, Lim14}, we analyzed various methods to whiten
-% synthetic rendering image and propose Non-Zero Whitened Histograms of
-% Orientations (NZ-WHO) which is a direct extension of \cite{Hariharan12}
-% designed for rendering images with textureless background. % Since a NZ-WHO
-% template has zero-mean and all elements in the template follow same
-% distribution, no explicit calibration is required if all the templates have
-% approximately the same number of cells.
-
-% Since Combining NZ-WHO with Conjugate Gradient,
-
-% \subsection{Non-Zero Whitened Histograms of Orientations (NZ-WHO)}
-% why non zero whitening and why it makes more sense than seeing 3D, IKEA
-% Overview of the subsections
-%   Generating covariance quickly
-%   Fast inversion
-%   Regularization
-% Overview of the subsections
-% In this section, we will give a brief overview of whole whitening stages.
-In the first section \ref{feature_statistics}, we will discuss about first and second order statistics of HOG feature.
-Then, we will discuss about using autocovariance $\Gamma$ to create covariance matrix $\Sigma$ for non-zero cells and SIMD implementation to speed up the generation.
-Then, we will explain fast and accurate way to solve $w = \Sigma^{-1}x$ using Conjugate Gradient method.
-% Finally, we will analyze the effect of regularization.
-
-% \subsection{Whitening and Textureless Background}
-\begin{comment}
-\subsection{Constructing the Covariance Matrix}
-\label{sec:feature_statistics}
-% Whats used in our work and using Autocovariance matrix
-We first collected the first and second order statistics (mean and
-autocovariance) of HOG features from arbitrary natural images. Following
-\cite{Hariharan12}, we assume Wide-Sense Stationarity (WSS) of HOG features
-generated from natural images. That is, we assume the mean of a HOG cell is
-independent of its place in the image, and the autocovariance of patches depends
-only on their relative location.
-
-In one dimension, let $x(u)$ be the feature at location $u$. Then WSS states
-that $\mathbb{E}\left[x(u)\right] = \mu_x$ for all $u$, and
-\begin{equation}
-\textrm{cov}_x(u,v) = \textrm{cov}_x(0, v-u) = \Gamma(v-u),
-\end{equation} where $\Gamma$ is the autocovariance. For simplicity, we show the 1D case but this can be easily extended to 2D spatial autocovariance.
-
-Therefore, assuming WSS allows us to synthesize the covariance matrix for
-templates \emph{of any size} from the autocovariance matrix. This hugely reduces
-the memory required because to build the covariance matrix of a template of $w
-\times h$ HOG cells (with 31 elements per cell), we only need a $w \times h
-\times 31$ autocovariance matrix. In comparison, the covariance matrix itself is
-$(w \times h \times 31) \times (w \times h \times 31)$. Furthermore, by using
-the autocovariance we can avoid storing the covariance matrix for every
-different aspect ratio used during detection.
-
-To further simplify $\Gamma$, we assumed horizontal and vertical symmetry. In
-our implementation, we compute a $40 \times 40 \times 31$ autocovariance matrix,
-meaning we can synthesize covariance matrices for HOG grids as big as $40 \times
-40$. In practice we limit the number of cells per template to 250.
-
-We use the GPU to parallelize the lookup of the correct autocovariance cells
-during covariance matrix syntheses. The real time analysis for various number of cells is on Figure \ref{fig:covariancetime}).
-
-\end{comment}
-
-% Since the statistics have been computed for a generic HOG feature, we can use
-% the same statistics for all templates and images. In practice, since it is
-% expensive to whiten all the sliding patches in the image, we followed
-% \cite{Hariharan12} and defined the templates to be $w =
-% \Sigma^{-1}(X-E[X])$\begin{comment}which is a good approximation of
-% $\Sigma^{-\frac{T}{2}} \Sigma^{-\frac{1}{2}}(X-E[X])$\end{comment}
-
-% \begin{comment}Gathering statistics, especially computing spatial covariance
-% of a signal is computationally burdensome. \end{comment} To speed up the
-% statistics collection, \begin{comment}in addition to the wide-sense
-% stationarity (WSS) of HOG, \end{comment}we assumed horizontal and vertical
-% symmetry of covariance.
-
- %Hariharan \etal \cite{Hariharan12} interpreted the whitening also as the
- %Linear Discriminant Analysis where each class has the same covariance $\Sigma$
- %but with different mean value. They defined this whitened HOG feature as
- %Whitened Histograms of Orientations (WHO) and we will follow their convention
- %of the name.
-
-% \subsection{Rendering}
-% 
-% We used a public rendering engine to create realistic rendering and
-% depth\begin{comment}\cite{Choy14render}\end{comment}. The CAD models we used
-% in our experiments contain color, texture and material information such as
-% transparency and reflectance. We tried to make the rendering as much realistic
-% as possible to simulate the natural image statistics. The example rendering is
-% in Fig. \ref{fig:rendering}. We also extracted depth information as well while
-% rendering to use in the reconstruction.
-
-% To whiten a HOG features, we first have to synthesize the covariance matrix.
-% Following the method of \cite{Hariharan12}, which assumes spatial Wide-Sense
-% Stationarity (WSS) of a feature, covariance matrix can be synthesized using
-% spatial autocovariance $\Gamma$. This assumes the \begin{comment} and features
-% such as HOG are gradients in a small patch whose statistics does not change
-% (an object can be in anywhere in an image)\end{comment}.
-
-%However, unlike small fixed-sized mid-level patches, the root templates have
-%different aspect ratios, different gradient patterns and large number of HOG
-%cells which results in large covariance $\Sigma \in \mathcal{R}^{7000 \times
-%7000}$ that is difficult to cache. Thus, to generate a NZ-WHO template, we have
-%to synthesize a covariance matrix and solve the system of linear equations.
-
-% Thus, every time we whiten a root template, we have to generate a covariance
-% matrix using autocovariance $\Gamma$.
-
-%\begin{comment} Also, since we are whitening only the non-zero HOG cells whose
-%position is unknown beforehand and all templates have different aspect ratio
-%for , we cannot cache the matrix. Using CPU, it takes about \end{comment}
-
-% In practice, synthesizing covariance matrix $\Sigma$ takes long time due to
-% its large size.  $\Sigma$ ranges from $\Sigma \in \mathcal{R}^{7000 \times
-% 7000}$ to $\Sigma \in \mathcal{R}^{7500 \times 7500}$. We vary the template
-% resolution and run $\Sigma$ generation on CPU and GPU 100 times and report the
-% average time in Fig. \ref{fig:covariancetime}.
-
-% \begin{figure}[t]
-%   \begin{center}
-%      \includegraphics[width=0.9\linewidth]{covariancetime} 
-%   \end{center}
-%   \caption{Time to generate $\Sigma$ for various number of cells (left) and same plot on log scale(right). The time complexity increases as $O(n^2)$ for $n$ number of cells.}
-%   \label{fig:covariancetime_crop}
-% \end{figure}
-
-% 1-dimensional version of SIMD implementation that generate covariance matrix $\Sigma$ from autocovariance $\Gamma$ on GPU is on the supplementary material.
-% \begin{comment}i
-% \begin{algorithm}
-% \KwData{ $\Gamma$ , nonzero cell indexes, thread x id, thread y id}
-% \KwResult{ $\Sigma$ }
-% \Begin{
-% $c_u \leftarrow \mod(x, N_f)$ define cell $u$ coordinate\; 
-% $f_u \leftarrow u / N_f$ define feature index
-% $c_v \leftarrow \mod(y, N_f)$ define cell $v$ coordinate\;
-% $f_v \leftarrow v / N_f$ define feature index
-% $T \leftarrow $ nonzero cell indexes\;
-% $\Sigma(w) \leftarrow \Gamma( N_f ( T(u) - T(v) +  )$\;
-% }
-% \caption{SIMD implementation of covariance synthesis from autocovariance}
-% \end{algorithm}
-% \end{comment}
-
-The final challenge in on-the-fly template evaluation is performing the
-convolution between the template and the target image. Standard convolution
-would be prohibitively slow for the high resolution templates we're using, so we
-implemented the convolution via Fast Fourier Transform on the GPU. This allows
-template evaluation to run in \scream{x ms}, compared to \scream{x ms} for the
-naive CPU implementation.
-
-%  If we use a high resolution template such as \ref{fig:rendering}
-
-% where $w$ is the weight we want to find and $x$ is the HOG feature from the
-% rendering and $\lambda$ is the regularization constant (see section
-% \ref{sec:regularization}). For $w\in \mathcal{R}^n$, it takes $O(n^3)$ time to
-% solve the linear equation. If we use a high resolution template to capture
-% small geometric properties we can get high accuracy matchings but the solving
-% the linear equation becomes computationally burdensome.
-
-% To briefly recap, the LU Decomposition and Cholesky Decomposition are most
-% popular methods to solve a linear equation. In linear algebra libraries such
-% as MATLAB, these decomposition methods are default method to solve a linear
-% equation (backslash \textbackslash in MATLAB). Since the covariance matrix is
-% Hermitian and Positive Semi-Definite, we can use Cholesky Decomposition which
-% is twice as fast as the LU Decomposition.
-
-% decomposition methods such as LU or Cholesky Decomposition not only take long
-% time but they also accumulate numerical error.
-
-%In our setting, we used high resolution template which has more than 250 HOG
-%cells. This result in $\Sigma \in \mathcal{R}^{7500 \times 7500}$. It takes
-%about 9 seconds if we use LU decomposition and 5 seconds if we use Cholesky
-%decomposition.  % The default way of solving the linear equation in many linear
-%algebra library is decomposing the matrix using LU Decomposition (in MATLAB the
-%default method of backslash operator) which takes $O(\frac{2}{3}n^3)$ flops for
-%$n\times n$ matrix. Since the matrix, $\Sigma + \lambda I$ is Hermitian and
-%Positive Semi Definite. We can speed up using Cholesky Decomposition.
-
-%We also used iterative Conjugate Gradient to make use of low rank property of
-%the covariance \cite{Gharbi12}. After adding small regularization, the
-%regularized covariance matrix has nice spectral property (Figure
-%\ref{fig:spectral}). The singular values are clustered in small region and most
-%of the energies are concentrated on the first (number) singular values. Thus,
-%the conjugate gradients stage doesn't go upto the size of the matrix to
-%converge.
-
-[Figure spectral analysis]
 
@@
   \includegraphics[width=0.5\linewidth]{residual}
-  \caption{Residual of differentd method}
-  \label{fig:whotime}
+  \caption{Residuals from different method}
+  \label{fig:whoresidual}
 \end{figure}
 
+\subsection{High Resolution Templates and FFT based Convolution}
+\label{sec:fft} 
+We generate high resolution templates with more than 250 HOG cells to capture
+details of an object to give accurate 2D-3D matching. These large templates
+cause computational burden when computing convolution. Though good for
+detecting accurate model and pose, convolution of high-resolution templates are
+much slower since computation time scales linearly with the number of HOG
+cells in the template. To overcome and speed up the convolution, we used FFT
+based GPU convolution \cite{Podlozhnyuk} which scales. Briefly, for length $n$ signal and
+length $m$ filter, naive convolution takes $O(nm)$ time whereas FFT-based
+convolution takes $O\left( (n + m)\log (n+m) \right)$ time. For large $m$, high
+resolution template, we can gain computational advantage.
+
 \subsection{Variations of WHO}
-\scream{sam thinks this should be moved to the experiments section}
+
+To validate our approach, we run an ensemble of NZ-WHO templates as a bank of exemplar detectors and compare its performance with other WHO variants.
+Since WHO variants uses HOG features, they are slower than HOG templates but WHO variants in general performs better than WHO by significant margin.
+However, WHO using Cholesky decomposition with Gaussian Elemination takes the most time yet performs worse than NZ-WHO which is two order of magnitude faster to generate.
+
+We also calibrated the various methods
+
+In the experiment, we compared the performance of HOG, WHO, WHO-CG, WHO-CG-Z and NZ-WHO.
+The WHO refers to standard WHO using the method presented in \cite{Hariharan12}, WHO-CG uses iterative Conjugate Gradient method to generate WHO.
+WHO-CG-Z uses whiten the whole template and zero out textureless region.
+NZ-WHO-CG is the NZ-WHO which whitens only non-zero cells using iterative Conjugate Gradient method.
+The time column indicates the time to generate one template.
+We followed calibration procedure presented in \cite{Aubry14}
+
+The experiment results is on Tab.~\ref{tab:who_initializations}
+We found out that without calibration, NZ-WHO performs the best on object
+detection on 3DObject car dataset \cite{Savarese07}. See Table
+\ref{tab:who_initializations} for detail. In essence, if we use calibration, we
+could achieve better performance but since our goal is to do 2D-3D matching and
+continuous viewpoint estimation using on-the-fly template generation, we did not
+calibrated our templates.
+
 We empirically found out that NZ-WHO performs reasonably well without time
@@
 confidence.% Note that in Section \ref{experiments}, we provide the same
-experiment with 9 CAD models.
+% experiment with 9 CAD models.
 
@@
 \end{table*}
-
-We found out that without calibration, NZ-WHO performs the best on object
-detection on 3DObject car dataset \cite{Savarese07}. See Table
-\ref{tab:who_initializations} for detail. In essence, if we use calibration, we
-could achieve better performance but since our goal is to do 2D-3D matching and
-continuous viewpoint estimation using on-the-fly template generation, we did not
-calibrated our templates.
-
-\begin{comment}
-\subsection{Whitening Non-Zero Cells}
-
-% learning weights for whitened templates
-But since it is difficult to make templates to have the number of cells, \cite{Hariharan12, Aubry14, Lim14} learned weights for convolution score from the template.
-However, we propose a novel way to guarantee normalized score distribution by decorrelating non-zero HOG cells and forcing each template to have approximately same number of cells.
-
-% 
-Unlike \cite{Aubry14}, we did not whiten all cells and then zero out some HOG cells that are on the background.
-Instead, we whiten only the cells with non-zero value.
-We empirically found out that by whitening the cells that has non-zero support actually performs better and takes less time solving the linear equation $w = \Sigma^{-1}x$ since the number of elements to whiten decreases.
-However, by selecting non-zero cells, we destroys inherent Toeplitz-Block-Toeplitz property of the covariance matrix which could speed up the inversion using Fourier Transformation \cite{Akaike73, Martinsson05}.
-
-  We propose a whitening stage for WHO feature template generation that can create template whose convolution score follow same distribution.
-This guarantees that we do not require any calibration stage after generating templates rapidly.
-We statistically compare the score distribution of whitening non-zero HOG cell only and whitening.
-  \end{comment}
-
-% \subsection{Effect of Regularization}
-% \label{sec:regularization}
-%  Also, since all covariance matrix is Positive Semi Definite, our matrix
-%  $\Sigma$ must be Positive Semi-Definite too. To guarantee the property, We
-%  found out that the regularization has significant impact on the performance.
-%  In \cite{Hariharan12}, Hariharan \etal used small fixed regularization since
-%  the covariance matrix of specially correlated features is intrinsically
-%  row-rank to make the matrix invertible.
-%  
-% However if we closely analyze the impact of the regularization, we can see that larger the $\lambda$ is, the centered HOG becomes more dominant. 
-% 
-% \begin{align}
-% (\Sigma + \lambda I)^{-1} & = \frac{1}{\lambda}\left(I + \frac{1}{\lambda}\Sigma \right)^{-1} \\
-% & = \frac{1}{\lambda}\left(I - \frac{1}{\lambda} \Sigma  + \frac{1}{\lambda^2} \Sigma^{2} 
-% 		- \frac{1}{\lambda^3} \Sigma^{3} + \cdots \right)
-% % & = \frac{1}{\lambda}I - \left(I + \frac{1}{\lambda} \Sigma \right)^{-1} \frac{1}{\lambda^2} \Sigma
-% % & = \frac{1}{\lambda}\left(I  - \frac{1}{1 + \frac{1}{\Sigma} \Tr{\Sigma}} \right)
-% \end{align} 
-% 
-% We empirically found out that as $\lambda$ increases, AP converges to that of centered HOG feature without any whitening.
-
-\begin{comment}
-\subsection{No Calibration}
-  We created coarse viewpoint templates by whitening non-zero HOG cells and compare the average precision on 3D Object dataset \cite{Savarese07} with that of whitening all HOG cells.
-
-\begin{table}
-\begin{center}
-\begin{tabular}{|l|c|c|}
-\hline
-Whitening and AP & Whiten & No Whitening \\
-\hline\hline
-Average Precision & 89.205 & 74.478 \\
-\hline
-\end{tabular}
-\end{center}
-\caption{Effect of whitening on 3D Object Car validation set using one CAD model. The whitening dramatically increased the AP.}
-\end{table}
-\begin{table}
-\begin{center}
-\begin{tabular}{|l|c|c|}
-\hline
-Calibration methods \&AP & Whiten non-zero & Whiten all \\
-\hline\hline
-None & 89.205 & 86.676 \\
-Linear & 88.430 & 85.720 \\
-Gaussian & 87.913 & 84.567\\
-Number of non-zero cells & 84.734 & N/A\\
-\hline
-\end{tabular}
-\end{center}
-\caption{Various calibration and AP on small experimental set.
-Since the whitening templates with constant number of HOG cells create normalized feature, calibration using negative patches did not improve the AP.}
-\end{table}
-\end{comment}
-
-\begin{comment}
-\subsection{High Resolution Templates and FFT based Convolution}
-\label{sec:fft} 
-We generate high resolution templates with more than 250 HOG cells to capture details of an object to give accurate 2D-3D matching.
-These large templates cause computational burden when computing convolution.
-Though good for detecting accurate model and pose, convolution of high-resolution templates are much more slower since computation time scales linearly with the number of HOG cells in the template.
-To overcome and speed up the convolution, we propose FFT based GPU convolution which scales.
-Suppose there are length $n$ signal and length $m$ filter, naive convolution takes $O(nm)$ time where as FFT-based convolution takes $O\left( (n + m)\log (n+m) \right)$ time.
-For large $m$, high resolution template, we can gain computational advantage.
-
-we pad zero to the 2D image features by the largest kernel size.
-And we transform the kernel to match the padded image feature.
-To compute convolution, we compute element-wise product with the transformed kernel and sum all the features.
-Unlike \cite{Podlozhnyuk}, we do not need to shift the data nor kernel if we use simple mathematical trick.
-
-\begin{align}
-    x_{pad} & = \mathcal{P}_{n+m}(x)\\
-    y_{pad} & = \mathcal{P}_{n+m}(y)\\
-    x_{pad} \ast y_{pad} & = \mathcal{F}^{-1}(\mathcal{F}(x_{pad}) \circ \mathcal{F}(y_{pad}))
-\end{align}
-
-  Where $\ast$ is the circular convolution and $\circ$ is the Hadamard Product and $\mathcal{F}$ is the Fourier Transformation and $\mathcal{P}_n$ is the padding operation that append zeros to make vector of size $n$.
-
-For each dimension of features, we transform kernel and image feature into frequency domain using Fast Fourier Transformation.
-We transform the image into frequency domain once and use the transformed image for all templates.
-
-We implemented the convolution using FFT on GPU and got 10x speed up.
-
-[Figure for convolution time for different template resolution, CPU, GPU, naive convolution]
-\end{comment}
-%------------------------------------------------------------------------
 

### 2014-11-14 egpaper_final.tex

@@
 
-\section{Estimating Parameters using MCMC}
+\section{Pose Fine-Tuning via MCMC}
 \label{sec:fine}
-% Estimating viewpoint continuously to fine tune a initial matching
-The NZ-WHO template matching method we have presented makes template generation
-and evaluation computationally inexpensive. This means we can efficiently
-explore the parameter space to find the best object pose, scale, model type and
-camera focal length.
-
-Since creating a template and validating the template become computationally
-inexpensive, making a proposal and validating the proposal to fine tune a 2D-3D
-matching became affordable. We used Metropolis-Hastings algorithm to generate a
-proposal pose and focal length and validate the proposal using the convolution
-and returning maximum response as a return.
-
-To fine-tune continuous pose and location of object, we require strong
-initialization. The initialization is a rough bounding box with small context
-and viewpoint. Since most of the standard detectors does not provide viewpoint
-of an object, we first run an ensemble of NZ-WHO templates to get rough
-viewpoints. Once we get rough viewpoint, we initialize the proposal $x_0$ and
-start sampling proposals.
-
-We modeled the distribution of object location and pose as an exponential distribution. 
-For proposal distribution, we used Gaussian distribution to propose next viewpoint and for viewpoint proposals
-and uniform distribution for model change proposals.
-
-More formally, suppose that $x = [p, m, f]$ where $p$ is the 3D rotation of the CAD model and
-$m$ is the CAD model index and $f$ is the focal length. We use Metropolis Hastings
-to optimize $x$.
-
-\begin{align}
-    A(x \rightarrow x') & =  min\left( 1,  \frac{P(x' g(x') \rightarrow x)}{P(x) g(x \rightarrow x')}\right) \\
-    g(x \rightarrow x + p_i') & \sim \mathcal{N}(\mu = 0,\sigma = c_1) \quad i \in \{1,2,3\}\\
-    g(x \rightarrow x + f') & \sim \mathcal{N}(\mu = 0,\sigma = c_2)\\
-    g(x \rightarrow x + m') & \sim c_3 \delta(m) + (1-c_3) Unif(1,M)
-\end{align}
-
-Where $g$ is the proposal distribution and $P$ is the distribution of which we
-defined using Gaussian distribution around previous state. $A$ is the
-acceptance probability where we accept new proposal with $A(x \rightarrow x')$.
-
-\begin{align}
-    P(x) & \sim e^{ c_4 \max_{s} w(x) \ast \mathcal{T}_s(\mathcal{I}) }
-\end{align}
-
-$P$ is the distribution of the pose and location of an object on image
-$\mathcal{I}$. One can also think of the image as an image cropped by detection
-bounding box. We synthesize covariance matrix and create NZ-WHO template $w(x)$ for particular viewpoint, focal length and CAD model.
-
-We initialize the $x$ using the result from the previous stage where we run our ensemble or NZ-WHO templates to get rough estimate.
-
-In sum, for new proposal $x'$, we make a NZ-WHO template on the fly 
-We found out that it requires good initialization to converge to local minima.
-
-We represented the probability using exponential family.
-
-So our model favors large convolution score $\max_{s} w(x) \ast T(\mathcal{I})$. 
-% there are several advantages that was not possible such as \textbf{on-the-fly} template generation and making large number of templates  
-\begin{figure}[t]
-\centering
-    \includegraphics[width=0.7\linewidth]{tuning2} \\ [-5pt]
-    \caption{Different modes of Metropolis Hasting proposals, see Section \ref{sec:fine}}
- \label{fig:tuningmode}
-\end{figure}
-
+\input{mcmc}
 \section{Experiments}
@@
 
+\clearpage
+\clearpage
 {\small

### 2014-11-14 intro.tex
added method overview

@@
 implemented as extensions to existing detectors, such as the implicit
-shape models~\cite{}, the constellation model~\cite{}, or the
-deformable part model~\cite{Xiang12,Pepik12,Fidler12,Hejrati14}.
+shape models~\cite{sun10eccv}, the constellation model~\cite{stark10bmvc}, or the
+deformable part model~\cite{gu10eccv,Xiang12,Pepik12,Fidler12,Hejrati14}.
 
@@
 
+\begin{comment}
 \scream{Are we keeping the paragraphs from here...}
@@
 \scream{... to here?}
+\end{comment}

### 2014-11-14 mcmc.tex
MCMC secomd pass by chris

@@
 \paragraph{Probabilistic formulation.}
-We parameterize the continuous parameter space as  $x = [p, m, f]$,
-where $p$ is the 3D rotation of the CAD model, $m$ is the discrete CAD
+We parameterize the continuous parameter space as  $p = [v, m, f]$,
+where $v$ is the 3D rotation of the CAD model, $m$ is the discrete CAD
 model index, and $f$ is the focal length.
@@
 We model the probability that the object in the test image
-$\mathcal{I}$ is generated by the parameters $x$ as a distribution in
+$\mathcal{I}$ is generated by the parameters $p$ as a distribution in
 the exponential family, and let
 \begin{align}
-    P(x) & \sim e^{ c_4 \max_{s} w(x) \ast \mathcal{T}_s(\mathcal{I})},
+    P(p) & \sim e^{ \max_{s} w(p) \ast \mathcal{T}_s(\mathcal{I})},
 \end{align}
-where $\max_{s} w(x) \ast T(\mathcal{I})$ is the convolution score of
-template $w(x)$ with image feautures $T(\mathcal{I})$, as defined
-in Sect.~\ref{}.
+where $\max_{s} w(p) \ast T_s(\mathcal{I})$ is the maximum convolution score of
+NZ-WHO template $w(p)$ with image feautures $T_s(\mathcal{I})$ for all scale $s$, as defined
+in Sect.~\ref{}. \scream{chris: I'll add this to technical part}
 
 \paragraph{Inference.}
-We approximate the MAP solution for $x$ by drawing samples from the
-distribution $P(x)$, using the Metropolis-Hastings
+We approximate the MAP solution for $p$ by drawing samples from the
+distribution $P(p)$, using the single component Metropolis-Hastings
 algorithm. Specifically, we use a variant that changes only a single
-component of the parameter vector $x$ at a time, termed Single
-Component Metropolis Hastings.
+component of the parameter vector $p$ at a time, termed Single
+Component Metropolis Hastings \cite{mcmc}.
 
-This algorithm changes the current state $x$ to a new state $x'$ based
+This algorithm changes the current state $p$ to a new state $q$ based
 on the acceptance probability
 \begin{align}
-    A(x \rightarrow x') & =  min\left( 1,  \frac{P(x' g(x') \rightarrow x)}{P(x) g(x \rightarrow x')}\right).
+    A(p \rightarrow q) & =  min\left( 1,  \frac{P(q) g(q \rightarrow p)}{P(p) g(p \rightarrow q)}\right).
 \end{align}
-We define $4$ different types of moves that can alter the state
+We define $3$ different types of moves that can alter the state
 (Fig.~\ref{fig:moves}), {\em (i)} changing the focal length $f$, {\em
-  (ii)} one of the rotational pose parameters $p_i$, {\em (iii)} scale
-  or translation, and {\em (iv)} CAD model index $m$. For (i) to
-  (iii), we use Gaussian proposal distributions, and a uniform
-  distribution over model changes for (iv).
+(ii)} one of the rotational pose parameters $v_i$, and {\em (iii)} CAD model
+index $m$. For (i) and (ii), we use Gaussian proposal distributions, and a uniform
+distribution over model changes for (iii). \scream{For scale and translation, we
+implicitly compute all possible translation and scale by convolving $w(q)$ to
+HOG pyramid.}
 \begin{align}
-    g(x \rightarrow x + p_i') & \sim \mathcal{N}(\mu = 0,\sigma = c_1) \quad i \in \{1,2,3\}\\
-    g(x \rightarrow x + f') & \sim \mathcal{N}(\mu = 0,\sigma = c_2)\\
-    g(x \rightarrow x + m') & \sim c_3 \delta(m) + (1-c_3) Unif(1,M),
+    g(p \rightarrow p + v_i') & \sim \mathcal{N}(\mu = 0,\sigma = \sigma_v) \quad i \in \{1,2,3\}\\
+    g(p \rightarrow p + f') & \sim \mathcal{N}(\mu = 0,\sigma = \sigma_f)\\
+    g(p \rightarrow p + m') & \sim c \delta(m) + (1-c) Unif(1,M),
 \end{align}
@@
 % local minima.
-In practice, we run this algorithm for \scream{} iterations, keeping
+
+In practice, we run this algorithm for 20 iterations, keeping
 the sample with the highest probability as our approximate estimate of
-the MAP solution.
-\scream{no idea what c is}
+the MAP solution. \scream{We set $\sigma_v = 5$ degree and $\sigma_f = 1$ and
+$c = 0.1$ for all experiments.}
 

### 2014-11-14 approach.tex
excised sec 4 in own file

--- 2014-11-14 egpaper_final.tex
@@
-\documentclass[10pt,twocolumn,letterpaper]{article}
-
-\usepackage{cvpr}
-\usepackage{times}
-\usepackage{epsfig}
-\usepackage{graphicx}
-\usepackage{amsmath}
-\usepackage{amssymb}
-\usepackage{caption}
-\usepackage{verbatim}
-\usepackage{subcaption}
-\usepackage{algorithm2e}
-\usepackage{rotating}
-\usepackage[space]{grffile}
-\usepackage[font=small,skip=0pt]{caption}
-%\DeclareMathOperator{\Tr}{Tr}
-% Include other packages here, before hyperref.
-
-% If you comment hyperref and then uncomment it, you should delete
-% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
-% run, let it finish, and you should be clear).
-\usepackage[breaklinks=true,bookmarks=false]{hyperref}
-\graphicspath{ {figures/} }
-% \cvprfinalcopy % *** Uncomment this line for the final submission
-
-\def\cvprPaperID{****} % *** Enter the CVPR Paper ID here
-\def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}
-
-% custom commands
-\newcommand{\scream}[1]{{\color{red} \bf *** #1 ***}}
-
-% Pages are numbered in submission mode, and unnumbered in camera-ready
-%\ifcvprfinal\pagestyle{empty}\fi
-\setcounter{page}{1}
-\begin{document}
-
-%%%%%%%%% TITLE
-\title{Enriching Object Detection with 2D-3D Registration and Continuous Viewpoint}
-%\title{Enrich Object Detection : 2D-3D registration and continuous viewpoint estimation}
-
-\author{First Author\\
-Institution1\\
-Institution1 address\\
-{\tt\small firstauthor@i1.org}
-% For a paper whose authors are all at the same institution,
-% omit the following lines up until the closing ``}''.
-% Additional authors and addresses can be added with ``\and'',
-% just like the second author.
-% To save space, use either the email address or home page, not both
-\and
-Second Author\\
-Institution2\\
-First line of institution2 address\\
-{\tt\small secondauthor@i2.org}
-}
-
-\maketitle
-%\thispagestyle{empty}
-
-%%%%%%%%% ABSTRACT
-\begin{abstract}
-A large body of recent work on object detection has focused on exploiting 3D CAD
-model databases to improve detection performance. Many of these approaches work
-by aligning exact 3D models to images using templates generated from renderings
-of the 3D models at a finite set of discrete viewpoints. The training procedures
-for these approaches, however, are very expensive and require gigabytes of
-memory and storage, and the viewpoint discretization hampers pose estimation
-performance.
-
-We propose an efficient method for synthesizing templates from 3D models that
-runs on the fly -- that is, it quickly produces detectors for an arbitrary
-viewpoint of a 3D model without expensive dataset-dependent training or template
-storage. Given a 3D model and an arbitrary continuous detection viewpoint, our
-method synthesizes a discriminative template by extracting features from a
-rendered view of the object and decorrelating spatial dependences among the
-features. Our decorrelation procedure relies on a gradient-based algorithm that
-is more numerically stable than standard decomposition-based procedures, and we
-efficiently search for candidate detections by computing FFT-based template
-convolutions. Due to the speed of our template synthesis procedure, we are able
-to perform joint optimization on continuous scale, translation, rotation, and
-focal length. We provide an efficient GPU implementation of our algorithm, and
-we validate its performance on 3DObject dataset and PASCAL 2012 dataset.
-
-%     Using 3D model to detect and register the model to RGB image has been a
-%     growing field of study. Recently, Aubry \etal \cite{Aubry14} and J. Lim
-%     \etal \cite{Lim14} tried to estimate pose and align exact CAD model to an
-%     image using part-based templates. Malisiewicz \etal \cite{Malisiewicz11}
-%     also addresses the issue by transferring metadata after detection. Hejrati
-%     \etal \cite{Hejrati14} uses template synthesis to detect an object. All
-%     these approaches require extensive training, a lot of memory space. Also,
-%     the training based approach requires defining fixed viewpoints which limit
-%     themselves.  To overcome these difficulties, we propose an efficient and
-%     fast way to synthesize and validate templates using on the fly realistic
-%     rendering that can jointly optimize scale, translation, rotation and focal
-%     length continuously. We render an object and extract features and
-%     decorrelate spatial dependencies within them on the fly to make a
-%     discriminative template. To speed up the decorrelation procedure, we adopt
-%     a gradient based algorithm which is numerically more stable than
-%     decomposition procedure. Finally, we efficiently search for candidate
-%     match by computing convolution using FFT and jointly optimize to match the
-%     object accurately. To speed up further, we propose an efficient GPU
-%     implementation and tested on PASCAL images.
-
-%   In contrast to other mid-level patch based 3D matching methods which
-%   requires extensive training and more than 10Gb of memory space and physical
-%   storage, ours require no training nor saving the templates thus enabling it
-%   to run on any personal computer.  To overcome these difficulties, we propose
-%   an efficient and fast way to synthesize and validate templates using on the
-%   fly realistic rendering that can jointly optimize scale, translation,
-%   rotation and focal length continuously. We render an object and extract
-%   features and decorrelate spatial dependencies within them on the fly to make
-%   a discriminative template. To speed up the decorrelation procedure, we adopt
-%   a gradient based algorithm which is numerically more stable than
-%   decomposition procedure. Finally, we efficiently search for candidate match
-%   by computing convolution using FFT and jointly optimize to match the object
-%   accurately. To speed up further, we propose an efficient GPU implementation
-%   and tested on PASCAL images.
-
-\end{abstract}
-
-%%%%%%%%% BODY TEXT
-\section{Introduction}
-\label{sec:intro}
-\input{intro}
-%
-\section{Related Work}
-\label{sec:related}
-\input{related}
-
-\section{Approach Overview}
-\label{sec:nz-who}
-\input{overview}
-
-\section{Pipeline}
 \subsection{Rendering}
@@
 This speedup allows us to generate NZ-WHO templates on the fly, allowing us to quickly evaluate arbitrary viewpoint hypotheses.}
-\scream{add comments about the fig:whocomparison}
+%\scream{add comments about the fig:whocomparison}
 
@@
 \end{table*}
-
-\section{Pose Fine-Tuning via MCMC}
-\label{sec:fine}
-\input{mcmc}
-\section{Experiments}
-\label{sec:experiments}
-\input{experiments}
-
-\section{Conclusion}
-
-\clearpage
-\clearpage
-{\small
-\bibliographystyle{ieee}
-\bibliography{egbib}
-}
-
-\end{document}

### 2014-11-14 egpaper_final.tex
excised sec 4 in own file

@@
 \section{Pipeline}
-\subsection{Rendering}
-
-We used a public rendering engine to create realistic rendering and
-depth. We used CAD models that contain color, texture and material information such as
-transparency and reflectance to make the rendering as much realistic
-as possible to simulate the natural image statistics. The example rendering is
-in Fig. \ref{fig:rendering}. We also extracted depth information as well while
-rendering to use in the reconstruction.
-
-We used a collection of CAD models to make exemplar renderings of CAD models and for viewpoints. The
-CAD models are cached so that when we fine-tune 2D-3D matching, so it can be rendered instantaneously.
-We made the renderings to change focal length and yaw, pitch, roll so that we can fine tune the matching
-continuously.
-
-\begin{figure}[t]
-  \begin{center}
-     \includegraphics[width=0.4\linewidth]{rendering}
-     \includegraphics[width=0.4\linewidth]{depth}
-  \end{center}
-  \caption{Example rendering and depth made by our renderer}
-  \label{fig:rendering}
-\end{figure}
-
-\subsection{Whitened Histograms of Orientations (WHO)}
-\label{sec:who}
-Recently, Hariharan \etal. introduced Whitened Histograms of Orientations (WHO)
-\cite{Hariharan12}, which uses statistics from natural images to whiten HOG
-templates, making them more discriminative. Whitening is a common signal
-processing operation for decorrelating a set of random variables
-\cite{Martinsson05, Belouchrani00}. More formally, suppose that we have a
-$k$-dimensional random variable $X \in \mathcal{R}^k$ with $Cov(X)=\Sigma$. By
-whitening the signal,
-\begin{equation}
-\tilde{X}=\Sigma^{-\frac{1}{2}}(X - E[X]) \label{eq:whitening}
-\end{equation}
-, we remove 2nd order correlation between all features. Since collecting covariance matrix for every template shape
- is expensive, \cite{Hariharan12} proposed easy way to synthesize
-covariance $\Sigma$ from autocovariance $\Gamma$ and we followed their method to generate $\Sigma$
-
-% The whitening and LDA have the same
-% formulation when we make a decision boundary $w = \Sigma^{-1}(\mu_+ - \mu_0)$
-% where $\mu_+$ is the features from a class (LDA) or a signal to whiten
-% (whitening), $\mu_0$ is the negative class center (LDA) or the signal mean
-% (whitening) and $\Sigma$ is the covariance matrix of classes (LDA) or
-% the correlation within signal (whitening).
-
-% In \cite{Hariharan12}, the authors compute the mean and covariance matrix by assuming Wide-Sense Stationarity (WSS) of HOG features
-% generated from natural images. That is, they assume the mean of a HOG cell is
-% independent of its place in the image, and the autocovariance of cells depends
-% only on their relative location.
-
-% In one dimension, let $x(u)$ be the feature at location $u$. Then WSS states
-% that $\mathbb{E}\left[x(u)\right] = \mu$ for all $u$, and
-% \begin{equation}
-% \textrm{cov}_x(u,v) = \textrm{cov}_x(0, v-u) = \Gamma(v-u),
-% \end{equation} where $\Gamma$ is the autocovariance. For simplicity, we describe the 1D case but this can be easily extended to 2D spatial autocovariance.
-% 
-% Therefore, assuming WSS allows the covariance matrix of templates \emph{of any
-% size} to be synthesized from the autocovariance matrix using a simple lookup.
-
-% However, the 
-% We propose Non-Zero Whitened Histograms of Orientations (NZ-WHO), that are both
-% more discriminative than WHO, and can be generated several orders of magnitude
-% faster (in 70ms compared to several seconds for WHO). This speed up means we
-% can generate templates on the fly, allowing our approach to evaluate arbitrary
-% viewpoint hypotheses.
-
-% Our method requires generating a covariance matrix of non-zero cells
-
-\subsubsection{Whitening Synthesized Templates and Non-Zero WHO}
-\label{sec:nzwho}
-Our first innovation is `Non-Zero' whitening. When synthesizing detection
-templates from rendered images, a common problem is how to handle the
-background. If the model is rendered over a natural image background, gradients
-in the background will be incorporated into the discriminative template,
-potentially causing false-positives if background elements exist in the query
-image.
-
-Alternatively, if the background is left textureless (see
-Fig.~\ref{fig:rendering}), whitening the resulting HOG template
-will produce undesirable background artifacts. These are created when centering
-the template (by subtracting the mean $\mu$), where strong negative weights are
-introduced in the textureless region (as seen in Fig.~\ref{fig:whocomparison}).
-This could result in positive matches being suppressed due to spurious
-background gradients.
-
-NZ-WHO removes these artifacts so that the background has no effect on the
-template response. Given HOG features $x$, we create a new vector $x'$ which
-contains only the non-zero elements of $x$. We select the same elements of
-$\mu$ to produce $\mu'$, while the autocovariance lookup is only performed for
-the cells with non-zero gradient, producing $\Sigma'$ corresponding to the
-features in $x'$. After solving the resulting system (which is now smaller than
-in the WHO approach) we find
-
-\begin{equation}
-w'=\Sigma'^{-1}(x' - \mu') \label{eq:nz-who},
-\end{equation}which we reassemble into the final NZ-WHO template $w$ by
-replacing the non-zero elements of $x$ with the corresponding $w'$ element.
-
-% Notice that $\Sigma$ is not square-rooted in Eq.~\ref{eq:nz-who}, whereas it is
-% in the definition of whitening (Eq.~\ref{eq:whitening}). This is because the
-% whitened template will only be used in the context of detection, which involves
-% the inner product with the whitened HOG features of the query image $y$:
-% \begin{equation}
-% (y-\mu)^{T}\Sigma^{-\frac{1}{2}}\Sigma^{-\frac{1}{2}}(x-\mu)\\
-% = (y-\mu)^{T} w.
-% \end{equation}
-% We can therefore capture the whitening of the query image features in $w$.
-
-% We use the GPU to parallelize the lookup of the correct autocovariance cells during covariance matrix syntheses, which is \scream{x} times faster than using the CPU (Figure \ref{fig:covariancetime}).
-
-%\scream{chris:We propose Non-Zero Whitened Histograms of Orientations (NZ-WHO), an improvement over WHO which is both more discriminative than WHO and can be computed many orders of magnitude faster than WHO (70ms as opposed to to several seconds for WHO).
-This speedup allows us to generate NZ-WHO templates on the fly, allowing us to quickly evaluate arbitrary viewpoint hypotheses.}
-\scream{add comments about the fig:whocomparison}
-
-\begin{figure}[t]
-  \begin{center}
-%   \fbox{\rule{0pt}{2in} \rule{0.9\linewidth}{0pt}}
-    % include whitening all centered cells
-    % \includegraphics[width=0.32\linewidth]{whiten_all_crop}
-    \setlength\tabcolsep{3pt}
-    \begin{tabular}{ccc}
-      HOG & WHO & NZ-WHO \\
-%     \begin{turn}{90}$w_+$\end{turn} &
-    \includegraphics[width=0.28\linewidth]{hog_crop} &
-    \includegraphics[width=0.28\linewidth]{whiten_all_crop} &
-    \includegraphics[width=0.28\linewidth]{whiten_non_zero_crop} \\
-    % include whitening all centered cells
-     % \includegraphics[width=0.282\linewidth]{whiten_all_neg_crop} 
-%     \begin{turn}{90}$-w_-$\end{turn} &
-     \includegraphics[width=0.28\linewidth]{hog_neg_crop} &
-     \includegraphics[width=0.28\linewidth]{whiten_all_neg_crop}  &
-     \includegraphics[width=0.28\linewidth]{whiten_non_zero_neg} \\
-    % include whitening all centered cells
- %    \begin{turn}{90}ihog\cite{vondrick2013}\end{turn} &
-    % \cite{vondrick2013}& 
-     \includegraphics[width=0.28\linewidth]{ihog_hog200_crop.png} &
-     \includegraphics[width=0.28\linewidth]{ihog_whiten_all200_crop.png} &
-     \includegraphics[width=0.28\linewidth]{ihog_whiten_non_zero200_crop.png} \\
- \end{tabular}
-  \end{center}
-  \caption{Comparison of HOG, WHO and NZ-WHO.
-Visualization of positive weights (first row),  visualization of negative weights (second row), HOGgles \cite{vondrick2013} (third row).
-Note that for WHO, whitening all cell result in strong negative edges on the empty region}
-  \label{fig:whocomparison}
-\end{figure}
-
-\subsubsection{Fast Whitening using Conjugate Gradient}
-
-The computational efficiency of our approach comes from using the iterative
-Conjugate Gradient method to whiten a HOG template. Whitening the non-zero
-feature vector $x'$ means a solving the system of linear equations, $\Sigma' w' = (x' -
-\mu')$. In
-\cite{Hariharan12}, the authors make use of the fact that covariance matrices
-are symmetric and positive semidefinite to solve the system via the Cholesky
-decomposition with Gaussian Elemination, which requires $O(n^3)$ time \scream{Citation for complexity}.
-
-The Conjugate Gradient method is an iterative algorithm for solving symmetric
-positive definite systems which runs in $O(n^2\kappa)$ time, where $\kappa$ is
-the condition number of the matrix. \scream{Citation for complexity}.
-
-This makes Conjugate Gradient faster than decomposition for matrices with small condition
-numbers relative to their size.
-
-The covariance matrix for HOG templates is typically ill-conditioned\cite{Hariharan12}, but we
-can add a regularization constant to the diagonal to reduce its condition
-number to the point where the conjugate gradient method will converge quickly.
-We use a constant of $0.15$, which reduces the condition number from $10^{20}$
-to $50$, much smaller than the dimension of the matrix (7000).
-
-As a result, a GPU implementation of conjugate gradient converges in 50
-ms when using 250 HOG cells, two orders of magnitude faster than the using
-Cholesky factorization with Gaussian Elemination. We report the real time
-analysis of whitening using decomposition and conjugate gradient methods in
-Fig.~\ref{fig:whotime}
-
-We compare the speed of each of template generation methods in
-Fig.~\cite{fig:covariancetime_crop} Using naive Cholesky decomposition,
-WHO template takes several seconds. But, if we use iterative Conjugate Gradient method, it only
-takes 100ms. If we use NZ-WHO, we can gain extra speed up since we only whitens non-zero cells.
-
-Also, since the iterative Conjugate Gradient method directly tries to reduce the residual (the norm of $y-Ax$ for $Ax = y$),
-it is more numerically stable than Cholesky decomposition with Gaussian Elemination. We vary the number of cells in a template
-and show that the residual of NZ-WHO is smaller than WHO Fig.~\ref{fig:whoresidual}.
-
-% Also, the residual from the Conjugate Gradient method (the norm of $y-Ax$ for $Ax = y$) is smaller than 
-% that of Cholesky decomposition.
-
-\begin{figure}[t]
-  \begin{center}
-  \begin{tabular}{cc}
-     \includegraphics[width=0.5\linewidth]{whotime} & 
-     \includegraphics[width=0.5\linewidth]{speedup}\\
-     (a) & (b) \\
- \end{tabular}
-  \end{center}
-  \caption{(a) Realtime analysis of whitening.
-HOG means feature extraction time, WHO-Chol uses method of \cite{Hariharan12} and WHO-CG uses iterative Conjugate Gradient, and NZ-WHO-CG uses only non-zero cells and use Conjugate Gradient.
-(b) final speed of using NZ-WHO compare to WHO}
-  \label{fig:whotime}
-\end{figure}
-
-\begin{figure}[t]
-  \centering
-  \includegraphics[width=0.5\linewidth]{residual}
-  \caption{Residuals from different method}
-  \label{fig:whoresidual}
-\end{figure}
-
-\subsection{High Resolution Templates and FFT based Convolution}
-\label{sec:fft} 
-We generate high resolution templates with more than 250 HOG cells to capture
-details of an object to give accurate 2D-3D matching. These large templates
-cause computational burden when computing convolution. Though good for
-detecting accurate model and pose, convolution of high-resolution templates are
-much slower since computation time scales linearly with the number of HOG
-cells in the template. To overcome and speed up the convolution, we used FFT
-based GPU convolution \cite{Podlozhnyuk} which scales. Briefly, for length $n$ signal and
-length $m$ filter, naive convolution takes $O(nm)$ time whereas FFT-based
-convolution takes $O\left( (n + m)\log (n+m) \right)$ time. For large $m$, high
-resolution template, we can gain computational advantage.
-
-\subsection{Variations of WHO}
-
-To validate our approach, we run an ensemble of NZ-WHO templates as a bank of exemplar detectors and compare its performance with other WHO variants.
-Since WHO variants uses HOG features, they are slower than HOG templates but WHO variants in general performs better than WHO by significant margin.
-However, WHO using Cholesky decomposition with Gaussian Elemination takes the most time yet performs worse than NZ-WHO which is two order of magnitude faster to generate.
-
-We also calibrated the various methods
-
-In the experiment, we compared the performance of HOG, WHO, WHO-CG, WHO-CG-Z and NZ-WHO.
-The WHO refers to standard WHO using the method presented in \cite{Hariharan12}, WHO-CG uses iterative Conjugate Gradient method to generate WHO.
-WHO-CG-Z uses whiten the whole template and zero out textureless region.
-NZ-WHO-CG is the NZ-WHO which whitens only non-zero cells using iterative Conjugate Gradient method.
-The time column indicates the time to generate one template.
-We followed calibration procedure presented in \cite{Aubry14}
-
-The experiment results is on Tab.~\ref{tab:who_initializations}
-We found out that without calibration, NZ-WHO performs the best on object
-detection on 3DObject car dataset \cite{Savarese07}. See Table
-\ref{tab:who_initializations} for detail. In essence, if we use calibration, we
-could achieve better performance but since our goal is to do 2D-3D matching and
-continuous viewpoint estimation using on-the-fly template generation, we did not
-calibrated our templates.
-
-We empirically found out that NZ-WHO performs reasonably well without time
-consuming calibration stage compare to other variational method to generate
-templates. We used 1 CAD model with viewpoints covering 24 azimuths and 4
-elevations. Each template takes approximately 80 milliseconds to generate a
-NZ-WHO template. We also calibrated templates using the method presented in
-\cite{Aubry14}. The calibration learns affine transformation of the detection
-confidence.% Note that in Section \ref{experiments}, we provide the same
-% experiment with 9 CAD models.
-
-\begin{table*}[!htbp]
-    \footnotesize
-    \begin{center}
-\begin{tabular}{|c|c|r|c|r|}
-\hline
-Methods (AP/MPPE) & before calibration  & time & after calibration \cite{Aubry14} & time \\
-\hline\hline
-HOG\cite{Dalal05}     & 72.3 / 65.0           &  31ms  & 60.4 / 50.2                 & 8.7 sec \\ 
-WHO\cite{Hariharan12} & 82.1 / 85.4           &  3811ms& 84.4 / 83.0                 & 12.4 sec  \\
-WHO-CG                & 81.7 / \textbf{84.9}  &  104ms & 83.7 / 87.3                 & 8.3 sec \\
-WHO-CG-Z              & 54.4 / 65.1           &  103ms & \textbf{92.8} / 86.7        & 8.7 sec  \\
-% NZC-WHO-Z    & 89.10/\textbf{78.64} &    & 91.15/74.79                  &     \\
-NZ-WHO-CG             & \textbf{90.0} / 82.8  &   79ms & 90.3 / \textbf{86.8}        & 8.5 sec   \\
-\hline
-\end{tabular}
-\end{center}
-\caption{Average Precision(AP) and Mean Precision in Pose Estimation (MPPE) \cite{Lopez-Sastre11} variations of WHO on 3DObject Car dataset\cite{Savarese07}.
-WHO refers to standard WHO using the method presented in \cite{Hariharan12}, WHO-CG uses iterative Conjugate Gradient method to generate WHO.
-WHO-CG-Z uses whiten the whole template and zero out textureless region.
-NZ-WHO-CG is the NZ-WHO which whitens only non-zero cells using iterative Conjugate Gradient method.
-The time column indicates the time to generate one template.
-We followed calibration procedure presented in \cite{Aubry14}.}
-\label{tab:who_initializations}
-\end{table*}
+\label{sec:approach}
+\input{approach}
 
@@
 \input{mcmc}
+
 \section{Experiments}

### 2014-11-14 approach.tex
started pass over sect 4

@@
+In this section, we describe our approach to generating 3D
+exemplare-based templates on-the-fly. It is based on 3D CAD model
+rendering (Sect.~\ref{sec:rendering}) followed by feature extraction
+and applying a whitening procedure. Based on the original whitening
+formulation (Sect.~\ref{sec:who}), we propose three novel extensions that
+enable the application of whitening to the on-the-fly setting.
+%
+First, we adapt the whitening to the specific case of rendered
+images (Sect.~\ref{sec:nzwho}). Second, we show how to speed up the
+whitening by two orders of magnitudes for high-resolution templates
+(Sect.~\ref{sec:fastwhiten}). And third, we improve the runtime of our
+3D exemplar template detectors also at test time, by performing
+convolutions in the frequency domain (Sect.~\ref{sec:fft}).
+
 \subsection{Rendering}
-
+\label{sec:rendering}
 We used a public rendering engine to create realistic rendering and
@@
 \label{sec:who}
+Our technique for rendering and training template detectors on-the-fly
+is drawing from recent work, which we review briefly in this section.
+%
 Recently, Hariharan \etal. introduced Whitened Histograms of Orientations (WHO)
@@
 \begin{equation}
-\tilde{X}=\Sigma^{-\frac{1}{2}}(X - E[X]) \label{eq:whitening}
+\tilde{X}=\Sigma^{-\frac{1}{2}}(X - E[X]) \label{eq:whitening},
 \end{equation}
-, we remove 2nd order correlation between all features. Since collecting covariance matrix for every template shape
+we remove 2nd order correlation between all features. Since collecting covariance matrix for every template shape
  is expensive, \cite{Hariharan12} proposed easy way to synthesize
-covariance $\Sigma$ from autocovariance $\Gamma$ and we followed their method to generate $\Sigma$
+covariance $\Sigma$ from autocovariance $\Gamma$ and we followed their
+method to generate $\Sigma$.
 
@@
 
-\subsubsection{Whitening Synthesized Templates and Non-Zero WHO}
+\subsection{Whitening Synthesized Templates and Non-Zero WHO}
 \label{sec:nzwho}
@@
 
-\subsubsection{Fast Whitening using Conjugate Gradient}
+\subsection{Fast Whitening using Conjugate Gradient}
+\label{sec:fastwhiten}
+Our second innovation lies in enhancing the computational efficiency
+of the whitening procedure, making it applicable to an on-the-fly
+rendering setting.
+%
+It originates from the insight that an iterative
+Conjugate Gradient method can be used to whiten a HOG template, which
+is much faster than the original procedure proposed
+in~\cite{Hariharan12} based on decomposition.
 
-The computational efficiency of our approach comes from using the iterative
-Conjugate Gradient method to whiten a HOG template. Whitening the non-zero
+Whitening the non-zero
 feature vector $x'$ means a solving the system of linear equations, $\Sigma' w' = (x' -
@@
 \end{figure}
-
+%
 \begin{figure}[t]
@@
 \subsection{Variations of WHO}
-
+\label{sec:variations}
 To validate our approach, we run an ensemble of NZ-WHO templates as a bank of exemplar detectors and compare its performance with other WHO variants.

### 2014-11-14 approach.tex
moved who comparison to exp section

@@
 analysis of whitening using decomposition and conjugate gradient methods in
-Fig.~\ref{fig:whotime}
+Fig.~\ref{fig:whotime}.
 
@@
 resolution template, we can gain computational advantage.
-
-\subsection{Variations of WHO}
-\label{sec:variations}
-To validate our approach, we run an ensemble of NZ-WHO templates as a bank of exemplar detectors and compare its performance with other WHO variants.
-Since WHO variants uses HOG features, they are slower than HOG templates but WHO variants in general performs better than WHO by significant margin.
-However, WHO using Cholesky decomposition with Gaussian Elemination takes the most time yet performs worse than NZ-WHO which is two order of magnitude faster to generate.
-
-We also calibrated the various methods
-
-In the experiment, we compared the performance of HOG, WHO, WHO-CG, WHO-CG-Z and NZ-WHO.
-The WHO refers to standard WHO using the method presented in \cite{Hariharan12}, WHO-CG uses iterative Conjugate Gradient method to generate WHO.
-WHO-CG-Z uses whiten the whole template and zero out textureless region.
-NZ-WHO-CG is the NZ-WHO which whitens only non-zero cells using iterative Conjugate Gradient method.
-The time column indicates the time to generate one template.
-We followed calibration procedure presented in \cite{Aubry14}
-
-The experiment results is on Tab.~\ref{tab:who_initializations}
-We found out that without calibration, NZ-WHO performs the best on object
-detection on 3DObject car dataset \cite{Savarese07}. See Table
-\ref{tab:who_initializations} for detail. In essence, if we use calibration, we
-could achieve better performance but since our goal is to do 2D-3D matching and
-continuous viewpoint estimation using on-the-fly template generation, we did not
-calibrated our templates.
-
-We empirically found out that NZ-WHO performs reasonably well without time
-consuming calibration stage compare to other variational method to generate
-templates. We used 1 CAD model with viewpoints covering 24 azimuths and 4
-elevations. Each template takes approximately 80 milliseconds to generate a
-NZ-WHO template. We also calibrated templates using the method presented in
-\cite{Aubry14}. The calibration learns affine transformation of the detection
-confidence.% Note that in Section \ref{experiments}, we provide the same
-% experiment with 9 CAD models.
-
-\begin{table*}[!htbp]
-    \footnotesize
-    \begin{center}
-\begin{tabular}{|c|c|r|c|r|}
-\hline
-Methods (AP/MPPE) & before calibration  & time & after calibration \cite{Aubry14} & time \\
-\hline\hline
-HOG\cite{Dalal05}     & 72.3 / 65.0           &  31ms  & 60.4 / 50.2                 & 8.7 sec \\ 
-WHO\cite{Hariharan12} & 82.1 / 85.4           &  3811ms& 84.4 / 83.0                 & 12.4 sec  \\
-WHO-CG                & 81.7 / \textbf{84.9}  &  104ms & 83.7 / 87.3                 & 8.3 sec \\
-WHO-CG-Z              & 54.4 / 65.1           &  103ms & \textbf{92.8} / 86.7        & 8.7 sec  \\
-% NZC-WHO-Z    & 89.10/\textbf{78.64} &    & 91.15/74.79                  &     \\
-NZ-WHO-CG             & \textbf{90.0} / 82.8  &   79ms & 90.3 / \textbf{86.8}        & 8.5 sec   \\
-\hline
-\end{tabular}
-\end{center}
-\caption{Average Precision(AP) and Mean Precision in Pose Estimation (MPPE) \cite{Lopez-Sastre11} variations of WHO on 3DObject Car dataset\cite{Savarese07}.
-WHO refers to standard WHO using the method presented in \cite{Hariharan12}, WHO-CG uses iterative Conjugate Gradient method to generate WHO.
-WHO-CG-Z uses whiten the whole template and zero out textureless region.
-NZ-WHO-CG is the NZ-WHO which whitens only non-zero cells using iterative Conjugate Gradient method.
-The time column indicates the time to generate one template.
-We followed calibration procedure presented in \cite{Aubry14}.}
-\label{tab:who_initializations}
-\end{table*}

### 2014-11-14 experiments.tex
moved who comparison to exp section

@@
 % fine-grained category.
+
+\subsection{Variations of WHO}
+\label{sec:variations}
+To validate our approach, we run an ensemble of NZ-WHO templates as a bank of exemplar detectors and compare its performance with other WHO variants.
+Since WHO variants uses HOG features, they are slower than HOG templates but WHO variants in general performs better than WHO by significant margin.
+However, WHO using Cholesky decomposition with Gaussian Elemination takes the most time yet performs worse than NZ-WHO which is two order of magnitude faster to generate.
+
+We also calibrated the various methods
+
+In the experiment, we compared the performance of HOG, WHO, WHO-CG, WHO-CG-Z and NZ-WHO.
+The WHO refers to standard WHO using the method presented in \cite{Hariharan12}, WHO-CG uses iterative Conjugate Gradient method to generate WHO.
+WHO-CG-Z uses whiten the whole template and zero out textureless region.
+NZ-WHO-CG is the NZ-WHO which whitens only non-zero cells using iterative Conjugate Gradient method.
+The time column indicates the time to generate one template.
+We followed calibration procedure presented in \cite{Aubry14}
+
+The experiment results is on Tab.~\ref{tab:who_initializations}
+We found out that without calibration, NZ-WHO performs the best on object
+detection on 3DObject car dataset \cite{Savarese07}. See Table
+\ref{tab:who_initializations} for detail. In essence, if we use calibration, we
+could achieve better performance but since our goal is to do 2D-3D matching and
+continuous viewpoint estimation using on-the-fly template generation, we did not
+calibrated our templates.
+
+We empirically found out that NZ-WHO performs reasonably well without time
+consuming calibration stage compare to other variational method to generate
+templates. We used 1 CAD model with viewpoints covering 24 azimuths and 4
+elevations. Each template takes approximately 80 milliseconds to generate a
+NZ-WHO template. We also calibrated templates using the method presented in
+\cite{Aubry14}. The calibration learns affine transformation of the detection
+confidence.% Note that in Section \ref{experiments}, we provide the same
+% experiment with 9 CAD models.
+
+\begin{table*}[!htbp]
+    \footnotesize
+    \begin{center}
+\begin{tabular}{|c|c|r|c|r|}
+\hline
+Methods (AP/MPPE) & before calibration  & time & after calibration \cite{Aubry14} & time \\
+\hline\hline
+HOG\cite{Dalal05}     & 72.3 / 65.0           &  31ms  & 60.4 / 50.2                 & 8.7 sec \\ 
+WHO\cite{Hariharan12} & 82.1 / 85.4           &  3811ms& 84.4 / 83.0                 & 12.4 sec  \\
+WHO-CG                & 81.7 / \textbf{84.9}  &  104ms & 83.7 / 87.3                 & 8.3 sec \\
+WHO-CG-Z              & 54.4 / 65.1           &  103ms & \textbf{92.8} / 86.7        & 8.7 sec  \\
+% NZC-WHO-Z    & 89.10/\textbf{78.64} &    & 91.15/74.79                  &     \\
+NZ-WHO-CG             & \textbf{90.0} / 82.8  &   79ms & 90.3 / \textbf{86.8}        & 8.5 sec   \\
+\hline
+\end{tabular}
+\end{center}
+\caption{Average Precision(AP) and Mean Precision in Pose Estimation (MPPE) \cite{Lopez-Sastre11} variations of WHO on 3DObject Car dataset\cite{Savarese07}.
+WHO refers to standard WHO using the method presented in \cite{Hariharan12}, WHO-CG uses iterative Conjugate Gradient method to generate WHO.
+WHO-CG-Z uses whiten the whole template and zero out textureless region.
+NZ-WHO-CG is the NZ-WHO which whitens only non-zero cells using iterative Conjugate Gradient method.
+The time column indicates the time to generate one template.
+We followed calibration procedure presented in \cite{Aubry14}.}
+\label{tab:who_initializations}
+\end{table*}
 

### 2014-11-14 intro.tex
intro and overview added citation

--- 2014-11-14 intro.tex
@@
 level of performance in 2D bounding box
-localization~\cite{pascal12,Felzenszwalb10,Girshick14}, due to their
+localization~\cite{pascal12, Felzenszwalb10, Overfeat, Krizhevsky12, Girshick14}, due to their
 ability to generalize across differences in object appearance,
@@
 implemented as extensions to existing detectors, such as the implicit
-shape models~\cite{}, the constellation model~\cite{}, or the
-deformable part model~\cite{Xiang12,Pepik12,Fidler12,Hejrati14}.
+shape models~\cite{sun10eccv}, the constellation model~\cite{stark10bmvc}, or the
+deformable part model~\cite{Felzenszwalb10, gu10eccv,Xiang12,Pepik12,Fidler12,Hejrati14}.
 

### 2014-11-14 approach.tex

@@
 the condition number of the matrix. \scream{Citation for complexity}.
-
+%
 This makes Conjugate Gradient faster than decomposition for matrices with small condition
@@
 ms when using 250 HOG cells, two orders of magnitude faster than the using
-Cholesky factorization with Gaussian Elemination. We report the real time
-analysis of whitening using decomposition and conjugate gradient methods in
-Fig.~\ref{fig:whotime}.
+Cholesky factorization with Gaussian Elemination.
 
-We compare the speed of each of template generation methods in
-Fig.~\cite{fig:covariancetime_crop} Using naive Cholesky decomposition,
-WHO template takes several seconds. But, if we use iterative Conjugate Gradient method, it only
-takes 100ms. If we use NZ-WHO, we can gain extra speed up since we only whitens non-zero cells.
+We report the real time analysis of whitening using decomposition and
+conjugate gradient methods in Fig.~\ref{fig:whotime}. (a) compares the
+absolute runtime of the different methods while (b) gives the obtained
+speedup. We see that % We compare the speed of each of template generation methods in
+% Fig.~\cite{fig:covariancetime_crop} Using naive Cholesky decomposition,
+WHO template takes several seconds for realistic template sizes of
+several hundred cells, while using the iterative Conjugate Gradient
+method, it only takes 100ms. If we use NZ-WHO, we can gain extra speed
+up since we only whitens non-zero cells.
 
-Also, since the iterative Conjugate Gradient method directly tries to reduce the residual (the norm of $y-Ax$ for $Ax = y$),
-it is more numerically stable than Cholesky decomposition with Gaussian Elemination. We vary the number of cells in a template
-and show that the residual of NZ-WHO is smaller than WHO Fig.~\ref{fig:whoresidual}.
-
+In addition, since the iterative Conjugate Gradient method directly
+tries to reduce the residual (the norm of $y-Ax$ for $Ax = y$), it is
+more numerically stable than Cholesky decomposition with Gaussian
+Elemination. We vary the number of cells in a template and show that
+the residual of NZ-WHO is smaller than WHO Fig.~\ref{fig:whoresidual}.
 % Also, the residual from the Conjugate Gradient method (the norm of $y-Ax$ for $Ax = y$) is smaller than 
@@
 length $m$ filter, naive convolution takes $O(nm)$ time whereas FFT-based
-convolution takes $O\left( (n + m)\log (n+m) \right)$ time. For large $m$, high
-resolution template, we can gain computational advantage.
+convolution takes $O\left( (n + m)\log (n+m) \right)$ time. For large
+$m$ (high resolution templates), we can gain computational advantage.

### 2014-11-14 experiments.tex
started another pass over 6

@@
 In this section, we give an experimental evaluation of our approach,
-highlighting two different aspects.
+highlighting three different aspects.
 
-First, we demonstrate that our method can be used for multi-view
+First, we verify that our NZ-WHO method delivers performance that is
+at least on par with the original WHO formulation~\cite{Hariharan12} in terms of
+accuracy, while at the same time resulting in large computational
+savings (Sect.~\ref{sec:variations}).
+
+Second, we demonstrate that our method can be used for multi-view
 object class detection in isolation. It can be applied in a sliding
@@
 
-Second, we show that our method can be used to complement the
+And third, we show that our method can be used to complement the
 detections provided by an existing object class detector, such
@@
 
-\subsection{Variations of WHO}
+\subsection{WHO Variants}
 \label{sec:variations}
@@
 
-\begin{table*}[!htbp]
+\begin{table}[!htbp]
     \footnotesize
-    \begin{center}
+    \setlength{\tabcolsep}{1pt}
+    \centering
 \begin{tabular}{|c|c|r|c|r|}
 \hline
-Methods (AP/MPPE) & before calibration  & time & after calibration \cite{Aubry14} & time \\
+Methods (AP/MPPE) & before calib.  & time & after calib.~\cite{Aubry14} & time \\
 \hline\hline
@@
 \end{tabular}
-\end{center}
 \caption{Average Precision(AP) and Mean Precision in Pose Estimation (MPPE) \cite{Lopez-Sastre11} variations of WHO on 3DObject Car dataset\cite{Savarese07}.
@@
 \label{tab:who_initializations}
-\end{table*}
+\end{table}
 

### 2014-11-14 experiments.tex
started pass over 3

@@
 \label{sec:variations}
-To validate our approach, we run an ensemble of NZ-WHO templates as a bank of exemplar detectors and compare its performance with other WHO variants.
-Since WHO variants uses HOG features, they are slower than HOG templates but WHO variants in general performs better than WHO by significant margin.
-However, WHO using Cholesky decomposition with Gaussian Elemination takes the most time yet performs worse than NZ-WHO which is two order of magnitude faster to generate.
+To validate our approach, we run an ensemble of NZ-WHO templates as a
+bank of exemplar detectors and compare its performance with other WHO
+variants, notable WHO~\cite{Hariharan12} and the original non-whitened
+HOG~\cite{Dalal05}. In addition, we evaluate WHO-CG and WHO-CG-Z:
+WHO-CG uses iterative Conjugate Gradient method to generate
+WHO. WHO-CG-Z whitens the whole template, but zeros out textureless
+region. NZ-WHO-CG is the NZ-WHO which whitens only non-zero cells using
+iterative Conjugate Gradients  (our method).
 
-We also calibrated the various methods
+Tab.~\ref{tab:who_initializations} gives the correponding results for
+the various methods on a subset of the 3D Object Classes car
+dataset~\cite{Savarese07} (all images corresponding to one particular
+car instance, seen from different viewpoints), reporting 3 quantities:
+detection performance in average precision (AP), pose estimation in mean
+precision in pose estimtation (MPPE), and the respective runtime.
+%
+For all methods, the table gives the results with and without
+calibration, using the calibration method of~\cite{Aubry14}. This
+calibration learns affine transformation of the detection confidence.
+For each method, we generated templates for 1 CAD model exemplar
+rendered from 24 azimuth and 4 elevation angles.
+% Since WHO variants uses HOG features, they are slower than
+% HOG templates but WHO variants in general performs better than WHO by
+% significant margin. However, WHO using Cholesky decomposition with
+% Gaussian Elemination takes the most time yet performs worse than
+% NZ-WHO which is two order of magnitude faster to generate.
 
-In the experiment, we compared the performance of HOG, WHO, WHO-CG, WHO-CG-Z and NZ-WHO.
-The WHO refers to standard WHO using the method presented in \cite{Hariharan12}, WHO-CG uses iterative Conjugate Gradient method to generate WHO.
-WHO-CG-Z uses whiten the whole template and zero out textureless region.
-NZ-WHO-CG is the NZ-WHO which whitens only non-zero cells using iterative Conjugate Gradient method.
-The time column indicates the time to generate one template.
-We followed calibration procedure presented in \cite{Aubry14}
+\paragraph{Results.}
+In Tab.~\ref{tab:who_initializations}, we observe that, on average,
+calibration indeed improves performance in terms of AP, sometimes
+drastically (e.g., from $54.4$ to $92.8$ for WHO-CG-Z), as observed in
+prior work~\cite{Aubry14}. At the same time, calibration is
+computationally expensiv, resulting in runtimes that are two orders of
+magnitudes larger than without calibration. Strikinly, our method
+NZ-WHO-CG achieves the second best AP of $90.0$ while completing in 79
+ms vs. 8.7 s when using calibration.
 
-The experiment results is on Tab.~\ref{tab:who_initializations}
-We found out that without calibration, NZ-WHO performs the best on object
-detection on 3DObject car dataset \cite{Savarese07}. See Table
-\ref{tab:who_initializations} for detail. In essence, if we use calibration, we
-could achieve better performance but since our goal is to do 2D-3D matching and
-continuous viewpoint estimation using on-the-fly template generation, we did not
-calibrated our templates.
-
-We empirically found out that NZ-WHO performs reasonably well without time
-consuming calibration stage compare to other variational method to generate
-templates. We used 1 CAD model with viewpoints covering 24 azimuths and 4
-elevations. Each template takes approximately 80 milliseconds to generate a
-NZ-WHO template. We also calibrated templates using the method presented in
-\cite{Aubry14}. The calibration learns affine transformation of the detection
-confidence.% Note that in Section \ref{experiments}, we provide the same
-% experiment with 9 CAD models.
+% We empirically found out that NZ-WHO performs reasonably well without time
+% consuming calibration stage compare to other variational method to generate
+% templates. We used 1 CAD model with viewpoints covering 24 azimuths and 4
+% elevations. Each template takes approximately 80 milliseconds to generate a
+% NZ-WHO template. We also calibrated templates using the method presented in
+% \cite{Aubry14}. e.% Note that in Section \ref{experiments}, we provide the same
+% % experiment with 9 CAD models.
 
@@
 % NZC-WHO-Z    & 89.10/\textbf{78.64} &    & 91.15/74.79                  &     \\
-NZ-WHO-CG             & \textbf{90.0} / 82.8  &   79ms & 90.3 / \textbf{86.8}        & 8.5 sec   \\
+NZ-WHO-CG {\em (ours)}  & \textbf{90.0} / 82.8  &   79ms & 90.3 / \textbf{86.8}        & 8.5 sec   \\
 \hline
@@
 \begin{tabular}{cc}
-  \hline
+%  \hline
   \includegraphics[width=0.49\linewidth]{car_cnn4_crop.png} &   
@@
   \includegraphics[width=0.49\linewidth]{car_cnn24_crop.png} \\   
-  \hline
+%  \hline
 \end{tabular}

### 2014-11-14 approach.tex
in progress third pass sec.4

@@
 NZ-WHO removes these artifacts so that the background has no effect on the
-template response. Given HOG features $x$, we create a new vector $x'$ which
-contains only the non-zero elements of $x$. We select the same elements of
+template response. Let $T$ be the feature extraction transformation and $p$ be
+the rendering setting (see Sect.~\ref{sec:fine}). Given HOG features $x=T(I_r)$
+from rendering image $I_r$, we create a new vector $x'$ which
+contains only the non-zero elements of $x$. We select the corresponding elements of
 $\mu$ to produce $\mu'$, while the autocovariance lookup is only performed for
@@
 rendering setting.
-%
+
 It originates from the insight that an iterative

### 2014-11-14 experiments.tex

@@
 highlighting three different aspects.
-
+%
 First, we verify that our NZ-WHO method delivers performance that is
@@
 savings (Sect.~\ref{sec:variations}).
-
+%
 Second, we demonstrate that our method can be used for multi-view
@@
 case (Sect.~\ref{sec:exp_iso}).
-
+%
 And third, we show that our method can be used to complement the
@@
 we show a considerable performance improvement compared to previous
-work in the task of joint object class detection and viewpoint
+work in the task of joint object class detection and VP
 estimation (Sect.~\ref{sec:exp_enrich}).
@@
   \end{tabular}
-\caption{Average Precision(AP) and Mean Precision in Pose Estimation (MPPE) \cite{Lopez-Sastre11} variations of WHO on 3DObject Car dataset\cite{Savarese07}.
-WHO refers to standard WHO using the method presented in \cite{Hariharan12}, WHO-CG uses iterative Conjugate Gradient method to generate WHO.
-WHO-CG-Z uses whiten the whole template and zero out textureless region.
-NZ-WHO-CG is the NZ-WHO which whitens only non-zero cells using iterative Conjugate Gradient method.
-The time column indicates the time to generate one template.
-We followed calibration procedure presented in \cite{Aubry14}.}
+  \caption{Average Precision(AP), Mean Precision in Pose Estimation
+    (MPPE)~\cite{Lopez-Sastre11}, and runtime for variations of WHO on
+    3D Object Classes cars~\cite{Savarese07}. Please see text for
+    details.}
+  % WHO refers to standard WHO using the
+  % method presented in \cite{Hariharan12}, WHO-CG uses iterative
+  % Conjugate Gradient method to generate WHO. WHO-CG-Z uses whiten the
+  % whole template and zero out textureless region. NZ-WHO-CG is the
+  % NZ-WHO which whitens only non-zero cells using iterative Conjugate
+  % Gradient method. The time column indicates the time to generate one
+  % template. We followed calibration procedure presented in \cite{Aubry14}.}
   \label{tab:who_initializations}
@@
   \end{center}
-  \caption{Average Precision(AP) and Mean Precision in Pose Estimation (MPPE) on 3DObject dataset car category.
-Our method produces high quality 2D-3D matching yet performs on par with state-of-the art detectors.}
+  \caption{Average Precision (AP) and Mean Precision in Pose
+    Estimation (MPPE) on 3D Object Classes~\cite{Savarese07} cars.}% Our method produces high quality 2D-3D matching yet performs on par with state-of-the art detectors.}
   \label{tab:3dobject}
@@
 \begin{tabular}{cc}
-  \includegraphics[width=0.45\linewidth]{car_3dobject/7.png} &   
-  \includegraphics[width=0.45\linewidth]{car_3dobject/8.png}\\ [-15pt]
+  \includegraphics[width=0.35\linewidth]{car_3dobject/7.png} &   
+  \includegraphics[width=0.35\linewidth]{car_3dobject/8.png}\\ [-15pt]
 %   (a) & (b) \\[0pt]
-  \includegraphics[width=0.45\linewidth]{car_3dobject/11.png} &   
-  \includegraphics[width=0.45\linewidth]{car_3dobject/12.png}\\ [-5pt]
+  \includegraphics[width=0.35\linewidth]{car_3dobject/11.png} &   
+  \includegraphics[width=0.35\linewidth]{car_3dobject/12.png}\\ [-5pt]
 %  (c) & (d) \\[0pt]
@@
 \end{center}
-\caption{Detection results on 3D Object Classes~\cite{Savarese07}. Original image (left) and detection result overlaid on top with a bounding box and corresponding confidence score(right)}
+\caption{Detection results on 3D Object
+  Classes~\cite{Savarese07}. Original image (left) and detection
+  result overlaid on top (right).}% with a bounding box and corresponding confidence score (right).}
   \label{fig:3dobject}
@@
    \includegraphics[width=0.33\linewidth]{tuning/3.png} \\[-5pt]
-   (a) & (b) & (c)\\
+%   (a) & (b) & (c)\\
    \includegraphics[width=0.33\linewidth]{tuning/4.png} &
@@
    \includegraphics[width=0.33\linewidth]{tuning/6.png} \\[-5pt]
-   (d) & (e) & (f)\\
+%   (d) & (e) & (f)\\
    \end{tabular}
@@
 
-\begin{figure*}[h]
+\begin{figure*}[t]
 \setlength\tabcolsep{1pt}
@@
 \begin{tabular}{|c|c|c|c|c|}
-   \hline
+%   \hline
   \includegraphics[width=0.24\textwidth]{car_cnn/1a.png} &   
@@
   \includegraphics[width=0.24\textwidth]{car_cnn/1d.png}  \\  
-   \hline
+%   \hline
   \includegraphics[width=0.24\textwidth]{car_cnn/2a.png} &   
@@
   \includegraphics[width=0.24\textwidth]{car_cnn/2e.png}  \\  
-   \hline
+%   \hline
   \includegraphics[width=0.24\textwidth]{car_cnn/4a.png} &   
@@
 %   \includegraphics[width=0.24\textwidth]{bicycle_cnn/3d.png}  \\
-  \hline
-  \includegraphics[width=0.24\textwidth]{bicycle_cnn/7a.png} &   
-  \includegraphics[width=0.24\textwidth]{bicycle_cnn/7b.png} &   
-  &\\
-  \hline
+%
+% sorry no space
+%  \hline
+%  \includegraphics[width=0.24\textwidth]{bicycle_cnn/7a.png} &   
+%  \includegraphics[width=0.24\textwidth]{bicycle_cnn/7b.png} &   
+%  &\\
+%  \hline
   \includegraphics[width=0.24\textwidth]{bicycle_cnn/4a.png} &   
@@
   \includegraphics[width=0.24\textwidth]{bicycle_cnn/4d.png}  \\
-  \hline
+%  \hline
   CNN Proposals & \multicolumn{3}{|c|}{Our matching results on proposal bounding boxes} \\
-  \hline
+%  \hline
 \end{tabular}
-\caption{Example enriched bounding boxes.
-Given R-CNN\cite{Girshick14} detection bounding boxes, our method predicted 2D-3D matching reasonably.
-On the first column, R-CNN detection bounding boxes overlaid.
-From the second to the last columns, output of our method given a R-CNN box.
-Blue boxes are R-CNN output and purple boxes are the tightest bounding box enclosing predicted CAD model}
+\caption{Example enriched bounding boxes. Given R-CNN\cite{Girshick14}
+  detection bounding boxes, our method predicted 2D-3D matching
+  reasonably. On the first column, R-CNN detection bounding boxes
+  overlaid. From the second to the last columns, output of our method
+  given a R-CNN box. Blue boxes are R-CNN output and purple boxes are
+  the tightest bounding box enclosing predicted CAD model.}
   \label{fig:pascal12cnn}
 \end{figure*}
-\begin{table*}[!htbp]
+%
+\begin{table*}[t]
     \footnotesize
@@
 \end{center}
-\caption{Average Precision(AP) and Average Viewpoint Precision(AVP) on PASCAL3D+~\cite{Xiang14}.
-For combined method (* + Ours), we use bounding boxes from * and augment viewpoint using our method.
-R-CNN and run our method to produce 2D-3D matching.
-If our method fails to give viewpoint, it predicts the viewpoint to be 0.
-Note that our method gives high quality metadata such as continuous 3D viewpoint, CAD model (rendering depth) and fine-grained category, whereas base-line methods gives 1D discrete azimuths.
-Our R-CNN was not an optimized version so the detection AP is lower than the state-of-the-art R-CNN performance}
+\caption{Average Precision(AP) and Average Viewpoint Precision (AVP) on
+  PASCAL3D+~\cite{Xiang14}. For combined methods (* + Ours), we use
+  bounding boxes from * and augment viewpoint using our method.}
+  % R-CNN
+  % and run our method to produce 2D-3D matching. If our method fails to
+  % give viewpoint, it predicts the viewpoint to be 0. Note that our
+  % method gives high quality metadata such as continuous 3D viewpoint,
+  % CAD model (rendering depth) and fine-grained category, whereas
+  % base-line methods gives 1D discrete azimuths. Our R-CNN was not an
+  % optimized version so the detection AP is lower than the
+  % state-of-the-art R-CNN performance}
 \label{tab:pascal12}
@@
   and viewpoint confusion table on PASCAL 12 car validation set using
-  R-CNN + Ours (full).
-From the top left, 4 views, 8 views, 16 views and 24 views.
-Since our method only augment the object detection, the AP remains the same for all cases.
-As we increase the viewpoint estimation, the AVP decreases.
-Note that since we estimate null viewpoint if our method fails to find match, there are more 0 viewpoint predictions (top row of confusion matrices) }
+  R-CNN + Ours (full). From the top left, 4 views, 8 views, 16 views
+  and 24 views.}
+ % Since our method only augment the object detection,
+ %  the AP remains the same for all cases. As we increase the viewpoint
+ %  estimation, the AVP decreases. Note that since we estimate null
+ %  viewpoint if our method fails to find match, there are more 0
+ %  viewpoint predictions (top row of confusion matrices) }
   \label{fig:car_cnn_ap}
@@
 \end{tabular}
-\caption{Stability of our method for overlapping R-CNN detection \cite{Girshick14}.
-Blue box is the R-CNN detection that is feed into the system as initial detection.
-Purple box and overlaid rendering is the final output of the system.
-Note that for various overlapping bounding boxes, our system accurately estimated the reasonable result}
+\caption{Robustness of our method for against irregular and truncated
+  R-CNN detection proposals (cyan).}
+  % \cite{Girshick14}. Blue box is the R-CNN detection that is feed into
+  % the system as initial detection. Purple box and overlaid rendering
+  % is the final output of the system. Note that for various overlapping
+  % bounding boxes, our system accurately estimated the reasonable
+  % result}
   \label{fig:stability}

### 2014-11-14 conclusion.tex
first draft conclusion

In this paper, we have proposed a method for generating 3D CAD model
exemplar detector templates on-the-fly, based on a novel variant of
WHO features called NZ-WHO. As it circumvents the need for
calibration, it is computationally efficient, allowing it to be run in
an on-the-fly setting. As a result, we can use our method to enrich
existing object class detections with additional information such as
precise 3D pose and 3D CAD model exemplar.

### 2014-11-14 approach.tex

@@
 In this section, we describe our approach to generating 3D
-exemplare-based templates on-the-fly. It is based on 3D CAD model
+exemplar-based templates on-the-fly. It is based on 3D CAD model
 rendering (Sect.~\ref{sec:rendering}) followed by feature extraction
@@
 \label{sec:rendering}
-We used a public rendering engine to create realistic rendering and
-depth. We used CAD models that contain color, texture and material information such as
-transparency and reflectance to make the rendering as much realistic
-as possible to simulate the natural image statistics. The example rendering is
-in Fig. \ref{fig:rendering}. We also extracted depth information as well while
-rendering to use in the reconstruction.
-
-We used a collection of CAD models to make exemplar renderings of CAD models and for viewpoints. The
-CAD models are cached so that when we fine-tune 2D-3D matching, so it can be rendered instantaneously.
-We made the renderings to change focal length and yaw, pitch, roll so that we can fine tune the matching
-continuously.
+We made rendering engine that uses color, texture and material information in
+CAD models to generate realistic rendering to simulate the natural image
+statistics. The example rendering is
+in Fig. \ref{fig:rendering}.
 
@@
   \end{center}
-  \caption{Example rendering and depth made by our renderer}
+  \caption{An example rendering and depth image made by our renderer}
   \label{fig:rendering}
@@
 Our technique for rendering and training template detectors on-the-fly
-is drawing from recent work, which we review briefly in this section.
-%
-Recently, Hariharan \etal. introduced Whitened Histograms of Orientations (WHO)
-\cite{Hariharan12}, which uses statistics from natural images to whiten HOG
+is drawing from recent work. Hariharan \etal. introduced Whitened Histograms of Orientations (WHO)
+\cite{Hariharan12}, which uses feature statistics from natural images to whiten HOG
 templates, making them more discriminative. Whitening is a common signal
 processing operation for decorrelating a set of random variables
-\cite{Martinsson05, Belouchrani00}. More formally, suppose that we have a
-$k$-dimensional random variable $X \in \mathcal{R}^k$ with $Cov(X)=\Sigma$. By
-whitening the signal,
-\begin{equation}
-\tilde{X}=\Sigma^{-\frac{1}{2}}(X - E[X]) \label{eq:whitening},
-\end{equation}
-we remove 2nd order correlation between all features. Since collecting covariance matrix for every template shape
- is expensive, \cite{Hariharan12} proposed easy way to synthesize
-covariance $\Sigma$ from autocovariance $\Gamma$ and we followed their
-method to generate $\Sigma$.
+\cite{Martinsson05, Belouchrani00}. By whitening features, we remove 2nd order
+correlation between all features.
+
+% More formally, suppose that we have a
+% $k$-dimensional random variable $X \in \mathcal{R}^k$ with $Cov(X)=\Sigma$. By
+% whitening the signal,
+% \begin{equation}
+% \tilde{X}=\Sigma^{-\frac{1}{2}}(X - E[X]) \label{eq:whitening},
+% \end{equation}
+
+% Since collecting covariance matrix for every template shape
+%  is expensive, \cite{Hariharan12} proposed easy way to synthesize
+% covariance $\Sigma$ from autocovariance $\Gamma$ and we followed their
+% method to generate $\Sigma$.
 

### 2014-11-14 mcmc.tex
redstuff

@@
 NZ-WHO template $w(p)$ with image feautures $T_s(\mathcal{I})$ for all scale $s$, as defined
-in Sect.~\ref{}. \scream{chris: I'll add this to technical part}
+in Sect.~\ref{sec:nzwho}.
 
@@
 index $m$. For (i) and (ii), we use Gaussian proposal distributions, and a uniform
-distribution over model changes for (iii). \scream{For scale and translation, we
+distribution over model changes for (iii). For scale and translation, we
 implicitly compute all possible translation and scale by convolving $w(q)$ to
-HOG pyramid.}
+HOG pyramid.
 \begin{align}
@@
 the sample with the highest probability as our approximate estimate of
-the MAP solution. \scream{We set $\sigma_v = 5$ degree and $\sigma_f = 1$ and
-$c = 0.1$ for all experiments.}
+the MAP solution. We set $\sigma_v = 5$ degree and $\sigma_f = 1$ and
+$c = 0.1$ for all experiments.
 

### 2014-11-14 intro.tex
intro spell check

@@
 lighting, and viewpoint. While this generalization
-ability of these methods is benefitial for robustness, it also limits
+ability of these methods is beneficial for robustness, it also limits
 the level of detail that these detectors can deliver as an output.
@@
 collection of 3D exemplar models, which they render from a
-large number of viewpoints. The resulting artifial images are then
+large number of viewpoints. The resulting artificial images are then
 used to train exemplar models that can be matched to a real-world
@@
 replacing the standard SVM with an LDA classifier
-(E-LDA)~\cite{Hariharan12}. As a result, it is feasible to train
+(E-LDA)~\cite{Hariharan12}, resulting in a whitened feature
+representation, termed WHO. As a result, it is feasible to train
 hundreds of thousands of mid-level patch detectors for
@@
 %
-Unfortunately, the performance of E-LDA relies crucially on an
+Unfortunately, the performance of WHO relies crucially on an
 additional calibration step that equalizes the detection scores of
@@
 validation set, it constitutes the major computational bottleneck of
-E-LDA, limiting its scalability.
+WHO, limiting its scalability.
 
@@
 exemplar CAD models to real-world images that circumvents the need for
-calibration, and greatly enhances the scalability of E-LDA. As a
+calibration, and greatly enhances the scalability of WHO. As a
 result, we can render novel views and train corresponding exemplar
@@
 by-product, we can formulate the alignment problem as a parameter
-search in a continuous pose space, consisting of yaw, pitch and roll, resulting in truely continuous pose estimates, which
+search in a continuous pose space, consisting of yaw, pitch and roll, resulting in truly continuous pose estimates, which
 we implement using MCMC sampling.
@@
 rendered 3D CAD data {\em on the fly}, enabled by a novel variant of
-E-LDA, and making efficient use of the specific characteristics of
-rendered images. To our knowledge, our method constitutes the first
-attempt to simultaneously render and train exemplar detectors on the
-fly.
+WHO, termed NZ-WHO, and making efficient use of the specific
+characteristics of rendered images. To our knowledge, our method
+constitutes the first attempt to simultaneously render and train
+exemplar detectors on the fly.
 % In our paper, we present Non-Zero Whiten Histograms of Orientations

### 2014-11-14 experiments.tex
spellcheck exp

@@
 
-Tab.~\ref{tab:who_initializations} gives the correponding results for
+Tab.~\ref{tab:who_initializations} gives the corresponding results for
 the various methods on a subset of the 3D Object Classes car
@@
 detection performance in average precision (AP), pose estimation in mean
-precision in pose estimtation (MPPE), and the respective runtime.
+precision in pose estimation (MPPE), and the respective runtime.
 %
@@
 prior work~\cite{Aubry14}. At the same time, calibration is
-computationally expensiv, resulting in runtimes that are two orders of
-magnitudes larger than without calibration. Strikinly, our method
+computationally expensive, resulting in runtimes that are two orders of
+magnitudes larger than without calibration. Strikingly, our method
 NZ-WHO-CG achieves the second best AP of $90.0$ while completing in 79
@@
 isolation, for the task of object class detection and viewpoint
-estimation, on the 3D Object Classes datset~\cite{Savarese07}, for the
+estimation, on the 3D Object Classes dataset~\cite{Savarese07}, for the
 categories {\em car} and {\em bicycle}.
@@
 using $9$ different CAD models and a total of \scream{} different
-viewpoints, using $X$ different evelation angles, $X$ azimuth angles,
+viewpoints, using $X$ different elevation angles, $X$ azimuth angles,
 and $X$ focal lengths. We run the entire ensemble exhaustively over
@@
 
-To show such ability, we evaluat our method on the PASCAL3D+
+To show such ability, we evaluate our method on the PASCAL3D+
 dataset~\cite{Xiang14}. This dataset augments PASCAL 2012 images with
@@
 %
-In order to accomodate this variability, we add a considerable context
+In order to accommodate this variability, we add a considerable context
 region around the proposed bounding boxes before running our method.
@@
 \end{tabular}
-\caption{Robustness of our method for against irregular and truncated
+\caption{Robustness of our method against irregular and truncated
   R-CNN detection proposals (cyan).}

### 2014-11-14 approach.tex
redstuff
spellcheck exp
spell check approach

@@
   \end{center}
-  \caption{An example rendering and depth image made by our renderer}
+  \caption{An example rendering and depth image from renderer.}
   \label{fig:rendering}
@@
 are symmetric and positive semidefinite to solve the system via the Cholesky
-decomposition with Gaussian Elemination, which requires $O(n^3)$ time \scream{Citation for complexity}.
+decomposition with Gaussian Elimination, which requires $O(n^3)$ time \scream{Citation for complexity}.
 
@@
 positive definite systems which runs in $O(n^2\kappa)$ time, where $\kappa$ is
-the condition number of the matrix. \scream{Citation for complexity}.
+the condition number of the matrix. \cite{Shewchuk94}.
 %
@@
 ms when using 250 HOG cells, two orders of magnitude faster than the using
-Cholesky factorization with Gaussian Elemination.
+Cholesky factorization with Gaussian Elimination.
 
@@
 more numerically stable than Cholesky decomposition with Gaussian
-Elemination. We vary the number of cells in a template and show that
+Elimination. We vary the number of cells in a template and show that
 the residual of NZ-WHO is smaller than WHO Fig.~\ref{fig:whoresidual}.

### 2014-11-14 approach.tex
red thing

--- 2014-11-14 approach.tex
@@
 are symmetric and positive semidefinite to solve the system via the Cholesky
-decomposition with Gaussian Elemination, which requires $O(n^3)$ time \scream{Citation for complexity}.
+decomposition with Gaussian Elemination, which requires $O(n^3)$ time.
 

### 2014-11-14 experiments.tex
red thing

--- 2014-11-14 experiments.tex
@@
 
-To that end, we create an ensemble of NZ-WHO templates (Sect.~\ref{})
-using $9$ different CAD models and a total of \scream{} different
-viewpoints, using $X$ different evelation angles, $X$ azimuth angles,
-and $X$ focal lengths. We run the entire ensemble exhaustively over
+To that end, we create an ensemble of NZ-WHO templates (Sect.~\ref{sec:approach})
+using $9$ different CAD models and a total of 192 different
+viewpoints, using 4 different evelation angles, 24 azimuth angles,
+and 2 focal lengths. We run the entire ensemble exhaustively over
 each test image, in a sliding window fashion.
@@
 For both cases, we compare the performance of a discrete incarnation
-of our method (Sect.~\ref{}) and our full model, including the
-fine-tuning based on MCMC~\cite{Sect.~\ref{}}
+of our method (Sect.~\ref{sec:approach}) and our full model, including the
+fine-tuning based on MCMC~\cite{Sect.~\ref{sec:tuning}}
 
@@
  More qualitative results are part of
-supplemental material~\scream{}
+supplemental material
 
@@
 \centering
-\begin{tabular}{|c|c|c|c|c|}
-%   \hline
+\begin{tabular}{|ccccc|}
+   \hline
   \includegraphics[width=0.24\textwidth]{car_cnn/1a.png} &   
@@
   \includegraphics[width=0.24\textwidth]{bicycle_cnn/4d.png}  \\
-%  \hline
+  \hline
   CNN Proposals & \multicolumn{3}{|c|}{Our matching results on proposal bounding boxes} \\
-%  \hline
+  \hline
 \end{tabular}

### 2014-11-14 approach.tex
teaser fig caption

--- 2014-11-14 approach.tex
@@
   \end{center}
-  \caption{(a) Realtime analysis of whitening.
-HOG means feature extraction time, WHO-Chol uses method of \cite{Hariharan12} and WHO-CG uses iterative Conjugate Gradient, and NZ-WHO-CG uses only non-zero cells and use Conjugate Gradient.
-(b) final speed of using NZ-WHO compare to WHO}
+  \caption{(a) Runtime analysis of whitening. HOG means feature
+    extraction time, WHO-Chol uses ~\cite{Hariharan12} and
+    WHO-CG uses iterative Conjugate Gradient. NZ-WHO-CG uses only
+    non-zero cells and Conjugate Gradient. (b) final speedup
+    of NZ-WHO vs. WHO.}
   \label{fig:whotime}

### 2014-11-14 approach.tex

--- 2014-11-14 approach.tex
@@
 are symmetric and positive semidefinite to solve the system via the Cholesky
-decomposition with Gaussian Elimination, which requires $O(n^3)$ time \scream{Citation for complexity}.
+decomposition with Gaussian Elemination, which requires $O(n^3)$ time.
 

### 2014-11-14 experiments.tex

--- 2014-11-14 experiments.tex
@@
 
-To that end, we create an ensemble of NZ-WHO templates (Sect.~\ref{})
-using $9$ different CAD models and a total of \scream{} different
-viewpoints, using $X$ different elevation angles, $X$ azimuth angles,
-and $X$ focal lengths. We run the entire ensemble exhaustively over
+To that end, we create an ensemble of NZ-WHO templates (Sect.~\ref{sec:approach})
+using $9$ different CAD models and a total of 192 different
+viewpoints, using 4 different evelation angles, 24 azimuth angles,
+and 2 focal lengths. We run the entire ensemble exhaustively over
 each test image, in a sliding window fashion.

### 2014-11-14 intro.tex

@@
   % (b)
-  \caption{Using a bank of CAD models, we generate NZ-WHO templates which can be used to either detect objects directly or initialize pose of an object in the bounding box from other detectors.
-Once initialization is given, we use NZ-WHO to propose and validate plausible pose on-the-fly and further tune the translation, 3D viewpoint and focal length continuously.}
+  \caption{Using a database of 3D CAD models, we generate NZ-WHO
+    templates which can be used to either detect objects directly or
+    enrich the output of an existing detector with high-quality,
+    continuous pose and 3D CAD model exemplar.}
+    % initialize pose of an object in the bounding box from other
+    % detectors. Once initialization is given, we use NZ-WHO to propose
+    % and validate plausible pose on-the-fly and
+    % further tune the translation, 3D viewpoint and focal length continuously.}
   % \vspace{-1em}

### 2014-11-14 egpaper_final.tex
first draft conclusion
spellcheck exp
added estimation on the title

@@
 %%%%%%%%% TITLE
-\title{Enriching Object Detection with 2D-3D Registration and Continuous Viewpoint}
+\title{Enriching Object Detection with 2D-3D Registration and Continuous Viewpoint Estimation}
 %\title{Enrich Object Detection : 2D-3D registration and continuous viewpoint estimation}
@@
 focal length. We provide an efficient GPU implementation of our algorithm, and
-we validate its performance on 3DObject dataset and PASCAL 2012 dataset.
+we validate its performance on 3D Object Classes and PASCAL3D+ datasets.
 
@@
 
-\section{Pipeline}
+\section{On-the-Fly Template Generation}
 \label{sec:approach}
@@
 \section{Conclusion}
+\label{conclusion}
+\input{conclusion}
 

### 2014-11-14 approach.tex
added back

@@
 \label{sec:rendering}
-We made rendering engine that uses color, texture and material information in
-CAD models to generate realistic rendering to simulate the natural image
-statistics. The example rendering is
-in Fig. \ref{fig:rendering}.
+
+We used a public rendering engine to create realistic rendering and
+depth. We used CAD models that contain color, texture and material information such as
+transparency and reflectance to make the rendering as much realistic
+as possible to simulate the natural image statistics. The example rendering is
+in Fig. \ref{fig:rendering}. We also extracted depth information as well while
+rendering to use in the reconstruction.
+
+We used a collection of CAD models to make exemplar renderings of CAD models and for viewpoints. The
+CAD models are cached so that when we fine-tune 2D-3D matching, so it can be rendered instantaneously.
+We made the renderings to change focal length and yaw, pitch, roll so that we can fine tune the matching
+continuously.
 
@@
 processing operation for decorrelating a set of random variables
-\cite{Martinsson05, Belouchrani00}. By whitening features, we remove 2nd order
-correlation between all features.
+
+\cite{Martinsson05, Belouchrani00}. More formally, suppose that we have a
+$k$-dimensional random variable $X \in \mathcal{R}^k$ with $Cov(X)=\Sigma$. By
+whitening the signal,
+\begin{equation}
+\tilde{X}=\Sigma^{-\frac{1}{2}}(X - E[X]) \label{eq:whitening},
+\end{equation}
+we remove 2nd order correlation between all features. Since collecting covariance matrix for every template shape
+ is expensive, \cite{Hariharan12} proposed easy way to synthesize
+covariance $\Sigma$ from autocovariance $\Gamma$ and we followed their
+method to generate $\Sigma$.
 

### 2014-11-14 conclusion.tex
intro spell check
red thing

@@
-In this paper, we have proposed a method for generating 3D CAD model
-exemplar detector templates on-the-fly, based on a novel variant of
-WHO features called NZ-WHO. As it circumvents the need for
-calibration, it is computationally efficient, allowing it to be run in
+We have proposed a method for generating 3D CAD model
+exemplar templates on-the-fly, based on a novel variant of
+WHO features (NZ-WHO). It circumvents the need for
+calibration, is computationally efficient, and allows it to be run in
 an on-the-fly setting. As a result, we can use our method to enrich
-existing object class detections with additional information such as
-precise 3D pose and 3D CAD model exemplar.
+existing object detections with additional information such as
+precise 3D pose and 3D CAD model exemplar. Combined with an R-CNN
+detector, we achieve state-of-the-art
+results in joint detection and VP estimation.

### 2014-11-14 egpaper_final.tex
8 pages
line breaker in title
number

@@
 
-\def\cvprPaperID{****} % *** Enter the CVPR Paper ID here
+\def\cvprPaperID{2349} % *** Enter the CVPR Paper ID here
 \def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}
@@
 %%%%%%%%% TITLE
-\title{Enriching Object Detection with 2D-3D Registration and Continuous Viewpoint Estimation}
+\title{Enriching Object Detection with 2D-3D Registration\\and Continuous Viewpoint Estimation}
 %\title{Enrich Object Detection : 2D-3D registration and continuous viewpoint estimation}
@@
 \label{conclusion}
+\vspace{-.2cm}
 \input{conclusion}

### 2014-11-14 experiments.tex
8 pages
number

@@
 model (ALM~\cite{Xiang12}), and the
-DPM-VOC+VP~\cite{Pepik12}. Fig.~\ref{fig:3dobject} gives corresponding
+DPM-VOC+VP~\cite{Pepik12}. Fig.~\ref{fig:3dobject} gives
 qualitative results.
@@
  \end{center}
- \caption{Effect of fine tuning. (left) original image, (middle) initial detection, (right) continuous fine tuning}
+ \caption{Effect of fine tuning. (left) original image, (middle) initial detection, (right) continuous fine tuning using Single-Component Metropolis Hastings}
  \label{fig:tuning}
@@
 \end{tabular}
-\caption{Average Precision (AP) and Average Viewpoint Precision (AVP)
+\caption{Average Precision (AP)(red) and Average Viewpoint Precision (AVP)(green)
   and viewpoint confusion table on PASCAL 12 car validation set using

### 2014-11-14 intro.tex
spell check
number

@@
 result, we can render novel views and train corresponding exemplar
-models {\em on the fly}, without the need for offline processing. As a
+models {\em on the fly}, without the need for offline processing and we call thses NZ-WHO templates \ref{fig:front}. As a
 by-product, we can formulate the alignment problem as a parameter
@@
 % (yaw, roll, pitch) and focal length.
-
+%
 Second, we show to enrich the output of an existing object class
@@
 estimates of 3D continuous pose and a 3D CAD model exemplar.
-
+%
 And third, we give an in-depth experimental study that demonstrates

### 2014-11-14 intro.tex
typo and capion4

--- 2014-11-14 intro.tex
@@
 result, we can render novel views and train corresponding exemplar
-models {\em on the fly}, without the need for offline processing. As a
+models {\em on the fly}, without the need for offline processing and we call these NZ-WHO templates \ref{fig:front}. As a
 by-product, we can formulate the alignment problem as a parameter

### 2014-11-18 egpaper_supp.tex
supplementary

\documentclass[10pt,twocolumn,letterpaper]{article}

\usepackage{cvpr}
\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{caption}
\usepackage{verbatim}
\usepackage{subcaption}
\usepackage{algorithm2e}
\usepackage{rotating}
\usepackage[space]{grffile}
\usepackage[font=small,skip=0pt]{caption}
%\DeclareMathOperator{\Tr}{Tr}
% Include other packages here, before hyperref.

% If you comment hyperref and then uncomment it, you should delete
% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
% run, let it finish, and you should be clear).
\usepackage[breaklinks=true,bookmarks=false]{hyperref}
\graphicspath{ {figures/} }
% \cvprfinalcopy % *** Uncomment this line for the final submission

\def\cvprPaperID{2349} % *** Enter the CVPR Paper ID here
\def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}

% custom commands
\newcommand{\scream}[1]{{\color{red} \bf *** #1 ***}}

% Pages are numbered in submission mode, and unnumbered in camera-ready
%\ifcvprfinal\pagestyle{empty}\fi
\setcounter{page}{1}
\begin{document}

%%%%%%%%% TITLE
\title{Supplementary Material for the Paper ``Enriching Object Detection with\\2D-3D Registration and Continuous Viewpoint Estimation''}
%\title{Enrich Object Detection : 2D-3D registration and continuous viewpoint estimation}

% \author{First Author\\
% Institution1\\
% Institution1 address\\
% {\tt\small firstauthor@i1.org}
% % For a paper whose authors are all at the same institution,
% % omit the following lines up until the closing ``}''.
% % Additional authors and addresses can be added with ``\and'',
% % just like the second author.
% % To save space, use either the email address or home page, not both
% \and
% Second Author\\
% Institution2\\
% First line of institution2 address\\
% {\tt\small secondauthor@i2.org}
% }

\maketitle
%\thispagestyle{empty}

%%%%%%%%% BODY TEXT
We present qualitative results in the supplementary material for our paper ``Enriching Object Detection with 2D-3D Registration and Continuous Viewpoint Estimation''.
% In Sect.~\ref{sec:3dobject}, we present detection result on qualitative results.

\section{3D Object Dataset}
\label{sect:3dobject}
We run our ensemble of NZ-WHO templates as a detector on 3D Object dataset\cite{savarese07} and present detection average precision, average viewpoint precision, viewpoint confusion matrix and mean precision in pose estimation. See Fig.~\ref{fig:3dobject_ap}

\begin{figure}[h]
  \centering
  \includegraphics[width=0.99\linewidth]{supp/car_ap_3dobject_tight.png}\\
  \vspace{-5pt}
  (a) Car\\
  \includegraphics[width=0.99\linewidth]{supp/bicycle_ap_3dobject_tight.png}\\
  \vspace{-5pt}
  (b) Bicycle
\caption{Detection and pose estimation on 3D Object dataset car category. (left) Average Precision (AP) and Average Viewpoint Precision (AVP) and (right) Viewpoint confusion table and MPPE, Viewpoint index 1 is front, 2 is front-right, 5 is back and 8 is front-left. Most of the error in viewpoint estimation come from frontal and back views}% with a bounding box and corresponding confidence score (right).}
  \label{fig:3dobject_ap}
\end{figure}

More qualitative results are on the Fig.~\ref{fig:3dobject_fig}. The each of the template in the ensemble of NZ-WHO templates has a corresponding rendering and a CAD model. These can be transferred as a metadata and overlay the rendering on top of the detection.

\begin{figure*}[h]
\setlength\tabcolsep{1pt}
\centering
\begin{tabular}{|c|c|}
  \hline
  \includegraphics[width=0.40\linewidth]{supp/car1.png} &
  \includegraphics[width=0.40\linewidth]{supp/bicycle1.png} \\
  \includegraphics[width=0.40\linewidth]{supp/car23.png} &
  \includegraphics[width=0.40\linewidth]{supp/bicycle3.png} \\
  \includegraphics[width=0.40\linewidth]{supp/car26.png} &
  \includegraphics[width=0.40\linewidth]{supp/bicycle4.png} \\
  \includegraphics[width=0.40\linewidth]{supp/car29.png} & 
  \includegraphics[width=0.40\linewidth]{supp/bicycle5.png} \\
  \includegraphics[width=0.40\linewidth]{supp/car10.png} &
  \includegraphics[width=0.40\linewidth]{supp/bicycle9.png} \\
  \includegraphics[width=0.40\linewidth]{supp/car13.png} &
  \includegraphics[width=0.40\linewidth]{supp/bicycle13.png} \\
  \includegraphics[width=0.40\linewidth]{supp/car15.png} &
  \includegraphics[width=0.40\linewidth]{supp/bicycle11.png} \\
  \includegraphics[width=0.40\linewidth]{supp/car8.png} &
  \includegraphics[width=0.40\linewidth]{supp/bicycle12.png} \\
  \includegraphics[width=0.40\linewidth]{supp/car20.png} & 
  \includegraphics[width=0.40\linewidth]{supp/bicycle15.png} \\
  \hline
  Car & Bicycle \\
  \hline
  \end{tabular}
\caption{Detection results on 3D Object dataset car and bike classes. In each column, original image (left) and detection result overlaid on top (right).}% with a bounding box and corresponding confidence score (right).}
  \label{fig:3dobject_fig}
\end{figure*}

\clearpage
\clearpage
{\small
\bibliographystyle{ieee}
\bibliography{egbib}
}

\end{document}

### 2014-11-18 approach.tex
typo and capion4
minor change

@@
 are symmetric and positive semidefinite to solve the system via the Cholesky
-decomposition with Gaussian Elemination, which requires $O(n^3)$ time.
+decomposition with Gaussian Elimination, which requires $O(n^3)$ time.
 
@@
 
-The covariance matrix for HOG templates is typically ill-conditioned\cite{Hariharan12}, but we
+The covariance matrix for HOG templates is typically
+ill-conditioned\cite{Hariharan12}, but we
 can add a regularization constant to the diagonal to reduce its condition
@@
     extraction time, WHO-Chol uses ~\cite{Hariharan12} and
-    WHO-CG uses iterative Conjugate Gradient. NZ-WHO-CG uses only
+    WHO-CG uses iterative Conjugate Gradient. NZ-WHO-CG (Ours) uses only
     non-zero cells and Conjugate Gradient. (b) final speedup

### 2014-11-18 egpaper_final.tex
minor change

@@
 convolutions. Due to the speed of our template synthesis procedure, we are able
-to perform joint optimization on continuous scale, translation, rotation, and
+to perform joint optimization on scale, translation, continuous rotation, and
 focal length. We provide an efficient GPU implementation of our algorithm, and

### 2014-11-18 egpaper_supp.tex
minor change

@@
 
-More qualitative results are on the Fig.~\ref{fig:3dobject_fig}.
+More qualitative results are on the Fig.~\ref{fig:3dobject_good} and Fig.~\ref{fig:3dobject_bad}.
 The each of the template in the ensemble of NZ-WHO templates has a corresponding rendering and a CAD model.
@@
   \hline
-  \includegraphics[width=0.40\linewidth]{supp/car1.png} &
-  \includegraphics[width=0.40\linewidth]{supp/bicycle1.png} \\
-  \includegraphics[width=0.40\linewidth]{supp/car23.png} &
-  \includegraphics[width=0.40\linewidth]{supp/bicycle3.png} \\
+  \includegraphics[width=0.40\linewidth]{supp/car32.png} &
+  \includegraphics[width=0.40\linewidth]{supp/bicycle17.png} \\
   \includegraphics[width=0.40\linewidth]{supp/car26.png} &
-  \includegraphics[width=0.40\linewidth]{supp/bicycle4.png} \\
+  \includegraphics[width=0.40\linewidth]{supp/bicycle18.png} \\
   \includegraphics[width=0.40\linewidth]{supp/car29.png} & 
-  \includegraphics[width=0.40\linewidth]{supp/bicycle5.png} \\
+  \includegraphics[width=0.40\linewidth]{supp/bicycle13.png} \\
   \includegraphics[width=0.40\linewidth]{supp/car10.png} &
   \includegraphics[width=0.40\linewidth]{supp/bicycle9.png} \\
-  \includegraphics[width=0.40\linewidth]{supp/car13.png} &
-  \includegraphics[width=0.40\linewidth]{supp/bicycle13.png} \\
-  \includegraphics[width=0.40\linewidth]{supp/car15.png} &
+  \includegraphics[width=0.40\linewidth]{supp/car1.png} &
   \includegraphics[width=0.40\linewidth]{supp/bicycle11.png} \\
@@
   \includegraphics[width=0.40\linewidth]{supp/bicycle15.png} \\
+  \includegraphics[width=0.40\linewidth]{supp/car31.png} & 
+  \includegraphics[width=0.40\linewidth]{supp/bicycle10.png} \\
+  \includegraphics[width=0.40\linewidth]{supp/car33.png} & 
+  \includegraphics[width=0.40\linewidth]{supp/bicycle16.png} \\
   \hline
@@
   \end{tabular}
-\caption{Detection results on 3D Object dataset car and bike classes.
+\caption{Successful detection results on 3D Object dataset car and bike classes.
 In each column, original image (left) and detection result overlaid on top (right).}% with a bounding box and corresponding confidence score (right).}
-  \label{fig:3dobject_fig}
+  \label{fig:3dobject_good}
+\end{figure*}
+
+\begin{figure*}[h]
+\setlength\tabcolsep{1pt}
+\centering
+\begin{tabular}{|c|c|}
+  \hline
+  \includegraphics[width=0.40\linewidth]{supp/car13.png} &
+  \includegraphics[width=0.40\linewidth]{supp/bicycle1.png} \\
+  \includegraphics[width=0.40\linewidth]{supp/car30.png} &
+  \includegraphics[width=0.40\linewidth]{supp/bicycle5.png} \\
+  \includegraphics[width=0.40\linewidth]{supp/car18.png} &
+  \includegraphics[width=0.40\linewidth]{supp/bicycle19.png} \\
+  \hline
+  Car & Bicycle \\
+  \hline
+  \end{tabular}
+\caption{Failed pose estimation results on 3D Object dataset car and bike classes.
+In each column, original image (left) and detection result overlaid on top (right).}% with a bounding box and corresponding confidence score (right).}
+  \label{fig:3dobject_bad}
 \end{figure*}

### 2014-11-18 experiments.tex
minor change

@@
 using $9$ different CAD models and a total of 192 different
-viewpoints, using 4 different evelation angles, 24 azimuth angles,
+viewpoints, using 4 different elevation angles, 24 azimuth angles,
 and 2 focal lengths. We run the entire ensemble exhaustively over
@@
     \hline\hline
-    car & \textbf{99.8}/91.7 &  98.4/93.4 & \textbf{99.8}/\textbf{97.5} \\ 
-    bicycle & 93.0/87.4 & 93.0/91.4 & \textbf{98.8}/\textbf{97.5} \\
+    car     & \textbf{99.8} / 91.7 & 98.4 / 93.4 & \textbf{99.8} / \textbf{97.5} \\ 
+    bicycle & 93.0 / 90.9          & 93.0 / 91.4 & \textbf{98.8} / \textbf{97.5} \\
     \hline
@@
 of our method (Sect.~\ref{sec:approach}) and our full model, including the
-fine-tuning based on MCMC~\cite{Sect.~\ref{sec:tuning}}
+fine-tuning based on MCMC (Sect.~\ref{sec:fine}).
 
@@
 in Fig.~\ref{fig:pascal12cnn}, and the effect of fine-tuning is
-visualized in Fig.~\ref{fig:tuning}.
-
- More qualitative results are part of
+visualized in Fig.~\ref{fig:tuning}. More qualitative results are part of
 supplemental material
-
 \paragraph{Results.}

### 2014-11-18 mcmc.tex
added back
minor change

@@
 where $\max_{s} w(p) \ast T_s(\mathcal{I})$ is the maximum convolution score of
-NZ-WHO template $w(p)$ with image feautures $T_s(\mathcal{I})$ for all scale $s$, as defined
+NZ-WHO template $w(p)$ with image features $T_s(\mathcal{I})$ for all scale $s$, as defined
 in Sect.~\ref{sec:nzwho}.
@@
 \begin{align}
-    g(p \rightarrow p + v_i') & \sim \mathcal{N}(\mu = 0,\sigma = \sigma_v) \quad i \in \{1,2,3\}\\
-    g(p \rightarrow p + f') & \sim \mathcal{N}(\mu = 0,\sigma = \sigma_f)\\
-    g(p \rightarrow p + m') & \sim c \delta(m) + (1-c) Unif(1,M),
+    g(p \rightarrow p + v_i') & \sim \mathcal{N}(\mu = p_{v_i},\sigma = \sigma_v) \quad i \in \{1,2,3\}\\
+    g(p \rightarrow p + f') & \sim \mathcal{N}(\mu = p_{f},\sigma = \sigma_f)\\
+    g(p \rightarrow p + m') & \sim c \delta(p_m) + (1-c) Unif(1,M),
 \end{align}
@@
 Since the Metropolis-Hastings algorithm is susceptible to getting
-stuck in local optima, we need a good initialiation in order to
+stuck in local optima, we need a good initialization in order to
 increase the probability to find a solution that is close to the

### 2014-11-19 egpaper_supp.tex
in progress

@@
 %%%%%%%%% BODY TEXT
-We present qualitative results in the supplementary material for our paper ``Enriching Object Detection with 2D-3D Registration and Continuous Viewpoint Estimation''.
+We present qualitative results in the supplementary material for our paper
+``Enriching Object Detection with 2D-3D Registration and Continuous Viewpoint
+Estimation''.
 % In Sect.~\ref{sec:3dobject}, we present detection result on qualitative results.
@@
 \label{sect:3dobject}
-We run our ensemble of NZ-WHO templates as a detector on 3D Object dataset\cite{savarese07} and present detection average precision, average viewpoint precision, viewpoint confusion matrix and mean precision in pose estimation.
-See Fig.~\ref{fig:3dobject_ap}
+We run our ensemble of NZ-WHO templates as a detector on 3D Object
+dataset\cite{savarese07} without tuning and present detection average precision, average
+viewpoint precision, viewpoint confusion matrix and mean precision in pose
+estimation. See Fig.~\ref{fig:3dobject_ap}
+
+Most of the error in viewpoint estimation come from frontal and back views
 
@@
   \vspace{-5pt}
-  (b) Bicycle
-\caption{Detection and pose estimation on 3D Object dataset car category.
-(left) Average Precision (AP) and Average Viewpoint Precision (AVP) and (right) Viewpoint confusion table and MPPE, Viewpoint index 1 is front, 2 is front-right, 5 is back and 8 is front-left.
-Most of the error in viewpoint estimation come from frontal and back views}% with a bounding box and corresponding confidence score (right).}
+    (b) Bicycle\\
+  \caption{Detection and pose estimation on 3D Object dataset car category (top) and bicycle category (bottom).
+  Average Precision (red) and Average Viewpoint Precision (green) (left)
+  Viewpoint confusion table and MPPE (right), Viewpoint index 1 is front, index 2 is
+  front-right, \dots index 8 is front-left. }
   \label{fig:3dobject_ap}
@@
 
-More qualitative results are on the Fig.~\ref{fig:3dobject_good} and Fig.~\ref{fig:3dobject_bad}.
-The each of the template in the ensemble of NZ-WHO templates has a corresponding rendering and a CAD model.
-These can be transferred as a metadata and overlay the rendering on top of the detection.
+We put successful car detection results on Fig.~\ref{fig:3dobject_car_good} and
+failure cases on Fig.~\ref{fig:3dobject_car_bad}. And for bicycle, successful
+bicycle detection results are on Fig.~\ref{fig:3dobject_bicycle_good} and
+failure cases on Fig.~\ref{fig:3dobject_bicycle_bad}.
 
@@
   \includegraphics[width=0.40\linewidth]{supp/car32.png} &
-  \includegraphics[width=0.40\linewidth]{supp/bicycle17.png} \\
-  \includegraphics[width=0.40\linewidth]{supp/car26.png} &
-  \includegraphics[width=0.40\linewidth]{supp/bicycle18.png} \\
+  \includegraphics[width=0.40\linewidth]{supp/car26.png} \\
   \includegraphics[width=0.40\linewidth]{supp/car29.png} & 
-  \includegraphics[width=0.40\linewidth]{supp/bicycle13.png} \\
-  \includegraphics[width=0.40\linewidth]{supp/car10.png} &
-  \includegraphics[width=0.40\linewidth]{supp/bicycle9.png} \\
+  \includegraphics[width=0.40\linewidth]{supp/car10.png} \\
   \includegraphics[width=0.40\linewidth]{supp/car1.png} &
-  \includegraphics[width=0.40\linewidth]{supp/bicycle11.png} \\
-  \includegraphics[width=0.40\linewidth]{supp/car8.png} &
-  \includegraphics[width=0.40\linewidth]{supp/bicycle12.png} \\
+  \includegraphics[width=0.40\linewidth]{supp/car8.png} \\
   \includegraphics[width=0.40\linewidth]{supp/car20.png} & 
-  \includegraphics[width=0.40\linewidth]{supp/bicycle15.png} \\
-  \includegraphics[width=0.40\linewidth]{supp/car31.png} & 
-  \includegraphics[width=0.40\linewidth]{supp/bicycle10.png} \\
-  \includegraphics[width=0.40\linewidth]{supp/car33.png} & 
-  \includegraphics[width=0.40\linewidth]{supp/bicycle16.png} \\
-  \hline
-  Car & Bicycle \\
+  \includegraphics[width=0.40\linewidth]{supp/car31.png} \\
+%   \includegraphics[width=0.40\linewidth]{supp/car33.png} & 
   \hline
   \end{tabular}
-\caption{Successful detection results on 3D Object dataset car and bike classes.
-In each column, original image (left) and detection result overlaid on top (right).}% with a bounding box and corresponding confidence score (right).}
-  \label{fig:3dobject_good}
+\caption{Successful detection results on 3D Object dataset car
+category. In each column, original image (left) and detection result overlaid on
+top (right).}% with a bounding box and corresponding confidence score (right).}
+  \label{fig:3dobject_car_good}
+\end{figure*}
+
+\begin{figure*}[h]
+\setlength\tabcolsep{1pt}
+\centering
+\begin{tabular}{|c|c|}
+  \hline
+  \includegraphics[width=0.40\linewidth]{supp/bicycle17.png} &
+  \includegraphics[width=0.40\linewidth]{supp/bicycle18.png} \\
+  \includegraphics[width=0.40\linewidth]{supp/bicycle13.png} &
+  \includegraphics[width=0.40\linewidth]{supp/bicycle9.png} \\
+  \includegraphics[width=0.40\linewidth]{supp/bicycle16.png} &
+  \includegraphics[width=0.40\linewidth]{supp/bicycle12.png} \\
+  \includegraphics[width=0.40\linewidth]{supp/bicycle15.png} &
+  \includegraphics[width=0.40\linewidth]{supp/bicycle10.png} \\
+  \hline
+  \end{tabular}
+\caption{Successful detection results on 3D Object dataset car
+classes. In each column, original image (left) and detection result overlaid on
+top (right).}% with a bounding box and corresponding confidence score (right).}
+  \label{fig:3dobject_bicycle_good}
 \end{figure*}
@@
   \includegraphics[width=0.40\linewidth]{supp/car13.png} &
-  \includegraphics[width=0.40\linewidth]{supp/bicycle1.png} \\
-  \includegraphics[width=0.40\linewidth]{supp/car30.png} &
-  \includegraphics[width=0.40\linewidth]{supp/bicycle5.png} \\
+  \includegraphics[width=0.40\linewidth]{supp/car30.png} \\ 
   \includegraphics[width=0.40\linewidth]{supp/car18.png} &
-  \includegraphics[width=0.40\linewidth]{supp/bicycle19.png} \\
-  \hline
-  Car & Bicycle \\
+  \includegraphics[width=0.40\linewidth]{supp/car25.png} \\
   \hline
   \end{tabular}
-\caption{Failed pose estimation results on 3D Object dataset car and bike classes.
-In each column, original image (left) and detection result overlaid on top (right).}% with a bounding box and corresponding confidence score (right).}
-  \label{fig:3dobject_bad}
+\caption{Failed pose estimation results on 3D Object dataset car and bike
+classes. In each column, original image (left) and detection result overlaid on
+top (right).}% with a bounding box and corresponding confidence score (right).}
+  \label{fig:3dobject_car_bad}
+\end{figure*}
+
+\begin{figure*}[h]
+\setlength\tabcolsep{1pt}
+\centering
+\begin{tabular}{|c|c|}
+\hline 
+  \includegraphics[width=0.40\linewidth]{supp/bicycle1.png} &
+  \includegraphics[width=0.40\linewidth]{supp/bicycle5.png} \\
+  \includegraphics[width=0.40\linewidth]{supp/bicycle19.png} &
+  \includegraphics[width=0.40\linewidth]{supp/bicycle20.png} \\
+\hline
+\end{tabular}
+\caption{Failed pose estimation results on 3D Object dataset car and bike
+classes. In each column, original image (left) and detection result overlaid on
+top (right).}% with a bounding box and corresponding confidence score (right).}
+  \label{fig:3dobject_bicycle_bad}
+\end{figure*}
+
+\section{PASCAL3D+}
+
+We run our ensemble of NZ-WHO templates as a detector on car
+and bicycle classes in PASCAL3D+ dataset  \cite{Xiang14} and present detection average precision,
+average viewpoint precision, viewpoint confusion matrix and mean precision in
+pose estimation. See Fig.~\ref{fig:3dobject_ap}
+
+For each of the proposal bounding box, we assumed that there is only one object and the object 
+\begin{figure*}[h]
+\setlength\tabcolsep{1pt}
+\centering
+\begin{tabular}{|cc|cc|}
+  \hline
+  \includegraphics[width=0.24\linewidth]{supp/occlusion1.png} &
+  \includegraphics[width=0.24\linewidth]{supp/occlusion1b.png} & 
+  \includegraphics[width=0.24\linewidth]{supp/pas_car1a.png} &
+  \includegraphics[width=0.24\linewidth]{supp/pas_car1b.png}  \\
+  \includegraphics[width=0.24\linewidth]{supp/pas_car3a.png} &
+  \includegraphics[width=0.24\linewidth]{supp/pas_car3b.png} & 
+  \includegraphics[width=0.24\linewidth]{supp/pas_car5a.png} &
+  \includegraphics[width=0.24\linewidth]{supp/pas_car5b.png}  \\
+  \includegraphics[width=0.24\linewidth]{supp/pas_car6a.png} &
+  \includegraphics[width=0.24\linewidth]{supp/pas_car6b.png} & 
+  \includegraphics[width=0.24\linewidth]{supp/pas_car7a.png} &
+  \includegraphics[width=0.24\linewidth]{supp/pas_car7b.png}  \\
+  \includegraphics[width=0.24\linewidth]{supp/pas_car10a.png} &
+  \includegraphics[width=0.24\linewidth]{supp/pas_car10b.png} & 
+  \includegraphics[width=0.24\linewidth]{supp/pas_car16a.png} &
+  \includegraphics[width=0.24\linewidth]{supp/pas_car16b.png}  \\
+  \includegraphics[width=0.24\linewidth]{supp/pas_car17a.png} &
+  \includegraphics[width=0.24\linewidth]{supp/pas_car17b.png} & 
+  \includegraphics[width=0.24\linewidth]{supp/pas_car19a.png} &
+  \includegraphics[width=0.24\linewidth]{supp/pas_car19b.png} \\
+  \includegraphics[width=0.24\linewidth]{supp/pas_car21a.png} &
+  \includegraphics[width=0.24\linewidth]{supp/pas_car21b.png} & 
+  \includegraphics[width=0.24\linewidth]{supp/pas_car22a.png} &
+  \includegraphics[width=0.24\linewidth]{supp/pas_car22b.png} \\
+  \includegraphics[width=0.24\linewidth]{supp/pas_car18a.png} &
+  \includegraphics[width=0.24\linewidth]{supp/pas_car18b.png} & 
+  \includegraphics[width=0.24\linewidth]{supp/pas_car18c.png} &
+  \includegraphics[width=0.24\linewidth]{supp/pas_car18d.png} \\
+  \hline
+  \end{tabular}
+\caption{Successful detection result on PASCAL3D+ dataset car class, First tow columns are the original images and second column detection result overlaid on top. }
+  \label{fig:pascal3d_car_good}
+\end{figure*}
+
+\begin{figure*}[h]
+\setlength\tabcolsep{1pt}
+\centering
+\begin{tabular}{|cc|cc|}
+  \hline
+  \includegraphics[width=0.22\linewidth]{supp/pas_bicycle3a.png} &
+  \includegraphics[width=0.22\linewidth]{supp/pas_bicycle3b.png} & 
+  \includegraphics[width=0.22\linewidth]{supp/pas_bicycle13a.png} &
+  \includegraphics[width=0.22\linewidth]{supp/pas_bicycle13b.png}  \\
+  \includegraphics[width=0.22\linewidth]{supp/pas_bicycle5a.png} &
+  \includegraphics[width=0.22\linewidth]{supp/pas_bicycle5b.png} & 
+  \includegraphics[width=0.22\linewidth]{supp/pas_bicycle6a.png} &
+  \includegraphics[width=0.22\linewidth]{supp/pas_bicycle6b.png}  \\
+  \includegraphics[width=0.15\linewidth]{supp/pas_bicycle7a.png} &
+  \includegraphics[width=0.15\linewidth]{supp/pas_bicycle7b.png} & 
+  \includegraphics[width=0.22\linewidth]{supp/pas_bicycle8a.png} &
+  \includegraphics[width=0.22\linewidth]{supp/pas_bicycle8b.png}  \\
+  \includegraphics[width=0.15\linewidth]{supp/pas_bicycle9a.png} &
+  \includegraphics[width=0.15\linewidth]{supp/pas_bicycle9b.png} & 
+  \includegraphics[width=0.22\linewidth]{supp/pas_bicycle10a.png} &
+  \includegraphics[width=0.22\linewidth]{supp/pas_bicycle10b.png}  \\
+  \includegraphics[width=0.22\linewidth]{supp/pas_bicycle1a.png} &
+  \includegraphics[width=0.22\linewidth]{supp/pas_bicycle1b.png} & 
+  \includegraphics[width=0.22\linewidth]{supp/pas_bicycle2a.png} &
+  \includegraphics[width=0.22\linewidth]{supp/pas_bicycle2b.png}  \\
+  \includegraphics[width=0.22\linewidth]{supp/pas_bicycle11a.png} &
+  \includegraphics[width=0.22\linewidth]{supp/pas_bicycle11b.png} & 
+  \includegraphics[width=0.22\linewidth]{supp/pas_bicycle12a.png} &
+  \includegraphics[width=0.22\linewidth]{supp/pas_bicycle12b.png}  \\
+  \hline
+  \end{tabular}
+\caption{Successful detection result on PASCAL3D+ dataset car class, First tow columns are the original images and second column detection result overlaid on top. }
+  \label{fig:pascal3d_bicycle_good}
+\end{figure*}
+
+\begin{figure*}[h]
+\setlength\tabcolsep{1pt}
+\centering
+\begin{tabular}{|cc|cc|}
+  \hline
+%   \includegraphics[width=0.24\linewidth]{supp/pas_car2a.png} &
+%   \includegraphics[width=0.24\linewidth]{supp/pas_car2b.png} & 
+%   \includegraphics[width=0.24\linewidth]{supp/pas_car4a.png} &
+%   \includegraphics[width=0.24\linewidth]{supp/pas_car4b.png} \\
+  \includegraphics[width=0.22\linewidth]{supp/pas_car8a.png} &
+  \includegraphics[width=0.22\linewidth]{supp/pas_car8b.png} & 
+  \includegraphics[width=0.22\linewidth]{supp/pas_car9a.png} &
+  \includegraphics[width=0.22\linewidth]{supp/pas_car9b.png} \\ 
+  \includegraphics[width=0.22\linewidth]{supp/pas_car11a.png} &
+  \includegraphics[width=0.22\linewidth]{supp/pas_car11b.png} & 
+  \includegraphics[width=0.22\linewidth]{supp/pas_car12a.png} &
+  \includegraphics[width=0.22\linewidth]{supp/pas_car12b.png} \\
+  \includegraphics[width=0.22\linewidth]{supp/pas_car14a.png} &
+  \includegraphics[width=0.22\linewidth]{supp/pas_car14b.png} & 
+  \includegraphics[width=0.22\linewidth]{supp/pas_car15a.png} &
+  \includegraphics[width=0.22\linewidth]{supp/pas_car15.png} \\ 
+  \includegraphics[width=0.22\linewidth]{supp/pas_car20a.png} &
+  \includegraphics[width=0.22\linewidth]{supp/pas_car20b.png} &
+  \includegraphics[width=0.22\linewidth]{supp/pas_car23a.png} &
+  \includegraphics[width=0.22\linewidth]{supp/pas_car23b.png} \\
+  \hline
+  \end{tabular}
+\caption{Detection failure results on PASCAL3D+ dataset car class}% with a bounding box and corresponding confidence score (right).}
+  \label{fig:pascal3d_car_bad}
+\end{figure*}
+
+\begin{figure*}[h]
+\setlength\tabcolsep{1pt}
+\centering
+\begin{tabular}{|cc|cc|}
+  \hline
+  \includegraphics[width=0.22\linewidth]{supp/pas_bicycle14a.png} &
+  \includegraphics[width=0.22\linewidth]{supp/pas_bicycle14b.png} & 
+  \includegraphics[width=0.15\linewidth]{supp/pas_bicycle15a.png}  &
+  \includegraphics[width=0.15\linewidth]{supp/pas_bicycle15b.png}  \\
+  \includegraphics[width=0.22\linewidth]{supp/pas_bicycle16a.png} &
+  \includegraphics[width=0.22\linewidth]{supp/pas_bicycle16b.png} & 
+  \includegraphics[width=0.22\linewidth]{supp/pas_bicycle17a.png}  &
+  \includegraphics[width=0.22\linewidth]{supp/pas_bicycle17b.png}  \\ 
+  \includegraphics[width=0.22\linewidth]{supp/pas_bicycle18a.png} &
+  \includegraphics[width=0.22\linewidth]{supp/pas_bicycle18b.png} & 
+  \includegraphics[width=0.22\linewidth]{supp/pas_bicycle19a.png}  &
+  \includegraphics[width=0.22\linewidth]{supp/pas_bicycle19b.png}  \\   \hline
+  \end{tabular}
+\caption{Detection Result on PASCAL3D+ dataset car class}% with a bounding box and corresponding confidence score (right).}
+  \label{fig:pascal3d_bicycle_bad}
 \end{figure*}

### 2014-11-20 egpaper_supp.tex
Supplementary material pdf

@@
 \usepackage{rotating}
+
 \usepackage[space]{grffile}
@@
 \label{sect:3dobject}
-We run our ensemble of NZ-WHO templates as a detector on 3D Object
-dataset\cite{savarese07} without tuning and present detection average precision, average
-viewpoint precision, viewpoint confusion matrix and mean precision in pose
-estimation. See Fig.~\ref{fig:3dobject_ap}
 
-Most of the error in viewpoint estimation come from frontal and back views
+It this section, we provide qualitative examples and plots for the experiment
+``2D-3D Matching as an Object Detector''. To recapitulate, we run our ensemble
+of NZ-WHO templates as an ensemble of exemplar templates on 3D Object
+dataset\cite{savarese07} without fine-tuning stage. The detection average
+precision, average viewpoint precision, viewpoint confusion matrix and mean
+precision in pose estimation results are on Fig.~\ref{fig:3dobject_ap}
 
@@
   \caption{Detection and pose estimation on 3D Object dataset car category (top) and bicycle category (bottom).
-  Average Precision (red) and Average Viewpoint Precision (green) (left)
-  Viewpoint confusion table and MPPE (right), Viewpoint index 1 is front, index 2 is
-  front-right, \dots index 8 is front-left. }
+  Average Precision (red) and Average Viewpoint Precision (green) are overlaid on the left plot and
+  viewpoint confusion table and MPPE are on the right plot. The viewpoint index 1 is front, index 2 is
+  front-right, \dots index 8 is front-left.}
   \label{fig:3dobject_ap}
@@
 
-We put successful car detection results on Fig.~\ref{fig:3dobject_car_good} and
+For qualitative results, we put successful car viewpoint prediction results on
+Fig.~\ref{fig:3dobject_car_good} and
 failure cases on Fig.~\ref{fig:3dobject_car_bad}. And for bicycle, successful
-bicycle detection results are on Fig.~\ref{fig:3dobject_bicycle_good} and
-failure cases on Fig.~\ref{fig:3dobject_bicycle_bad}.
+results are on Fig.~\ref{fig:3dobject_bicycle_good} and
+failure cases on Fig.~\ref{fig:3dobject_bicycle_bad}. We followed detection
+and viewpoint estimation criteria of \cite{Xiang12} where detection is correct
+iff intersection over union of more than 0.5 and viewpoint estimation is
+correct iff detection is correct \emph{and} azimuth of the viewpoint
+prediction falls in to the correct viewpoint bin.
 
@@
   \includegraphics[width=0.40\linewidth]{supp/car31.png} \\
-%   \includegraphics[width=0.40\linewidth]{supp/car33.png} & 
   \hline
   \end{tabular}
-\caption{Successful detection results on 3D Object dataset car
-category. In each column, original image (left) and detection result overlaid on
-top (right).}% with a bounding box and corresponding confidence score (right).}
+\caption{Successful detection results on 3D Object dataset, car
+category. In each column, original image is on the left and detection result overlaid on
+the right.}% with a bounding box and corresponding confidence score (right).}
   \label{fig:3dobject_car_good}
@@
   \end{tabular}
-\caption{Successful detection results on 3D Object dataset car
-classes. In each column, original image (left) and detection result overlaid on
-top (right).}% with a bounding box and corresponding confidence score (right).}
+\caption{Successful detection results on 3D Object dataset, bicycle
+category. In each column, original image is on the left and detection result overlaid on
+the right).}% with a bounding box and corresponding confidence score (right).}
   \label{fig:3dobject_bicycle_good}
@@
   \end{tabular}
-\caption{Failed pose estimation results on 3D Object dataset car and bike
-classes. In each column, original image (left) and detection result overlaid on
-top (right).}% with a bounding box and corresponding confidence score (right).}
+\caption{Failed detection or pose estimation results on 3D Object dataset, car
+category. In each column, original image is on the left and detection result overlaid
+on the right.}% with a bounding box and corresponding confidence score (right).}
   \label{fig:3dobject_car_bad}
@@
 \end{tabular}
-\caption{Failed pose estimation results on 3D Object dataset car and bike
-classes. In each column, original image (left) and detection result overlaid on
-top (right).}% with a bounding box and corresponding confidence score (right).}
+\caption{Failed detection or pose estimation results on 3D Object dataset, bicycle
+category. In each column, original image is on the left and detection result overlaid on
+the right.}% with a bounding box and corresponding confidence score (right).}
   \label{fig:3dobject_bicycle_bad}
@@
 
-We run our ensemble of NZ-WHO templates as a detector on car
-and bicycle classes in PASCAL3D+ dataset  \cite{Xiang14} and present detection average precision,
-average viewpoint precision, viewpoint confusion matrix and mean precision in
-pose estimation. See Fig.~\ref{fig:3dobject_ap}
+It this section, we provide qualitative examples and plots for the experiment
+``Enriching Existing Detection''. To recapitulate, we used object detection
+bounding boxes from state-of-the-art detectors \cite{Girshick14, Pepik12} and
+enrich bounding boxes with 2D-3D registration and continuous viewpoint
+estimation. We present detection average precision, average viewpoint
+precision, viewpoint confusion matrix and mean precision in pose estimation
+results on Fig.~\ref{fig:pascal_ap}.
 
-For each of the proposal bounding box, we assumed that there is only one object and the object 
+We followed the evaluation criteria of \cite{Xiang14} for detection and
+viewpoint estimation.
+
+In this experiment, we used R-CNN\cite{Girshick14} for detection bounding box
+proposals and our system produces accurate 2D-3D matching on the proposal
+regions. We used $15\%$ context (extend the proposal region by $15\%$ on the
+top, right, left and bottom). We run our pipeline on PASCAL3D+
+dataset\cite{Xiang14} with fine-tuning stage.
+
+If our method fails to estimate viewpoint (confidence score is below 45), it
+estimates 0 azimuth, 0 elevation, 0 yaw. Note that for all categories and
+different number of viewpoints, our method has difficulty discerning frontal
+view and back view.
+
+\begin{figure*}[h]
+  \centering
+  \begin{tabular}{cc}
+  \includegraphics[width=0.45\linewidth]{car_cnn4_crop.png}&
+  \includegraphics[width=0.45\linewidth]{car_cnn8_crop.png}\\
+    (a) Car, 4 views&
+    (b) Car, 8 views\\
+  \includegraphics[width=0.45\linewidth]{car_cnn16_crop.png}&
+  \includegraphics[width=0.45\linewidth]{car_cnn24_crop.png}\\
+    (c) Car, 16 views&
+    (d) Car, 24 views\\
+  \includegraphics[width=0.45\linewidth]{supp/bicycle_cnn4_crop.png}&
+  \includegraphics[width=0.45\linewidth]{supp/bicycle_cnn8_crop.png}\\
+    (e) Bicycle, 4 views&
+    (j) Bicycle, 8 views\\  
+  \includegraphics[width=0.45\linewidth]{supp/bicycle_cnn16_crop.png}&
+  \includegraphics[width=0.45\linewidth]{supp/bicycle_cnn24_crop.png}\\
+    (g) Bicycle, 16 views&
+    (h) Bicycle, 24 views\\
+  \end{tabular}
+  \caption{Detection and pose estimation on PASCAL3D+ dataset. On the left, we
+  present average precision curve (red) average viewpoint precision curve
+  (green). On the right, we present confusion matrix and mean precision in pose
+  estimation. Viewpoint index 1 is front, index 2 is front-right \dots and
+  $n-1$ is front-left for number of viewpoints $n$.}
+  \label{fig:pascal_ap}
+\end{figure*}
+
+We put qualitative results on Fig.~\ref{fig:pascal3d_car_good} to
+Fig.~\ref{fig:pascal3d_bicycle_bad}.
+
 \begin{figure*}[h]
@@
   \end{tabular}
-\caption{Successful detection result on PASCAL3D+ dataset car class, First tow columns are the original images and second column detection result overlaid on top. }
+  \caption{Successful detection and pose estimation result on PASCAL3D+ dataset
+  car category, On each column, original image is on the left and overlaid
+  2D-3D registration on the right with a proposal bounding box (blue) and a
+  predicted bounding box (purple).} 
   \label{fig:pascal3d_car_good}
@@
   \end{tabular}
-\caption{Successful detection result on PASCAL3D+ dataset car class, First tow columns are the original images and second column detection result overlaid on top. }
+\caption{Successful detection and pose estimation result on PASCAL3D+ dataset
+  bicycle category, On each column, original image is on the left and overlaid
+  2D-3D registration on the right with a proposal bounding box (blue) and a
+  predicted bounding box (purple).} 
   \label{fig:pascal3d_bicycle_good}
@@
   \end{tabular}
-\caption{Detection failure results on PASCAL3D+ dataset car class}% with a bounding box and corresponding confidence score (right).}
+\caption{Failed detection or pose estimation result on PASCAL3D+ dataset
+  car category, On each column, original image is on the left and overlaid
+  2D-3D registration on the right with a proposal bounding box (blue) and a
+  predicted bounding box (purple).} 
   \label{fig:pascal3d_car_bad}
@@
   \end{tabular}
-\caption{Detection Result on PASCAL3D+ dataset car class}% with a bounding box and corresponding confidence score (right).}
+\caption{Failed detection or pose estimation result on PASCAL3D+ dataset
+  bicycle category, On each column, original image is on the left and overlaid
+  2D-3D registration on the right with a proposal bounding box (blue) and a
+  predicted bounding box (purple).} 
   \label{fig:pascal3d_bicycle_bad}
+\end{figure*}
+
+\section{Fine Tuning}
+
+In this section, we give qualitative examples of before and after the
+fine-tuning stage on Fig.~\ref{tuning}.
+
+See section ``Pose Fine-Tuning via MCMC'' for more detail.
+
+\begin{figure*}[h]
+\setlength\tabcolsep{1pt}
+\centering
+\begin{tabular}{ccc}
+  \includegraphics[width=0.22\linewidth]{supp/tuning_1a.png} &
+  \includegraphics[width=0.22\linewidth]{supp/tuning_1b.png} & 
+  \includegraphics[width=0.22\linewidth]{supp/tuning_1c.png}  \\
+  \includegraphics[width=0.22\linewidth]{supp/tuning_2a.png} &
+  \includegraphics[width=0.22\linewidth]{supp/tuning_2b.png} & 
+  \includegraphics[width=0.22\linewidth]{supp/tuning_2c.png}  \\ 
+  \includegraphics[width=0.22\linewidth]{supp/tuning_3a.png} &
+  \includegraphics[width=0.22\linewidth]{supp/tuning_3b.png} & 
+  \includegraphics[width=0.22\linewidth]{supp/tuning_3c.png}  \\   
+  \includegraphics[width=0.22\linewidth]{supp/tuning_4a.png} &
+  \includegraphics[width=0.22\linewidth]{supp/tuning_4b.png} & 
+  \includegraphics[width=0.22\linewidth]{supp/tuning_4c.png}  \\     
+  \includegraphics[width=0.22\linewidth]{supp/tuning_5a.png} &
+  \includegraphics[width=0.22\linewidth]{supp/tuning_5b.png} & 
+  \includegraphics[width=0.22\linewidth]{supp/tuning_5c.png}  \\
+  \includegraphics[width=0.22\linewidth]{supp/tuning_6a.png} &
+  \includegraphics[width=0.22\linewidth]{supp/tuning_6b.png} & 
+  \includegraphics[width=0.22\linewidth]{supp/tuning_6c.png}  \\
+  \end{tabular}
+\caption{From left to right, original images, initial pose estimations and
+fine-tuned result. The numbers, from the left, indicate detection confidence
+and intersection over union respectively.} 
+  \label{fig:tuning}
 \end{figure*}

### 2014-11-20 egpaper_supp.tex
pass over suppl

@@
 %%%%%%%%% BODY TEXT
-We present qualitative results in the supplementary material for our paper
-``Enriching Object Detection with 2D-3D Registration and Continuous Viewpoint
-Estimation''.
+In the following, we present additional quantitative and qualitative
+results that accompany the experiments described in Sect.~6 of the
+main paper, ``Enriching Object Detection with 2D-3D Registration and
+Continuous Viewpoint Estimation''.
 % In Sect.~\ref{sec:3dobject}, we present detection result on qualitative results.
 
-\section{3D Object Dataset}
+\section{2D-3D Matching as an Object Detector}
 \label{sect:3dobject}
+It this section, we provide qualitative examples and plots for the experiment
+``2D-3D Matching as an Object Detector'' (Sect.~6.2 in the main
+paper).
 
-It this section, we provide qualitative examples and plots for the experiment
-``2D-3D Matching as an Object Detector''. To recapitulate, we run our ensemble
-of NZ-WHO templates as an ensemble of exemplar templates on 3D Object
-dataset\cite{savarese07} without fine-tuning stage. The detection average
-precision, average viewpoint precision, viewpoint confusion matrix and mean
-precision in pose estimation results are on Fig.~\ref{fig:3dobject_ap}
-
+To recapitulate, we run our ensemble
+of NZ-WHO templates on the 3D Object Classes
+dataset~\cite{savarese07}, without the fine-tuning
+stage. Fig.~\ref{fig:3dobject_ap} gives the corresponding detection
+average precision, average viewpoint precision, viewpoint confusion
+matrix and mean precision in pose estimation results. Specifically, we
+followed the detection and viewpoint estimation criteria
+of~\cite{Xiang12} where a detection is correct iff
+intersection over union is at least $0.5$ and viewpoint estimation is
+correct iff detection is correct \emph{and} azimuth of the viewpoint
+prediction falls into the correct viewpoint bin.
+%
 \begin{figure}[h]
@@
     (b) Bicycle\\
-  \caption{Detection and pose estimation on 3D Object dataset car category (top) and bicycle category (bottom).
-  Average Precision (red) and Average Viewpoint Precision (green) are overlaid on the left plot and
-  viewpoint confusion table and MPPE are on the right plot. The viewpoint index 1 is front, index 2 is
-  front-right, \dots index 8 is front-left.}
+  \caption{Detection and pose estimation on 3D Object
+    Classes~\cite{savarese07} car (a) and bicycle (b).
+    Average Precision (red) and Average Viewpoint Precision (green)
+    are given in the left plot and viewpoint confusion table and MPPE
+    are given in the right plot. The viewpoint index 1 is front, 2 is
+    front-right, \dots, 8 is front-left.}
   \label{fig:3dobject_ap}
@@
 
-For qualitative results, we put successful car viewpoint prediction results on
-Fig.~\ref{fig:3dobject_car_good} and
-failure cases on Fig.~\ref{fig:3dobject_car_bad}. And for bicycle, successful
-results are on Fig.~\ref{fig:3dobject_bicycle_good} and
-failure cases on Fig.~\ref{fig:3dobject_bicycle_bad}. We followed detection
-and viewpoint estimation criteria of \cite{Xiang12} where detection is correct
-iff intersection over union of more than 0.5 and viewpoint estimation is
-correct iff detection is correct \emph{and} azimuth of the viewpoint
-prediction falls in to the correct viewpoint bin.
+Fig.~\ref{fig:3dobject_car_good} shows successful detection and
+viewpoint estimation results for car,
+Fig.~\ref{fig:3dobject_bicycle_good} for
+bicycle. Fig.~\ref{fig:3dobject_car_bad} and
+Fig.~\ref{fig:3dobject_bicycle_bad} show failure cases, which are
+mostly due to confused front and back views for cars, and slanted
+bicycle poses.
 

### 2014-11-20 egpaper_supp.tex
8 pages

@@
 
-\section{PASCAL3D+}
+\section{Enriching Existing Detections}
+%
+It this section, we provide qualitative examples and plots for the experiment
+``Enriching Existing Detections'' (Sect.~6.3 in the main paper).
 
-It this section, we provide qualitative examples and plots for the experiment
-``Enriching Existing Detection''. To recapitulate, we used object detection
-bounding boxes from state-of-the-art detectors \cite{Girshick14, Pepik12} and
-enrich bounding boxes with 2D-3D registration and continuous viewpoint
-estimation. We present detection average precision, average viewpoint
-precision, viewpoint confusion matrix and mean precision in pose estimation
-results on Fig.~\ref{fig:pascal_ap}.
+To recapitulate, we enrich object detection bounding boxes from
+a state-of-the-art detector (R-CNN~\cite{Girshick14}) with 2D-3D
+registration and continuous viewpoint estimation. We present detection
+average precision, average viewpoint precision, viewpoint confusion
+matrix and mean precision in pose estimation results in
+Fig.~\ref{fig:pascal_ap}, following the evaluation criteria
+of~\cite{Xiang14} for detection and viewpoint
+estimation. Fig.~\ref{fig:pascal3d_car_good} to
+Fig.~\ref{fig:pascal3d_bicycle_bad} give qualitative results.
+%
+%In this experiment, we use R-CNN\cite{Girshick14} for detection bounding box
+%proposals and our system produces accurate 2D-3D matching on the proposal
+%regions.
 
-We followed the evaluation criteria of \cite{Xiang14} for detection and
-viewpoint estimation.
-
-In this experiment, we used R-CNN\cite{Girshick14} for detection bounding box
-proposals and our system produces accurate 2D-3D matching on the proposal
-regions. We used $15\%$ context (extend the proposal region by $15\%$ on the
-top, right, left and bottom). We run our pipeline on PASCAL3D+
-dataset\cite{Xiang14} with fine-tuning stage.
-
-If our method fails to estimate viewpoint (confidence score is below 45), it
-estimates 0 azimuth, 0 elevation, 0 yaw. Note that for all categories and
-different number of viewpoints, our method has difficulty discerning frontal
-view and back view.
-
+We use $15\%$ context (extending the proposal region by $15\%$ on the
+top, right, left, and bottom). We run our pipeline on the
+PASCAL3D+~\cite{Xiang14} dataset, including our fine-tuning stage.
+%
+%If our method fails to estimate viewpoint (confidence score is below
+%45), it
+If our method fails to estimate viewpoint (confidence score is below a
+threshold), it outputs 0 azimuth, 0 elevation, 0 yaw. Note that for
+both categories and different numbers of viewpoints, our method has
+difficulty distinguishing front and back views, but yields little
+confusion between neighboring views. The failure cases given in
+Fig.~\ref{fig:pascal3d_car_bad} and
+Fig.~\ref{fig:pascal3d_bicycle_bad} are mostly caused by truncation,
+occlusion, and unusual object shape.
+%
 \begin{figure*}[h]
@@
 \end{figure*}
-
-We put qualitative results on Fig.~\ref{fig:pascal3d_car_good} to
-Fig.~\ref{fig:pascal3d_bicycle_bad}.
-
+%
 \begin{figure*}[h]
@@
 \section{Fine Tuning}
-
-In this section, we give qualitative examples of before and after the
-fine-tuning stage on Fig.~\ref{tuning}.
-
-See section ``Pose Fine-Tuning via MCMC'' for more detail.
-
+Lastly, we provide qualitative examples of the fine-tuning stage of
+our pipeline based on MCMC sampling (Sect.~5 in the main paper) in
+Fig.~\ref{fig:tuning}. Please note that, while the visual difference
+appear subtle, our method often manages to improve upon the initial
+pose estimate.
+%
 \begin{figure*}[h]
@@
 
-\clearpage
-\clearpage
 {\small

### 2014-11-20 egpaper_supp.tex
suppl progress

@@
   \end{tabular}
-\caption{Successful detection results on 3D Object dataset, car
-category. In each column, original image is on the left and detection result overlaid on
-the right.}% with a bounding box and corresponding confidence score (right).}
+\caption{Successful detection results on 3D Object
+  Classes~\cite{savarese07} cars. Original image (left) and overlaid
+  detection result (right).}% with a bounding box and corresponding
+                            % confidence score (right).}
   \label{fig:3dobject_car_good}
@@
   \end{tabular}
-\caption{Successful detection results on 3D Object dataset, bicycle
-category. In each column, original image is on the left and detection result overlaid on
-the right).}% with a bounding box and corresponding confidence score (right).}
+\caption{Successful detection results on 3D Object
+  Classes~\cite{savarese07} bicycles. Original image (left) and
+  overlaid detection result (right).}
   \label{fig:3dobject_bicycle_good}
@@
   \end{tabular}
-\caption{Failed detection or pose estimation results on 3D Object dataset, car
-category. In each column, original image is on the left and detection result overlaid
-on the right.}% with a bounding box and corresponding confidence score (right).}
+\caption{Failed detection or pose estimation on 3D Object
+  Classes~\cite{savarese07} cars. Original image (left) and overlaid
+  detection result (right).}
   \label{fig:3dobject_car_bad}
@@
 \end{tabular}
-\caption{Failed detection or pose estimation results on 3D Object dataset, bicycle
-category. In each column, original image is on the left and detection result overlaid on
-the right.}% with a bounding box and corresponding confidence score (right).}
+\caption{Failed detection or pose estimation on 3D Object
+  Classes~\cite{savarese07} bicycles. Original image (left) and overlaid
+  detection result (right).}
   \label{fig:3dobject_bicycle_bad}
@@
   \end{tabular}
-  \caption{Detection and pose estimation on PASCAL3D+ dataset. On the left, we
-  present average precision curve (red) average viewpoint precision curve
-  (green). On the right, we present confusion matrix and mean precision in pose
-  estimation. Viewpoint index 1 is front, index 2 is front-right \dots and
-  $n-1$ is front-left for number of viewpoints $n$.}
+  \caption{Detection and pose estimation on PASCAL3D+~\cite{Xiang14}
+    cars and bicycles.
+    Average Precision (red) and Average Viewpoint Precision (green)
+    are given in the left plot and viewpoint confusion table and MPPE
+    are given in the right plot. The viewpoint index 1 is front, 2 is
+    front-right, \dots, $n-1$ is front-left for number of viewpoints $n$.}
+ % On the left, we
+ %  present average precision curve (red) average viewpoint precision curve
+ %  (green). On the right, we present confusion matrix and mean precision in pose
+ %  estimation. Viewpoint index 1 is front, index 2 is front-right \dots and
+ %  $n-1$ is front-left for number of viewpoints $n$.}
   \label{fig:pascal_ap}

### 2014-11-20 egpaper_supp.tex
done pass over supp

@@
   \end{tabular}
-  \caption{Successful detection and pose estimation result on PASCAL3D+ dataset
-  car category, On each column, original image is on the left and overlaid
-  2D-3D registration on the right with a proposal bounding box (blue) and a
+  \caption{Successful detection and pose estimation results on
+    PASCAL3D+~\cite{Xiang14} cars. Original image (left) and
+  overlaid detection result (right). Proposal bounding box (blue) and
   predicted bounding box (purple).}
@@
   \end{tabular}
-\caption{Successful detection and pose estimation result on PASCAL3D+ dataset
-  bicycle category, On each column, original image is on the left and overlaid
-  2D-3D registration on the right with a proposal bounding box (blue) and a
+\caption{Successful detection and pose estimation results on
+    PASCAL3D+~\cite{Xiang14} bicycles. Original image (left) and
+  overlaid detection result (right). Proposal bounding box (blue) and
   predicted bounding box (purple).} 
@@
   \end{tabular}
-\caption{Failed detection or pose estimation result on PASCAL3D+ dataset
-  car category, On each column, original image is on the left and overlaid
-  2D-3D registration on the right with a proposal bounding box (blue) and a
+\caption{Failed detection or pose estimation result on
+  PASCAL3D+~\cite{Xiang14} cars. Original image (left) and
+  overlaid detection result (right). Proposal bounding box (blue) and
   predicted bounding box (purple).} 
@@
   \end{tabular}
-\caption{Failed detection or pose estimation result on PASCAL3D+ dataset
-  bicycle category, On each column, original image is on the left and overlaid
-  2D-3D registration on the right with a proposal bounding box (blue) and a
+\caption{Failed detection or pose estimation result on
+  PASCAL3D+~\cite{Xiang14} bicycles. Original image (left) and
+  overlaid detection result (right). Proposal bounding box (blue) and
   predicted bounding box (purple).} 
@@
   \end{tabular}
-\caption{From left to right, original images, initial pose estimations and
-fine-tuned result. The numbers, from the left, indicate detection confidence
-and intersection over union respectively.} 
+\caption{Effect of fine-tuning based on MCMC sampling. From left to
+  right: original image, initial pose estimate, and fine-tuned
+  result. Numbers indicate detection confidence (s) and intersection
+  over union (o), respectively.} 
   \label{fig:tuning}

### 2014-11-21 experiments.tex
Supplementary material pdf
compressed

@@
     HOG\cite{Dalal05}      & 72.3 / 65.0          &  31ms  & 60.4 / 50.2           & 8.7 sec \\ 
-    WHO\cite{Hariharan12} & 82.1 / 85.4           &  3811ms& 84.4 / 83.0                 & 12.4 sec  \\
-    WHO-CG                & 81.7 / \textbf{84.9}  &  104ms & 83.7 / 87.3                 & 8.3 sec \\
+    WHO\cite{Hariharan12}  & 82.1 / \textbf{85.4} &  3811ms& 84.4 / 83.0           & 12.4 sec\\
+    WHO-CG                 & 81.7 / 84.9          &  104ms & 83.7 / \textbf{87.3}  & 8.3 sec \\
     WHO-CG-Z               & 54.4 / 65.1          &  103ms & \textbf{92.8} / 86.7  & 8.7 sec \\
-    % NZC-WHO-Z    & 89.10/\textbf{78.64} &    & 91.15/74.79                  &     \\
-    NZ-WHO-CG {\em (ours)}  & \textbf{90.0} / 82.8  &   79ms & 90.3 / \textbf{86.8}        & 8.5 sec   \\
+    % NZC-WHO-Z    & 89.10 /\textbf{78.64} &    & 91.15 / 74.79                  &     \\
+    NZ-WHO-CG {\em (ours)} & \textbf{90.0} / 82.8 &   79ms & 90.3 / 86.8           & 8.5 sec \\
     \hline
@@
 worse than both methods ($91.7$ vs. $93.4$ and $97.5$ for cars, and
-$87.4$ vs. $91.4$ and $97.5$ for bicycles, respectively).
+$90.9$ vs. $91.4$ and $97.5$ for bicycles, respectively).
 
@@
   result overlaid on top (right).}% with a bounding box and corresponding confidence score (right).}
-  \label{fig:3dobject}
+  \label{fig:3dobject_vis}
 \end{figure}
@@
 variants trained on 8 viewpoint categories, since these perform best
-in terms of AP. For both methods,
+in terms of AP. For both cases,
 we use the original score for plotting precision-recall curves
@@
 enrich the detections with additional viewpoint information provided
-by our method. For DPM-VOC+VP, we fall back to the viewpoint
-estimation provided by this method in case the confidence of our
-method falls below a threshold. For R-CNN, we fall back to a default
-viewpoint prediction ($0$ angles).
+by our method. We fall back to a default
+viewpoint prediction ($0$ angles) in case the confidence of our
+method falls below a threshold.
 

### 2014-11-21 experiments.tex
minor changes

@@
 prior work~\cite{Aubry14}. At the same time, calibration is
-computationally expensive, resulting in runtimes that are two orders of
+computationally expensive, resulting in generation time that are two orders of
 magnitudes larger than without calibration. Strikingly, our method
@@
     HOG\cite{Dalal05}      & 72.3 / 65.0          &  31ms  & 60.4 / 50.2           & 8.7 sec \\ 
-    WHO\cite{Hariharan12}  & 82.1 / \textbf{85.4} &  3811ms& 84.4 / 83.0           & 12.4 sec\\
+    WHO\cite{Hariharan12}  & 82.1 / \textbf{85.4} &  6162ms& 84.4 / 83.0           & 15.4 sec\\
     WHO-CG                 & 81.7 / 84.9          &  104ms & 83.7 / \textbf{87.3}  & 8.3 sec \\
@@
   \caption{Average Precision(AP), Mean Precision in Pose Estimation
-    (MPPE)~\cite{Lopez-Sastre11}, and runtime for variations of WHO on
+    (MPPE)~\cite{Lopez-Sastre11}, and generation time for variations of WHO on
     3D Object Classes cars~\cite{Savarese07}. Please see text for

### 2015-01-20 rebuttal/rebuttal.md
Rebuttal

We appreciate the valuable comments from all the reviewers. We are happy to
hear RWs agree that we address a

The paper present major improvements to the WHO approach (speed and performance) by thoroughly analyzing exisitn gWHO and performed extensive experiments to validate as pointed by [R1] and

# Weakness

## Scalability [R1]

This gives the user degree of accuracy they aim

## Realistic Textured Model as oppose to Simple Geometric Model

## Effectiveness of Fine Tuning [R1]

This gives the user degree of accuracy they aim

## Limited PASCAL 3D+ Experiments

- This is a good dataset to report results in pose estimation, and improving
  the baseline is one of the strength of the paper. However, the strength of
  the dataset is that it has more than 10 categories: why report results only
  on cars and bicycles?[R2]

Another good thing about this approach is that it can augment the output of 2D detectors which is very valuable.[R1]

## Writing [R2]

As [R2] pointed out, we thank [R2] for pointing out missing references. The final version will not have any writing issues.

# Ambiguity

## Calibration, Inversion one time process?

almost 4 seconds for original WHO computation seems very bad. From the text, it seems to me that the authors considered the time of the inversion of Sigma. Since it can be done only once (or downloaded from internet) there is no reason to consider it! Also, a fair comparison would consider a GPU implementation of the (sparse) matrix product involved, and that would probably be extremely fast as well [R2]

Rebuttal : The matrix $\Sigma \in \mathcal{R}^{(W\times H\times F) \times (W\times H\times F)}$ where $W$ is the number of HOG cells in width and $H$ is the number of HOG cells in the height and $F$ is the number of features which is 31 for HOG. Usually, the sigma matrix is about $7000 \times 7000$ for a specific template size and if you save it as a 4Byte double this takes 180MByte which is prohibitive. Not only the matrix is aspect ratio specific, but it also is specific for foreground mask. Our approach, which we experimentally validated, decorrelates only the foreground thus requires foreground mask specific sigma. Thus there is no way to cache/download the large matrix sigma. The other reviews [R1, R3] considered as a great improvement over WHO feature. The matrix is very dens due to the fact that the lines are usually continuous. All templates have different aspect ratio which cannot be cached nor downloadable. The inversion is unique for each template. We will emphasize  this point in the final paper.

## Variation of WHO.

almost 4 seconds for original WHO computation seems very bad. From the text, it seems to me that the authors considered the time of the inversion of Sigma. Since it can be done only once (or downloaded from internet) there is no reason to consider it! Also, a fair comparison would consider a GPU implementation of the (sparse) matrix product involved, and that would probably be extremely fast as well [R2]
Rebuttal : All templates have different aspect ratio which cannot be cached nor downloadable. The inversion is unique for each template.
analyzing the existing WHO approach and suggesting improvements to it. The authors have performed extensive experiments to validate their approach, comparing against all variations of WHO and justifying their insights. I think this part of the work is very well done. The proposed method shows considerable improvement over the existing state of the art techniques. It is much simpler to understand and optimize than existing techniques which is an added advantage. [R1]

### 2015-01-22 rebuttal/rebuttal.md
rebuttal draft

@@
 We appreciate the valuable comments from all the reviewers. We are happy to
-hear RWs agree that we address a
+hear reviewers agree that we proposed “efficient”[R2,R3] and “considerable
+improvements to WHO”[R1] in terms of “speed”[R1,R3] and “detection
+performance”[R1]. The method was “well motivated”  was validated with
+“extensive experiments”[R1].
 
-The paper present major improvements to the WHO approach (speed and performance) by thoroughly analyzing exisitn gWHO and performed extensive experiments to validate as pointed by [R1] and
+R1.1 & [R2 one-time]: Our method proposed a way to fine tune the viewpoint in
+continuous space without expensive training thus providing vision community a
+modular framework for view estimation. However, caching all possible templates
+would be intractable and difficult to cover continuous azimuth, elevation,
+in-plane rotation, focal length and intraclass CAD models. To overcome, our
+method generates proposals on-the-fly which requires covariance inversion which
+we handled by Conjugate Gradient.
 
-# Weakness
+R1 & R2, effectiveness of fine-tuning: The continuous viewpoint estimation not
+only recovers from wrong pose but also accurately refine the viewpoint.
+Unfortunately, the PASCAL 3D+ and 3D Object datasets only measures the number
+of correct viewpoint bins from bird-eye view. If a viewpoint estimation fall
+into the correct bin in the coarse estimation, the improvement from the
+fine-tuning cannot be measured. So the improvements comes from the fine-tuning
+measured using the criteria is the number of recovers from wrong initialization
+only. We will explain this point in our final paper.
 
-## Scalability [R1]
+R1, RCNN + Ours: DPM-VOC+VP method templates are made from ground truth
+bounding boxes so the bounding boxes are more tight and informative compare to
+region based bounding boxes (RCNN). Our algorithm tries to handle such
+incorrect bounding boxes by creating HOG scale pyramid for the given bounding
+box but more accurate the bounding box is, better the performance. This effect
+is dominant for coarser viewpoint where RCNN and DPM-VOC+VP have similar
+performance.
 
-This gives the user degree of accuracy they aim
+R2, inversion time: Sigma is a covariance matrix of size (W x H x F) x (W x H x
+F) where W and H are the number of HOG cells in a row and a column, F is the
+dimension of HOG feature [Hariharan et al. 12]. In practice, we used
+high-resolution template and the resulting covariance matrix was around
+7000x7000 (~180MByte in single precision). Thus, using the Cholesky
+decomposition, it took more than 4 seconds on i7-4770K. To get extra speed up,
+we also tried to make use of the Toeplitz-Block-Toeplitz structure and achieved
+O(n log n) time complexity using DFT but the time complexity coefficient was
+too large and the non-zero pattern destroys the Toeplitz structure so we did
+not incorporated in our paper. We did not emphasize this point in detail
+[Sec.4] but will try to incorporate this point in the final version.
 
-## Realistic Textured Model as oppose to Simple Geometric Model
+Second point raised by [R2] is that the sigma matrix product can be done in GPU
+implementation. We think the reviewer meant matrix decomposition since we
+compared the matrix inversion time. We thank [R2] for correctly pointing this
+out and we will incorporate GPU implementation of Cholesky decomposition
+experiment in our final paper.
 
-## Effectiveness of Fine Tuning [R1]
+R3, Zia el al.: We thank the reviewer for point this out. We agree that Zia et
+al. tackles the similar problem. However, due to their complex model, their
+model requires accurate bounding box and viewpoint estimation. On the other
+hand, our method can work as a standalone detector and performs on par with
+many state-of-the-art detectors though the dataset is saturated as correctly
+pointed by [R1]. But we think this is a good comparison and we will add
+discussion and comparison with Zia et al on the final version.
 
-This gives the user degree of accuracy they aim
+We thank R2 for pointing out writing errors and missing references. Although
+our article is “well written”[R1] and “explains ... well”[R1], we also noticed
+the errors and fixed them including the ones pointed out by R2. We apologize
+for such mistakes.
 
-## Limited PASCAL 3D+ Experiments
-
-- This is a good dataset to report results in pose estimation, and improving
-  the baseline is one of the strength of the paper. However, the strength of
-  the dataset is that it has more than 10 categories: why report results only
-  on cars and bicycles?[R2]
-
-Another good thing about this approach is that it can augment the output of 2D detectors which is very valuable.[R1]
-
-## Writing [R2]
-
-As [R2] pointed out, we thank [R2] for pointing out missing references. The final version will not have any writing issues.
-
-# Ambiguity
-
-## Calibration, Inversion one time process?
-
-almost 4 seconds for original WHO computation seems very bad.
-From the text, it seems to me that the authors considered the time of the inversion of Sigma.
-Since it can be done only once (or downloaded from internet) there is no reason to consider it!
-Also, a fair comparison would consider a GPU implementation of the (sparse) matrix product involved, and that would probably be extremely fast as well [R2]
-
-Rebuttal : The matrix $\Sigma \in \mathcal{R}^{(W\times H\times F) \times (W\times H\times F)}$ where $W$ is the number of HOG cells in width and $H$ is the number of HOG cells in the height and $F$ is the number of features which is 31 for HOG.
-Usually, the sigma matrix is about $7000 \times 7000$ for a specific template size and if you save it as a 4Byte double this takes 180MByte which is prohibitive.
-Not only the matrix is aspect ratio specific, but it also is specific for foreground mask.
-Our approach, which we experimentally validated, decorrelates only the foreground thus requires foreground mask specific sigma.
-Thus there is no way to cache/download the large matrix sigma.
-The other reviews [R1, R3] considered as a great improvement over WHO feature.
-The matrix is very dens due to the fact that the lines are usually continuous.
-All templates have different aspect ratio which cannot be cached nor downloadable.
-The inversion is unique for each template.
-We will emphasize  this point in the final paper.
-
-## Variation of WHO.
-
-almost 4 seconds for original WHO computation seems very bad.
-From the text, it seems to me that the authors considered the time of the inversion of Sigma.
-Since it can be done only once (or downloaded from internet) there is no reason to consider it!
-Also, a fair comparison would consider a GPU implementation of the (sparse) matrix product involved, and that would probably be extremely fast as well [R2]
-Rebuttal : All templates have different aspect ratio which cannot be cached nor downloadable. The inversion is unique for each template.
-analyzing the existing WHO approach and suggesting improvements to it.
-The authors have performed extensive experiments to validate their approach, comparing against all variations of WHO and justifying their insights.
-I think this part of the work is very well done.
-The proposed method shows considerable improvement over the existing state of the art techniques.
-It is much simpler to understand and optimize than existing techniques which is an added advantage.
-[R1]
+We will try our best to incorporate all the remaining issues pointed out by the
+reviewers to the final paper should it be accepted.

### 2015-01-22 rebuttal/rebuttal.md
minor change

@@
 We appreciate the valuable comments from all the reviewers. We are happy to
-hear reviewers agree that we proposed “efficient”[R2,R3] and “considerable
+hear reviewers agree on that we proposed “efficient”[R2,R3] and “considerable
 improvements to WHO”[R1] in terms of “speed”[R1,R3] and “detection
-performance”[R1]. The method was “well motivated”  was validated with
+performance”[R1]. The method was “well motivated”  and validated with
 “extensive experiments”[R1].
@@
 modular framework for view estimation. However, caching all possible templates
-would be intractable and difficult to cover continuous azimuth, elevation,
+would be intractable and difficult to cover all continuous azimuth, elevation,
 in-plane rotation, focal length and intraclass CAD models. To overcome, our
-method generates proposals on-the-fly which requires covariance inversion which
-we handled by Conjugate Gradient.
+method generates proposals on-the-fly which requires covariance inversion.
 
 R1 & R2, effectiveness of fine-tuning: The continuous viewpoint estimation not
-only recovers from wrong pose but also accurately refine the viewpoint.
+only recovers from wrong pose but also accurately refines the coarse viewpoint estimation.
 Unfortunately, the PASCAL 3D+ and 3D Object datasets only measures the number
-of correct viewpoint bins from bird-eye view. If a viewpoint estimation fall
+of correct viewpoint bins from bird-eye view. If a viewpoint estimation falls
 into the correct bin in the coarse estimation, the improvement from the
-fine-tuning cannot be measured. So the improvements comes from the fine-tuning
-measured using the criteria is the number of recovers from wrong initialization
-only. We will explain this point in our final paper.
+fine-tuning cannot be measured using the metric. So the improvements come 
+measured using the criteria is the number of viewpoint recovery from grossly wrong estimation 
+only. This point was not explicit in the paper so we will add this point in our final paper.
 
-R1, RCNN + Ours: DPM-VOC+VP method templates are made from ground truth
-bounding boxes so the bounding boxes are more tight and informative compare to
-region based bounding boxes (RCNN). Our algorithm tries to handle such
-incorrect bounding boxes by creating HOG scale pyramid for the given bounding
-box but more accurate the bounding box is, better the performance. This effect
+R1, RCNN + Ours: DPM-VOC+VP method templates were made from ground truth
+bounding boxes so the bounding boxes tend to be tighter and more informative than
+the region based bounding boxes (RCNN). Our algorithm handles over/under 
+estimated bounding boxes by creating HOG scale pyramid but more accurate 
+the bounding box is, the better the performance. This effect
 is dominant for coarser viewpoint where RCNN and DPM-VOC+VP have similar
-performance.
+detection performance.
 
@@
 O(n log n) time complexity using DFT but the time complexity coefficient was
-too large and the non-zero pattern destroys the Toeplitz structure so we did
-not incorporated in our paper. We did not emphasize this point in detail
-[Sec.4] but will try to incorporate this point in the final version.
+too large and the non-zero pattern destroys the Toeplitz structure. We 
+did not fully explained the size of the matrix [Sec.4] but will try to 
+incorporate this point in the final version.
 
@@
 
-R3, Zia el al.: We thank the reviewer for point this out. We agree that Zia et
-al. tackles the similar problem. However, due to their complex model, their
-model requires accurate bounding box and viewpoint estimation. On the other
-hand, our method can work as a standalone detector and performs on par with
-many state-of-the-art detectors though the dataset is saturated as correctly
-pointed by [R1]. But we think this is a good comparison and we will add
-discussion and comparison with Zia et al on the final version.
+R3, Zia el al.: We thank the reviewer for pointing this out. We agree that Zia et
+al. tackles the similar problem. However, due to the complexity, their
+model requires accurate bounding box as well as viewpoint estimation as an 
+initialization. On the other hand, our method can work as a standalone detector 
+and performs on par with many state-of-the-art detectors on the 3D Object dataset
+though the dataset is saturated as correctly pointed out by [R1]. But we think 
+this is a good comparison and we will add comparison with Zia et al on the final version.
 
 We thank R2 for pointing out writing errors and missing references. Although
-our article is “well written”[R1] and “explains ... well”[R1], we also noticed
-the errors and fixed them including the ones pointed out by R2. We apologize
+our article is “well written”[R1] and “explains ... well”[R1], there were slipped errors
+which we fixed them including the ones pointed out by R2. We apologize
 for such mistakes.

### 2015-01-22 rebuttal/rebuttal.md
Spelling and grammar changes (some major)

@@
 
-R1.1 & [R2 one-time]: Our method proposed a way to fine tune the viewpoint in
-continuous space without expensive training thus providing vision community a
-modular framework for view estimation. However, caching all possible templates
-would be intractable and difficult to cover all continuous azimuth, elevation,
-in-plane rotation, focal length and intraclass CAD models. To overcome, our
+Caching Sigma inverse for the templates [R1, R2]: 
+We propose a way to fine tune the viewpoint in
+continuous space without expensive training, thus providing the vision community
+with a modular framework for viewpoint estimation. However, caching all the possible
+templates for continuous azimuth, elevation, in-plane rotation, focal length and
+intraclass CAD models is intractable. To overcome this, our
 method generates proposals on-the-fly which requires covariance inversion.
 
-R1 & R2, effectiveness of fine-tuning: The continuous viewpoint estimation not
-only recovers from wrong pose but also accurately refines the coarse viewpoint estimation.
-Unfortunately, the PASCAL 3D+ and 3D Object datasets only measures the number
-of correct viewpoint bins from bird-eye view. If a viewpoint estimation falls
-into the correct bin in the coarse estimation, the improvement from the
-fine-tuning cannot be measured using the metric. So the improvements come 
-measured using the criteria is the number of viewpoint recovery from grossly wrong estimation 
-only. This point was not explicit in the paper so we will add this point in our final paper.
+Effectiveness of fine-tuning [R1, R2]:
+Our continuous viewpoint estimation method not only accurately refines the coarse
+viewpoint estimation but also recovers from incorrect pose initializations.
+Unfortunately, the PASCAL 3D+ and 3D Object datasets only measure the number
+of correct viewpoint bins from bird-eye view. If the coarse viewpoint estimation
+falls into the correct bin, we cannot observe further refinement using this metric.
+Therefore, the improvements we present only represent the refinement of poses that
+are initially estimated incorrectly.
+This point was not explicit in the paper abd we will add it to our final paper.
 
@@
 
-R2, inversion time: Sigma is a covariance matrix of size (W x H x F) x (W x H x
-F) where W and H are the number of HOG cells in a row and a column, F is the
+Sigma inversion time [R2]:
+Sigma is a covariance matrix of size (W x H x F) x (W x H x F)
+where W and H are the number of HOG cells in a row and a column, and F is the
 dimension of HOG feature [Hariharan et al. 12]. In practice, we used
@@
 too large and the non-zero pattern destroys the Toeplitz structure. We 
-did not fully explained the size of the matrix [Sec.4] but will try to 
+did not fully explain the size of the matrix [Sec.4] but will
 incorporate this point in the final version.
 
-Second point raised by [R2] is that the sigma matrix product can be done in GPU
+The second point raised by [R2] is that the sigma matrix product can be done in GPU
 implementation. We think the reviewer meant matrix decomposition since we
 compared the matrix inversion time. We thank [R2] for correctly pointing this
-out and we will incorporate GPU implementation of Cholesky decomposition
+out and we will incorporate a GPU implementation of the Cholesky decomposition
 experiment in our final paper.
 
-R3, Zia el al.: We thank the reviewer for pointing this out. We agree that Zia et
+Related work from Zia el al. [R3]:
+We thank the reviewer for pointing this out. We agree that Zia et
 al. tackles the similar problem. However, due to the complexity, their
@@
 and performs on par with many state-of-the-art detectors on the 3D Object dataset
-though the dataset is saturated as correctly pointed out by [R1]. But we think 
-this is a good comparison and we will add comparison with Zia et al on the final version.
+(though the dataset is saturated as correctly pointed out by [R1]).
+We will add comparison with Zia et al on the final version.
 
-We thank R2 for pointing out writing errors and missing references. Although
-our article is “well written”[R1] and “explains ... well”[R1], there were slipped errors
-which we fixed them including the ones pointed out by R2. We apologize
-for such mistakes.
+We thank [R2] for pointing out writing errors and missing references. Although
+our article is “well written” [R1] and “explains ... well” [R1], some minor errors
+slipped through, which will of course be fixed in the final version.
+We apologize for such mistakes.
 
 We will try our best to incorporate all the remaining issues pointed out by the
-reviewers to the final paper should it be accepted.
+reviewers in the final paper should it be accepted.

### 2015-01-23 rebuttal/rebuttal.md
minor modification by chris

@@
 
-Caching Sigma inverse for the templates [R1, R2]: 
-We propose a way to fine tune the viewpoint in
+One-time calibration [R1, R2]: We propose a way to fine tune the viewpoint in
 continuous space without expensive training, thus providing the vision community
@@
 intraclass CAD models is intractable. To overcome this, our
-method generates proposals on-the-fly which requires covariance inversion.
+method generates proposals on-the-fly which requires covariance inversion on-the-fly.
 
-Effectiveness of fine-tuning [R1, R2]:
-Our continuous viewpoint estimation method not only accurately refines the coarse
+Effectiveness of fine-tuning [R1, R2]: Our continuous viewpoint estimation
+method not only accurately refines the coarse
 viewpoint estimation but also recovers from incorrect pose initializations.
@@
 falls into the correct bin, we cannot observe further refinement using this metric.
-Therefore, the improvements we present only represent the refinement of poses that
+Therefore, the improvements only represent the recovery of poses that
 are initially estimated incorrectly.
-This point was not explicit in the paper abd we will add it to our final paper.
+This point was not explicit in the paper and we will add it to our final paper.
 
-R1, RCNN + Ours: DPM-VOC+VP method templates were made from ground truth
+RCNN + Ours [R1]: DPM-VOC+VP method templates were made from ground truth
 bounding boxes so the bounding boxes tend to be tighter and more informative than
@@
 
-Sigma inversion time [R2]:
-Sigma is a covariance matrix of size (W x H x F) x (W x H x F)
+Sigma inversion time [R2]: Sigma is a covariance matrix of size (W x H x F) x (W x H x F)
 where W and H are the number of HOG cells in a row and a column, and F is the
@@
 
-Related work from Zia el al. [R3]:
-We thank the reviewer for pointing this out. We agree that Zia et
+Related work from Zia el al. [R3]: We thank the reviewer for pointing this out. We agree that Zia et
 al. tackles the similar problem. However, due to the complexity, their

### 2015-01-23 rebuttal/rebuttal.md
Jon's recommendations

@@
 continuous space without expensive training, thus providing the vision community
-with a modular framework for viewpoint estimation. However, caching all the possible
-templates for continuous azimuth, elevation, in-plane rotation, focal length and
+with a modular framework for viewpoint estimation. However, caching 
+templates for continuous azimuths, elevations, in-plane rotations, focal lengths and
 intraclass CAD models is intractable. To overcome this, our
-method generates proposals on-the-fly which requires covariance inversion on-the-fly.
+method generates templates on-the-fly which requires covariance inversion on-the-fly.
 
@@
 Unfortunately, the PASCAL 3D+ and 3D Object datasets only measure the number
-of correct viewpoint bins from bird-eye view. If the coarse viewpoint estimation
+of correct viewpoint bins from a bird’s-eye view. If the coarse viewpoint estimation
 falls into the correct bin, we cannot observe further refinement using this metric.
-Therefore, the improvements only represent the recovery of poses that
-are initially estimated incorrectly.
+Therefore, the improvements only represent the recoveries of poses from
+grossly wrong estimations.
 This point was not explicit in the paper and we will add it to our final paper.
 
-RCNN + Ours [R1]: DPM-VOC+VP method templates were made from ground truth
-bounding boxes so the bounding boxes tend to be tighter and more informative than
-the region based bounding boxes (RCNN). Our algorithm handles over/under 
+RCNN + Ours improvements [R1]: DPM-VOC+VP method templates were made from ground truth
+bounding boxes, so the bounding boxes tend to be tighter and more informative than
+the region-based bounding boxes (RCNN). Our algorithm handles over/under 
 estimated bounding boxes by creating HOG scale pyramid but more accurate 
@@
 dimension of HOG feature [Hariharan et al. 12]. In practice, we used
-high-resolution template and the resulting covariance matrix was around
+high-resolution templates, resulting in a covariance matrix size of about
 7000x7000 (~180MByte in single precision). Thus, using the Cholesky
-decomposition, it took more than 4 seconds on i7-4770K. To get extra speed up,
+decomposition, inversion took more than 4 seconds on i7-4770K. To get an extra speed-up,
 we also tried to make use of the Toeplitz-Block-Toeplitz structure and achieved
@@
 model requires accurate bounding box as well as viewpoint estimation as an 
-initialization. On the other hand, our method can work as a standalone detector 
+initialization. On the contrary, our method works also as a standalone detector 
 and performs on par with many state-of-the-art detectors on the 3D Object dataset
@@
 reviewers in the final paper should it be accepted.
+
+Total: 3971/4000 Character
+
+----------------------Reviews not incorporated------------------------
+From R1
+“The work relies on using realistic (with texture) 3D models. This limits the applicability where such rich models are not available.”
+“The proposed technique relies on a large number of templates, and their evaluation at many scales.”
+
+From R2
+“concerns about the reality of the speed-up” -- do some rough calculation about the naive approach to directly show the speedup of your method
+“limited experiments”
+
+From R3
+“a little more background on WHO could be given”
+“could be tested on KITTI”
+“missing baseline”

### 2015-01-26 rebuttal/rebuttal.md
added michaels' suggestions

@@
-We appreciate the valuable comments from all the reviewers. We are happy to
-hear reviewers agree on that we proposed “efficient”[R2,R3] and “considerable
-improvements to WHO”[R1] in terms of “speed”[R1,R3] and “detection
-performance”[R1]. The method was “well motivated”  and validated with
-“extensive experiments”[R1].
+We appreciate the valuable comments from all the reviewers.
+We are happy to hear reviewers agree on that we proposed “efficient”[R2,R3] and “considerable improvements to WHO”[R1] in terms of “speed”[R1,R3] and “detection performance”[R1].
+The method was “well motivated”  and validated with “extensive experiments”[R1].
 
-One-time calibration [R1, R2]: We propose a way to fine tune the viewpoint in
-continuous space without expensive training, thus providing the vision community
-with a modular framework for viewpoint estimation. However, caching 
-templates for continuous azimuths, elevations, in-plane rotations, focal lengths and
-intraclass CAD models is intractable. To overcome this, our
-method generates templates on-the-fly which requires covariance inversion on-the-fly.
+Contribution & caching templates [R1, R2]: Contribution in our paper is threefold: 1.
+WHO whitening speedup, 2.
+bypassing the expensive calibration stage with NZ-WHO, 3.
+on-the-fly template learning for continuous viewpoint estimation.
+These novelties enable us to generate rendering and learn calibrated template on-the-fly that makes MCMC procedure tractable.
+Thus we fine tune the viewpoint in continuous space without expensive training nor calibration, thus providing the vision community with a modular framework for continuous viewpoint estimation.
+Otherwise it would be intractable to cache and calibrate templates for continuous azimuths, elevations, in-plane rotations, focal lengths and intraclass CAD models.
 
-Effectiveness of fine-tuning [R1, R2]: Our continuous viewpoint estimation
-method not only accurately refines the coarse
-viewpoint estimation but also recovers from incorrect pose initializations.
-Unfortunately, the PASCAL 3D+ and 3D Object datasets only measure the number
-of correct viewpoint bins from a bird’s-eye view. If the coarse viewpoint estimation
-falls into the correct bin, we cannot observe further refinement using this metric.
-Therefore, the improvements only represent the recoveries of poses from
-grossly wrong estimations.
-This point was not explicit in the paper and we will add it to our final paper.
+Effectiveness of fine-tuning [R1, R2]: Our continuous viewpoint estimation method not only accurately refines the coarse viewpoint estimation but also recovers from incorrect pose initializations.
+Unfortunately, the PASCAL 3D+ and 3D Object datasets only measure the number of correct viewpoint bins from a bird’s-eye view.
+If the coarse viewpoint estimation falls into the correct bin, we cannot observe further refinement using this metric.
+Therefore, the improvements only represent the recoveries of poses from grossly wrong estimations.
 
-RCNN + Ours improvements [R1]: DPM-VOC+VP method templates were made from ground truth
-bounding boxes, so the bounding boxes tend to be tighter and more informative than
-the region-based bounding boxes (RCNN). Our algorithm handles over/under 
-estimated bounding boxes by creating HOG scale pyramid but more accurate 
-the bounding box is, the better the performance. This effect
-is dominant for coarser viewpoint where RCNN and DPM-VOC+VP have similar
-detection performance.
+RCNN + Ours improvements [R1]: DPM-VOC+VP method templates were made from ground truth bounding boxes, so the bounding boxes tend to be tighter and more informative than the region-based bounding boxes (RCNN).
+Our algorithm handles over/under estimated bounding boxes by creating HOG scale pyramid but more accurate the bounding box is, the better the performance.
+This effect is dominant for coarser viewpoint where RCNN and DPM-VOC+VP have similar detection performance.
 
-Sigma inversion time [R2]: Sigma is a covariance matrix of size (W x H x F) x (W x H x F)
-where W and H are the number of HOG cells in a row and a column, and F is the
-dimension of HOG feature [Hariharan et al. 12]. In practice, we used
-high-resolution templates, resulting in a covariance matrix size of about
-7000x7000 (~180MByte in single precision). Thus, using the Cholesky
-decomposition, inversion took more than 4 seconds on i7-4770K. To get an extra speed-up,
-we also tried to make use of the Toeplitz-Block-Toeplitz structure and achieved
-O(n log n) time complexity using DFT but the time complexity coefficient was
-too large and the non-zero pattern destroys the Toeplitz structure. We 
-did not fully explain the size of the matrix [Sec.4] but will
-incorporate this point in the final version.
+Calibration time [R1]: Yes, the calibration is a one-time process for each template.
+We followed the standard calibration technique [Aubry 14] and used 200k random negative patches for each template.
+The method calibrates each template independently.
 
-The second point raised by [R2] is that the sigma matrix product can be done in GPU
-implementation. We think the reviewer meant matrix decomposition since we
-compared the matrix inversion time. We thank [R2] for correctly pointing this
-out and we will incorporate a GPU implementation of the Cholesky decomposition
-experiment in our final paper.
+Sigma inversion time [R2]: To enable on-the-fly template generation, we had to dramatically speed up the covariance inversion time and remove the calibration stage while maintaining the performance.
+Sigma is a covariance matrix of size (W x H x F) x (W x H x F) [Hariharan et al.
+12] and is unique for each aspect ratio and foreground mask [Sec.
+4.3].
+In practice, we used high-resolution templates, resulting in a covariance matrix size of about 7000x7000 (~180MByte in single precision).
+Thus, it took ~4 seconds on i7-4770K to inverse matrix using the Cholesky decomposition.
+Also the sigma matrix is unique for a template size and foreground mask.
 
-Related work from Zia el al. [R3]: We thank the reviewer for pointing this out. We agree that Zia et
-al. tackles the similar problem. However, due to the complexity, their
-model requires accurate bounding box as well as viewpoint estimation as an 
-initialization. On the contrary, our method works also as a standalone detector 
-and performs on par with many state-of-the-art detectors on the 3D Object dataset
-(though the dataset is saturated as correctly pointed out by [R1]).
+The second point raised by [R2] is that the sigma matrix product can be done on GPU.
+We think the reviewer meant matrix decomposition since matrix product has been done on GPU using FFT and we compared the matrix inversion time only.
+We thank [R2] for correctly pointing this out and we will incorporate a GPU implementation of the Cholesky decomposition experiment in our final paper.
+
+Related work from Zia et al.
+[R3]: We thank the reviewer for pointing this out.
+We agree that Zia et al.
+tackles the similar problem.
+However, due to the complexity, their model requires accurate bounding box as well as viewpoint estimation as an initialization.
+On the contrary, our method works also as a standalone detector and performs on par with many state-of-the-art detectors on the 3D Object dataset (though the dataset is saturated as correctly pointed out by [R1]).
 We will add comparison with Zia et al on the final version.
 
-We thank [R2] for pointing out writing errors and missing references. Although
-our article is “well written” [R1] and “explains ... well” [R1], some minor errors
-slipped through, which will of course be fixed in the final version.
+2 Classes [R2]: Unlike [Zia et al.
+PAMI 13](car,bike), [Hejrati el al.
+CVPR14](car) and [Fidler et al.
+NIPS12](car,box) we used the car class in PASCAL challenge that varies from a racing car to a truck so the class represents strong intraclass variation.
+Also, our bicycle class exhibits similar intraclass variability that ranges from three-wheeled bicycles to acrobatic BMX bicycles.
+We think that the classes are commonly found and real-world applications yet include strong intraclass variability and drastic viewpoints.
+
+Saturated 3D Object [R1]: The AP results reported on Table 2 show some degree of saturation.
+However MPPE results show that it is still a challenging task and it evaluates the performance fairly since the dataset contains 480 images of cars from various poses and scales.
+Also the Table 2 has yet another significance that learning from synthetic images can be applied to real images.
+Also the qualitative results on Figure 7 on the paper and Figure 3.
+and 4 on the supplementary material are from the dataset and show that our algorithm can actually estimate 3D viewpoint accurately whereas other algorithms can only estimate rough geometry.
+
+We thank [R2] for pointing out writing errors and missing references.
+Although our article is “well written” [R1] and “explains ...
+well” [R1], some minor errors slipped through, which will of course be fixed in the final version.
 We apologize for such mistakes.
 
-We will try our best to incorporate all the remaining issues pointed out by the
-reviewers in the final paper should it be accepted.
+We will try our best to incorporate all the remaining issues pointed out by the reviewers in the final paper should it be accepted.
 
-Total: 3971/4000 Character
+5457/4000 character
+
+-------------------------------------------------------------------------
+
+- R2's comment of lack of novelty: we have to strongly argue against that!
+we do have plenty of novelty, the most important one being the introduction of the on-the-fly rendering + template learning idea, that makes the MCMC procedure tractable!
+nobody has done that before!
+
+- R2's concern about the speedup of WHO: 'why do we consider the inversion time at all' is not addressed!
+I can't see 'almost 4 seconds' in Tab.
+1.
+also, our crucial argument is about the fact that we don't need _calibration_ in order to get good performance, and the speedup w/o considering calibration is not even very relevant?
+
+- R2: we have to argue that making progress on 2 classes is already valuable (and give plenty of references that do that)
+
+- R1's question about 1-time-calibration: is this incorporated in Tab. 1?
+that's his question, so 'yes'!
+also, we have to argue that this in fact _not_ a 1-time-thing, but has to be repeated for templates of different sizes (as they arise all the time in our on-the-fly setting - we don't even know the dimensions beforehand)!
+
+- R1's comment about the significance of the saturated results
 

### 2015-01-27 rebuttal/rebuttal.md
Sam

@@
 We appreciate the valuable comments from all the reviewers.
-We are happy to hear reviewers agree on that we proposed “efficient”[R2,R3] and “considerable improvements to WHO”[R1] in terms of “speed”[R1,R3] and “detection performance”[R1].
-The method was “well motivated”  and validated with “extensive experiments”[R1].
+We're pleased that reviewers agreed our proposed method was “efficient”[R2,R3],  “well motivated”[R1], and validated with “extensive experiments”[R1], as well as demonstrating “considerable improvements to WHO”[R1] in terms of “speed”[R1,R3] and “detection performance”[R1].
 
+Lack of novelty [R2]: we are quite surprised about R2’s ‘strong reject’ assessment due to missing novelty.
+We believe that both the main conceptual innovations of our paper: 1) training E-LDA template models on-the-fly from rendered CAD data, and 2) removing the need for calibration and speeding up WHO, are significant novel contributions.
+R1 believes they have the potential to ‘affect the broader recognition community as a whole’.
+Furthermore, we demonstrate how to exploit on-the-fly rendering and training for continuous viewpoint estimation using MCMC, which would be computationally prohibitive using offline training.
+
+\begin{comment}
 Contribution & caching templates [R1, R2]: Contribution in our paper is threefold: 1.
@@
 Otherwise it would be intractable to cache and calibrate templates for continuous azimuths, elevations, in-plane rotations, focal lengths and intraclass CAD models.
+\end{comment}
+
+Number of templates [R1]: We partly agree.
+It is the problem inherent to all template-based-matching algorithm.
+However, we can reduce the number templates while maintaining the performance since we first use sparse viewpoints to initialize viewpoint and further optimize viewpoint continuously on-the-fly.
 
@@
 
-Calibration time [R1]: Yes, the calibration is a one-time process for each template.
+Calibration time [R1]: Yes, the calibration is a one-time process for each template (second column of Table.2).
 We followed the standard calibration technique [Aubry 14] and used 200k random negative patches for each template.
@@
 Thus, it took ~4 seconds on i7-4770K to inverse matrix using the Cholesky decomposition.
-Also the sigma matrix is unique for a template size and foreground mask.
 
@@
 CVPR14](car) and [Fidler et al.
-NIPS12](car,box) we used the car class in PASCAL challenge that varies from a racing car to a truck so the class represents strong intraclass variation.
-Also, our bicycle class exhibits similar intraclass variability that ranges from three-wheeled bicycles to acrobatic BMX bicycles.
-We think that the classes are commonly found and real-world applications yet include strong intraclass variability and drastic viewpoints.
+NIPS12](car,box) we used the PASCAL challenge car class which exhibits large intraclass variation, from racing car to truck.
+Similarly, our bicycle class ranges from three-wheeled bicycles to acrobatic BMX bicycles.
+These classes are commonly found in real-world applications and include variability in viewpoint and intraclass appearance that allow us to fairly evaluate our method.
 
@@
 
-We will try our best to incorporate all the remaining issues pointed out by the reviewers in the final paper should it be accepted.
+6223/4000
 
-5457/4000 character
+-------------------------------------------------------------------------
+
+R1's comments:
+* Number of template evaluations [R1]: what do we want to say here? ...
+* calibration time _per image_  [R1] - what are the runtimes reported in table 2? are they per image? if so, does _each of these_ runtimes contain the calibration time (I hope not)?
+* in Tab. 3, I don't really see a difference in the performance of DPM-VOC-VP + fine-tuning and the corresponding RCNN-method - or am I missing something?
 

### 2015-01-27 rebuttal/rebuttal.md
added recommendations TODO from Michael

@@
 
-Effectiveness of fine-tuning [R1, R2]: Our continuous viewpoint estimation method not only accurately refines the coarse viewpoint estimation but also recovers from incorrect pose initializations.
+Effectiveness of fine-tuning [R1, R2], at crude viewpoints[R1]: Our continuous viewpoint estimation method not only accurately refines the coarse viewpoint estimation but also recovers from incorrect pose initializations.
 Unfortunately, the PASCAL 3D+ and 3D Object datasets only measure the number of correct viewpoint bins from a bird’s-eye view.
@@
 
-Calibration time [R1]: Yes, the calibration is a one-time process for each template (second column of Table.2).
+Calibration time [R1]: Calibration is a one-time process during the training training per and we reported the time to generated each calibrated template (last column of Table.2).
 We followed the standard calibration technique [Aubry 14] and used 200k random negative patches for each template.
@@
 
-Sigma inversion time [R2]: To enable on-the-fly template generation, we had to dramatically speed up the covariance inversion time and remove the calibration stage while maintaining the performance.
+Sigma inversion time [R2]: ADD IMPORTANCE OF SKIPPING CALIBRATION.
+To enable on-the-fly template generation, we had to dramatically speed up the covariance inversion time and remove the calibration stage while maintaining the performance.
 Sigma is a covariance matrix of size (W x H x F) x (W x H x F) [Hariharan et al.
@@
 Thus, it took ~4 seconds on i7-4770K to inverse matrix using the Cholesky decomposition.
+FOR THIS LARGE TEMPLATE, 0.1s is FAST.
 
@@
 We apologize for such mistakes.
+
+We will try our best to incorporate all the remaining issues pointed out by the reviewers in the final paper should it be accepted.
 

### 2015-03-25 rebuttal/rebuttal.md
Added selector matrix $S$ that generates $x', \mu', \Sigma'$.

@@
 
+------------------------------------------------------------------
+
+We appreciate the valuable comments from all the reviewers.
+We're pleased that reviewers agreed our proposed method was “efficient”[R2,R3], “well motivated”[R1], and validated with “extensive experiments”[R1], as well as demonstrating “considerable improvements to WHO”[R1] in terms of “speed”[R1,R3] and “detection performance”[R1].
+
+We believe that the main novelties of our parer are: 1) simultaneously rendering and training a template on-the-fly in real time, 2) removing the need for calibration, and introducing the Conjugate Gradient method for WHO computation which yields superior timing and residuals, 3) continuous viewpoint and focal length estimation using on-the-fly template generation and validation.
+We concur that our work has a "nice contribution"[R3] and has the potential to "affect the broader recognition community as a whole"[R1]
+
+Detailed questions in order:
+
+R1:
+
+Number of templates: we agree that the number of template evaluation is, in principle, a computational bottleneck of template-based methods.
+In our work, we address it by adaptively choosing which template to train (and successively evaluate) online, at recognition time, as part of our MCMC fine-tuning.
+
+Effectiveness of fine-tuning: the Average Viewpoint Precision (AVP) discretize azimuth into n bins to evaluate viewpoint estimation performance.
+Thus, for coarser viewpoints, the viewpoint bins get wider so the improvement from fine-tuning can hardly be measured.
+
+Calibration time: the timings reported on the last column of Tab.
+1 are per learned template and do indeed include the calibration times.
+Each template is calibrated exactly once, independently, using the technique from [Aubry et al.
+CVPR'14] on 200k random negative patches.
+
+Saturation of results: we agree that results are beginning to saturate on the 3D Object Classes dataset, but we believe it is still valuable due to its controlled conditions (viewpoint annotations, balanced number of images per object instance and viewpoint).
+Furthermore, we are achieving close to state-of-the-art performance using exclusively synthetic training data.
+
+R2:
+
+Improvement of WHO computation: we would like to clarify three points: 1) the main speedup of our method results from avoiding the need for calibration as well as the fast matrix inversion, 2) covariance (sigma) matrix inversion is a one-time operation, but has to be done independently for each template since the aspect ratios and the foreground pattern of a template is unique thus the matrix cannot be shared, and there is no gain from caching the matrix, 3) the non-negligible run time is an effect of our high resolution templates (resulting in sigma matrix of size about 7000x7000 entries, 180 MByte in single precision).
+
+Sparse GPU matrix product: since we did in fact implement the matrix product on the GPU in FFT-space (Sect.
+4.5) we believe the question might address the Cholesky decomposition on GPU.
+We will add a corresponding timing comparison to Tab.
+1.
+
+2 classes: in line with prior work [Aubry et al.
+CVPR'14] (chair), [Hejrati et al.
+CVPR'14] (car,box), [Zia et al.
+PAMI'13] (car,bike), [Fidler et al.
+NIPS'12] (car,box), and numerous others, we believe that making progress on selected classes can be a valuable contribution.
+Unfortunately, the CAD models shipped with Pascal 3D+ are not suitable for rendering, so we acquired models from a third party.
+We are currently collecting CAD models from other sources to enable more diverse experiments.
+
+R3:
+
+Relation to [Zia et al.
+PAMI'13]: their work learns a coarse, parametric shape model from hand-annotated CAD models and needs a strong initialization from an existing detector, while our method directly provides CAD model alignments without human intervention and can be run as a standalone detector, resulting in performance on par with state-of-the-art (Tab.
+1).
+We are of course happy to include the reported results on 3D Object Classes in Tab.
+1 in the final version.
+
 -------------------------------------------------------------------------

### 2015-03-25 approach.tex
Added selector matrix $S$ that generates $x', \mu', \Sigma'$.

@@
 
-We used a public rendering engine to create realistic rendering and
-depth. We used CAD models that contain color, texture and material information such as
-transparency and reflectance to make the rendering as much realistic
-as possible to simulate the natural image statistics. The example rendering is
-in Fig. \ref{fig:rendering}. We also extracted depth information as well while
-rendering to use in the reconstruction.
+We used an off-the-shelf rendering engine that can create a realistic rendering and
+a depth map. The CAD models we used contain color, texture and material information such as
+transparency and reflectance to make the rendering as realistic
+as possible to simulate the natural image statistics. An rendering example that we used in our experiments is
+in Fig. \ref{fig:rendering}. Along with a rendering, we extracted a depth map which can later 
+be used for reconstruction.
 
-We used a collection of CAD models to make exemplar renderings of CAD models and for viewpoints. The
-CAD models are cached so that when we fine-tune 2D-3D matching, so it can be rendered instantaneously.
-We made the renderings to change focal length and yaw, pitch, roll so that we can fine tune the matching
-continuously.
+To handle intraclass variability, we used various CAD models (sedan, truck, racing car, hatchback etc) to cover intraclass variability and made renderings of these CAD models for various viewpoints.
+The
+CAD models were cached so that when we fine-tune 2D-3D matching, we can render the model instantaneously.
+Our renderer can continuously vary yaw, pitch, roll and the focal length as well so that the final fine tuning stage produces accurate the continuous viewpoint, a focal length and a bounding box.
 
@@
 \label{sec:who}
-Our technique for rendering and training template detectors on-the-fly
+Our technique for rendering and generating exemplar template detectors on-the-fly
 is drawing from recent work. Hariharan \etal. introduced Whitened Histograms of Orientations (WHO)
@@
 processing operation for decorrelating a set of random variables
-
 \cite{Martinsson05, Belouchrani00}. More formally, suppose that we have a
@@
 whitening the signal,
+
 \begin{equation}
@@
 \end{equation}
-we remove 2nd order correlation between all features. Since collecting covariance matrix for every template shape
- is expensive, \cite{Hariharan12} proposed easy way to synthesize
+
+we remove 2nd order correlation between all features. Since collecting covariance
+matrix for every template shape is expensive, \cite{Hariharan12} proposed an easy
+way to synthesize
 covariance $\Sigma$ from autocovariance $\Gamma$ and we followed their
@@
 NZ-WHO removes these artifacts so that the background has no effect on the
-template response. Let $T$ be the feature extraction transformation and $p$ be
-the rendering setting (see Sect.~\ref{sec:fine}). Given HOG features $x=T(I_r)$
-from rendering image $I_r$, we create a new vector $x'$ which
-contains only the non-zero elements of $x$. We select the corresponding elements of
-$\mu$ to produce $\mu'$, while the autocovariance lookup is only performed for
-the cells with non-zero gradient, producing $\Sigma'$ corresponding to the
-features in $x'$. After solving the resulting system (which is now smaller than
+template response. Let a vectorized HOG features of a rendering image $x\in
+\mathcal{R}^{nd}$ be $x=T_f(I_r)$ where $n$ is the number HOG cells and $d$ be
+the dimension of HOG feature. We create a new vector $x'$ which contains only
+the non-zero elements of $x$. To be specific, let $I_d\in \mathcal{R}^{d\times
+    d}$ be the identity matrix, $n'$ be the number of non-zero HOG cells, and a
+matrix $S\in \mathcal{R}^{n'd \times nd}$ be the masking matrix that selects
+non-zero HOG cell. For instance, a template has  $n=3, n'=2$, and only the
+second HOG cell has $0$ norm, then
+
+\begin{align}
+S = \left[ \begin{array}{ccc}
+        I_d & \mathbf{0} & \mathbf{0}\\
+        \mathbf{0} & \mathbf{0} & I_d
+        \end{array} \right]
+\end{align}
+
+Then, we can define $x' = S x, \mu' = S\mu, \Sigma' = S \Sigma S^T$.
+After solving the resulting system (which is now smaller than
 in the WHO approach) we find
@@
 w'=\Sigma'^{-1}(x' - \mu') \label{eq:nz-who},
-\end{equation}which we reassemble into the final NZ-WHO template $w$ by
-replacing the non-zero elements of $x$ with the corresponding $w'$ element.
+\end{equation}
+
+which we restore zero cells and reshape the vector into the final NZ-WHO
+template that has the same dimension as the original HOG template.
 
@@
 
-As a result, a GPU implementation of conjugate gradient converges in 50
+As a result, a GPU implementation of conjugate gradient converges in 80
 ms when using 250 HOG cells, two orders of magnitude faster than the using
@@
 several hundred cells, while using the iterative Conjugate Gradient
-method, it only takes 100ms. If we use NZ-WHO, we can gain extra speed
+method, it only takes 80ms. If we use NZ-WHO, we can gain extra speed
 up since we only whitens non-zero cells.

### 2015-03-25 egpaper_final.tex
Added selector matrix $S$ that generates $x', \mu', \Sigma'$.

@@
 \graphicspath{ {figures/} }
-% \cvprfinalcopy % *** Uncomment this line for the final submission
+\cvprfinalcopy % *** Uncomment this line for the final submission
 
@@
 
-\author{First Author\\
-Institution1\\
-Institution1 address\\
-{\tt\small firstauthor@i1.org}
+\author{Christopher B. Choy, Michael Stark, Sam Corbett-Davies, Silvio Savarese\\
+    Stanford University, Max Plank Institutes\\
+    {\tt\small \{chrischoy, scorbett, stark, ssilvio\}@stanford.edu}
 % For a paper whose authors are all at the same institution,
@@
 % To save space, use either the email address or home page, not both
-\and
-Second Author\\
-Institution2\\
-First line of institution2 address\\
-{\tt\small secondauthor@i2.org}
 }

### 2015-03-28 approach.tex
approach change

@@
 
-We used an off-the-shelf rendering engine that can create a realistic rendering and
-a depth map. The CAD models we used contain color, texture and material information such as
-transparency and reflectance to make the rendering as realistic
-as possible to simulate the natural image statistics. An rendering example that we used in our experiments is
-in Fig. \ref{fig:rendering}. Along with a rendering, we extracted a depth map which can later 
-be used for reconstruction.
+We used an off-the-shelf rendering engine that can create a realistic rendering
+and a depth map. The CAD models we used contain color, texture and material
+information such as transparency and reflectance to make the rendering as
+realistic as possible to simulate the natural image statistics. An rendering
+example that we used in our experiments is in Fig. \ref{fig:rendering}. Along
+with a rendering, we extracted a depth map which can later be used for
+reconstruction.
 
-To handle intraclass variability, we used various CAD models (sedan, truck, racing car, hatchback etc) to cover intraclass variability and made renderings of these CAD models for various viewpoints.
-The
-CAD models were cached so that when we fine-tune 2D-3D matching, we can render the model instantaneously.
-Our renderer can continuously vary yaw, pitch, roll and the focal length as well so that the final fine tuning stage produces accurate the continuous viewpoint, a focal length and a bounding box.
+To handle intraclass variability, we used various CAD models (sedan, truck,
+racing car, hatchback etc) to cover intraclass variability and made renderings
+of these CAD models from various viewpoints. The CAD models were cached so that
+when we fine-tune 2D-3D matching, we can render the model instantaneously. Our
+renderer can continuously vary yaw, pitch, roll and the focal length as well so
+that the final fine tuning stage produces accurate the continuous viewpoint, a
+focal length and a bounding box.
 
@@
 \label{sec:who}
-Our technique for rendering and generating exemplar template detectors on-the-fly
-is drawing from recent work. Hariharan \etal. introduced Whitened Histograms of Orientations (WHO)
-\cite{Hariharan12}, which uses feature statistics from natural images to whiten HOG
-templates, making them more discriminative. Whitening is a common signal
-processing operation for decorrelating a set of random variables
-\cite{Martinsson05, Belouchrani00}. More formally, suppose that we have a
-$k$-dimensional random variable $X \in \mathcal{R}^k$ with $Cov(X)=\Sigma$. By
-whitening the signal,
+Our technique for rendering and generating exemplar template detectors
+on-the-fly is drawing from recent work. Hariharan \etal. introduced Whitened
+Histograms of Orientations (WHO), which uses feature statistics from natural
+images to create a large number of classifiers analytically using Linear
+Discriminant Analysis(LDA) rather than training SVM
+classifiers\cite{Hariharan12}. The confidence score for data $x_i$ can be defined as
 
-\begin{equation}
-\tilde{X}=\Sigma^{-\frac{1}{2}}(X - E[X]) \label{eq:whitening},
-\end{equation}
+\begin{align}
+    S(x_i) = w_{x_t}^T x_i
+\end{align}
 
-we remove 2nd order correlation between all features. Since collecting covariance
-matrix for every template shape is expensive, \cite{Hariharan12} proposed an easy
-way to synthesize
-covariance $\Sigma$ from autocovariance $\Gamma$ and we followed their
-method to generate $\Sigma$.
+where $w_{x_t} = \Sigma^{-1} (x_t - \mu)$ is a LDA classifier for a template $x_t$.
+
+% \begin{align}
+%     S(x_i) = w_{x_t}^T x_i\\
+%     w_{x_t} = \Sigma^{-1} (x_t - \mu)
+% \end{align}
+
+% The advantage of the approach is twofold: (a) you do not need a large number of
+% training and hard negative mining \cite{Felzenszwalb10} (b) it takes a fraction
+% of time generate (train) a discriminative template.
+
+% templates, making them more discriminative. Whitening is a common signal
+% processing operation for decorrelating a set of random variables
+% \cite{Martinsson05, Belouchrani00}. More formally, suppose that we have a
+% $k$-dimensional random variable $X \in \mathcal{R}^k$ with $Cov(X)=\Sigma$. By
+% whitening the signal,
+% 
+% \begin{equation}
+% \Phi(X)=\Sigma^{-\frac{1}{2}}(X - E[X]) \label{eq:whitening}
+% \end{equation}
+% 
+% we remove 2nd order correlation between all features. Since collecting covariance
+% matrix for every template shape is expensive, \cite{Hariharan12} proposed an easy
+% way to synthesize
+% covariance $\Sigma$ from autocovariance $\Gamma$ and we followed their
+% method to generate $\Sigma$.
 
@@
 
-% Since collecting covariance matrix for every template shape
-%  is expensive, \cite{Hariharan12} proposed easy way to synthesize
-% covariance $\Sigma$ from autocovariance $\Gamma$ and we followed their
-% method to generate $\Sigma$.
+Since collecting second order statistics to generate a covariance matrix for
+every template shape is expensive, \cite{Hariharan12} proposed easy way to
+synthesize covariance $\Sigma$. The method \cite{Hariharan12} assumes
+Wide-Sense Stationarity(WSS) of HOG features generated from natural images.
+Assumption they made was that the mean $\mu$ and autocovariance $\Gamma$ of HOG
+features do not vary with respect to the location. In this paper, we followed
+their method to generate $\Sigma$.
+
+% is independent of its place in the image, and the autocovariance of cells
+% depends only on their relative location.
 
@@
 % the correlation within signal (whitening).
-
-% In \cite{Hariharan12}, the authors compute the mean and covariance matrix by assuming Wide-Sense Stationarity (WSS) of HOG features
-% generated from natural images. That is, they assume the mean of a HOG cell is
-% independent of its place in the image, and the autocovariance of cells depends
-% only on their relative location.
 
@@
 NZ-WHO removes these artifacts so that the background has no effect on the
-template response. Let a vectorized HOG features of a rendering image $x\in
-\mathcal{R}^{nd}$ be $x=T_f(I_r)$ where $n$ is the number HOG cells and $d$ be
+template response. Let a vectorized HOG features of a rendering image $x = [ \begin{array}{ccccc}x_1^T & x_2^T & \cdots & x_n^T\end{array} ]^T \in
+\mathcal{R}^{nd}$ where $x_i$ is the $i$th HOG cell feature and $n$ is the number HOG cells and $d$ is
 the dimension of HOG feature. We create a new vector $x'$ which contains only
-the non-zero elements of $x$. To be specific, let $I_d\in \mathcal{R}^{d\times
+the non-zero HOG cell features of $x$. To be specific, let $I_d\in \mathcal{R}^{d\times
     d}$ be the identity matrix, $n'$ be the number of non-zero HOG cells, and a
 matrix $S\in \mathcal{R}^{n'd \times nd}$ be the masking matrix that selects
-non-zero HOG cell. For instance, a template has  $n=3, n'=2$, and only the
+non-zero HOG cells. For instance, a template has  $n=3, n'=2$, and only the
 second HOG cell has $0$ norm, then
@@
 
-Then, we can define $x' = S x, \mu' = S\mu, \Sigma' = S \Sigma S^T$.
+The matrix selects HOG features that corresponds to the first cell and the third cell.
+Using the selector $S$, we can define new vectorized HOG features $x' = S x, \mu' = S\mu, \Sigma' = S \Sigma S^T$.
 After solving the resulting system (which is now smaller than

### 2015-03-30 approach.tex
Major approach modification don. minor mcmc and overview
Approach major whiten to LDA update
MCMC minor math update
experiment, major PASCAL12 table to scriptsize

@@
 
-We used an off-the-shelf rendering engine that can create a realistic rendering
-and a depth map. The CAD models we used contain color, texture and material
-information such as transparency and reflectance to make the rendering as
-realistic as possible to simulate the natural image statistics. An rendering
-example that we used in our experiments is in Fig. \ref{fig:rendering}. Along
-with a rendering, we extracted a depth map which can later be used for
-reconstruction.
+We used an off-the-shelf rendering engine to generate a realistic rendering
+and a depth map. The CAD models we used contain texture and material
+information. These make the rendering more realistic and allows us to transfer
+natural image statistics to rendered images. Along
+with a rendering, we extracted a depth map which can be used for
+reconstruction\ref{fig:rendering}.
 
-To handle intraclass variability, we used various CAD models (sedan, truck,
-racing car, hatchback etc) to cover intraclass variability and made renderings
-of these CAD models from various viewpoints. The CAD models were cached so that
-when we fine-tune 2D-3D matching, we can render the model instantaneously. Our
-renderer can continuously vary yaw, pitch, roll and the focal length as well so
-that the final fine tuning stage produces accurate the continuous viewpoint, a
-focal length and a bounding box.
+To handle intraclass and viewpoint variability, we used various CAD models and
+made renderings of these CAD models from different viewpoints.  Note that we
+continuously vary yaw, pitch, roll and the focal length as well so that the
+final fine tuning stage can produce accurate viewpoint estimations
+(Sect.~\ref{sec:fine}).
 
@@
 Discriminant Analysis(LDA) rather than training SVM
-classifiers\cite{Hariharan12}. The confidence score for data $x_i$ can be defined as
+classifiers\cite{Hariharan12}. The confidence score for data $x_i$ can be
+defined as $ S(x_i) = w_{x_t}^T x_i$ where $w_{x_t} = \Sigma^{-1} (x_t - \mu)$
+is an LDA classifier for a template $x_t$. Since collecting covariance matrices
+for all possible template shape is intractable, \cite{Hariharan12} assumed
+Wide-Sense Stationarity(WSS) of HOG features and generated a covariance
+$\Sigma$ from autocovariance $\Gamma$ collected on a large collection of
+natural images. i.e. for a 31 dim HOG feature $x_t$ at location $t$
 
 \begin{align}
-    S(x_i) = w_{x_t}^T x_i
+    E[x_t] & = \mu\\
+    E[(x_{t} - \mu ) (x_{\tau} - \mu)] & = E[(x_0 - \mu)(x_{\tau - t} - \mu)]
 \end{align}
 
-where $w_{x_t} = \Sigma^{-1} (x_t - \mu)$ is a LDA classifier for a template $x_t$.
+In this paper, we followed their method to generate $\Sigma$.
 
@@
 
-Since collecting second order statistics to generate a covariance matrix for
-every template shape is expensive, \cite{Hariharan12} proposed easy way to
-synthesize covariance $\Sigma$. The method \cite{Hariharan12} assumes
-Wide-Sense Stationarity(WSS) of HOG features generated from natural images.
-Assumption they made was that the mean $\mu$ and autocovariance $\Gamma$ of HOG
-features do not vary with respect to the location. In this paper, we followed
-their method to generate $\Sigma$.
-
 % is independent of its place in the image, and the autocovariance of cells
@@
 \label{sec:nzwho}
-Our first innovation is `Non-Zero' whitening. When synthesizing detection
+Our first improvement is `Non-Zero' whitening. When synthesizing detection
 templates from rendered images, a common problem is how to handle the
 background. If the model is rendered over a natural image background, gradients
-in the background will be incorporated into the discriminative template,
-potentially causing false-positives if background elements exist in the query
-image.
+in the background will be incorporated into the discriminative template.
 
@@
 Fig.~\ref{fig:rendering}), whitening the resulting HOG template
-will produce undesirable background artifacts. These are created when centering
-the template (by subtracting the mean $\mu$), where strong negative weights are
-introduced in the textureless region (as seen in Fig.~\ref{fig:whocomparison}).
+, strong negative weights are introduced in the textureless region (by
+subtracting the mean $\mu$) as seen in Fig.~\ref{fig:whocomparison}.
 This could result in positive matches being suppressed due to spurious
@@
 NZ-WHO removes these artifacts so that the background has no effect on the
-template response. Let a vectorized HOG features of a rendering image $x = [ \begin{array}{ccccc}x_1^T & x_2^T & \cdots & x_n^T\end{array} ]^T \in
-\mathcal{R}^{nd}$ where $x_i$ is the $i$th HOG cell feature and $n$ is the number HOG cells and $d$ is
-the dimension of HOG feature. We create a new vector $x'$ which contains only
-the non-zero HOG cell features of $x$. To be specific, let $I_d\in \mathcal{R}^{d\times
-    d}$ be the identity matrix, $n'$ be the number of non-zero HOG cells, and a
-matrix $S\in \mathcal{R}^{n'd \times nd}$ be the masking matrix that selects
-non-zero HOG cells. For instance, a template has  $n=3, n'=2$, and only the
-second HOG cell has $0$ norm, then
+template response. Let a vectorized HOG features of a rendering image $x = [
+\begin{array}{ccccc}x_1^T & x_2^T & \cdots & x_n^T\end{array} ]^T \in
+\mathcal{R}^{nd}$ where $x_i$ is the $i$th HOG cell feature and $n$ is the
+number HOG cells and $d$ is the dimension of HOG feature. We create a new
+vector $\bar{x}$ which contains only the non-zero HOG cell features of $x$. To be
+specific, let $I_d\in \mathcal{R}^{d\times d}$ be the identity matrix, $\bar{n}$ be
+the number of non-zero HOG cells, and a matrix $S\in \mathcal{R}^{\bar{n}d \times
+    nd}$ be the masking matrix that selects non-zero HOG cells. For instance, a
+template has  $n=3, \bar{n}=2$, and only the second HOG cell has $0$ norm, then
 
@@
 The matrix selects HOG features that corresponds to the first cell and the third cell.
-Using the selector $S$, we can define new vectorized HOG features $x' = S x, \mu' = S\mu, \Sigma' = S \Sigma S^T$.
-After solving the resulting system (which is now smaller than
-in the WHO approach) we find
+
+Using the selector $S$, we can define new vectorized HOG features $\bar{x} = S x,
+\bar{\mu} = S\mu, \bar{\Sigma} = S \Sigma S^T$. After solving the resulting system (which
+is now smaller than in the WHO approach) we find
 
 \begin{equation}
-w'=\Sigma'^{-1}(x' - \mu') \label{eq:nz-who},
+    \bar{w}=\bar{\Sigma}^{-1}(\bar{x} - \bar{\mu}) \label{eq:nz-who},
 \end{equation}
 
-which we restore zero cells and reshape the vector into the final NZ-WHO
-template that has the same dimension as the original HOG template.
+To speed up the convolution, we restore zero cells and reshape the vector $\bar{w}$
+and compute convolution.
 
@@
 \label{sec:fastwhiten}
-Our second innovation lies in enhancing the computational efficiency
-of the whitening procedure, making it applicable to an on-the-fly
-rendering setting.
+% To speed up LDA synthesize, we introduced Conjugate Gradient method.
+% for solving the matrix inversion Eq.~\ref{eq:nz-who}.
+% This process speeds up , making it applicable to an on-the-fly rendering setting.
+% It originates from the insight that an iterative Conjugate Gradient method can be used to whiten a HOG template, which is much faster than the original procedure proposed in~\cite{Hariharan12} based on decomposition.
 
-It originates from the insight that an iterative
-Conjugate Gradient method can be used to whiten a HOG template, which
-is much faster than the original procedure proposed
-in~\cite{Hariharan12} based on decomposition.
-
-Whitening the non-zero
-feature vector $x'$ means a solving the system of linear equations, $\Sigma' w' = (x' -
-\mu')$. In
+Synthesizing an LDA template Eq.~\ref{eq:nz-who} requires solving the system of
+linear equations, $\bar{\Sigma} \bar{w} = (\bar{x} - \bar{\mu})$. In
 \cite{Hariharan12}, the authors make use of the fact that covariance matrices
@@
 %
-This makes Conjugate Gradient faster than decomposition for matrices with small condition
-numbers relative to their size.
+This makes Conjugate Gradient faster than decomposition for matrices with small
+condition numbers relative to their size.
 
 The covariance matrix for HOG templates is typically
-ill-conditioned\cite{Hariharan12}, but we
-can add a regularization constant to the diagonal to reduce its condition
-number to the point where the conjugate gradient method will converge quickly.
+ill-conditioned\cite{Hariharan12}, but adding a small regularization constant to
+the diagonal reduces its condition number.
 We use a constant of $0.15$, which reduces the condition number from $10^{20}$
@@
 
-As a result, a GPU implementation of conjugate gradient converges in 80
-ms when using 250 HOG cells, two orders of magnitude faster than the using
-Cholesky factorization with Gaussian Elimination.
+As a result, a GPU implementation of conjugate gradient converges in 60
+ms when using 250 HOG cells on Nvidia GTX660, two orders of magnitude faster
+than the using Cholesky factorization with Gaussian Elimination.
 
@@
 several hundred cells, while using the iterative Conjugate Gradient
-method, it only takes 80ms. If we use NZ-WHO, we can gain extra speed
+method, it only takes 60ms. If we use NZ-WHO, we can gain extra speed
 up since we only whitens non-zero cells.
@@
 \label{sec:fft}
+
 We generate high resolution templates with more than 250 HOG cells to capture
@@
 cells in the template. To overcome and speed up the convolution, we used FFT
-based GPU convolution \cite{Podlozhnyuk} which scales. Briefly, for length $n$ signal and
-length $m$ filter, naive convolution takes $O(nm)$ time whereas FFT-based
-convolution takes $O\left( (n + m)\log (n+m) \right)$ time. For large
+based GPU convolution \cite{Podlozhnyuk} which scales. Briefly, for length $n$
+signal and length $m$ filter, naive convolution takes $O(nm)$ time whereas
+FFT-based convolution takes $O\left( (n + m)\log (n+m) \right)$ time. For large
 $m$ (high resolution templates), we can gain computational advantage.

### 2015-03-30 mcmc.tex
compressed
minor changes
Major approach modification don. minor mcmc and overview
Approach major whiten to LDA update
MCMC minor math update
experiment, major PASCAL12 table to scriptsize

@@
     g(p \rightarrow p + f') & \sim \mathcal{N}(\mu = p_{f},\sigma = \sigma_f)\\
-    g(p \rightarrow p + m') & \sim c \delta(p_m) + (1-c) Unif(1,M),
+    g(p \rightarrow p + m') & \sim (1-c) \delta(p_m) + c Unif(1,M),
 \end{align}
@@
     \includegraphics[width=0.7\linewidth]{tuning2} \\ [-5pt]
-    \caption{Metropolis Hastings move types (Section~\ref{sec:fine}).}
+    \caption{Search space that our fine-tuning stage handles (Section~\ref{sec:fine}).}
  \label{fig:moves}
@@
 \paragraph{Initialization.}
-Since the Metropolis-Hastings algorithm is susceptible to getting
-stuck in local optima, we need a good initialization in order to
+Since the objective function is non-convex, we need a good initialization in order to
 increase the probability to find a solution that is close to the

### 2015-04-01 2349.tex
rename files, add extended abstract template

--- 2015-03-25 egpaper_final.tex
@@
 
-\author{Christopher B. Choy, Michael Stark, Sam Corbett-Davies, Silvio Savarese\\
-    Stanford University, Max Plank Institutes\\
+\author{Christopher Bongsoo Choy\textsuperscript{\dag}, Michael Stark\textsuperscript{\dag \ddag}, Sam Corbett-Davies\textsuperscript{\dag}, Silvio Savarese\textsuperscript{\dag}\\
+    Stanford University\textsuperscript{\dag}, Max Plank Institutes\textsuperscript{\ddag}\\
     {\tt\small \{chrischoy, scorbett, stark, ssilvio\}@stanford.edu}
@@
 
+\section{Acknowledgement}
+This work has been supported by the Max Planck Center for Visual Computing \& Communication.
+
 \clearpage

### 2015-04-01 2349_ext.tex
rename files, add extended abstract template

% Use class option [extendedabs] to prepare the 1-page extended abstract.
\documentclass[extendedabs]{bmvc2k}
\usepackage[colorlinks = true,
            linkcolor = blue,
            urlcolor  = blue,
            citecolor = blue,
            anchorcolor = blue]{hyperref}

% Document starts here
\begin{document}

\title{A Plumbline Constraint for the Rational Function Lens Distortion Model}
\addauthor{
David Claus$^1$, 
Andrew Fitzgibbon$^2$
}{}{1}
\addinstitution{
$^1$Department of Engineering Science, Oxford University. 
$^2$Microsoft Research Cambridge.
}

\maketitle
\let\thefootnote\relax\footnote{This is an extended abstract. The full paper is available at the \href{http://www.cv-foundation.org/openaccess/CVPR2015.py}{Computer Vision Foundation webpage}. }
\vspace{-0.2in}

% Extended abstract begins here.  In a one-page document, there is
% little need for section headers, but you may use \section etc if you
% wish.

\noindent
Calibration of lens distortion has traditionally proceeded in one
of three ways.  The first is to use known correspondences between
feature points in one or more images, and the world 3D points.
This is typically done using a checkerboard or a calibration grid
of dots where corners or dot centres can be reliably
located~\cite{Tsai86}. A second class of calibration techniques is
termed auto-calibration as it relies solely on detecting static
points within a scene~\cite{Zhang96,Fitzgibbon01}.  This paper fits
into the third category, where straight lines in the world are used
to determine the distortion parameters.  This {\em plumbline}
technique was first mooted by~\cite{Brown71}, and has been applied
to various distortion models~\cite{Devernay01,Swaminathan00}.

We show in this paper how a plumbline constraint can be implemented
using the rational function model for lens
distortion~\cite{Claus05}, under which straight lines are imaged as
conics, and this permits an elegant factorization of the conics
into the camera calibration and the equations of the straight
lines.  This differs from previous plumbline work in two ways:
first, a factorization-based algorithm can be formulated to
estimate the distortion; second, nonlinear refinement of the
distortion can be easily implemented to minimize a good
approximation of geometric distance in the image plane.  The simplicity of the mapping leads to fast and efficient convergence of the
nonlinear algorithm over a range of starting positions.

\newcommand{\tr}{^{\top}}
\newcommand{\matx}[1]{\mbox{\tt #1}}
\newcommand{\vect}[1]{{\bf #1}}
For a perspective camera, the mapping from image pixels $(i,j)$ to 3D rays
$\vect d(i,j)$ can be expressed as:
\begin{equation}
\vect d(i,j) = \begin{pmatrix}
B_{11} i   + B_{12}  j + B_{13} 1\\
B_{21} i   + B_{22}  j + B_{23} 1\\
B_{31} i   + B_{32}  j + B_{33} 1
\end{pmatrix}
= \matx B \begin{pmatrix}i\\j\\1\end{pmatrix}, \label{eqn:pinhole}
\end{equation}
where the $3\times3$ matrix $\matx B = \matx R^\top \matx K^{-1}$, and
$\matx R$ is often chosen to be the identity~\cite{Hartley00}.  The
rational function model handles lens distortion by permitting
$i$ and $j$ to appear in higher order polynomials, in particular
quadratic:
\begin{equation}
\vect d(i,j) = \begin{pmatrix}
A_{11} i^2 + A_{12} ij + A_{13} j^2 + A_{14} i + A_{15} j + A_{16}\\
A_{21} i^2 + A_{22} ij + A_{23} j^2 + A_{24} i + A_{25} j + A_{26}\\
A_{31} i^2 + A_{32} ij + A_{33} j^2 + A_{34} i + A_{35} j + A_{36}
           \end{pmatrix}.
           \label{eqn:model}
\end{equation}

\newcommand{\A}{\mbox{${\tt A}$}}
\newcommand{\Chi}{\raisebox{.4ex}{$\boldsymbol\chi$}}
This model may be written as a linear combination of the distortion
parameters, in a $3\times6$ matrix \A\ (analogous to $\matx B$
above), and a 6-vector $\Chi$ of monomials in $i$ and $j$.  Define
$\Chi$ as the ``lifting'' of image point $(i,j)$ to a six
dimensional space
\begin{equation}
\Chi(i,j) =
[i^2,\;\;ij,\;\;j^2,\;\;i,\;\;j,\;\;1]^{\top}\label{eqn:Chi}
\end{equation}
The imaging model~(\ref{eqn:model}) may then be written
\begin{equation}
\vect d(i,j) = \A \Chi(i,j) \label{eqn:project}
\end{equation}

\def\conic{{\boldsymbol\theta}}
A line in the scene forms a plane with the origin of camera
coordinates, and is imaged to the set of $\vect d$ in that plane.
This yields the line equation $\vect l\tr \vect d = 0$ which, in
terms of image points $(i,j)$ becomes
\begin{equation}
\vect l\tr \A \Chi = 0 \Longleftrightarrow \conic^{\top} \Chi = 0,
\end{equation}
where $\conic = (A_{xx}, A_{xy}, A_{yy}, A_x, A_y,
A_{_\mathit{0}})\tr$ are the parameters of a conic in image coordinates $(i,j)$
and $\Chi$ is given by (\ref{eqn:Chi}).  Here we observe the
important property that lines in the world go to conics under the
rational function model.  The task of calibration is then to find an
\A\ which will map these conics in the distorted image back to
straight lines.

By fitting a conic to the image of the line, we obtain
parameters~$\conic$, and thus the constraint
$\conic = \A\tr \vect l$
for unknown $\A$ and $\vect l$.  The equality is exact as any scale
factor is included in $\vect l$. Collecting $L$ such constraints, we
obtain
\begin{align}
\underbrace{\left[ \conic_1 \mid \ldots \mid \conic_L
\right]}_{6\times L} & =
\underbrace{\phantom{\left[\right]}\A\tr}_{6\times 3}
\underbrace{\left[ \vect l_1 \mid \ldots \mid \vect l_L \right]}_{3\times L}
\nonumber
\end{align}
which we write as
$\matx C = \A\tr \matx L\label{eqn:proj_line}$
so the matrix of conic parameters $\matx C$ is of rank no greater
than~$3$.  Therefore $\A$ can be computed up to a homography by
factorization: if $\matx U \matx S \matx V\tr = \matx C$ is the SVD
of $\matx C$, then $\A = \matx S_{(1:3,1:3)} {\matx U_{(:,1:3)}}\tr$
is one member of the equivalence class of solutions.

\begin{figure}[t]
\includegraphics[width=\linewidth]{images/fig1.png}
\caption{
Edges corresponding to straight lines in the real world are
detected (a) and the plumbline constraint is used to compute the
distortion parameters, giving the rectified image (b)}
\vspace{-2mm}
\end{figure}

The matrix $\matx C$ will not be rank 3 if the conics were obtained by
fitting to noisy image data.  The above factorization truncates $\matx C$
to rank 3 by minimizing the error in the conic parameter space, and as
discussed in the paper, this is sensitive to noise.  The strategy for
fitting \A\ from noisy image data is to run a non-linear optimization that
finds the \A\ which minimizes the error between the image data and straight
lines projected (as conics) into the distorted image.  The nonlinear
objective measures the Sampson distance~\cite{Hartley00} from the conics to
the detected edgels.  Let $\vect e_{\ell k} = (i_{\ell k},j_{\ell k})$
denote the $k^{th}$ edgel in linked segment $\ell$. The Sampson distance is
a first order approximation to the distance from a point to a conic. The
error function $\varepsilon(\matx A, \vect l_1, \ldots, \vect l_L)$ we
minimize is then given by (with $\conic^\ell := \matx A \vect l_\ell$)
\begin{equation}
\def\t#1{\conic^\ell_{#1}}
\varepsilon =
\sum_{\ell = 1}^{L} \sum_{k=1}^{n_\ell }
\frac
{\left[(\conic^\ell)\tr\Chi\left(i_{\ell k},j_{\ell k}\right)\right]^2}
{(2\t1 i_{\ell k} + \t2 j_{\ell k} + \t4)^2 + (2\t3 j_{\ell k} +
\t2 i_{\ell k} + \t5)^2}
\nonumber
\end{equation}
Implementation of this method by edge detection and edge linking is
described in the paper, as are the details of the nonlinear optimization.
Our conclusion is that the simplicity of the rational function model,
coupled with its ability to model a variety of lenses, makes it a useful
model to consider when dealing with lenses exhibiting moderate to severe
distortion.

\bibliography{egbib}

\end{document}

### 2015-04-01 egpaper_supp.tex
minor changes
rename files, add extended abstract template

@@
 %%%%%%%%% TITLE
-\title{Supplementary Material for the Paper ``Enriching Object Detection with\\2D-3D Registration and Continuous Viewpoint Estimation''}
+\title{Supplementary Material for the Paper ``Enriching Object Detection with\\
+2D-3D Registration and Continuous Viewpoint Estimation''}
 %\title{Enrich Object Detection : 2D-3D registration and continuous viewpoint estimation}
@@
   \hline
+  \includegraphics[width=0.24\linewidth]{supp/pas_aero1a.jpg} &
+  \includegraphics[width=0.24\linewidth]{supp/pas_aero1b.png} &
+  \includegraphics[width=0.24\linewidth]{supp/pas_aero2a.jpg} &
+  \includegraphics[width=0.24\linewidth]{supp/pas_aero2b.png} \\
+  \includegraphics[width=0.24\linewidth]{supp/pas_aero3a.jpg} &
+  \includegraphics[width=0.24\linewidth]{supp/pas_aero3b.png} &
+  \includegraphics[width=0.24\linewidth]{supp/pas_aero4a.jpg} &
+  \includegraphics[width=0.24\linewidth]{supp/pas_aero4b.png} \\
+  \hline
+  \end{tabular}
+  \caption{Successful detection and pose estimation results on
+    PASCAL3D+~\cite{Xiang14} aeroplanes. Original image (left) and
+  overlaid detection result (right). Proposal bounding box (blue) and
+  predicted bounding box (purple).}
+  \label{fig:pascal3d_aero_good}
+\end{figure*}
+
+\begin{figure*}[h]
+\setlength\tabcolsep{1pt}
+\centering
+\begin{tabular}{|cc|cc|}
+  \hline
   \includegraphics[width=0.24\linewidth]{supp/occlusion1.png} &
@@
   \includegraphics[width=0.22\linewidth]{supp/tuning_1c.png}  \\
-  \includegraphics[width=0.22\linewidth]{supp/tuning_2a.png} &
-  \includegraphics[width=0.22\linewidth]{supp/tuning_2b.png} & 
-  \includegraphics[width=0.22\linewidth]{supp/tuning_2c.png}  \\ 
+  \includegraphics[width=0.22\linewidth]{supp/tuning_7a.png} &
+  \includegraphics[width=0.22\linewidth]{supp/tuning_7b.png} & 
+  \includegraphics[width=0.22\linewidth]{supp/tuning_7c.png}  \\ 
   \includegraphics[width=0.22\linewidth]{supp/tuning_3a.png} &

### 2015-04-01 approach.tex
grammar mod

@@
 rendering (Sect.~\ref{sec:rendering}) followed by feature extraction
-and applying a whitening procedure. Based on the original whitening
+and whitening. Based on the original whitening
 formulation (Sect.~\ref{sec:who}), we propose three novel extensions that
@@
 images (Sect.~\ref{sec:nzwho}). Second, we show how to speed up the
-whitening by two orders of magnitudes for high-resolution templates
-(Sect.~\ref{sec:fastwhiten}). And third, we improve the runtime of our
-3D exemplar template detectors also at test time, by performing
+whitening by two orders of magnitude for high-resolution templates
+(Sect.~\ref{sec:fastwhiten}). Third, we improve the evaluation of our
+3D exemplar template detectors at test time by performing
 convolutions in the frequency domain (Sect.~\ref{sec:fft}).
@@
 and a depth map. The CAD models we used contain texture and material
-information. These make the rendering more realistic and allows us to transfer
-natural image statistics to rendered images. Along
-with a rendering, we extracted a depth map which can be used for
+information. These make the rendering more realistic and allow us to transfer
+natural image statistics to rendered images. During rendering we extract a depth map which can be used for
 reconstruction\ref{fig:rendering}.
@@
 Our technique for rendering and generating exemplar template detectors
-on-the-fly is drawing from recent work. Hariharan \etal. introduced Whitened
+on-the-fly draws from recent work by Hariharan \etal~\cite{Hariharan12}. They introduced Whitened
 Histograms of Orientations (WHO), which uses feature statistics from natural
 images to create a large number of classifiers analytically using Linear
-Discriminant Analysis(LDA) rather than training SVM
-classifiers\cite{Hariharan12}. The confidence score for data $x_i$ can be
+Discriminant Analysis (LDA) rather than training SVM
+classifiers. The confidence score for data $x_i$ can be
 defined as $ S(x_i) = w_{x_t}^T x_i$ where $w_{x_t} = \Sigma^{-1} (x_t - \mu)$
@@
 $\Sigma$ from autocovariance $\Gamma$ collected on a large collection of
-natural images. i.e. for a 31 dim HOG feature $x_t$ at location $t$
+natural images. For a 31 dim HOG feature $x_t$ at location $t$
 
@@
     E[x_t] & = \mu\\
-    E[(x_{t} - \mu ) (x_{\tau} - \mu)] & = E[(x_0 - \mu)(x_{\tau - t} - \mu)]
+    E[(x_{t} - \mu ) (x_{\tau} - \mu)] & = E[(x_0 - \mu)(x_{\tau - t} - \mu)].
 \end{align}
@@
 Alternatively, if the background is left textureless (see
-Fig.~\ref{fig:rendering}), whitening the resulting HOG template
-, strong negative weights are introduced in the textureless region (by
-subtracting the mean $\mu$) as seen in Fig.~\ref{fig:whocomparison}.
+Fig.~\ref{fig:rendering}), whitening the resulting HOG template introduces strong negative weights in the textureless region (by
+subtracting the mean $\mu$), as seen in Fig.~\ref{fig:whocomparison}.
 This could result in positive matches being suppressed due to spurious
@@
 \begin{array}{ccccc}x_1^T & x_2^T & \cdots & x_n^T\end{array} ]^T \in
-\mathcal{R}^{nd}$ where $x_i$ is the $i$th HOG cell feature and $n$ is the
-number HOG cells and $d$ is the dimension of HOG feature. We create a new
+\mathcal{R}^{nd}$ where $x_i$ is the $i$th HOG cell feature, $n$ is the
+number of HOG cells and $d$ is the dimension of the HOG feature. We create a new
 vector $\bar{x}$ which contains only the non-zero HOG cell features of $x$. To be
@@
 
-The matrix selects HOG features that corresponds to the first cell and the third cell.
+The matrix selects HOG features that correspond to the first and third cells.
 
@@
 Visualization of positive weights (first row),  visualization of negative weights (second row), HOGgles \cite{vondrick2013} (third row).
-Note that for WHO, whitening all cell result in strong negative edges on the empty region}
+Note that for WHO, whitening all cells results in strong negative edges on the empty region}
   \label{fig:whocomparison}
@@
 
-Synthesizing an LDA template Eq.~\ref{eq:nz-who} requires solving the system of
+Synthesizing the LDA template in Eq.~\ref{eq:nz-who} requires solving the system of
 linear equations, $\bar{\Sigma} \bar{w} = (\bar{x} - \bar{\mu})$. In
@@
 positive definite systems which runs in $O(n^2\kappa)$ time, where $\kappa$ is
-the condition number of the matrix. \cite{Shewchuk94}.
+the condition number of the matrix~\cite{Shewchuk94}.
 %
@@
 The covariance matrix for HOG templates is typically
-ill-conditioned\cite{Hariharan12}, but adding a small regularization constant to
+ill-conditioned~\cite{Hariharan12}, but adding a small regularization constant to
 the diagonal reduces its condition number.
@@
 We report the real time analysis of whitening using decomposition and
-conjugate gradient methods in Fig.~\ref{fig:whotime}. (a) compares the
+Conjugate Gradient methods in Fig.~\ref{fig:whotime}. (a) compares the
 absolute runtime of the different methods while (b) gives the obtained
@@
 % Fig.~\cite{fig:covariancetime_crop} Using naive Cholesky decomposition,
-WHO template takes several seconds for realistic template sizes of
-several hundred cells, while using the iterative Conjugate Gradient
-method, it only takes 60ms. If we use NZ-WHO, we can gain extra speed
-up since we only whitens non-zero cells.
+whitening the WHO template takes several seconds for realistic template sizes of
+several hundred cells, but only 60ms using the Conjugate Gradient
+method. If we use NZ-WHO, we can gain extra speed
+up since we only whiten non-zero cells.
 
@@
 more numerically stable than Cholesky decomposition with Gaussian
-Elimination. We vary the number of cells in a template and show that
-the residual of NZ-WHO is smaller than WHO Fig.~\ref{fig:whoresidual}.
+Elimination. In Fig.~\ref{fig:whoresidual} we vary the number of cells in a template and show that
+the residual of NZ-WHO is smaller than that of WHO.
 % Also, the residual from the Conjugate Gradient method (the norm of $y-Ax$ for $Ax = y$) is smaller than 
@@
 cause computational burden when computing convolution. Though good for
-detecting accurate model and pose, convolution of high-resolution templates are
-much slower since computation time scales linearly with the number of HOG
-cells in the template. To overcome and speed up the convolution, we used FFT
-based GPU convolution \cite{Podlozhnyuk} which scales. Briefly, for length $n$
+accurately determining model and pose, these large templates slow down the convolution since computation time scales linearly with the number of HOG
+cells in the template. To overcome this, we used FFT-based GPU convolution \cite{Podlozhnyuk}. Briefly, for length $n$
 signal and length $m$ filter, naive convolution takes $O(nm)$ time whereas

### 2015-04-01 egpaper_final.tex
grammar mod

@@
 by aligning exact 3D models to images using templates generated from renderings
-of the 3D models at a finite set of discrete viewpoints. The training procedures
-for these approaches, however, are very expensive and require gigabytes of
-memory and storage, and the viewpoint discretization hampers pose estimation
+of the 3D models at a set of discrete viewpoints. However, the training procedures for these approaches are very expensive and require gigabytes of
+memory and storage, while the viewpoint discretization hampers pose estimation
 performance.
@@
 convolutions. Due to the speed of our template synthesis procedure, we are able
-to perform joint optimization on scale, translation, continuous rotation, and
+to perform joint optimization of scale, translation, continuous rotation, and
 focal length. We provide an efficient GPU implementation of our algorithm, and

### 2015-04-01 experiments.tex
Added selector matrix $S$ that generates $x', \mu', \Sigma'$.
Major approach modification don. minor mcmc and overview
Approach major whiten to LDA update
MCMC minor math update
experiment, major PASCAL12 table to scriptsize
grammar mod

@@
 window fashion and deliver 2D bounding box as well as viewpoint
-information. Our method compares on par to state-of-the-art in this
+information. Our method is competitive with the state-of-the-art in this
 case (Sect.~\ref{sec:exp_iso}).
 %
-And third, we show that our method can be used to complement the
+Finally, we show that our method can be used to complement the
 detections provided by an existing object class detector, such
@@
 To validate our approach, we run an ensemble of NZ-WHO templates as a
-bank of exemplar detectors and compare its performance with other WHO
+bank of detectors and compare its performance with other WHO
 variants, notable WHO~\cite{Hariharan12} and the original non-whitened
@@
 using $9$ different CAD models and a total of 192 different
-viewpoints, using 4 different elevation angles, 24 azimuth angles,
+viewpoints: 4 elevation angles, 24 azimuth angles,
 and 2 focal lengths. We run the entire ensemble exhaustively over
-each test image, in a sliding window fashion.
+each test image in a sliding window fashion.
 
@@
 model (ALM~\cite{Xiang12}), and the
-DPM-VOC+VP~\cite{Pepik12}. Fig.~\ref{fig:3dobject} gives
+DPM-VOC+VP~\cite{Pepik12}. Fig.~\ref{fig:3dobject_vis} gives
 qualitative results.
@@
 account for various azimuths. Thus V-DPM and VOC-DPM provide discrete
-azimuth only whereas our method provides 3D viewpoint (yaw, pitch,
+azimuths only whereas our method provides 3D viewpoint (yaw, pitch,
 roll), CAD instance (model index, rendering, depth) and focal length.
@@
 We use detection bounding boxes provided by both object detectors and
-augment it using our method to give viewpoint estimation. We use
+augment use our method to perform fine-grained viewpoint estimation. We use
 detection bounding boxes from two different methods:
@@
 we use the original score for plotting precision-recall curves
-(meaning that we can not improve over their AP), but
-enrich the detections with additional viewpoint information provided
-by our method. We fall back to a default
+(meaning that we can not improve over their AP). We revert back to a default
 viewpoint prediction ($0$ angles) in case the confidence of our
@@
 in Fig.~\ref{fig:pascal12cnn}, and the effect of fine-tuning is
-visualized in Fig.~\ref{fig:tuning}. More qualitative results are part of
-supplemental material
+visualized in Fig.~\ref{fig:tuning}. More qualitative results can be found in the
+supplemental material.
 \paragraph{Results.}
 %
-In Tab.~\ref{tab:pascal12}, we make mainly two observation. First, we
+In Tab.~\ref{tab:pascal12}, we make two main observations. First, we
 see that adding our method to DPM-VOC+VP consistently improves
@@
 qualitatively for two different test images. In both cases, the
-fine-tuned visually comes closer to the true 3D pose.
+fine-tuned pose is a better visual match to the true 3D pose.
 % We got significant improvement on viewpoint estimation by using our
@@
 %   \hline
-  \includegraphics[width=0.24\textwidth]{car_cnn/2a.png} &   
-  \includegraphics[width=0.24\textwidth]{car_cnn/2b.png} &   
-  \includegraphics[width=0.24\textwidth]{car_cnn/2c.png} &   
-  \includegraphics[width=0.24\textwidth]{car_cnn/2e.png}  \\  
+%  \includegraphics[width=0.24\textwidth]{car_cnn/2a.png} &   
+%  \includegraphics[width=0.24\textwidth]{car_cnn/2b.png} &   
+%  \includegraphics[width=0.24\textwidth]{car_cnn/2c.png} &   
+%  \includegraphics[width=0.24\textwidth]{car_cnn/2e.png}  \\  
 %   \hline
@@
 \end{tabular}
-\caption{Example enriched bounding boxes. Given R-CNN\cite{Girshick14}
+\caption{Example enriched bounding boxes. Given R-CNN~\cite{Girshick14}
   detection bounding boxes, our method predicted 2D-3D matching
-  reasonably. On the first column, R-CNN detection bounding boxes
-  overlaid. From the second to the last columns, output of our method
-  given a R-CNN box. Blue boxes are R-CNN output and purple boxes are
+  reasonably.
+The first column shows bounding boxed produced by R-CNN detection.
+Subsequent columns show the output of our method given this bounding box input.
+Blue boxes are R-CNN output and purple boxes are
   the tightest bounding box enclosing predicted CAD model.}
@@
 \begin{table*}[t]
-    \footnotesize
+    \scriptsize
   \begin{center}
@@
     \hline\hline
+    aeroplane-4v        & 40.0 / 34.6         & 41.5 / 37.4             & 41.1 / 32.7       & 41.1 / 30.5        & 67.8 / \textbf{41.3}         & 67.8 / 40.8 \\ \hline
+    aeroplane-8v        & 39.8 / 23.4         & 40.5 / 28.6             & 41.1 / 26.8       & 41.1 / 24.2        & 67.8 / 26.8         & 67.8 / \textbf{27.4} \\ \hline
+    aeroplane-16v       & 43.6 / 15.4         & 38.0 / 15.9             & 41.1 / 17.7       & 41.1 / 16.3        & 67.8 / 21.2         & 67.8 / \textbf{21.5} \\ \hline
+    aeroplane-24v       & 42.2 / 8.0          & 36.0 /  9.7             & 41.1 / 10.9       & 41.1 / 10.2        & 67.8 / 15.6         & 67.8 / \textbf{15.7} \\ \hline
+    \hline
     car-4v              & 37.2 / 20.2         & 45.6 / 36.9             & 47.6 / 42.7       & 47.6 / \textbf{42.7}        & 49.6 / 41.5         & 49.6 / 41.5\\ \hline
@@
     car-24v             & 36.3 / 13.7         & 42.1 / 24.6             & 47.6 / 27.4       & 47.6 / 27.4        & 49.6 / 27.0         & 49.6 / \textbf{27.6}\\ \hline
+    \hline
+    chair-4v            & 11.1 / 6.8          & 8.7  / 6.1              &  11.4 / 7.1       & 11.4 / 6.7         & 25.2 / 10.6         & 25.2 / \textbf{10.7} \\ \hline
+    chair-8v            & 11.4 / 5.9          & 11.3 / 9.4              &  11.4 / 6.6       & 11.4 / 6.6         & 25.2 / \textbf{9.4}          & 25.2 / 9.3 \\ \hline
+    chair-16v           & 12.8 / 6.0          & 10.2 / 6.1              &  11.4 / 4.7       & 11.4 / 4.7         & 25.2 / \textbf{6.7}          & 25.2 / 6.7 \\ \hline
+    chair-24v           & 12.6 / 4.4          & 8.0  / 4.2              &  11.4 / 3.1       & 11.4 / 3.4         & 25.2 / 4.6          & 25.2 / \textbf{5.4} \\ \hline
     \hline
@@
   \end{center}
-\caption{Average Precision(AP) and Average Viewpoint Precision (AVP) on
+\caption{Average Precision (AP) and Average Viewpoint Precision (AVP) on
   PASCAL3D+~\cite{Xiang14}. For combined methods (* + Ours), we use
@@
 \end{table*}
+
+\begin{comment}
+\hline
+boat-4v             & 3.0 / 1.5           & 0.5 / 0.3               &  /        &  /         & 27.9 / 11.3         & 27.9 / 11.5 \\ \hline
+boat-8v             & 5.8 / 1.0           & 0.5 / 0.2               &  /        &  /         & 27.9 / 5.4          & 27.9 / 5.4 \\ \hline
+boat-16v            & 6.2 / 0.5           & 0.7 / 0.3               &  /        &  /         & 27.9 / 2.0          & 27.9 / 2.0 \\ \hline
+boat-24v            & 6.0 / 0.3           & 5.3 / 2.2               &  /        &  /         & 27.9 / 1.8          & 27.9 / 2.5 \\ \hline
+\end{comment}
 

### 2015-04-01 intro.tex
minor change
grammar mod

--- 2014-11-14 intro.tex
@@
   \includegraphics[width=0.99\linewidth]{front} % \\[-5pt]
-  % (a)\\[0pt]
-  % \setlength\tabcolsep{0pt}
-  % \begin{tabular}{cc}
-  %     \includegraphics[width=0.45\linewidth]{car/orig2} & 
-  %     \includegraphics[width=0.45\linewidth]{car/overlay2}
-  %  %   \begin{tabular}{cc}
-  %  %       \includegraphics[width=0.16\linewidth]{cad_car/2001-2004 Ford Ranger Edge} & 
-  %  %       \includegraphics[width=0.16\linewidth]{cad_car/2002 Dodge Ram FedEx} \\ 
-  %  %       \includegraphics[width=0.16\linewidth]{cad_car/2007-Nissan-Versa-_-Tiida-SL} & 
-  %  %       \includegraphics[width=0.16\linewidth]{cad_car/2008-Jeep-Cherokee} \\ 
-  %  %       \includegraphics[width=0.16\linewidth]{cad_car/2009 Toyota Cargo} & 
-  %  %       \includegraphics[width=0.16\linewidth]{cad_car/2010-Chevrolet-Aveo5-LT} \\ 
-  %  %       \includegraphics[width=0.16\linewidth]{cad_car/2012-Citroen-DS4}  
-  %  %   \end{tabular}
-  % \end{tabular}\\
-  % (b)
   \caption{Using a database of 3D CAD models, we generate NZ-WHO
@@
 lighting, and viewpoint. While this generalization
-ability of these methods is beneficial for robustness, it also limits
+ability is beneficial for robustness, it limits
 the level of detail that these detectors can deliver as an output.
@@
 detectors in addition to 2D bounding boxes. Several attempts have been
-made to estimate viewpoint along with object class detections,
-implemented as extensions to existing detectors, such as the implicit
-shape models~\cite{sun10eccv}, the constellation model~\cite{stark10bmvc}, or the
+made to extend existing detectors to estimate viewpoint along with object class detections, including the implicit
+shape model~\cite{sun10eccv}, the constellation model~\cite{stark10bmvc}, and the
 deformable part model~\cite{Felzenszwalb10, gu10eccv,Xiang12,Pepik12,Fidler12,Hejrati14}.
@@
 statistical learning techniques. Now, this problem is being revisited
-mostly due to two reasons: {\em (i)} the availability of 3D CAD models
+for two main reasons: {\em (i)} the availability of 3D CAD models
 for many object classes and {\em (ii)} the availability of robust
@@
 % require supervision to achieve 2D-3D matching.
-% In medical community, registering 3D scan data to 2D image enabled various minimally invasive surgeries \cite{Markelj12}.
+% In medical community, registering 3D scan data to 2D image enabled various
+% minimally invasive surgeries \cite{Markelj12}.
 %
@@
 
-For (i), recent approaches to 2D-3D matching~\cite{Aubry14, Lim14}
-typically rely on a
+For (i), recent approaches to 2D-3D matching~\cite{Aubry14, Lim14} rely on a
 collection of 3D exemplar models, which they render from a
@@
 replacing the standard SVM with an LDA classifier
-(E-LDA)~\cite{Hariharan12}, resulting in a whitened feature
-representation, termed WHO. As a result, it is feasible to train
+(E-LDA)~\cite{Hariharan12}. The result is a whitened feature
+representation, termed WHO (Whitened Histogram of Orientations). This development makes it feasible to train
 hundreds of thousands of mid-level patch detectors for
@@
 result, we can render novel views and train corresponding exemplar
-models {\em on the fly}, without the need for offline processing. As a
+models {\em on the fly}, without the need for offline processing. We call these NZ-WHO templates \ref{fig:front}. As a
 by-product, we can formulate the alignment problem as a parameter
-search in a continuous pose space, consisting of yaw, pitch and roll, resulting in truly continuous pose estimates, which
+search in a continuous pose space, consisting of yaw, pitch and roll, which
 we implement using MCMC sampling.
+
 %  require a large number of rendering and 2D
@@
 
-Our paper makes the following specific contributions.
+Our paper makes the following contributions:
 
@@
 % (yaw, roll, pitch) and focal length.
-
-Second, we show to enrich the output of an existing object class
+%
+Second, we demonstrate that our method can enrich the output of an existing object class
 detector, such as the DPM~\cite{Felzenszwalb10} or the
-R-CNN~\cite{Girshick14} with additional 3D information, applying our
-method to candidate detections provided by the respective detector. As
-a result, we can refine the original detections with additional
-estimates of 3D continuous pose and a 3D CAD model exemplar.
-
-And third, we give an in-depth experimental study that demonstrates
+R-CNN~\cite{Girshick14} with additional 3D information. By applying our
+method to candidate detections provided by the respective detector, we can augment the original detections with an
+estimate of 3D continuous pose and a 3D CAD model exemplar.
+%
+Finally, we give an in-depth experimental study that demonstrates
 the effectiveness of our approach on a standard benchmark for

### 2015-04-01 mcmc.tex
grammar mod

@@
 index $m$. For (i) and (ii), we use Gaussian proposal distributions, and a uniform
-distribution over model changes for (iii). For scale and translation, we
-implicitly compute all possible translation and scale by convolving $w(q)$ to
-HOG pyramid.
+distribution over model changes for (iii). We implicitly compute all possible translation and scale by convolving $w(q)$ with a HOG pyramid.
 \begin{align}
@@
     g(p \rightarrow p + f') & \sim \mathcal{N}(\mu = p_{f},\sigma = \sigma_f)\\
-    g(p \rightarrow p + m') & \sim (1-c) \delta(p_m) + c Unif(1,M),
+    g(p \rightarrow p + m') & \sim (1-c) \delta(p_m) + c\,\textrm{Unif}(1,M),
 \end{align}
@@
 the sample with the highest probability as our approximate estimate of
-the MAP solution. We set $\sigma_v = 5$ degree and $\sigma_f = 1$ and
+the MAP solution. We set $\sigma_v = 5^\circ$, $\sigma_f = 1$ and
 $c = 0.1$ for all experiments.
@@
 Since the objective function is non-convex, we need a good initialization in order to
-increase the probability to find a solution that is close to the
+increase the probability that we find a solution close to the
 global optima. We achieve this by first running a discrete,

### 2015-04-01 2349.tex

--- 2015-03-25 egpaper_final.tex
@@
 
-\author{Christopher B. Choy, Michael Stark, Sam Corbett-Davies, Silvio Savarese\\
-    Stanford University, Max Plank Institutes\\
+\author{Christopher Bongsoo Choy\textsuperscript{\dag}, Michael Stark\textsuperscript{\dag \ddag}, Sam Corbett-Davies\textsuperscript{\dag}, Silvio Savarese\textsuperscript{\dag}\\
+    \textsuperscript{\dag}Stanford University, \textsuperscript{\ddag}Max Plank Institutes\\
     {\tt\small \{chrischoy, scorbett, stark, ssilvio\}@stanford.edu}
@@
 by aligning exact 3D models to images using templates generated from renderings
-of the 3D models at a finite set of discrete viewpoints. The training procedures
-for these approaches, however, are very expensive and require gigabytes of
-memory and storage, and the viewpoint discretization hampers pose estimation
-performance.
+of the 3D models at a set of discrete viewpoints. However, the training
+procedures for these approaches are computationally expensive and require
+gigabytes of memory and storage, while the viewpoint discretization hampers
+pose estimation performance.
 

### 2015-04-01 approach.tex

@@
 % Fig.~\cite{fig:covariancetime_crop} Using naive Cholesky decomposition,
-whitening the WHO template takes several seconds for realistic template sizes of
+whitening the HOG template takes several seconds for realistic template sizes of
 several hundred cells, but only 60ms using the Conjugate Gradient
@@
 cause computational burden when computing convolution. Though good for
-accurately determining model and pose, these large templates slow down the convolution since computation time scales linearly with the number of HOG
-cells in the template. To overcome this, we used FFT-based GPU convolution \cite{Podlozhnyuk}. Briefly, for length $n$
+accurately determining model and pose, these large templates slow down the
+convolution since computation time scales linearly with the number of HOG cells
+in the template. To overcome this, we used FFT-based GPU convolution
+\cite{Podlozhnyuk}. Briefly, for length $n$ 
 signal and length $m$ filter, naive convolution takes $O(nm)$ time whereas

### 2015-04-01 intro.tex

@@
 detectors in addition to 2D bounding boxes. Several attempts have been
-made to extend existing detectors to estimate viewpoint along with object class detections, including the implicit
-shape model~\cite{sun10eccv}, the constellation model~\cite{stark10bmvc}, and the
+made to extend existing detectors to estimate viewpoint along with object class
+detections, including the implicit shape model~\cite{sun10eccv}, the
+constellation model~\cite{stark10bmvc}, and the
 deformable part model~\cite{Felzenszwalb10, gu10eccv,Xiang12,Pepik12,Fidler12,Hejrati14}.
@@
 3D CAD model instances to real world test images~\cite{Aubry14,
-  Lim14,Kholgade14, Chen13, Kostas14}. Interestingly, the problem of matching 3D models to 2D
-images has been explored since the early days of computer
+  Lim14,Kholgade14, Chen13, Kostas14}. Interestingly, the problem of matching
+3D models to 2D images has been explored since the early days of computer
 vision~\cite{Lowe87}, but had largely been neglected in recent years
@@
 (E-LDA)~\cite{Hariharan12}. The result is a whitened feature
-representation, termed WHO (Whitened Histogram of Orientations). This development makes it feasible to train
-hundreds of thousands of mid-level patch detectors for
-recognition~\cite{Aubry14}.
+representation, termed WHO (Whitened Histogram of Orientations). This
+development makes it feasible to train hundreds of thousands of mid-level patch
+detectors for recognition~\cite{Aubry14}.
 %
@@
 result, we can render novel views and train corresponding exemplar
-models {\em on the fly}, without the need for offline processing. We call these NZ-WHO templates \ref{fig:front}. As a
+models {\em on the fly}, without the need for offline processing. We call these Non-Zero Whiten Histograms of Orientations(NZ-WHO) templates \ref{fig:front}. As a
 by-product, we can formulate the alignment problem as a parameter
@@
 rendered 3D CAD data {\em on the fly}, enabled by a novel variant of
-WHO, termed NZ-WHO, and making efficient use of the specific
+WHO, termed Non-Zero Whiten Histograms of Orientations(NZ-WHO), and making efficient use of the specific
 characteristics of rendered images. To our knowledge, our method

### 2015-04-07 2349.tex
extended abstract and Michael's edit

@@
 \author{Christopher Bongsoo Choy\textsuperscript{\dag}, Michael Stark\textsuperscript{\dag \ddag}, Sam Corbett-Davies\textsuperscript{\dag}, Silvio Savarese\textsuperscript{\dag}\\
-    \textsuperscript{\dag}Stanford University, \textsuperscript{\ddag}Max Plank Institutes\\
-    {\tt\small \{chrischoy, scorbett, stark, ssilvio\}@stanford.edu}
+	\textsuperscript{\dag}Stanford University, \textsuperscript{\ddag}Max Planck Institute for Informatics\\
+	{\tt\small \{chrischoy, scorbett, ssilvio\}@stanford.edu, \textsuperscript{\ddag}stark@mpi-inf.mpg.de }
 % For a paper whose authors are all at the same institution,
@@
 to perform joint optimization of scale, translation, continuous rotation, and
-focal length. We provide an efficient GPU implementation of our algorithm, and
-we validate its performance on 3D Object Classes and PASCAL3D+ datasets.
+focal length using Metropolis-Hastings algorithm. We provide an efficient GPU
+implementation of our algorithm, and we validate its performance on 3D Object
+Classes and PASCAL3D+ datasets.
 
@@
 
-\section{Acknowledgement}
+\paragraph{Acknowledgement}
 This work has been supported by the Max Planck Center for Visual Computing \& Communication.

### 2015-04-07 2349_ext.tex
extended abstract and Michael's edit

@@
             anchorcolor = blue]{hyperref}
+\graphicspath{ {figures/} }
 
@@
 
-\title{A Plumbline Constraint for the Rational Function Lens Distortion Model}
+\title{Enriching Object Detection with 2D-3D Registration and Continuous Viewpoint Estimation}
 \addauthor{
-David Claus$^1$, 
-Andrew Fitzgibbon$^2$
-}{}{1}
+Christopher Bongsoo Choy\textsuperscript{\dag}, Michael Stark\textsuperscript{\dag \ddag}, Sam Corbett-Davies\textsuperscript{\dag}, Silvio Savarese\textsuperscript{\dag}}{}{1}
 \addinstitution{
-$^1$Department of Engineering Science, Oxford University. 
-$^2$Microsoft Research Cambridge.
+\textsuperscript{\dag}Stanford University, \textsuperscript{\ddag}Max Planck Institute for Informatics
 }
@@
 \noindent
-Calibration of lens distortion has traditionally proceeded in one
-of three ways.  The first is to use known correspondences between
-feature points in one or more images, and the world 3D points.
-This is typically done using a checkerboard or a calibration grid
-of dots where corners or dot centres can be reliably
-located~\cite{Tsai86}. A second class of calibration techniques is
-termed auto-calibration as it relies solely on detecting static
-points within a scene~\cite{Zhang96,Fitzgibbon01}.  This paper fits
-into the third category, where straight lines in the world are used
-to determine the distortion parameters.  This {\em plumbline}
-technique was first mooted by~\cite{Brown71}, and has been applied
-to various distortion models~\cite{Devernay01,Swaminathan00}.
+% In this paper, we propose a novel method for 2D-3D alignment of exemplar CAD
+% models to real-world images that circumvents the need for calibration and
+% greatly enhances the scalability of WHO. Our model generates a discriminative
+% exemplar template on-the-fly and align model accurately using MCMC.
 
-We show in this paper how a plumbline constraint can be implemented
-using the rational function model for lens
-distortion~\cite{Claus05}, under which straight lines are imaged as
-conics, and this permits an elegant factorization of the conics
-into the camera calibration and the equations of the straight
-lines.  This differs from previous plumbline work in two ways:
-first, a factorization-based algorithm can be formulated to
-estimate the distortion; second, nonlinear refinement of the
-distortion can be easily implemented to minimize a good
-approximation of geometric distance in the image plane.  The simplicity of the mapping leads to fast and efficient convergence of the
-nonlinear algorithm over a range of starting positions.
+A large body of recent work on object detection has focused on providing more
+than a bounding box of an object. Some exploited 3D CAD
+model databases to provide viewpoint estimation. These approaches work
+by aligning exact 3D models to images using templates generated from renderings
+of the 3D models at a set of discrete viewpoints.
 
-\newcommand{\tr}{^{\top}}
-\newcommand{\matx}[1]{\mbox{\tt #1}}
-\newcommand{\vect}[1]{{\bf #1}}
-For a perspective camera, the mapping from image pixels $(i,j)$ to 3D rays
-$\vect d(i,j)$ can be expressed as:
-\begin{equation}
-\vect d(i,j) = \begin{pmatrix}
-B_{11} i   + B_{12}  j + B_{13} 1\\
-B_{21} i   + B_{22}  j + B_{23} 1\\
-B_{31} i   + B_{32}  j + B_{33} 1
-\end{pmatrix}
-= \matx B \begin{pmatrix}i\\j\\1\end{pmatrix}, \label{eqn:pinhole}
-\end{equation}
-where the $3\times3$ matrix $\matx B = \matx R^\top \matx K^{-1}$, and
-$\matx R$ is often chosen to be the identity~\cite{Hartley00}.  The
-rational function model handles lens distortion by permitting
-$i$ and $j$ to appear in higher order polynomials, in particular
-quadratic:
-\begin{equation}
-\vect d(i,j) = \begin{pmatrix}
-A_{11} i^2 + A_{12} ij + A_{13} j^2 + A_{14} i + A_{15} j + A_{16}\\
-A_{21} i^2 + A_{22} ij + A_{23} j^2 + A_{24} i + A_{25} j + A_{26}\\
-A_{31} i^2 + A_{32} ij + A_{33} j^2 + A_{34} i + A_{35} j + A_{36}
-           \end{pmatrix}.
-           \label{eqn:model}
-\end{equation}
+However, training the template for all viewpoint and CAD models is not feasible
+since gathering all training data for different viewpoint and CAD models is
+expensive.  Instead, it has been realized that template-based exemplar
+detectors based on HOG features can be trained analytically, by
+replacing the standard SVM with an LDA classifier $w_{x_t}$ for a template $x_t$
+~\cite{Hariharan12}.
 
-\newcommand{\A}{\mbox{${\tt A}$}}
-\newcommand{\Chi}{\raisebox{.4ex}{$\boldsymbol\chi$}}
-This model may be written as a linear combination of the distortion
-parameters, in a $3\times6$ matrix \A\ (analogous to $\matx B$
-above), and a 6-vector $\Chi$ of monomials in $i$ and $j$.  Define
-$\Chi$ as the ``lifting'' of image point $(i,j)$ to a six
-dimensional space
-\begin{equation}
-\Chi(i,j) =
-[i^2,\;\;ij,\;\;j^2,\;\;i,\;\;j,\;\;1]^{\top}\label{eqn:Chi}
-\end{equation}
-The imaging model~(\ref{eqn:model}) may then be written
-\begin{equation}
-\vect d(i,j) = \A \Chi(i,j) \label{eqn:project}
-\end{equation}
+The result is a whitened feature representation, termed WHO (Whitened Histogram
+of Orientations). This development makes it feasible to train hundreds of
+thousands of mid-level patch detectors for recognition.
 
-\def\conic{{\boldsymbol\theta}}
-A line in the scene forms a plane with the origin of camera
-coordinates, and is imaged to the set of $\vect d$ in that plane.
-This yields the line equation $\vect l\tr \vect d = 0$ which, in
-terms of image points $(i,j)$ becomes
-\begin{equation}
-\vect l\tr \A \Chi = 0 \Longleftrightarrow \conic^{\top} \Chi = 0,
-\end{equation}
-where $\conic = (A_{xx}, A_{xy}, A_{yy}, A_x, A_y,
-A_{_\mathit{0}})\tr$ are the parameters of a conic in image coordinates $(i,j)$
-and $\Chi$ is given by (\ref{eqn:Chi}).  Here we observe the
-important property that lines in the world go to conics under the
-rational function model.  The task of calibration is then to find an
-\A\ which will map these conics in the distorted image back to
-straight lines.
+Though it achieved remarkable improvements, generating LDA templates (matrix
+decomposition with Gaussian Elimination) and calibrating them are
+computationally expensive and require gigabytes of memory and storage, while
+the viewpoint discretization hampers pose estimation performance.
 
-By fitting a conic to the image of the line, we obtain
-parameters~$\conic$, and thus the constraint
-$\conic = \A\tr \vect l$
-for unknown $\A$ and $\vect l$.  The equality is exact as any scale
-factor is included in $\vect l$. Collecting $L$ such constraints, we
-obtain
-\begin{align}
-\underbrace{\left[ \conic_1 \mid \ldots \mid \conic_L
-\right]}_{6\times L} & =
-\underbrace{\phantom{\left[\right]}\A\tr}_{6\times 3}
-\underbrace{\left[ \vect l_1 \mid \ldots \mid \vect l_L \right]}_{3\times L}
-\nonumber
-\end{align}
-which we write as
-$\matx C = \A\tr \matx L\label{eqn:proj_line}$
-so the matrix of conic parameters $\matx C$ is of rank no greater
-than~$3$.  Therefore $\A$ can be computed up to a homography by
-factorization: if $\matx U \matx S \matx V\tr = \matx C$ is the SVD
-of $\matx C$, then $\A = \matx S_{(1:3,1:3)} {\matx U_{(:,1:3)}}\tr$
-is one member of the equivalence class of solutions.
+% In this paper, instead of caching and calibrating all templates on training
+% time, we selectively generate templates on testing time as well to estimate
+% viewpoint continuously using the technique we proposed termed Non-Zero Whitened
+% Histograms of Orientations (NZ-WHO).
+
+% The method uses Conjugate Gradient method to efficiently generate an LDA template on-the-fly (60 ms) without expensive calibration steps.
 
 \begin{figure}[t]
-\includegraphics[width=\linewidth]{images/fig1.png}
-\caption{
-Edges corresponding to straight lines in the real world are
-detected (a) and the plumbline constraint is used to compute the
-distortion parameters, giving the rectified image (b)}
-\vspace{-2mm}
+  \centering
+  % \includegraphics[width=0.9\linewidth]{schematics} 
+  \includegraphics[width=0.8\linewidth]{front} % \\[-5pt]
+  \caption{Using a database of 3D CAD models, we generate NZ-WHO
+    templates which can be used to either detect objects directly or
+    enrich the output of an existing detector with high-quality,
+    continuous pose and 3D CAD model exemplar.}
+    % initialize pose of an object in the bounding box from other
+    % detectors. Once initialization is given, we use NZ-WHO to propose
+    % and validate plausible pose on-the-fly and
+    % further tune the translation, 3D viewpoint and focal length continuously.}
+  % \vspace{-1em}
+  \label{fig:front}
 \end{figure}
 
-The matrix $\matx C$ will not be rank 3 if the conics were obtained by
-fitting to noisy image data.  The above factorization truncates $\matx C$
-to rank 3 by minimizing the error in the conic parameter space, and as
-discussed in the paper, this is sensitive to noise.  The strategy for
-fitting \A\ from noisy image data is to run a non-linear optimization that
-finds the \A\ which minimizes the error between the image data and straight
-lines projected (as conics) into the distorted image.  The nonlinear
-objective measures the Sampson distance~\cite{Hartley00} from the conics to
-the detected edgels.  Let $\vect e_{\ell k} = (i_{\ell k},j_{\ell k})$
-denote the $k^{th}$ edgel in linked segment $\ell$. The Sampson distance is
-a first order approximation to the distance from a point to a conic. The
-error function $\varepsilon(\matx A, \vect l_1, \ldots, \vect l_L)$ we
-minimize is then given by (with $\conic^\ell := \matx A \vect l_\ell$)
-\begin{equation}
-\def\t#1{\conic^\ell_{#1}}
-\varepsilon =
-\sum_{\ell = 1}^{L} \sum_{k=1}^{n_\ell }
-\frac
-{\left[(\conic^\ell)\tr\Chi\left(i_{\ell k},j_{\ell k}\right)\right]^2}
-{(2\t1 i_{\ell k} + \t2 j_{\ell k} + \t4)^2 + (2\t3 j_{\ell k} +
-\t2 i_{\ell k} + \t5)^2}
-\nonumber
-\end{equation}
-Implementation of this method by edge detection and edge linking is
-described in the paper, as are the details of the nonlinear optimization.
-Our conclusion is that the simplicity of the rational function model,
-coupled with its ability to model a variety of lenses, makes it a useful
-model to consider when dealing with lenses exhibiting moderate to severe
-distortion.
+\paragraph{Overview}
+
+In this paper, we propose a novel method for 2D-3D alignment of exemplar CAD
+models to real-world images that circumvents the need for calibration and
+greatly enhances the scalability of WHO. As a result, we can render novel views
+and train corresponding exemplar models {\em on-the-fly}, without the need for
+offline processing. We call these Non-Zero Whitened Histograms of Orientations
+(NZ-WHO) templates Fig.~\ref{fig:front}. As a by-product, we can formulate the
+alignment problem as a parameter search in a continuous pose space, consisting
+of yaw, pitch and roll, which we implement using MCMC sampling.
+
+First, we present a novel method for training exemplar models from
+rendered 3D CAD data on-the-fly, enabled by a novel variant of
+WHO, termed Non-Zero Whitened Histograms of Orientations (NZ-WHO), and making
+efficient use of the specific characteristics of rendered images. To our
+knowledge, our method constitutes the first attempt to simultaneously render
+and train exemplar detectors on-the-fly.
+
+Second, we demonstrate that our method can enrich the output of an existing
+object class detector, such as the DPM or the
+R-CNN with additional 3D information. By applying our
+method to candidate detections provided by the respective detector, we can
+augment the original detections with an estimate of 3D continuous pose and a 3D
+CAD model exemplar.
+
+Finally, we give an in-depth experimental study that demonstrates
+the effectiveness of our approach on a standard benchmark for
+object detection and viewpoint estimation~\cite{Xiang14}.
+
+\begin{figure}[t]
+\small
+\setlength\tabcolsep{1pt}
+\centering
+\begin{tabular}{ccccc}
+  \includegraphics[width=0.2\textwidth]{car_cnn/2c.png} &
+  \includegraphics[width=0.2\textwidth]{car_cnn/2e.png} \\
+  \includegraphics[width=0.2\textwidth]{bicycle_cnn/4b.png} &
+  \includegraphics[width=0.2\textwidth]{bicycle_cnn/4c.png} \\
+\end{tabular}
+\caption{Example enriched bounding boxes. Given R-CNN
+	detection bounding boxes, our method predicts the best 2D-3D
+	registration given the bounding box input. Blue boxes are R-CNN output and
+	purple boxes are the tightest bounding box enclosing predicted CAD model.}
+\label{fig:pascal12cnn}
+\end{figure}
+
+\paragraph{Non-Zero Whitened Histograms of Orientations}
+
+NZ-WHO removes these artifacts so that the background has no effect on the
+template response. Let a vectorized HOG feature of a rendering image $x = [
+x_1^T ,  \cdots , x_n^T ]^T \in \mathcal{R}^{nd}$ where $x_i$ is the $i$th HOG cell feature, $n$ is the
+number of HOG cells and $d$ is the dimension of the HOG feature. We create a new
+vector $\bar{x}$ which contains only the non-zero HOG cell features of $x$.
+Synthesizing the LDA template requires solving the system of linear equations
+$\bar{w}=\bar{\Sigma}^{-1}(\bar{x} - \bar{\mu})$. In \cite{Hariharan12}, the
+authors solve the system via the Cholesky decomposition, which requires
+$O(n^3)$ time. Instead, we introduced the Conjugate Gradient method to generate
+LDA templates. The method runs in $O(n^2\kappa)$ time, where $\kappa$ is the condition number of the matrix and achieved more than 100x speed-up.
+
+% Also, the residual from the Conjugate Gradient method (the norm of $y-Ax$ for
+% $Ax = y$) is smaller than 
+% that of Cholesky decomposition.
+
+\paragraph{Fine-Tuning using MCMC}
+Due to the speed of our template synthesis procedure, we are able to perform
+joint optimization of scale, translation, continuous rotation, and focal length
+using the Metropolis-Hastings algorithm.
+
+We model the probability of an object with the parameter $\theta$ in the test
+image $\mathcal{I}$ as $P(\theta| \mathcal{I}) \sim e^{ \max_{s} w(\theta)
+	\ast \mathcal{T}_s(\mathcal{I})}$. We approximate the MAP solution for $p$ by
+drawing samples from the distribution $P(\theta | \mathcal{I})$, using the
+Metropolis-Hastings algorithm.
+
+\paragraph{Experiments}
+
+First, we verify that our NZ-WHO method delivers performance that is
+at least on par with the original WHO formulation~\cite{Hariharan12} in terms of
+accuracy, while at the same time resulting in large computational
+savings.
+
+Second, we demonstrate that our method can be used for multi-view
+object class detection in isolation. It can be applied in a sliding
+window fashion and deliver 2D bounding box as well as viewpoint
+information. Our method is competitive with the state-of-the-art in this
+case.
+
+Finally, we show that our method can be used to complement the
+detections provided by an existing object class detector, such
+as DPM or RCNN. In this case, we show a considerable performance improvement
+compared to previous work in the task of joint object class detection and VP
+estimation. Example outputs of our model are on Fig.~\ref{fig:pascal12cnn}.
 

### 2015-04-07 approach.tex
extended abstract and Michael's edit

@@
 
-We used an off-the-shelf rendering engine to generate a realistic rendering
+We use an off-the-shelf rendering engine to generate a realistic rendering
 and a depth map. The CAD models we used contain texture and material
 information. These make the rendering more realistic and allow us to transfer
-natural image statistics to rendered images. During rendering we extract a depth map which can be used for
-reconstruction\ref{fig:rendering}.
+natural image statistics to rendered images Fig.~\ref{fig:rendering}.
 
@@
 for all possible template shape is intractable, \cite{Hariharan12} assumed
-Wide-Sense Stationarity(WSS) of HOG features and generated a covariance
+Wide-Sense Stationarity (WSS) of HOG features and generated a covariance
 $\Sigma$ from autocovariance $\Gamma$ collected on a large collection of
-natural images. For a 31 dim HOG feature $x_t$ at location $t$
+natural images. In this paper, we further assumed symmetry of the
+autocovariance. For a 31-dimension HOG feature $x_t$ at location $t$
 
 \begin{align}
-    E[x_t] & = \mu\\
-    E[(x_{t} - \mu ) (x_{\tau} - \mu)] & = E[(x_0 - \mu)(x_{\tau - t} - \mu)].
+    E[x_t] & = E[x_\tau] = \mu\\
+    \Gamma_{\|t - \tau\|} & = E[(x_{t} - \mu ) (x_{\tau} - \mu)] \\
+              & = E[(x_0 - \mu)(x_{\tau - t} - \mu)].
 \end{align}
 
-In this paper, we followed their method to generate $\Sigma$.
+for all $t$ and $\tau$. In practice, we gathered $\Gamma$ up to $|t - \tau |
+\le 40$ both horizontally and diagonally.
 
@@
 Alternatively, if the background is left textureless (see
-Fig.~\ref{fig:rendering}), whitening the resulting HOG template introduces strong negative weights in the textureless region (by
-subtracting the mean $\mu$), as seen in Fig.~\ref{fig:whocomparison}.
+Fig.~\ref{fig:rendering}), whitening the resulting HOG template introduces
+strong negative weights in the textureless region (by subtracting the mean
+$\mu$), as seen in Fig.~\ref{fig:whocomparison}.
 This could result in positive matches being suppressed due to spurious
@@
 NZ-WHO removes these artifacts so that the background has no effect on the
-template response. Let a vectorized HOG features of a rendering image $x = [
+template response. Let a vectorized HOG feature of a rendering image $x = [
 \begin{array}{ccccc}x_1^T & x_2^T & \cdots & x_n^T\end{array} ]^T \in
@@
 \begin{equation}
-    \bar{w}=\bar{\Sigma}^{-1}(\bar{x} - \bar{\mu}) \label{eq:nz-who},
+    \bar{w}=\bar{\Sigma}^{-1}(\bar{x} - \bar{\mu}) \label{eq:nz-who}
 \end{equation}
@@
   \end{center}
-  \caption{Comparison of HOG, WHO and NZ-WHO.
-Visualization of positive weights (first row),  visualization of negative weights (second row), HOGgles \cite{vondrick2013} (third row).
-Note that for WHO, whitening all cells results in strong negative edges on the empty region}
+  \caption{Comparison of HOG, WHO and NZ-WHO. Visualization of positive weights
+      (first row),  visualization of negative weights (second row), HOGgles
+      \cite{vondrick2013} (third row). Note that for WHO, whitening all cells
+      results in strong negative edges on the empty region.}
   \label{fig:whocomparison}
@@
 ms when using 250 HOG cells on Nvidia GTX660, two orders of magnitude faster
-than the using Cholesky factorization with Gaussian Elimination.
+than using Cholesky factorization with Gaussian Elimination.
 
@@
 whitening the HOG template takes several seconds for realistic template sizes of
-several hundred cells, but only 60ms using the Conjugate Gradient
+several hundred cells, but only 60 ms using the Conjugate Gradient
 method. If we use NZ-WHO, we can gain extra speed
@@
 more numerically stable than Cholesky decomposition with Gaussian
-Elimination. In Fig.~\ref{fig:whoresidual} we vary the number of cells in a template and show that
-the residual of NZ-WHO is smaller than that of WHO.
+Elimination. In Fig.~\ref{fig:whoresidual} we vary the number of cells in a
+template and show that the residual of NZ-WHO is smaller than that of WHO.
 % Also, the residual from the Conjugate Gradient method (the norm of $y-Ax$ for $Ax = y$) is smaller than 
@@
   \caption{(a) Runtime analysis of whitening. HOG means feature
-    extraction time, WHO-Chol uses ~\cite{Hariharan12} and
+    extraction time, WHO-Chol uses our implementation of ~\cite{Hariharan12} and
     WHO-CG uses iterative Conjugate Gradient. NZ-WHO-CG (Ours) uses only
@@
   \includegraphics[width=0.5\linewidth]{residual}
-  \caption{Residuals from different method}
+  \caption{Residuals of different method}
   \label{fig:whoresidual}
@@
 
-\subsection{High Resolution Templates and FFT based Convolution}
+\subsection{High Resolution Templates and FFT-based Convolution}
 \label{sec:fft}

### 2015-04-07 experiments.tex
extended abstract and Michael's edit

@@
 NZ-WHO-CG achieves the second best AP of $90.0$ while completing in 79
-ms vs. 8.7 s when using calibration.
+ms vs. 8.5 s when using calibration.
 
@@
   \end{tabular}
-  \caption{Average Precision(AP), Mean Precision in Pose Estimation
+  \caption{Average Precision (AP), Mean Precision in Pose Estimation
     (MPPE)~\cite{Lopez-Sastre11}, and generation time for variations of WHO on
@@
     \hline
-     AP/MPPE& Ours & ALM\cite{Xiang12} & VOC-DPM\cite{Pepik12} \\
+    AP/MPPE& Ours & ALM\cite{Xiang12} & DPM-VOC+VP\cite{Pepik12} \\
     \hline\hline
@@
 high quality viewpoint annotations thus is ideal to measure pose
-estimation. The dataset proposes new metric called Average Viewpoint
+estimation. The dataset proposes a new metric called Average Viewpoint
 Precision (AVP) where it measures the area under viewpoint precision
-and detection recall curve. The viewpoints is measured by azimuth
+and detection recall curve. The viewpoint is measured by azimuth
 similarity. If the distance between predicted azimuth and ground truth
@@
 The baseline methods V-DPM~\cite{Xiang14} and
-DPM-VOC+VP~\cite{Pepik12}) reported on the PASCAL3D+ dataset are
+DPM-VOC+VP~\cite{Pepik12} reported on the PASCAL3D+ dataset are
 variants of DPM~\cite{Felzenszwalb10} where each component of DPM
-account for various azimuths. Thus V-DPM and VOC-DPM provide discrete
+accounts for azimuth. Thus V-DPM and DPM-VOC+VP provide discrete
 azimuths only whereas our method provides 3D viewpoint (yaw, pitch,
-roll), CAD instance (model index, rendering, depth) and focal length.
+roll), CAD model instance (model index, rendering, depth) and focal length.
 %
@@
 We use detection bounding boxes provided by both object detectors and
-augment use our method to perform fine-grained viewpoint estimation. We use
+ use our method to perform fine-grained viewpoint estimation. We use
 detection bounding boxes from two different methods:
-DPM-VOC+VP\cite{Pepik12} and R-CNN~\cite{Girshick14}, both in their
+DPM-VOC+VP~\cite{Pepik12} and R-CNN~\cite{Girshick14}, both in their
 variants trained on 8 viewpoint categories, since these perform best
@@
   \includegraphics[width=0.24\textwidth]{car_cnn/1d.png}  \\  
-%   \hline
-%  \includegraphics[width=0.24\textwidth]{car_cnn/2a.png} &   
-%  \includegraphics[width=0.24\textwidth]{car_cnn/2b.png} &   
-%  \includegraphics[width=0.24\textwidth]{car_cnn/2c.png} &   
-%  \includegraphics[width=0.24\textwidth]{car_cnn/2e.png}  \\  
-%   \hline
+   \hline
+  \includegraphics[width=0.24\textwidth]{car_cnn/2a.png} &   
+  \includegraphics[width=0.24\textwidth]{car_cnn/2b.png} &   
+  \includegraphics[width=0.24\textwidth]{car_cnn/2c.png} &   
+  \includegraphics[width=0.24\textwidth]{car_cnn/2e.png}  \\  
+   \hline
   \includegraphics[width=0.24\textwidth]{car_cnn/4a.png} &   
@@
   reasonably.
-The first column shows bounding boxed produced by R-CNN detection.
+The first column shows bounding boxes produced by R-CNN detection.
 Subsequent columns show the output of our method given this bounding box input.
@@
     \hline\hline
-    aeroplane-4v        & 40.0 / 34.6         & 41.5 / 37.4             & 41.1 / 32.7       & 41.1 / 30.5        & 67.8 / \textbf{41.3}         & 67.8 / 40.8 \\ \hline
-    aeroplane-8v        & 39.8 / 23.4         & 40.5 / 28.6             & 41.1 / 26.8       & 41.1 / 24.2        & 67.8 / 26.8         & 67.8 / \textbf{27.4} \\ \hline
-    aeroplane-16v       & 43.6 / 15.4         & 38.0 / 15.9             & 41.1 / 17.7       & 41.1 / 16.3        & 67.8 / 21.2         & 67.8 / \textbf{21.5} \\ \hline
-    aeroplane-24v       & 42.2 / 8.0          & 36.0 /  9.7             & 41.1 / 10.9       & 41.1 / 10.2        & 67.8 / 15.6         & 67.8 / \textbf{15.7} \\ \hline
-    \hline
+%    aeroplane-4v        & 40.0 / 34.6         & 41.5 / 37.4             & 41.1 / 32.7       & 41.1 / 30.5        & 67.8 / \textbf{41.3}         & 67.8 / 40.8 \\ \hline
+%    aeroplane-8v        & 39.8 / 23.4         & 40.5 / 28.6             & 41.1 / 26.8       & 41.1 / 24.2        & 67.8 / 26.8         & 67.8 / \textbf{27.4} \\ \hline
+%    aeroplane-16v       & 43.6 / 15.4         & 38.0 / 15.9             & 41.1 / 17.7       & 41.1 / 16.3        & 67.8 / 21.2         & 67.8 / \textbf{21.5} \\ \hline
+%    aeroplane-24v       & 42.2 / 8.0          & 36.0 /  9.7             & 41.1 / 10.9       & 41.1 / 10.2        & 67.8 / 15.6         & 67.8 / \textbf{15.7} \\ \hline
+%    \hline
     car-4v              & 37.2 / 20.2         & 45.6 / 36.9             & 47.6 / 42.7       & 47.6 / \textbf{42.7}        & 49.6 / 41.5         & 49.6 / 41.5\\ \hline
@@
     \hline
-    chair-4v            & 11.1 / 6.8          & 8.7  / 6.1              &  11.4 / 7.1       & 11.4 / 6.7         & 25.2 / 10.6         & 25.2 / \textbf{10.7} \\ \hline
-    chair-8v            & 11.4 / 5.9          & 11.3 / 9.4              &  11.4 / 6.6       & 11.4 / 6.6         & 25.2 / \textbf{9.4}          & 25.2 / 9.3 \\ \hline
-    chair-16v           & 12.8 / 6.0          & 10.2 / 6.1              &  11.4 / 4.7       & 11.4 / 4.7         & 25.2 / \textbf{6.7}          & 25.2 / 6.7 \\ \hline
-    chair-24v           & 12.6 / 4.4          & 8.0  / 4.2              &  11.4 / 3.1       & 11.4 / 3.4         & 25.2 / 4.6          & 25.2 / \textbf{5.4} \\ \hline
-    \hline
+%    chair-4v            & 11.1 / 6.8          & 8.7  / 6.1              &  11.4 / 7.1       & 11.4 / 6.7         & 25.2 / 10.6         & 25.2 / \textbf{10.7} \\ \hline
+%    chair-8v            & 11.4 / 5.9          & 11.3 / 9.4              &  11.4 / 6.6       & 11.4 / 6.6         & 25.2 / \textbf{9.4}          & 25.2 / 9.3 \\ \hline
+%    chair-16v           & 12.8 / 6.0          & 10.2 / 6.1              &  11.4 / 4.7       & 11.4 / 4.7         & 25.2 / \textbf{6.7}          & 25.2 / 6.7 \\ \hline
+%    chair-24v           & 12.6 / 4.4          & 8.0  / 4.2              &  11.4 / 3.1       & 11.4 / 3.4         & 25.2 / 4.6          & 25.2 / \textbf{5.4} \\ \hline
+%    \hline
     bicycle-4v          & 45.2 / 41.7         & 46.9 / 43.9             & 48.1 / 47.6       & 48.1 / 46.6        & 61.7 / 56.5         & 61.7 / \textbf{56.7}\\ \hline

### 2015-04-07 intro.tex
extended abstract and Michael's edit

--- 2015-04-01 intro.tex
@@
 result, we can render novel views and train corresponding exemplar
-models {\em on the fly}, without the need for offline processing. We call these NZ-WHO templates \ref{fig:front}. As a
+models {\em on-the-fly}, without the need for offline processing. We call these Non-Zero Whitened Histograms of Orientations (NZ-WHO) templates \ref{fig:front}. As a
 by-product, we can formulate the alignment problem as a parameter
@@
 First, we present a novel method for training exemplar models from
-rendered 3D CAD data {\em on the fly}, enabled by a novel variant of
-WHO, termed NZ-WHO, and making efficient use of the specific
+rendered 3D CAD data {\em on-the-fly}, enabled by a novel variant of
+WHO, termed Non-Zero Whitened Histograms of Orientations (NZ-WHO), and making efficient use of the specific
 characteristics of rendered images. To our knowledge, our method
 constitutes the first attempt to simultaneously render and train
-exemplar detectors on the fly.
-% In our paper, we present Non-Zero Whiten Histograms of Orientations
+exemplar detectors on-the-fly.
+% In our paper, we present Non-Zero Whitened Histograms of Orientations
 % (NZ-WHO) to dramatically speed up the template generation and get rid

### 2015-04-07 mcmc.tex
extended abstract and Michael's edit

@@
 \paragraph{Probabilistic formulation.}
-We parameterize the continuous parameter space as  $p = [v, m, f]$,
+We parameterize the continuous parameter space as  $\theta = [v, m, f]$,
 where $v$ is the 3D rotation of the CAD model, $m$ is the discrete CAD
@@
 
-We model the probability that the object in the test image
-$\mathcal{I}$ is generated by the parameters $p$ as a distribution in
-the exponential family, and let
+We model the probability of an object with the parameter $\theta$ in the test
+image $\mathcal{I}$ as a distribution in the exponential family, and let
 \begin{align}
-    P(p) & \sim e^{ \max_{s} w(p) \ast \mathcal{T}_s(\mathcal{I})},
+    P(\theta| \mathcal{I}) & \sim e^{ \max_{s} w(\theta) \ast \mathcal{T}_s(\mathcal{I})},
 \end{align}
-where $\max_{s} w(p) \ast T_s(\mathcal{I})$ is the maximum convolution score of
-NZ-WHO template $w(p)$ with image features $T_s(\mathcal{I})$ for all scale $s$, as defined
-in Sect.~\ref{sec:nzwho}.
+where $\max_{s} w(\theta) \ast T_s(\mathcal{I})$ is the maximum convolution score of
+NZ-WHO template $w(\theta)$ with image features $T_s(\mathcal{I})$ for all scale
+$s$, as defined in Sect.~\ref{sec:nzwho}.
 
 \paragraph{Inference.}
-We approximate the MAP solution for $p$ by drawing samples from the
-distribution $P(p)$, using the single component Metropolis-Hastings
+We approximate the MAP solution for $\theta$ by drawing samples from the
+distribution $P(\theta | \mathcal{I})$, using the Metropolis-Hastings
 algorithm. Specifically, we use a variant that changes only a single
 component of the parameter vector $p$ at a time, termed Single
-Component Metropolis Hastings \cite{mcmc}.
+Component Metropolis-Hastings \cite{mcmc}.
 
@@
 \begin{align}
-    A(p \rightarrow q) & =  min\left( 1,  \frac{P(q) g(q \rightarrow p)}{P(p) g(p \rightarrow q)}\right).
+    A(\theta \rightarrow \theta^+) & =  min\left( 1, \frac{P(\theta^+ |
+            \mathcal{I}) g(\theta^+ \rightarrow \theta)}{P(\theta | \mathcal{I})
+            g(\theta \rightarrow \theta^+)}\right)
 \end{align}
@@
 (ii)} one of the rotational pose parameters $v_i$, and {\em (iii)} CAD model
-index $m$. For (i) and (ii), we use Gaussian proposal distributions, and a uniform
-distribution over model changes for (iii). We implicitly compute all possible translation and scale by convolving $w(q)$ with a HOG pyramid.
+index $m$. For (i) and (ii), we use Gaussian proposal distributions, and a
+uniform distribution over model changes for (iii). We implicitly compute all
+possible translation and scale by convolving $w(\theta^+)$ with a HOG pyramid.
 \begin{align}
-    g(p \rightarrow p + v_i') & \sim \mathcal{N}(\mu = p_{v_i},\sigma = \sigma_v) \quad i \in \{1,2,3\}\\
-    g(p \rightarrow p + f') & \sim \mathcal{N}(\mu = p_{f},\sigma = \sigma_f)\\
-    g(p \rightarrow p + m') & \sim (1-c) \delta(p_m) + c\,\textrm{Unif}(1,M),
+    g(\theta \rightarrow \theta(v_i^+)) & \sim
+    \mathcal{N}(\theta_{v_i},\sigma_v) \quad \mbox{ for }\; i \in \{1,2,3\}\\
+    g(\theta \rightarrow \theta(f^+)) & \sim \mathcal{N}(\theta_{f}, \sigma_f)\\
+    g(\theta \rightarrow \theta(m^+)) & \sim (1-c) \delta(\theta_m) +
+    c\,\textrm{Unif}(1,M)
 \end{align}
-where $g$ is the proposal distribution. % and $P$ is the distribution of which we
+where $g$ is the proposal distribution, and $m \in \{1,\cdots,M\}$. 
+% and $P$ is the distribution of which we
 %defined using Gaussian distribution around previous state. $A$ is the
@@
     \includegraphics[width=0.7\linewidth]{tuning2} \\ [-5pt]
-    \caption{Search space that our fine-tuning stage handles (Section~\ref{sec:fine}).}
+    \caption{Search space that our fine-tuning stage handles (Sect.~\ref{sec:fine}).}
  \label{fig:moves}
@@
 templates) in order to get promising candidate 2D bounding boxes and
-poses to start from. We then initialize $x_0$ for each of these candidates.
+poses to start from. We then initialize $\theta$ for each of these candidates.

### 2015-04-07 2349_ext.tex
modified ext abstract

@@
 A large body of recent work on object detection has focused on providing more
-than a bounding box of an object. Some exploited 3D CAD
+information than a bounding box of an object. Some used 3D CAD
 model databases to provide viewpoint estimation. These approaches work
@@
 The result is a whitened feature representation, termed WHO (Whitened Histogram
-of Orientations). This development makes it feasible to train hundreds of
-thousands of mid-level patch detectors for recognition.
+of Orientations). This development makes it feasible to train a large number of
+mid-level patch detectors for recognition.
 
-Though it achieved remarkable improvements, generating LDA templates (matrix
-decomposition with Gaussian Elimination) and calibrating them are
-computationally expensive and require gigabytes of memory and storage, while
-the viewpoint discretization hampers pose estimation performance.
+Though generating and calibrating LDA templates (matrix decomposition with
+Gaussian Elimination) achieved remarkable improvements, they are
+computationally expensive and use a prohibitive amount of memory and storage.
+In addition, viewpoint discretization hampers pose estimation performance.
 
@@
   % \includegraphics[width=0.9\linewidth]{schematics} 
-  \includegraphics[width=0.8\linewidth]{front} % \\[-5pt]
+  \includegraphics[width=0.9\linewidth]{front} % \\[-5pt]
   \caption{Using a database of 3D CAD models, we generate NZ-WHO
@@
 
+\vspace{-0.1in}
 \paragraph{Overview}
@@
 offline processing. We call these Non-Zero Whitened Histograms of Orientations
-(NZ-WHO) templates Fig.~\ref{fig:front}. As a by-product, we can formulate the
-alignment problem as a parameter search in a continuous pose space, consisting
-of yaw, pitch and roll, which we implement using MCMC sampling.
+(NZ-WHO) templates. First, we generate an ensemble of NZ-WHO templates to find
+coarse viewpoints and fine-tune them using MCMC. The schematic of our pipeline
+is on Fig.~\ref{fig:front}. As a by-product, we can formulate the alignment
+problem as a parameter search in a continuous pose space, consisting of yaw,
+pitch and roll, which we implement using MCMC sampling.
 
@@
 R-CNN with additional 3D information. By applying our
-method to candidate detections provided by the respective detector, we can
-augment the original detections with an estimate of 3D continuous pose and a 3D
+method to candidate detections provided by the respective detector, we augment the original detections with an estimate of 3D continuous pose and a 3D
 CAD model exemplar.
 
-Finally, we give an in-depth experimental study that demonstrates
-the effectiveness of our approach on a standard benchmark for
+Finally, our in-depth experimental study demonstrates
+the effectiveness of the approach on a standard benchmark for
 object detection and viewpoint estimation~\cite{Xiang14}.
@@
 \begin{tabular}{ccccc}
-  \includegraphics[width=0.2\textwidth]{car_cnn/2c.png} &
-  \includegraphics[width=0.2\textwidth]{car_cnn/2e.png} \\
-  \includegraphics[width=0.2\textwidth]{bicycle_cnn/4b.png} &
-  \includegraphics[width=0.2\textwidth]{bicycle_cnn/4c.png} \\
+  \includegraphics[width=0.18\textwidth]{car_cnn/2c.png} &
+  \includegraphics[width=0.18\textwidth]{car_cnn/2e.png} \\
+  \includegraphics[width=0.18\textwidth]{bicycle_cnn/4b.png} &
+  \includegraphics[width=0.18\textwidth]{bicycle_cnn/4c.png} \\
 \end{tabular}
@@
 
+\vspace{-0.1in}
 \paragraph{Non-Zero Whitened Histograms of Orientations}
@@
 
+\vspace{-0.1in}
 \paragraph{Fine-Tuning using MCMC}
@@
 
+\vspace{-0.1in}
 \paragraph{Experiments}

### 2015-04-08 2349.tex
CVPR cam-ready. reduced the size of images, major updates on the extended cam-ready

@@
 \newcommand{\scream}[1]{{\color{red} \bf *** #1 ***}}
-
 % Pages are numbered in submission mode, and unnumbered in camera-ready
-%\ifcvprfinal\pagestyle{empty}\fi
-\setcounter{page}{1}
+\ifcvprfinal\pagestyle{empty}\fi
+% \setcounter{page}{1}
 \begin{document}
@@
 \maketitle
-%\thispagestyle{empty}
+\thispagestyle{empty}
 
@@
 \paragraph{Acknowledgement}
-This work has been supported by the Max Planck Center for Visual Computing \& Communication.
+We acknowledge the support of NSF CAREER grant (N1054127), Ford-Stanford
+Innovation Alliance Award, DARPA, Korea Foundation for Advanced Studies and
+the Max Planck Center for Visual Computing \& Communication.
 

### 2015-04-08 2349_ext.tex
CVPR cam-ready. reduced the size of images, major updates on the extended cam-ready

@@
 
-\noindent
+\begin{figure}[t]
+  \centering
+  % \includegraphics[width=0.9\linewidth]{schematics} 
+  \includegraphics[width=0.9\linewidth]{front} % \\[-5pt]
+  \caption{Using a database of 3D CAD models, we generate NZ-WHO
+    templates which can be used to either detect objects directly or
+    enrich the output of an existing detector with high-quality,
+    continuous pose and 3D CAD model exemplar.}
+    % initialize pose of an object in the bounding box from other
+    % detectors. Once initialization is given, we use NZ-WHO to propose
+    % and validate plausible pose on-the-fly and
+    % further tune the translation, 3D viewpoint and focal length continuously.}
+  % \vspace{-1em}
+  \label{fig:front}
+\end{figure}
+\vspace{-0.15in}
+
 % In this paper, we propose a novel method for 2D-3D alignment of exemplar CAD
@@
 
+\noindent
 A large body of recent work on object detection has focused on providing more
@@
 by aligning exact 3D models to images using templates generated from renderings
-of the 3D models at a set of discrete viewpoints.
+of the 3D models at a set of discrete viewpoints~\cite{Aubry14}.
 
@@
 
-\begin{figure}[t]
-  \centering
-  % \includegraphics[width=0.9\linewidth]{schematics} 
-  \includegraphics[width=0.9\linewidth]{front} % \\[-5pt]
-  \caption{Using a database of 3D CAD models, we generate NZ-WHO
-    templates which can be used to either detect objects directly or
-    enrich the output of an existing detector with high-quality,
-    continuous pose and 3D CAD model exemplar.}
-    % initialize pose of an object in the bounding box from other
-    % detectors. Once initialization is given, we use NZ-WHO to propose
-    % and validate plausible pose on-the-fly and
-    % further tune the translation, 3D viewpoint and focal length continuously.}
-  % \vspace{-1em}
-  \label{fig:front}
-\end{figure}
+\vspace{-0.15in}
+\paragraph{Overview.} In this paper, we propose a novel method for 2D-3D
+alignment of exemplar CAD models to real-world images that circumvents the need
+for calibration and greatly enhances the scalability of WHO. As a result, we
+can render novel views and train corresponding exemplar models {\em
+	on-the-fly}, without the need for offline processing. We call these Non-Zero
+Whitened Histograms of Orientations (NZ-WHO) templates. To our knowledge, our
+method constitutes the first attempt to simultaneously render and train
+exemplar detectors on-the-fly.
 
-\vspace{-0.1in}
-\paragraph{Overview}
+First, we adapt the whitening to the specific case of rendered images. We show
+how to speed up the whitening by two orders of magnitude for high-resolution
+templates using Conjugate Gradient method. Also, we improve the evaluation of
+our 3D exemplar template detectors at test time by performing convolutions in
+the frequency domain.
 
-In this paper, we propose a novel method for 2D-3D alignment of exemplar CAD
-models to real-world images that circumvents the need for calibration and
-greatly enhances the scalability of WHO. As a result, we can render novel views
-and train corresponding exemplar models {\em on-the-fly}, without the need for
-offline processing. We call these Non-Zero Whitened Histograms of Orientations
-(NZ-WHO) templates. First, we generate an ensemble of NZ-WHO templates to find
-coarse viewpoints and fine-tune them using MCMC. The schematic of our pipeline
-is on Fig.~\ref{fig:front}. As a by-product, we can formulate the alignment
-problem as a parameter search in a continuous pose space, consisting of yaw,
-pitch and roll, which we implement using MCMC sampling.
+These components make template generation and evaluation computationally
+inexpensive. Thus, we are able to efficiently explore the continuous parameter
+space to find the best object pose, scale, 3D CAD model type and camera focal
+length. The schematic of our pipeline is on Fig.~\ref{fig:front}.
 
-First, we present a novel method for training exemplar models from
-rendered 3D CAD data on-the-fly, enabled by a novel variant of
-WHO, termed Non-Zero Whitened Histograms of Orientations (NZ-WHO), and making
-efficient use of the specific characteristics of rendered images. To our
-knowledge, our method constitutes the first attempt to simultaneously render
-and train exemplar detectors on-the-fly.
-
-Second, we demonstrate that our method can enrich the output of an existing
-object class detector, such as the DPM or the
-R-CNN with additional 3D information. By applying our
-method to candidate detections provided by the respective detector, we augment the original detections with an estimate of 3D continuous pose and a 3D
-CAD model exemplar.
-
-Finally, our in-depth experimental study demonstrates
-the effectiveness of the approach on a standard benchmark for
-object detection and viewpoint estimation~\cite{Xiang14}.
+Finally, our experimental study demonstrates the effectiveness of the
+approach on several standard benchmarks for object detection and viewpoint
+estimation. We also demonstrate that our method can enrich the output of an
+existing object class detector, such as the DPM or the R-CNN with additional 3D
+information.
 
@@
 \vspace{-0.1in}
-\paragraph{Non-Zero Whitened Histograms of Orientations}
+\paragraph{Non-Zero Whitened Histograms of Orientations.} Many works that use
+rendering did not take the effect of background into account~\cite{Aubry14}
+when synthesizing and whitening to generate an LDA template. Our NZ-WHO removes
+background region while whitening thus it prevents irrelevant regions from
+corrupting the foreground.
 
-NZ-WHO removes these artifacts so that the background has no effect on the
-template response. Let a vectorized HOG feature of a rendering image $x = [
-x_1^T ,  \cdots , x_n^T ]^T \in \mathcal{R}^{nd}$ where $x_i$ is the $i$th HOG cell feature, $n$ is the
-number of HOG cells and $d$ is the dimension of the HOG feature. We create a new
-vector $\bar{x}$ which contains only the non-zero HOG cell features of $x$.
-Synthesizing the LDA template requires solving the system of linear equations
-$\bar{w}=\bar{\Sigma}^{-1}(\bar{x} - \bar{\mu})$. In \cite{Hariharan12}, the
-authors solve the system via the Cholesky decomposition, which requires
-$O(n^3)$ time. Instead, we introduced the Conjugate Gradient method to generate
-LDA templates. The method runs in $O(n^2\kappa)$ time, where $\kappa$ is the condition number of the matrix and achieved more than 100x speed-up.
+NZ-WHO method greatly speeds up the LDA generation. We introduced the Conjugate
+Gradient method which runs in $O(n^2\kappa)$ time for LDA generation. Finally,
+we experimentally show that our uncalibrated NZ-WHO template performs on par
+with a calibrated WHO template but 100x faster to generate.
 
@@
 \vspace{-0.1in}
-\paragraph{Fine-Tuning using MCMC}
-Due to the speed of our template synthesis procedure, we are able to perform
-joint optimization of scale, translation, continuous rotation, and focal length
-using the Metropolis-Hastings algorithm.
+\paragraph{Fine-Tuning using MCMC.} Due to the speed of our template synthesis
+procedure, we are able to perform joint optimization of scale, translation,
+continuous rotation, and focal length using the Metropolis-Hastings algorithm.
 
@@
 \vspace{-0.1in}
-\paragraph{Experiments}
-
-First, we verify that our NZ-WHO method delivers performance that is
-at least on par with the original WHO formulation~\cite{Hariharan12} in terms of
-accuracy, while at the same time resulting in large computational
-savings.
+\paragraph{Experiments} First, we verify that our NZ-WHO method delivers
+performance that is at least on par with the original WHO
+formulation~\cite{Hariharan12} in terms of accuracy, while at the same time
+resulting in large computational savings.
 
@@
 
+\vspace{-0.1in}
+\paragraph{Acknowledgement.} We acknowledge the support of NSF CAREER grant
+(N1054127), Ford-Stanford Innovation Alliance Award, DARPA, Korea Foundation
+for Advanced Studies and the Max Planck Center for Visual Computing \&
+Communication.
+
 \bibliography{egbib}

### 2015-04-10 2349-supp.tex
cam ready final

--- 2015-04-01 egpaper_supp.tex
@@
 
+\author{Christopher Bongsoo Choy\textsuperscript{\dag}, Michael Stark\textsuperscript{\ddag}, Sam Corbett-Davies\textsuperscript{\dag}, Silvio Savarese\textsuperscript{\dag}\\
+	\textsuperscript{\dag}Stanford University, \textsuperscript{\ddag}Max Planck Institute for Informatics\\
+	{\tt\small \{chrischoy, scorbett, ssilvio\}@stanford.edu, \textsuperscript{\ddag}stark@mpi-inf.mpg.de }
+% For a paper whose authors are all at the same institution,
+% omit the following lines up until the closing ``}''.
+% Additional authors and addresses can be added with ``\and'',
+% just like the second author.
+% To save space, use either the email address or home page, not both
+}
 % \author{First Author\\
@@
 Continuous Viewpoint Estimation''.
+\let\thefootnote\relax\footnote{Please visit \href{https://www.youtube.com/watch?v=YKtioOXY8yQ}{https://www.youtube.com/watch?v=YKtioOXY8yQ} for a biref summary of the paper and MCMC fine-tuning visualizations.}
 % In Sect.~\ref{sec:3dobject}, we present detection result on qualitative results.
@@
 \end{figure*}
-%
-\begin{figure*}[h]
-\setlength\tabcolsep{1pt}
-\centering
-\begin{tabular}{|cc|cc|}
-  \hline
-  \includegraphics[width=0.24\linewidth]{supp/pas_aero1a.jpg} &
-  \includegraphics[width=0.24\linewidth]{supp/pas_aero1b.png} &
-  \includegraphics[width=0.24\linewidth]{supp/pas_aero2a.jpg} &
-  \includegraphics[width=0.24\linewidth]{supp/pas_aero2b.png} \\
-  \includegraphics[width=0.24\linewidth]{supp/pas_aero3a.jpg} &
-  \includegraphics[width=0.24\linewidth]{supp/pas_aero3b.png} &
-  \includegraphics[width=0.24\linewidth]{supp/pas_aero4a.jpg} &
-  \includegraphics[width=0.24\linewidth]{supp/pas_aero4b.png} \\
-  \hline
-  \end{tabular}
-  \caption{Successful detection and pose estimation results on
-    PASCAL3D+~\cite{Xiang14} aeroplanes. Original image (left) and
-  overlaid detection result (right). Proposal bounding box (blue) and
-  predicted bounding box (purple).}
-  \label{fig:pascal3d_aero_good}
-\end{figure*}
+
+% \begin{figure*}[h]
+% \setlength\tabcolsep{1pt}
+% \centering
+% \begin{tabular}{|cc|cc|}
+%   \hline
+%   \includegraphics[width=0.24\linewidth]{supp/pas_aero1a.jpg} &
+%   \includegraphics[width=0.24\linewidth]{supp/pas_aero1b.png} &
+%   \includegraphics[width=0.24\linewidth]{supp/pas_aero2a.jpg} &
+%   \includegraphics[width=0.24\linewidth]{supp/pas_aero2b.png} \\
+%   \includegraphics[width=0.24\linewidth]{supp/pas_aero3a.jpg} &
+%   \includegraphics[width=0.24\linewidth]{supp/pas_aero3b.png} &
+%   \includegraphics[width=0.24\linewidth]{supp/pas_aero4a.jpg} &
+%   \includegraphics[width=0.24\linewidth]{supp/pas_aero4b.png} \\
+%   \hline
+%   \end{tabular}
+%   \caption{Successful detection and pose estimation results on
+%     PASCAL3D+~\cite{Xiang14} aeroplanes. Original image (left) and
+%   overlaid detection result (right). Proposal bounding box (blue) and
+%   predicted bounding box (purple).}
+%   \label{fig:pascal3d_aero_good}
+% \end{figure*}
 
@@
 \centering
-\begin{tabular}{ccc}
+\begin{tabular}{|ccc|}
+	\hline
   \includegraphics[width=0.22\linewidth]{supp/tuning_1a.png} &
@@
   \includegraphics[width=0.22\linewidth]{supp/tuning_6c.png}  \\
+	\hline
   \end{tabular}

### 2015-04-10 2349.tex
cam ready final

@@
 
-\author{Christopher Bongsoo Choy\textsuperscript{\dag}, Michael Stark\textsuperscript{\dag \ddag}, Sam Corbett-Davies\textsuperscript{\dag}, Silvio Savarese\textsuperscript{\dag}\\
+\author{Christopher Bongsoo Choy\textsuperscript{\dag}, Michael Stark\textsuperscript{\ddag}, Sam Corbett-Davies\textsuperscript{\dag}, Silvio Savarese\textsuperscript{\dag}\\
 	\textsuperscript{\dag}Stanford University, \textsuperscript{\ddag}Max Planck Institute for Informatics\\
@@
 We acknowledge the support of NSF CAREER grant (N1054127), Ford-Stanford
-Innovation Alliance Award, DARPA, Korea Foundation for Advanced Studies and
-the Max Planck Center for Visual Computing \& Communication.
+Innovation Alliance Award, DARPA, Fulbright New Zealand, Korea Foundation for
+Advanced Studies and the Max Planck Center for Visual Computing \&
+Communication.
 

### 2015-04-10 2349_ext.tex
cam ready final

@@
 A large body of recent work on object detection has focused on providing more
-information than a bounding box of an object. Some used 3D CAD
+information than the bounding box of an object. One set of methods use 3D CAD
 model databases to provide viewpoint estimation. These approaches work
@@
 
-However, training the template for all viewpoint and CAD models is not feasible
-since gathering all training data for different viewpoint and CAD models is
-expensive.  Instead, it has been realized that template-based exemplar
+However, training templates for all viewpoints and CAD models is not feasible
+since it requires a huge amount of training data to be acquired. Instead, it has been realized that template-based exemplar
 detectors based on HOG features can be trained analytically, by
@@
 
-Though generating and calibrating LDA templates (matrix decomposition with
+Though generating and calibrating LDA templates (via matrix decomposition with
 Gaussian Elimination) achieved remarkable improvements, they are
@@
 space to find the best object pose, scale, 3D CAD model type and camera focal
-length. The schematic of our pipeline is on Fig.~\ref{fig:front}.
+length. An overview of our pipeline can be seen in Fig.~\ref{fig:front}.
 
@@
 estimation. We also demonstrate that our method can enrich the output of an
-existing object class detector, such as the DPM or the R-CNN with additional 3D
+existing object class detector, such as DPM or R-CNN, with additional 3D
 information.
@@
 \paragraph{Non-Zero Whitened Histograms of Orientations.} Many works that use
-rendering did not take the effect of background into account~\cite{Aubry14}
-when synthesizing and whitening to generate an LDA template. Our NZ-WHO removes
-background region while whitening thus it prevents irrelevant regions from
+rendering do not take the background into account
+when synthesizing and whitening to generate an LDA template~\cite{Aubry14}. Our NZ-WHO removes the
+background region while whitening thus preventing irrelevant regions from
 corrupting the foreground.
 
-NZ-WHO method greatly speeds up the LDA generation. We introduced the Conjugate
-Gradient method which runs in $O(n^2\kappa)$ time for LDA generation. Finally,
-we experimentally show that our uncalibrated NZ-WHO template performs on par
-with a calibrated WHO template but 100x faster to generate.
+In addition, our NZ-WHO method uses Conjugate Gradient to greatly speeds up the LDA generation. We show that our uncalibrated NZ-WHO template performs on par
+with a calibrated WHO template while being 100x faster to generate.
 
@@
 image $\mathcal{I}$ as $P(\theta| \mathcal{I}) \sim e^{ \max_{s} w(\theta)
-	\ast \mathcal{T}_s(\mathcal{I})}$. We approximate the MAP solution for $p$ by
+	\ast \mathcal{T}_s(\mathcal{I})}$. We approximate the MAP solution for $\theta$ by
 drawing samples from the distribution $P(\theta | \mathcal{I})$, using the
@@
 object class detection in isolation. It can be applied in a sliding
-window fashion and deliver 2D bounding box as well as viewpoint
+window fashion to deliver 2D bounding boxes and viewpoint
 information. Our method is competitive with the state-of-the-art in this
@@
 detections provided by an existing object class detector, such
-as DPM or RCNN. In this case, we show a considerable performance improvement
-compared to previous work in the task of joint object class detection and VP
-estimation. Example outputs of our model are on Fig.~\ref{fig:pascal12cnn}.
+as DPM or R-CNN. In this case, we show a considerable performance improvement
+compared to previous work in the task of joint object class detection and viewpoint
+estimation. Example outputs of our model are in Fig.~\ref{fig:pascal12cnn}.
 
@@
 (N1054127), Ford-Stanford Innovation Alliance Award, DARPA, Korea Foundation
-for Advanced Studies and the Max Planck Center for Visual Computing \&
+for Advanced Studies, Fulbright New Zealand and the Max Planck Center for Visual Computing \&
 Communication.

### 2015-04-10 experiments.tex
CVPR cam-ready. reduced the size of images, major updates on the extended cam-ready
cam ready final

@@
 
+\vspace{-0.1in}
 \paragraph{Setup.}
@@
 
+\vspace{-0.1in}
 \paragraph{Results.}
@@
     \hline
-    Methods (AP/MPPE) & before calib.  & time & after calib.~\cite{Aubry14} & time \\
+    Methods (AP/MPPE) & before calib.  & synth. time & after calib.~\cite{Aubry14} & calib. time \\
     \hline\hline
@@
   \caption{Average Precision (AP), Mean Precision in Pose Estimation
-    (MPPE)~\cite{Lopez-Sastre11}, and generation time for variations of WHO on
-    3D Object Classes cars~\cite{Savarese07}. Please see text for
-    details.}
+      (MPPE)~\cite{Lopez-Sastre11} of variants of WHO on 3D Object Classes
+      cars~\cite{Savarese07}, and their corresponding synthesis and calibration
+      time per template. Please see text for details.}
   % WHO refers to standard WHO using the
@@
     % \includegraphics[width=0.9\linewidth]{tuning} 
-   \includegraphics[width=0.33\linewidth]{tuning/1.png} &
-   \includegraphics[width=0.33\linewidth]{tuning/2.png} &
-   \includegraphics[width=0.33\linewidth]{tuning/3.png} \\[-5pt]
+   \includegraphics[width=0.33\linewidth]{tuning/1_sm.png} &
+   \includegraphics[width=0.33\linewidth]{tuning/2_sm.png} &
+   \includegraphics[width=0.33\linewidth]{tuning/3_sm.png} \\[-5pt]
 %   (a) & (b) & (c)\\
-   \includegraphics[width=0.33\linewidth]{tuning/4.png} &
-   \includegraphics[width=0.33\linewidth]{tuning/5.png} &
-   \includegraphics[width=0.33\linewidth]{tuning/6.png} \\[-5pt]
+   \includegraphics[width=0.33\linewidth]{tuning/4_sm.png} &
+   \includegraphics[width=0.33\linewidth]{tuning/5_sm.png} &
+   \includegraphics[width=0.33\linewidth]{tuning/6_sm.png} \\[-5pt]
 %   (d) & (e) & (f)\\
@@
 (meaning that we can not improve over their AP). We revert back to a default
-viewpoint prediction ($0$ angles) in case the confidence of our
+viewpoint prediction ($0^\circ$ azimuth) in case the confidence of our
 method falls below a threshold.
@@
 supplemental material.
+
+\vspace{-0.1in}
 \paragraph{Results.}
@@
 \centering
-\begin{tabular}{|ccccc|}
+\begin{tabular}{|c|c|c|c|c|}
   \hline
@@
 %  &\\
-%  \hline
+  \hline
   \includegraphics[width=0.24\textwidth]{bicycle_cnn/4a.png} &   
@@
 \end{tabular}
-\caption{Example enriched bounding boxes. Given R-CNN~\cite{Girshick14}
-  detection bounding boxes, our method predicted 2D-3D matching
-  reasonably.
-The first column shows bounding boxes produced by R-CNN detection.
-Subsequent columns show the output of our method given this bounding box input.
-Blue boxes are R-CNN output and purple boxes are
-  the tightest bounding box enclosing predicted CAD model.}
+\caption{Examples of enriched bounding boxes. Given R-CNN~\cite{Girshick14}
+    detection bounding boxes, our method predicted 2D-3D matching reasonably.
+    The first column shows bounding box candidates produced by R-CNN detection.
+    Subsequent columns show the output of our method given the bounding box
+    from R-CNN detection candidates. Blue boxes are R-CNN output and purple
+    boxes are the tightest bounding box enclosing predicted CAD model.}
   \label{fig:pascal12cnn}
@@
 \centering
-\begin{tabular}{cc}
+\begin{tabular}{c}
 %  \hline
-  \includegraphics[width=0.49\linewidth]{car_cnn4_crop.png} &   
-  \includegraphics[width=0.49\linewidth]{car_cnn8_crop.png} \\   
-  \includegraphics[width=0.49\linewidth]{car_cnn16_crop.png} &   
-  \includegraphics[width=0.49\linewidth]{car_cnn24_crop.png} \\   
+%  \includegraphics[width=0.49\linewidth]{car_cnn4_crop.png}    
+%  \includegraphics[width=0.49\linewidth]{car_cnn8_crop.png} \\   
+%  \includegraphics[width=0.49\linewidth]{car_cnn16_crop.png} &   
+  \includegraphics[width=0.9\linewidth]{car_cnn24_crop.png} \\   
 %  \hline
@@
   and viewpoint confusion table on PASCAL 12 car validation set using
-  R-CNN + Ours (full). From the top left, 4 views, 8 views, 16 views
-  and 24 views.}
+  R-CNN + Ours (full) for 24 views. All four viewpoint discretizations are available on the supplementary paper.}
  % Since our method only augment the object detection,
@@
 
+\vspace{-0.1in}
 \paragraph{Robustness.}

### 2015-04-10 mcmc.tex
CVPR cam-ready. reduced the size of images, major updates on the extended cam-ready
cam ready final

@@
 algorithm. Specifically, we use a variant that changes only a single
-component of the parameter vector $p$ at a time, termed Single
+component of the parameter vector $\theta$ at a time, termed Single
 Component Metropolis-Hastings \cite{mcmc}.
 
-This algorithm changes the current state $p$ to a new state $q$ based
+This algorithm changes the current state $\theta$ to a new state $\theta^+$ based
 on the acceptance probability
@@
 \centering
-    \includegraphics[width=0.7\linewidth]{tuning2} \\ [-5pt]
+    \includegraphics[width=0.7\linewidth]{tuning2_small} \\ [-5pt]
     \caption{Search space that our fine-tuning stage handles (Sect.~\ref{sec:fine}).}
